### 2022-04-26 txt/rigetti.tex
txt and mathematica files

\documentclass[11pt,a4paper,reqno, oneside]{amsart}

\usepackage{amsopn}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsaddr}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{color}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{enumerate}
\usepackage{cite}
\usepackage{todonotes}
\usepackage{amsfonts}

\usepackage[ruled,vlined]{algorithm2e}

\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{geometry}
\usepackage{array}

\usepackage{tikz}
\usetikzlibrary{angles,quotes}
\usetikzlibrary{decorations.pathreplacing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\eg}{{\emph{e.g.\/}}}
\newcommand{\ie}{{\emph{i.e.\/}}}
\newcommand{\etal}{\emph{et al.}}
\providecommand{\keywords}[1]{\newline Keywords: #1}
\providecommand{\sep}{\hspace{-3pt};\xspace}
\providecommand{\pacs}[1]{\newline PACS: #1}
\newcommand{\halmos}{\par\hfill $\Box$\vspace{6pt}}

\providecommand{\proof}{\noindent{\emph{Proof.}}}
\providecommand{\proofof}[1]{\vspace{12pt}\noindent{\emph{Proof of #1.}}}

\newcommand{\LieG}[2]{\ensuremath{\mathds{#1}(#2)}}
\newcommand{\SU}[1]{\LieG{SU}{#1}}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\wek}{\mathbf{vec}}
\DeclareMathOperator{\res}{\mathbf{res}}
\DeclareMathOperator{\Log}{Log}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\unres}{unres}

\newcommand{\qi}{\texttt{QI}}
\newcommand{\QI}{\qi}
\newcommand{\TRQS}{\texttt{TRQS}}
\newcommand{\trqs}{\TRQS}
\newcommand{\Mn}[1]{\ensuremath{\mathds{M}_n({#1})}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\E}{\ensuremath{\mathbb{E}}}
\newcommand{\Z}{\ensuremath{\mathbb{Z}}}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\Complex}{\ensuremath{\mathbb{C}}}

\newcommand{\boldzero}{\ensuremath{\mathbf{0}}}

\newcommand{\boldone}{\ensuremath{\mathds{1}}}
\newcommand{\Cplx}{\ensuremath{\C}}
\newcommand{\HS}[1]{\ensuremath{\mathcal{#1}}}
\newcommand{\QFT}{\ensuremath{\mathrm{QFT}}}
\newcommand{\ket}[1]{\ensuremath{|#1\rangle}}
\newcommand{\bra}[1]{\ensuremath{\langle#1|}}
\newcommand{\ketbra}[2]{\ensuremath{\ket{#1} \! \bra{#2}}}
\newcommand{\proj}[1]{\ensuremath{\ketbra{#1}{#1}}}
\newcommand{\braket}[2]{\ensuremath{\langle{#1}|{#2}\rangle}}
\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}
\newcommand{\complexity}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\new}[1]{ \textcolor{red}{#1} }
\newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\Id}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\connected}{\sim}
\newcommand{\SPAN}{\mathrm{span}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\Lrm}{\ensuremath{\mathrm{L}}}
\newcommand{\Urm}{\ensuremath{\mathrm{U}}}
\newcommand{\ee}{\ensuremath{\mathrm{e}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\ii}{\ensuremath{\mathrm{i}}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\MM}{\mathcal{M}}
\newcommand{\NN}{\mathcal{N}}
\newcommand{\YY}{\mathcal{Y}}
\newcommand{\OO}{\mathcal{O}}
\newcommand{\s}{\mathcal{S}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\TT}{\mathcal{T}}
\newcommand{\CC}{\mathcal{C}}
\newcommand{\PP}{\mathcal{P}}
\renewcommand{\SS}{\mathcal{S}}
\newcommand{\UU}{\mathcal{U}}
\newcommand{\LL}{\mathcal{L}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\VV}{\mathcal{V}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\DU}{\mathcal{DU}}
\newcommand{\NOT}{\sigma_x}
\newcommand{\idop}[1][\XX]{\ensuremath{\1_{#1}}}
\newcommand{\diaguni}{\ensuremath{\mathcal{DU}}}
\newcommand{\diagmodul}{\ensuremath{\mathcal{D}^{\leq 1}_d}}
\newcommand{\inner}[2]{\ensuremath{\langle{#1} \,,{#2}\rangle}}
\newcommand{\ketV}[1]{\ensuremath{|#1\rangle\!\rangle}}
\newcommand{\braV}[1]{\ensuremath{\langle\!\langle#1|}}
\newcommand{\ketbraV}[2]{\ensuremath{\ketV{#1}\braV{#2}}}
\newcommand{\projV}[1]{\ensuremath{\ketbraV{#1}{#1}}}
\newcommand{\braketV}[2]{\ensuremath{\langle\!\langle{#1}|{#2}\rangle\!\rangle}}
\newcommand{\eqdef}{\mathrel{:=}}

%macros for various succes probabilites
\newcommand{\popt}{\tilde{p}_\mathrm{opt}} % minmal error discrimination
%without ent assitance
\newcommand{\poptent}{p_\mathrm{opt}}  % minmal error discrimination withent
%assitance
\newcommand{\pent}{p_\mathrm{u}} % unambigous discrimination with ent assitance
\newcommand{\p}{\tilde{p}_\mathrm{u}}  % unambigous discrimination without ent
%assitance

%\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newtheorem{scheme}{Scheme}

\title{Benchmarking of Rigetti architecture}

\author{Paulina Lewandowska$^{1}$, Aleksandra Krawiec$^{1}$, Konrad Ja\l 
owiecki$^1$ and \L ukasz Pawela* $^{1}$}

\address{$^1$Institute of Theoretical and Applied Informatics, Polish
Academy of Sciences, ul. Ba{\l}tycka 5, 44-100 Gliwice, Poland}

\begin{document}
\maketitle
$^{*}$ \normalsize{E-mail address: \url{lpawela@iitis.pl}}
\begin{abstract}

\end{abstract}

\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Consider the following scenario. There is an unknown measurement device and the
only thing we know about it is that it performs one of two known measurements,
call them $\mathcal{S}$ and $\mathcal{T}$. We put a state into the device and
our goal is to decide which of the measurements is performed. We aim to identify
the assumptions needed for perfect discrimination of $\mathcal{S}$ and $\TT$.
Further, we want to construct the optimal discrimination scheme for this task. 
In
the case when perfect distinctions is not possible, we would like to bound
from above the probability of correct discrimination as well as derive a scheme
which enables a correct guess with the optimal probability.

The second field of our interest is finding the optimal strategy for the
discrimination. In other words, we would like to know which state should be used
to provide the greatest possible probability of correct discrimination.

In the simplest approach we may think of measurements $\mathcal{S}$ and $\TT$
as measure-and-prepare channels outputting diagonal states, that is classical
probability distributions, see Fig.~\ref{fig:non-ent-disc}. This notion will be
formalized in later sections. Thus, the simplest approach to this problem is to
consider the distance between probability distributions. We can use the distance
between these distributions as an upper bound on the probability of correct
discrimination. In this setting it is also straightforward to find the optimal
state for the discrimination.

Of course, there is another possibility. As we are dealing with quantum states,
we can utilize entanglement. Hence, we input one part of the entangled state
into the unknown measurement device and later use the other part to strengthen
the inference. The scheme of this process is presented in
Fig.~\ref{fig:diamond}.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{gatewe.pdf}
	\caption{
		A schematic representation of the setup for distinguishing 
		measurements without entanglement.}
	\label{fig:non-ent-disc}
\end{figure}

\begin{figure}[h!]
	\centering 
	\includegraphics[width=0.9\linewidth]{gates1.pdf}

	\caption{ A schematic representation of the setup for distinguishing
		measurements using entangled states. One of two known measurements $\mathcal{S}$
		or $\TT$ is performed on part $A$ of the input state $\ket{\psi_{AB}}$. We use
		the output label $i$ and perform a conditional binary measurement
		$\mathcal{R}_i$ on part $B$. By the use of its output we formulate our guess, 
		that is we decide  
		weather
		the measurement performed on part $A$ was $\mathcal{S}$ or $\TT$.
	}\label{fig:diamond}
\end{figure}

\newpage
\section{Problem formulation } 
Consider two von Neumann measurements $\PP_U$ and $\PP_{\Id}$ for  \begin{equation}
U = H_2 \left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H_2^\dagger,
\end{equation}
where
$U$ is unitary matrix parameterized by angle $\phi \in [0, 2\pi)$ and $H_2$ is Hadamard matrix.

\subsection{Holevo-Helstrom theorem}
The celebrated result by Helstrom gives an upper
bound on the probability of correct distinction between two von Neumann measurements
$\PP_U$ and $\PP_{\Id}$ in terms of their distance with the use of the diamond norm
\begin{equation}
p \leq \frac12 + \frac14 \| \PP_U - \PP_{\Id} \|_\diamond.
\end{equation}

\begin{theorem}(Tw. 1 from \cite{puchala2018strategies})\label{th:minE}
	Let $U\in \UU_d$ and let $\PP_U$ and $\PP_\Id$ be two von Neumann 
	measurements. 
	Let also 
	$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$. Then
	\begin{equation}
	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond,
	\end{equation}
	where $\Phi_U$ is unitary channel.
\end{theorem}

\subsection{Discrimination of unitary channels}

Before we proceed to presenting our main results, we need to briefly discuss the
problem of discrimination of unitary channels. This can be done without the
usage of entangled input. In order to formulate the condition for perfect
discrimination of unitary channels we introduce the notion of numerical range of
a matrix $A \in M_d$, denoted by $W(A) =\{\bra{x}A\ket{x}: \ket{x} \in \C^d, \;
\;\braket{x}{x}=1\}$. The celebrated Hausdorf-T\"oplitz
theorem states that
$W(A)$ is a convex set and therefore $W(A) =\{\tr A \sigma : \sigma \in \Omega_d
\}$. Let us now recall the well-known result for the
distinguishability of unitary channels.
	Let $U \in \UU_d$ and $\Phi_U: \rho \mapsto U \rho U^\dagger$ be a unitary 
	channel. 
	Then 
	\begin{equation}
	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
	\end{equation}
	where $\nu = \min_{x \in W(U^\dagger)} |x|  $.

\begin{proposition}
 Let $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ and	let 
 $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
	\begin{equation}
	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
	\Phi_\Id\|_\diamond
	\end{equation}
\end{proposition}
\begin{proof} We know that
$
	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
$
	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. For $U = H_2 \left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H_2^\dagger$ we obtain that $\nu = \frac{|1 + e^{i \phi} | }{2}$. 
	The condition $ 	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
	\Phi_\Id\|_\diamond $ is equivalent to prove that
	\begin{equation}
	\max_{E \in \diaguni_2 } \nu_E = \nu = \frac{|1 + e^{i \phi} | }{2},
	\end{equation}
	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $ We can prove that
	\begin{equation}
	\min_{\ket{x} \in \CC^2  \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = \min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
	\end{equation}
For that, to calculate $\nu_E$ we obtain \begin{equation}
	\max_{E \in \diaguni_2 } \nu_E  = \max_{E \in \diaguni_2 }  \min_{\rho \in \Omega_2} \left| \tr \rho U E  \right|
\end{equation}
For that, our task is reduce to show that
	\begin{equation}
	\forall E \in \diaguni_2 \,\, | \tr \rho U E | \le \nu. 
	\end{equation}
	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ and let us take $\rho = \left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
	From spectral theorem, let us note $U$ as
	\begin{equation}
	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
	\end{equation}
	where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$, whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.

	Then we have 
	\begin{equation}
	\begin{split}
	& \forall E \in \diaguni_2 \,\,\, | \tr \rho U E | = \frac{1}{2}  \left| \tr H_2 \diag(1, e^{i\phi}) H_2^\dagger E \right| =  \\ &
	\frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) \right|  = 
	\frac{1}{2} \left| e^{i \phi}  \bra{x_1} E \ket{x_1} + \bra{x_2} E \ket{x_2} \right| = \\& 
	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| = 
	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le \nu, 
		\end{split}
	\end{equation}
	which completes the proof.
\end{proof}

\begin{remark}
	The probability of correct discrimination of von Neumann measurements 
	$\PP_U$ and $\PP_{\Id}$ for $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, 
	where $\phi \in [0, 2\pi)$ is given by
	\begin{equation}
	p \le \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
	\end{equation}
\end{remark}

\subsection{Form of discriminator}
On the other hand, for Hermiticity-preserving $\Phi$, we have the following 
alternative formula for the diamond norm

\begin{equation}\label{eqn:diamond-sqrt}
\|  \Phi \|_\diamond = \max_\rho \left\|(\1\otimes \sqrt{\rho}) J(\Phi) 
(\1\otimes 
\sqrt{\rho})\right\|_1.
\end{equation}
The state $\rho$, for which $\|  \Phi \|_\diamond=\left\|(\1\otimes 
\sqrt{\rho}) 
J(\Phi) (\1\otimes 
\sqrt{\rho})\right\|_1$, will be called a \textit{discriminator}.

\begin{theorem}\label{rozrpomiarow}
Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ such that $0 \not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
	\begin{enumerate}
		\item $\rho_1,\rho_2 \in \Omega_2$
		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
	\end{enumerate}
	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of $U$. Then  we have 
	\begin{equation}
	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i \phi}}{2}\right|^2}.
	\end{equation}
	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą wartością własną $U\in \mathrm{U}(\XX)$.
\end{theorem}
\begin{proof} From \ref{th:minE} we have 
	\begin{equation}
	\begin{split}
	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} ||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in \diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) ||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || \Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| \Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
	\end{split}
	\end{equation}
The diamond norm between two unitary channels can be calculated by 
	\begin{equation}
	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = \min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
	\end{equation}
Hence,  it is enough to calculate the formula
\begin{equation}
\begin{split}
\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
\end{split}
\end{equation}
Recall, let us note $U$ as
\begin{equation}
U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
\end{equation}
where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$, whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$. 
Consider two cases:

	$1^\circ$ Consider $\phi = \pi$. Then $U$ is of the form
	\begin{equation}
	U = \left(\begin{array}{cc}0&1\\1&0\end{array}\right).
	\end{equation}
Then $0 \in W(U)$. 	From Proposition 3 in ~\cite{puchala2018strategies} the measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if and only if there exists $\rho \in \Omega_2$ such that
	\begin{equation}
	\mathrm{diag}\left(U^\dagger \rho\right) = 0.
	\end{equation}
Hence, for $U $ we have 
	\begin{equation}
	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} \left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right) =  \mathrm{diag} \left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
	\end{equation}
 It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the form
	\begin{equation}
	\rho = \left(\begin{array}{cc}\rho_{1,1}&0\\0&\rho_{2,2}\end{array}\right),
	\end{equation}
	where $\rho_{1,1},\rho_{2,2} \ge 0$ and  $\rho_{1,1}+\rho_{2,2}=1$.

	$2^\circ$ Consider  $\phi \not = \pi$. 
The spectrum of $U$ is of the form $\sigma(U) = \{e^{\mathbf{i} \phi},1\}$. Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
	\begin{equation}
	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
	\end{equation}
Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = \ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 \in \Omega_2$ and satisfies the requirements of theorem. Hence, the discriminator $\rho \in \Omega_2$ has the form 
	\begin{equation}
	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = \left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
	\end{equation}
%and 
%	\begin{equation}
%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 + e^{\mathbf{i} \phi}}{2}\right|^2 },
%	\end{equation}

%	
%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we have 
%	\begin{equation}
%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 \right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = \frac{\lambda_1+\lambda_2}{2}. 
%	\end{equation}
%	Therefore, we have
%	\begin{equation}
%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- \left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
%	\end{equation}
%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. Then we have 
%	\begin{equation}
%	\begin{split}
%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E \right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = \frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} \lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} \left(\lambda_1 + \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
%	\end{split}
%	\end{equation} 
%So we have 
%	\begin{equation}
%	\left|\tr\left(UE \rho \right) \right| = \left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 \bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} \right|.
%	\end{equation}
%	It implies that
%	\begin{equation}
%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  |\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
%	\end{equation}
%	Hence we obtain
%	\begin{equation}
%	\begin{split}
%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 -\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
%	\end{split}
%	\end{equation}
For $\rho =  \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we obtain
	\begin{equation}
	\begin{split}
	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} = \\& \sum_{i=1}^2  \sqrt{\left(\bra{i}U^\dagger\rho U \ket{i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho U \ket{i}|^2} = \\& \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + \lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i} \left| \frac{\lambda_1 + \lambda_2}{2}\right|^2} = \\&  \sum_{i=1}^2 2 \bra{i} \rho \ket{i} \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = 
	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } ,
	\end{split}
	\end{equation}
which completes the proof.
\end{proof}

\begin{remark}\label{lemma:rho}
	Let $\rho_{0} = \frac{1}{2} 
	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)$. Then 
	\begin{equation}
	 \max_\rho \left\|(\1\otimes \sqrt{\rho}) J(\PP_U - \PP_{\Id}) 
	(\1\otimes 
	\sqrt{\rho})\right\|_1 =    \left\|(\1\otimes \sqrt{\rho_0}) J(\PP_U - 
	\PP_{\Id}) 
		(\1\otimes 
		\sqrt{\rho_0})\right\|_1
	\end{equation}
	for  $U = H_2\diag(1, e^{i \phi}) H_2^\dagger $, 
		where $\phi \in [0, 2\pi)$. 
\end{remark}

\begin{scheme}\label{remark:discriminator}

Let us consider the problem of discrimination of von Neumann measurements 
$\PP_U$
and $\PP_{\Id}$ for $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, 
	where $\phi \in [0, 2\pi)$. The schematic representation of theoretical 
	setup is shown in Fig.~\ref{fig:theoretical}. 
\begin{figure}[h!]
	\centering 
	\includegraphics[width=0.75\linewidth, angle=-90]{rys-theoretical.jpg}

	\caption{ A schematic representation of the setup for distinguishing
		measurements using entangled states. One of two known measurements 
		$\mathcal{P}_U$
		or $\PP_\Id$ is performed on part $A$ of the input state $\ket{\psi}$. 
		We use
		the output label $i$ and perform a conditional binary measurement
		$\mathcal{P}_{V_i}$ on part $B$. By the use of its output we formulate 
		our guess, 
		that is we decide  
		weather
		the measurement performed on part $A$ was $\mathcal{P}_U$ or 
		$\PP_\Id$. In out approach, if  $ j = 0$ we decide  $\PP_U$, if
		$j = 1$ we decide $\PP_{\Id}$. 
	}\label{fig:theoretical}
\end{figure} 
From ~\cite{puchala2018strategies}(Proposition 4) and Lemma~\ref{lemma:rho} we 
have 
	\begin{equation}
	\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
	\rangle \rangle. 
	\end{equation}
	From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
	Let us define \begin{equation}
	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
	\otimes \Id_2 \right)(\proj{\psi})
	\end{equation}
	where $\ket{\psi}$ is defined in Remark~\ref{remark:discriminator}. From 
	Hahn-Jordan decomposition let \begin{equation}
	X = P - Q
	\end{equation}
	where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $im(P)$ and $im(Q)$, 
	respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
	\begin{equation}
	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
	\end{equation}
	and 
	\begin{equation}
	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right) 
	\end{equation}
	Hence, we define $V_0$ such that
	\begin{equation}
	\begin{split}
	V_0 \ket{x_p} = \ket{0} \\ 
	V_0 \ket{x_q} = \ket{1}
	\end{split}
	\end{equation}
	and $V_1$ such that
	\begin{equation}
	\begin{split}
	V_1 \ket{y_p} = \ket{0} \\ 
	V_1 \ket{y_q} = \ket{1}
	\end{split}
	\end{equation}
	The explicit form of $V_0$ and $V_1$ we can see in \texttt{one-qubit.nb}.
	Finally, we obtain the measurement $\mu$ of the form
	\begin{equation}
	\begin{split}
	 \mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
	 \proj{0} V_1^\dagger  \\ 
	\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
	\proj{1} V_1^\dagger  
	\end{split}
	\end{equation}
\end{scheme}
This scheme is only theoretical. It is not possible to implement it on Rigetti 
architecture. For this, we will consider two approaches. The first one is 
described 
by using postselection whereas the second one is considered by implementation 
of controlled unitary gate. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Construction of $V_0$ and $V_1$}
	It turned out that for case $\phi = \frac{k \pi}{16}$, where $k=0,\ldots,31$ the controlled unitary $V_0$ and $V_1$ have the following form
	\begin{equation}
	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi(16-k)}{64} \right)&-i \cos\left( \frac{\pi(16-k)}{64} \right)\\ \cos\left( \frac{\pi(16-k)}{64} \right)& \sin\left( \frac{\pi(16-k)}{64} \right)\end{array}\right) 
	\end{equation}

		\begin{equation}
	V_1 = \left(\begin{array}{cc}-i \cos\left( \frac{\pi(16-k)}{64} \right) &i \sin\left( \frac{\pi(16-k)}{64} \right)\\\sin\left( \frac{\pi(16-k)}{64} \right) &  \cos\left( \frac{\pi(16-k)}{64} \right) \end{array}\right) 
	\end{equation}

\newpage
\begin{scheme}(By using postsellection)

\begin{figure}[h!]
	\centering 
	\includegraphics[width=0.75\linewidth, angle=-90]{rys-postsellection.jpg}

	\caption{ A schematic representation of the setup for distinguishing
		measurements using postselection. 
	}\label{fig:postsellection}
\end{figure}
\begin{enumerate}
\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
\rangle. $
\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
\item We implement unitary $V_0 $ or $ V_1$.
\item We prepare the measurement $\Delta$ in standard basis (already exist on 
Rigetti architecture) on each qubits.
\item We calculate the probability of correct discrimination in the following 
way
\begin{equation}
p = ...
\end{equation}
\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
\end{enumerate}
\end{scheme}

\newpage
\begin{scheme}(By using controlled unitary)
\begin{figure}[h!]
	\centering 
	\includegraphics[width=0.75\linewidth, angle=-90]{rys-controlled.jpg}

	\caption{ A schematic representation of the setup for distinguishing
		measurements using controlled unitary gate. 
	}\label{fig:controlled}
\end{figure}
\begin{enumerate}
\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
\rangle. $
\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
\item We implement controlled unitary $V_0 \oplus V_1$.
\item We prepare the measurement $\Delta$ in standard basis (already exist on 
Rigetti architecture) on each qubits.
\item We calculate the probability of correct discrimination in the following 
way
\begin{equation}
p = \frac{|j=0 \wedge \Phi_{U} | + |j=1 \wedge \Phi_{\1}|}{\text{all 
cases}}
\end{equation}
\end{enumerate}
\end{scheme}

\section*{Acknowledgments}

This work was supported by the project ,,Near-term quantum computers Challenges, 
optimal implementations and applications'' under
Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the 
Team-Net programme of the
Foundation for Polish Science co-financed by the European Union under the European Regional
Development Fund.

\bibliographystyle{ieeetr}
\bibliography{rigetti.bib}

\end{document}

### 2022-05-16 txt/rigetti.tex
v0 and v1 analitical form

@@
 architecture. For this, we will consider two approaches. The first one is 
-described 
-by using postselection whereas the second one is considered by implementation 
+described  by using postselection whereas the second one is considered by implementation 
 of controlled unitary gate. 
@@
 \subsection{Construction of $V_0$ and $V_1$}
-	It turned out that for case $\phi = \frac{k \pi}{16}$, where $k=0,\ldots,31$ the controlled unitary $V_0$ and $V_1$ have the following form
+	For each $\phi \in \R$,  the controlled unitary $V_0$ and $V_1$ have the following form
 	\begin{equation}
-	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi(16-k)}{64} \right)&-i \cos\left( \frac{\pi(16-k)}{64} \right)\\ \cos\left( \frac{\pi(16-k)}{64} \right)& \sin\left( \frac{\pi(16-k)}{64} \right)\end{array}\right)
+	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i \cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - \phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
 	\end{equation}
@@
 		\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left( \frac{\pi(16-k)}{64} \right) &i \sin\left( \frac{\pi(16-k)}{64} \right)\\\sin\left( \frac{\pi(16-k)}{64} \right) &  \cos\left( \frac{\pi(16-k)}{64} \right) \end{array}\right)
+	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i \sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
 	\end{equation}
@@
 \item We implement unitary $V_0 $ or $ V_1$.
-\item We prepare the measurement $\Delta$ in standard basis (already exist on 
+\item We prepare the measurement $\Delta$ in standard basis (already exists on 
 Rigetti architecture) on each qubits.

### 2022-06-15 txt-softwarex/SoftwareX_article_template.tex
softwarex formatka

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

\usepackage{float}

\usepackage{todonotes}

\restylefloat{table}

\newcommand{\eg}{{\emph{e.g.\/}}}
\newcommand{\ie}{{\emph{i.e.\/}}}
\newcommand{\ket}[1]{\ensuremath{|#1\rangle}}
\newcommand{\bra}[1]{\ensuremath{\langle#1|}}
\newcommand{\ketbra}[2]{\ensuremath{\ket{#1}\bra{#2}}}
\newcommand{\proj}[1]{\ensuremath{\ketbra{#1}{#1}}}
\newcommand{\braket}[2]{\ensuremath{\langle{#1}|{#2}\rangle}}
\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}
\newcommand{\complexity}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\new}[1]{ \textcolor{red}{#1} }
\newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\Id}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\connected}{\sim}
\newcommand{\SPAN}{\mathrm{span}}
\newcommand{\Lrm}{\ensuremath{\mathrm{L}}}
\newcommand{\Urm}{\ensuremath{\mathrm{U}}}
\newcommand{\ee}{\ensuremath{\mathrm{e}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\ii}{\ensuremath{\mathrm{i}}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\MM}{\mathcal{M}}
\newcommand{\NN}{\mathcal{N}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\TT}{\mathcal{T}}
\newcommand{\PP}{\mathcal{P}}
\renewcommand{\SS}{\mathcal{S}}
\newcommand{\UU}{\mathcal{U}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\DU}{\mathcal{DU}}
\newcommand{\NOT}{\sigma_x}
\newcommand{\idop}[1][\XX]{\ensuremath{\1_{#1}}}
\newcommand{\diaguni}{\ensuremath{\mathcal{DU}}}
%\DeclareMathOperator{\diag}{diag}
%\DeclareMathOperator{\diag}{diag}
\journal{SoftwareX}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Benchmarking on Rigetti architecture}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{Paulina Lewandowska}
\author{\L ukasz Pawela}

\address{Institute of Theoretical and Applied Informatics, Polish Academy
	of Sciences, Ba{\l}tycka 5, 44-100 Gliwice, Poland}

\begin{abstract}
We introduce library ?, a comprehensive open source framework for benchmarking Amazon Braket Rigetti IonQ architectures ? 
The framework is built around  the scheme of discrimination of von Neumann measurements. The library provides algorithm for ... Our main aim is creating a common platform  for open research.  ?

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Benchmarking of Rigetti architecture \sep Discrimination of quantum measurements \sep Von Neumann measurements discrimination

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}

Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & For example v42 \\
\hline
C2 & Permanent link to code/repository used for this code version & For example: $https://github.com/mozart/mozart2$ \\
\hline
C3 & Code Ocean compute capsule & For example: $https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
\hline
C4 & Legal Code License   & List one of the approved licenses \\
\hline
C5 & Code versioning system used & For example svn, git, mercurial, etc. put none if none \\
\hline
C6 & Software code languages, tools, and services used & For example C++, python, r, MPI, OpenCL, etc. \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & \\
\hline
C8 & If available Link to developer documentation/manual & For example: $http://mozart.github.io/documentation/$ \\
\hline
C9 & Support email for questions & \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\linenumbers

%% main text

The permanent link to code/repository or the zip archive should include the following requirements:

README.txt and LICENSE.txt.

Source code in a src/ directory, not the root of the repository.

Tag corresponding with the version of the software that is reviewed.

Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.

\section{Motivation and significance}

Noisy intermediate-scale quantum
(NISQ)~\cite{preskill} devices are currently storming the market. We
have a selection of readily available quantum computers based on different
architectures. Historically, the first widely introduced quantum computing
architecture is D-Wave's quantum annealer~\cite{}.

https://quantumcomputingreport.com/scorecards/qubit-technology/

Additional approaches to quantum computing are currently in development. For 
instance we have Ionq's computer based on ion traps and Xanadu's optical 
lattices. As they are in prototype versions no access to general public is 
provided.

Next, we have computers implementing the gate model of quantum computation.
These are the best potentially developed machines, which can be thought
of as fully quantum computers, by which we understand that the qubits can be in
an entangled state.

Currently one of the main providers of such architectures is Rigetti and its Quantum Cloud Services platform. The company has
released three generations of QPUs so far: Rigetti 8Q Agave, Rigetti 19Q Acorn
and Rigetti 16Q Aspen-1. The most recent one was deployed in November 2018 and
is a downgrade in terms of number of qubits compared to the previous 19 qubit
one. However, the new chip is reportedly much more robust to noise and the
proposed architecture is much easier to scale up. The new unit is supposed to
serve as a building block for a 128 qubit
system~\footnote{https://medium.com/rigetti/the-rigetti-128-qubit-chip-and-what-it-means-for-quantum-df757d1b71ea}.
As was the case for IBM, Rigetti also provides a \texttt{Python} library, 
\texttt{pyquil}~\cite{}, which enables easy access to the machine.

\todo[inline]{co napisac o tym Amazonie, czy nic ?}

\todo[inline]{rysunki architektur}

%
%\begin{figure}[h]
%	\centering 
%	
%	\includegraphics[width=0.9\linewidth]{aspen.png} 
%	\caption{?}
%	\label{fig:aspen}
%\end{figure}

Now the natural question arises: how to construct a good metric of the
computational power of such devices? 
Lately, there have emerged propositions from the scientific community on how to
benchmark such devices.

 First let us mention the work by Michielsen
\emph{et.al.}~\cite{michielsen2017benchmarking}. In there the authors study the
IBM-QE device. Their first test is the creation of the entangled state
$\frac{1}{\sqrt{2}} (\ket{01} - \ket{10})$. Next they implement a
two-qubit+two-qubit adder. Another test is an identity operation, realized by an
even number of CNOT operations. Their final test is a quantum error correction
scheme (is it possible with measurement-controlled-operations?). The final
conclusion is that, except for simple circuits, the device fails to return
correct results.

Another, recent approach is utilizing quantum communication protocols in testing
of quantum architectures~\cite{zhukov2019quantum}. Here, the authors decide to
utilize superdense coding and the BB84 quantum cryptography protocol as
benchmarks for the IBM Q devices. They utilize the mutual information of the
transferred bits as a figure of merit for the quantum computer.

Other approaches focus on generative model training. One of these
works~\cite{hamilton2018generative} is aimed at small architectures, up to 5
qubits. Another recently presented is much more
robust~\cite{benedetti2018generative}. The main drawback of both of them is the
level of complication.

The goal of this work is to introduce a new benchmark for Rigetti architecture...

\label{}
\todo[inline]{
	Introduce the scientific background and the motivation for developing the software. - motywacje

	Explain why the software is important, and describe the exact (scientific) problem(s) it solves. - czemu ejst wazne, jakie problemy rozwiazuje

	Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software. - do czego sie to przyczyni w przyszlosci

	Provide a description of the experimental setting (how does the user use the software?). - w jaki sposób użytkownik korzysta z oprogramowania?

	Introduce related work in literature (cite or list algorithms used, other software etc.). - inne oprogramowania i algorytmy }

\section{Software description}
\label{}
\todo[inline]{Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact. }

We will first give a general overview of the structure of the code in Section~\ref{sec:sortware-architecture} and then provide additional details on the functionality of benchmark's schemes  in Section~\ref{sec:sortware-functionalities}.

\subsection{Software Architecture}\label{sec:sortware-architecture}
\label{}
\todo[inline]{
	Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.}

\subsection{Software Functionalities}\label{sec:sortware-functionalities}
\todo[inline]{Present the major functionalities of the software.}

In the scope of this Paper, we aim at  exploring ideas revolving around quantum gate model-inspired computing devices, and assess their feasibility to benchmark a modern quantum architectures. The main idea that we have envisioned for this project is  introducing new concepts of algorithms for NISQ devices benchmarking. This project aims to characterize the computing power and investigate possible practical applications of such devices having access by Amazon Braket.  First of all, we will focus on constraining quantum algorithms being relatively easy to implement on quantum architectures with straightforward, intuitive operational interpretation. Moreover, we need to possess a scalability, that is the ability to adjust to large range of architectures size.  
These properties will give us major advantage over the existing approaches  of benchmarking.

This idea is built upon two specific tasks that are to be achieved within this proposal. 
The first task is to   desing a benchmark based on discrimination of von Nemaumm measurements scheme. While the second one is to extension  this approach to benchmark on the grounds of certification of von Neumann measurements scheme.

\subsubsection{Model specification}
Theoretically, scenario of this set up assume that Alice and Bob have an unknown measurement device, black--box.  Alice has hiden one of the two measurements  in the black box.  The only information which Bob has is that it performs one of such  measurements. 
The  goal of discrimination of von Neumann measurements  is to determine by Bob whether it is possible to discriminate measurements perfectly, i.e. with probability equals one. If this is not possible, he  would like to know the upper bound of such a probability.  Theoretical results of discrimination of von Neumann measurements is well-known and characterized in~\cite{puchala2018strategies}.    The scheme of von Neumann discrimination is presented in Fig.~\ref{fig:scheme} and 
can be divided into the following steps:

\begin{enumerate}
	\item Alice and Bob share entanglement state $\ket{\psi_{AB}}$.
	\item Alice performs one of two known measurements on part $A$ of the input state  $\ket{\psi_{AB}}$.
	\item Alice  uses
	the output label $i$ and performs a conditional binary measurement on part $B$.
	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and makes a decision  basis of the condition binary measurement.
\end{enumerate}

\begin{figure}[h]
	\centering

	\includegraphics[width=0.9\linewidth]{gates1.pdf} 
	\caption{A schematic representation of the setup for distinguishing
		measurements by using entanglement. }
	\label{fig:scheme}
\end{figure}

\subsubsection{Theoretical results}

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity notation, square matrices will be denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$ will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is positive semidefinite operators having
trace equal to one, will be denoted $\DD_d$.  The subset of $M_d$ consisting of unitary matrices will be denoted by
$\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  An unitary transformation 
\todo[inline]{channel} CPTP

$\Phi_{U}$ is defined as $\Phi_U(\cdot) := U \cdot U^\dagger$ for  $U \in \UU_d$. A general quantum
measurement, that is a positive operator valued measure (POVM) $\PP$ is a
collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
all the effects are rank-one projection operators, then such a measurement is
called von Neumann measurement. Every von Neumann measurement can be
parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
for a von Neumann measurement with effects $\{\proj{u_1}, \ldots, \proj{u_d}\}$,
where $\ket{u_i}$ is the $i$-th column of the unitary matrix $U$. The action of
quantum measurement $\PP_{U}$ on some state $\rho \in \mathcal{D}_d$ can be
expressed as the action of a quantum channel
$
\PP_{U} : \rho \rightarrow \sum_{i=1}^d \bra{u_i} \rho \ket{u_i} \proj{i}.
$ Every von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta \circ \Phi_{(UE)^\dagger}$, where $\Delta$ denotes the completely dephasing channel.

Let us now consider linear mappings transforming  square matrices into square 
matrices 
that is \ $\Phi: M_{d_1} \to M_{d_2}$. 
 We define its completely bounded trace
	norm, also known as a diamond norm, as
	\begin{equation}
	\|\Phi\|_\diamond = \max_{\|X\|_1=1} \| \left(\Phi \otimes \1\right) (X) \|_1.
	\end{equation}

The celebrated result by Helstrom~\cite{helstrom1976quantum} gives an upper
bound on the probability of correct distinction between two quantum channels
$\Phi$ and $\Psi$ in terms of their distance with the use of the diamond norm
\begin{equation}
p \leq \frac12 + \frac14 \| \Phi - \Psi \|_\diamond.
\end{equation}

In the general case, the diamond norm of a Hermiticity-preserving maps $\Phi$ can be computed using the Semidefinite Program~\cite{watrous2018theory} and state 
primal and dual problem in the following form:

%
%\begin{minipage}{0.495\linewidth}
%	\begin{equation*}
%		\begin{split}
%			\text{\textbf{Primal problem:}} \\
%			\text{maximize:}\quad & \tr(X J(\Phi)) \\[2mm]
%			\text{subject to:}\quad &  \left[ \begin{array}{cc}\Id_{d_2} \otimes \rho & X \\ X^* & \Id_{d_2} \otimes \rho  \end{array} \right] \ge 0 \\
%			& \rho \in \HH_d^+\\ 
%			& X \in M_{d1,d2}.
%		\end{split}
%	\end{equation*}
%\end{minipage}
%\begin{minipage}{0.495\linewidth}
%	\begin{equation*}
%		\begin{split}
%			\text{\textbf{Dual problem:}} \\
%			\text{minimize:}\quad & ||\tr_1(Y)||_\infty \\[2mm]
%			\text{subject to:}\quad & \left[ \begin{array}{cc}Y & -J(\Phi) \\ -J(\Phi) &  Y \end{array} \right] \ge 0 \\
%			& Y \in \HH_{d_1d_2}^+.
%		\end{split}
%	\end{equation*}
%	\vspace{0.5cm}
%\end{minipage}

\subsubsection{Rigetti architecture's limits/ practical solutions}
\todo[inline]{nie wiem, moze tu o conditional measurement i o sposobach ominiecia tego problemu - postselekcja i kontrolowana unitarka}

We may encounter numerous obstacles in the implementation process due to the limited architecture of quantum computer. 
Let us take a closer look at the setup for distinguishing von Neumann 
measurements (see Fig.~\ref{fig:diamond}). One of the components of such a scheme is to perform the conditional binary measurement. The first limitation is lack to possibility of implementation of the conditional binary measurement. The only possible measurement performed on quantum architectures is measurement in the computational basis. 
A postselection method provides us with a clever going around the obstacle. The postselection  scheme (see Fig.~\ref{postselection})  can be described as follow.

\begin{enumerate}
	\item We prepare input state $\ket{\psi_{AB}}$.
	\item One of two measurements is performed on part A.
	\item We prepare optimal measurements $V_j$, which are well known by Holevo--Helstrom theorem and perform them on part $B$.
	\item We get the output label $i$.
	\item We include these cases for which $i = j$. Otherwise, we reject them.
	\item By the use of $V_j$ output, we decide whether the measurement was performed on part $A$.
	\item We count the probability of postselection.
\end{enumerate}

\begin{figure}[h!]
	\includegraphics[scale=1.5]{onequbit.pdf}
	\caption{A schematic representation of the setup for distinguishing
		measurements using postselection.}
	\label{postselection}
\end{figure}

\subsection{Sample code snippets analysis (optional)}
\todo[inline]{moze tu kod tej postselekcji  i kontrolowanej unitarki ? }
\label{}

\section{Illustrative Examples}
\subsection{One-qubit measurements}
Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$. In this simplest case,  we consider two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H_2 diag(0,\ee^{\ii \phi}) H_2$, where $H_d$--Hadamard matrix of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected probability $p_{success}$ of correct distinction between two measurements $\PP_\1$ and $\PP_U$  is given by
\begin{equation}
p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = \frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
\end{equation}
by the assumption the discriminator is on the form $\ket{\psi} = \frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
(tu wyniki z rigettiego...)

\subsection{Two-qubit measurements}

\section{Impact }

\textbf{This is the main section of the article and the reviewers weight the description here appropriately}

Indicate in what way new research questions can be pursued as a result of the software (if any).

Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).

Indicate in what way the software has changed the daily practice of its users (if so).

Indicate how widespread the use of the software is within and outside the intended user group.

Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).

\section{Conclusions}
\label{}

Set out the conclusion of this original software publication.

\section{Conflict of Interest}
Please select the appropriate text:

Potential conflict of interest exists:
We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work. The nature of potential conflict of interest is described below: [Describe conflict of interest]

No conflict of interest exists:
We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.

\section*{Acknowledgements}

This work was supported by the Foundation for Polish Science (FNP) under grant
number POIR.04.04.00-00-17C1/18-00.

% The Appendices part is started with the command \appendix;
% appendix sections are then done as normal sections
% \appendix

% \section{}
% \label{}

% References:
% If you have bibdatabase file and want bibtex to generate the
% bibitems, please use
%
%  \bibliographystyle{elsarticle-num} 
%  \bibliography{<your bibdatabase>}

% else use the following coding to input the bibitems directly in the
% TeX file.

\begin{thebibliography}{00}

\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and beyond." Quantum 2 (2018): 79.
\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking gate-based quantum computers." Computer Physics Communications 220 (2017): 44-55.
\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication protocols as a benchmark for programmable quantum computers." Quantum Information Processing 18.1 (2019): 1-23.
\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu, and Raphael C. Pooser. "Generative model benchmarks for superconducting qubits." Physical Review A 99.6 (2019): 062323.
\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative modeling approach for benchmarking and training shallow quantum circuits." npj Quantum Information 5.1 (2019): 1-9.
\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for optimal single-shot discrimination of quantum measurements." Physical Review A 98.4 (2018): 042103.
\end{thebibliography}
\todo[inline]{Please add the reference to the software repository if DOI for software  is available. }

\section*{Current executable software version}
\label{}

Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
\hline
S1 & Current software version & For example 1.1, 2.4 etc. \\
\hline
S2 & Permanent link to executables of this version  & For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
\hline
S3 & Legal Software License & List one of the approved licenses \\
\hline
S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
\hline
S5 & Installation requirements \& dependencies & \\
\hline
S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: $http://mozart.github.io/documentation/$ \\
\hline
S7 & Support email for questions & \\
\hline
\end{tabular}
\caption{Software metadata (optional)}
\label{} 
\end{table}

\end{document}
\endinput
%%
%% End of file `SoftwareX_article_template.tex'.

### 2022-06-21 txt-softwarex/SoftwareX_article_template.tex
add the beginning of sction about example

@@
 \newcommand{\diaguni}{\ensuremath{\mathcal{DU}}}
+\newcommand{\diag}{\mathrm{diag}}
+\newcommand{\tr}{\mathrm{tr}}
 %\DeclareMathOperator{\diag}{diag}
@@
 \journal{SoftwareX}
+
+\newtheorem{theorem}{Theorem}
 
@@
 
+\subsubsection{Diamond norm}
 Let us now consider linear mappings transforming  square matrices into square 
@@
 
-In the general case, the diamond norm of a Hermiticity-preserving maps $\Phi$ can be computed using the Semidefinite Program~\cite{watrous2018theory} and state 
-primal and dual problem in the following form:
+\begin{theorem}
+Let $U\in \UU_d$ and let $\PP_U$ and $\PP_\Id$ be two von Neumann 
+measurements. 
+Let also 
+$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$. Then
+\begin{equation}
+\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
+\Phi_\Id\|_\diamond,
+\end{equation}
+where $\Phi_U$ is unitary channel.
+\end{theorem}
+
+\paragraph{Discrimination of unitary channels}
+
+Before we proceed to presenting our main results, we need to briefly discuss the
+problem of discrimination of unitary channels. This can be done without the
+usage of entangled input. In order to formulate the condition for perfect
+discrimination of unitary channels we introduce the notion of numerical range of
+a matrix $A \in M_d$, denoted by $W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
+\mathbb{C}^d, \;
+\;\braket{x}{x}=1\}$. The celebrated Hausdorf-T\"oplitz
+theorem states that
+$W(A)$ is a convex set and therefore $W(A) =\{\tr A \sigma : \sigma \in \Omega_d
+\}$. Let us now recall the well-known result for the
+distinguishability of unitary channels.
+	Let $U \in \UU_d$ and $\Phi_U: \rho \mapsto U \rho U^\dagger$ be a unitary 
+	channel. 
+	Then 
+	\begin{equation}
+	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
+	\end{equation}
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $.
+
+%\begin{proposition}
+ Let $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ and	let 
+ $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
+	\begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
+	\Phi_\Id\|_\diamond
+	\end{equation}
+%\end{proposition}
+
+%In the general case, the diamond norm of a Hermiticity-preserving maps $\Phi$ 
+%can be computed using the Semidefinite Program~\cite{watrous2018theory} and 
+%state 
+%primal and dual problem in the following form:
 
@@
 \section{Illustrative Examples}
-\subsection{One-qubit measurements}
-Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$.
-In this simplest case,  we consider two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H_2 diag(0,\ee^{\ii \phi}) H_2$, where $H_d$--Hadamard matrix of dimension $d$, $0 \le \phi < 2\pi$.
-By theoretical results, the expected probability $p_{success}$ of correct distinction between two measurements $\PP_\1$ and $\PP_U$  is given by
+
+Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
+Assume that the unitary matrix $U$ is of the form 
 \begin{equation}
-p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = \frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
+U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
 \end{equation}
-by the assumption the discriminator is on the form $\ket{\psi} = \frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
-(tu wyniki z rigettiego...)
+where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
+In this section we will compare theoretical probability of correct 
+discrimination between these measurements and the realization on real devices.
+The theoretical probability can be calculated using Holevo-Helstrom theorem. 
+This probability will be calculated in 
+subsection~\ref{sec:example_theoretical_probability}. Later, we will 
+discuss the realization of this scheme on real devices in 
+subsection~\ref{sec:example_realization}. For such realization, we 
+will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
+and final measurement (see sec.~\ref{sec_example_final_measurement}).
 
-\subsection{Two-qubit measurements}
+\subsection{Theoretical bound}\label{sec:example_theoretical_probability}
+
+\subsection{Realization}\label{sec:example_realization}
+
+\subsubsection{Discriminator}\label{sec:example_discriminator}
+
+\subsubsection{Final measurement}\label{sec_example_final_measurement}
+
+%Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$. In 
+%this simplest case,  we consider two von Neumann measurements $\PP_\1$ and 
+%$\PP_U$ for $U = H_2 diag(0,\ee^{\ii \phi}) H_2$, where $H_d$--Hadamard matrix 
+%of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected 
+%probability $p_{success}$ of correct distinction between two measurements 
+%$\PP_\1$ and $\PP_U$  is given by
+%\begin{equation}
+%p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = 
+%\frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
+%\end{equation}
+%by the assumption the discriminator is on the form $\ket{\psi} = 
+%\frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
+%(tu wyniki z rigettiego...)
 

### 2022-06-21 txt-softwarex/SoftwareX_article_template.tex
add text about he example from rigetti.tex to SoftwareX_article

@@
 %% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
+\usepackage{amsthm}
 
@@
 
+\usepackage{amsmath}
 \newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
+\newtheorem{remark}{Remark}
+\newtheorem{scheme}{Scheme}
 
@@
 
+\begin{proposition}
+ Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
+ $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
+	\begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
+	\Phi_\Id\|_\diamond
+	\end{equation}
+\end{proposition}
+\begin{proof} We know that
+$
+	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
+$
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. For $U = H_2 \left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H_2^\dagger$ we obtain that $\nu = \frac{|1 + e^{i \phi} | }{2}$. 
+	The condition $ 	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
+	\Phi_\Id\|_\diamond $ is equivalent to prove that
+	\begin{equation}
+	\max_{E \in \diaguni_2 } \nu_E = \nu = \frac{|1 + e^{i \phi} | }{2},
+	\end{equation}
+	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $ We can prove that
+	\begin{equation}
+	\min_{\ket{x} \in \mathbb{C}^2  \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = \min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
+	\end{equation}
+For that, to calculate $\nu_E$ we obtain \begin{equation}
+	\max_{E \in \diaguni_2 } \nu_E  = \max_{E \in \diaguni_2 }  \min_{\rho \in \Omega_2} \left| \tr \rho U E  \right|
+\end{equation}
+For that, our task is reduce to show that
+	\begin{equation}
+	\forall E \in \diaguni_2 \,\, | \tr \rho U E | \le \nu. 
+	\end{equation}
+	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ and let us take $\rho = \left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
+	From spectral theorem, let us note $U$ as
+	\begin{equation}
+	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
+	\end{equation}
+	where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$, whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
+
+	Then we have 
+\begin{equation}
+\begin{split}
+& \forall E \in \diaguni_2 \,\,\, | \tr \rho U E | = \frac{1}{2}  \left| \tr H_2 \diag(1, e^{i\phi}) H_2^\dagger E \right| =  \\ &
+\frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) \right|  = 
+\frac{1}{2} \left| e^{i \phi}  \bra{x_1} E \ket{x_1} + \bra{x_2} E \ket{x_2} \right| = \\& 
+\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| = 
+\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le \nu, 
+	\end{split}
+\end{equation}
+	which completes the proof.
+\end{proof}
+
+\begin{remark}
+	The probability of correct discrimination of von Neumann measurements 
+	$\PP_U$ and $\PP_{\Id}$ for $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, 
+	where $\phi \in [0, 2\pi)$ is given by
+	\begin{equation}
+	p \le \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
+	\end{equation}
+\end{remark}
+
 \subsection{Realization}\label{sec:example_realization}
@@
 
+\begin{theorem}\label{rozrpomiarow}
+Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ such that $0 \not\in W(U)$.
+If there exists the discriminator $\rho \in \Omega_2$ of the form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
+	\begin{enumerate}
+		\item $\rho_1,\rho_2 \in \Omega_2$
+		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
+		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
+		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
+	\end{enumerate}
+	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
+	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of $U$. Then  we have 
+	\begin{equation}
+	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i \phi}}{2}\right|^2}.
+	\end{equation}
+	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą wartością własną $U\in \mathrm{U}(\XX)$.
+\end{theorem}
+\begin{proof} From \ref{th:minE} we have 
+	\begin{equation}
+	\begin{split}
+	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} ||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in \diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) ||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || \Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| \Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
+	\end{split}
+	\end{equation}
+The diamond norm between two unitary channels can be calculated by 
+	\begin{equation}
+	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = \min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
+	\end{equation}
+Hence,  it is enough to calculate the formula
+\begin{equation}
+\begin{split}
+\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
+\end{split}
+\end{equation}
+Recall, let us note $U$ as
+\begin{equation}
+U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
+\end{equation}
+where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$, whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
+Consider two cases:
+
+	$1^\circ$ Consider $\phi = \pi$. Then $U$ is of the form
+	\begin{equation}
+	U = \left(\begin{array}{cc}0&1\\1&0\end{array}\right).
+	\end{equation}
+Then $0 \in W(U)$.
+	From Proposition 3 in ~\cite{puchala2018strategies} the measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if and only if there exists $\rho \in \Omega_2$ such that
+	\begin{equation}
+	\mathrm{diag}\left(U^\dagger \rho\right) = 0.
+	\end{equation}
+Hence, for $U $ we have 
+	\begin{equation}
+	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} \left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right) =  \mathrm{diag} \left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
+	\end{equation}
+ It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the form
+	\begin{equation}
+	\rho = \left(\begin{array}{cc}\rho_{1,1}&0\\0&\rho_{2,2}\end{array}\right),
+	\end{equation}
+	where $\rho_{1,1},\rho_{2,2} \ge 0$ and  $\rho_{1,1}+\rho_{2,2}=1$.
+
+	$2^\circ$ Consider  $\phi \not = \pi$. 
+The spectrum of $U$ is of the form $\sigma(U) = \{e^{\mathbf{i} \phi},1\}$. Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
+	\begin{equation}
+	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
+	\end{equation}
+Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = \ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$.
+Obviously,  $\rho_1,\rho_2 \in \Omega_2$ and satisfies the requirements of theorem.
+Hence, the discriminator $\rho \in \Omega_2$ has the form
+	\begin{equation}
+	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = \left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
+	\end{equation}
+%and 
+%	\begin{equation}
+%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 + e^{\mathbf{i} \phi}}{2}\right|^2 },
+%	\end{equation}
+
+%	
+%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we have 
+%	\begin{equation}
+%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 \right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = \frac{\lambda_1+\lambda_2}{2}. 
+%	\end{equation}
+%	Therefore, we have
+%	\begin{equation}
+%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- \left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
+%	\end{equation}
+%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. Then we have 
+%	\begin{equation}
+%	\begin{split}
+%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E \right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = \frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} \lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} \left(\lambda_1 + \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
+%	\end{split}
+%	\end{equation} 
+%So we have 
+%	\begin{equation}
+%	\left|\tr\left(UE \rho \right) \right| = \left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 \bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} \right|.
+%	\end{equation}
+%	It implies that
+%	\begin{equation}
+%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  |\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
+%	\end{equation}
+%	Hence we obtain
+%	\begin{equation}
+%	\begin{split}
+%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 -\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
+%	\end{split}
+%	\end{equation}
+For $\rho =  \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we obtain
+	\begin{equation}
+	\begin{split}
+	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} = \\& \sum_{i=1}^2  \sqrt{\left(\bra{i}U^\dagger\rho U \ket{i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho U \ket{i}|^2} = \\& \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + \lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i} \left| \frac{\lambda_1 + \lambda_2}{2}\right|^2} = \\&  \sum_{i=1}^2 2 \bra{i} \rho \ket{i} \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } =
+	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } ,
+	\end{split}
+	\end{equation}
+which completes the proof.
+\end{proof}
+
+\begin{remark}\label{lemma:rho}
+	Let $\rho_{0} = \frac{1}{2} 
+	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)$. Then 
+	\begin{equation}
+	 \max_\rho \left\|(\1\otimes \sqrt{\rho}) J(\PP_U - \PP_{\Id}) 
+	(\1\otimes 
+	\sqrt{\rho})\right\|_1 =    \left\|(\1\otimes \sqrt{\rho_0}) J(\PP_U - 
+	\PP_{\Id}) 
+		(\1\otimes 
+		\sqrt{\rho_0})\right\|_1
+	\end{equation}
+	for  $U = H_2\diag(1, e^{i \phi}) H_2^\dagger $, 
+		where $\phi \in [0, 2\pi)$. 
+\end{remark}
+
 \subsubsection{Final measurement}\label{sec_example_final_measurement}
+\begin{scheme}
+Let us consider the problem of discrimination of von Neumann measurements 
+$\PP_U$
+and $\PP_{\Id}$ for $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, 
+	where $\phi \in [0, 2\pi)$. The schematic representation of theoretical 
+	setup is shown in Fig.~\ref{fig:theoretical}.
+
+From ~\cite{puchala2018strategies}(Proposition 4) and Lemma~\ref{lemma:rho} we 
+have 
+	\begin{equation}
+	\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
+	\rangle \rangle. 
+	\end{equation}
+	From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
+	Let us define \begin{equation}
+	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
+	\otimes \Id_2 \right)(\proj{\psi})
+	\end{equation}
+	where $\ket{\psi}$ is defined in Remark~\ref{remark:discriminator}. From 
+	Hahn-Jordan decomposition let \begin{equation}
+	X = P - Q
+	\end{equation}
+	where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
+	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $im(P)$ and $im(Q)$, 
+	respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
+	\begin{equation}
+	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
+	\end{equation}
+	and 
+	\begin{equation}
+	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right) 
+	\end{equation}
+	Hence, we define $V_0$ such that
+	\begin{equation}
+	\begin{split}
+	V_0 \ket{x_p} = \ket{0} \\ 
+	V_0 \ket{x_q} = \ket{1}
+	\end{split}
+	\end{equation}
+	and $V_1$ such that
+	\begin{equation}
+	\begin{split}
+	V_1 \ket{y_p} = \ket{0} \\ 
+	V_1 \ket{y_q} = \ket{1}
+	\end{split}
+	\end{equation}
+	The explicit form of $V_0$ and $V_1$ we can see in \texttt{one-qubit.nb}.
+	Finally, we obtain the measurement $\mu$ of the form
+	\begin{equation}
+	\begin{split}
+	 \mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
+	 \proj{0} V_1^\dagger  \\ 
+	\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
+	\proj{1} V_1^\dagger  
+	\end{split}
+	\end{equation}
+\end{scheme}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+
+\paragraph{Construction of $V_0$ and $V_1$}
+	For each $\phi \in \mathbb{R}$,  the controlled unitary $V_0$ and $V_1$ have the following form
+	\begin{equation}
+	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i \cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - \phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+	\end{equation}
+
+		\begin{equation}
+	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i \sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+	\end{equation}
+
+\begin{scheme}(By using postsellection)
+
+%\begin{figure}[h!]
+%	\centering 
+%	\includegraphics[width=0.75\linewidth, angle=-90]{rys-postsellection.jpg} 
+%	
+%	\caption{ A schematic representation of the setup for distinguishing
+%		measurements using postselection. 
+%	}\label{fig:postsellection}
+%\end{figure}
+\begin{enumerate}
+\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
+\rangle. $
+\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
+\item We implement unitary $V_0 $ or $ V_1$.
+\item We prepare the measurement $\Delta$ in standard basis (already exists on 
+Rigetti architecture) on each qubits.
+\item We calculate the probability of correct discrimination in the following 
+way
+\begin{equation}
+p = ...
+\end{equation}
+%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
+\end{enumerate}
+\end{scheme}
+
+\begin{scheme}(By using controlled unitary)
+%\begin{figure}[h!]
+%	\centering 
+%	\includegraphics[width=0.75\linewidth, angle=-90]{rys-controlled.jpg} 
+%	
+%	\caption{ A schematic representation of the setup for distinguishing
+%		measurements using controlled unitary gate. 
+%	}\label{fig:controlled}
+%\end{figure}
+\begin{enumerate}
+\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
+\rangle. $
+\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
+\item We implement controlled unitary $V_0 \oplus V_1$.
+\item We prepare the measurement $\Delta$ in standard basis (already exist on 
+Rigetti architecture) on each qubits.
+\item We calculate the probability of correct discrimination in the following 
+way
+\begin{equation}
+p = \frac{|j=0 \wedge \Phi_{U} | + |j=1 \wedge \Phi_{\1}|}{\text{all 
+cases}}
+\end{equation}
+\end{enumerate}
+\end{scheme}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-06-23 txt-softwarex/SoftwareX_article_template.tex
add theorems to the section about example

@@
 discrimination between these measurements and the realization on real devices.
-The theoretical probability can be calculated using Holevo-Helstrom theorem. 
+The theoretical probability can be calculated using Holevo-Helstrom theorem and 
+Theorem [] from~\cite{puchala2018strategies}. 
 This probability will be calculated in 
@@
 
+\begin{theorem}
+The optimal probability of correct discrimination between von Neumann
+measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
+where $\phi \in [0, 2\pi)$ is given by
+\begin{equation}
+p = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
+\end{equation}
+\end{theorem}
+
+\todo[inline]{change proof of proposition into proof of theorem}
 \begin{proposition}
@@
 
-\begin{remark}
-	The probability of correct discrimination of von Neumann measurements 
-	$\PP_U$ and $\PP_{\Id}$ for $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, 
-	where $\phi \in [0, 2\pi)$ is given by
-	\begin{equation}
-	p \le \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
-	\end{equation}
-\end{remark}
-
 \subsection{Realization}\label{sec:example_realization}
+Now we focus on the realization of the discrimination protocol. We will 
+discriminate between $\PP_U$ and $\PP_\1$. To do so, we need to know exact 
+forms of the input state and final measurement. We will indicate the optimal 
+input state in subsection~\ref{sec:example_discriminator} and the final 
+measurement in subsection~\ref{sec_example_final_measurement}.
 
 \subsubsection{Discriminator}\label{sec:example_discriminator}
+
+\begin{proposition}
+Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
+and $\PP_\1$, where $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
+2\pi)$.  The optimal input state has the form
+\begin{equation}
+\ket{\psi_{AB}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
+\end{equation}
+\end{proposition}
+
+\todo[inline]{add formal proof of the proposition}
 
@@
 \subsubsection{Final measurement}\label{sec_example_final_measurement}
-\begin{scheme}
-Let us consider the problem of discrimination of von Neumann measurements 
-$\PP_U$
-and $\PP_{\Id}$ for $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, 
-	where $\phi \in [0, 2\pi)$. The schematic representation of theoretical 
-	setup is shown in Fig.~\ref{fig:theoretical}.
+In this subsection we will derive exact form of the final measurement in the
+problem of discrimination of von Neumann measurements $\PP_U$ and $\PP_{\Id}$
+for $U = H \diag(1, e^{i \phi}) H^\dagger$, where $\phi \in [0, 2\pi)$.
+
+\begin{proposition}
+The  final measurement has the form
+\begin{equation}
+\begin{split}
+\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
+\proj{0} V_1^\dagger  \\ 
+\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
+\proj{1} V_1^\dagger,
+\end{split}
+\end{equation}
+where for each $\phi \in \mathbb{R}$,  the controlled unitaries $V_0$ and $V_1$ 
+have the form
+\begin{equation}
+V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
+\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
+\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+\end{equation}
+\begin{equation}
+V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
+\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) 
+&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+\end{equation}
+\end{proposition}
+\todo[inline]{add proof of the proposition}
+
+%The schematic representation of theoretical 
+%setup is shown in Fig.~\ref{fig:theoretical}.
 
@@
 \end{equation}
-\end{scheme}
 
@@
 	\end{equation}
+
+\subsubsection{Two schemes of practical realization}
 

### 2022-06-23 txt/manuscript.tex
new file with the manuscript

--- 2022-06-23 txt-softwarex/SoftwareX_article_template.tex
@@
 \begin{abstract}
-We introduce library ?, a comprehensive open source framework for benchmarking Amazon Braket Rigetti IonQ architectures ? 
-The framework is built around  the scheme of discrimination of von Neumann measurements. The library provides algorithm for ... Our main aim is creating a common platform  for open research.  ?
+We introduce library ?, a comprehensive open source framework for benchmarking 
+Amazon Braket Rigetti IonQ architectures ? 
+The framework is built around  the scheme of discrimination of von Neumann 
+measurements. The library provides algorithm for ... Our main aim is creating a 
+common platform  for open research.  ?
 
@@
 %% keywords here, in the form: keyword \sep keyword
-Benchmarking of Rigetti architecture \sep Discrimination of quantum measurements \sep Von Neumann measurements discrimination
+Benchmarking of Rigetti architecture \sep Discrimination of quantum 
+measurements \sep Von Neumann measurements discrimination
 
@@
 
-Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.
+Ancillary data table required for subversion of the codebase. Kindly replace 
+examples in right column with the correct information about your current code, 
+and leave the left column as it is.
 
@@
 \hline
-\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
+\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this 
+column} \\
 \hline
@@
 \hline
-C2 & Permanent link to code/repository used for this code version & For example: $https://github.com/mozart/mozart2$ \\
-\hline
-C3 & Code Ocean compute capsule & For example: $https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
+C2 & Permanent link to code/repository used for this code version & For 
+example: $https://github.com/mozart/mozart2$ \\
+\hline
+C3 & Code Ocean compute capsule & For example: 
+$https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
 \hline
@@
 \hline
-C5 & Code versioning system used & For example svn, git, mercurial, etc. put none if none \\
-\hline
-C6 & Software code languages, tools, and services used & For example C++, python, r, MPI, OpenCL, etc. \\
+C5 & Code versioning system used & For example svn, git, mercurial, etc. put 
+none if none \\
+\hline
+C6 & Software code languages, tools, and services used & For example C++, 
+python, r, MPI, OpenCL, etc. \\
 \hline
@@
 \hline
-C8 & If available Link to developer documentation/manual & For example: $http://mozart.github.io/documentation/$ \\
+C8 & If available Link to developer documentation/manual & For example: 
+$http://mozart.github.io/documentation/$ \\
 \hline
@@
 
-The permanent link to code/repository or the zip archive should include the following requirements:
+The permanent link to code/repository or the zip archive should include the 
+following requirements:
 
@@
 
-Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+Documentation in the repository in a docs/ directory, and/or READMEs, as 
+appropriate.
 
@@
 
-Currently one of the main providers of such architectures is Rigetti and its Quantum Cloud Services platform. The company has
+Currently one of the main providers of such architectures is Rigetti and its 
+Quantum Cloud Services platform. The company has
 released three generations of QPUs so far: Rigetti 8Q Agave, Rigetti 19Q Acorn
@@
 
-The goal of this work is to introduce a new benchmark for Rigetti architecture...
+The goal of this work is to introduce a new benchmark for Rigetti 
+architecture...
 
@@
 \todo[inline]{
-	Introduce the scientific background and the motivation for developing the software. - motywacje
-
-	Explain why the software is important, and describe the exact (scientific) problem(s) it solves. - czemu ejst wazne, jakie problemy rozwiazuje
-
-	Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
-- do czego sie to przyczyni w przyszlosci
-
-	Provide a description of the experimental setting (how does the user use the software?). - w jaki sposób użytkownik korzysta z oprogramowania?
-
-	Introduce related work in literature (cite or list algorithms used, other software etc.). - inne oprogramowania i algorytmy }
+	Introduce the scientific background and the motivation for developing the 
+	software. - motywacje
+
+	Explain why the software is important, and describe the exact (scientific) 
+	problem(s) it solves. - czemu ejst wazne, jakie problemy rozwiazuje
+
+	Indicate in what way the software has contributed (or how it will 
+	contribute in the future) to the process of scientific discovery; if 
+	available, this is to be supported by citing a research paper using the 
+	software. - do czego sie to przyczyni w przyszlosci
+
+	Provide a description of the experimental setting (how does the user use 
+	the software?). - w jaki sposób użytkownik korzysta z oprogramowania?
+
+	Introduce related work in literature (cite or list algorithms used, other 
+	software etc.). - inne oprogramowania i algorytmy }
 
@@
 \label{}
-\todo[inline]{Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact. }
-
-We will first give a general overview of the structure of the code in Section~\ref{sec:sortware-architecture} and then provide additional details on the functionality of benchmark's schemes  in Section~\ref{sec:sortware-functionalities}.
+\todo[inline]{Describe the software in as much as is necessary to establish a 
+vocabulary needed to explain its impact. }
+
+We will first give a general overview of the structure of the code in 
+Section~\ref{sec:sortware-architecture} and then provide additional details on 
+the functionality of benchmark's schemes  in 
+Section~\ref{sec:sortware-functionalities}.
 
@@
 \todo[inline]{
-	Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.}
+	Give a short overview of the overall software architecture; provide a 
+	pictorial component overview or similar (if possible). If necessary provide 
+	implementation details.}
 
@@
 
-In the scope of this Paper, we aim at  exploring ideas revolving around quantum gate model-inspired computing devices, and assess their feasibility to benchmark a modern quantum architectures.
-The main idea that we have envisioned for this project is  introducing new concepts of algorithms for NISQ devices benchmarking.
-This project aims to characterize the computing power and investigate possible practical applications of such devices having access by Amazon Braket.
-First of all, we will focus on constraining quantum algorithms being relatively easy to implement on quantum architectures with straightforward, intuitive operational interpretation.
-Moreover, we need to possess a scalability, that is the ability to adjust to large range of architectures size.
-These properties will give us major advantage over the existing approaches  of benchmarking.
-
-This idea is built upon two specific tasks that are to be achieved within this proposal. 
-The first task is to   desing a benchmark based on discrimination of von Nemaumm measurements scheme.
-While the second one is to extension  this approach to benchmark on the grounds of certification of von Neumann measurements scheme.
+In the scope of this Paper, we aim at  exploring ideas revolving around quantum 
+gate model-inspired computing devices, and assess their feasibility to 
+benchmark a modern quantum architectures. The main idea that we have envisioned 
+for this project is  introducing new concepts of algorithms for NISQ devices 
+benchmarking. This project aims to characterize the computing power and 
+investigate possible practical applications of such devices having access by 
+Amazon Braket.  First of all, we will focus on constraining quantum algorithms 
+being relatively easy to implement on quantum architectures with 
+straightforward, intuitive operational interpretation. Moreover, we need to 
+possess a scalability, that is the ability to adjust to large range of 
+architectures size.  
+These properties will give us major advantage over the existing approaches  of 
+benchmarking.
+
+This idea is built upon two specific tasks that are to be achieved within this 
+proposal. 
+The first task is to   desing a benchmark based on discrimination of von 
+Nemaumm measurements scheme. While the second one is to extension  this 
+approach to benchmark on the grounds of certification of von Neumann 
+measurements scheme.
 
 \subsubsection{Model specification}
-Theoretically, scenario of this set up assume that Alice and Bob have an unknown measurement device, black--box.
-Alice has hiden one of the two measurements  in the black box.
-The only information which Bob has is that it performs one of such  measurements.
-The  goal of discrimination of von Neumann measurements  is to determine by Bob whether it is possible to discriminate measurements perfectly, i.e.
-with probability equals one.
-If this is not possible, he  would like to know the upper bound of such a probability.
-Theoretical results of discrimination of von Neumann measurements is well-known and characterized in~\cite{puchala2018strategies}.
-The scheme of von Neumann discrimination is presented in Fig.~\ref{fig:scheme} and
+Theoretically, scenario of this set up assume that Alice and Bob have an 
+unknown measurement device, black--box.  Alice has hiden one of the two 
+measurements  in the black box.  The only information which Bob has is that it 
+performs one of such  measurements. 
+The  goal of discrimination of von Neumann measurements  is to determine by Bob 
+whether it is possible to discriminate measurements perfectly, i.e. with 
+probability equals one. If this is not possible, he  would like to know the 
+upper bound of such a probability.  Theoretical results of discrimination of 
+von Neumann measurements is well-known and characterized 
+in~\cite{puchala2018strategies}.    The scheme of von Neumann discrimination is 
+presented in Fig.~\ref{fig:scheme} and 
 can be divided into the following steps:
@@
 	\item Alice and Bob share entanglement state $\ket{\psi_{AB}}$.
-	\item Alice performs one of two known measurements on part $A$ of the input state  $\ket{\psi_{AB}}$.
+	\item Alice performs one of two known measurements on part $A$ of the input 
+	state  $\ket{\psi_{AB}}$.
 	\item Alice  uses
-	the output label $i$ and performs a conditional binary measurement on part $B$.
-	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and makes a decision  basis of the condition binary measurement.
+	the output label $i$ and performs a conditional binary measurement on part 
+	$B$.
+	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
+	makes a decision  basis of the condition binary measurement.
 \end{enumerate}
@@
 Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
-the field $\mathbb{C}$. For  simplicity notation, square matrices will be denoted by
-$M_d$.
-The subset of $M_d$ consisting of Hermitian matrices of dimension $d$ will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite matrices of dimension $d$ by $\HH_d^+$.
-The set of quantum states, that is positive semidefinite operators having
-trace equal to one, will be denoted $\DD_d$.  The subset of $M_d$ consisting of unitary matrices will be denoted by
+the field $\mathbb{C}$. For  simplicity notation, square matrices will be 
+denoted by
+$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$ 
+will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite 
+matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is 
+positive semidefinite operators having
+trace equal to one, will be denoted $\DD_d$.  The subset of $M_d$ consisting of 
+unitary matrices will be denoted by
 $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
@@
 
-$\Phi_{U}$ is defined as $\Phi_U(\cdot) := U \cdot U^\dagger$ for  $U \in \UU_d$. A general quantum
+$\Phi_{U}$ is defined as $\Phi_U(\cdot) := U \cdot U^\dagger$ for  $U \in 
+\UU_d$. A general quantum
 measurement, that is a positive operator valued measure (POVM) $\PP$ is a
@@
 \PP_{U} : \rho \rightarrow \sum_{i=1}^d \bra{u_i} \rho \ket{u_i} \proj{i}.
-$ Every von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta \circ \Phi_{(UE)^\dagger}$, where $\Delta$ denotes the completely dephasing channel.
+$ Every von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta 
+\circ \Phi_{(UE)^\dagger}$, where $\Delta$ denotes the completely dephasing 
+channel.
 
@@
 %			\text{maximize:}\quad & \tr(X J(\Phi)) \\[2mm]
-%			\text{subject to:}\quad &  \left[ \begin{array}{cc}\Id_{d_2} \otimes \rho & X \\ X^* & \Id_{d_2} \otimes \rho  \end{array} \right] \ge 0 \\
+%			\text{subject to:}\quad &  \left[ \begin{array}{cc}\Id_{d_2} 
+%\otimes \rho & X \\ X^* & \Id_{d_2} \otimes \rho  \end{array} \right] \ge 0 \\
 %			& \rho \in \HH_d^+\\ 
@@
 %			\text{minimize:}\quad & ||\tr_1(Y)||_\infty \\[2mm]
-%			\text{subject to:}\quad & \left[ \begin{array}{cc}Y & -J(\Phi) \\ -J(\Phi) &  Y \end{array} \right] \ge 0 \\
+%			\text{subject to:}\quad & \left[ \begin{array}{cc}Y & -J(\Phi) \\ 
+%-J(\Phi) &  Y \end{array} \right] \ge 0 \\
 %			& Y \in \HH_{d_1d_2}^+.
@@
 \subsubsection{Rigetti architecture's limits/ practical solutions}
-\todo[inline]{nie wiem, moze tu o conditional measurement i o sposobach ominiecia tego problemu - postselekcja i kontrolowana unitarka}
-
-We may encounter numerous obstacles in the implementation process due to the limited architecture of quantum computer. 
+\todo[inline]{nie wiem, moze tu o conditional measurement i o sposobach 
+ominiecia tego problemu - postselekcja i kontrolowana unitarka}
+
+We may encounter numerous obstacles in the implementation process due to the 
+limited architecture of quantum computer. 
 Let us take a closer look at the setup for distinguishing von Neumann 
-measurements (see Fig.~\ref{fig:diamond}).
-One of the components of such a scheme is to perform the conditional binary measurement.
-The first limitation is lack to possibility of implementation of the conditional binary measurement.
-The only possible measurement performed on quantum architectures is measurement in the computational basis.
-A postselection method provides us with a clever going around the obstacle. The postselection  scheme (see Fig.~\ref{postselection})  can be described as follow.
+measurements (see Fig.~\ref{fig:diamond}). One of the components of such a 
+scheme is to perform the conditional binary measurement. The first limitation 
+is lack to possibility of implementation of the conditional binary measurement. 
+The only possible measurement performed on quantum architectures is measurement 
+in the computational basis. 
+A postselection method provides us with a clever going around the obstacle. The 
+postselection  scheme (see Fig.~\ref{postselection})  can be described as 
+follow.
 
@@
 	\item One of two measurements is performed on part A.
-	\item We prepare optimal measurements $V_j$, which are well known by Holevo--Helstrom theorem and perform them on part $B$.
+	\item We prepare optimal measurements $V_j$, which are well known by 
+	Holevo--Helstrom theorem and perform them on part $B$.
 	\item We get the output label $i$.
 	\item We include these cases for which $i = j$. Otherwise, we reject them.
-	\item By the use of $V_j$ output, we decide whether the measurement was performed on part $A$.
+	\item By the use of $V_j$ output, we decide whether the measurement was 
+	performed on part $A$.
 	\item We count the probability of postselection.
@@
 $
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. For $U = H_2 \left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H_2^\dagger$ we obtain that $\nu = \frac{|1 + e^{i \phi} | }{2}$. 
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. For $U = H_2 
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H_2^\dagger$ we 
+	obtain that $\nu = \frac{|1 + e^{i \phi} | }{2}$. 
 	The condition $ 	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
@@
 	\begin{equation}
-	\min_{\ket{x} \in \mathbb{C}^2  \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = \min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
+	\min_{\ket{x} \in \mathbb{C}^2  \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
+	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
 	\end{equation}
 For that, to calculate $\nu_E$ we obtain \begin{equation}
-	\max_{E \in \diaguni_2 } \nu_E  = \max_{E \in \diaguni_2 }  \min_{\rho \in \Omega_2} \left| \tr \rho U E  \right|
+	\max_{E \in \diaguni_2 } \nu_E  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
+	\Omega_2} \left| \tr \rho U E  \right|
 \end{equation}
@@
 	\end{equation}
-	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ and let us take $\rho = \left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
+	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ 
+	and let us take $\rho = 
+	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
 	From spectral theorem, let us note $U$ as
@@
 	\end{equation}
-	where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$, whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
+	where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is 
+	of the form $\ket{x_1} = 
+	\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
+	 whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
+	\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
 
@@
 \begin{split}
-& \forall E \in \diaguni_2 \,\,\, | \tr \rho U E | = \frac{1}{2}  \left| \tr H_2 \diag(1, e^{i\phi}) H_2^\dagger E \right| =  \\ &
-\frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) \right|  = 
-\frac{1}{2} \left| e^{i \phi}  \bra{x_1} E \ket{x_1} + \bra{x_2} E \ket{x_2} \right| = \\& 
-\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| = 
-\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le \nu, 
+& \forall E \in \diaguni_2 \,\,\, | \tr \rho U E | = \frac{1}{2}  \left| \tr 
+H_2 \diag(1, e^{i\phi}) H_2^\dagger E \right| =  \\ &
+\frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) 
+\right|  = 
+\frac{1}{2} \left| e^{i \phi}  \bra{x_1} E \ket{x_1} + \bra{x_2} E \ket{x_2} 
+\right| = \\& 
+\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| 
+= 
+\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
+\nu, 
 	\end{split}
@@
 \begin{theorem}\label{rozrpomiarow}
-Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ such that $0 \not\in W(U)$.
-If there exists the discriminator $\rho \in \Omega_2$ of the form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
+Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = 
+H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
+\not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the 
+form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
 	\begin{enumerate}
@@
 	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
-	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of $U$. Then  we have 
-	\begin{equation}
-	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i \phi}}{2}\right|^2}.
-	\end{equation}
-	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą wartością własną $U\in \mathrm{U}(\XX)$.
+	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of 
+	$U$. Then  we have 
+	\begin{equation}
+	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i 
+	\phi}}{2}\right|^2}.
+	\end{equation}
+	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą 
+	%wartością własną $U\in \mathrm{U}(\XX)$.
 \end{theorem}
@@
 	\begin{split}
-	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} ||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in \diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) ||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || \Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| \Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
+	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} 
+	||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in 
+	\diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) 
+	||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || 
+	\Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| 
+	\Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
 	\end{split}
@@
 	\begin{equation}
-	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = \min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
+	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = 
+	\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho 
+	)|^2}.
 	\end{equation}
@@
 \end{equation}
-where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$, whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
+where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of 
+the form $\ket{x_1} = 
+\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
+ whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
+\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
+
 Consider two cases:
@@
 	\end{equation}
-Then $0 \in W(U)$.
-	From Proposition 3 in ~\cite{puchala2018strategies} the measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if and only if there exists $\rho \in \Omega_2$ such that
+Then $0 \in W(U)$. 	From Proposition 3 in ~\cite{puchala2018strategies} the 
+measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if 
+and only if there exists $\rho \in \Omega_2$ such that
 	\begin{equation}
@@
 	\begin{equation}
-	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} \left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right) =  \mathrm{diag} \left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
-	\end{equation}
- It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the form
+	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} 
+	\left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right)
+	 =  \mathrm{diag} 
+	\left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
+	\end{equation}
+ It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for 
+ which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the 
+ form
 	\begin{equation}
@@
 	$2^\circ$ Consider  $\phi \not = \pi$. 
-The spectrum of $U$ is of the form $\sigma(U) = \{e^{\mathbf{i} \phi},1\}$. Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
+The spectrum of $U$ is of the form $\sigma(U) = \{e^{\mathbf{i} \phi},1\}$. 
+Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
 	\begin{equation}
@@
 	\end{equation}
-Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = \ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$.
-Obviously,  $\rho_1,\rho_2 \in \Omega_2$ and satisfies the requirements of theorem.
-Hence, the discriminator $\rho \in \Omega_2$ has the form
-	\begin{equation}
-	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = \left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
+Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = 
+\ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 
+\in \Omega_2$ and satisfies the requirements of theorem. Hence, the 
+discriminator $\rho \in \Omega_2$ has the form 
+	\begin{equation}
+	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = 
+	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
 	\end{equation}
@@
 %	\begin{equation}
-%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 + e^{\mathbf{i} \phi}}{2}\right|^2 },
+%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 
+%+ e^{\mathbf{i} \phi}}{2}\right|^2 },
 %	\end{equation}
@@
 %	
-%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we have 
+%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} 
+%\rho_2$ we have 
 %	\begin{equation}
-%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 \right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = \frac{\lambda_1+\lambda_2}{2}. 
+%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 
+%\right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = 
+%\frac{\lambda_1+\lambda_2}{2}. 
 %	\end{equation}
@@
 %	\begin{equation}
-%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- \left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
+%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- 
+%\left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
 %	\end{equation}
-%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. Then we have 
+%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 
+%e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. 
+%Then we have 
 %	\begin{equation}
 %	\begin{split}
-%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E \right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = \frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} \lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} \left(\lambda_1 + \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
+%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E 
+%\right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = 
+%\frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} 
+%\lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} 
+%\left(\lambda_1 
+%+ \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
 %	\end{split}
@@
 %	\begin{equation}
-%	\left|\tr\left(UE \rho \right) \right| = \left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 \bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} \right|.
+%	\left|\tr\left(UE \rho \right) \right| = 
+%\left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 
+%\bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} 
+%\right|.
 %	\end{equation}
@@
 %	\begin{equation}
-%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  |\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
+%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  
+%|\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
 %	\end{equation}
@@
 %	\begin{split}
-%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 -\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
+%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} 
+%\sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} 
+%\right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 
+%-\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
 %	\end{split}
@@
 	\begin{split}
-	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} = \\& \sum_{i=1}^2  \sqrt{\left(\bra{i}U^\dagger\rho U \ket{i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho U \ket{i}|^2} = \\& \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + \lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i} \left| \frac{\lambda_1 + \lambda_2}{2}\right|^2} = \\&  \sum_{i=1}^2 2 \bra{i} \rho \ket{i} \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } =
+	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=1}^2  
+	\sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 
+	4|\bra{i}\rho\ket{u_i}|^2} = \\& \sum_{i=1}^2  
+	\sqrt{\left(\bra{i}U^\dagger\rho U \ket{i} + \bra{i} \rho \ket{i} \right)^2 
+	- 4|\bra{i}\rho U \ket{i}|^2} = \\& \sum_{i=1}^2  \sqrt{4 \bra{i}\rho 
+	\ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + 
+	\lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=1}^2  \sqrt{4 
+	\bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i} \left| \frac{\lambda_1 + 
+	\lambda_2}{2}\right|^2} = \\&  \sum_{i=1}^2 2 \bra{i} \rho \ket{i} \sqrt{1 
+	-\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| 
+	\frac{\lambda_1 + \lambda_2}{2}\right|^2 } = 
 	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } ,
@@
 \paragraph{Construction of $V_0$ and $V_1$}
-	For each $\phi \in \mathbb{R}$,  the controlled unitary $V_0$ and $V_1$ have the following form
-	\begin{equation}
-	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i \cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - \phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
-	\end{equation}
-
-		\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i \sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+	For each $\phi \in \mathbb{R}$,  the controlled unitary $V_0$ and $V_1$ 
+	have the following form
+	\begin{equation}
+	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
+	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
+	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+	\end{equation}
+
+		\begin{equation}
+	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
+	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
+	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
 	\end{equation}
@@
 
-\textbf{This is the main section of the article and the reviewers weight the description here appropriately}
-
-Indicate in what way new research questions can be pursued as a result of the software (if any).
-
-Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
-
-Indicate in what way the software has changed the daily practice of its users (if so).
-
-Indicate how widespread the use of the software is within and outside the intended user group.
-
-Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
+\textbf{This is the main section of the article and the reviewers weight the 
+description here appropriately}
+
+Indicate in what way new research questions can be pursued as a result of the 
+software (if any).
+
+Indicate in what way, and to what extent, the pursuit of existing research 
+questions is improved (if so).
+
+Indicate in what way the software has changed the daily practice of its users 
+(if so).
+
+Indicate how widespread the use of the software is within and outside the 
+intended user group.
+
+Indicate in what way the software is used in commercial settings and/or how it 
+led to the creation of spin-off companies (if so).
 
@@
 Potential conflict of interest exists:
-We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work.
-The nature of potential conflict of interest is described below: [Describe conflict of interest]
+We wish to draw the attention of the Editor to the following facts, which may 
+be considered as potential conflicts of interest, and to significant financial 
+contributions to this work. The nature of potential conflict of interest is 
+described below: [Describe conflict of interest]
 
 No conflict of interest exists:
-We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
+We wish to confirm that there are no known conflicts of interest associated 
+with this publication and there has been no significant financial support for 
+this work that could have influenced its outcome.
 
@@
 
-\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and beyond." Quantum 2 (2018): 79.
-\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking gate-based quantum computers." Computer Physics Communications 220 (2017): 44-55.
-\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication protocols as a benchmark for programmable quantum computers." Quantum Information Processing 18.1 (2019): 1-23.
-\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu, and Raphael C. Pooser. "Generative model benchmarks for superconducting qubits." Physical Review A 99.6 (2019): 062323.
-\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative modeling approach for benchmarking and training shallow quantum circuits." npj Quantum Information 5.1 (2019): 1-9.
-\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for optimal single-shot discrimination of quantum measurements." Physical Review A 98.4 (2018): 042103.
+\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and 
+beyond." Quantum 2 (2018): 79.
+\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking 
+gate-based quantum computers." Computer Physics Communications 220 (2017): 
+44-55.
+\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication 
+protocols as a benchmark for programmable quantum computers." Quantum 
+Information Processing 18.1 (2019): 1-23.
+\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu, 
+and Raphael C. Pooser. "Generative model benchmarks for superconducting 
+qubits." Physical Review A 99.6 (2019): 062323.
+\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative 
+modeling approach for benchmarking and training shallow quantum circuits." npj 
+Quantum Information 5.1 (2019): 1-9.
+\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for 
+optimal single-shot discrimination of quantum measurements." Physical Review A 
+98.4 (2018): 042103.
 \end{thebibliography}
-\todo[inline]{Please add the reference to the software repository if DOI for software  is available. }
+\todo[inline]{Please add the reference to the software repository if DOI for 
+software  is available. }
 
@@
 
-Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.
+Ancillary data table required for sub version of the executable software: (x.1, 
+x.2 etc.) kindly replace examples in right column with the correct information 
+about your executables, and leave the left column as it is.
 
@@
 \hline
-\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
+\textbf{Nr.} & \textbf{(Executable) software metadata description} & 
+\textbf{Please fill in this column} \\
 \hline
@@
 \hline
-S2 & Permanent link to executables of this version  & For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
+S2 & Permanent link to executables of this version  & For example: 
+$https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
 \hline
@@
 \hline
-S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
+S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, 
+Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based 
+etc. \\
 \hline
@@
 \hline
-S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: $http://mozart.github.io/documentation/$ \\
+S6 & If available, link to user manual - if formally published include a 
+reference to the publication in the reference list & For example: 
+$http://mozart.github.io/documentation/$ \\
 \hline

### 2022-06-23 txt/manuscript.tex
proofs

@@
 \newtheorem{scheme}{Scheme}
+\newtheorem{lemma}{Lemma}
 
@@
 positive semidefinite operators having
-trace equal to one, will be denoted $\DD_d$.  The subset of $M_d$ consisting of 
+trace equal to one, will be denoted $\Omega_d$.  The subset of $M_d$ consisting of 
 unitary matrices will be denoted by
 $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$.  An unitary transformation 
-\todo[inline]{channel} CPTP
-
-$\Phi_{U}$ is defined as $\Phi_U(\cdot) := U \cdot U^\dagger$ for  $U \in 
+$\DD \UU_d$.  We will also need a linear
+mapping transforming $M_{d_1}$ into $M_{d_2}$, which will be denoted \begin{equation}
+\Phi: M_{d_1 } \rightarrow M_{d_2}.
+\end{equation} Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
+and trace preserving (CPTP).
+Mostly, we will use the unitary channels
+$\Phi_{U}$ which are defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
 \UU_d$. A general quantum
@@
 parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
-for a von Neumann measurement with effects $\{\proj{u_1}, \ldots, \proj{u_d}\}$,
-where $\ket{u_i}$ is the $i$-th column of the unitary matrix $U$. The action of
-quantum measurement $\PP_{U}$ on some state $\rho \in \mathcal{D}_d$ can be
+for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
+quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
 expressed as the action of a quantum channel
 $
-\PP_{U} : \rho \rightarrow \sum_{i=1}^d \bra{u_i} \rho \ket{u_i} \proj{i}.
+\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
 $ Every von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta 
@@
 
-The celebrated result by Helstrom~\cite{helstrom1976quantum} gives an upper
-bound on the probability of correct distinction between two quantum channels
-$\Phi$ and $\Psi$ in terms of their distance with the use of the diamond norm
-\begin{equation}
-p \leq \frac12 + \frac14 \| \Phi - \Psi \|_\diamond.
-\end{equation}
-
-\begin{theorem}
-Let $U\in \UU_d$ and let $\PP_U$ and $\PP_\Id$ be two von Neumann 
-measurements. 
-Let also 
-$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$. Then
+The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
+in terms of their distance with the use of the diamond norm
+\begin{equation}
+p =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
+\end{equation}
+
+In case then 
+we consider the discrimination setup between two von Neumann 
+measurements $\PP_U$ and $\PP_\Id$, $U\in \UU_d$ we obtain that (from Theorem 1 \cite{puchala2018strategies})
 \begin{equation}
@@
 \end{equation}
-where $\Phi_U$ is unitary channel.
-\end{theorem}
+where $\Phi_U$ is unitary channel and 
+$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$
 
@@
 Before we proceed to presenting our main results, we need to briefly discuss the
-problem of discrimination of unitary channels. This can be done without the
-usage of entangled input. In order to formulate the condition for perfect
+problem of discrimination of unitary channels.  In order to formulate the condition for perfect
 discrimination of unitary channels we introduce the notion of numerical range of
@@
 %\begin{proposition}
- Let $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ and	let 
+ Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
  $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
@@
 The theoretical probability can be calculated using Holevo-Helstrom theorem and 
-Theorem [] from~\cite{puchala2018strategies}. 
+Theorem 1 from~\cite{puchala2018strategies}. 
 This probability will be calculated in 
@@
 \end{theorem}
-
-\todo[inline]{change proof of proposition into proof of theorem}
-\begin{proposition}
- Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
- $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
+\begin{proof}
+	From Holevo-Helstrom theorem we obtain
+	\begin{equation}
+	p = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond,
+	\end{equation}
+	therefore from Theorem 1 in \cite{puchala2018strategies} we have 
+	\begin{equation}
+	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond. 
+	\end{equation}
+	From Lemma~\ref{lemma:min-e-optimal} we show that 
 	\begin{equation}
@@
 	\Phi_\Id\|_\diamond
-	\end{equation}
-\end{proposition}
+	\end{equation} and hence, from the problem of discrimination of unitary channels, we receive 
+	\begin{equation}
+	p = \frac{1}{2} + \frac{1}{2} \sqrt{1 - \nu^2} = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
+	\end{equation} which completes the proof.
+\end{proof}
+
+\todo[inline]{change proof of proposition into proof of theorem}
+\begin{lemma}\label{lemma:min-e-optimal}
+ Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
+ $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
+	\begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
+	\Phi_\Id\|_\diamond,
+	\end{equation}
+
+\end{lemma}
 \begin{proof} We know that
@@
 $
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. For $U = H_2 
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H_2^\dagger$ we 
-	obtain that $\nu = \frac{|1 + e^{i \phi} | }{2}$. 
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. For $U = H 
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that $W(U^\dagger) $ 
+	obtain that $\nu^2 = 1 - \frac{|1 - e^{i \phi} | }{2}$. 
 	The condition $ 	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
@@
 	\end{equation}
-	where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is 
+	where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is 
 	of the form $\ket{x_1} = 
@@
 	\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
-
-	Then we have 
+	Then, we have 
 \begin{equation}
@@
 & \forall E \in \diaguni_2 \,\,\, | \tr \rho U E | = \frac{1}{2}  \left| \tr 
-H_2 \diag(1, e^{i\phi}) H_2^\dagger E \right| =  \\ &
+H \diag(1, e^{i\phi}) H^\dagger E \right| =  \\ &
 \frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) 
@@
 Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = 
-H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
+H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
 \not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the 
@@
 \end{equation}
-where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of 
+where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is of 
 the form $\ket{x_1} = 
@@
 	$2^\circ$ Consider  $\phi \not = \pi$. 
-The spectrum of $U$ is of the form $\sigma(U) = \{e^{\mathbf{i} \phi},1\}$. 
+The spectrum of $U$ is of the form $\sigma(U) = \{e^{i \phi},1\}$. 
 Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
@@
 	\end{equation}
-	for  $U = H_2\diag(1, e^{i \phi}) H_2^\dagger $, 
+	for  $U = H\diag(1, e^{i \phi}) H^\dagger $, 
 		where $\phi \in [0, 2\pi)$. 
@@
 %this simplest case,  we consider two von Neumann measurements $\PP_\1$ and 
-%$\PP_U$ for $U = H_2 diag(0,\ee^{\ii \phi}) H_2$, where $H_d$--Hadamard matrix 
+%$\PP_U$ for $U = H diag(0,\ee^{\ii \phi}) H$, where $H_d$--Hadamard matrix 
 %of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected 

### 2022-06-23 txt/rigetti.tex
proofs

@@
 
-In the simplest approach we may think of measurements $\mathcal{S}$ and $\TT$
-as measure-and-prepare channels outputting diagonal states, that is classical
-probability distributions, see Fig.~\ref{fig:non-ent-disc}. This notion will be
-formalized in later sections. Thus, the simplest approach to this problem is to
-consider the distance between probability distributions. We can use the distance
-between these distributions as an upper bound on the probability of correct
-discrimination. In this setting it is also straightforward to find the optimal
-state for the discrimination.
-
 Of course, there is another possibility. As we are dealing with quantum states,
@@
 Fig.~\ref{fig:diamond}.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.7\linewidth]{gatewe.pdf}
-	\caption{
-		A schematic representation of the setup for distinguishing 
-		measurements without entanglement.}
-	\label{fig:non-ent-disc}
-\end{figure}
 

### 2022-07-04 txt/manuscript.tex
add pictures to manuscript
changes in proofs

@@
 
-\subsection{Theoretical bound}\label{sec:example_theoretical_probability}
-
-\begin{theorem}
-The optimal probability of correct discrimination between von Neumann
-measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
-where $\phi \in [0, 2\pi)$ is given by
-\begin{equation}
-p = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
-\end{equation}
-\end{theorem}
-\begin{proof}
-	From Holevo-Helstrom theorem we obtain
-	\begin{equation}
-	p = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond,
-	\end{equation}
-	therefore from Theorem 1 in \cite{puchala2018strategies} we have 
-	\begin{equation}
-	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond. 
-	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal} we show that 
-	\begin{equation}
-		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-	\Phi_\Id\|_\diamond
-	\end{equation} and hence, from the problem of discrimination of unitary channels, we receive 
-	\begin{equation}
-	p = \frac{1}{2} + \frac{1}{2} \sqrt{1 - \nu^2} = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
-	\end{equation} which completes the proof.
-\end{proof}
-
-\todo[inline]{change proof of proposition into proof of theorem}
+\subsection{Theoretical probability}\label{sec:example_theoretical_probability}
+In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.
+To do that, we will present an auxiliary lemma.
 \begin{lemma}\label{lemma:min-e-optimal}
@@
 \end{lemma}
-\begin{proof} We know that
+\begin{proof} Recall that the distance between two unitary channels is given by
 	$
@@
 	$
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. For $U = H 
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that $W(U^\dagger) $ 
-	obtain that $\nu^2 = 1 - \frac{|1 - e^{i \phi} | }{2}$. 
-	The condition $ 	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-	\Phi_\Id\|_\diamond $ is equivalent to prove that
+	where $\nu_U = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$.
+
+	For $U = H 
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{i \phi} | }{4}$. So, 
+	\begin{equation}
+	\|  \Phi_U  - \Phi_{\1} \|_\diamond = \frac{| 1 - e^{i \phi} |}{2}. 
+	\end{equation} 
+		It implies that it is enough to prove  \begin{equation}
+		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+		\Phi_\Id\|_\diamond  = \frac{| 1 - e^{i \phi} |}{2}.
+		\end{equation}
+
+		It implies that we can prove  equivalently  the following condition
+		\begin{equation}
+		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
+		\end{equation}
+	It implies that it is enough to prove 
 	\begin{equation}
@@
 	\end{equation}
-	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $ We can prove that
-	\begin{equation}
-	\min_{\ket{x} \in \mathbb{C}^2  \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
+	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
+
+	We can prove that
+	\begin{equation}
+	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
 	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
 	\end{equation}
-For that, to calculate $\nu_E$ we obtain \begin{equation}
-	\max_{E \in \diaguni_2 } \nu_E  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
+	For that we obtain \begin{equation}
+	\max_{E \in \diaguni_2 } \nu_{UE}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
 		\Omega_2} \left| \tr \rho U E  \right|
@@
 \end{proof}
+\begin{theorem}
+The optimal probability of correct discrimination between von Neumann
+measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
+where $\phi \in [0, 2\pi)$ is given by
+\begin{equation}
+p = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
+\end{equation}
+\end{theorem}
+\begin{proof}
+	From Holevo-Helstrom theorem we obtain
+	\begin{equation}
+	p = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond,
+	\end{equation}
+	therefore from Theorem 1 in \cite{puchala2018strategies} we have 
+	\begin{equation}
+	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond. 
+	\end{equation}
+	From Lemma~\ref{lemma:min-e-optimal} we show that 
+	\begin{equation}
+		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
+	\Phi_\Id\|_\diamond
+	\end{equation} and hence, from the problem of discrimination of unitary channels, we receive 
+	\begin{equation}
+	p = \frac{1}{2} + \frac{1}{2} \sqrt{1 - \nu^2} = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
+	\end{equation} which completes the proof.
+\end{proof}
+
+\todo[inline]{change proof of proposition into proof of theorem}
 
@@
 
-%The schematic representation of theoretical 
-%setup is shown in Fig.~\ref{fig:theoretical}.
+The schematic representation of theoretical setup is shown in the following 
+figure.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.2]{pics/theoretical_scheme}
+\caption{Theoretical discrimination scheme}
+\label{fig:theoretical_scheme}
+\end{figure}
 
@@
 
-%\begin{figure}[h!]
-%	\centering 
-%	\includegraphics[width=0.75\linewidth, angle=-90]{rys-postsellection.jpg} 
-%	
-%	\caption{ A schematic representation of the setup for distinguishing
-%		measurements using postselection. 
-%	}\label{fig:postsellection}
-%\end{figure}
+\begin{figure}[h!]
+\centering 
+\includegraphics[scale=1.2]{pics/postselection}
+
+\caption{ A schematic representation of the setup for distinguishing
+	measurements using postselection. 
+}\label{fig:postsellection}
+\end{figure}
 \begin{enumerate}
@@
 \begin{scheme}(By using controlled unitary)
-%\begin{figure}[h!]
-%	\centering 
-%	\includegraphics[width=0.75\linewidth, angle=-90]{rys-controlled.jpg} 
-%	
-%	\caption{ A schematic representation of the setup for distinguishing
-%		measurements using controlled unitary gate. 
-%	}\label{fig:controlled}
-%\end{figure}
+\begin{figure}[h!]
+\centering 
+\includegraphics[scale=1.2]{pics/controlled_unitary}
+
+\caption{ A schematic representation of the setup for distinguishing
+	measurements using controlled unitary gate. 
+}\label{fig:controlled}
+\end{figure}
 \begin{enumerate}

### 2022-07-04 txt/manuscript.tex
proofs cd

@@
 \usepackage{amsthm}
-
+\usepackage{mathtools}
 %% The lineno packages adds line numbers. Start line numbering with
@@
 	$
-	where $\nu_U = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$.
-
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$. 
 	For $U = H 
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{i \phi} | }{4}$. So, 
-	\begin{equation}
-	\|  \Phi_U  - \Phi_{\1} \|_\diamond = \frac{| 1 - e^{i \phi} |}{2}. 
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
+	\begin{equation}
+	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |. 
 	\end{equation} 
@@
 		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-		\Phi_\Id\|_\diamond  = \frac{| 1 - e^{i \phi} |}{2}.
-		\end{equation}
-
-		It implies that we can prove  equivalently  the following condition
-		\begin{equation}
-		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
-		\end{equation}
-	It implies that it is enough to prove 
-	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_E = \nu = \frac{|1 + e^{i \phi} | }{2},
+		\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
+		\end{equation}
+%		It implies that we can prove  equivalently  the following condition
+%		\begin{equation}
+%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
+%		\end{equation}
+This condition is equivalent to 
+	\begin{equation}
+	\max_{E \in \diaguni_2 } \nu_{E} \coloneqq \nu = \frac{|1 + e^{i \phi} | }{2},
 	\end{equation}
 	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $ 
-
 	We can prove that
@@
 	\end{equation}
-	For that we obtain \begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{UE}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
-		\Omega_2} \left| \tr \rho U E  \right|
+	So we obtain \begin{equation}
+	\max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
+		\Omega_2} \left| \tr \left( \rho U E \right) \right|
 	\end{equation}
@@
 	\begin{equation}
-	\forall E \in \diaguni_2 \,\, | \tr \rho U E | \le \nu. 
+	\forall E \in \diaguni_2 \,\, | \tr \left(\rho U E\right) | \le \nu. 
 	\end{equation}
@@
 	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
-	From spectral theorem, let us note $U$ as
+	From spectral theorem, let us decompose $U$ as
 	\begin{equation}
@@
 	\begin{split}
-	& \forall E \in \diaguni_2 \,\,\, | \tr \rho U E | = \frac{1}{2}  \left| \tr 
-	H \diag(1, e^{i\phi}) H^\dagger E \right| =  \\ &
+	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
+	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
 	\frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) 
@@
 	\begin{equation}
-	p = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond,
-	\end{equation}
-	therefore from Theorem 1 in \cite{puchala2018strategies} we have 
+	p = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
+	\end{equation}
+	Whereas, from Theorem 1 in \cite{puchala2018strategies}, we have 
 	\begin{equation}
@@
 	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-	\Phi_\Id\|_\diamond
-	\end{equation} and hence, from the problem of discrimination of unitary channels, we receive 
-	\begin{equation}
-	p = \frac{1}{2} + \frac{1}{2} \sqrt{1 - \nu^2} = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
+	\Phi_\Id\|_\diamond,
+	\end{equation} which is exactly equal to 
+	\begin{equation}
+	\|\Phi_{U} - 
+	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|. 
+	\end{equation}
+	Finally, we obtain that
+	\begin{equation}
+	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
+	\end{equation}
+	It implies that
+	\begin{equation}
+	p  = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
 	\end{equation} which completes the proof.
 \end{proof}
-
-\todo[inline]{change proof of proposition into proof of theorem}
 
@@
 Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
-and $\PP_\1$, where $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
+and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
 2\pi)$.  The optimal input state has the form
@@
 
-\todo[inline]{add formal proof of the proposition}
-
-\begin{theorem}\label{rozrpomiarow}
-Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = 
-H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
-\not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the 
-form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
-	\begin{enumerate}
-		\item $\rho_1,\rho_2 \in \Omega_2$
-		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
-		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
-		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
-	\end{enumerate}
-	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
-	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of 
-	$U$. Then  we have 
-	\begin{equation}
-	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i 
-	\phi}}{2}\right|^2}.
-	\end{equation}
-	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą 
-	%wartością własną $U\in \mathrm{U}(\XX)$.
-\end{theorem}
-\begin{proof} From \ref{th:minE} we have 
-	\begin{equation}
-	\begin{split}
-	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} 
-	||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in 
-	\diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) 
-	||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || 
-	\Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| 
-	\Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
-	\end{split}
-	\end{equation}
-The diamond norm between two unitary channels can be calculated by 
-	\begin{equation}
-	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = 
-	\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho 
-	)|^2}.
-	\end{equation}
-Hence,  it is enough to calculate the formula
-\begin{equation}
-\begin{split}
-\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
-\end{split}
-\end{equation}
-Recall, let us note $U$ as
-\begin{equation}
-U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
-\end{equation}
-where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is of 
-the form $\ket{x_1} = 
-\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
- whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
-\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
-
-Consider two cases:
-
-	$1^\circ$ Consider $\phi = \pi$. Then $U$ is of the form
-	\begin{equation}
-	U = \left(\begin{array}{cc}0&1\\1&0\end{array}\right).
-	\end{equation}
-Then $0 \in W(U)$. 	From Proposition 3 in ~\cite{puchala2018strategies} the 
-measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if 
-and only if there exists $\rho \in \Omega_2$ such that
-	\begin{equation}
-	\mathrm{diag}\left(U^\dagger \rho\right) = 0.
-	\end{equation}
-Hence, for $U $ we have 
-	\begin{equation}
-	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} 
-	\left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right)
-	 =  \mathrm{diag} 
-	\left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
-	\end{equation}
- It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for 
- which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the 
- form
-	\begin{equation}
-	\rho = \left(\begin{array}{cc}\rho_{1,1}&0\\0&\rho_{2,2}\end{array}\right),
-	\end{equation}
-	where $\rho_{1,1},\rho_{2,2} \ge 0$ and  $\rho_{1,1}+\rho_{2,2}=1$.
-
-	$2^\circ$ Consider  $\phi \not = \pi$. 
-The spectrum of $U$ is of the form $\sigma(U) = \{e^{i \phi},1\}$. 
-Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
-	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
-	\end{equation}
-Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = 
-\ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 
-\in \Omega_2$ and satisfies the requirements of theorem. Hence, the 
-discriminator $\rho \in \Omega_2$ has the form 
-	\begin{equation}
-	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = 
-	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
-	\end{equation}
-%and 
+%
+%
+%\begin{theorem}\label{rozrpomiarow}
+%Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = 
+%H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
+%\not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the 
+%form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
+%	\begin{enumerate}
+%		\item $\rho_1,\rho_2 \in \Omega_2$
+%		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
+%		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
+%		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
+%	\end{enumerate}
+%	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
+%	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of 
+%	$U$. Then  we have 
 %	\begin{equation}
-%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 
-%+ e^{\mathbf{i} \phi}}{2}\right|^2 },
+%	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i 
+%	\phi}}{2}\right|^2}.
 %	\end{equation}
-
-%	
-%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} 
-%\rho_2$ we have 
-%	\begin{equation}
-%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 
-%\right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = 
-%\frac{\lambda_1+\lambda_2}{2}. 
-%	\end{equation}
-%	Therefore, we have
-%	\begin{equation}
-%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- 
-%\left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
-%	\end{equation}
-%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 
-%e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. 
-%Then we have 
+%	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą 
+%	%wartością własną $U\in \mathrm{U}(\XX)$.
+%\end{theorem}
+%\begin{proof} From \ref{th:minE} we have 
 %	\begin{equation}
 %	\begin{split}
-%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E 
-%\right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = 
-%\frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} 
-%\lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} 
-%\left(\lambda_1 
-%+ \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
+%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} 
+%	||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in 
+%	\diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) 
+%	||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || 
+%	\Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| 
+%	\Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
 %	\end{split}
 %	\end{equation}
-%So we have 
+%The diamond norm between two unitary channels can be calculated by 
 %	\begin{equation}
-%	\left|\tr\left(UE \rho \right) \right| = 
-%\left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 
-%\bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} 
-%\right|.
+%	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = 
+%	\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho 
+%	)|^2}.
 %	\end{equation}
-%	It implies that
+%Hence,  it is enough to calculate the formula
+%\begin{equation}
+%\begin{split}
+%\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
+%\end{split}
+%\end{equation}
+%Recall, let us note $U$ as
+%\begin{equation}
+%U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
+%\end{equation}
+%where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is of 
+%the form $\ket{x_1} = 
+%\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
+% whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
+%\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
+% 
+%Consider two cases:
+%
+%	$1^\circ$ Consider $\phi = \pi$. Then $U$ is of the form
 %	\begin{equation}
-%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  
-%|\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
+%	U = \left(\begin{array}{cc}0&1\\1&0\end{array}\right).
 %	\end{equation}
-%	Hence we obtain
+%Then $0 \in W(U)$. 	From Proposition 3 in ~\cite{puchala2018strategies} the 
+%measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if 
+%and only if there exists $\rho \in \Omega_2$ such that
 %	\begin{equation}
-%	\begin{split}
-%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} 
-%\sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} 
-%\right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 
-%-\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
-%	\end{split}
+%	\mathrm{diag}\left(U^\dagger \rho\right) = 0.
 %	\end{equation}
-For $\rho =  \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we obtain
+%Hence, for $U $ we have 
+%	\begin{equation}
+%	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} 
+%	\left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right)
+%	 =  \mathrm{diag} 
+%	\left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
+%	\end{equation}
+% It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for 
+% which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the 
+% form
+%	\begin{equation}
+%	\rho = \left(\begin{array}{cc}\rho_{1,1}&0\\0&\rho_{2,2}\end{array}\right),
+%	\end{equation}
+%	where $\rho_{1,1},\rho_{2,2} \ge 0$ and  $\rho_{1,1}+\rho_{2,2}=1$.
+%
+%	$2^\circ$ Consider  $\phi \not = \pi$. 
+%The spectrum of $U$ is of the form $\sigma(U) = \{e^{i \phi},1\}$. 
+%Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
+%	\begin{equation}
+%	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
+%	\end{equation}
+%Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = 
+%\ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 
+%\in \Omega_2$ and satisfies the requirements of theorem. Hence, the 
+%discriminator $\rho \in \Omega_2$ has the form 
+%	\begin{equation}
+%	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = 
+%	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
+%	\end{equation}
+%%and 
+%%	\begin{equation}
+%%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 
+%%+ e^{\mathbf{i} \phi}}{2}\right|^2 },
+%%	\end{equation}
+%
+%	
+%%	
+%%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} 
+%%\rho_2$ we have 
+%%	\begin{equation}
+%%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 
+%%\right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = 
+%%\frac{\lambda_1+\lambda_2}{2}. 
+%%	\end{equation}
+%%	Therefore, we have
+%%	\begin{equation}
+%%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- 
+%%\left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
+%%	\end{equation}
+%%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 
+%%e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. 
+%%Then we have 
+%%	\begin{equation}
+%%	\begin{split}
+%%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E 
+%%\right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = 
+%%\frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} 
+%%\lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} 
+%%\left(\lambda_1 
+%%+ \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
+%%	\end{split}
+%%	\end{equation} 
+%%So we have 
+%%	\begin{equation}
+%%	\left|\tr\left(UE \rho \right) \right| = 
+%%\left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 
+%%\bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} 
+%%\right|.
+%%	\end{equation}
+%%	It implies that
+%%	\begin{equation}
+%%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  
+%%|\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
+%%	\end{equation}
+%%	Hence we obtain
+%%	\begin{equation}
+%%	\begin{split}
+%%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} 
+%%\sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} 
+%%\right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 
+%%-\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
+%%	\end{split}
+%%	\end{equation
+\begin{proof}
+
 	\begin{equation}
 	\begin{split}
-	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=1}^2  
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond & =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1   \\ & =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \sum_{i=0}^{d-1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  \|_1  \\ & = \max_{\rho \in \Omega_d} \| \sum_{i=0}^{d-1} \proj{i} \otimes \sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1  \\ & =
+	 \max_{\rho \in \Omega_d} \| \sum_{i=0}^{d-1}\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1
+	\end{split}
+	\end{equation}
+	We can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, \ket{y}$ the following equation holds 
+	\begin{equation}
+	\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha \beta |\braket{x}{y}|^2}.
+	\end{equation}
+	By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} \ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} \ket{i} \|}$ we obtain 
+	\begin{equation}
+		\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_d} \sum_{i=0}^{d-1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i }\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
+	\end{equation}
+	\todo[inline]{dokonczyc}
+
+	Let us consider  $\rho =   \frac{1}{2}  	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
+	\begin{equation}
+	\begin{split}
+	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=0}^1  
 	\sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 
-	4|\bra{i}\rho\ket{u_i}|^2} = \\& \sum_{i=1}^2  
-	\sqrt{\left(\bra{i}U^\dagger\rho U \ket{i} + \bra{i} \rho \ket{i} \right)^2 
-	- 4|\bra{i}\rho U \ket{i}|^2} = \\& \sum_{i=1}^2  \sqrt{4 \bra{i}\rho 
+		4|\bra{i}\rho\ket{u_i}|^2} = \\&  \sum_{i=0}^1  \sqrt{4 \bra{i}\rho 
 		\ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + 
-	\lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=1}^2  \sqrt{4 
-	\bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i} \left| \frac{\lambda_1 + 
-	\lambda_2}{2}\right|^2} = \\&  \sum_{i=1}^2 2 \bra{i} \rho \ket{i} \sqrt{1 
+			\lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=0}^1  \sqrt{4 
+		\bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i}^2\left| \frac{\lambda_1 + 
+			\lambda_2}{2}\right|^2} = \\&  \sum_{i=0}^1 2 \bra{i} \rho \ket{i} \sqrt{1 
 		-\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| 
 		\frac{\lambda_1 + \lambda_2}{2}\right|^2 } = 
-	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } ,
+	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } = |1-e^{i \phi }|. 
 	\end{split}
+	\end{equation}
+	From the definition of Choi matrix $J(\Phi)$ of $\Phi$ we have
+	\begin{equation}
+\| (\Id\otimes \sqrt{\rho} ) J(\Phi)  (\Id\otimes \sqrt{\rho} ) \|_1  =  \| (\Phi \otimes \Id) \left(  | \sqrt{\rho}^\top \rangle  \rangle \langle \langle \sqrt{\rho}^\top | \right) \|_1.
+	\end{equation}
+	So we obtain that \begin{equation}
+	\ket{\psi_{AB}} =   | \sqrt{\rho}^\top \rangle  \rangle = \frac{1}{\sqrt{2} } | \Id_2 \rangle \rangle, 
 	\end{equation}
@@
 
-\begin{remark}\label{lemma:rho}
-	Let $\rho_{0} = \frac{1}{2} 
-	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)$. Then 
-	\begin{equation}
-	 \max_\rho \left\|(\1\otimes \sqrt{\rho}) J(\PP_U - \PP_{\Id}) 
-	(\1\otimes 
-	\sqrt{\rho})\right\|_1 =    \left\|(\1\otimes \sqrt{\rho_0}) J(\PP_U - 
-	\PP_{\Id}) 
-		(\1\otimes 
-		\sqrt{\rho_0})\right\|_1
-	\end{equation}
-	for  $U = H\diag(1, e^{i \phi}) H^\dagger $, 
-		where $\phi \in [0, 2\pi)$. 
-\end{remark}
+%
+%
+%\begin{remark}\label{lemma:rho}
+%	Let $\rho_{0} = \frac{1}{2} 
+%	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)$. Then 
+%	\begin{equation}
+%	 \max_\rho \left\|(\1\otimes \sqrt{\rho}) J(\PP_U - \PP_{\Id}) 
+%	(\1\otimes 
+%	\sqrt{\rho})\right\|_1 =    \left\|(\1\otimes \sqrt{\rho_0}) J(\PP_U - 
+%	\PP_{\Id}) 
+%		(\1\otimes 
+%		\sqrt{\rho_0})\right\|_1
+%	\end{equation}
+%	for  $U = H\diag(1, e^{i \phi}) H^\dagger $, 
+%		where $\phi \in [0, 2\pi)$. 
+%\end{remark}
 

### 2022-07-05 txt/manuscript.tex
reformulate structure of text

@@
 
+\subsubsection{Rigetti architecture's limits/ practical solutions}
+
+We may encounter numerous obstacles in the implementation process due to the 
+limited architecture of quantum computer. 
+Let us take a closer look at the setup for distinguishing von Neumann 
+measurements (see Fig.~\ref{fig:diamond}). One of the components of such a 
+scheme is to perform the conditional binary measurement. The first limitation 
+is lack to possibility of implementation of the conditional binary measurement. 
+The only possible measurement performed on quantum architectures is measurement 
+in the computational basis. 
+A postselection method provides us with a clever going around the obstacle. The 
+postselection  scheme (see Fig.~\ref{postselection})  can be described as 
+follow.
+
+\begin{enumerate}
+	\item We prepare input state $\ket{\psi_{AB}}$.
+	\item One of two measurements is performed on part A.
+	\item We prepare optimal measurements $V_j$, which are well known by 
+	Holevo--Helstrom theorem and perform them on part $B$.
+	\item We get the output label $i$.
+	\item We include these cases for which $i = j$. Otherwise, we reject them.
+	\item By the use of $V_j$ output, we decide whether the measurement was 
+	performed on part $A$.
+	\item We count the probability of postselection.
+\end{enumerate}
+
+\todo[inline]{PAMIETAJ O DAGGERACH !!!}
+
+\begin{figure}[h!]
+	\includegraphics[scale=1.5]{onequbit.pdf}
+	\caption{A schematic representation of the setup for distinguishing
+		measurements using postselection.}
+	\label{postselection}
+\end{figure}
+
+The schematic representation of theoretical setup is shown in the following 
+figure.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1.2]{pics/theoretical_scheme}
+	\caption{Theoretical discrimination scheme}
+	\label{fig:theoretical_scheme}
+\end{figure}
+\todo[inline]{konretne przyklady zobaczymy potem... }
+
+\subsubsection{Two schemes of practical realization}
+
+\begin{scheme}(By using postsellection)
+
+	\begin{figure}[h!]
+		\centering 
+		\includegraphics[scale=1.2]{pics/postselection}
+
+		\caption{ A schematic representation of the setup for distinguishing
+			measurements using postselection. 
+		}\label{fig:postsellection}
+	\end{figure}
+	\begin{enumerate}
+		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
+		\rangle. $
+		\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
+		\item We implement unitary $V_0 $ or $ V_1$.
+		\item We prepare the measurement $\Delta$ in standard basis (already exists on 
+		Rigetti architecture) on each qubits.
+		\item We calculate the probability of correct discrimination in the following 
+		way
+		\begin{equation}
+		p = ...
+		\end{equation}
+		%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
+	\end{enumerate}
+\end{scheme}
+
+\begin{scheme}(By using controlled unitary)
+	\begin{figure}[h!]
+		\centering 
+		\includegraphics[scale=1.2]{pics/controlled_unitary}
+
+		\caption{ A schematic representation of the setup for distinguishing
+			measurements using controlled unitary gate. 
+		}\label{fig:controlled}
+	\end{figure}
+	\begin{enumerate}
+		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
+		\rangle. $
+		\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
+		\item We implement controlled unitary $V_0 \oplus V_1$.
+		\item We prepare the measurement $\Delta$ in standard basis (already exist on 
+		Rigetti architecture) on each qubits.
+		\item We calculate the probability of correct discrimination in the following 
+		way
+		\begin{equation}
+		p = \frac{|j=0 \wedge \Phi_{U} | + |j=1 \wedge \Phi_{\1}|}{\text{all 
+				cases}}
+		\end{equation}
+	\end{enumerate}
+\end{scheme}
+
 \subsubsection{Theoretical results}
@@
 \Phi: M_{d_1 } \rightarrow M_{d_2}.
-\end{equation} Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
+\end{equation} 
+\todo[inline]{nie mowimy channel} 
+Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
 and trace preserving (CPTP).
@@
 where $\Phi_U$ is unitary channel and 
-$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$
+$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$.
 
@@
 %\end{minipage}
-
-\subsubsection{Rigetti architecture's limits/ practical solutions}
-\todo[inline]{nie wiem, moze tu o conditional measurement i o sposobach 
-ominiecia tego problemu - postselekcja i kontrolowana unitarka}
-
-We may encounter numerous obstacles in the implementation process due to the 
-limited architecture of quantum computer. 
-Let us take a closer look at the setup for distinguishing von Neumann 
-measurements (see Fig.~\ref{fig:diamond}). One of the components of such a 
-scheme is to perform the conditional binary measurement. The first limitation 
-is lack to possibility of implementation of the conditional binary measurement. 
-The only possible measurement performed on quantum architectures is measurement 
-in the computational basis. 
-A postselection method provides us with a clever going around the obstacle. The 
-postselection  scheme (see Fig.~\ref{postselection})  can be described as 
-follow.
-
-\begin{enumerate}
-	\item We prepare input state $\ket{\psi_{AB}}$.
-	\item One of two measurements is performed on part A.
-	\item We prepare optimal measurements $V_j$, which are well known by 
-	Holevo--Helstrom theorem and perform them on part $B$.
-	\item We get the output label $i$.
-	\item We include these cases for which $i = j$. Otherwise, we reject them.
-	\item By the use of $V_j$ output, we decide whether the measurement was 
-	performed on part $A$.
-	\item We count the probability of postselection.
-\end{enumerate}
-
-\begin{figure}[h!]
-	\includegraphics[scale=1.5]{onequbit.pdf}
-	\caption{A schematic representation of the setup for distinguishing
-		measurements using postselection.}
-	\label{postselection}
-\end{figure}
-
-\subsection{Sample code snippets analysis (optional)}
-\todo[inline]{moze tu kod tej postselekcji  i kontrolowanej unitarki ? }
-\label{}
 
@@
 
-The schematic representation of theoretical setup is shown in the following 
-figure.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/theoretical_scheme}
-\caption{Theoretical discrimination scheme}
-\label{fig:theoretical_scheme}
-\end{figure}
-
 From ~\cite{puchala2018strategies}(Proposition 4) and Lemma~\ref{lemma:rho} we 
@@
 
-\subsubsection{Two schemes of practical realization}
-
-\begin{scheme}(By using postsellection)
-
-\begin{figure}[h!]
-\centering 
-\includegraphics[scale=1.2]{pics/postselection}
-
-\caption{ A schematic representation of the setup for distinguishing
-	measurements using postselection. 
-}\label{fig:postsellection}
-\end{figure}
-\begin{enumerate}
-\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
-\rangle. $
-\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
-\item We implement unitary $V_0 $ or $ V_1$.
-\item We prepare the measurement $\Delta$ in standard basis (already exists on 
-Rigetti architecture) on each qubits.
-\item We calculate the probability of correct discrimination in the following 
-way
-\begin{equation}
-p = ...
-\end{equation}
-%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
-\end{enumerate}
-\end{scheme}
-
-\begin{scheme}(By using controlled unitary)
-\begin{figure}[h!]
-\centering 
-\includegraphics[scale=1.2]{pics/controlled_unitary}
-
-\caption{ A schematic representation of the setup for distinguishing
-	measurements using controlled unitary gate. 
-}\label{fig:controlled}
-\end{figure}
-\begin{enumerate}
-\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
-\rangle. $
-\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
-\item We implement controlled unitary $V_0 \oplus V_1$.
-\item We prepare the measurement $\Delta$ in standard basis (already exist on 
-Rigetti architecture) on each qubits.
-\item We calculate the probability of correct discrimination in the following 
-way
-\begin{equation}
-p = \frac{|j=0 \wedge \Phi_{U} | + |j=1 \wedge \Phi_{\1}|}{\text{all 
-cases}}
-\end{equation}
-\end{enumerate}
-\end{scheme}
+\todo[inline]{obwody }
+\todo[inline]{TU WYNIKI Z RIGETTIEGO}
+
+\subsection{Sample code snippets analysis (optional)}
+\todo[inline]{moze tu kod tej postselekcji  i kontrolowanej unitarki ? }
+\label{}
 

### 2022-08-02 txt/manuscript.tex
manuscript changes - proofs

@@
 \subsubsection{Model specification}
-Theoretically, scenario of this set up assume that Alice and Bob have an 
-unknown measurement device, black--box.  Alice has hiden one of the two 
-measurements  in the black box.  The only information which Bob has is that it 
+Theoretically, the scenario of this set-up assumes that Alice and Bob have an 
+unknown measurement device, a black--box. Alice has hidden one of the two 
+measurements, say $\SS$ and $\TT$,  in the black box. Bob only has information that it 
 performs one of such measurements. 
-The  goal of discrimination of von Neumann measurements  is to determine by Bob 
-whether it is possible to discriminate measurements perfectly, i.e. with 
-probability equals one. If this is not possible, he  would like to know the 
-upper bound of such a probability.  Theoretical results of discrimination of 
-von Neumann measurements is well-known and characterized 
-in~\cite{puchala2018strategies}.    The scheme of von Neumann discrimination is 
+First, they want to tell whether it is possible to discriminate $\SS$ and $\TT$ perfectly, i.e. with probability equal to one. If this is not the case, we would like to
+know the upper bound of such a probability. 
+Theoretical results of discrimination of 
+von Neumann measurements are well-known and characterized 
+in~\cite{puchala2018strategies}.   
+They devised the optimal discrimination strategy between two von Neumann measurements and also calculated the exact probability of their discrimination.
+
+In this work we will consider the problem of discrimination between the von Neumann measurement in the computational basis  and  the von Neumann measurement in basis $U$, where $U$ is a unitary matrix.
+This scheme is 
 presented in Fig.~\ref{fig:scheme} and 
@@
 
-\begin{enumerate}
-	\item Alice and Bob share entanglement state $\ket{\psi_{AB}}$.
-	\item Alice performs one of two known measurements on part $A$ of the input 
-	state  $\ket{\psi_{AB}}$.
-	\item Alice  uses
-	the output label $i$ and performs a conditional binary measurement on part 
-	$B$.
-	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
-	makes a decision  basis of the condition binary measurement.
-\end{enumerate}
-
-\begin{figure}[h]
+\begin{figure}[h!]
 	\centering 
-
 	\includegraphics[width=0.9\linewidth]{gates1.pdf} 
@@
 
-\subsubsection{Rigetti architecture's limits/ practical solutions}
-
-We may encounter numerous obstacles in the implementation process due to the 
-limited architecture of quantum computer. 
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1.5]{pics/theoretical_scheme}
+	\caption{Theoretical discrimination scheme}
+	\label{fig:theoretical_scheme}
+\end{figure}
+\todo[inline]{tan powinien byc $\PP_{V_i}$}
+
+\begin{enumerate}\item Alice and Bob share entanglement state $\ket{\psi_{AB}}$.
+	\item Alice performs one of two known measurements,  say $\PP_{\Id}$ and $\PP_{U}$,  on part $A$ of the input 
+	state  $\ket{\psi_{AB}}$.
+	\item Alice  uses
+	the output label $i$ and performs the conditional binary measurement on the part 
+	$B$.
+	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
+	makes a decision based on received label $j$.
+If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box.
+Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box.
+\end{enumerate}
+
+\subsubsection{Quantum architecture's limits and practical solutions}
+
 Let us take a closer look at the setup for distinguishing von Neumann 
-measurements (see Fig.~\ref{fig:diamond}). One of the components of such a 
+measurements (see Fig.~\ref{fig:scheme}). One of the components of such a 
 scheme is to perform the conditional binary measurement. The first limitation 
-is lack to possibility of implementation of the conditional binary measurement. 
-The only possible measurement performed on quantum architectures is measurement 
-in the computational basis. 
-A postselection method provides us with a clever going around the obstacle. The 
-postselection  scheme (see Fig.~\ref{postselection})  can be described as 
-follow.
-
-\begin{enumerate}
-	\item We prepare input state $\ket{\psi_{AB}}$.
-	\item One of two measurements is performed on part A.
-	\item We prepare optimal measurements $V_j$, which are well known by 
-	Holevo--Helstrom theorem and perform them on part $B$.
-	\item We get the output label $i$.
-	\item We include these cases for which $i = j$. Otherwise, we reject them.
-	\item By the use of $V_j$ output, we decide whether the measurement was 
-	performed on part $A$.
-	\item We count the probability of postselection.
-\end{enumerate}
-
-\todo[inline]{PAMIETAJ O DAGGERACH !!!}
-
+is a lack of possibility of implementing the conditional binary measurement. 
+The only possible measurement performed on quantum architectures is the measurement 
+on a computational basis. 
+Here, we present two possible methods that provide a clever way to cross the obstacle (two schemes of practical realization).
+
+The first way is a postselection scheme which can be described as 
+follow.  The schematic representation of this setup we can see on Fig.~\ref{postselection}.     
+\begin{scheme}(By using postsellection)
+
+\todo[inline]{PAMIETAJ O DAGGERACH  no i u nas to bedzie nazwane $\PP_{V^\dagger_j}$!!!} 
 \begin{figure}[h!]
@@
 
-The schematic representation of theoretical setup is shown in the following 
-figure.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.2]{pics/theoretical_scheme}
-	\caption{Theoretical discrimination scheme}
-	\label{fig:theoretical_scheme}
-\end{figure}
-\todo[inline]{konretne przyklady zobaczymy potem... }
-
-\subsubsection{Two schemes of practical realization}
-
-\begin{scheme}(By using postsellection)
-
 \begin{figure}[h!]
@@
 \begin{enumerate}
-		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
-		\rangle. $
-		\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
-		\item We implement unitary $V_0 $ or $ V_1$.
-		\item We prepare the measurement $\Delta$ in standard basis (already exists on 
-		Rigetti architecture) on each qubits.
-		\item We calculate the probability of correct discrimination in the following 
-		way
-		\begin{equation}
-		p = ...
-		\end{equation}
-		%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
+	\item We prepare input state $\ket{\psi_{AB}}$.
+	\item One of two measurements is performed on part A.
+	\item We prepare optimal measurements $V_j$, which are well known by 
+	Holevo--Helstrom theorem and perform them on part $B$.
+	\item We receive an output label $i$.
+	\item We include these cases for which $i = j$. Otherwise, we reject them.
+	\item By the use of $V_j$ output, we decide whether the measurement was 
+	performed on part $A$.
+	\item We count the probability of postselection.
 \end{enumerate}
+
+%	\begin{enumerate}
+%		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
+%		\rangle. $
+%		\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
+%		\item We implement unitary $V_0 $ or $ V_1$.
+%		\item We prepare the measurement $\Delta$ in standard basis (already exists on 
+%		Rigetti architecture) on each qubits.
+%		\item We calculate the probability of correct discrimination in the following 
+%		way
+%		\begin{equation}
+%		p = ...
+%		\end{equation}
+%		%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
+%	\end{enumerate}
 \end{scheme}
@@
 
-\subsubsection{Theoretical results}
+\subsubsection{Mathematical preliminaries}
 
@@
 \end{equation}
-\todo[inline]{nie mowimy channel} 
+
 Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
 and trace preserving (CPTP).
-Mostly, we will use the unitary channels
-$\Phi_{U}$ which are defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
+A unitary channel
+$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
 \UU_d$. A general quantum
@@
 all the effects are rank-one projection operators, then such a measurement is
-called von Neumann measurement. Every von Neumann measurement can be
+called a von Neumann measurement. Every von Neumann measurement can be
 parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
@@
 
-\subsubsection{Diamond norm}
-Let us now consider linear mappings transforming  square matrices into square 
+\subsubsection{Discrimination of a quantum operations}
+This section defines a norm on the space of linear mappings, known as the diamond norm,
+and establishes some of its properties. 
+Next, we will also explain the precise connection between this
+norm and the task of quantum operations discrimination.
+
+Let us now consider a  linear mapping transforming  square matrices into square 
 matrices 
-that is \ $\Phi: M_{d_1} \to M_{d_2}$. 
- We define its completely bounded trace
-norm, also known as a diamond norm, as
+that is $\Phi: M_{d_1} \to M_{d_2}$. 
+ We define the diamond norm of a map $\Phi$ as 
 \begin{equation}
@@
 \begin{equation}
-p =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
+p_{succ} =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
 \end{equation}

### 2022-08-10 txt/manuscript.tex
changes  pictures and proofs

@@
 benchmark a modern quantum architectures. The main idea that we have envisioned 
-for this project is  introducing new concepts of algorithms for NISQ devices 
+for this project is  introducing new concepts of benchmarks for NISQ devices 
 benchmarking. This project aims to characterize the computing power and 
 investigate possible practical applications of such devices having access by 
-Amazon Braket.  First of all, we will focus on constraining quantum algorithms 
-being relatively easy to implement on quantum architectures with 
-straightforward, intuitive operational interpretation. Moreover, we need to 
-possess a scalability, that is the ability to adjust to large range of 
-architectures size.  
-These properties will give us major advantage over the existing approaches  of 
-benchmarking.
-
-This idea is built upon two specific tasks that are to be achieved within this 
-proposal. 
-The first task is to   desing a benchmark based on discrimination of von 
-Nemaumm measurements scheme. While the second one is to extension  this 
-approach to benchmark on the grounds of certification of von Neumann 
-measurements scheme.
+Amazon Braket.
 
@@
 performs one of such measurements. 
-First, they want to tell whether it is possible to discriminate $\SS$ and $\TT$ perfectly, i.e. with probability equal to one. If this is not the case, we would like to
-know the upper bound of such a probability. 
+They want to know the upper bound of the   probability of correct discrimination between $\SS$ and $\TT$ and construct the optimal discrimination strategy between them to achieve the highest possible probability of discrimination.
 Theoretical results of discrimination of 
@@
 in~\cite{puchala2018strategies}.
-They devised the optimal discrimination strategy between two von Neumann measurements and also calculated the exact probability of their discrimination.
-
-In this work we will consider the problem of discrimination between the von Neumann measurement in the computational basis  and  the von Neumann measurement in basis $U$, where $U$ is a unitary matrix.
+
+In this work we will consider the problem of discrimination between von Neumann measurement in the computational basis  and  the von Neumann measurement in basis $U$, where $U$ is a unitary matrix. 
 This scheme is 
-presented in Fig.~\ref{fig:scheme} and 
+presented in Fig.~\ref{fig:theoretical_scheme} and 
 can be divided into the following steps:
+
+%\begin{figure}[h!]
+%	\centering 
+%	\includegraphics[width=0.9\linewidth]{gates1.pdf} 
+%	\caption{A schematic representation of the setup for distinguishing
+%		measurements by using entanglement. }
+%	\label{fig:scheme}
+%\end{figure}
 
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{gates1.pdf} 
-	\caption{A schematic representation of the setup for distinguishing
-		measurements by using entanglement. }
-	\label{fig:scheme}
-\end{figure}
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.5]{pics/theoretical_scheme}
+	\includegraphics[scale=1.7]{pics/theoretical_scheme}
 	\caption{Theoretical discrimination scheme}
@@
 \end{figure}
-\todo[inline]{tan powinien byc $\PP_{V_i}$}
 
@@
 	state  $\ket{\psi_{AB}}$.
-	\item Alice  uses
-	the output label $i$ and performs the conditional binary measurement on the part 
-	$B$.
+	\item Alice   performs the conditional binary measurement on the part 
+	$B$ based on
+	the output label $i$. 
 	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
@@
 Let us take a closer look at the setup for distinguishing von Neumann 
-measurements (see Fig.~\ref{fig:scheme}). One of the components of such a 
-scheme is to perform the conditional binary measurement. The first limitation 
+measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of such a 
+scheme is to perform the conditional binary measurement. The first limitation of NISQ devices 
 is a lack of possibility of implementing the conditional binary measurement. 
@@
 
-The first way is a postselection scheme which can be described as 
-follow.  The schematic representation of this setup we can see on Fig.~\ref{postselection}.     
+The first way is to use a postselection whereas the second method is to apply a controlled unitary. The methods are described above.
+
 \begin{scheme}(By using postsellection)
 
-\todo[inline]{PAMIETAJ O DAGGERACH  no i u nas to bedzie nazwane $\PP_{V^\dagger_j}$!!!} 
-\begin{figure}[h!]
-	\includegraphics[scale=1.5]{onequbit.pdf}
-	\caption{A schematic representation of the setup for distinguishing
-		measurements using postselection.}
-	\label{postselection}
-\end{figure}
+\todo[inline]{wyzej mamy bez daggera, trzeba to ustalic} 
+%\begin{figure}[h!]
+%	\includegraphics[scale=1.5]{onequbit.pdf}
+%	\caption{A schematic representation of the setup for distinguishing
+%		measurements using postselection.}
+%	\label{postselection}
+%\end{figure}
+
+\begin{enumerate}
+	\item Alice and Bob prepare entanglement state $\ket{\psi_{AB}}$.
+	\item Alice performs one of two quantum channels, $\Phi_{\Id}$ and $\Phi_{U}$,  on part $A$ of the input 
+	state  $\ket{\psi_{AB}}$.
+	\item Alice measures the part $A$ of the input state  $\ket{\psi_{AB}}$ and receives an output label $i$.
+	\item  
+	From Holevo--Helstrom theorem, 
+	 Bob performs the conditional binary measurement $\PP_{V_j^\dagger}$ on the part 	$B$.
+	\item They include these cases for which $i = j$. Otherwise, they reject them.
+	\item
+	Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
+	makes a decision based on received label $j$.
+If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box.
+Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box.
+\end{enumerate}
+
+The schematic representation of this setup we can see on Fig.~\ref{fig:postsellection}.
 
@@
 	\centering 
-	\includegraphics[scale=1.2]{pics/postselection}
+	\includegraphics[scale=1.7]{pics/postselection}
 
@@
 \end{figure}
+
+PROBABILITY 
+		\begin{equation}
+		p = ...
+		\end{equation}
+		%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
+
+\end{scheme}
+
+\begin{scheme}(By using controlled unitary)
+
 	\begin{enumerate}
-	\item We prepare input state $\ket{\psi_{AB}}$.
-	\item One of two measurements is performed on part A.
-	\item We prepare optimal measurements $V_j$, which are well known by 
-	Holevo--Helstrom theorem and perform them on part $B$.
-	\item We receive an output label $i$.
-	\item We include these cases for which $i = j$. Otherwise, we reject them.
-	\item By the use of $V_j$ output, we decide whether the measurement was 
-	performed on part $A$.
-	\item We count the probability of postselection.
-\end{enumerate}
-
-%	\begin{enumerate}
+			\item Alice and Bob prepare entanglement state $\ket{\psi_{AB}}$.
 %		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
 %		\rangle. $
-%		\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
-%		\item We implement unitary $V_0 $ or $ V_1$.
-%		\item We prepare the measurement $\Delta$ in standard basis (already exists on 
-%		Rigetti architecture) on each qubits.
-%		\item We calculate the probability of correct discrimination in the following 
-%		way
-%		\begin{equation}
-%		p = ...
-%		\end{equation}
-%		%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
-%	\end{enumerate}
-\end{scheme}
-
-\begin{scheme}(By using controlled unitary)
+		\item Alice performs one of two quantum channels, $\Phi_{\Id}$ and $\Phi_{U}$,  on part $A$ of the input 
+		state  $\ket{\psi_{AB}}$.
+		\item Alice and Bob implement controlled unitary $V_0 \oplus V_1$ obtained from Holevo--Helstrom theorem.	
+		\item Alice and Bob prepare the measurement $\Delta$ in computational basis on theirs systems.
+		\item Bob	makes a decision based on received label $j$.
+If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box.
+Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box.
+
+	\end{enumerate}
+
 \begin{figure}[h!]
 	\centering 
-		\includegraphics[scale=1.2]{pics/controlled_unitary}
+	\includegraphics[scale=1.5]{pics/controlled_unitary}
 
@@
 \end{figure}
-	\begin{enumerate}
-		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
-		\rangle. $
-		\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
-		\item We implement controlled unitary $V_0 \oplus V_1$.
-		\item We prepare the measurement $\Delta$ in standard basis (already exist on 
-		Rigetti architecture) on each qubits.
-		\item We calculate the probability of correct discrimination in the following 
-		way
+
+PROBABILITY
+
 \begin{equation}
@@
 \end{equation}
-	\end{enumerate}
+
 \end{scheme}
@@
 \end{equation} 
+There
+exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
+Jamio{\l}kowski isomorphism.
 
@@
 quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
-expressed as the action of a quantum channel
+seen as  a measure-and-prepare quantum channel as follows 
 $
 \PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-$ Every von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta 
+$ It is worth noting that a given  von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta 
 \circ \Phi_{(UE)^\dagger}$, where $\Delta$ denotes the completely dephasing 
@@
 
-\subsubsection{Discrimination of a quantum operations}
-This section defines a norm on the space of linear mappings, known as the diamond norm,
+\subsubsection{Diamond norm}
+This section defines a special norm on the space of linear mappings, known as the diamond norm,
 and establishes some of its properties. 
-Next, we will also explain the precise connection between this
+Next, we will also explain the precise connection between the diamond
 norm and the task of quantum operations discrimination.
 
-Let us now consider a  linear mapping transforming  square matrices into square 
+Let us  consider a  linear mapping transforming  square matrices into square 
 matrices 
@@
 \end{equation}
+
+\begin{equation}
+\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}_\Phi  \left( \Id \otimes \sqrt{\rho} \right)  \|_1  \end{equation}
+
+\subsubsection{Discrimination of a quantum operations}
 
@@
 
-% The Appendices part is started with the command \appendix;
-% appendix sections are then done as normal sections
-% \appendix
-
-% \section{}
-% \label{}
-
-% References:
-% If you have bibdatabase file and want bibtex to generate the
-% bibitems, please use
-%
-%  \bibliographystyle{elsarticle-num} 
-%  \bibliography{<your bibdatabase>}
-
-% else use the following coding to input the bibitems directly in the
-% TeX file.
+ \section{}
+ \label{}
+
+ References:
+ If you have bibdatabase file and want bibtex to generate the
+ bibitems, please use
+
+  \bibliographystyle{elsarticle-num} 
+  \bibliography{<your bibdatabase>}
+
+ else use the following coding to input the bibitems directly in the
+ TeX file.
+
+ \bibliographystyle{ieeetr}
+ \bibliography{rigetti}
 

### 2022-08-28 txt/manuscript.tex
i am done

@@
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this section we will compare theoretical probability of correct 
-discrimination between these measurements and the realization on real devices.
-The theoretical probability can be calculated using Holevo-Helstrom theorem and 
+In this section we present theoretical probability of correct 
+discrimination between these measurements. Moreover, we create the optimal theoretical strategy of their discriminate. 
+Such a probability can be calculated using Holevo-Helstrom theorem and 
 Theorem 1 from~\cite{puchala2018strategies}. 
@@
 subsection~\ref{sec:example_theoretical_probability}. Later, we will 
-discuss the realization of this scheme on real devices in 
+discuss the realization of this scheme in 
 subsection~\ref{sec:example_realization}. For such realization, we 
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop-discrim}
 Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
@@
 	\begin{split}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond & =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1   \\ & =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \sum_{i=0}^{d-1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  \|_1  \\ & = \max_{\rho \in \Omega_d} \| \sum_{i=0}^{d-1} \proj{i} \otimes \sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1  \\ & =
-	 \max_{\rho \in \Omega_d} \| \sum_{i=0}^{d-1}\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond & =  \max_{\rho \in \Omega_2} \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1   \\ & =  \max_{\rho \in \Omega_2} \| \left( \Id \otimes \sqrt{\rho} \right) \sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  \|_1  \\ & = \max_{\rho \in \Omega_2} \| \sum_{i=0}^{1} \proj{i} \otimes \sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1  \\ & =
+	 \max_{\rho \in \Omega_2} \| \sum_{i=0}^{1}\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1
 	\end{split}
@@
 	\begin{equation}
-		\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_d} \sum_{i=0}^{d-1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i }\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
+		\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} \sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i }\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
 	\end{equation}
 	\todo[inline]{dokonczyc}
-
-	Let us consider  $\rho =   \frac{1}{2}  	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
+	Let us take  $\rho_0 =   \frac{1}{2}  	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
 	\begin{equation}
@@
 	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=0}^1  
-	\sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 
-		4|\bra{i}\rho\ket{u_i}|^2} = \\&  \sum_{i=0}^1  \sqrt{4 \bra{i}\rho 
-		\ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + 
-			\lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=0}^1  \sqrt{4 
-		\bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i}^2\left| \frac{\lambda_1 + 
-			\lambda_2}{2}\right|^2} = \\&  \sum_{i=0}^1 2 \bra{i} \rho \ket{i} \sqrt{1 
-		-\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| 
-		\frac{\lambda_1 + \lambda_2}{2}\right|^2 } = 
-	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } = |1-e^{i \phi }|. 
+	\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
+		4|\bra{i}\rho_0\ket{u_i}|^2} = \\& 
+	\sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} = \\ & 
+	 \sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} \ket{i} + 
+			e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} =\\&  \sum_{i=0}^1  \sqrt{ 
+		\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + 
+			e^{i \phi}}{2}\right|^2} = \\&  \sum_{i=0}^1\braket{i}{i} \sqrt{1 
+		-\left| \frac{1+ e^{i \phi}}{2}\right|^2 } = 
+	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } = \frac{|1-e^{i \phi }|}{2}. 
 	\end{split}
 	\end{equation}
-	From the definition of Choi matrix $J(\Phi)$ of $\Phi$ we have
-	\begin{equation}
-\| (\Id\otimes \sqrt{\rho} ) J(\Phi)  (\Id\otimes \sqrt{\rho} ) \|_1  =  \| (\Phi \otimes \Id) \left(  | \sqrt{\rho}^\top \rangle  \rangle \langle \langle \sqrt{\rho}^\top | \right) \|_1.
+	Due to that, we know  
+	that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem of discrimination between 
+	$\PP_{\Id} $ and $\PP_U$, where 
+	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm ).
+
+	\begin{equation}
+		\| \PP_{U} - \PP_{\Id}  \|_\diamond  =  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1  
+=  \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top \rangle  \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
 	\end{equation}
@@
 \begin{proposition}
+	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
+	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
+	2\pi)$.  
 The  final measurement has the form
@@
 \end{proposition}
-\todo[inline]{add proof of the proposition}
-
-From ~\cite{puchala2018strategies}(Proposition 4) and Lemma~\ref{lemma:rho} we 
-have 
+
+\begin{proof}
+From Proposition~\ref{prop-discrim} we have the form of discriminator given by
 \begin{equation}
@@
 X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
-\otimes \Id_2 \right)(\proj{\psi})
-\end{equation}
-where $\ket{\psi}$ is defined in Remark~\ref{remark:discriminator}. From 
-Hahn-Jordan decomposition let \begin{equation}
+\otimes \Id_2 \right)(\proj{\psi}).
+\end{equation} From 
+We consider the Hahn-Jordan decomposition, let \begin{equation}
 X = P - Q
@@
 where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
-Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $im(P)$ and $im(Q)$, 
+So, let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
 respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
@@
 \begin{equation}
-\begin{split}
-V_0 \ket{x_p} = \ket{0} \\ 
-V_0 \ket{x_q} = \ket{1}
-\end{split}
+\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
 \end{equation}
@@
 \begin{equation}
-\begin{split}
+\begin{cases} 
 V_1 \ket{y_p} = \ket{0} \\ 
 V_1 \ket{y_q} = \ket{1}
-\end{split}
-\end{equation}
-The explicit form of $V_0$ and $V_1$ we can see in \texttt{one-qubit.nb}.
+\end{cases} 
+\end{equation}
+For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H \diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given by following (see also \texttt{one-qubit.nb}).
+The unitary $V_0$ 
+has the following form
+\begin{equation}
+V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
+\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
+	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+\end{equation}
+whereas the unitary  $V_1$  has the form
+\begin{equation}
+V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
+\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
+\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+\end{equation}
+for all $\phi \in [0,2\pi)$. 
 Finally, we obtain the measurement $\mu$ of the form
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-
-\paragraph{Construction of $V_0$ and $V_1$}
-	For each $\phi \in \mathbb{R}$,  the controlled unitary $V_0$ and $V_1$ 
-	have the following form
-	\begin{equation}
-	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
-	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
-	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
-	\end{equation}
-
-		\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
-	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
-	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
-	\end{equation}
-
-\todo[inline]{obwody }
-\todo[inline]{TU WYNIKI Z RIGETTIEGO}
+\end{proof}
+
+\section{Implementation}
+In this section we will compare theoretical probability of correct 
+discrimination between these measurements and the realization on real devices.
+\todo[inline]{TU WYNIKI PRAKTYTCZNE }
+\todo[inline]{tu rozklad i obwody}
 

### 2022-09-29 txt/manuscript.tex
Rewrite section 2.2.1.

@@
 \subsubsection{Model specification}
-Theoretically, the scenario of this set-up assumes that Alice and Bob have an 
-unknown measurement device, a black--box. Alice has hidden one of the two 
-measurements, say $\SS$ and $\TT$,  in the black box. Bob only has information that it 
-performs one of such measurements. 
-They want to know the upper bound of the   probability of correct discrimination between $\SS$ and $\TT$ and construct the optimal discrimination strategy between them to achieve the highest possible probability of discrimination.
-Theoretical results of discrimination of 
-von Neumann measurements are well-known and characterized 
-in~\cite{puchala2018strategies}.
-
-In this work we will consider the problem of discrimination between von Neumann measurement in the computational basis  and  the von Neumann measurement in basis $U$, where $U$ is a unitary matrix. 
-This scheme is 
-presented in Fig.~\ref{fig:theoretical_scheme} and 
-can be divided into the following steps:
+The scenario assumes that Alice and Bob have access to an unknown measurement
+device, a black box. Alice has hidden one of the two measurements, either $\SS$
+or $\TT$, in the black box. Bob only has the information that the black box
+performs one of these measurements. They want to know the upper bound on the
+probability of correct discrimination between $\SS$ and $\TT$. They also want to
+construct the optimal discrimination strategy to achieve the highest probability
+of correct discrimination. Theoretical results on discrimination of von Neumann
+measurements are characterized in~\cite{puchala2018strategies}.
+
+In this work we will consider the problem of discrimination between von Neumann 
+measurement in the computational basis and a von Neumann measurement in basis 
+$U$, where $U$ is a unitary matrix. 
+The scheme of discrimination can be divided into the following steps, which are 
+illustrated in Fig.~\ref{fig:theoretical_scheme}.
 
@@
 
+\begin{enumerate}
+	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on registers 
+	$A$ and $B$.
+	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
+	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$.
+	\item Alice performs the conditional binary measurement on the part 
+	$B$ based on the output label $i$. 
+	\item  Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and 
+	makes a decision based on the received label $j$. If $j=0$, then he decides 
+	that the the black box contains $\PP_U$. Otherwise, he decides that the 
+	black box contains $\PP_{\Id}$. 
+\end{enumerate}
+
 \begin{figure}[h!]
@@
 \end{figure}
-
-\begin{enumerate}\item Alice and Bob share entanglement state $\ket{\psi_{AB}}$.
-	\item Alice performs one of two known measurements,  say $\PP_{\Id}$ and $\PP_{U}$,  on part $A$ of the input 
-	state  $\ket{\psi_{AB}}$.
-	\item Alice   performs the conditional binary measurement on the part 
-	$B$ based on
-	the output label $i$. 
-	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
-	makes a decision based on received label $j$.
-If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box.
-Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box.
-\end{enumerate}
 

### 2022-09-29 txt/manuscript.tex
Correct schemes in section 2.2.2.

@@
 \begin{enumerate}
-	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on registers 
+	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on systems 
 	$A$ and $B$.
@@
 Let us take a closer look at the setup for distinguishing von Neumann 
-measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of such a 
-scheme is to perform the conditional binary measurement. The first limitation of NISQ devices 
-is a lack of possibility of implementing the conditional binary measurement. 
-The only possible measurement performed on quantum architectures is the measurement 
-on a computational basis. 
-Here, we present two possible methods that provide a clever way to cross the obstacle (two schemes of practical realization).
-
-The first way is to use a postselection whereas the second method is to apply a controlled unitary. The methods are described above.
+measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of 
+this scheme is to perform the conditional binary measurement. 
+Unfortunately, current NISQ devices do not allow for performing conditional 
+binary measurements.
+The only possible measurement performed on quantum architectures is the 
+measurement in the computational basis. 
+We  will present two possible methods providing a clever way to cross this 
+obstacle. These will be two schemes of practical realization. 
+The first method consists in using post-selection while the second method 
+consists in applying a controlled unitary. These methods are described below.
 
@@
 \begin{enumerate}
-	\item Alice and Bob prepare entanglement state $\ket{\psi_{AB}}$.
-	\item Alice performs one of two quantum channels, $\Phi_{\Id}$ and $\Phi_{U}$,  on part $A$ of the input 
-	state  $\ket{\psi_{AB}}$.
-	\item Alice measures the part $A$ of the input state  $\ket{\psi_{AB}}$ and receives an output label $i$.
+\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on systems 
+$A$ and $B$.
+\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or 
+$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
+\item Alice measures part $A$ of the input state  $\ket{\psi_{AB}}$ and 
+receives an output label $i$.
 \item  
-	From Holevo--Helstrom theorem, 
-	 Bob performs the conditional binary measurement $\PP_{V_j^\dagger}$ on the part 	$B$.
-	\item They include these cases for which $i = j$. Otherwise, they reject them.
-	\item
-	Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
-	makes a decision based on received label $j$.
-If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box.
-Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box.
+From Holevo--Helstrom theorem, Bob performs the conditional binary 
+measurement	$\PP_{V_j^\dagger}$ on part $B$.
+\item They include the cases for which $i = j$.\todo{?} Otherwise, they reject 
+them. 
+\item Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and makes a
+decision based on received label $j$. If $j=0$, then he decides that the the
+black box contains $\PP_U$. Otherwise, he decides that the black box contains
+$\PP_{\Id}$.
 \end{enumerate}
 
-The schematic representation of this setup we can see on Fig.~\ref{fig:postsellection}.
+The schematic representation of this setup is depicted in 
+Fig.~\ref{fig:postsellection}.
 
@@
 \begin{enumerate}
-			\item Alice and Bob prepare entanglement state $\ket{\psi_{AB}}$.
-%		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
-%		\rangle. $
-		\item Alice performs one of two quantum channels, $\Phi_{\Id}$ and $\Phi_{U}$,  on part $A$ of the input 
-		state  $\ket{\psi_{AB}}$.
-		\item Alice and Bob implement controlled unitary $V_0 \oplus V_1$ obtained from Holevo--Helstrom theorem.	
-		\item Alice and Bob prepare the measurement $\Delta$ in computational basis on theirs systems.
-		\item Bob	makes a decision based on received label $j$.
-If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box.
-Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box.
-
+\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on 
+systems $A$ and $B$..
+%\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
+%\rangle. $
+\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or
+$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
+\item Alice and Bob implement controlled unitary $V_0 \oplus V_1$ obtained from 
+Holevo--Helstrom theorem.	
+\item Alice and Bob prepare the measurement $\Delta$ in computational basis on 
+their systems.
+\item Bob makes a decision based on received label $j$. If $j=0$, then he
+decides that the the black box contains $\PP_U$. Otherwise, he decides that the
+black box contains $\PP_{\Id}$.
 \end{enumerate}
 
+The schematic representation of this setup is depicted in 
+Fig.~\ref{fig:controlled}.     
 \begin{figure}[h!]

### 2022-09-29 txt/manuscript.tex
Last part of section 2 rewritten.

@@
 Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
-the field $\mathbb{C}$. For  simplicity notation, square matrices will be 
-denoted by
+the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
 $M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
@@
 matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
-positive semidefinite operators having
-trace equal to one, will be denoted $\Omega_d$.  The subset of $M_d$ consisting of 
-unitary matrices will be denoted by
-$\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$.  We will also need a linear
-mapping transforming $M_{d_1}$ into $M_{d_2}$, which will be denoted \begin{equation}
+positive semidefinite operators having trace equal to one, will be denoted
+$\Omega_d$.  The subset of $M_d$ consisting of unitary matrices will be denoted
+by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
+$\DD \UU_d$.  We will also need a linear mapping transforming $M_{d_1}$ into
+$M_{d_2}$, which will be denoted 
+\begin{equation}
 \Phi: M_{d_1 } \rightarrow M_{d_2}.
@@
 \subsubsection{Diamond norm}
-This section defines a special norm on the space of linear mappings, known as the diamond norm,
-and establishes some of its properties. 
-Next, we will also explain the precise connection between the diamond
-norm and the task of quantum operations discrimination.
+This section defines a special norm on the space of linear mappings, known as 
+the diamond norm, and establishes some of its properties. 
+Next, we will explain the precise connection between the diamond
+norm and the task of quantum operation discrimination.
 
 Let us  consider a  linear mapping transforming  square matrices into square 
-matrices 
-that is $\Phi: M_{d_1} \to M_{d_2}$. 
+matrices that is $\Phi: M_{d_1} \to M_{d_2}$. 
 We define the diamond norm of a map $\Phi$ as 
@@
 
-In case then 
-we consider the discrimination setup between two von Neumann 
-measurements $\PP_U$ and $\PP_\Id$, $U\in \UU_d$ we obtain that (from Theorem 1 \cite{puchala2018strategies})
+In the case of discrimination between two von Neumann measurements $\PP_U$ and 
+$\PP_\Id$ we know that (from Theorem 1 \cite{puchala2018strategies})
 \begin{equation}
@@
 \end{equation}
-where $\Phi_U$ is unitary channel and 
-$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$.
+where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
+unitary matrices of dimension $d$.
 
@@
 In this section we present theoretical probability of correct 
-discrimination between these measurements. Moreover, we create the optimal theoretical strategy of their discriminate. 
+discrimination between these measurements. Moreover, we create the optimal 
+theoretical strategy of their discrimination. 
 Such a probability can be calculated using Holevo-Helstrom theorem and 
@@
 Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
-	$\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
+$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then 
 \begin{equation}
@@
 \end{equation}
-
 \end{lemma}

### 2022-09-29 txt/manuscript.tex
Many minor corrections in section 3.

@@
 	\begin{equation}
-	\forall E \in \diaguni_2 \,\, | \tr \left(\rho U E\right) | \le \nu. 
+	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \nu. 
 	\end{equation}
@@
 	\end{equation}
-	where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is 
+	where  for eigenvalue $\lambda_1 = e^{i \phi}$, the corresponding 
+	eigenvector is 
 	of the form $\ket{x_1} = 
@@
 	\end{equation}
-	Whereas, from Theorem 1 in \cite{puchala2018strategies}, we have 
+	From Theorem 1 in~\cite{puchala2018strategies} we have 
 	\begin{equation}
@@
 	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal} we show that 
+	From Lemma~\ref{lemma:min-e-optimal} we know that for our unitary matrix 
+	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
 	\begin{equation}
@@
 \begin{split}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond & =  \max_{\rho \in \Omega_2} \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1   \\ & =  \max_{\rho \in \Omega_2} \| \left( \Id \otimes \sqrt{\rho} \right) \sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  \|_1  \\ & = \max_{\rho \in \Omega_2} \| \sum_{i=0}^{1} \proj{i} \otimes \sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1  \\ & =
-	 \max_{\rho \in \Omega_2} \| \sum_{i=0}^{1}\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1
+\| \PP_{U} - \PP_{\Id}  \|_\diamond 
+& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
+J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
+\\ 
+& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
+\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
+\right\|_1  \\ 
+& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
+\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
+\\ 
+& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
+\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
 \end{split}
 \end{equation}
-	We can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, \ket{y}$ the following equation holds 
-	\begin{equation}
-	\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha \beta |\braket{x}{y}|^2}.
-	\end{equation}
-	By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} \ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} \ket{i} \|}$ we obtain 
-	\begin{equation}
-		\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} \sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i }\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
+One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
+\ket{y}$ the following equation holds~\cite{watrous} 
+\begin{equation}
+\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
+\beta |\braket{x}{y}|^2}.
+\end{equation}
+By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
+\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
+\ket{i} \|}$ we obtain 
+\begin{equation}
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
+	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
+	}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
 \end{equation}
 \todo[inline]{dokonczyc}
-	Let us take  $\rho_0 =   \frac{1}{2}  	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
+Let us take  $\rho_0 =   \frac{1}{2}  	
+\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
 \begin{equation}
 \begin{split}
-	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=0}^1  
+||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
+&= \sum_{i=0}^1  
 \sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
-		4|\bra{i}\rho_0\ket{u_i}|^2} = \\& 
-	\sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} = \\ & 
-	 \sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} \ket{i} + 
-			e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} =\\&  \sum_{i=0}^1  \sqrt{ 
-		\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + 
-			e^{i \phi}}{2}\right|^2} = \\&  \sum_{i=0}^1\braket{i}{i} \sqrt{1 
-		-\left| \frac{1+ e^{i \phi}}{2}\right|^2 } = 
-	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } = \frac{|1-e^{i \phi }|}{2}. 
+4|\bra{i}\rho_0\ket{u_i}|^2}  \\
+&= \sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} 
+\\ 
+&=\sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} 
+\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
+&= \sum_{i=0}^1  \sqrt{
+\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + e^{i \phi}}{2}\right|^2}  \\
+&= \sum_{i=0}^1\braket{i}{i} \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
+= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
+&= \frac{|1-e^{i \phi }|}{2}.
 \end{split}
@@
 Due to that, we know  
-	that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem of discrimination between 
+that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem 
+of discrimination between 
 $\PP_{\Id} $ and $\PP_U$, where 
-	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm ).
-
-	\begin{equation}
-		\| \PP_{U} - \PP_{\Id}  \|_\diamond  =  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1  
-=  \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top \rangle  \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
+$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
+).
+
+\begin{equation}
+\begin{split}
+\| \PP_{U} - \PP_{\Id}  \|_\diamond  
+&=  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( 
+\Id \otimes \sqrt{\rho} \right) \|_1 \\
+&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
+\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
+\end{split}
 \end{equation}
 So we obtain that \begin{equation}
-	\ket{\psi_{AB}} =   | \sqrt{\rho}^\top \rangle  \rangle = \frac{1}{\sqrt{2} } | \Id_2 \rangle \rangle, 
+\ket{\psi_{AB}} =   | \sqrt{\rho}^\top \rangle  \rangle = \frac{1}{\sqrt{2} } | 
+\Id_2 \rangle \rangle, 
 \end{equation}
@@
 From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
-Let us define \begin{equation}
+Let us define 
+\begin{equation}
 X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
 \otimes \Id_2 \right)(\proj{\psi}).
-\end{equation} From 
-We consider the Hahn-Jordan decomposition, let \begin{equation}
+\end{equation} 
+We consider the Hahn-Jordan decomposition. Let 
+\begin{equation}
 X = P - Q
@@
 \begin{equation}
-\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right) 
+\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
 \end{equation}
@@
 V_1 \ket{y_q} = \ket{1}
-\end{cases} 
-\end{equation}
-For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H \diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given by following (see also \texttt{one-qubit.nb}).
-The unitary $V_0$ 
-has the following form
-\begin{equation}
-V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
+\end{cases}. 
+\end{equation}
+For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
+\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
+follows (see also \texttt{one-qubit.nb}).
+The unitary $V_0$ has the form
+\begin{equation}
+V_0 = \left(
+\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
 \cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
-	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
+\end{array}
+\right),
 \end{equation}
@@
 \sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
-\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right)
 \end{equation}
@@
 \mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{1} V_1^\dagger  
+\proj{1} V_1^\dagger.  
 \end{split}

### 2022-10-01 txt/manuscript.tex
preli

@@
 The scenario assumes that Alice and Bob have access to an unknown measurement
-device, a black box. Alice has hidden one of the two measurements, either $\SS$
-or $\TT$, in the black box. Bob only has the information that the black box
-performs one of these measurements. They want to know the upper bound on the
-probability of correct discrimination between $\SS$ and $\TT$. They also want to
-construct the optimal discrimination strategy to achieve the highest probability
-of correct discrimination. Theoretical results on discrimination of von Neumann
-measurements are characterized in~\cite{puchala2018strategies}.
-
-In this work we will consider the problem of discrimination between von Neumann 
-measurement in the computational basis and a von Neumann measurement in basis 
+device, a black box. Alice has hidden one of the two measurements, either $\PP$
+or $\mathcal{Q}$, in the black box. Bob only has the information that the black box
+performs one of these measurements. They want to determine an upper bound on the
+probability of correct discrimination between $\PP$ and $\mathcal{Q}$. Moreover, they also want to
+construct an optimal discrimination strategy to achieve the highest probability. Theoretical results were characterized in~\cite{puchala2018strategies}.
+
+In this work, we will consider the problem of discrimination between von Neumann 
+measurements. One of them on the computational basis, the second one on basis 
 $U$, where $U$ is a unitary matrix. 
@@
 illustrated in Fig.~\ref{fig:theoretical_scheme}.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1.7]{pics/theoretical_scheme}
+	\caption{Theoretical  scheme of discrimination  between von Neumann measurements $\PP_{U}$ and $\PP_\Id$. }
+	\label{fig:theoretical_scheme}
+\end{figure}
 
@@
 	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
-	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$.
-	\item Alice performs the conditional binary measurement on the part 
+	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$ and measures the system $A$.
+	\item Alice performs the conditional binary measurement $\PP_{V_i}$ on the part 
 	$B$ based on the output label $i$. 
-	\item  Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and 
+	\item  Bob measures the system $B$ of the input state  $\ket{\psi_{AB}}$ and 
 	makes a decision based on the received label $j$. If $j=0$, then he decides 
@@
 
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.7]{pics/theoretical_scheme}
-	\caption{Theoretical discrimination scheme}
-	\label{fig:theoretical_scheme}
-\end{figure}
-
 \subsubsection{Quantum architecture's limits and practical solutions}
@@
 measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of 
-this scheme is to perform the conditional binary measurement. 
+this scheme is to perform a conditional binary measurement. 
 Unfortunately, current NISQ devices do not allow for performing conditional 
@@
 obstacle. These will be two schemes of practical realization. 
-The first method consists in using post-selection while the second method 
+The first method consists in using postselection while the second method 
 consists in applying a controlled unitary. These methods are described below.
 
-\begin{scheme}(By using postsellection)
+\begin{scheme}(Postselection)
 
@@
 \item  
-From Holevo--Helstrom theorem, Bob performs the conditional binary 
+Based on Holevo--Helstrom theorem, Bob performs a conditional binary 
 measurement	$\PP_{V_j^\dagger}$ on part $B$.
-\item They include the cases for which $i = j$.\todo{?} Otherwise, they reject 
-them. 
+\item To calculate the probability of correct discrimination, they include just those cases for which $i = j$.
 \item Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and makes a
-decision based on received label $j$. If $j=0$, then he decides that the the
+decision based on received label $j$. If $i=j=0$, then he decides that the 
 black box contains $\PP_U$. Otherwise, he decides that the black box contains
@@
 
-PROBABILITY 
-		\begin{equation}
-		p = ...
-		\end{equation}
-		%\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
+Due to the fact that the measurement result is nondeterministic, we are forced to consider the following circuits
+in the postselection procedure
+\begin{equation}
+\begin{split}
+(\Phi_{U}, \mathcal{P}_{V_k}, i, j) \\ 
+(\Phi_{\Id}, \mathcal{P}_{V_k}, i, j)
+\end{split}
+\end{equation}
+where $k=\{0,1\}, i=\{0,1\}$ and $ j=\{0,1\}$. 
+The optimal probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows.
+		\begin{equation}
+		p = \frac{\#(\Phi_U, \PP_{V_i},i,0) + \#(\Phi_\Id, \PP_{V_i},i,1)}{\#(\Phi_U, \PP_{V_i},i,j) + \#(\Phi_\Id, \PP_{V_i},i,j)}, 
+		\end{equation}
+where $i=\{0,1\}$ and $ j=\{0,1\}$.
 
@@
 \item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on 
-systems $A$ and $B$..
-%\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
-%\rangle. $
+systems $A$ and $B$.
 \item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or
@@
 
-PROBABILITY
-
-\begin{equation}
-p = \frac{|j=0 \wedge \Phi_{U} | + |j=1 \wedge \Phi_{\1}|}{\text{all 
-		cases}}
-\end{equation}
-
+Here, we consider the following circuits
+by using controlled unitary
+\begin{equation}
+\begin{split}
+(\Phi_{U}, V_0 \oplus V_1, i, j) \\ 
+(\Phi_{\Id},  V_0 \oplus V_1, i, j)
+\end{split}
+\end{equation}
+where $i=\{0,1\}$ and $ j=\{0,1\}$. 
+Then, the optimal probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows.
+\begin{equation}
+p = \frac{\#(\Phi_U,V_0 \oplus V_1,i,0) + \#(\Phi_\Id,V_0 \oplus V_1,i,1) }{\#(\Phi_U,V_0 \oplus V_1,i,j) + \#(\Phi_\Id,V_0 \oplus V_1,i,j)}
+\end{equation}
+where $i=\{0,1\}$ and $ j=\{0,1\}$. 
 \end{scheme}
@@
 and trace preserving (CPTP).
-A unitary channel
+In this work we will consider a special class of quantum channels, called unitary channels. A unitary channel
 $\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
@@
 \PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-$ It is worth noting that a given  von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta 
-\circ \Phi_{(UE)^\dagger}$, where $\Delta$ denotes the completely dephasing 
-channel.
+$
 

### 2022-10-02 txt/manuscript.tex
realization for fourier case

@@
 \usepackage{todonotes} 
+\usepackage{url}
 
@@
 positive semidefinite operators having trace equal to one, will be denoted
-$\Omega_d$.  The subset of $M_d$ consisting of unitary matrices will be denoted
+$\Omega_d$. 
+ The subset of $M_d$ consisting of unitary matrices will be denoted
 by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
@@
 Jamio{\l}kowski isomorphism. 
-
+For a given linear mapping $\Phi_M$ corresponding  Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
+\begin{equation}
+\mathcal{J}(\Phi) \coloneqq \sum_{i,j=1}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
 Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
 and trace preserving (CPTP).
-In this work we will consider a special class of quantum channels, called unitary channels. A unitary channel
+In this work we will consider a special class of quantum channels, called unitary channels. Let $U \in \UU_d$ be a unitary operator. A unitary channel
 $\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
@@
 
-\subsubsection{Diamond norm}
+\subsubsection{Diamond norm and the task of discrimination between quantum operators}
 This section defines a special norm on the space of linear mappings, known as 
@@
 
-\begin{equation}
-\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}_\Phi  \left( \Id \otimes \sqrt{\rho} \right)  \|_1  \end{equation}
-
-\subsubsection{Discrimination of a quantum operations}
-
 The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
@@
 \begin{equation}
-p_{succ} =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
-\end{equation}
-
+p_{\text{succ}}(\TT, \SS) =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
+\end{equation}
 In the case of discrimination between two von Neumann measurements $\PP_U$ and 
@@
 Before we proceed to presenting our main results, we need to briefly discuss the
-problem of discrimination of unitary channels.  In order to formulate the condition for perfect
-discrimination of unitary channels we introduce the notion of numerical range of
-a matrix $A \in M_d$, denoted by $W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
+problem of discrimination of unitary channels.  For this purpose, we introduce the notion of numerical range of
+a given matrix $A \in M_d$. The set \begin{equation}
+W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
 \mathbb{C}^d, \;
-\;\braket{x}{x}=1\}$. The celebrated Hausdorf-T\"oplitz
-theorem states that
-$W(A)$ is a convex set and therefore $W(A) =\{\tr A \sigma : \sigma \in \Omega_d
-\}$. Let us now recall the well-known result for the
+\;\braket{x}{x}=1\}.
+\end{equation}   
+is the numerical range of $A$.
+The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.
+
+ Let us now recall the well-known result for the
 distinguishability of unitary channels.
-	Let $U \in \UU_d$ and $\Phi_U: \rho \mapsto U \rho U^\dagger$ be a unitary 
+	Let $U \in \UU_d$ and $\Phi_U$ be a unitary 
 	channel. 
-	Then 
+	Then, the following equation holds
 	\begin{equation}
@@
 	\end{equation}
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $.
-
-%\begin{proposition}
- Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
- $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
-	\begin{equation}
-	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-	\Phi_\Id\|_\diamond
-	\end{equation}
-%\end{proposition}
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. And hence the optimal probability to discriminate two unitary channel is given by 
+	\begin{equation}
+	p_{\text{succ}}(\Phi_U, \Phi_\Id) = \frac{1}{2} + \frac{1}{2} \sqrt{1-\nu^2}.
+	\end{equation}
 
@@
 
-\section{Illustrative Examples}
+\section{Illustrative Example}
 
@@
 \begin{equation}
-U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
-\end{equation}
+U = H 
+\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
+\end{equation}
+%\begin{equation}
+%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
+%\end{equation}
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
@@
 theoretical strategy of their discrimination. 
-Such a probability can be calculated using Holevo-Helstrom theorem and 
-Theorem 1 from~\cite{puchala2018strategies}. 
-This probability will be calculated in 
+The otimal probability will be calculated in 
 subsection~\ref{sec:example_theoretical_probability}. Later, we will 
@@
 \subsection{Theoretical probability}\label{sec:example_theoretical_probability}
+
 In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.
@@
 Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
-$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then 
+$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds 
 \begin{equation}
@@
 \end{lemma}
+\todo[inline]{spr dowod}
 \begin{proof} Recall that the distance between two unitary channels is given by
@@
 \end{theorem}
+\todo[inline]{spr dowod}
 \begin{proof}
@@
 \begin{proof}
-
+For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
+\begin{equation}
+\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
+Then, we have
 \begin{equation}
@@
 So we obtain that \begin{equation}
-\ket{\psi_{AB}} =   | \sqrt{\rho}^\top \rangle  \rangle = \frac{1}{\sqrt{2} } | 
+\ket{\psi_{AB}} \coloneqq  | \sqrt{\rho}^\top \rangle  \rangle 
+\end{equation}
+and hence we have 
+\begin{equation}
+\ket{\psi_{AB}}= \frac{1}{\sqrt{2} } | 
 \Id_2 \rangle \rangle, 
@@
 
-\subsubsection{Final measurement}\label{sec_example_final_measurement}
-In this subsection we will derive exact form of the final measurement in the
+\subsubsection{Conditional measurement}\label{sec_example_final_measurement}
+In this subsection we will derive exact form of the conditional measurement in the
 problem of discrimination of von Neumann measurements $\PP_U$ and $\PP_{\Id}$
@@
 	2\pi)$.  
-The  final measurement has the form
+The  conditioned measurement has the form
 \begin{equation}
@@
 \begin{proof}
+	\todo[inline]{spr dowod}
 From Proposition~\ref{prop-discrim} we have the form of discriminator given by
@@
 \todo[inline]{TU WYNIKI PRAKTYTCZNE }
-\todo[inline]{tu rozklad i obwody}
+
+\subsection{Native case}
+
+\subsection{IBMQ}
+
+\subsection{Lucy}
+
+\subsection{Rigetti}
 
@@
 number POIR.04.04.00-00-17C1/18-00.
-
- \section{}
- \label{}
-
- References:
- If you have bibdatabase file and want bibtex to generate the
- bibitems, please use
-
-  \bibliographystyle{elsarticle-num} 
-  \bibliography{<your bibdatabase>}
-
- else use the following coding to input the bibitems directly in the
- TeX file.
-
- \bibliographystyle{ieeetr}
- \bibliography{rigetti}
 
@@
 98.4 (2018): 042103.
+\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
+\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
+\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02. 
 \end{thebibliography}

### 2022-10-02 txt/manuscript.tex
prproofs done and checked

@@
 by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$.  We will also need a linear mapping transforming $M_{d_1}$ into
+$\DD \UU_d$. 
+	An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$.
+Whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
+
+ We will also need a linear mapping transforming $M_{d_1}$ into
 $M_{d_2}$, which will be denoted 
@@
 \end{lemma}
-\todo[inline]{spr dowod}
+
 \begin{proof} Recall that the distance between two unitary channels is given by
@@
 	For $U = H 
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
 	\begin{equation}
@@
 	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{E} \coloneqq \nu = \frac{|1 + e^{i \phi} | }{2},
+	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
 	\end{equation}
 	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
-	We can prove that
+
+%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
+ The celebrated Hausdorf-T{\o}plitz theorem~\cite{hausdorff, toeplitz} states that
+$W(A)$ of any matrix $A \in M_d$ is a convex set and therefore
+\begin{equation}
+W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}. 
+\end{equation}
+So we obtain that 
 	\begin{equation}
@@
 	\end{equation}
-	So we obtain \begin{equation}
+	And then we have 
+	 \begin{equation}
  \max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
@@
 	\begin{equation}
-	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \nu. 
-	\end{equation}
+	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \mu
+	\end{equation}
+	where $\mu \coloneqq \max_{E \in \diaguni_2 } \nu_{E}.$
+
 	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ 
-	and let us take $\rho = 
+	and take $\rho = 
 	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
@@
 	\end{equation}
-	where  for eigenvalue $\lambda_1 = e^{i \phi}$, the corresponding 
+	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
 	eigenvector is 
-	of the form $\ket{x_1} = 
-	\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
-	whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
-	\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
+	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	$,
+	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
+	$.
 	Then, we have 
@@
 	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
-	\frac{1}{2} \left| \tr\left((  e^{i \phi} \proj{x_1} + 1 \proj{x_2} ) E \right) 
+	\frac{1}{2} \left| \tr\left((   \proj{x_1} +e^{i \phi}\proj{x_2} ) E \right) 
 	\right|  = 
-	\frac{1}{2} \left| e^{i \phi}  \bra{x_1} E \ket{x_1} + \bra{x_2} E \ket{x_2} 
+	\frac{1}{2} \left|  \bra{x_1} E \ket{x_1} +  e^{i \phi}\bra{x_2} E \ket{x_2} 
 	\right| = \\& 
@@
 	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
-	\nu, 
+	\mu, 
 	\end{split}
@@
 \begin{equation}
-p = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
+p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
 \end{equation}
 \end{theorem}
-\todo[inline]{spr dowod}
+
 \begin{proof}
@@
 	\begin{equation}
-	p = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
+p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
 	\end{equation}
@@
 	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal} we know that for our unitary matrix 
+	From Lemma~\ref{lemma:min-e-optimal} we know that for 
 	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
@@
 	\end{equation}
-	Finally, we obtain that
-	\begin{equation}
-	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
-	\end{equation}
+%	Finally, we obtain that
+%	\begin{equation}
+%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
+%	\end{equation}
 	It implies that
 	\begin{equation}
-	p  = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
 	\end{equation} which completes the proof.
@@
 
-%
-%
-%\begin{theorem}\label{rozrpomiarow}
-%Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = 
-%H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
-%\not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the 
-%form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
-%	\begin{enumerate}
-%		\item $\rho_1,\rho_2 \in \Omega_2$
-%		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
-%		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
-%		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
-%	\end{enumerate}
-%	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
-%	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of 
-%	$U$. Then  we have 
-%	\begin{equation}
-%	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i 
-%	\phi}}{2}\right|^2}.
-%	\end{equation}
-%	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą 
-%	%wartością własną $U\in \mathrm{U}(\XX)$.
-%\end{theorem}
-%\begin{proof} From \ref{th:minE} we have 
-%	\begin{equation}
-%	\begin{split}
-%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} 
-%	||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in 
-%	\diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) 
-%	||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || 
-%	\Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| 
-%	\Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
-%	\end{split}
-%	\end{equation}
-%The diamond norm between two unitary channels can be calculated by 
-%	\begin{equation}
-%	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = 
-%	\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho 
-%	)|^2}.
-%	\end{equation}
-%Hence,  it is enough to calculate the formula
-%\begin{equation}
-%\begin{split}
-%\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
-%\end{split}
-%\end{equation}
-%Recall, let us note $U$ as
-%\begin{equation}
-%U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
-%\end{equation}
-%where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is of 
-%the form $\ket{x_1} = 
-%\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
-% whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
-%\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.
-% 
-%Consider two cases:
-%
-%	$1^\circ$ Consider $\phi = \pi$. Then $U$ is of the form
-%	\begin{equation}
-%	U = \left(\begin{array}{cc}0&1\\1&0\end{array}\right).
-%	\end{equation}
-%Then $0 \in W(U)$. 	From Proposition 3 in ~\cite{puchala2018strategies} the 
-%measurements $\mathcal{P}_U, \mathcal{P}_\1$ are perfectly distinguishable if 
-%and only if there exists $\rho \in \Omega_2$ such that
-%	\begin{equation}
-%	\mathrm{diag}\left(U^\dagger \rho\right) = 0.
-%	\end{equation}
-%Hence, for $U $ we have 
-%	\begin{equation}
-%	0 = \mathrm{diag}\left(U^\dagger \rho\right) = \mathrm{diag} 
-%	\left(\left(\begin{array}{cc}0&1\\1&0\end{array}\right)\left(\begin{array}{cc}\rho_{1,1}&\rho_{1,2}\\\rho_{2,1}&\rho_{2,2}\end{array}\right)\right)
-%	 =  \mathrm{diag} 
-%	\left(\begin{array}{cc}\rho_{2,1}&\rho_{2,2}\\\rho_{1,1}&\rho_{1,2}\end{array}\right).
-%	\end{equation}
-% It implies that $\rho_{2,1}=\rho_{1,2} = 0$. Therefore $\rho \in \Omega_2$ for 
-% which $\mathcal{P}_U, \mathcal{P}_\1$  are perfectly distinguishable is of the 
-% form
-%	\begin{equation}
-%	\rho = \left(\begin{array}{cc}\rho_{1,1}&0\\0&\rho_{2,2}\end{array}\right),
-%	\end{equation}
-%	where $\rho_{1,1},\rho_{2,2} \ge 0$ and  $\rho_{1,1}+\rho_{2,2}=1$.
-%
-%	$2^\circ$ Consider  $\phi \not = \pi$. 
-%The spectrum of $U$ is of the form $\sigma(U) = \{e^{i \phi},1\}$. 
-%Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
-%	\begin{equation}
-%	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
-%	\end{equation}
-%Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = 
-%\ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 
-%\in \Omega_2$ and satisfies the requirements of theorem. Hence, the 
-%discriminator $\rho \in \Omega_2$ has the form 
-%	\begin{equation}
-%	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = 
-%	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
-%	\end{equation}
-%%and 
-%%	\begin{equation}
-%%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 
-%%+ e^{\mathbf{i} \phi}}{2}\right|^2 },
-%%	\end{equation}
-%
-%	
-%%	
-%%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} 
-%%\rho_2$ we have 
-%%	\begin{equation}
-%%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 
-%%\right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = 
-%%\frac{\lambda_1+\lambda_2}{2}. 
-%%	\end{equation}
-%%	Therefore, we have
-%%	\begin{equation}
-%%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- 
-%%\left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
-%%	\end{equation}
-%%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 
-%%e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. 
-%%Then we have 
-%%	\begin{equation}
-%%	\begin{split}
-%%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E 
-%%\right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = 
-%%\frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} 
-%%\lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} 
-%%\left(\lambda_1 
-%%+ \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
-%%	\end{split}
-%%	\end{equation} 
-%%So we have 
-%%	\begin{equation}
-%%	\left|\tr\left(UE \rho \right) \right| = 
-%%\left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 
-%%\bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} 
-%%\right|.
-%%	\end{equation}
-%%	It implies that
-%%	\begin{equation}
-%%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  
-%%|\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
-%%	\end{equation}
-%%	Hence we obtain
-%%	\begin{equation}
-%%	\begin{split}
-%%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} 
-%%\sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} 
-%%\right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 
-%%-\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
-%%	\end{split}
-%%	\end{equation
 \begin{proof}
+Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0, 
+2\pi)$ be decomposed as 
+	\begin{equation}
+	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
+	\end{equation}
+	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
+	eigenvector is 
+	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	$,
+	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
+	$.
+
 For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
@@
 \| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
-Then, we have
+Hence, we obtain
 \begin{equation}
@@
 & =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
-J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
+\mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
 \\ 
@@
 \ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
-\ket{i} \|}$ we obtain 
+\ket{i} \|}$ we have
 \begin{equation}
@@
 \end{equation}
-\todo[inline]{dokonczyc}
 Let us take  $\rho_0 =   \frac{1}{2}  	
@@
 	4|\bra{i}\rho_0\ket{u_i}|^2}  \\
-&= \sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} 
+&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2} 
 \\ 
-&=\sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} 
+&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1} 
 	\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
-&= \sum_{i=0}^1  \sqrt{
-\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + e^{i \phi}}{2}\right|^2}  \\
-&= \sum_{i=0}^1\braket{i}{i} \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
+&= \sum_{i=0}^1 
+ \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
 = 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
-&= \frac{|1-e^{i \phi }|}{2}.
+&= |1-e^{i \phi }|.
 \end{split}
 \end{equation}
-Due to that, we know  
-that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem 
-of discrimination between 
-$\PP_{\Id} $ and $\PP_U$, where 
-$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
-).
-
+Observe that
 \begin{equation}
@@
 \| \PP_{U} - \PP_{\Id}  \|_\diamond  
-&=  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( 
+&=  \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
 \Id \otimes \sqrt{\rho} \right) \|_1 \\
@@
 \end{equation}
-So we obtain that \begin{equation}
-\ket{\psi_{AB}} \coloneqq  | \sqrt{\rho}^\top \rangle  \rangle 
-\end{equation}
-and hence we have 
-\begin{equation}
-\ket{\psi_{AB}}= \frac{1}{\sqrt{2} } | 
+Due to that, we know  
+that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ is the discriminator of the problem 
+of discrimination between 
+$\PP_{\Id} $ and $\PP_U$ for 
+$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
+).      Hence we obtain that \begin{equation}
+\ket{\psi_{AB}} \coloneqq   | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
 \Id_2 \rangle \rangle,
@@
 \begin{proof}
-	\todo[inline]{spr dowod}
 From Proposition~\ref{prop-discrim} we have the form of discriminator given by
@@
 \end{equation}
-From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
+From Holevo-Helstrom theorem  we constrain a conditional measurement $\mu$.  
 Let us define 
@@
 \end{equation} 
-We consider the Hahn-Jordan decomposition. Let 
+From the Hahn-Jordan decomposition, let us note
 \begin{equation}
@@
 \end{equation}
-where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
-So, let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
-respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
+where $P, Q \ge 0 $. 
+Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
+respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
 \begin{equation}
@@
 discrimination between these measurements and the realization on real devices.
-\todo[inline]{TU WYNIKI PRAKTYTCZNE }
+\todo[inline]{TU WYNIKI PRAKTYCZNE }
 
@@
 \subsection{Sample code snippets analysis (optional)}
-\todo[inline]{moze tu kod tej postselekcji  i kontrolowanej unitarki ? }
+\todo[inline]{moze tu fragmenty kodu ? }
 \label{}
@@
 \bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02. 
+\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
+\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
 \end{thebibliography}
+
 \todo[inline]{Please add the reference to the software repository if DOI for 

### 2022-10-05 txt/manuscript.tex
circuit drawings
Add pictures of circuits in Section 4.

@@
 
-\subsection{Native case}
+\subsection{Generic case}
+Now we present the circuits for the generic case.
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-None}
+\caption{Circuit representing state preparation in the  generic case.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-None}
+\caption{Circuit representing $U^\dagger$ in the generic case.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-None}
+\caption{Circuit representing $V_0^\dagger$ in the generic case.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
+\caption{Circuit representing controlled $V_0$ and $V_1$ the generic case.}
+\end{figure}
+
+\subsection{IBMQ and Lucy}
 
@@
 
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-ibmq}
+\caption{Circuit representing state preparation for IBMQ.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-ibmq}
+\caption{Circuit representing $U^\dagger$ for IBMQ.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-ibmq}
+\caption{Circuit representing $V_0^\dagger$ for IBMQ.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
+\caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
+\end{figure}
+
 \subsection{Lucy}
 
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-lucy}
+\caption{Circuit representing state preparation for Lucy.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-lucy}
+\caption{Circuit representing $U^\dagger$ for Lucy.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-lucy}
+\caption{Circuit representing $V_0^\dagger$ for Lucy.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
+\caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
+\end{figure}
+
 \subsection{Rigetti}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-rigetti}
+\caption{Circuit representing state preparation for Rigetti.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-rigetti}
+\caption{Circuit representing $U^\dagger$ for Rigetti.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-rigetti}
+\caption{Circuit representing $V_0^\dagger$ for Rigetti.}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
+\caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}
+\end{figure}
 

### 2022-10-06 txt/manuscript.tex
native gates adding

@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-None}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-None}
 \caption{Circuit representing state preparation in the  generic case.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-None}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-None}
 \caption{Circuit representing $U^\dagger$ in the generic case.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-None}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-None}
 \caption{Circuit representing $V_0^\dagger$ in the generic case.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
 \caption{Circuit representing controlled $V_0$ and $V_1$ the generic case.}
@@
 \subsection{IBMQ}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-ibmq}
+ basis gates = ["cx", "i", "rz", "sx", "x"]
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-ibmq}
 \caption{Circuit representing state preparation for IBMQ.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-ibmq}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-ibmq}
 \caption{Circuit representing $U^\dagger$ for IBMQ.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-ibmq}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-ibmq}
 \caption{Circuit representing $V_0^\dagger$ for IBMQ.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
 \caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
@@
 \subsection{Lucy}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-lucy}
+ basis gates  =["ecr", "i", "rz", "sx", "x"] 
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-lucy}
 \caption{Circuit representing state preparation for Lucy.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-lucy}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-lucy}
 \caption{Circuit representing $U^\dagger$ for Lucy.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-lucy}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-lucy}
 \caption{Circuit representing $V_0^\dagger$ for Lucy.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
 \caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
@@
 \subsection{Rigetti}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-rigetti}
+ basis gates = ["cz", "rx", "rz"]
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-rigetti}
 \caption{Circuit representing state preparation for Rigetti.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-rigetti}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-rigetti}
 \caption{Circuit representing $U^\dagger$ for Rigetti.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-rigetti}
+\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-rigetti}
 \caption{Circuit representing $V_0^\dagger$ for Rigetti.}
@@
 \centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
+\includegraphics[scale=0.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
 \caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}

### 2022-11-07 txt/manuscript.tex
changing drawings
add mathematical foundations

@@
 
-\todo[inline]{wyzej mamy bez daggera, trzeba to ustalic} 
 %\begin{figure}[h!]
@@
 In the case of discrimination between two von Neumann measurements $\PP_U$ and 
-$\PP_\Id$ we know that (from Theorem 1 \cite{puchala2018strategies})
+$\PP_\Id$ we know that (from Theorem 1 in \cite{puchala2018strategies})
 \begin{equation}

### 2022-11-07 txt/maths.tex
add mathematical foundations

--- 2022-10-05 txt/manuscript.tex
@@
 
-\begin{frontmatter}
+\subsubsection{Model specification}
+The scenario of measurements discrimination assumes that we have access to an unknown measurement
+device. One of the two measurements, either $\PP$
+or $\mathcal{Q}$,  was used during an experiment. The only information we have that one of these measurements was 
+performed. We want to determine an upper bound on the
+probability of correct discrimination between $\PP$ and $\mathcal{Q}$. Moreover, we also want to
+construct an optimal discrimination strategy to achieve the highest possible probability.
 
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Benchmarking on Rigetti architecture}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author{Paulina Lewandowska}
-\author{\L ukasz Pawela}
-
-\address{Institute of Theoretical and Applied Informatics, Polish Academy
-	of Sciences, Ba{\l}tycka 5, 44-100 Gliwice, Poland}
-
-\begin{abstract}
-We introduce library ?, a comprehensive open source framework for benchmarking 
-Amazon Braket Rigetti IonQ architectures ? 
-The framework is built around  the scheme of discrimination of von Neumann 
-measurements. The library provides algorithm for ... Our main aim is creating a 
-common platform  for open research.  ?
-
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-Benchmarking of Rigetti architecture \sep Discrimination of quantum 
-measurements \sep Von Neumann measurements discrimination
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-\section*{Required Metadata}
-\label{}
-
-\section*{Current code version}
-\label{}
-
-Ancillary data table required for subversion of the codebase. Kindly replace 
-examples in right column with the correct information about your current code, 
-and leave the left column as it is.
-
-\begin{table}[H]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-\hline
-\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this 
-column} \\
-\hline
-C1 & Current code version & For example v42 \\
-\hline
-C2 & Permanent link to code/repository used for this code version & For 
-example: $https://github.com/mozart/mozart2$ \\
-\hline
-C3 & Code Ocean compute capsule & For example: 
-$https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
-\hline
-C4 & Legal Code License   & List one of the approved licenses \\
-\hline
-C5 & Code versioning system used & For example svn, git, mercurial, etc. put 
-none if none \\
-\hline
-C6 & Software code languages, tools, and services used & For example C++, 
-python, r, MPI, OpenCL, etc. \\
-\hline
-C7 & Compilation requirements, operating environments \& dependencies & \\
-\hline
-C8 & If available Link to developer documentation/manual & For example: 
-$http://mozart.github.io/documentation/$ \\
-\hline
-C9 & Support email for questions & \\
-\hline
-\end{tabular}
-\caption{Code metadata (mandatory)}
-\label{} 
-\end{table}
-
-\linenumbers
-
-%% main text
-
-The permanent link to code/repository or the zip archive should include the 
-following requirements:
-
-README.txt and LICENSE.txt.
-
-Source code in a src/ directory, not the root of the repository.
-
-Tag corresponding with the version of the software that is reviewed.
-
-Documentation in the repository in a docs/ directory, and/or READMEs, as 
-appropriate.
-
-\section{Motivation and significance}
-
-Noisy intermediate-scale quantum
-(NISQ)~\cite{preskill} devices are currently storming the market. We
-have a selection of readily available quantum computers based on different
-architectures. Historically, the first widely introduced quantum computing
-architecture is D-Wave's quantum annealer~\cite{}.
-
-https://quantumcomputingreport.com/scorecards/qubit-technology/
-
-Additional approaches to quantum computing are currently in development. For 
-instance we have Ionq's computer based on ion traps and Xanadu's optical 
-lattices. As they are in prototype versions no access to general public is 
-provided.
-
-Next, we have computers implementing the gate model of quantum computation.
-These are the best potentially developed machines, which can be thought
-of as fully quantum computers, by which we understand that the qubits can be in
-an entangled state.
-
-Currently one of the main providers of such architectures is Rigetti and its 
-Quantum Cloud Services platform. The company has
-released three generations of QPUs so far: Rigetti 8Q Agave, Rigetti 19Q Acorn
-and Rigetti 16Q Aspen-1. The most recent one was deployed in November 2018 and
-is a downgrade in terms of number of qubits compared to the previous 19 qubit
-one. However, the new chip is reportedly much more robust to noise and the
-proposed architecture is much easier to scale up. The new unit is supposed to
-serve as a building block for a 128 qubit
-system~\footnote{https://medium.com/rigetti/the-rigetti-128-qubit-chip-and-what-it-means-for-quantum-df757d1b71ea}.
-As was the case for IBM, Rigetti also provides a \texttt{Python} library, 
-\texttt{pyquil}~\cite{}, which enables easy access to the machine.
-
-\todo[inline]{co napisac o tym Amazonie, czy nic ?}
-
-\todo[inline]{rysunki architektur}
-
-%
-%\begin{figure}[h]
-%	\centering 
-%	
-%	\includegraphics[width=0.9\linewidth]{aspen.png} 
-%	\caption{?}
-%	\label{fig:aspen}
-%\end{figure}
-
-Now the natural question arises: how to construct a good metric of the
-computational power of such devices? 
-Lately, there have emerged propositions from the scientific community on how to
-benchmark such devices.
-
- First let us mention the work by Michielsen
-\emph{et.al.}~\cite{michielsen2017benchmarking}. In there the authors study the
-IBM-QE device. Their first test is the creation of the entangled state
-$\frac{1}{\sqrt{2}} (\ket{01} - \ket{10})$. Next they implement a
-two-qubit+two-qubit adder. Another test is an identity operation, realized by an
-even number of CNOT operations. Their final test is a quantum error correction
-scheme (is it possible with measurement-controlled-operations?). The final
-conclusion is that, except for simple circuits, the device fails to return
-correct results.
-
-Another, recent approach is utilizing quantum communication protocols in testing
-of quantum architectures~\cite{zhukov2019quantum}. Here, the authors decide to
-utilize superdense coding and the BB84 quantum cryptography protocol as
-benchmarks for the IBM Q devices. They utilize the mutual information of the
-transferred bits as a figure of merit for the quantum computer.
-
-Other approaches focus on generative model training. One of these
-works~\cite{hamilton2018generative} is aimed at small architectures, up to 5
-qubits. Another recently presented is much more
-robust~\cite{benedetti2018generative}. The main drawback of both of them is the
-level of complication.
-
-The goal of this work is to introduce a new benchmark for Rigetti 
-architecture...
-
-\label{}
-\todo[inline]{
-	Introduce the scientific background and the motivation for developing the 
-	software. - motywacje
-
-	Explain why the software is important, and describe the exact (scientific) 
-	problem(s) it solves. - czemu ejst wazne, jakie problemy rozwiazuje
-
-	Indicate in what way the software has contributed (or how it will 
-	contribute in the future) to the process of scientific discovery; if 
-	available, this is to be supported by citing a research paper using the 
-	software. - do czego sie to przyczyni w przyszlosci
-
-	Provide a description of the experimental setting (how does the user use 
-	the software?). - w jaki sposób użytkownik korzysta z oprogramowania?
-
-	Introduce related work in literature (cite or list algorithms used, other 
-	software etc.). - inne oprogramowania i algorytmy }
-
-\section{Software description}
-\label{}
-\todo[inline]{Describe the software in as much as is necessary to establish a 
-vocabulary needed to explain its impact. }
-
-We will first give a general overview of the structure of the code in 
-Section~\ref{sec:sortware-architecture} and then provide additional details on 
-the functionality of benchmark's schemes  in 
-Section~\ref{sec:sortware-functionalities}.
-
-\subsection{Software Architecture}\label{sec:sortware-architecture}
-\label{}
-\todo[inline]{
-	Give a short overview of the overall software architecture; provide a 
-	pictorial component overview or similar (if possible). If necessary provide 
-	implementation details.}
-
-\subsection{Software Functionalities}\label{sec:sortware-functionalities}
-\todo[inline]{Present the major functionalities of the software.}
-
-In the scope of this Paper, we aim at  exploring ideas revolving around quantum 
-gate model-inspired computing devices, and assess their feasibility to 
-benchmark a modern quantum architectures. The main idea that we have envisioned 
-for this project is  introducing new concepts of benchmarks for NISQ devices 
-benchmarking. This project aims to characterize the computing power and 
-investigate possible practical applications of such devices having access by 
-Amazon Braket.
-
-\subsubsection{Model specification}
-The scenario assumes that Alice and Bob have access to an unknown measurement
-device, a black box. Alice has hidden one of the two measurements, either $\PP$
-or $\mathcal{Q}$, in the black box. Bob only has the information that the black box
-performs one of these measurements. They want to determine an upper bound on the
-probability of correct discrimination between $\PP$ and $\mathcal{Q}$. Moreover, they also want to
-construct an optimal discrimination strategy to achieve the highest probability. Theoretical results were characterized in~\cite{puchala2018strategies}.
-
-In this work, we will consider the problem of discrimination between von Neumann 
-measurements. One of them on the computational basis, the second one on basis 
+Discriminating between von Neumann measurements is valuable from the applications viewpoint. That is because, unlike other types of measurements, they can be implemented on current hardware.
+So
+here, we will consider the discrimination task between two von Neumann measurements, one of them on the computational basis, whereas the second one on basis 
 $U$, where $U$ is a unitary matrix. 
-The scheme of discrimination can be divided into the following steps, which are 
-illustrated in Fig.~\ref{fig:theoretical_scheme}.
+Theoretical scenario was characterized in~\cite{puchala2018strategies}.
+Such a scheme can be best described into the following steps 
+and illustrated in
+Fig.~\ref{fig:theoretical_scheme}.
 
@@
 	\centering
-	\includegraphics[scale=1.7]{pics/theoretical_scheme}
+$  $	\includegraphics[scale=1.7]{pics/theoretical_scheme}
 	\caption{Theoretical  scheme of discrimination  between von Neumann measurements $\PP_{U}$ and $\PP_\Id$. }
@@
 
-%\begin{figure}[h!]
-%	\centering 
-%	\includegraphics[width=0.9\linewidth]{gates1.pdf} 
-%	\caption{A schematic representation of the setup for distinguishing
-%		measurements by using entanglement. }
-%	\label{fig:scheme}
-%\end{figure}
-
 \begin{enumerate}
-	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on systems 
-	$A$ and $B$.
-	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
-	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$ and measures the system $A$.
-	\item Alice performs the conditional binary measurement $\PP_{V_i}$ on the part 
-	$B$ based on the output label $i$. 
-	\item  Bob measures the system $B$ of the input state  $\ket{\psi_{AB}}$ and 
-	makes a decision based on the received label $j$. If $j=0$, then he decides 
-	that the the black box contains $\PP_U$. Otherwise, he decides that the 
-	black box contains $\PP_{\Id}$. 
+	\item We initialize the discriminator $\ket{\psi_{0}}$ on bipartite  system.
+	\item We perform one of two known measurements (either $\PP_{\Id}$ or 
+	$\PP_{U}$) on first part of the input state  $\ket{\psi_{0}}$, that means $\left(\PP \otimes \Id \right) (\proj{\psi_0})$.  
+	\item We measure the  first system and obtain a label $i$. 
+	\item We perform the conditional binary  (optimal) measurement $\PP_{V_i}$ on the second part based on the output label $i$. 
+	\item  We measure the second  system of the input state  $\ket{\psi_{0}}$ and 
+	make a decision based on the received label $j$. If $j=0$, then we decide 
+	that the $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs. 
 \end{enumerate}
@@
 measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of 
-this scheme is to perform a conditional binary measurement. 
-Unfortunately, current NISQ devices do not allow for performing conditional 
-binary measurements.
-The only possible measurement performed on quantum architectures is the 
-measurement in the computational basis. 
+this scheme is to perform a conditional  measurement. 
+However, current NISQ devices do not allow for performing conditional 
+ measurements.
+
 We  will present two possible methods providing a clever way to cross this 
@@
 \begin{enumerate}
-\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on systems 
-$A$ and $B$.
-\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or 
-$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
-\item Alice measures part $A$ of the input state  $\ket{\psi_{AB}}$ and 
-receives an output label $i$.
+\item We prepare  the discriminator $\ket{\psi_{0}}$ on bipartite system.
+\item We perform one of two quantum channels, either $\Phi_{\Id}$ or 
+$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left( \Phi \otimes \Id\right)(\proj{\psi_0})$.
+\item We measure the first part of the input state  $\ket{\psi_{0}}$ and 
+receive an output label $i$.
 \item  
-Based on Holevo--Helstrom theorem, Bob performs a conditional binary 
-measurement	$\PP_{V_j^\dagger}$ on part $B$.
-\item To calculate the probability of correct discrimination, they include just those cases for which $i = j$.
-\item Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and makes a
-decision based on received label $j$. If $i=j=0$, then he decides that the 
-black box contains $\PP_U$. Otherwise, he decides that the black box contains
-$\PP_{\Id}$.
+Based on Holevo--Helstrom theorem, we perform a conditional binary 
+measurement	$\PP_{V_j}$ and hence, we implement the quantum channel $\Phi_{V_j^\dagger}$ on the second part. 
+\item To calculate the probability of correct discrimination, we include just those cases for which $i = j$.
+\item We measure the second part of the input state  $\ket{\psi_{0}}$ and make a
+decision based on received label $j$. If $i=j=0$, then we decide that  
+$\PP_U$ occurs.  If $i=j=1$, we decide that 
+$\PP_{\Id}$ occurs.
 \end{enumerate}
@@
 \begin{split}
-(\Phi_{U}, \mathcal{P}_{V_k}, i, j) \\ 
-(\Phi_{\Id}, \mathcal{P}_{V_k}, i, j)
+(\Phi_{U^\dagger}, \Phi_{V_k^\dagger}, i, j) \\ 
+(\Phi_{\Id}, \Phi_{V_k^\dagger}, i, j)
 \end{split}
@@
 where $k=\{0,1\}, i=\{0,1\}$ and $ j=\{0,1\}$. 
-The optimal probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows.
+The optimal probability $p_{\text{succ}}(\PP_{U}, \PP_{\Id}) $ of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows
 		\begin{equation}
-		p = \frac{\#(\Phi_U, \PP_{V_i},i,0) + \#(\Phi_\Id, \PP_{V_i},i,1)}{\#(\Phi_U, \PP_{V_i},i,j) + \#(\Phi_\Id, \PP_{V_i},i,j)}, 
+		p_{\text{succ}}(\PP_{U}, \PP_{\Id})= \frac{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,0) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,1)}{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,j) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,j)},
 		\end{equation}
@@
 \begin{enumerate}
-\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on 
-systems $A$ and $B$.
-\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or
-$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
-\item Alice and Bob implement controlled unitary $V_0 \oplus V_1$ obtained from 
-Holevo--Helstrom theorem.	
-\item Alice and Bob prepare the measurement $\Delta$ in computational basis on 
-their systems.
-\item Bob makes a decision based on received label $j$. If $j=0$, then he
-decides that the the black box contains $\PP_U$. Otherwise, he decides that the
-black box contains $\PP_{\Id}$.
+\item We prepare the discriminator $\ket{\psi_{0}}$ on bipartite 
+system. 
+\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
+$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
+\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
+Observe that   $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger} = \proj{0} \otimes \Phi_{V_0^\dagger}  + \proj{1} \otimes \Phi_{V_1^\dagger}.
+$
+\item We measure all systems in computational basis $\Delta$.
+\item We make a decision based on received label $j$ on the second system. If $j=0$, then we
+decide that $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs.
 \end{enumerate}
@@
 \begin{split}
-(\Phi_{U}, V_0 \oplus V_1, i, j) \\ 
-(\Phi_{\Id},  V_0 \oplus V_1, i, j)
+(\Phi_{U^\dagger}, \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j) \\ 
+(\Phi_{\Id},  \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j)
 \end{split}
@@
 \begin{equation}
-p = \frac{\#(\Phi_U,V_0 \oplus V_1,i,0) + \#(\Phi_\Id,V_0 \oplus V_1,i,1) }{\#(\Phi_U,V_0 \oplus V_1,i,j) + \#(\Phi_\Id,V_0 \oplus V_1,i,j)}
+p = \frac{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,0) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,1) }{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j)}
 \end{equation}
@@
 
-Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
-the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
-$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
-will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
-matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
-positive semidefinite operators having trace equal to one, will be denoted
-$\Omega_d$. 
- The subset of $M_d$ consisting of unitary matrices will be denoted
-by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$. 
-	An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$.
-Whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
-
- We will also need a linear mapping transforming $M_{d_1}$ into
-$M_{d_2}$, which will be denoted 
+In this and the following sections we will denote complex Euclidean spaces $\mathbb{C}^d$ with $\XX, \mathcal{Y}$ etc.
+When needed the dimension of a space $\XX$ will be denoted $\dim(\XX)$.
+The set of matrices transforming vectors from $\XX$ to $\mathcal{Y}$ will be denoted $\mathrm{L}(\XX, \mathcal{Y})$.
+ We will also need a linear mapping transforming $\mathrm{L}(\XX)$ into
+$\mathrm{L}(\mathcal{Y})$, which will be denoted 
 \begin{equation}
-\Phi: M_{d_1 } \rightarrow M_{d_2}.
+\Phi: \mathrm{L}(\XX) \rightarrow \mathrm{L}(\mathcal{Y}).
 \end{equation} 
 There
-exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
+exists a bijection between introduced linear mappings $\Phi$ and set of matrices $\mathrm{L}(\mathcal{Y} \otimes \mathcal{X})$,  known as the Choi-
 Jamio{\l}kowski isomorphism. 
-For a given linear mapping $\Phi_M$ corresponding  Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
+For a given linear mapping $\Phi$ the corresponding  Choi operator $J(\Phi)$ is explicitly written as 
 \begin{equation}
-\mathcal{J}(\Phi) \coloneqq \sum_{i,j=1}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
+J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
 Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
 and trace preserving (CPTP).
-In this work we will consider a special class of quantum channels, called unitary channels. Let $U \in \UU_d$ be a unitary operator. A unitary channel
-$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
-\UU_d$. A general quantum
+We will consider a special class of quantum channels, called unitary channels. A unitary channel
+$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  and unitary $U$.
+
+A general quantum
 measurement, that is a positive operator valued measure (POVM) $\PP$ is a
@@
 called a von Neumann measurement. Every von Neumann measurement can be
-parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
-for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
-where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
-quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
-seen as  a measure-and-prepare quantum channel as follows 
-$
-\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-$
+parameterized by a unitary matrix $U$ which the effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+ale creating by taking $\ket{u_i}$ as  $i+1$-th column of the unitary matrix $U$. 
+Hence, we will use the notation $\PP_{U}$. 
+%
+%
+% The action of
+%quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
+%seen as  a measure-and-prepare quantum channel as follows 
+%$
+%\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
+%$
 
@@
 
-Let us  consider a  linear mapping transforming  square matrices into square 
-matrices that is $\Phi: M_{d_1} \to M_{d_2}$. 
 We define the diamond norm of a map $\Phi$ as 
 \begin{equation}
-\|\Phi\|_\diamond = \max_{\|X\|_1=1} \| \left(\Phi \otimes \1\right) (X) \|_1.
+\|\Phi\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left(\Phi \otimes \1\right) (\proj{\psi}) \|_1.
 \end{equation}
+The quantum state $\ket{\psi}$ which maximizes the diamond norm we will call as discriminator.
 
-The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
+The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$, 
 in terms of their distance with the use of the diamond norm
 \begin{equation}
-p_{\text{succ}}(\TT, \SS) =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
+p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond.
 \end{equation}
-In the case of discrimination between two von Neumann measurements $\PP_U$ and 
-$\PP_\Id$ we know that (from Theorem 1 \cite{puchala2018strategies})
-\begin{equation}
-\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
-\Phi_\Id\|_\diamond,
-\end{equation}
-where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
-unitary matrices of dimension $d$.
-
-\paragraph{Discrimination of unitary channels}
-
-Before we proceed to presenting our main results, we need to briefly discuss the
-problem of discrimination of unitary channels.  For this purpose, we introduce the notion of numerical range of
-a given matrix $A \in M_d$. The set \begin{equation}
-W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
-\mathbb{C}^d, \;
-\;\braket{x}{x}=1\}.
-\end{equation}   
-is the numerical range of $A$.
-The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.
-
- Let us now recall the well-known result for the
-distinguishability of unitary channels.
-	Let $U \in \UU_d$ and $\Phi_U$ be a unitary 
-	channel. 
-	Then, the following equation holds
-	\begin{equation}
-	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-	\end{equation}
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. And hence the optimal probability to discriminate two unitary channel is given by 
-	\begin{equation}
-	p_{\text{succ}}(\Phi_U, \Phi_\Id) = \frac{1}{2} + \frac{1}{2} \sqrt{1-\nu^2}.
-	\end{equation}
-
-%In the general case, the diamond norm of a Hermiticity-preserving maps $\Phi$ 
-%can be computed using the Semidefinite Program~\cite{watrous2018theory} and 
-%state 
-%primal and dual problem in the following form:
-
-%
-%\begin{minipage}{0.495\linewidth}
-%	\begin{equation*}
-%		\begin{split}
-%			\text{\textbf{Primal problem:}} \\
-%			\text{maximize:}\quad & \tr(X J(\Phi)) \\[2mm]
-%			\text{subject to:}\quad &  \left[ \begin{array}{cc}\Id_{d_2} 
-%\otimes \rho & X \\ X^* & \Id_{d_2} \otimes \rho  \end{array} \right] \ge 0 \\
-%			& \rho \in \HH_d^+\\ 
-%			& X \in M_{d1,d2}.
-%		\end{split}
-%	\end{equation*}
-%\end{minipage}
-%\begin{minipage}{0.495\linewidth}
-%	\begin{equation*}
-%		\begin{split}
-%			\text{\textbf{Dual problem:}} \\
-%			\text{minimize:}\quad & ||\tr_1(Y)||_\infty \\[2mm]
-%			\text{subject to:}\quad & \left[ \begin{array}{cc}Y & -J(\Phi) \\ 
-%-J(\Phi) &  Y \end{array} \right] \ge 0 \\
-%			& Y \in \HH_{d_1d_2}^+.
-%		\end{split}
-%	\end{equation*}
-%	\vspace{0.5cm}
-%\end{minipage}
 
@@
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this section we present theoretical probability of correct 
-discrimination between these measurements. Moreover, we create the optimal 
-theoretical strategy of their discrimination. 
-The otimal probability will be calculated in 
-subsection~\ref{sec:example_theoretical_probability}. Later, we will 
-discuss the realization of this scheme in 
-subsection~\ref{sec:example_realization}. For such realization, we 
-will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
-and final measurement (see sec.~\ref{sec_example_final_measurement}).
 
-\subsection{Theoretical probability}\label{sec:example_theoretical_probability}
-
-In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.
-To do that, we will present an auxiliary lemma.
-\begin{lemma}\label{lemma:min-e-optimal}
-Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
-$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds 
-\begin{equation}
-\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-\Phi_\Id\|_\diamond,
-\end{equation}
-\end{lemma}
-
-\begin{proof} Recall that the distance between two unitary channels is given by
-	$
-	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-	$
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$. 
-	For $U = H 
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
-	\begin{equation}
-	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |. 
-	\end{equation} 
-		It implies that it is enough to prove  \begin{equation}
-		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-		\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
-		\end{equation}
-%		It implies that we can prove  equivalently  the following condition
-%		\begin{equation}
-%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
-%		\end{equation}
-This condition is equivalent to 
-	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
-	\end{equation}
-	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
-
-%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
- The celebrated Hausdorf-T{\o}plitz theorem~\cite{hausdorff, toeplitz} states that
-$W(A)$ of any matrix $A \in M_d$ is a convex set and therefore
-\begin{equation}
-W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}. 
-\end{equation}
-So we obtain that 
-	\begin{equation}
-	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
-	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
-	\end{equation}
-	And then we have 
-	 \begin{equation}
- \max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
-		\Omega_2} \left| \tr \left( \rho U E \right) \right|
-	\end{equation}
-	For that, our task is reduce to show that
-	\begin{equation}
-	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \mu
-	\end{equation}
-	where $\mu \coloneqq \max_{E \in \diaguni_2 } \nu_{E}.$
-
-	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ 
-	and take $\rho = 
-	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
-	From spectral theorem, let us decompose $U$ as
-	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
-	\end{equation}
-	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
-	eigenvector is 
-	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
-	$.
-	Then, we have 
-	\begin{equation}
-	\begin{split}
-	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
-	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
-	\frac{1}{2} \left| \tr\left((   \proj{x_1} +e^{i \phi}\proj{x_2} ) E \right) 
-	\right|  = 
-	\frac{1}{2} \left|  \bra{x_1} E \ket{x_1} +  e^{i \phi}\bra{x_2} E \ket{x_2} 
-	\right| = \\& 
-	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| 
-	= 
-	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
-	\mu, 
-	\end{split}
-	\end{equation}
-	which completes the proof.
-\end{proof}
+\subsubsection{Probability}\label{sec:example_probability}
 \begin{theorem}
 The optimal probability of correct discrimination between von Neumann
-measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
-where $\phi \in [0, 2\pi)$ is given by
+measurements $\PP_U$ and $\PP_{\Id}$ is given by
 \begin{equation}
@@
 
-\begin{proof}
-	From Holevo-Helstrom theorem we obtain
-	\begin{equation}
-p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
-	\end{equation}
-	From Theorem 1 in~\cite{puchala2018strategies} we have 
-	\begin{equation}
-	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond. 
-	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal} we know that for 
-	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
-	\begin{equation}
-		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-	\Phi_\Id\|_\diamond,
-	\end{equation} which is exactly equal to 
-	\begin{equation}
-	\|\Phi_{U} - 
-	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|. 
-	\end{equation}
-%	Finally, we obtain that
-%	\begin{equation}
-%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
-%	\end{equation}
-	It implies that
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
-	\end{equation} which completes the proof.
-\end{proof}
-
-\subsection{Realization}\label{sec:example_realization}
-Now we focus on the realization of the discrimination protocol. We will 
-discriminate between $\PP_U$ and $\PP_\1$. To do so, we need to know exact 
-forms of the input state and final measurement. We will indicate the optimal 
-input state in subsection~\ref{sec:example_discriminator} and the final 
-measurement in subsection~\ref{sec_example_final_measurement}.
-
 \subsubsection{Discriminator}\label{sec:example_discriminator}
@@
 \begin{proposition}\label{prop-discrim}
-Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
-and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
-2\pi)$.  The optimal input state has the form
+ The optimal input state has the form
 \begin{equation}
-\ket{\psi_{AB}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
+\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
 \end{equation}
@@
 
-\begin{proof}
-Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0, 
-2\pi)$ be decomposed as 
-	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
-	\end{equation}
-	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
-	eigenvector is 
-	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
-	$.
+%
 
-For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
-\begin{equation}
-\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
-Hence, we obtain
-\begin{equation}
-\begin{split}
-\| \PP_{U} - \PP_{\Id}  \|_\diamond 
-& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
-\mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
-\\ 
-& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
-\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
-\right\|_1  \\ 
-& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
-\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
-\\ 
-& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
-\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
-\end{split}
-\end{equation}
-One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
-\ket{y}$ the following equation holds~\cite{watrous} 
-\begin{equation}
-\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
-\beta |\braket{x}{y}|^2}.
-\end{equation}
-By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
-\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
-\ket{i} \|}$ we have
-\begin{equation}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
-	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
-	}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
-\end{equation}
-Let us take  $\rho_0 =   \frac{1}{2}  	
-\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
-\begin{equation}
-\begin{split}
-||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
-&= \sum_{i=0}^1  
-\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
-	4|\bra{i}\rho_0\ket{u_i}|^2}  \\
-&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2} 
-\\ 
-&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1} 
-	\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
-&= \sum_{i=0}^1 
- \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
-= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
-&= |1-e^{i \phi }|.
-\end{split}
-\end{equation}
-Observe that
-\begin{equation}
-\begin{split}
-\| \PP_{U} - \PP_{\Id}  \|_\diamond  
-&=  \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
-\Id \otimes \sqrt{\rho} \right) \|_1 \\
-&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
-\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
-\end{split}
-\end{equation}
-Due to that, we know  
-that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ is the discriminator of the problem 
-of discrimination between 
-$\PP_{\Id} $ and $\PP_U$ for 
-$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
-).      Hence we obtain that \begin{equation}
-\ket{\psi_{AB}} \coloneqq   | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
-\Id_2 \rangle \rangle,
-\end{equation}
-which completes the proof.
-\end{proof}
-
-%
-%
-%\begin{remark}\label{lemma:rho}
-%	Let $\rho_{0} = \frac{1}{2} 
-%	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)$. Then 
-%	\begin{equation}
-%	 \max_\rho \left\|(\1\otimes \sqrt{\rho}) J(\PP_U - \PP_{\Id}) 
-%	(\1\otimes 
-%	\sqrt{\rho})\right\|_1 =    \left\|(\1\otimes \sqrt{\rho_0}) J(\PP_U - 
-%	\PP_{\Id}) 
-%		(\1\otimes 
-%		\sqrt{\rho_0})\right\|_1
-%	\end{equation}
-%	for  $U = H\diag(1, e^{i \phi}) H^\dagger $, 
-%		where $\phi \in [0, 2\pi)$. 
-%\end{remark}
-
-\subsubsection{Conditional measurement}\label{sec_example_final_measurement}
-In this subsection we will derive exact form of the conditional measurement in the
-problem of discrimination of von Neumann measurements $\PP_U$ and $\PP_{\Id}$
-for $U = H \diag(1, e^{i \phi}) H^\dagger$, where $\phi \in [0, 2\pi)$.
+\subsubsection{Conditional binary measurement/Optimal measurement}\label{sec_example_final_measurement}
 
 \begin{proposition}  
-	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
-	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
-	2\pi)$.  
-The  conditioned measurement has the form
+The  optimal measurement has the following form
 \begin{equation}
@@
 \end{equation}
-where for each $\phi \in \mathbb{R}$,  the controlled unitaries $V_0$ and $V_1$ 
-have the form
+where for each $\phi \in \mathbb{R}$ and  the unitaries $V_0$,  $V_1$ 
+have the following form
 \begin{equation}
@@
 \end{proposition}
-
-\begin{proof}
-From Proposition~\ref{prop-discrim} we have the form of discriminator given by
-\begin{equation}
-\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
-\rangle \rangle. 
-\end{equation}
-From Holevo-Helstrom theorem  we constrain a conditional measurement $\mu$.  
-Let us define 
-\begin{equation}
-X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
-\otimes \Id_2 \right)(\proj{\psi}).
-\end{equation} 
-From the Hahn-Jordan decomposition, let us note
-\begin{equation}
-X = P - Q
-\end{equation}
-where $P, Q \ge 0 $. 
-Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
-respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
-\begin{equation}
-\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
-\end{equation}
-and 
-\begin{equation}
-\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
-\end{equation}
-Hence, we define $V_0$ such that
-\begin{equation}
-\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
-\end{equation}
-and $V_1$ such that
-\begin{equation}
-\begin{cases} 
-V_1 \ket{y_p} = \ket{0} \\ 
-V_1 \ket{y_q} = \ket{1}
-\end{cases}. 
-\end{equation}
-For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
-\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
-follows (see also \texttt{one-qubit.nb}).
-The unitary $V_0$ has the form
-\begin{equation}
-V_0 = \left(
-\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
-\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
-\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
-\end{array}
-\right),
-\end{equation}
-whereas the unitary  $V_1$  has the form
-\begin{equation}
-V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
-\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
-\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right)
-\end{equation}
-for all $\phi \in [0,2\pi)$. 
-Finally, we obtain the measurement $\mu$ of the form
-\begin{equation}
-\begin{split}
-\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{0} V_1^\dagger  \\ 
-\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{1} V_1^\dagger.  
-\end{split}
-\end{equation}
-
-\end{proof}
-
-\section{Implementation}
-In this section we will compare theoretical probability of correct 
-discrimination between these measurements and the realization on real devices.
-\todo[inline]{TU WYNIKI PRAKTYCZNE }
-
-\subsection{Generic case}
-Now we present the circuits for the generic case.
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-None}
-\caption{Circuit representing state preparation in the  generic case.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-None}
-\caption{Circuit representing $U^\dagger$ in the generic case.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-None}
-\caption{Circuit representing $V_0^\dagger$ in the generic case.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
-\caption{Circuit representing controlled $V_0$ and $V_1$ the generic case.}
-\end{figure}
-
-\subsection{IBMQ and Lucy}
-
-\subsection{IBMQ}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-ibmq}
-\caption{Circuit representing state preparation for IBMQ.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-ibmq}
-\caption{Circuit representing $U^\dagger$ for IBMQ.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-ibmq}
-\caption{Circuit representing $V_0^\dagger$ for IBMQ.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
-\caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
-\end{figure}
-
-\subsection{Lucy}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-lucy}
-\caption{Circuit representing state preparation for Lucy.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-lucy}
-\caption{Circuit representing $U^\dagger$ for Lucy.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-lucy}
-\caption{Circuit representing $V_0^\dagger$ for Lucy.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
-\caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
-\end{figure}
-
-\subsection{Rigetti}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-rigetti}
-\caption{Circuit representing state preparation for Rigetti.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-rigetti}
-\caption{Circuit representing $U^\dagger$ for Rigetti.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-rigetti}
-\caption{Circuit representing $V_0^\dagger$ for Rigetti.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
-\caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}
-\end{figure}
-
-\subsection{Sample code snippets analysis (optional)}
-\todo[inline]{moze tu fragmenty kodu ? }
-\label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$. In 
-%this simplest case,  we consider two von Neumann measurements $\PP_\1$ and 
-%$\PP_U$ for $U = H diag(0,\ee^{\ii \phi}) H$, where $H_d$--Hadamard matrix 
-%of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected 
-%probability $p_{success}$ of correct distinction between two measurements 
-%$\PP_\1$ and $\PP_U$  is given by
-%\begin{equation}
-%p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = 
-%\frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
-%\end{equation}
-%by the assumption the discriminator is on the form $\ket{\psi} = 
-%\frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
-%(tu wyniki z rigettiego...)
-
-\section{Impact }
-
-\textbf{This is the main section of the article and the reviewers weight the 
-description here appropriately}
-
-Indicate in what way new research questions can be pursued as a result of the 
-software (if any).
-
-Indicate in what way, and to what extent, the pursuit of existing research 
-questions is improved (if so).
-
-Indicate in what way the software has changed the daily practice of its users 
-(if so).
-
-Indicate how widespread the use of the software is within and outside the 
-intended user group.
-
-Indicate in what way the software is used in commercial settings and/or how it 
-led to the creation of spin-off companies (if so).
-
-\section{Conclusions}
-\label{}
-
-Set out the conclusion of this original software publication.
-
-\section{Conflict of Interest}
-Please select the appropriate text:
-
-Potential conflict of interest exists:
-We wish to draw the attention of the Editor to the following facts, which may 
-be considered as potential conflicts of interest, and to significant financial 
-contributions to this work. The nature of potential conflict of interest is 
-described below: [Describe conflict of interest]
-
-No conflict of interest exists:
-We wish to confirm that there are no known conflicts of interest associated 
-with this publication and there has been no significant financial support for 
-this work that could have influenced its outcome.
-
-\section*{Acknowledgements}
-
-This work was supported by the Foundation for Polish Science (FNP) under grant
-number POIR.04.04.00-00-17C1/18-00.
 
@@
 
-\todo[inline]{Please add the reference to the software repository if DOI for 
-software  is available. }
+\end{document}
 
-\section*{Current executable software version}
-\label{}
-
-Ancillary data table required for sub version of the executable software: (x.1, 
-x.2 etc.) kindly replace examples in right column with the correct information 
-about your executables, and leave the left column as it is.
-
-\begin{table}[!h]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-\hline
-\textbf{Nr.} & \textbf{(Executable) software metadata description} & 
-\textbf{Please fill in this column} \\
-\hline
-S1 & Current software version & For example 1.1, 2.4 etc. \\
-\hline
-S2 & Permanent link to executables of this version  & For example: 
-$https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
-\hline
-S3 & Legal Software License & List one of the approved licenses \\
-\hline
-S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, 
-Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based 
-etc. \\
-\hline
-S5 & Installation requirements \& dependencies & \\
-\hline
-S6 & If available, link to user manual - if formally published include a 
-reference to the publication in the reference list & For example: 
-$http://mozart.github.io/documentation/$ \\
-\hline
-S7 & Support email for questions & \\
-\hline
-\end{tabular}
-\caption{Software metadata (optional)}
-\label{} 
-\end{table}
-
-\end{document}
-\endinput
 %%

### 2022-11-07 txt/maths.tex
Update note with mathematical foundations

@@
 \newcommand{\PP}{\mathcal{P}}
+\newcommand{\QQ}{\mathcal{Q}}
 \renewcommand{\SS}{\mathcal{S}}
@@
 
-\subsubsection{Model specification}
-The scenario of measurements discrimination assumes that we have access to an unknown measurement
-device. One of the two measurements, either $\PP$
-or $\mathcal{Q}$,  was used during an experiment. The only information we have that one of these measurements was 
-performed. We want to determine an upper bound on the
-probability of correct discrimination between $\PP$ and $\mathcal{Q}$. Moreover, we also want to
-construct an optimal discrimination strategy to achieve the highest possible probability.
+\subsubsection{Motivation}
 
-Discriminating between von Neumann measurements is valuable from the applications viewpoint. That is because, unlike other types of measurements, they can be implemented on current hardware.
-So
-here, we will consider the discrimination task between two von Neumann measurements, one of them on the computational basis, whereas the second one on basis 
-$U$, where $U$ is a unitary matrix. 
-Theoretical scenario was characterized in~\cite{puchala2018strategies}.
-Such a scheme can be best described into the following steps 
-and illustrated in
-Fig.~\ref{fig:theoretical_scheme}.
+Suppose we have access to a device performing one of the predefined von Neumann
+measurements\footnote{In PyQBench, we restrict ourselves to discriminating von Neumann measurements.
+This is because, unlike other measurement types, they can be implemented on actual hardware.
+},  $\PP$ or $\QQ$. While the $\PP$ and $\QQ$ are known, it is not known which of them is
+performed when the device executes. Based on the measurement outcome, you have to guess which
+measurement was performed (but you can perform arbitrary unitary operations before and after the
+measurement). What is the highest probability of making a correct guess? And what do you have to do
+to achieve it? And, most importantly, why would we want to do this?
+
+Suppose that you know a strategy that, for an ideal device, would yield a probability
+$p_{\text{succ}}$ of successfully discriminating between two measurements. Will the probability be
+the same on an actual physical device? For current, Noisy Intermediate Scale Quantum devices
+(NISQs), the answer is: certainly not. However, the error rate that you make when guessing can be
+used as a benchmarking metric. PyQBench helps you in organizing such discrimination experiments for
+a single qubit system\footnote{As we will soon see, the optimal discrimination strategy requires
+the usage of an additional auxiliary qubit.}, executing them on real hardware or simulators, and
+computing discrimination probabilities based on the measured bitstrings.
+
+\subsubsection{Discrimination scheme}
+
+Without loss of generality, we consider discrimination between a measurement in the computational
+Z-basis ($\PP_\Id$), and an alternative measurement performed in the basis $U$
+($\PP_U$)\footnote{Explaining why we can consider only Z-basis and alternative measurement is beyond
+the scope of this technical documentation. See \cite{puchala2018strategies} if you are interested in
+the explanation.}. In PyQBench, we operate only on two-level systems, but the discrimination scheme,
+described in detail in \cite{puchala2018strategies}, makes no assumptions about the dimensionality.
+
+In general, the discrimination scheme, presented in Fig.\ref{fig:theoretical_scheme}, requires a
+second system of the same dimensionality as the measured one. First, the joint system is prepared in
+some state $\ket{\psi_0}$. Then, the unknown measurement is performed on the first part of the
+system. Based on its outcome $i$, another measurement $\mathcal{P}_{V_i}$ is performed to obtain an
+outcome $j$. Finally, if $j=0$ we guess that the performed measurement is $\mathcal{P}_U$, otherwise
+we guess that it was $\mathcal{P}_\Id$.
 
@@
 	\centering
-$  $	\includegraphics[scale=1.7]{pics/theoretical_scheme}
+	\includegraphics[scale=1.7]{pics/theoretical_scheme}
 	\caption{Theoretical  scheme of discrimination  between von Neumann measurements $\PP_{U}$ and $\PP_\Id$. }
@@
 \end{figure}
-
-\begin{enumerate}
-	\item We initialize the discriminator $\ket{\psi_{0}}$ on bipartite  system.
-	\item We perform one of two known measurements (either $\PP_{\Id}$ or 
-	$\PP_{U}$) on first part of the input state  $\ket{\psi_{0}}$, that means $\left(\PP \otimes \Id \right) (\proj{\psi_0})$.  
-	\item We measure the  first system and obtain a label $i$. 
-	\item We perform the conditional binary  (optimal) measurement $\PP_{V_i}$ on the second part based on the output label $i$. 
-	\item  We measure the second  system of the input state  $\ket{\psi_{0}}$ and 
-	make a decision based on the received label $j$. If $j=0$, then we decide 
-	that the $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs. 
-\end{enumerate}
 

### 2022-11-23 txt/maths.tex
Update maths.tex and direct_sum.tex

@@
 \usepackage{amsthm}
+\usepackage{amsmath}
 \usepackage{mathtools}
@@
 
-\subsubsection{Quantum architecture's limits and practical solutions}
+\subsubsection{Limitations of NISQ devices and practical discrimination schemes}
 
-Let us take a closer look at the setup for distinguishing von Neumann 
-measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of 
-this scheme is to perform a conditional  measurement. 
-However, current NISQ devices do not allow for performing conditional 
- measurements.
+Current NISQ devices are unable to perform conditional measurements, which is the biggest
+obstacle to implementing our scheme on real hardware. Luckily, we can overcome it by
+cleverly adjusting our scheme so that it only uses components available on current devices.
+We have two possible choices here: using a postselection or a direct sum
+$V_0^\dagger\oplus V_1^\dagger$.
 
-We  will present two possible methods providing a clever way to cross this 
-obstacle. These will be two schemes of practical realization. 
-The first method consists in using postselection while the second method 
-consists in applying a controlled unitary. These methods are described below.
+\begin{scheme}(By using postselection)
 
-\begin{scheme}(Postselection)
-
-%\begin{figure}[h!]
-%	\includegraphics[scale=1.5]{onequbit.pdf}
-%	\caption{A schematic representation of the setup for distinguishing
-%		measurements using postselection.}
-%	\label{postselection}
-%\end{figure}
-
-\begin{enumerate}
-\item We prepare  the discriminator $\ket{\psi_{0}}$ on bipartite system.
-\item We perform one of two quantum channels, either $\Phi_{\Id}$ or 
-$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left( \Phi \otimes \Id\right)(\proj{\psi_0})$.
-\item We measure the first part of the input state  $\ket{\psi_{0}}$ and 
-receive an output label $i$.
-\item  
-Based on Holevo--Helstrom theorem, we perform a conditional binary 
-measurement	$\PP_{V_j}$ and hence, we implement the quantum channel $\Phi_{V_j^\dagger}$ on the second part. 
-\item To calculate the probability of correct discrimination, we include just those cases for which $i = j$.
-\item We measure the second part of the input state  $\ket{\psi_{0}}$ and make a
-decision based on received label $j$. If $i=j=0$, then we decide that  
-$\PP_U$ occurs.  If $i=j=1$, we decide that 
-$\PP_{\Id}$ occurs.
-\end{enumerate}
-
-The schematic representation of this setup is depicted in 
-Fig.~\ref{fig:postsellection}.
+The first idea is very simple. Instead of performing a conditional measurement, for each
+measurement $\PP_U, \PP_\Id$ to be discriminated and each choice of $k \in \{0, 1\}$ we run circuit presented in Fig. \ref{fig:postselection}.
 
@@
 	\centering
-	\includegraphics[scale=1.7]{pics/postselection}
+	\includegraphics[scale=1.7]{pics/postselection_no_channels}
 
-	\caption{ A schematic representation of the setup for distinguishing
-		measurements using postselection. 
-	}\label{fig:postsellection}
+	\caption{
+		Postselection scheme of discrimination between von Neumann measurements $\PP_{U}$ and $\PP_\Id$.
+	}\label{fig:postselection}
 \end{figure}
 
-Due to the fact that the measurement result is nondeterministic, we are forced to consider the following circuits
-in the postselection procedure
+But now our experiment does not match the previously described scheme, right?
+Yes, unless we discard all the outcomes for which $i\ne k$ (hence the name \emph{postselection},
+we are selecting valid outcomes after the experiment is performed).
+
+% \begin{scheme}(Postselection)
+
+% %\begin{figure}[h!]
+% %	\includegraphics[scale=1.5]{onequbit.pdf}
+% %	\caption{A schematic representation of the setup for distinguishing
+% %		measurements using postselection.}
+% %	\label{postselection}
+% %\end{figure}
+
+% \begin{enumerate}
+% \item We prepare  the discriminator $\ket{\psi_{0}}$ on bipartite system.
+% \item We perform one of two quantum channels, either $\Phi_{\Id}$ or
+% $\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left( \Phi \otimes \Id\right)(\proj{\psi_0})$.
+% \item We measure the first part of the input state  $\ket{\psi_{0}}$ and
+% receive an output label $i$.
+% \item
+% Based on Holevo--Helstrom theorem, we perform a conditional binary
+% measurement	$\PP_{V_j}$ and hence, we implement the quantum channel $\Phi_{V_j^\dagger}$ on the second part.
+% \item To calculate the probability of correct discrimination, we include just those cases for which $i = j$.
+% \item We measure the second part of the input state  $\ket{\psi_{0}}$ and make a
+% decision based on received label $j$. If $i=j=0$, then we decide that
+% $\PP_U$ occurs.  If $i=j=1$, we decide that
+% $\PP_{\Id}$ occurs.
+% \end{enumerate}
+
+More precisely, our experiments can be grouped into classes identified by tuples of the form
+$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen measurement.
+We discard all the experiments for which $k \ne i$. Hence, the total number of valid experiments is
+
 \begin{equation}
-\begin{split}
-(\Phi_{U^\dagger}, \Phi_{V_k^\dagger}, i, j) \\ 
-(\Phi_{\Id}, \Phi_{V_k^\dagger}, i, j)
-\end{split}
+	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}
 \end{equation}
-where $k=\{0,1\}, i=\{0,1\}$ and $ j=\{0,1\}$. 
-The optimal probability $p_{\text{succ}}(\PP_{U}, \PP_{\Id}) $ of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows
+
+We now need to count the experiments (among the valid ones) resulting in successful discrimination.
+If we have chosen $\PP_U$, then we guess correctly iff $j=0$. Similarly, for
+$P_\Id$, we guess correctly iff $j=1$. If we define
+\begin{eqnarray}
+	N_{\PP_U} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_U, k = i, j = 0\} \\
+	N_{\PP_\Id} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_\Id, k = i, j = 1\}
+\end{eqnarray}
+then the empirical success probability can be computed as
+
 \begin{equation}
-		p_{\text{succ}}(\PP_{U}, \PP_{\Id})= \frac{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,0) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,1)}{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,j) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,j)},
+p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{N_{\PP_U} + N_{\PP_\Id}}{N_{\text{total}}}.
 \end{equation}
-where $i=\{0,1\}$ and $ j=\{0,1\}$.
 

### 2022-12-07 txt/manuscript.tex
Update abstract, keywords and authors

@@
 
-\title{Benchmarking on Rigetti architecture}
+\title{}
 
@@
 
+\author{Konrad Jałowiecki}
 \author{Paulina Lewandowska}
-\author{\L ukasz Pawela}
+\author{Profesor Kierownik \L ukasz Pawela}
 
@@
 \begin{abstract}
-We introduce library ?, a comprehensive open source framework for benchmarking 
-Amazon Braket Rigetti IonQ architectures ? 
-The framework is built around  the scheme of discrimination of von Neumann 
-measurements. The library provides algorithm for ... Our main aim is creating a 
-common platform  for open research.  ?
+We introduce PyQBench, an innovative open-source framework for benchmarking 
+gate-based quantum computers. PyQBench can benchmark NISQ devices by verifying their capability of
+discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
+command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
+family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
+measurements instead of predefined ones.
 
@@
 %% keywords here, in the form: keyword \sep keyword
-Benchmarking of Rigetti architecture \sep Discrimination of quantum 
-measurements \sep Von Neumann measurements discrimination
+Quantum computing \sep
+Benchmarking quantum computers \sep 
+Discrimination of quantum measurements \sep 
+Discrimination of von Neumann Measurements \sep
+Open-source \sep
+Python programming
 

### 2022-12-12 txt/manuscript.tex
Update title and corresponding author
Update manuscript
creating appendix and rewriting mathemaytical prelimaties and parametrized family

@@
-%% 
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%% SP 2008/03/01
-
 \documentclass[preprint,12pt, a4paper]{elsarticle}
 
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
 \usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
+
 \usepackage{amsthm}
 \usepackage{mathtools}
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
+
 \usepackage{lineno}
@@
 \newcommand{\tr}{\mathrm{tr}}
-%\DeclareMathOperator{\diag}{diag}
-%\DeclareMathOperator{\diag}{diag}
 \journal{SoftwareX}
@@
 
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author{Konrad Jałowiecki}
+\title{PyQBench: a Python library for benchmarking gate-based quantum computers}
+
+\author{Konrad Jałowiecki\corref{cor1}}
+\ead{dexter2206@gmail.com}
+\cortext[cor1]{Corresponding author}
+
 \author{Paulina Lewandowska}
@@
 
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
+%\PACS 03.67.−a \sep 03.67.Lx
+
+\MSC 81P68
 
@@
 \begin{enumerate}
-	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on systems 
+	\item Alice and Bob share an entangled state $\ket{\psi_{0}}$ (discriminator) on systems 
 	$A$ and $B$.
 	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
-	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$ and measures the system $A$.
+	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{0}}$ and measures the system $A$.
 	\item Alice performs the conditional binary measurement $\PP_{V_i}$ on the part 
 	$B$ based on the output label $i$. 
-	\item  Bob measures the system $B$ of the input state  $\ket{\psi_{AB}}$ and 
+	\item  Bob measures the system $B$ of the input state  $\ket{\psi_{0}}$ and 
 	makes a decision based on the received label $j$. If $j=0$, then he decides 
@@
 \begin{enumerate}
-\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on systems 
+\item Alice and Bob prepare an entangled state $\ket{\psi_{0}}$ (discriminator) on systems 
 $A$ and $B$.
 \item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or 
-$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
-\item Alice measures part $A$ of the input state  $\ket{\psi_{AB}}$ and 
+$\Phi_{U^\dagger}$,  on part $A$ of the input state  $\ket{\psi_{0}}$.
+\item Alice measures part $A$ of the input state  $\ket{\psi_{0}}$ and 
 receives an output label $i$.
@@
 Based on Holevo--Helstrom theorem, Bob performs a conditional binary 
-measurement	$\PP_{V_j^\dagger}$ on part $B$.
+measurement	$\PP_{V_j}$ and implements the unitary channel 	$\Phi_{V_j^\dagger}$ on part $B$.
 \item To calculate the probability of correct discrimination, they include just those cases for which $i = j$.
-\item Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and makes a
+\item Bob measures part $B$ of the input state  $\ket{\psi_{0}}$ and makes a
 decision based on received label $j$. If $i=j=0$, then he decides that the 
@@
 		\begin{equation}
-		p = \frac{\#(\Phi_U, \PP_{V_i},i,0) + \#(\Phi_\Id, \PP_{V_i},i,1)}{\#(\Phi_U, \PP_{V_i},i,j) + \#(\Phi_\Id, \PP_{V_i},i,j)}, 
+		p = \frac{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,0) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,1)}{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,j) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,j)}, 
 		\end{equation}
@@
 \begin{enumerate}
-\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on 
+\item Alice and Bob prepare an entangled state $\ket{\psi_{0}}$ on 
 systems $A$ and $B$.
 \item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or
-$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
-\item Alice and Bob implement controlled unitary $V_0 \oplus V_1$ obtained from 
+$\Phi_{U^\dagger}$,  on part $A$ of the input state  $\ket{\psi_{0}}$.
+\item Alice and Bob implement  direct sum of unitary channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$ obtained from 
 Holevo--Helstrom theorem.	
@@
 $\DD \UU_d$. 
-	An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$.
-Whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
+	An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$, whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
 
@@
 There
-exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
-Jamio{\l}kowski isomorphism. 
-For a given linear mapping $\Phi_M$ corresponding  Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
-\begin{equation}
-\mathcal{J}(\Phi) \coloneqq \sum_{i,j=1}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
-Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
+exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $M_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism. 
+For a given linear mapping $\Phi$ the corresponding Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
+\begin{equation}
+\mathcal{J}(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
+We introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
 and trace preserving (CPTP).
-In this work we will consider a special class of quantum channels, called unitary channels. Let $U \in \UU_d$ be a unitary operator. A unitary channel
-$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
-\UU_d$. A general quantum
-measurement, that is a positive operator valued measure (POVM) $\PP$ is a
+In this work we will consider a special class of quantum channels, called unitary channels.  A 
+channel
+$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
+\UU_d$.
+
+Finally, we define a quantum
+measurement, that is a positive operator valued measure (POVM) denoted by $\PP, \mathcal{Q}$ etc. This is a 
 collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
-\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
-all the effects are rank-one projection operators, then such a measurement is
-called a von Neumann measurement. Every von Neumann measurement can be
-parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
-for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
-where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
+effects, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
+all effects are rank-one projection operators, then such a measurement is
+called a von Neumann measurement. 
+Every von Neumann measurement can be
+parameterized by a unitary matrix $U$ with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+where $\ket{u_i}$ is the $i$-th column of the unitary matrix $U$.  Hence we will use the notation $\PP_{U}$.  The action of
 quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
@@
 \PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-$
+$ Moreover, observe that each von Neumann measuement $\PP_{U}$ can be written as compostion of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
 
@@
 \end{equation}
-
-The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
+The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\Psi$  and $\Phi$, 
 in terms of their distance with the use of the diamond norm
 \begin{equation}
-p_{\text{succ}}(\TT, \SS) =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
-\end{equation}
-In the case of discrimination between two von Neumann measurements $\PP_U$ and 
-$\PP_\Id$ we know that (from Theorem 1 in \cite{puchala2018strategies})
+p_{\text{succ}}(\Psi, \Phi) =  \frac12 + \frac14 \| \Psi - \Phi \|_\diamond.
+\end{equation}
+from Theorem 1 in \cite{puchala2018strategies}, the distance between two von Neumann measurements $\PP_U$ and 
+$\PP_\Id$ is given by
 \begin{equation}
@@
 \end{equation}   
-is the numerical range of $A$.
+is called numerical range of $A$.
 The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.
 
- Let us now recall the well-known result for the
-distinguishability of unitary channels.
 	Let $U \in \UU_d$ and $\Phi_U$ be a unitary 
@@
 	\end{equation}
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. And hence the optimal probability to discriminate two unitary channel is given by 
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. Finally, the optimal probability to discriminate two unitary channel is given by 
 	\begin{equation}
@@
 subsection~\ref{sec:example_realization}. For such realization, we 
-will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
-and final measurement (see sec.~\ref{sec_example_final_measurement}).
+will need the optimal input state (see sec.~\ref{sec:example_discriminator}), 
+and the optimal final measurement (see sec.~\ref{sec_example_final_measurement}).
 
@@
 
-In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.
-To do that, we will present an auxiliary lemma.
-\begin{lemma}\label{lemma:min-e-optimal}
-Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
-$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds 
-\begin{equation}
-\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-\Phi_\Id\|_\diamond,
-\end{equation}
-\end{lemma}
-
-\begin{proof} Recall that the distance between two unitary channels is given by
-	$
-	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-	$
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$. 
-	For $U = H 
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
-	\begin{equation}
-	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |. 
-	\end{equation} 
-		It implies that it is enough to prove  \begin{equation}
-		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-		\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
-		\end{equation}
-%		It implies that we can prove  equivalently  the following condition
-%		\begin{equation}
-%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
-%		\end{equation}
-This condition is equivalent to 
-	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
-	\end{equation}
-	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
-
-%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
- The celebrated Hausdorf-T{\o}plitz theorem~\cite{hausdorff, toeplitz} states that
-$W(A)$ of any matrix $A \in M_d$ is a convex set and therefore
-\begin{equation}
-W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}. 
-\end{equation}
-So we obtain that 
-	\begin{equation}
-	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
-	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
-	\end{equation}
-	And then we have 
-	 \begin{equation}
- \max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
-		\Omega_2} \left| \tr \left( \rho U E \right) \right|
-	\end{equation}
-	For that, our task is reduce to show that
-	\begin{equation}
-	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \mu
-	\end{equation}
-	where $\mu \coloneqq \max_{E \in \diaguni_2 } \nu_{E}.$
-
-	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ 
-	and take $\rho = 
-	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
-	From spectral theorem, let us decompose $U$ as
-	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
-	\end{equation}
-	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
-	eigenvector is 
-	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
-	$.
-	Then, we have 
-	\begin{equation}
-	\begin{split}
-	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
-	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
-	\frac{1}{2} \left| \tr\left((   \proj{x_1} +e^{i \phi}\proj{x_2} ) E \right) 
-	\right|  = 
-	\frac{1}{2} \left|  \bra{x_1} E \ket{x_1} +  e^{i \phi}\bra{x_2} E \ket{x_2} 
-	\right| = \\& 
-	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| 
-	= 
-	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
-	\mu, 
-	\end{split}
-	\end{equation}
-	which completes the proof.
-\end{proof}
-\begin{theorem}
+\begin{theorem}\label{th:probability}
 The optimal probability of correct discrimination between von Neumann
@@
 
-\begin{proof}
-	From Holevo-Helstrom theorem we obtain
-	\begin{equation}
-p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
-	\end{equation}
-	From Theorem 1 in~\cite{puchala2018strategies} we have 
-	\begin{equation}
-	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond. 
-	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal} we know that for 
-	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
-	\begin{equation}
-		\min_{E \in \diaguni_2} \|\Phi_{UE} - 
-	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
-	\Phi_\Id\|_\diamond,
-	\end{equation} which is exactly equal to 
-	\begin{equation}
-	\|\Phi_{U} - 
-	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|. 
-	\end{equation}
-%	Finally, we obtain that
-%	\begin{equation}
-%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
-%	\end{equation}
-	It implies that
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
-	\end{equation} which completes the proof.
-\end{proof}
-
 \subsection{Realization}\label{sec:example_realization}
-Now we focus on the realization of the discrimination protocol. We will 
-discriminate between $\PP_U$ and $\PP_\1$. To do so, we need to know exact 
-forms of the input state and final measurement. We will indicate the optimal 
-input state in subsection~\ref{sec:example_discriminator} and the final 
-measurement in subsection~\ref{sec_example_final_measurement}.
+
+To indicate the optimal strategy  we will present two propositions.
+The first one is concentrated around the discriminator as the optimal input state of discrimination strategy, whereas the second one describes the optimal final measurement.
 
@@
 \begin{equation}
-\ket{\psi_{AB}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
+\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
 \end{equation}
@@
 
-\begin{proof}
-Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0, 
-2\pi)$ be decomposed as 
-	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
-	\end{equation}
-	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
-	eigenvector is 
-	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
-	$.
-
-For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
-\begin{equation}
-\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
-Hence, we obtain
-\begin{equation}
-\begin{split}
-\| \PP_{U} - \PP_{\Id}  \|_\diamond 
-& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
-\mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
-\\ 
-& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
-\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
-\right\|_1  \\ 
-& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
-\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
-\\ 
-& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
-\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
-\end{split}
-\end{equation}
-One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
-\ket{y}$ the following equation holds~\cite{watrous} 
-\begin{equation}
-\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
-\beta |\braket{x}{y}|^2}.
-\end{equation}
-By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
-\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
-\ket{i} \|}$ we have
-\begin{equation}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
-	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
-	}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
-\end{equation}
-Let us take  $\rho_0 =   \frac{1}{2}  	
-\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
-\begin{equation}
-\begin{split}
-||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
-&= \sum_{i=0}^1  
-\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
-	4|\bra{i}\rho_0\ket{u_i}|^2}  \\
-&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2} 
-\\ 
-&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1} 
-	\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
-&= \sum_{i=0}^1 
- \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
-= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
-&= |1-e^{i \phi }|.
-\end{split}
-\end{equation}
-Observe that
-\begin{equation}
-\begin{split}
-\| \PP_{U} - \PP_{\Id}  \|_\diamond  
-&=  \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
-\Id \otimes \sqrt{\rho} \right) \|_1 \\
-&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
-\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
-\end{split}
-\end{equation}
-Due to that, we know  
-that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ is the discriminator of the problem 
-of discrimination between 
-$\PP_{\Id} $ and $\PP_U$ for 
-$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
-).      Hence we obtain that \begin{equation}
-\ket{\psi_{AB}} \coloneqq   | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
-\Id_2 \rangle \rangle,
-\end{equation}
-which completes the proof.
-\end{proof}
-
-%
-%
-%\begin{remark}\label{lemma:rho}
-%	Let $\rho_{0} = \frac{1}{2} 
-%	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)$. Then 
-%	\begin{equation}
-%	 \max_\rho \left\|(\1\otimes \sqrt{\rho}) J(\PP_U - \PP_{\Id}) 
-%	(\1\otimes 
-%	\sqrt{\rho})\right\|_1 =    \left\|(\1\otimes \sqrt{\rho_0}) J(\PP_U - 
-%	\PP_{\Id}) 
-%		(\1\otimes 
-%		\sqrt{\rho_0})\right\|_1
-%	\end{equation}
-%	for  $U = H\diag(1, e^{i \phi}) H^\dagger $, 
-%		where $\phi \in [0, 2\pi)$. 
-%\end{remark}
-
 \subsubsection{Conditional measurement}\label{sec_example_final_measurement}
-In this subsection we will derive exact form of the conditional measurement in the
-problem of discrimination of von Neumann measurements $\PP_U$ and $\PP_{\Id}$
-for $U = H \diag(1, e^{i \phi}) H^\dagger$, where $\phi \in [0, 2\pi)$.
-
-\begin{proposition}
+
+\begin{proposition}\label{prop:optimal-measurement}
 	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
@@
 \mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{0} V_1^\dagger  \\ 
+\proj{0} V_1^\dagger,  \\ 
 \mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
@@
 \end{equation}
+and
 \begin{equation}
@@
 \end{proposition}
-
-\begin{proof}
-From Proposition~\ref{prop-discrim} we have the form of discriminator given by
-\begin{equation}
-\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
-\rangle \rangle. 
-\end{equation}
-From Holevo-Helstrom theorem  we constrain a conditional measurement $\mu$.  
-Let us define 
-\begin{equation}
-X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
-\otimes \Id_2 \right)(\proj{\psi}).
-\end{equation} 
-From the Hahn-Jordan decomposition, let us note
-\begin{equation}
-X = P - Q
-\end{equation}
-where $P, Q \ge 0 $. 
-Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
-respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
-\begin{equation}
-\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
-\end{equation}
-and 
-\begin{equation}
-\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
-\end{equation}
-Hence, we define $V_0$ such that
-\begin{equation}
-\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
-\end{equation}
-and $V_1$ such that
-\begin{equation}
-\begin{cases} 
-V_1 \ket{y_p} = \ket{0} \\ 
-V_1 \ket{y_q} = \ket{1}
-\end{cases}. 
-\end{equation}
-For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
-\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
-follows (see also \texttt{one-qubit.nb}).
-The unitary $V_0$ has the form
-\begin{equation}
-V_0 = \left(
-\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
-\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
-\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
-\end{array}
-\right),
-\end{equation}
-whereas the unitary  $V_1$  has the form
-\begin{equation}
-V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
-\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
-\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right)
-\end{equation}
-for all $\phi \in [0,2\pi)$. 
-Finally, we obtain the measurement $\mu$ of the form
-\begin{equation}
-\begin{split}
-\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{0} V_1^\dagger  \\ 
-\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{1} V_1^\dagger.  
-\end{split}
-\end{equation}
-
-\end{proof}
 
@@
 
+\appendix
+\section{Optimal probability}
+
+In this Appendix we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.
+To do that, we will present an auxiliary lemma.
+\begin{lemma}\label{lemma:min-e-optimal}
+	Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
+	$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds 
+	\begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
+	\Phi_\Id\|_\diamond,
+	\end{equation}
+\end{lemma}
+
+\begin{proof} Recall that the distance between two unitary channels is given by
+	$
+	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
+	$
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$. 
+	For $U = H 
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So, 
+	\begin{equation}
+	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |. 
+	\end{equation} 
+	It implies that it is enough to prove  \begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
+	\end{equation}
+	%		It implies that we can prove  equivalently  the following condition
+	%		\begin{equation}
+	%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
+	%		\end{equation}
+	This condition is equivalent to 
+	\begin{equation}
+	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
+	\end{equation}
+	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
+
+	%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
+	The celebrated Hausdorf-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
+	$W(A)$ of any matrix $A \in M_d$ is a convex set and therefore
+	\begin{equation}
+	W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}. 
+	\end{equation}
+	So, we obtain that 
+	\begin{equation}
+	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| = 
+	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|. 
+	\end{equation}
+	Then, we have 
+	\begin{equation}
+	\max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in 
+		\Omega_2} \left| \tr \left( \rho U E \right) \right|.
+	\end{equation}
+	For that, our task is reduced to show that
+	\begin{equation}
+	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \mu,
+	\end{equation}
+	where $\mu \coloneqq \max_{E \in \diaguni_2 } \nu_{E}.$
+
+	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $ 
+	and take $\rho = 
+	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $. 
+	From spectral theorem, let us decompose $U$ as
+	\begin{equation}
+	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
+	\end{equation}
+	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
+	eigenvector is 
+	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	$,
+	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
+	$.
+	Then, we have 
+	\begin{equation}
+	\begin{split}
+	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
+	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
+	\frac{1}{2} \left| \tr\left((   \proj{x_1} +e^{i \phi}\proj{x_2} ) E \right) 
+	\right|  = 
+	\frac{1}{2} \left|  \bra{x_1} E \ket{x_1} +  e^{i \phi}\bra{x_2} E \ket{x_2} 
+	\right| = \\& 
+	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right| 
+	= 
+	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
+	\mu, 
+	\end{split}
+	\end{equation}
+	which completes the proof.
+\end{proof}
+\begin{proof}[Proof of Theorem~\ref{th:probability}]
+	From Holevo-Helstrom theorem we obtain
+	\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
+	\end{equation}
+	From Theorem 1 in~\cite{puchala2018strategies} we have 
+	\begin{equation}
+	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond. 
+	\end{equation}
+	From Lemma~\ref{lemma:min-e-optimal} we know that for 
+	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
+	\begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
+	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
+	\Phi_\Id\|_\diamond,
+	\end{equation} which is exactly equal to 
+	\begin{equation}
+	\|\Phi_{U} - 
+	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|. 
+	\end{equation}
+	%	Finally, we obtain that
+	%	\begin{equation}
+	%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
+	%	\end{equation}
+	It implies that
+	\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
+	\end{equation} which completes the proof.
+\end{proof}
+
+\section{Optimal discrimination strategy}
+In this Appendix we present proofs of Proposition~\ref{prop-discrim} and Proposition~\ref{prop:optimal-measurement} to indicate the optimal discrimination strategy.
+\begin{proof}[Proof of Proposition~\ref{prop-discrim}]
+	Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0, 
+	2\pi)$ be decomposed as 
+	\begin{equation}
+	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
+	\end{equation}
+	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
+	eigenvector is 
+	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	$,
+	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
+	$.
+	For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
+	\begin{equation}
+	\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
+	Hence, we obtain
+	\begin{equation}
+	\begin{split}
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond 
+	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
+	\mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
+	\\ 
+	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
+	\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
+	\right\|_1  \\ 
+	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
+	\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
+	\\ 
+	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
+	\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
+	\end{split}
+	\end{equation}
+	One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
+	\ket{y}$ the following equation holds~\cite{watrous} 
+	\begin{equation}
+	\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
+		\beta |\braket{x}{y}|^2}.
+	\end{equation}
+	By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
+		\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
+		\ket{i} \|}$ we have
+	\begin{equation}
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
+	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
+		}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
+	\end{equation}
+	Let us take  $\rho_0 =   \frac{1}{2}  	
+	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
+	\begin{equation}
+	\begin{split}
+	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
+	&= \sum_{i=0}^1  
+	\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
+		4|\bra{i}\rho_0\ket{u_i}|^2}  \\
+	&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2} 
+	\\ 
+	&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1} 
+		\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
+	&= \sum_{i=0}^1 
+	\sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
+	= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
+	&= |1-e^{i \phi }|.
+	\end{split}
+	\end{equation}
+	Observe that
+	\begin{equation}
+	\begin{split}
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond  
+	&=  \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
+	\Id \otimes \sqrt{\rho} \right) \|_1 \\
+	&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
+	\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
+	\end{split}
+	\end{equation}
+	Due to that, we know  
+	that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ is the discriminator of the problem 
+	of discrimination between 
+	$\PP_{\Id} $ and $\PP_U$ for 
+	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm).      Hence, we obtain that \begin{equation}
+	\ket{\psi_{AB}} \coloneqq   | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
+	\Id_2 \rangle \rangle,
+	\end{equation}
+	which completes the proof.
+\end{proof}
+
+\begin{proof}[Proof of Proposition~\ref{prop:optimal-measurement}]
+	From Proposition~\ref{prop-discrim} we obtain the exact form of discriminator given by
+	\begin{equation}
+	\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
+	\rangle \rangle. 
+	\end{equation}
+	From Holevo-Helstrom theorem  we constrain a conditional measurement $\mu$.  
+	Let us define 
+	\begin{equation}
+	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
+	\otimes \Id_2 \right)(\proj{\psi}).
+	\end{equation} 
+	From the Hahn-Jordan decomposition, let us note
+	\begin{equation}
+	X = P - Q
+	\end{equation}
+	where $P, Q \ge 0 $. 
+	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
+	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
+	\begin{equation}
+	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
+	\end{equation}
+	and 
+	\begin{equation}
+	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
+	\end{equation}
+	Hence, we define $V_0$ as
+	\begin{equation}
+	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
+	\end{equation}
+	and $V_1$ as
+	\begin{equation}
+	\begin{cases} 
+	V_1 \ket{y_p} = \ket{0} \\ 
+	V_1 \ket{y_q} = \ket{1}
+	\end{cases}. 
+	\end{equation}
+	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
+	\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
+	follows \todo[inline]{udostepniamy ten plik nb?}(see also \texttt{one-qubit.nb}).
+	The unitary $V_0$ has the form
+	\begin{equation}
+	V_0 = \left(
+	\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
+	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
+		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
+	\end{array}
+	\right),
+	\end{equation}
+	whereas the unitary  $V_1$  has the form
+	\begin{equation}
+	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
+	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
+	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right),
+	\end{equation}
+	for all $\phi \in [0,2\pi)$. 
+	Finally, we obtain the measurement $\mu$ of the form
+	\begin{equation}
+	\begin{split}
+	\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
+	\proj{0} V_1^\dagger, \\ 
+	\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
+	\proj{1} V_1^\dagger.  
+	\end{split}
+	\end{equation} 
+\end{proof}
+
 \end{document}

### 2022-12-12 txt/rigetti.tex
creating appendix and rewriting mathemaytical prelimaties and parametrized family

@@
 	setup is shown in Fig.~\ref{fig:theoretical}.
-\begin{figure}[h!]
-	\centering 
-	\includegraphics[width=0.75\linewidth, angle=-90]{rys-theoretical.jpg}
 
-	\caption{ A schematic representation of the setup for distinguishing
-		measurements using entangled states. One of two known measurements 
-		$\mathcal{P}_U$
-		or $\PP_\Id$ is performed on part $A$ of the input state $\ket{\psi}$. 
-		We use
-		the output label $i$ and perform a conditional binary measurement
-		$\mathcal{P}_{V_i}$ on part $B$. By the use of its output we formulate 
-		our guess, 
-		that is we decide  
-		weather
-		the measurement performed on part $A$ was $\mathcal{P}_U$ or 
-		$\PP_\Id$. In out approach, if  $ j = 0$ we decide  $\PP_U$, if
-		$j = 1$ we decide $\PP_{\Id}$. 
-	}\label{fig:theoretical}
-\end{figure} 
 From ~\cite{puchala2018strategies}(Proposition 4) and Lemma~\ref{lemma:rho} we 
@@
 
-\begin{figure}[h!]
-	\centering 
-	\includegraphics[width=0.75\linewidth, angle=-90]{rys-postsellection.jpg}
-
-	\caption{ A schematic representation of the setup for distinguishing
-		measurements using postselection. 
-	}\label{fig:postsellection}
-\end{figure}
 \begin{enumerate}
@@
 \begin{scheme}(By using controlled unitary)
-\begin{figure}[h!]
-	\centering 
-	\includegraphics[width=0.75\linewidth, angle=-90]{rys-controlled.jpg}
 
-	\caption{ A schematic representation of the setup for distinguishing
-		measurements using controlled unitary gate. 
-	}\label{fig:controlled}
-\end{figure}
 \begin{enumerate}
@@
 
+PyQBench to biblioteka języka Python oraz narzędzie wiersza polecenia służące do testowania bramkowych komputerów kwantowych na podstawie ich zdolności do rozróżniania pomiędzy dwoma pomiarami von Neumanna w różnych bazach.
+Narzędzie wiersza polecenia pozwala na uruchomienie benchmarków wykorzystujących rozróżnianie między pomiarem w bazie obliczeniowej a pomiarem w bazie definiowanej przez sparametryzowaną rodzinę Fouriera.
+Użytkownik może wybierać, czy eksperyment zostanie przeprowadzony przy pomocy postselekcji czy alternatywnej metody “sumy prostej”, oraz kontrolować różne aspekty przeprowadzanego eksperymentu, takie jak liczba próbek używanych w samplowaniu, indeksy kubitów, zakresy kąta dla sparametryzowanej rodziny Fouriera.
+Jeżeli użytkownik chce użyć pomiaru w innej bazie, może wykorzystać PyQBench jako bibliotekę.
+Ten tryb użycia wymaga większego nakładu pracy, ale pozwala na rozszerzenie parametrów eksperymentu.
+Warto wspomnieć, że w przypadku backendów udostępniających informacje o kalibracji kubitów, PyQBench wspiera mitygację błędów metodą matrix-free measurement mitigation.
+ Jednym z testowanych komputerów kwantowych był IBMQ, na którym wykonywane zostały eksperymenty na podstawie benchmarku rozróżniania pomiarów von Neumanna. 
+Obecnie opracowujemy zebrane wyniki.
+Biblioteka PyQBench będzie otwartym oprogramowaniem (ang. open source). Niebawem również zostanie wysłany artykuł do publikacji w czasopiśmie.  
 \section*{Acknowledgments}

### 2022-12-12 txt/manuscript.tex
drobnostki

@@
 the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
-$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
-will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
-matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
+$M_d$.  
+%The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
+%will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
+%matrices of dimension $d$ by $\HH_d^+$. 
+The set of quantum states, that is
 positive semidefinite operators having trace equal to one, will be denoted
@@
 	\begin{split}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond  
-	&=  \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
-	\Id \otimes \sqrt{\rho} \right) \|_1 \\
-	&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
+ \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
+	\Id \otimes \sqrt{\rho} \right) \|_1 = \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
 	\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
@@
 	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm).      Hence, we obtain that \begin{equation}
-	\ket{\psi_{AB}} \coloneqq   | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
+	\ket{\psi_{0}} \coloneqq   | \sqrt{\rho_0}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
 	\Id_2 \rangle \rangle,
@@
 	\begin{equation}
-	\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
+	\ket{\psi_0} = | \sqrt{\rho_0}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
 	\rangle \rangle. 
@@
 	\begin{equation}
-	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
-	\otimes \Id_2 \right)(\proj{\psi}).
+	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id 
+	\otimes \Id_2 \right)(\proj{\psi_0}).
 	\end{equation} 

### 2022-12-21 txt/manuscript.tex
writing.....
Fix PACS numbers
Remove instructions from "Current code version"
delete caes

@@
 
-\subsection{IBMQ and Lucy}
-
-\subsection{IBMQ}
- basis gates = ["cx", "i", "rz", "sx", "x"]
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-ibmq}
-\caption{Circuit representing state preparation for IBMQ.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-ibmq}
-\caption{Circuit representing $U^\dagger$ for IBMQ.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-ibmq}
-\caption{Circuit representing $V_0^\dagger$ for IBMQ.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
-\caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
-\end{figure}
-
 \subsection{Lucy}
  basis gates  =["ecr", "i", "rz", "sx", "x"]
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-lucy}
-\caption{Circuit representing state preparation for Lucy.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-lucy}
-\caption{Circuit representing $U^\dagger$ for Lucy.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-lucy}
-\caption{Circuit representing $V_0^\dagger$ for Lucy.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
-\caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
-\end{figure}
 
@@
  basis gates = ["cz", "rx", "rz"]
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-rigetti}
-\caption{Circuit representing state preparation for Rigetti.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-rigetti}
-\caption{Circuit representing $U^\dagger$ for Rigetti.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-rigetti}
-\caption{Circuit representing $V_0^\dagger$ for Rigetti.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
-\caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}
-\end{figure}
 
@@
 \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$. In 
-%this simplest case,  we consider two von Neumann measurements $\PP_\1$ and 
-%$\PP_U$ for $U = H diag(0,\ee^{\ii \phi}) H$, where $H_d$--Hadamard matrix 
-%of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected 
-%probability $p_{success}$ of correct distinction between two measurements 
-%$\PP_\1$ and $\PP_U$  is given by
-%\begin{equation}
-%p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = 
-%\frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
-%\end{equation}
-%by the assumption the discriminator is on the form $\ket{\psi} = 
-%\frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
-%(tu wyniki z rigettiego...)
 
@@
 	\begin{equation}
-	\ket{\psi_0} = | \sqrt{\rho_0}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
+	\ket{\psi_0}  = \frac{1}{\sqrt{2}} |\Id_2 
 	\rangle \rangle. 

### 2022-12-21 txt/manuscript.tex
Update metadata

--- 2022-12-12 txt/manuscript.tex
@@
 \newcommand{\tr}{\mathrm{tr}}
+\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}
 \journal{SoftwareX}
@@
 
-%\PACS 03.67.−a \sep 03.67.Lx
+\PACS 03.67.-a \sep 03.67.Lx
 
@@
 
-Ancillary data table required for subversion of the codebase. Kindly replace 
-examples in right column with the correct information about your current code, 
-and leave the left column as it is.
-
 \begin{table}[H]
@@
 \hline
-C1 & Current code version & For example v42 \\
-\hline
-C2 & Permanent link to code/repository used for this code version & For 
-example: $https://github.com/mozart/mozart2$ \\
+C1 & Current code version & 0.1.0 \\
+\hline
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/iitis/PyQBench} \\
 \hline
@@
 \hline
-C4 & Legal Code License   & List one of the approved licenses \\
-\hline
-C5 & Code versioning system used & For example svn, git, mercurial, etc. put 
-none if none \\
-\hline
-C6 & Software code languages, tools, and services used & For example C++, 
-python, r, MPI, OpenCL, etc. \\
-\hline
-C7 & Compilation requirements, operating environments \& dependencies & \\
+C4 & Legal Code License & Apache License 2.0\\
+\hline
+C5 & Code versioning system used & git \\
+\hline
+C6 & Software code languages, tools, and services used & Python, Qiskit, AWS Braket \\
+\hline
+C7 & Compilation requirements, operating environments \& dependencies & 
+\texttt{Python >= 3.8}\newline
+\texttt{amazon-braket-sdk \textapprox= 1.33.0}\newline
+\texttt{numpy \textapprox= 1.14.5}\newline
+\texttt{scipy \textapprox= 1.7.3}\newline
+\texttt{pandas \textapprox= 1.5.0}\newline
+\texttt{pydantic \textapprox= 1.9.0}\newline
+\texttt{qiskit \textapprox= 0.39.0}\newline
+\texttt{mthree \textapprox= 1.1.0}\newline
+\texttt{tqdm \textapprox= 4.64.1}\newline
+\texttt{pyyaml \textapprox= 6.0}\\
 \hline
@@
 \hline
-C9 & Support email for questions & \\
+C9 & Support email for questions & \url{dexter2206@gmail.com}\\
 \hline

### 2022-12-21 txt/manuscript.tex
ack

@@
 
-\section*{Required Metadata}
-\label{}
-
 \section*{Current code version}
@@
 \hline
-C3 & Code Ocean compute capsule & For example: 
-$https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
+C3 & Code Ocean compute capsule & ?????????\\
 \hline
@@
 \hline
-C8 & If available Link to developer documentation/manual & For example: 
-$http://mozart.github.io/documentation/$ \\
+C8 & If available Link to developer documentation/manual & ?????\\
 \hline
@@
 
-The permanent link to code/repository or the zip archive should include the 
-following requirements:
-
-README.txt and LICENSE.txt.
-
-Source code in a src/ directory, not the root of the repository.
-
-Tag corresponding with the version of the software that is reviewed.
-
-Documentation in the repository in a docs/ directory, and/or READMEs, as 
-appropriate.
+%The permanent link to code/repository or the zip archive should include the 
+%following requirements: 
+%
+%README.txt and LICENSE.txt.
+%
+%Source code in a src/ directory, not the root of the repository.
+%
+%Tag corresponding with the version of the software that is reviewed.
+%
+%Documentation in the repository in a docs/ directory, and/or READMEs, as 
+%appropriate.
 
 \section{Motivation and significance}
+
+\todo[inline]{In particular, we compile circuits to standard gate sets of the vendor using compiler RECZNEGO?, and we perform experiments across different qubit subsets.}
+
+quantum volume - '' has become the de-facto standard benchmark to quantify the capability of Noisy Intermediate-Scale Quantum (NISQ) devices '' \cite{pelofske2022volume}
 
@@
 architectures. Historically, the first widely introduced quantum computing
-architecture is D-Wave's quantum annealer~\cite{}.
-
-https://quantumcomputingreport.com/scorecards/qubit-technology/
+architecture is D-Wave's quantum annealer.
 
@@
 
+This software has two main contributions.
+
 \textbf{This is the main section of the article and the reviewers weight the 
@@
 
-Set out the conclusion of this original software publication.
-
+In this study, we develop  a Python library PyQBench, an innovative open-source framework for benchmarking 
+gate-based quantum computers.
+
+%%%%%%%%%%%%%% 
+PyQBench can benchmark NISQ devices by verifying their capability of
+discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
+command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
+family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
+measurements instead of predefined ones.
 \section{Conflict of Interest}
-Please select the appropriate text:
-
-Potential conflict of interest exists:
-We wish to draw the attention of the Editor to the following facts, which may 
-be considered as potential conflicts of interest, and to significant financial 
-contributions to this work. The nature of potential conflict of interest is 
-described below: [Describe conflict of interest]
-
-No conflict of interest exists:
-We wish to confirm that there are no known conflicts of interest associated 
-with this publication and there has been no significant financial support for 
-this work that could have influenced its outcome.
+No conflict of interest exists: We wish to confirm that there are no known
+conflicts of interest associated with this publication and there has been no
+significant financial support for this work that could have influenced its out-
+come.
 
@@
 
-This work was supported by the Foundation for Polish Science (FNP) under grant
-number POIR.04.04.00-00-17C1/18-00.
+This work is  supported by
+the project “Near-term quantum computers Challenges, optimal implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the Team-Net programme of the Foundation for Polish Science co-financed by the European Union under the European Regional Development Fund.
+PL is also a holder of European Union scholarship through the European Social Fund, 
+grant InterPOWER (POWR.03.05.00-00-Z305).
 
@@
 \bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
+
+\bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
 \end{thebibliography}

### 2023-01-01 txt/maths.tex
preliminaries

@@
 \begin{eqnarray}
-	N_{\PP_U} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_U, k = i, j = 0\} \\
-	N_{\PP_\Id} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_\Id, k = i, j = 1\}
+	N_{\PP_U} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_U, k = i, j = 0\}, \\
+	N_{\PP_\Id} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_\Id, k = i, j = 1\},
 \end{eqnarray}
@@
 
-\begin{scheme}(By using controlled unitary)
+\begin{scheme}(By using direct sum)
 
@@
 system.
-\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
-$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
-\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
+%\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
+%$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
+\item We apply one of unitary,   either $U^\dagger$ or
+$\Id$, on  the first system. 
+%\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
 Observe that   $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger} = \proj{0} \otimes \Phi_{V_0^\dagger}  + \proj{1} \otimes \Phi_{V_1^\dagger}.
 $
-\item We measure all systems in computational basis $\Delta$.
+\item We apply direct sum $V_0^\dagger \oplus V_1^\dagger$ on the whole systems. 
+\item We measure both  systems in computational basis $\Delta$.
 \item We make a decision based on received label $j$ on the second system. If $j=0$, then we
@@
 
-Here, we consider the following circuits
-by using controlled unitary
+In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where $\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$.
+The number of successful trials for $U$ and $\Id$, respectively, can be written  as
+\begin{eqnarray}
+N_{\PP_U} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_U, j = 0\}, \\
+N_{\PP_\Id} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_\Id, j = 1\}. 
+\end{eqnarray}
+Then, the probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is given by
 \begin{equation}
-\begin{split}
-(\Phi_{U^\dagger}, \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j) \\
-(\Phi_{\Id},  \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j)
-\end{split}
+p_{\text{succ}} = \frac{N_{\PP_{U}} + N_{\PP_{\Id}}}{N_{\text{total}}},
 \end{equation}
-where $i=\{0,1\}$ and $ j=\{0,1\}$.
-Then, the optimal probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows.
-\begin{equation}
-p = \frac{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,0) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,1) }{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j)}
-\end{equation}
-where $i=\{0,1\}$ and $ j=\{0,1\}$.
+where $N_{\text{total}}$ is the number of trials. 
 \end{scheme}
@@
 \subsubsection{Mathematical preliminaries}
-
-In this and the following sections we will denote complex Euclidean spaces $\mathbb{C}^d$ with $\XX, \mathcal{Y}$ etc.
-When needed the dimension of a space $\XX$ will be denoted $\dim(\XX)$.
-The set of matrices transforming vectors from $\XX$ to $\mathcal{Y}$ will be denoted $\mathrm{L}(\XX, \mathcal{Y})$.
- We will also need a linear mapping transforming $\mathrm{L}(\XX)$ into
-$\mathrm{L}(\mathcal{Y})$, which will be denoted
-\begin{equation}
-\Phi: \mathrm{L}(\XX) \rightarrow \mathrm{L}(\mathcal{Y}).
-\end{equation}
-There
-exists a bijection between introduced linear mappings $\Phi$ and set of matrices $\mathrm{L}(\mathcal{Y} \otimes \mathcal{X})$,  known as the Choi-
-Jamio{\l}kowski isomorphism.
-For a given linear mapping $\Phi$ the corresponding  Choi operator $J(\Phi)$ is explicitly written as
-\begin{equation}
-J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
-Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
-and trace preserving (CPTP).
-We will consider a special class of quantum channels, called unitary channels. A unitary channel
-$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  and unitary $U$.
 

### 2023-01-01 txt/maths.tex
Update math.tex

@@
 
+\subsubsection{Notation and some preliminaries}
+
+Recall that a general quantum
+measurement, that is a positive operator valued measure (POVM) $\PP$ is a
+collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
+\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$.
+In PyQBench, we are interested only in von Neumann measurements, i.e. measurements
+for which all the effects are rank-one projectors. Every such measurement can be
+parameterized by a unitary matrix $U$ which the effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+are created by taking $\ket{u_i}$ as  $i+1$-th column of the unitary matrix $U$.
+We will denote von Neumann measurements described by the matrix $U$ by $\PP_{U}$.
+
+Typically, NISQ devices can only perform measurements in computational $Z$-basis.
+To perform an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$
+to the measured system and then follow with $Z$-basis measurement. Hence, the following two
+circuits are equivalent.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1.7]{pics/vonneuman}
+	\caption{Decomposition of von Neumann measurement}
+	\label{fig:vonnneuman}
+\end{figure}
+
+Note that the decomposition above is basically a change of basis in which the measurement
+is performed.
+
 \subsubsection{Discrimination scheme}
@@
 \item We measure both systems in computational basis $\Delta$.
-\item We make a decision based on received label $j$ on the second system. If $j=0$, then we
+\item We make a decision based on the received label $j$ on the second system. If $j=0$, then we
 decide that $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs.
@@
 
-A general quantum
-measurement, that is a positive operator valued measure (POVM) $\PP$ is a
-collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
-\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
-all the effects are rank-one projection operators, then such a measurement is
-called a von Neumann measurement. Every von Neumann measurement can be
-parameterized by a unitary matrix $U$ which the effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
-ale creating by taking $\ket{u_i}$ as  $i+1$-th column of the unitary matrix $U$.
-Hence, we will use the notation $\PP_{U}$.
 %
@@
 
-\section{Illustrative Example}
+\subsubsection{Example of computing optimal measurements and discriminator}
 
-Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
-Assume that the unitary matrix $U$ is of the form
+So far, we only discussed how the discrimination is performed using two different
+schemes, assuming, that all needed components ($V_0$, $V_1$,$\ket{\psi_0}$) are known.
+In this section, we will show how all the necessary ingredients look like for
+von Neumann measurements defined by the parametrized Fourier family:
+
 \begin{equation}
@@
 \end{equation}
-%\begin{equation}
-%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
-%\end{equation}
+
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
 
-\subsubsection{Probability}\label{sec:example_probability}
 \begin{theorem}
@@
 
-\subsubsection{Discriminator}\label{sec:example_discriminator}
-
 \begin{proposition}\label{prop-discrim}
@@
 \end{proposition}
-
-%
 

### 2023-01-01 txt/maths.tex
prelinria done

@@
 
-\subsubsection{Mathematical preliminaries}
-
-%
-%
-% The action of
-%quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
-%seen as  a measure-and-prepare quantum channel as follows
-%$
-%\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-%$
-
-\subsubsection{Diamond norm and the task of discrimination between quantum operators}
-This section defines a special norm on the space of linear mappings, known as
-the diamond norm, and establishes some of its properties.
-Next, we will explain the precise connection between the diamond
-norm and the task of quantum operation discrimination.
-
-We define the diamond norm of a map $\Phi$ as
-\begin{equation}
-\|\Phi\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left(\Phi \otimes \1\right) (\proj{\psi}) \|_1.
-\end{equation}
-The quantum state $\ket{\psi}$ which maximizes the diamond norm we will call as discriminator.
+\subsubsection{Optimal discrimination scheme}
 
@@
 \begin{equation}
-p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond.
+p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond, 
 \end{equation}
+where 
+\begin{equation}
+\|\PP\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left(\PP \otimes \1\right) (\proj{\psi}) \|_1.
+\end{equation}
+The quantum state $\ket{\psi}$ which maximizes the diamond norm is called as discriminator.
 
-\subsubsection{Example of computing optimal measurements and discriminator}
+Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is possible to construct the necessary components  ($\ket{\psi_0}$, $V_0$, $V_1$) to create the optimal discrimination strategy.
+
+\subsubsection{Discrimination scheme for parameterized Fourier family}
 
 So far, we only discussed how the discrimination is performed using two different
-schemes, assuming, that all needed components ($V_0$, $V_1$,$\ket{\psi_0}$) are known.
-In this section, we will show how all the necessary ingredients look like for
-von Neumann measurements defined by the parametrized Fourier family:
+schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known.
+While the determination of $V_0$ and $V_1$ is a simple task provided the discriminator $\ket{\psi_{0}}$ is known, it turns out,
+sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
+is, in general, NP-hard problem. 
+We have found the analytical solution of the discrimination scheme for a particular class of von Neumann measurements.
+
+Here,  we will show how all the necessary ingredients look like for
+von Neumann measurements defined by the parameterized Fourier family:
 
@@
 	U = H
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger, 
 \end{equation}
-
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
@@
 
-\subsubsection{Conditional binary measurement/Optimal measurement}\label{sec_example_final_measurement}
-
 \begin{proposition}
@@
 \mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1
-\proj{0} V_1^\dagger  \\
+\proj{0} V_1^\dagger,   \\
 \mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1

### 2023-01-04 txt/maths.tex
merge ...

--- 2023-01-01 txt/maths.tex
@@
 We have two possible choices here: using a postselection or a direct sum
-$V_0^\dagger\oplus V_1^\dagger$.
+$\Phi_{V_0^\dagger}\oplus \Phi_{V_1^\dagger}$.
 
@@
 
-\begin{scheme}(By using direct sum)
+\begin{scheme}(By using controlled unitary)
 
@@
 system.
-%\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
-%$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
-\item We apply one of unitary,   either $U^\dagger$ or
-$\Id$, on  the first system. 
-%\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
+\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
+$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
+\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
 Observe that   $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger} = \proj{0} \otimes \Phi_{V_0^\dagger}  + \proj{1} \otimes \Phi_{V_1^\dagger}.
 $
-\item We apply direct sum $V_0^\dagger \oplus V_1^\dagger$ on the whole systems. 
-\item We measure both  systems in computational basis $\Delta$.
+\item We measure all systems in computational basis $\Delta$.
 \item We make a decision based on received label $j$ on the second system. If $j=0$, then we
@@
 
-In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where $\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$.
-The number of successful trials for $U$ and $\Id$, respectively, can be written  as
-\begin{eqnarray}
-N_{\PP_U} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_U, j = 0\}, \\
-N_{\PP_\Id} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_\Id, j = 1\}. 
-\end{eqnarray}
-Then, the probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is given by
+Here, we consider the following circuits
+by using controlled unitary
 \begin{equation}
-p_{\text{succ}} = \frac{N_{\PP_{U}} + N_{\PP_{\Id}}}{N_{\text{total}}},
+\begin{split}
+(\Phi_{U^\dagger}, \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j) \\
+(\Phi_{\Id},  \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j)
+\end{split}
 \end{equation}
-where $N_{\text{total}}$ is the number of trials. 
+where $i=\{0,1\}$ and $ j=\{0,1\}$.
+Then, the optimal probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows.
+\begin{equation}
+p = \frac{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,0) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,1) }{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j)}
+\end{equation}
+where $i=\{0,1\}$ and $ j=\{0,1\}$.
 \end{scheme}
@@
 \subsubsection{Mathematical preliminaries}
+
+In this and the following sections we will denote complex Euclidean spaces $\mathbb{C}^d$ with $\XX, \mathcal{Y}$ etc.
+When needed the dimension of a space $\XX$ will be denoted $\dim(\XX)$.
+The set of matrices transforming vectors from $\XX$ to $\mathcal{Y}$ will be denoted $\mathrm{L}(\XX, \mathcal{Y})$.
+ We will also need a linear mapping transforming $\mathrm{L}(\XX)$ into
+$\mathrm{L}(\mathcal{Y})$, which will be denoted
+\begin{equation}
+\Phi: \mathrm{L}(\XX) \rightarrow \mathrm{L}(\mathcal{Y}).
+\end{equation}
+There
+exists a bijection between introduced linear mappings $\Phi$ and set of matrices $\mathrm{L}(\mathcal{Y} \otimes \mathcal{X})$,  known as the Choi-
+Jamio{\l}kowski isomorphism.
+For a given linear mapping $\Phi$ the corresponding  Choi operator $J(\Phi)$ is explicitly written as
+\begin{equation}
+J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
+Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
+and trace preserving (CPTP).
+We will consider a special class of quantum channels, called unitary channels. A unitary channel
+$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  and unitary $U$.
 
@@
 \mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1
-\proj{0} V_1^\dagger  \\
+\proj{0} V_1^\dagger,  \\
 \mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1

### 2023-01-04 txt/rigetti.tex
merge ...

--- 2022-06-23 txt/rigetti.tex
@@
 \end{scheme}
-
+%
+%
+%
+%PyQBench to biblioteka języka Python oraz narzędzie wiersza polecenia służące do testowania bramkowych komputerów kwantowych na podstawie ich zdolności do rozróżniania pomiędzy dwoma pomiarami von Neumanna w różnych bazach.
+Narzędzie wiersza polecenia pozwala na uruchomienie benchmarków wykorzystujących rozróżnianie między pomiarem w bazie obliczeniowej a pomiarem w bazie definiowanej przez sparametryzowaną rodzinę Fouriera.
+Użytkownik może wybierać, czy eksperyment zostanie przeprowadzony przy pomocy postselekcji czy alternatywnej metody “sumy prostej”, oraz kontrolować różne aspekty przeprowadzanego eksperymentu, takie jak liczba próbek używanych w samplowaniu, indeksy kubitów, zakresy kąta dla sparametryzowanej rodziny Fouriera.
+Jeżeli użytkownik chce użyć pomiaru w innej bazie, może wykorzystać PyQBench jako bibliotekę.
+Ten tryb użycia wymaga większego nakładu pracy, ale pozwala na rozszerzenie parametrów eksperymentu.
+Warto wspomnieć, że w przypadku backendów udostępniających informacje o kalibracji kubitów, PyQBench wspiera mitygację błędów metodą matrix-free measurement mitigation.
+% Jednym z testowanych komputerów kwantowych był IBMQ, na którym wykonywane zostały eksperymenty na podstawie benchmarku rozróżniania pomiarów von Neumanna. 
+%Obecnie opracowujemy zebrane wyniki.
+%Biblioteka PyQBench będzie otwartym oprogramowaniem (ang. open source). Niebawem również zostanie wysłany artykuł do publikacji w czasopiśmie.  
 \section*{Acknowledgments}

### 2023-01-04 txt/maths.tex
maths
maths ended

--- 2023-01-01 txt/maths.tex
@@
 \begin{equation}
-	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}
+	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}. 
 \end{equation}
@@
 The quantum state $\ket{\psi}$ which maximizes the diamond norm is called as discriminator.
-
 Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is possible to construct the necessary components  ($\ket{\psi_0}$, $V_0$, $V_1$) to create the optimal discrimination strategy.
@@
 schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known.
-While the determination of $V_0$ and $V_1$ is a simple task provided the discriminator $\ket{\psi_{0}}$ is known, it turns out,
+It turned out that the determination of $V_0$ and $V_1$ is a simple task while the discriminator $\ket{\psi_{0}}$ is known.
+However,
 sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
@@
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-
-\begin{theorem}
-The optimal probability of correct discrimination between von Neumann
-measurements $\PP_U$ and $\PP_{\Id}$ is given by
+In this case, the optimal input state is Bell state of the form
 \begin{equation}
-p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
+\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \ket{00} + \ket{11}.
 \end{equation}
-\end{theorem}
-
-\begin{proposition}\label{prop-discrim}
- The optimal input state has the form
-\begin{equation}
-\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
-\end{equation}
-\end{proposition}
-
-\begin{proposition}
-The  optimal measurement has the following form
-\begin{equation}
-\begin{split}
-\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1
-\proj{0} V_1^\dagger,   \\
-\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1
-\proj{1} V_1^\dagger,
-\end{split}
-\end{equation}
-where for each $\phi \in \mathbb{R}$ and  the unitaries $V_0$,  $V_1$
+And, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
 have the following form
@@
 \end{equation}
-\end{proposition}
+Finally, we have also calculated the theoretical probability of correct discrimination between von Neumann
+measurements $\PP_U$ and $\PP_{\Id}$ is given by
+\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
+\end{equation}
+More details and proofs of the construction's validity   we can find in the article \cite{}.
 

### 2023-01-30 txt/manuscript.tex
pyqbench as library done

@@
-\documentclass[preprint,12pt, a4paper]{elsarticle}
+\documentclass[preprint,12pt, a4paper, dvipsnames]{elsarticle}
 
@@
 \usepackage{lineno}
+\usepackage{listings}
 
@@
 
+\usepackage{xcolor}
+
+\usepackage{caption}
+\usepackage{subcaption}
+
+\definecolor{codegreen}{rgb}{0.25,0.93,0.31}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+%
+%\lstdefinestyle{mystyle}{
+%	backgroundcolor=\color{backcolour},   
+%	commentstyle=\color{codegreen},
+%	keywordstyle=\color{magenta},
+%	numberstyle=\tiny\color{codegray},
+%	stringstyle=\color{codepurple},
+%	basicstyle=\ttfamily\footnotesize,
+%	breakatwhitespace=false,         
+%	breaklines=true,                 
+%	captionpos=b,                    
+%	keepspaces=true,                 
+%	numbers=left,                    
+%	numbersep=5pt,                  
+%	showspaces=false,                
+%	showstringspaces=false,
+%	showtabs=false,                  
+%	tabsize=2
+%}
+%
+%\lstset{style=mystyle} 
+\lstset{frame=tb,
+	language=Python,
+	aboveskip=3mm,
+	belowskip=3mm,
+	showstringspaces=false,
+	columns=flexible,
+	basicstyle={\small\ttfamily},
+	numberstyle=\color{blue},
+	keywordstyle=\color{blue},
+	commentstyle=\color{PineGreen},
+	stringstyle=\color{ForestGreen},
+	breaklines=true,
+	breakatwhitespace=true,
+	tabsize=3,
+	escapeinside={@}{@},
+	literate=
+	{0}{{{\color{red}0}}}1
+	{1}{{{\color{red}1}}}1
+	{2}{{{\color{red}2}}}1
+	{3}{{{\color{red}3}}}1
+	{4}{{{\color{red}4}}}1
+	{5}{{{\color{red}5}}}1
+	{6}{{{\color{red}6}}}1
+	{7}{{{\color{red}7}}}1
+	{8}{{{\color{red}8}}}1
+	{9}{{{\color{red}9}}}1
+    {v0}{{{\color{black}v0}}}1 %% we can not style only numeric literals
+    {v1}{{{\color{black}v1}}}1
+}
 \restylefloat{table}
@@
 \hline
-C3 & Code Ocean compute capsule & ?????????\\
+C3 & Code Ocean compute capsule & \todo[inline]{???}\\
 \hline
@@
 \texttt{tqdm \textapprox= 4.64.1}\newline
-\texttt{pyyaml \textapprox= 6.0}\\
-\hline
-C8 & If available Link to developer documentation/manual & ?????\\
+\texttt{pyyaml \textapprox= 6.0} \todo[inline]{everything???}\\
+\hline 
+C8 & If available Link to developer documentation/manual & \todo[inline]{???}\\
 \hline
@@
 
+!!!!!!!
+
+Suppose we have access to a device performing one of the predefined von Neumann
+measurements, $\PP$ or $\QQ$. In PyQBench, we restrict ourselves to discriminating von Neumann measurements.
+This is because, unlike other measurement types, they can be implemented on actual hardware. While the $\PP$ and $\QQ$ are known, it is not known which of them is
+performed when the device executes. Based on the measurement outcome, you have to guess which
+measurement was performed (but you can perform arbitrary unitary operations before and after the
+measurement). What is the highest probability of making a correct guess? And what do you have to do
+to achieve it? And, most importantly, why would we want to do this?
+
+Suppose that you know a strategy that, for an ideal device, would yield a probability
+$p_{\text{succ}}$ of successfully discriminating between two measurements. Will the probability be
+the same on an actual physical device? For current, Noisy Intermediate Scale Quantum devices
+(NISQs), the answer is: certainly not. However, the error rate that you make when guessing can be
+used as a benchmarking metric. PyQBench helps you in organizing such discrimination experiments for
+a single qubit system, executing them on real hardware or simulators, and
+computing discrimination probabilities based on the measured bitstrings.
+
+\section{Preliminaries and discrimination scheme approach}
+This section is divided into two parts.
+In Section~\ref{sec:maths}, we introduce the necessary notation and preliminaries needed to understand the concept of PyQBench. Next, in Section~\ref{sec:discrimination-scheme}, 
+we will present a general overview of the discrimination scheme in theoretical terms. We will also mention NISQ devices' limitations and possible practical solutions in the implementation process.
+
+\subsection{Mathematical preliminaries}\label{sec:maths}
+Recall that a general quantum
+measurement, that is a positive operator valued measure (POVM) $\PP$ is a
+collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
+\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$.
+In PyQBench, we are interested only in von Neumann measurements, i.e. measurements
+for which all the effects are rank-one projectors. Every such measurement can be
+parameterized by a unitary matrix $U$ which the effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+are created by taking $\ket{u_i}$ as  $i+1$-th column of the unitary matrix $U$.
+We will denote von Neumann measurements described by the matrix $U$ by $\PP_{U}$.
+
+Typically, NISQ devices can only perform measurements in computational $Z$-basis.
+To perform an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$
+to the measured system and then follow with $Z$-basis measurement. Hence, the following two
+circuits are equivalent.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1.7]{pics/vonneuman}
+	\caption{Decomposition of von Neumann measurement}
+	\label{fig:vonnneuman}
+\end{figure}
+
+Note that the decomposition above is basically a change of basis in which the measurement
+is performed.
+
+\subsection{Discrimination scheme}\label{sec:discrimination-scheme}
+
+Without loss of generality, we consider discrimination between a measurement in the computational
+Z-basis ($\PP_\Id$), and an alternative measurement performed in the basis $U$
+($\PP_U$)\footnote{Explaining why we can consider only Z-basis and alternative measurement is beyond
+	the scope of this technical documentation. See \cite{puchala2018strategies} if you are interested in
+	the explanation.}. In PyQBench, we operate only on two-level systems, but the discrimination scheme,
+described in detail in \cite{puchala2018strategies}, makes no assumptions about the dimensionality.
+
+In general, the discrimination scheme, presented in Fig.\ref{fig:theoretical_scheme}, requires a
+second system of the same dimensionality as the measured one. First, the joint system is prepared in
+some state $\ket{\psi_0}$. Then, the unknown measurement is performed on the first part of the
+system. Based on its outcome $i$, another measurement $\mathcal{P}_{V_i}$ is performed to obtain an
+outcome $j$. Finally, if $j=0$ we guess that the performed measurement is $\mathcal{P}_U$, otherwise
+we guess that it was $\mathcal{P}_\Id$.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1.7]{pics/theoretical_scheme}
+	\caption{Theoretical  scheme of discrimination  between von Neumann measurements $\PP_{U}$ and $\PP_\Id$. }
+	\label{fig:theoretical_scheme}
+\end{figure}
+
+\subsubsection{Limitations of NISQ devices and practical discrimination schemes}
+
+Current NISQ devices are unable to perform conditional measurements, which is the biggest
+obstacle to implementing our scheme on real hardware. Luckily, we can overcome it by
+cleverly adjusting our scheme so that it only uses components available on current devices.
+We have two possible choices here: using a postselection or a direct sum
+$V_0^\dagger\oplus V_1^\dagger$.
+
+\begin{scheme}(By using postselection)
+
+	The first idea is very simple. Instead of performing a conditional measurement, for each
+	measurement $\PP_U, \PP_\Id$ to be discriminated and each choice of $k \in \{0, 1\}$ we run circuit presented in Fig. \ref{fig:postselection}.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[scale=1.7]{pics/postselection_no_channels}
+
+		\caption{
+			Postselection scheme of discrimination between von Neumann measurements $\PP_{U}$ and $\PP_\Id$.
+		}\label{fig:postselection}
+	\end{figure}
+
+	But now our experiment does not match the previously described scheme, right?
+	Yes, unless we discard all the outcomes for which $i\ne k$ (hence the name \emph{postselection},
+	we are selecting valid outcomes after the experiment is performed).
+
+	% \begin{scheme}(Postselection)
+
+	% %\begin{figure}[h!]
+	% %	\includegraphics[scale=1.5]{onequbit.pdf}
+	% %	\caption{A schematic representation of the setup for distinguishing
+	% %		measurements using postselection.}
+	% %	\label{postselection}
+	% %\end{figure}
+
+	% \begin{enumerate}
+	% \item We prepare  the discriminator $\ket{\psi_{0}}$ on bipartite system.
+	% \item We perform one of two quantum channels, either $\Phi_{\Id}$ or
+	% $\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left( \Phi \otimes \Id\right)(\proj{\psi_0})$.
+	% \item We measure the first part of the input state  $\ket{\psi_{0}}$ and
+	% receive an output label $i$.
+	% \item
+	% Based on Holevo--Helstrom theorem, we perform a conditional binary
+	% measurement	$\PP_{V_j}$ and hence, we implement the quantum channel $\Phi_{V_j^\dagger}$ on the second part.
+	% \item To calculate the probability of correct discrimination, we include just those cases for which $i = j$.
+	% \item We measure the second part of the input state  $\ket{\psi_{0}}$ and make a
+	% decision based on received label $j$. If $i=j=0$, then we decide that
+	% $\PP_U$ occurs.  If $i=j=1$, we decide that
+	% $\PP_{\Id}$ occurs.
+	% \end{enumerate}
+
+	More precisely, our experiments can be grouped into classes identified by tuples of the form
+	$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen measurement.
+	We discard all the experiments for which $k \ne i$. Hence, the total number of valid experiments is
+
+	\begin{equation}
+	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}. 
+	\end{equation}
+
+	We now need to count the experiments (among the valid ones) resulting in successful discrimination.
+	If we have chosen $\PP_U$, then we guess correctly iff $j=0$. Similarly, for
+	$P_\Id$, we guess correctly iff $j=1$. If we define
+	\begin{eqnarray}
+	N_{\PP_U} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_U, k = i, j = 0\}, \\
+	N_{\PP_\Id} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_\Id, k = i, j = 1\},
+	\end{eqnarray}
+	then the empirical success probability can be computed as
+
+	\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{N_{\PP_U} + N_{\PP_\Id}}{N_{\text{total}}}.
+	\end{equation}
+
+\end{scheme}
+
+\begin{scheme}(By using direct sum)
+
+	\begin{enumerate}
+		\item We prepare the discriminator $\ket{\psi_{0}}$ on bipartite
+		system.
+		%\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
+		%$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
+		\item We apply one of unitary,   either $U^\dagger$ or
+		$\Id$, on the first system.
+		%\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
+Observe that   $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger} = \proj{0} \otimes \Phi_{V_0^\dagger}  + \proj{1} \otimes \Phi_{V_1^\dagger}.
+$
+		\item We apply direct sum $V_0^\dagger \oplus V_1^\dagger$ on the whole systems.
+		\item We measure both systems in computational basis $\Delta$.
+		\item We make a decision based on the received label $j$ on the second system. If $j=0$, then we
+		decide that $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs.
+	\end{enumerate}
+
+	The schematic representation of this setup is depicted in
+	Fig.~\ref{fig:controlled}.
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[scale=1.5]{pics/controlled_unitary}
+
+		\caption{ A schematic representation of the setup for distinguishing
+			measurements using controlled unitary gate.
+		}\label{fig:controlled}
+	\end{figure}
+
+	In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where $\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$.
+The number of successful trials for $U$ and $\Id$, respectively, can be written  as
+	\begin{eqnarray}
+	N_{\PP_U} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_U, j = 0\}, \\
+	N_{\PP_\Id} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_\Id, j = 1\}.
+	\end{eqnarray}
+	Then, the probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is given by
+	\begin{equation}
+	p_{\text{succ}} = \frac{N_{\PP_{U}} + N_{\PP_{\Id}}}{N_{\text{total}}},
+	\end{equation}
+	where $N_{\text{total}}$ is the number of trials.
+\end{scheme}
+
+\subsubsection{Optimal discrimination scheme}
+
+The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$,
+in terms of their distance with the use of the diamond norm
+\begin{equation}
+p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond, 
+\end{equation}
+where 
+\begin{equation}
+\|\PP\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left(\PP \otimes \1\right) (\proj{\psi}) \|_1.
+\end{equation}
+The quantum state $\ket{\psi}$ which maximizes the diamond norm is called as discriminator.
+Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is possible to construct the necessary components  ($\ket{\psi_0}$, $V_0$, $V_1$) to create the optimal discrimination strategy.
+
  \section{Software description}
  \label{}
-\todo[inline]{Describe the software in as much as is necessary to establish a 
-vocabulary needed to explain its impact. }
-
-We will first give a general overview of the structure of the code in 
-Section~\ref{sec:sortware-architecture} and then provide additional details on 
-the functionality of benchmark's schemes  in 
-Section~\ref{sec:sortware-functionalities}.
-
-\subsection{Software Architecture}\label{sec:sortware-architecture}
-\label{}
-\todo[inline]{
-	Give a short overview of the overall software architecture; provide a 
-	pictorial component overview or similar (if possible). If necessary provide 
-	implementation details.}
+ This section is divided into two parts.
+ In Section~\ref{sec:sortware-functionalities} we present the details of PyQBench functionality. Next, in Section~\ref{sec:sortware-architecture}, 
+ we will give a general overview of the software architecture.
 
 \subsection{Software Functionalities}\label{sec:sortware-functionalities}
-\todo[inline]{Present the major functionalities of the software.}
 
@@
 
-\subsubsection{Model specification}
-The scenario assumes that Alice and Bob have access to an unknown measurement
-device, a black box. Alice has hidden one of the two measurements, either $\PP$
-or $\mathcal{Q}$, in the black box. Bob only has the information that the black box
-performs one of these measurements. They want to determine an upper bound on the
-probability of correct discrimination between $\PP$ and $\mathcal{Q}$. Moreover, they also want to
-construct an optimal discrimination strategy to achieve the highest probability. Theoretical results were characterized in~\cite{puchala2018strategies}.
-
-In this work, we will consider the problem of discrimination between von Neumann 
-measurements. One of them on the computational basis, the second one on basis 
-$U$, where $U$ is a unitary matrix. 
-The scheme of discrimination can be divided into the following steps, which are 
-illustrated in Fig.~\ref{fig:theoretical_scheme}.
-
+\subsection{Software Architecture}\label{sec:sortware-architecture}
+PyQBench can be used in two different ways:
+\begin{itemize}
+\item As a library. This is a more extensible, but also more laborious way of using PyQBench. Most importantly, this way allows for more advanced scripting defining your own measurements scheme.
+
+\item As a CLI tool. This mode of operation trades extensibility for simplicity of usage, as it allows only for running Fourier-discrimination experiments defined with simple YAML input files.
+\end{itemize}
+
+\subsubsection{PyQBench as a library}\label{sec:pyqbench-as-library}
+This guide introduces basic concepts needed for using PyQBench as a library from a Python script. In particular, we will cover the following topics:
+\begin{enumerate}
+\item Defining experiment using circuit components.
+\item Assembling circuits needed for given benchmarking scheme.
+\item Running experiment on simulator or hardware.
+\item Obtaining empirical probability of successful discrimination between measurements.
+\end{enumerate}
+
+On the conceptual level, every discrimination experiment performed in PyQBench needs the following:
+\begin{enumerate}
+\item Discriminator, i.e. optimal initial state for the circuit.
+\item Unitary $U^\dagger$ defining alternative measurement to be discriminated from the measurement in Z-basis.
+\item $V_0^\dagger$ and $V_1^\dagger$, positive and negative parts of optimal measurement from Holevo-Helstrom theorem.
+\end{enumerate}
+Currently available quantum computers typically cannot start execution from an arbitrary state.
+Instead, we have to prepare it ourselves.
+Hence, to execute experiment using postselection scheme, we need an instruction taking to the desired discriminator
+and instructions implementing $U^\dagger$, $V_0^\dagger$ and $V_1^\dagger$.
+
+\subsubsection{Example of usage}
+In our example, we will use $U =  H$ (the Hadamard gate).
+To keep us focused on the implementation in PyQBench and not delve too deep into mathematical explanation, we simply provide explicit formulas for discriminator $\ket{\Psi_0} $, $V_0$ and $V_1$, leaving the calculations to the interested reader.
+
+The explicit formula for discriminator in our toy model reads:
+\begin{equation}
+\ket{\Psi_0} = \frac{1}{\sqrt{2}} (\ket{00} + \ket{11}), 
+\end{equation}
+with corresponding parts of optimal measurement being equal to
+\begin{equation}
+V_0 = 
+\left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right), 
+\end{equation}
+and \begin{equation}
+V_1 = 
+\left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right), 
+\end{equation} 
+where \begin{equation}
+\alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} \cos\left( \frac{3}{8} \pi \right),
+\end{equation}
+\begin{equation}
+\beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} \sin\left( \frac{3}{8} \pi \right).
+\end{equation}
+
+As a next step, we need decompose our matrices into actual sequences of gates.
+We are lucky, because our discriminator is just a Bell state. Thus, the circuit taking $\ket{00}$ to $\ket{\Phi_0}$ is well known, and comprises Hadamard gate followed by CNOT gate on both qubits. 
 \begin{figure}[h!]
 	\centering
-	\includegraphics[scale=1.7]{pics/theoretical_scheme}
-	\caption{Theoretical  scheme of discrimination  between von Neumann measurements $\PP_{U}$ and $\PP_\Id$. }
-	\label{fig:theoretical_scheme}
+	\includegraphics[scale=1.7]{pics/discriminator}
+	\caption{Decomposition of the discriminator $\ket{\Phi_0}$. }
+	\label{fig:discriminator}
 \end{figure}
 
-%\begin{figure}[h!]
-%	\centering 
-%	\includegraphics[width=0.9\linewidth]{gates1.pdf} 
-%	\caption{A schematic representation of the setup for distinguishing
-%		measurements by using entanglement. }
-%	\label{fig:scheme}
-%\end{figure}
-
+For $V_0$ and $V_1$ observe that $V_0 = RY\left(\frac{3}{4} \pi \right) $, where $RY$ is rotation gate around the $Y$ axis defined by 
+\begin{equation}
+RY(\theta) = 
+\left(\begin{array}{cc} \cos\frac{\theta}{2} & -\sin\frac{\theta}{2} \\ \sin\frac{\theta}{2} & \cos\frac{\theta}{2} \end{array}\right).  
+\end{equation} 
+To obtain $V_1$  we need only to swap the columns, which is equivalent to following $V_0$ by $X$ matrix, more precisely 
+\begin{equation}
+V_1 =  RY\left(\frac{3}{4} \pi \right) \cdot X. 
+\end{equation}
+
+Now running the simulation is as simple as invoking functions imported from qbench package.
+
+\todo[inline]{listingi swieca sie na razie jak choinka ale bedziemy kolorki drasowac}
+\begin{lstlisting}[language=Python, caption=Simulation benchmark by using postselection]
+
+simulator = Aer.get_backend("aer_simulator")
+postselection_result = benchmark_using_postselection(
+	backend=simulator,
+	target=0,
+	ancilla=1,
+	state_preparation=state_prep(),
+	u_dag=u_dag(),
+	v0_dag=v0_dag(),
+	v1_dag=v1_dag(),
+	num_shots_per_measurement=10000,
+)
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python, caption=Simulation benchmark by using direct sum]
+
+simulator = Aer.get_backend("aer_simulator")
+direct_sum_result = benchmark_using_direct_sum(
+backend=simulator,
+target=1,
+ancilla=2,
+state_preparation=state_prep(),
+u_dag=u_dag(),
+v0_v1_direct_sum_dag=v0_v1_direct_sum_dag(),
+num_shots_per_measurement=10000,
+)
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python, caption=Computation of probability]
+p_succ = (2 + np.sqrt(2)) / 4
+print(f"Real p_succ = {p_succ}")
+print(
+f"Postselection: p_succ = {postselection_result}, abs. error = {p_succ - postselection_result}"
+)
+print(f"Direct sum: p_succ = {direct_sum_result}, abs. error = {p_succ - direct_sum_result}")
+
+\end{lstlisting}
+
+\begin{lstlisting}
+Real p_succ = 0.8535533905932737
+Postselection: p_succ = 0.8559797193791593, abs. error = -0.0024263287858855564
+Direct sum: p_succ = 0.85605, abs. error = -0.0024966094067262468
+\end{lstlisting}
+
+\subsubsection{Gaining more control over the benchmarking process}
+In the example presented above we used functions that automate the whole process - from the circuit assembly, through running the simulations to interpreting the results.
+But what if we want more control over some parts of this process?
+Maybe we want play around with some models?
+Or maybe we want to run the same experiment on multiple backends and we don’t want them to be assembled over and over again?
+
+ PyQBench provides functions performing:
 \begin{enumerate}
-	\item Alice and Bob share an entangled state $\ket{\psi_{0}}$ (discriminator) on systems 
-	$A$ and $B$.
-	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
-	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{0}}$ and measures the system $A$.
-	\item Alice performs the conditional binary measurement $\PP_{V_i}$ on the part 
-	$B$ based on the output label $i$. 
-	\item  Bob measures the system $B$ of the input state  $\ket{\psi_{0}}$ and 
-	makes a decision based on the received label $j$. If $j=0$, then he decides 
-	that the the black box contains $\PP_U$. Otherwise, he decides that the 
-	black box contains $\PP_{\Id}$. 
+\item assembly of circuits needed for experiment, provided the components discussed above
+\item interpretation of the obtained measurements
 \end{enumerate}
-
-\subsubsection{Quantum architecture's limits and practical solutions}
-
-Let us take a closer look at the setup for distinguishing von Neumann 
-measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of 
-this scheme is to perform a conditional binary measurement. 
-Unfortunately, current NISQ devices do not allow for performing conditional 
-binary measurements.
-The only possible measurement performed on quantum architectures is the 
-measurement in the computational basis. 
-We  will present two possible methods providing a clever way to cross this 
-obstacle. These will be two schemes of practical realization. 
-The first method consists in using postselection while the second method 
-consists in applying a controlled unitary. These methods are described below.
-
-\begin{scheme}(Postselection)
-
-%\begin{figure}[h!]
-%	\includegraphics[scale=1.5]{onequbit.pdf}
-%	\caption{A schematic representation of the setup for distinguishing
-%		measurements using postselection.}
-%	\label{postselection}
-%\end{figure}
-
+When using these functions, you need to take care of running circuits on some backend yourself, but it gives you unlimited power over the whole process.
+The difference between such approaches is illustrated on the diagrams below.
+
+When using these functions, you need to take care of running circuits on some backend yourself, but it gives you unlimited power over the whole process.
+The difference between the two approaches is illustrated on the diagrams below.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=1\textwidth]{pics/scheme1}
+%		\caption{$y=x$}
+		\label{fig:simplified}
+	\end{subfigure}
+	\vfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+	\includegraphics[width=1\textwidth]{pics/scheme2}
+%		\caption{$y=3\sin x$}
+		\label{fig:execution}
+	\end{subfigure}
+\end{figure}
+
+\pagebreak
+
+Next, we divide the experiment into two parts: 
 \begin{enumerate}
-\item Alice and Bob prepare an entangled state $\ket{\psi_{0}}$ (discriminator) on systems 
-$A$ and $B$.
-\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or 
-$\Phi_{U^\dagger}$,  on part $A$ of the input state  $\ket{\psi_{0}}$.
-\item Alice measures part $A$ of the input state  $\ket{\psi_{0}}$ and 
-receives an output label $i$.
-\item  
-Based on Holevo--Helstrom theorem, Bob performs a conditional binary 
-measurement	$\PP_{V_j}$ and implements the unitary channel 	$\Phi_{V_j^\dagger}$ on part $B$.
-\item To calculate the probability of correct discrimination, they include just those cases for which $i = j$.
-\item Bob measures part $B$ of the input state  $\ket{\psi_{0}}$ and makes a
-decision based on received label $j$. If $i=j=0$, then he decides that the 
-black box contains $\PP_U$. Otherwise, he decides that the black box contains
-$\PP_{\Id}$.
+	\item Assembling  circuits
+	\item Running  circuits
 \end{enumerate}
 
-The schematic representation of this setup is depicted in 
-Fig.~\ref{fig:postsellection}.
-
-\begin{figure}[h!]
-	\centering 
-	\includegraphics[scale=1.7]{pics/postselection}
-
-	\caption{ A schematic representation of the setup for distinguishing
-		measurements using postselection. 
-	}\label{fig:postsellection}
-\end{figure}
-
-Due to the fact that the measurement result is nondeterministic, we are forced to consider the following circuits
-in the postselection procedure
-\begin{equation}
-\begin{split}
-(\Phi_{U^\dagger}, \Phi_{V_k^\dagger}, i, j) \\ 
-(\Phi_{\Id}, \Phi_{V_k^\dagger}, i, j)
-\end{split}
-\end{equation}
-where $k=\{0,1\}, i=\{0,1\}$ and $ j=\{0,1\}$. 
-The optimal probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows.
-		\begin{equation}
-		p = \frac{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,0) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,1)}{\#(\Phi_{U^\dagger}, \Phi_{V_i^\dagger},i,j) + \#(\Phi_\Id, \Phi_{V_i^\dagger},i,j)}, 
-		\end{equation}
-where $i=\{0,1\}$ and $ j=\{0,1\}$.
-
-\end{scheme}
-
-\begin{scheme}(By using controlled unitary)
-
-\begin{enumerate}
-\item Alice and Bob prepare an entangled state $\ket{\psi_{0}}$ on 
-systems $A$ and $B$.
-\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or
-$\Phi_{U^\dagger}$,  on part $A$ of the input state  $\ket{\psi_{0}}$.
-\item Alice and Bob implement  direct sum of unitary channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$ obtained from 
-Holevo--Helstrom theorem.	
-\item Alice and Bob prepare the measurement $\Delta$ in computational basis on 
-their systems.
-\item Bob makes a decision based on received label $j$. If $j=0$, then he
-decides that the the black box contains $\PP_U$. Otherwise, he decides that the
-black box contains $\PP_{\Id}$.
-\end{enumerate}
-
-The schematic representation of this setup is depicted in 
-Fig.~\ref{fig:controlled}.     
-\begin{figure}[h!]
-	\centering 
-	\includegraphics[scale=1.5]{pics/controlled_unitary}
-
-	\caption{ A schematic representation of the setup for distinguishing
-		measurements using controlled unitary gate. 
-	}\label{fig:controlled}
-\end{figure}
-
-Here, we consider the following circuits
-by using controlled unitary
-\begin{equation}
-\begin{split}
-(\Phi_{U^\dagger}, \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j) \\ 
-(\Phi_{\Id},  \Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}, i, j)
-\end{split}
-\end{equation}
-where $i=\{0,1\}$ and $ j=\{0,1\}$. 
-Then, the optimal probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is as follows.
-\begin{equation}
-p = \frac{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,0) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,1) }{\#(\Phi_{U^\dagger},\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j) + \#(\Phi_\Id,\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger},i,j)}
-\end{equation}
-where $i=\{0,1\}$ and $ j=\{0,1\}$. 
-\end{scheme}
-
-\subsubsection{Mathematical preliminaries}
-
-Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
-the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
-$M_d$.  
-%The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
-%will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
-%matrices of dimension $d$ by $\HH_d^+$. 
-The set of quantum states, that is
-positive semidefinite operators having trace equal to one, will be denoted
-$\Omega_d$. 
- The subset of $M_d$ consisting of unitary matrices will be denoted
-by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$. 
-	An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$, whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
-
- We will also need a linear mapping transforming $M_{d_1}$ into
-$M_{d_2}$, which will be denoted 
-\begin{equation}
-\Phi: M_{d_1 } \rightarrow M_{d_2}.
-\end{equation} 
-There
-exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $M_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism. 
-For a given linear mapping $\Phi$ the corresponding Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
-\begin{equation}
-\mathcal{J}(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
-We introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
-and trace preserving (CPTP).
-In this work we will consider a special class of quantum channels, called unitary channels.  A 
-channel
-$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
-\UU_d$.
-
-Finally, we define a quantum
-measurement, that is a positive operator valued measure (POVM) denoted by $\PP, \mathcal{Q}$ etc. This is a 
-collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
-effects, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
-all effects are rank-one projection operators, then such a measurement is
-called a von Neumann measurement. 
-Every von Neumann measurement can be
-parameterized by a unitary matrix $U$ with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
-where $\ket{u_i}$ is the $i$-th column of the unitary matrix $U$.  Hence we will use the notation $\PP_{U}$.  The action of
-quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
-seen as  a measure-and-prepare quantum channel as follows 
-$
-\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-$ Moreover, observe that each von Neumann measuement $\PP_{U}$ can be written as compostion of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
-
-\subsubsection{Diamond norm and the task of discrimination between quantum operators}
-This section defines a special norm on the space of linear mappings, known as 
-the diamond norm, and establishes some of its properties. 
-Next, we will explain the precise connection between the diamond
-norm and the task of quantum operation discrimination.
-
-Let us  consider a  linear mapping transforming  square matrices into square 
-matrices that is $\Phi: M_{d_1} \to M_{d_2}$. 
-We define the diamond norm of a map $\Phi$ as 
-\begin{equation}
-\|\Phi\|_\diamond = \max_{\|X\|_1=1} \| \left(\Phi \otimes \1\right) (X) \|_1.
-\end{equation}
-The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\Psi$  and $\Phi$, 
-in terms of their distance with the use of the diamond norm
-\begin{equation}
-p_{\text{succ}}(\Psi, \Phi) =  \frac12 + \frac14 \| \Psi - \Phi \|_\diamond.
-\end{equation}
-from Theorem 1 in \cite{puchala2018strategies}, the distance between two von Neumann measurements $\PP_U$ and 
-$\PP_\Id$ is given by
-\begin{equation}
-\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
-\Phi_\Id\|_\diamond,
-\end{equation}
-where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
-unitary matrices of dimension $d$.
-
-\paragraph{Discrimination of unitary channels}
-
-Before we proceed to presenting our main results, we need to briefly discuss the
-problem of discrimination of unitary channels.  For this purpose, we introduce the notion of numerical range of
-a given matrix $A \in M_d$. The set \begin{equation}
-W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
-\mathbb{C}^d, \;
-\;\braket{x}{x}=1\}.
-\end{equation}   
-is called numerical range of $A$.
-The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.
-
-	Let $U \in \UU_d$ and $\Phi_U$ be a unitary 
-	channel. 
-	Then, the following equation holds
-	\begin{equation}
-	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-	\end{equation}
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. Finally, the optimal probability to discriminate two unitary channel is given by 
-	\begin{equation}
-	p_{\text{succ}}(\Phi_U, \Phi_\Id) = \frac{1}{2} + \frac{1}{2} \sqrt{1-\nu^2}.
-	\end{equation}
-
-%In the general case, the diamond norm of a Hermiticity-preserving maps $\Phi$ 
-%can be computed using the Semidefinite Program~\cite{watrous2018theory} and 
-%state 
-%primal and dual problem in the following form:
+Let us focus only on the postselection case, as the direct sum case is analogous. In addition, we need to import two more functions from PyQBench.
+
+\begin{lstlisting}[language=Python, caption=Assembling circuits]
+from qbench.schemes.postselection import (
+assemble_postselection_circuits,
+compute_probabilities_from_postselection_measurements,
+)
+
+circuits = assemble_postselection_circuits(
+target=0,
+ancilla=1,
+state_preparation=state_prep(),
+u_dag=u_dag(),
+v0_dag=v0_dag(),
+v1_dag=v1_dag(),
+)
+
+circuits
+\end{lstlisting}
 
 %
-%\begin{minipage}{0.495\linewidth}
-%	\begin{equation*}
-%		\begin{split}
-%			\text{\textbf{Primal problem:}} \\
-%			\text{maximize:}\quad & \tr(X J(\Phi)) \\[2mm]
-%			\text{subject to:}\quad &  \left[ \begin{array}{cc}\Id_{d_2} 
-%\otimes \rho & X \\ X^* & \Id_{d_2} \otimes \rho  \end{array} \right] \ge 0 \\
-%			& \rho \in \HH_d^+\\ 
-%			& X \in M_{d1,d2}.
-%		\end{split}
-%	\end{equation*}
-%\end{minipage}
-%\begin{minipage}{0.495\linewidth}
-%	\begin{equation*}
-%		\begin{split}
-%			\text{\textbf{Dual problem:}} \\
-%			\text{minimize:}\quad & ||\tr_1(Y)||_\infty \\[2mm]
-%			\text{subject to:}\quad & \left[ \begin{array}{cc}Y & -J(\Phi) \\ 
-%-J(\Phi) &  Y \end{array} \right] \ge 0 \\
-%			& Y \in \HH_{d_1d_2}^+.
-%		\end{split}
-%	\end{equation*}
-%	\vspace{0.5cm}
-%\end{minipage}
-
-\section{Illustrative Example}
-
-Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
-Assume that the unitary matrix $U$ is of the form 
+%\begin{lstlisting}[language=Python, caption=Python example]
+%{'id_v0': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b1585b9a0>,
+%'id_v1': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b37fbfa90>,
+%'u_v0': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b1585bf40>,
+%'u_v1': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b1585bf10>}
+%\end{lstlisting}
+
+Now we only need to run the circuits.
+To make things more interesting, we will run a noisy and noiseless simulation of our circuits.
+We will use the same backend as before, and our noise model will only comprise readout errors on both qubits.
+
+\begin{lstlisting}[language=Python, caption=Noise models]
+from qiskit.providers.aer import noise
+
+error = noise.ReadoutError([[0.75, 0.25], [0.8, 0.2]])
+
+noise_model = noise.NoiseModel()
+noise_model.add_readout_error(error, [0])
+noise_model.add_readout_error(error, [1])
+
+noise_model
+\end{lstlisting}
+
+Once we have our noise model ready, we can execute our circuits with and without noise.
+To this end, we will use Qiskit’s execute function.
+One caveat is that we have to keep track which measurements correspond to which circuit.
+We do so by fixing an ordering on the keys in circuits dictionary.
+
+\begin{lstlisting}[language=Python, caption=Running  circuits]
+from qiskit import execute
+
+keys_ordering = ["id_v0", "id_v1", "u_v0", "u_v1"]
+all_circuits = [circuits[key] for key in keys_ordering]
+
+counts_noisy = (
+execute(all_circuits, backend=simulator, noise_model=noise_model, shots=10000).result().get_counts()
+)
+
+counts_noiseless = execute(all_circuits, backend=simulator, shots=10000).result().get_counts()
+
+print(f"Noisless counts: {counts_noiseless}")
+print(f"Noisy counts: {counts_noisy}")
+\end{lstlisting}
+
+%
+%Noisless counts: [{'11': 737, '00': 731, '10': 4163, '01': 4369}, {'01': 750, '00': 4217, '10': 716, '11': 4317}, {'01': 740, '10': 693, '00': 4209, '11': 4358}, {'11': 775, '01': 4341, '00': 765, '10': 4119}]
+%Noisy counts: [{'01': 1720, '11': 514, '10': 1760, '00': 6006}, {'11': 529, '00': 6025, '10': 1705, '01': 1741}, {'11': 531, '01': 1726, '00': 5956, '10': 1787}, {'01': 1808, '11': 515, '10': 1681, '00': 5996}]
+
+Finally, the only thing left is to compute the success probabilities. We do so by passing bitstring counts to function \\ \texttt{compute\_probabilities\_from\_postselection\_measurements}.
+
+\begin{lstlisting}[language=Python, caption=Computation probability without noise]
+prob_succ_noiseless = compute_probabilities_from_postselection_measurements(
+id_v0_counts=counts_noiseless[0],
+id_v1_counts=counts_noiseless[1],
+u_v0_counts=counts_noiseless[2],
+u_v1_counts=counts_noiseless[3],
+)
+
+print(prob_succ_noiseless)
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python, caption=Computation probability including noise]
+prob_succ_noisy = compute_probabilities_from_postselection_measurements(
+id_v0_counts=counts_noisy[0],
+id_v1_counts=counts_noisy[1],
+u_v0_counts=counts_noisy[2],
+u_v1_counts=counts_noisy[3],
+)
+
+print(prob_succ_noisy)
+\end{lstlisting} 
+The success probability is 0.8524401115559386, whereas if we obtain some noise, the succes probability is equal to 0.5017958400693446
+As expected, noisy simulations gave us results that are further away from the exact ones.
+
+This concludes introduction to PyQBench library. If you are interested see additoinal usage examples in our examples directory.
+
+\subsubsection{PyQBench as a CLI tool}\label{sec:pyqbench-as-cli} 
+Using PyQBench as a library allows one to conduct, in principle, arbitrary two-qubit von Neumann measurement experiment.
+However, as discussed in the previous guide, it requires some amount of boilerplate code.
+
+However, for a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
+
+\todo[inline]{to be continued }
+
+\section{Discrimination scheme for parameterized Fourier family and implementation}
+
+\subsection{Discrimination scheme}
+So far, we only discussed how the discrimination is performed using two different
+schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known.
+It turned out that the determination of $V_0$ and $V_1$ is a simple task while the discriminator $\ket{\psi_{0}}$ is known.
+However,
+sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
+is, in general, NP-hard problem. 
+We have found the analytical solution of the discrimination scheme for a particular class of von Neumann measurements.
+
+Here,  we will show how all the necessary ingredients look like for
+von Neumann measurements defined by the parameterized Fourier family:
+
 \begin{equation}
 	U = H
-\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
-\end{equation}
-%\begin{equation}
-%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
-%\end{equation}
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger, 
+\end{equation}
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this section we present theoretical probability of correct 
-discrimination between these measurements. Moreover, we create the optimal 
-theoretical strategy of their discrimination. 
-The otimal probability will be calculated in 
-subsection~\ref{sec:example_theoretical_probability}. Later, we will 
-discuss the realization of this scheme in 
-subsection~\ref{sec:example_realization}. For such realization, we 
-will need the optimal input state (see sec.~\ref{sec:example_discriminator}), 
-and the optimal final measurement (see sec.~\ref{sec_example_final_measurement}).
-
-\subsection{Theoretical probability}\label{sec:example_theoretical_probability}
-
-\begin{theorem}\label{th:probability}
-The optimal probability of correct discrimination between von Neumann
-measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
-where $\phi \in [0, 2\pi)$ is given by
-\begin{equation}
-p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
-\end{equation}
-\end{theorem}
-
-\subsection{Realization}\label{sec:example_realization}
-
-To indicate the optimal strategy  we will present two propositions.
-The first one is concentrated around the discriminator as the optimal input state of discrimination strategy, whereas the second one describes the optimal final measurement.
-
-\subsubsection{Discriminator}\label{sec:example_discriminator}
-
-\begin{proposition}\label{prop-discrim}
-Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
-and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
-2\pi)$.  The optimal input state has the form
-\begin{equation}
-\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
-\end{equation}
-\end{proposition}
-
-\subsubsection{Conditional measurement}\label{sec_example_final_measurement}
-
-\begin{proposition}\label{prop:optimal-measurement}
-	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
-	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
-	2\pi)$.  
-The  conditioned measurement has the form
-\begin{equation}
-\begin{split}
-\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{0} V_1^\dagger,  \\ 
-\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
-\proj{1} V_1^\dagger,
-\end{split}
-\end{equation}
-where for each $\phi \in \mathbb{R}$,  the controlled unitaries $V_0$ and $V_1$ 
-have the form
+In this case, the optimal input state is Bell state of the form
+\begin{equation}
+	\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \ket{00} + \ket{11}.
+\end{equation}
+And, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
+have the following form
 \begin{equation}
@@
 \end{equation}
-and
 \begin{equation}
@@
 \end{equation}
-\end{proposition}
-
-\section{Implementation}
-In this section we will compare theoretical probability of correct 
-discrimination between these measurements and the realization on real devices.
-\todo[inline]{TU WYNIKI PRAKTYCZNE }
-
-\subsection{Generic case}
-Now we present the circuits for the generic case.
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-None}
-\caption{Circuit representing state preparation in the  generic case.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-None}
-\caption{Circuit representing $U^\dagger$ in the generic case.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-None}
-\caption{Circuit representing $V_0^\dagger$ in the generic case.}
-\end{figure}
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
-\caption{Circuit representing controlled $V_0$ and $V_1$ the generic case.}
-\end{figure}
-
-\subsection{Lucy}
- basis gates  =["ecr", "i", "rz", "sx", "x"]
-
-\subsection{Rigetti}
- basis gates = ["cz", "rx", "rz"]
-
-\subsection{Sample code snippets analysis (optional)}
-\todo[inline]{moze tu fragmenty kodu ? }
-\label{}
-
-\section{Impact }
-
+Finally, we have also calculated the theoretical probability of correct discrimination between von Neumann
+measurements $\PP_U$ and $\PP_{\Id}$ is given by
+\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
+\end{equation}
+More details and proofs of the construction's validity   we can find in the \ref{app:optimal-probability} and \ref{app:optimal-strategy}.
+
+\subsection{Implementation}
+Here, we will present the results obtained on real devices. For this work we chose IMBQ software. \todo[inline]{tu dokladne informacje o maszynie i rysuneczki}
+
+\section{Impact}
+\todo[inline]{OJCIEC WYKAZ SIE, bo trzeba to dobrze sprzedac, nizej tekst z formatki softwarex}
 This software has two main contributions.
@@
 \appendix
-\section{Optimal probability}
-
-In this Appendix we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$.
-To do that, we will present an auxiliary lemma.
+\section{Mathematical preliminaries} \label{app:preliminaries}
+
+Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
+the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
+$M_d$.  
+%The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
+%will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
+%matrices of dimension $d$ by $\HH_d^+$. 
+By $\Omega_d$, we will denote the set of quantum states, that is
+positive semidefinite operators having trace equal to one. 
+The subset of $M_d$ consisting of unitary matrices will be denoted
+by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
+$\DD \UU_d$. 
+%An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$, whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
+
+We will also need a linear mapping transforming $M_{d_1}$ into
+$M_{d_2}$, which will be denoted 
+\begin{equation}
+\Phi: M_{d_1 } \rightarrow M_{d_2}.
+\end{equation} 
+There
+exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $M_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism. 
+For a given linear mapping $\Phi$ the corresponding Choi operator $J(\Phi)$ is explicitly written as 
+\begin{equation}
+J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
+
+We introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
+and trace preserving (CPTP).
+In this work we will consider a special class of quantum channels, called unitary channels.  A 
+channel
+$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for any $U \in 
+\UU_d$.
+
+The action of
+von Neumann measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
+seen as  a measure-and-prepare quantum channel as follows \begin{equation}
+\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
+\end{equation}
+Moreover, observe that each von Neumann measuement $\PP_{U}$ poses a  composition of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
+
+We need to also briefly discuss about the distance between unitary channels and von Neumann measurements. From \cite[Theorem 1]{puchala2018strategies}, the distance between measurements $\PP_U$ and 
+$\PP_\Id$ ie equal to 
+\begin{equation}
+\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
+\Phi_\Id\|_\diamond,
+\end{equation} whereas to express the distance between unitary channels, we need to introduce the notion of numerical range. The set \begin{equation}
+W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
+\mathbb{C}^d, \;
+\;\braket{x}{x}=1\}.
+\end{equation}   
+is called numerical range of  a matrix $A \in M_d$.
+The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}. 
+Due to the definition of $W(A)$, the distance between two unitary channels $\Phi_{U} $ and $\Phi_\Id$
+can be written as 
+\begin{equation}
+\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
+\end{equation}
+where $\nu = \min_{x \in W(U^\dagger)} |x|  $.
+
+\section{Optimal probability} \label{app:optimal-probability}
+
+Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
+Assume that the unitary matrix $U$ is of the form 
+\begin{equation}
+U = H 
+\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
+\end{equation}
+%\begin{equation}
+%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
+%\end{equation}
+where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
+In this section we present theoretical probability of correct 
+discrimination between these measurements. To do that, we will present an auxiliary lemma.   
 \begin{lemma}\label{lemma:min-e-optimal}
@@
 	%		\end{equation}
-	This condition is equivalent to 
+	This condition is equivalent to show
 	\begin{equation}
@@
 	The celebrated Hausdorf-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
-	$W(A)$ of any matrix $A \in M_d$ is a convex set and therefore
+	$W(A)$ of any matrix $A \in M_d$ is a convex set, and therefore we have 
 	\begin{equation}
@@
 	\end{equation}
-	So, we obtain that 
+	So, we can assume that 
 	\begin{equation}
@@
 	\begin{equation}
-	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \mu,
-	\end{equation}
-	where $\mu \coloneqq \max_{E \in \diaguni_2 } \nu_{E}.$
+	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \max_{E \in \diaguni_2 } \nu_{E}. 
+	\end{equation}
 
@@
 	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
-	\end{equation}
-	where  for eigenvalue $\lambda_1 = 1$, the corresponding 
+	U= \lambda_0 \ketbra{x_0}{x_0} + \lambda_1 \ketbra{x_1}{x_1}, 
+	\end{equation}
+	where  for eigenvalue $\lambda_0 = 1$, the corresponding 
 	eigenvector is 
-	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	of the form $\ket{x_0} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
 	$,
-	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
+	whereas for  $\lambda_1= e^{i \phi}$ we have $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right] 
 	$.
@@
 	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
-	\frac{1}{2} \left| \tr\left((   \proj{x_1} +e^{i \phi}\proj{x_2} ) E \right) 
+	\frac{1}{2} \left| \tr\left((   \proj{x_0} +e^{i \phi}\proj{x_1} ) E \right) 
 	\right|  = 
-	\frac{1}{2} \left|  \bra{x_1} E \ket{x_1} +  e^{i \phi}\bra{x_2} E \ket{x_2} 
+	\frac{1}{2} \left|  \bra{x_0} E \ket{x_0} +  e^{i \phi}\bra{x_1} E \ket{x_1} 
 	\right| = \\& 
@@
 	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le 
-	\mu, 
+	\max_{E \in \diaguni_2 } \nu_{E}, 
 	\end{split}
@@
 \end{proof}
-\begin{proof}[Proof of Theorem~\ref{th:probability}]
-	From Holevo-Helstrom theorem we obtain
+
+\begin{theorem}\label{th:probability}
+	The optimal probability of correct discrimination between von Neumann
+	measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
+	where $\phi \in [0, 2\pi)$ is given by
+	\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} . 
+	\end{equation}
+\end{theorem}
+
+\begin{proof}
+	From Holevo-Helstrom theorem, we obtain
 	\begin{equation}
@@
 	\end{equation}
-	From Theorem 1 in~\cite{puchala2018strategies} we have 
+	From~\cite[Theorem 1]{puchala2018strategies}, we have 
 	\begin{equation}
@@
 	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal} we know that for 
-	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that
+	From Lemma~\ref{lemma:min-e-optimal},  we know that for 
+	$U =  H \diag(1, e^{i \phi}) H^\dagger$,  it also holds that
 	\begin{equation}
@@
 
-\section{Optimal discrimination strategy}
-In this Appendix we present proofs of Proposition~\ref{prop-discrim} and Proposition~\ref{prop:optimal-measurement} to indicate the optimal discrimination strategy.
-\begin{proof}[Proof of Proposition~\ref{prop-discrim}]
+\section{Optimal discrimination strategy} \label{app:optimal-strategy}
+
+In this Appendix we create the optimal 
+theoretical strategy of  discrimination between $\PP_{U}$ and $\PP_{\Id}$. 
+To indicate the optimal strategy, we will present two propositions.
+The first one is concentrated around the discriminator as the optimal input state of discrimination strategy, whereas the second one describes the optimal final measurement.
+
+\begin{proposition}\label{prop-discrim}
+	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
+	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
+	2\pi)$.  The  discriminator has the form
+	\begin{equation}
+	\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
+	\end{equation}
+\end{proposition}
+
+\begin{proof}
 	Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0, 
@@
 	\begin{equation}
-	\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
+	\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) J(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
 	Hence, we obtain
@@
 	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
-	\mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
+	J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
 	\\ 
@@
 	\begin{split}
- \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\PP_{U} - \PP_{\Id} )  \left( 
+ \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( 
 	\Id \otimes \sqrt{\rho} \right) \|_1 = \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
@@
 	Due to that, we know  
-	that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ is the discriminator of the problem 
+	that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ equals $\frac{1}{\sqrt{2} } | 
+	\Id_2 \rangle \rangle$ is the discriminator of the problem 
 	of discrimination between 
@@
 	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm).      Hence, we obtain that \begin{equation}
-	\ket{\psi_{0}} \coloneqq   | \sqrt{\rho_0}^\top \rangle \rangle = \frac{1}{\sqrt{2} } | 
+	\ket{\psi_{0}} =  \frac{1}{\sqrt{2} } | 
 	\Id_2 \rangle \rangle,
@@
 
-\begin{proof}[Proof of Proposition~\ref{prop:optimal-measurement}]
+\begin{proposition}\label{prop:optimal-measurement}
+	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
+	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
+	2\pi)$.  
+	The   controlled unitaries $V_0$ and $V_1$ 
+	have the form
+	\begin{equation}
+	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
+	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
+		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+	\end{equation}
+	and
+	\begin{equation}
+	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
+	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) 
+	&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+	\end{equation}
+\end{proposition}
+
+\begin{proof}
 	From Proposition~\ref{prop-discrim} we obtain the exact form of discriminator given by
@@
 	\end{equation}
-	From Holevo-Helstrom theorem  we constrain a conditional measurement $\mu$.  
+	From Holevo-Helstrom theorem~\cite{watrous}, we constrain a conditional measurement $\mu$.  
 	Let us define 
@@
 	\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
-	follows \todo[inline]{udostepniamy ten plik nb?}(see also \texttt{one-qubit.nb}).
-	The unitary $V_0$ has the form
+	follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
+	the unitary $V_0$ has the form
 	\begin{equation}
@@
 	for all $\phi \in [0,2\pi)$. 
-	Finally, we obtain the measurement $\mu$ of the form
-	\begin{equation}
-	\begin{split}
-	\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
-	\proj{0} V_1^\dagger, \\ 
-	\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
-	\proj{1} V_1^\dagger.  
-	\end{split}
-	\end{equation} 
 \end{proof}

### 2023-01-31 txt/manuscript.tex
Update manuscript

@@
 \texttt{Python >= 3.8}\newline
-\texttt{amazon-braket-sdk \textapprox= 1.33.0}\newline
-\texttt{numpy \textapprox= 1.14.5}\newline
-\texttt{scipy \textapprox= 1.7.3}\newline
+\texttt{numpy \textapprox= 1.22.0}\newline
+\texttt{scipy \textapprox= 1.7.0}\newline
 \texttt{pandas \textapprox= 1.5.0}\newline
-\texttt{pydantic \textapprox= 1.9.0}\newline
-\texttt{qiskit \textapprox= 0.39.0}\newline
+\texttt{amazon-braket-sdk >= 1.11.1}\newline
+\texttt{pydantic \textapprox= 1.9.1}\newline
+\texttt{qiskit \textapprox= 0.37.2}\newline
 \texttt{mthree \textapprox= 1.1.0}\newline
 \texttt{tqdm \textapprox= 4.64.1}\newline
-\texttt{pyyaml \textapprox= 6.0} \todo[inline]{everything???}\\
-\hline 
-C8 & If available Link to developer documentation/manual & \todo[inline]{???}\\
+\texttt{pyyaml \textapprox= 6.0}\newline
+\texttt{qiskit-braket-provider \textapprox= 0.0.3}\\
+\hline
+C8 & If available Link to developer documentation/manual &
+\url{https://pyqbench.readthedocs.io/en/latest/}\\
 \hline
@@
 \section{Motivation and significance}
+
+Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market,
+with a wide selection of devices based on different architectures and accompanying software
+solutions. Among hardware providers offering public access to their gate--based devices, one could
+mention Rigetti, IBM, Oxford Quantum Group, IonQ or Xanadu. Other vendors offer devices operating in
+different paradigms. Notably, one could mention D-Wave and their quantum
+annealers, or QuEra devices based on neural atoms. \todo[inline]{Expand this list and provide short
+description of those architectures}. Most vendors provide their own software stack and
+application programming interface for accessing their devices. To name a few, Rigetti's computers
+are available through their Forest SDK and PyQuil library and IBM Q computers can be accessed
+through Qiskit or IBM Quantum Experience web interface. Some cloud services, like Amazon Braket, offer access to several quantum devices under a unified API. On top of that, several
+libraries and frameworks can integrate with different hardware vendors. Examples of such frameworks
+include IBM Q's Qiskit or Zapata Computing's Orquestra.
+
+It is well known that NISQ devices have their limitations. The question is to what extent those
+devices can perform meaningful computations? To answer this question, one has to devise a
+methodology for benchmarking them. For gate--based computers, on which this paper focuses, there
+already exist several approaches. \todo[inline]{List the methods}.
+
+\todo[inline]{What benchmarking techniques are readily available?}
+
+In this paper, we introduce yet another method for benchmarking gate--based devices with a simple
+operational interpretation. In our method, we test how well the given device can distinguish between
+two von Neumann measurements performed in different bases. We implemented our method in an
+open-source Python library called PyQBench. The library supports any device available through Qiskit
+library, and thus can be used with providers such as IBM Q or Amazon Braket. Along with the library,
+the PyQBench package contains a command line tool for running benchmarks in most common scenarios.
+
+\begin{itemize}
+	\item NISQs are becoming widespread and easily available for the general audience
+	\item As with any computational technology, there's a need for benchmarking NISQs to assess
+	their potential usability.
+	\item Our work aims to provide a new benchmarking scheme for gate-based devices.
+	\item Why is PyQBench important?
+	\begin{itemize}
+		\item There exist multiple benchmarking methods already on the market
+		\item Most of them have the following drawbacks:
+		\begin{itemize}
+			\item Their interpretation is not very intuitive (We cannot phrase it like this without
+			explaining why it is so)
+			\item Hard to use (is this true?)
+			\item No libraries are readily available in Python (needs to be checked).
+		\end{itemize}
+		\item PyQBench is easy to install, it works with any Qiskit backend, and its results are
+		easy to understand and interpret.
+	\end{itemize}
+\end{itemize}
 

### 2023-02-01 txt/manuscript.tex
benchmarki

@@
 methodology for benchmarking them. For gate--based computers, on which this paper focuses, there
-already exist several approaches. \todo[inline]{List the methods}.
-
+already exist several approaches. \todo[inline]{List the methods}
+
+\begin{itemize}
+	\item several examples of benchmarks -- all our metrics are readily available for devices with two qubits only and circuit depths $< 10$  for all benchmarks it should be possible to execute
+	tweaked variants on larger devices when they become available \cite{cornelissen2021scalable}
+	\item random benchmarking \cite{liu2022sampling, knill2007randomized, wallman2014randomized} and general overwiev see here \cite{helsen2022general}
+	\item MQT Bench: Benchmarking Software and
+	Design Automation Tools for Quantum Computing \cite{mqt2022} -- przejebane 
+	\item QUARK framework for quantum compjuting application benchmarking for QUBO using D-QAwe ? \cite{quark2022} --  (e. g., a novel QUBO formulation
+	of the partial MAX-SAT problem) and benchmark these on
+	different infrastructures (e. g., D-Wave and simulation). 
+	\item SupermarQ: A Scalable Quantum Benchmark Suite -- Recent works within the quantum computer architecture
+	community have taken the first steps towards quantum
+	benchmarking. The PPL+2020 [16] suite was evaluated on
+	seven superconducting QPUs, focused on characterizing the
+	error rates of different operations, and demonstrated the
+	time dependence of their performance. The TriQ [17] suite
+	was used to perform a cross-platform comparison between
+	superconducting and trapped-ion systems and revealed the
+	importance of software visibility into the hardware’s native
+	gates. However, the scalability of these suites is limited by
+	their reliance on circuit simulation to estimate how well the
+	QPUs are performing. SupermarQ extends these works by
+	introducing a systematic and principled approach to building
+	a scalable quantum benchmark suite \cite{supermarq2022}
+
+\end{itemize}
 \todo[inline]{What benchmarking techniques are readily available?}
@@
 \begin{thebibliography}{00}
-
+	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
+S., Smith, K.
+N., Viszlai, J., ...
+Chong, F.
+T.
+(2022, April).
+Supermarq: A scalable quantum benchmark suite.
+In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp.
+587-603).
+IEEE.
+	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
+	\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
+B., Jost, J.
+D., ...
+Wineland, D.
+J.
+(2008).
+Randomized benchmarking of quantum gates.
+Physical Review A, 77(1), 012307.
+	\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
+	\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
+ \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
+(2021).
+Benchmarking near-term quantum computers via random circuit sampling.
+arXiv preprint arXiv:2105.05232.
+\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
+\bibitem{quark2022} Finžgar, J.
+R., Ross, P., Hölscher, L., Klepsch, J.,  Luckow, A.
+(2022, September).
+QUARK: A framework for quantum computing application benchmarking.
+In 2022 IEEE International Conference on Quantum Computing and Engineering (QCE) (pp.
+226-237).
+IEEE.
 \bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and

### 2023-02-11 txt/manuscript.tex
lecimy

@@
 However, for a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
-
-\todo[inline]{to be continued }
+The workflow is best describe as a list of steps:
+
+\begin{enumerate}
+
+\item Preparing configuration files describing backend and the experiment scenario.
+\item Submitting/running experiments. Depending on the experiment scenario, execution can be synchronous, or asynchronous.
+\item (optional) Checking status of the submitted jobs if the execution is asynchronous.
+\item For asynchronous jobs, 
+resolve jobs into actual measurements.
+\item Computing discrimination probabilities and outputting the resulting table.
+\end{enumerate} 
+\subsubsection{Preparing configuration files}
+To prepare configyurartion files we need to define the experiment and the   backend 
+which we want to benchmark. Experiments and backends are defined in YAML files. An example experiment definition looks as follows.
+
+\begin{lstlisting}[language=Python, caption=Defining the experiment]
+type: discrimination-fourier
+qubits:
+- target: 0
+ancilla: 1
+- target: 2
+ancilla: 3
+angles:
+start: 0
+stop: 2 * pi
+num_steps: 50
+gateset: ibmq
+method: direct_sum
+num_shots: 100
+\end{lstlisting}
+
+The components of the experiment is as follows:
+\begin{itemize}
+	\item The type describes type of the experiment.
+Currently, the only option for type is discrimination-fourier.
+In the future, other benchmarks may be added, in which keys the types key should contain their name.
+	\item The qubits list describes pair of qubits on which the experiment should be run. In our example, the benchmark will run on two pairs of qubits. First pair is 0 and 1, second pair is 2 and 3.
+	Notice that we distinguish between ancilla and target qubit, so e.g
+
+	\begin{lstlisting}[language=Python]
+qubits:
+	- target: 0
+      ancilla: 1
+	\end{lstlisting}
+	is not the same as 
+	\begin{lstlisting}[language=Python]
+qubits:
+	- target: 1
+      ancilla: 0
+	\end{lstlisting}
+\item The angles key describe range of angles for Fourier parametrized family.
+The range is always uniform, starts at the start, ends at stop and contains num$\_$steps points, including both start and stop.
+The start and stop can be arithmetic expressions using pi literal.
+For instance range defined as:
+\begin{lstlisting}[language=Python]
+angles:
+	start: 0
+	stop: 2 *pi
+	num_steps: 3
+\end{lstlisting}
+ would contain three angles $0, \pi$  and $2\pi$.
+ \item The gateset key informs what gates can be used in the experiment. The possible choices are [imbq, lucy, rigetti, ]. ... 
+ \item he method can take one of two values: direct$\_$sum or postselection, and as the name suggests, defines which method is used to implement the experiment.
+ \item The num$\_$shots defines how many shots are performed in the experiment for particular angle, qubit pair and circuit.
+For the purpose of calculating possible costs, this is how you compute total number of shots and executed circuits.
+Let $N$ be the number of qubit pairs in qubits key and let $M$ be the number of steps defined in the angles key.
+Then number of executed circuits is $2MN$ for the direct$\_$sum method and $4MN$ for the postselection method.
+Each of those circuits is executed num$\_$shots times.
+\end{itemize}
+
+Observe that the experiment file does not specify what backend to use. This way, the same experiment file can be used on multiple backends.
+Defining a backend may be quit complicated.
+Different backends may require different information to be used.
+For instance, IBMQ backends might require hub, group and project, whereas backends from the Aer package do not.
+Hence, the exact format of the YAML file depends on what backend one wants to use.
+Below are the available options.
+
+\begin{lstlisting}[language=Python, caption=IBMQ backends]
+name: ibmq_quito
+asynchronous: true
+provider:
+	hub: ibm-q
+	group: open
+	project: main
+\end{lstlisting}
+
+IBMQ backends typically require and access token to IBM Quantum Experience.
+It would be unsafe to store them in plain text, and therefore the token is configured separately.
+Before running the experiment, you should place your token in the IBMQ$\_$TOKEN environmental variable.
+
+\subsubsection{Backends obtainable from simple providers}
+In many cases, backend can be created using Provider.get$\_$backend() method. For such cases, PyQBench provides a simple description. For instance:
+
+\begin{lstlisting}[language=Python]
+provider: qiskit_braket_provider:AWSBraketProvider
+name: SV1
+asynchronous: true
+\end{lstlisting}
+
+This backend will be created using code similar to the one below:
+
+\begin{lstlisting}[language=Python]
+from qiskit_braket_provider import AWSBraketProvider
+
+provider = AWSBraketProvider()
+backend = provider.get_backend("SV1")
+\end{lstlisting}
+
+For this to work, the following conditions have to be satisfied:
+provider key has to contain full Python path of the provider class, where the class itself is separated from the module with colon. The provider class needs to have parameter-less initializer.
+
+\subsubsection{Backends constructed from a simple function call???}
+\subsubsection{Notes on using the asynchronous flag???}
+\subsubsection{Running the experiment and collecting measurements data}
+Running the experiment is done by using the following command line invocation:
+
+\begin{lstlisting}[language=Python]
+qbench disc-fourier benchmark experiment_file.yaml backend_file.yaml
+\end{lstlisting}
+The output file will be printed to stdout. Optionally, the - -output OUTPUT flag might be provided to write the output to the OUTPUT file instead.
+
+The result of running the above command can be twofold:
+\begin{itemize}
+	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, job $\_$ids correlated with the circuit they correspond to.
+	\item If the backend is synchronous, the output will contain measurement data (bitstrings) for each of the circuits run.
+\end{itemize}
+
+\todo[inline]{outputy???}
+
+\subsubsection{(Optional) Getting status of asynchronous jobs}
+The whole point of running the asynchronous jobs is to be able to retrieve the results at a later point in time.
+But how do you know that the jobs you submitted to the backend have completed or not?
+You can of course, inspect the file manually and check e.g.
+IBMQ dashboard to see the statuses of the jobs.
+However, PyQBench provides a helper command that will fetch the statuses for you.
+The command is:
+\begin{lstlisting}[language=Python]
+qbench disc-fourier status async-results.yml
+\end{lstlisting}
+and it will display dictionary with histogram of statuses.
+
+\subsubsection{Resolving asynchronous jobs}
+Before we can compute the discrimination probabilities, we have to obtain measurements from the submitted jobs. This is done using the following command:
+
+\begin{lstlisting}[language=Python]
+qbench disc-fourier resolve async-results.yml resolved.yml
+\end{lstlisting}
+
+The resolved results, stored in resolved.yml, would look just like the experiment was run synchronously.
+In other words, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment.
+We are ready to move on to computing probabilities.
+
+\subsubsection{Computing probabilities}
+To construct a table with discrimination probabilities, you can use the following command
+
+\begin{lstlisting}[language=Python]
+qbench disc-fourier tabulate resolved.yml results.csv 
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python]
+target,ancilla,phi,disc_prob,mit_disc_prob
+0,1,0.0,0.5009,0.5009414225941422
+0,1,0.3141592653589793,0.56505,0.5680439330543934
+0,1,0.6283185307179586,0.62695,0.6327928870292887
+0,1,0.9424777960769379,0.69045,0.6992154811715481
+0,1,1.2566370614359172,0.76165,0.7736924686192469
+0,1,1.5707963267948966,0.81305,0.8274581589958159
+\end{lstlisting}
+
+As we can see, it contains a single row for each tuple of (target, ancilla, phi).
+The disc$\_$prob column will contain the discrimination probability for given configuration.
+The mit$\_$disc$\_$prob column contains discrimination probability if Mthree mitigation was applied.
 

### 2023-02-11 txt/manuscript.tex
cli added

--- 2023-02-01 txt/manuscript.tex
@@
 \end{tabular}
-\caption{Code metadata (mandatory)}
+\caption{Code metadata}
 \label{}
@@
 In Section~\ref{sec:maths}, we introduce the necessary notation and preliminaries needed to understand the concept of PyQBench. Next, in Section~\ref{sec:discrimination-scheme},
-we will present a general overview of the discrimination scheme in theoretical terms. We will also mention NISQ devices' limitations and possible practical solutions in the implementation process.
+we will present a general overview of the discrimination scheme in theoretical terms. We will also mention NISQ devices' limitations and possible practical solutions during implementation process.
 
 \subsection{Mathematical preliminaries}\label{sec:maths}
-Recall that a general quantum
+A general quantum
 measurement, that is a positive operator valued measure (POVM) $\PP$ is a
@@
 for which all the effects are rank-one projectors. Every such measurement can be
-parameterized by a unitary matrix $U$ which the effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
-are created by taking $\ket{u_i}$ as  $i+1$-th column of the unitary matrix $U$.
+parameterized by a unitary matrix $U$ which effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+are created by taking $\ket{u_i}$ as  $(i+1)$-th column of the unitary matrix $U$.
 We will denote von Neumann measurements described by the matrix $U$ by $\PP_{U}$.
@@
 	\includegraphics[scale=1.7]{pics/vonneuman}
-	\caption{Decomposition of von Neumann measurement}
+	\caption{Decomposition of a von Neumann measurement $\PP_{U}$. }
 	\label{fig:vonnneuman}
@@
 
-Without loss of generality, we consider discrimination between a measurement in the computational
+Without loss of generality, we consider discrimination task between a measurement in the computational
 Z-basis ($\PP_\Id$), and an alternative measurement performed in the basis $U$
-($\PP_U$)\footnote{Explaining why we can consider only Z-basis and alternative measurement is beyond
+($\PP_U$)\footnote{Explaining why we can consider only Z-basis and alternative measurement $\PP_{U}$ is beyond
 	the scope of this technical documentation. See \cite{puchala2018strategies} if you are interested in
@@
 
-In general, the discrimination scheme, presented in Fig.\ref{fig:theoretical_scheme}, requires a
-second system of the same dimensionality as the measured one. First, the joint system is prepared in
+In general, the discrimination scheme, presented in Fig.~\ref{fig:theoretical_scheme}, requires an
+auxiliary system of the same dimensionality as the measured one. First, the joint system is prepared in
 some state $\ket{\psi_0}$. Then, the unknown measurement is performed on the first part of the
@@
 
-	The first idea is very simple. Instead of performing a conditional measurement, for each
+	The first idea uses a postselection. Instead of performing a conditional measurement, for each
 	measurement $\PP_U, \PP_\Id$ to be discriminated and each choice of $k \in \{0, 1\}$ we run circuit presented in Fig. \ref{fig:postselection}.
@@
 		\caption{
-			Postselection scheme of discrimination between von Neumann measurements $\PP_{U}$ and $\PP_\Id$.
+			A schematic representation of the setup for distinguishing
+			measurements $\PP_{U}$ and $\PP_{\Id}$ using direct sum.
 		}\label{fig:postselection}
@@
 
-	But now our experiment does not match the previously described scheme, right?
-	Yes, unless we discard all the outcomes for which $i\ne k$ (hence the name \emph{postselection},
-	we are selecting valid outcomes after the experiment is performed).
+%	But now our experiment does not match the previously described scheme, right?
+%	Yes, unless we discard all the outcomes for which $i\ne k$ (hence the name \emph{postselection},
+%	we are selecting valid outcomes after the experiment is performed).
 
@@
 	% \end{enumerate}
-
-	More precisely, our experiments can be grouped into classes identified by tuples of the form
-	$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen measurement.
-	We discard all the experiments for which $k \ne i$. Hence, the total number of valid experiments is
+The experiments can be grouped into classes identified by tuples of the form
+	$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen measurement, $k \in \{0,1\}$, $i \in \{0,1\}$ and $j \in \{0,1\}$.
+	In postselection approach, we discard all the experiments for which $k \ne i$. Hence, the total number of valid experiments is
 
@@
 
-	We now need to count the experiments (among the valid ones) resulting in successful discrimination.
+	Finally, we count the experiments (among the valid ones) resulting in successful discrimination.
 	If we have chosen $\PP_U$, then we guess correctly iff $j=0$. Similarly, for
@@
 
-	\begin{enumerate}
-		\item We prepare the discriminator $\ket{\psi_{0}}$ on bipartite
-		system.
-		%\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
-		%$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
-		\item We apply one of unitary,   either $U^\dagger$ or
-		$\Id$, on the first system.
-		%\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
+The second idea uses  the direct sum $V_0^\dagger \oplus V_1^\dagger.$    Here, instead of performing a conditional
+measurement $\PP_{V_k}$, where $k\in \{0,1\}$ we run circuit presented in	Fig.~\ref{fig:controlled}.
+%	\begin{enumerate}
+%		\item We prepare the discriminator $\ket{\psi_{0}}$ on bipartite
+%		system.
+%		%\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
+%		%$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
+%		\item We apply one of unitary,   either $U^\dagger$ or
+%		$\Id$, on the first system.
+%		%\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
 Observe that   $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger} = \proj{0} \otimes \Phi_{V_0^\dagger}  + \proj{1} \otimes \Phi_{V_1^\dagger}.
 $
-		\item We apply direct sum $V_0^\dagger \oplus V_1^\dagger$ on the whole systems.
-		\item We measure both systems in computational basis $\Delta$.
-		\item We make a decision based on the received label $j$ on the second system. If $j=0$, then we
-		decide that $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs.
-	\end{enumerate}
-
-	The schematic representation of this setup is depicted in
-	Fig.~\ref{fig:controlled}.
+%		\item We apply direct sum $V_0^\dagger \oplus V_1^\dagger$ on the whole systems.
+%		\item We measure both systems in computational basis $\Delta$.
+%		\item We make a decision based on the received label $j$ on the second system. If $j=0$, then we
+%		decide that $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs.
+%	\end{enumerate}
+
+%	The schematic representation of this setup is depicted in
+%	Fig.~\ref{fig:controlled}.
 	\begin{figure}[h!]
@@
 		\caption{ A schematic representation of the setup for distinguishing
-			measurements using controlled unitary gate.
+			measurements $\PP_{U}$ and $\PP_{\Id}$ using direct sum.
 		}\label{fig:controlled}
@@
 
+\section{Discrimination scheme for parameterized Fourier family and implementation}
+
+So far, we only discussed how the discrimination is performed using two different
+schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known.
+It turned out that the determination of $V_0$ and $V_1$ is a simple task while the discriminator $\ket{\psi_{0}}$ is known.
+However,
+sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
+is, in general, NP-hard problem.
+We have found the analytical solution of the discrimination scheme for a particular class of von Neumann measurements.
+
+Here,  we will show how all the necessary ingredients look like for
+von Neumann measurements defined by the parameterized Fourier family:
+
+\begin{equation}
+U = H
+\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger,
+\end{equation}
+where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
+In this case, the optimal input state is Bell state of the form
+\begin{equation}
+\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \ket{00} + \ket{11}.
+\end{equation}
+And, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
+have the following form
+\begin{equation}
+V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
+\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
+	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+\end{equation}
+\begin{equation}
+V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
+\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
+&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+\end{equation}
+Finally, we have also calculated the theoretical probability of correct discrimination between von Neumann
+measurements $\PP_U$ and $\PP_{\Id}$ is given by
+\begin{equation}
+p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
+\end{equation}
+More details and proofs of the construction's validity   we can find in the \ref{app:optimal-probability} and \ref{app:optimal-strategy}.
+
  \section{Software description}
@@
 \begin{itemize}
-\item As a library. This is a more extensible, but also more laborious way of using PyQBench. Most importantly, this way allows for more advanced scripting defining your own measurements scheme.
-
-\item As a CLI tool. This mode of operation trades extensibility for simplicity of usage, as it allows only for running Fourier-discrimination experiments defined with simple YAML input files.
+\item As a library. This way allows for more advanced scripting defining your own measurements scheme.
+
+\item As a CLI tool. This mode of operation trades extensibility for simplicity of usage, as it allows only for running Fourier-discrimination experiments defined with  YAML input files.
 \end{itemize}
 
-\subsubsection{PyQBench as a library}\label{sec:pyqbench-as-library}
+\section{PyQBench as a library}\label{sec:pyqbench-as-library}
 This guide introduces basic concepts needed for using PyQBench as a library from a Python script. In particular, we will cover the following topics:
@@
 \item Assembling circuits needed for given benchmarking scheme.
-\item Running experiment on simulator or hardware.
+\item Running experiment on a simulator or a hardware.
 \item Obtaining empirical probability of successful discrimination between measurements.
@@
 \end{enumerate}
-Currently available quantum computers typically cannot start execution from an arbitrary state.
+%Currently available quantum computers typically cannot start execution from an arbitrary state.
 Instead, we have to prepare it ourselves.
-Hence, to execute experiment using postselection scheme, we need an instruction taking to the desired discriminator
-and instructions implementing $U^\dagger$, $V_0^\dagger$ and $V_1^\dagger$.
+Hence, to execute experiment using postselection scheme, we need an instruction taking to the desired discriminator $\ket{\psi_0}$
+%and instructions implementing $U^\dagger$, $V_0^\dagger$ and $V_1^\dagger$.
+Whereas, execute experiment using direct sum approach, we need an instruction taking to the desired discriminator  $\ket{\psi_0}$
+%and instructions implementing $U^\dagger$, $V_0^\dagger \oplus V_1^\dagger$.
 
@@
 In our example, we will use $U =  H$ (the Hadamard gate).
-To keep us focused on the implementation in PyQBench and not delve too deep into mathematical explanation, we simply provide explicit formulas for discriminator $\ket{\Psi_0} $, $V_0$ and $V_1$, leaving the calculations to the interested reader.
-
-The explicit formula for discriminator in our toy model reads:
-\begin{equation}
-\ket{\Psi_0} = \frac{1}{\sqrt{2}} (\ket{00} + \ket{11}),
+% To keep us focused on the implementation in PyQBench and not delve too deep into mathematical explanation, we simply provide explicit formulas for discriminator $\ket{\Psi_0} $, $V_0$ and $V_1$, leaving the calculations to the interested reader.
+The explicit formula for discriminator in this model reads
+\begin{equation}
+\ket{\psi_0} = \frac{1}{\sqrt{2}} (\ket{00} + \ket{11}),
 \end{equation}
@@
 \end{equation}
-
 As a next step, we need decompose our matrices into actual sequences of gates.
-We are lucky, because our discriminator is just a Bell state. Thus, the circuit taking $\ket{00}$ to $\ket{\Phi_0}$ is well known, and comprises Hadamard gate followed by CNOT gate on both qubits.
+The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$ is well known, and comprises Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
 \begin{figure}[h!]
@@
 	\includegraphics[scale=1.7]{pics/discriminator}
-	\caption{Decomposition of the discriminator $\ket{\Phi_0}$. }
+	\caption{Decomposition of the discriminator $\ket{\psi_0}$. }
 	\label{fig:discriminator}
 \end{figure}
-
 For $V_0$ and $V_1$ observe that $V_0 = RY\left(\frac{3}{4} \pi \right) $, where $RY$ is rotation gate around the $Y$ axis defined by
@@
 \end{equation}
-
-Now running the simulation is as simple as invoking functions imported from qbench package.
-
+Finally, the optimal probability of correct discrimination between $\PP_{U}$, where $U=H$ and $\PP_{\Id}$ is given by 
+\begin{equation}
+p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{\sqrt{2}}{4}. 
+\end{equation}
+The detailed calculation we can see in \ref{app:hadamard}.
+
+Now we simulate  theoretical framework using PyQBench. We will start with simulation in Qiskit SDK with Aer simulator. First, we import necessary modules. \todo[inline]{czy to zdanie jest poprawne?} 
 \todo[inline]{listingi swieca sie na razie jak choinka ale bedziemy kolorki drasowac}
+
+\begin{lstlisting}[language=Python]
+from qiskit import QuantumCircuit, Aer
+import numpy as np
+\end{lstlisting}
+Next we import needed functions from PyQBench. For our example we will need two functions. 
+\begin{lstlisting}[language=Python]
+from qbench.schemes.postselection import benchmark_using_postselection
+from qbench.schemes.direct_sum import benchmark_using_direct_sum
+\end{lstlisting}
+To run any of these functions, we need to define components that we discussed below.
+Most importantly, we need to create Qiskit instructions, not circuits.
+We can conveniently do so by constructing circuit acting on qubits 0 and 1 and then converting them using \textit{to\_instruction()} method.
+\begin{lstlisting}[language=Python, caption= Defining components for Hadamard experiment]
+def state_prep():
+	circuit = QuantumCircuit(2)
+	circuit.h(0)
+	circuit.cnot(0, 1)
+	return circuit.to_instruction()
+
+def u_dag():
+	circuit = QuantumCircuit(1)
+	circuit.h(0)
+	return circuit.to_instruction()
+
+def v0_dag():
+	circuit = QuantumCircuit(1)
+	circuit.ry(-np.pi * 3 / 4, 0)
+	return circuit.to_instruction()
+
+def v1_dag():
+	circuit = QuantumCircuit(1)
+	circuit.ry(-np.pi * 3 / 4, 0)
+	circuit.x(0)
+	return circuit.to_instruction()
+
+def v0_v1_direct_sum_dag():
+	circuit = QuantumCircuit(2)
+	circuit.ry(-np.pi * 3 / 4, 0)
+	circuit.cnot(0, 1)
+	return circuit.to_instruction()
+
+\end{lstlisting}
+For the purpose of this example,  we define Qiskit Aer simulator.
+\begin{lstlisting}[language=Python, caption= Defining a backend]
+simulator = Aer.get_backend("aer_simulator")
+
+\end{lstlisting}
+Now running the simulation is as simple as invoking functions imported from PyQBench package.
 \begin{lstlisting}[language=Python, caption=Simulation benchmark by using postselection]
-
-simulator = Aer.get_backend("aer_simulator")
 postselection_result = benchmark_using_postselection(
@@
 \begin{lstlisting}[language=Python, caption=Simulation benchmark by using direct sum]
-
-simulator = Aer.get_backend("aer_simulator")
 direct_sum_result = benchmark_using_direct_sum(
@@
 \end{lstlisting}
-
+Finally, we calculate the empirical probability obtained from postselection and direct sum experiment and calculate the absolute error between analytical and empirical results. 
 \begin{lstlisting}[language=Python, caption=Computation of probability]
 p_succ = (2 + np.sqrt(2)) / 4
-print(f"Real p_succ = {p_succ}")
+print(f"Analytical p_succ = {p_succ}")
 print(
@@
 \begin{lstlisting}
-Real p_succ = 0.8535533905932737
+Analytical p_succ = 0.8535533905932737
 Postselection: p_succ = 0.8559797193791593, abs. error = -0.0024263287858855564
@@
 But what if we want more control over some parts of this process?
-Maybe we want play around with some models?
-Or maybe we want to run the same experiment on multiple backends and we don’t want them to be assembled over and over again?
-
- PyQBench provides functions performing:
+One possibility would be to add more and more parameters to \textit{benchmark\_using\_xyz} functions, but this approach clearly is not very scalable.
+Also, there is no way we can anticipate all the possible use cases.
+ We decided on another approach.  PyQBench provides functions performing:
 \begin{enumerate}
@@
 \end{enumerate}
-When using these functions, you need to take care of running circuits on some backend yourself, but it gives you unlimited power over the whole process.
-The difference between such approaches is illustrated on the diagrams below.
-
-When using these functions, you need to take care of running circuits on some backend yourself, but it gives you unlimited power over the whole process.
  The difference between the two approaches is illustrated on the diagrams below.
 
-\begin{figure}
+\begin{figure}[ht!]
 	\centering
@@
 		\centering
-		\includegraphics[width=1\textwidth]{pics/scheme1}
+		\includegraphics[width=0.8\textwidth]{pics/scheme1}
 %		\caption{$y=x$}
@@
 		\centering
-	\includegraphics[width=1\textwidth]{pics/scheme2}
-%		\caption{$y=3\sin x$}
+	\includegraphics[width=0.8\textwidth]{pics/scheme2}
 		\label{fig:execution}
@@
 
-Next, we divide the experiment into two parts:
+By choosing this approach we need to divide the experiment into two parts:
 \begin{enumerate}
@@
 \end{enumerate}
-
 Let us focus only on the postselection case, as the direct sum case is analogous. In addition, we need to import two more functions from PyQBench.
-
 \begin{lstlisting}[language=Python, caption=Assembling circuits]
@@
 )
-
+\end{lstlisting}
+The function \textit{assemble\_postselection\_circuits} creates all of neceserry circuits, nicely packed in a dictionary.
+Each informs if the circuit implements identity or alternative measurement on the target qubit, and which of $V_0$ and
+$V_1$ is used.
+\begin{lstlisting}[language=Python]
 circuits = assemble_postselection_circuits(
@@
 
-circuits
-\end{lstlisting}
-
+\end{lstlisting}
 %
@@
 %\end{lstlisting}
-
 Now we only need to run the circuits.
-To make things more interesting, we will run a noisy and noiseless simulation of our circuits.
+To make this example more interesting, we will run a noisy and noiseless simulation of our circuits.
 We will use the same backend as before, and our noise model will only comprise readout errors on both qubits.
-
 \begin{lstlisting}[language=Python, caption=Noise models]
@@
 noise_model.add_readout_error(error, [1])
-
-noise_model
-\end{lstlisting}
-
+\end{lstlisting}
 Once we have our noise model ready, we can execute our circuits with and without noise.
@@
 One caveat is that we have to keep track which measurements correspond to which circuit.
-We do so by fixing an ordering on the keys in circuits dictionary.
-
+We do so by fixing an ordering on the keys in \textit{circuits} dictionary.
 \begin{lstlisting}[language=Python, caption=Running  circuits]
@@
 counts_noiseless = execute(all_circuits, backend=simulator, shots=10000).result().get_counts()
-
-print(f"Noisless counts: {counts_noiseless}")
-print(f"Noisy counts: {counts_noisy}")
-\end{lstlisting}
-
-%
-%Noisless counts: [{'11': 737, '00': 731, '10': 4163, '01': 4369}, {'01': 750, '00': 4217, '10': 716, '11': 4317}, {'01': 740, '10': 693, '00': 4209, '11': 4358}, {'11': 775, '01': 4341, '00': 765, '10': 4119}]
-%Noisy counts: [{'01': 1720, '11': 514, '10': 1760, '00': 6006}, {'11': 529, '00': 6025, '10': 1705, '01': 1741}, {'11': 531, '01': 1726, '00': 5956, '10': 1787}, {'01': 1808, '11': 515, '10': 1681, '00': 5996}]
-
-Finally, the only thing left is to compute the success probabilities. We do so by passing bitstring counts to function \\ \texttt{compute\_probabilities\_from\_postselection\_measurements}.
+\end{lstlisting}
+Finally, we compute the success probabilities. We do so by passing bitstring counts to  \textit{compute\_probabilities\_from\_postselection\_measurements} function.
 
@@
 \end{lstlisting}
-The success probability is 0.8524401115559386, whereas if we obtain some noise, the succes probability is equal to 0.5017958400693446
+The success probability is 0.8524401115559386, whereas if we obtain some noise, the success probability is equal to 0.5017958400693446
 As expected, noisy simulations gave us results that are further away from the exact ones.
-
-This concludes introduction to PyQBench library. If you are interested see additoinal usage examples in our examples directory.
-
-\subsubsection{PyQBench as a CLI tool}\label{sec:pyqbench-as-cli}
+This concludes introduction to PyQBench library.
+
+\section{PyQBench as a CLI tool}\label{sec:pyqbench-as-cli}
 Using PyQBench as a library allows one to conduct, in principle, arbitrary two-qubit von Neumann measurement experiment.
 However, as discussed in the previous guide, it requires some amount of boilerplate code.
-
-However, for a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
-
-\todo[inline]{to be continued }
-
-\section{Discrimination scheme for parameterized Fourier family and implementation}
-
-\subsection{Discrimination scheme}
-So far, we only discussed how the discrimination is performed using two different
-schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known.
-It turned out that the determination of $V_0$ and $V_1$ is a simple task while the discriminator $\ket{\psi_{0}}$ is known.
-However,
-sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
-is, in general, NP-hard problem.
-We have found the analytical solution of the discrimination scheme for a particular class of von Neumann measurements.
-
-Here,  we will show how all the necessary ingredients look like for
-von Neumann measurements defined by the parameterized Fourier family:
-
-\begin{equation}
-	U = H
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger,
-\end{equation}
-where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this case, the optimal input state is Bell state of the form
-\begin{equation}
-	\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \ket{00} + \ket{11}.
-\end{equation}
-And, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
-have the following form
-\begin{equation}
-	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
-		\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
-			\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
-\end{equation}
-\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
-		\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
-		&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
-\end{equation}
-Finally, we have also calculated the theoretical probability of correct discrimination between von Neumann
-measurements $\PP_U$ and $\PP_{\Id}$ is given by
-\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
-\end{equation}
-More details and proofs of the construction's validity   we can find in the \ref{app:optimal-probability} and \ref{app:optimal-strategy}.
-
-\subsection{Implementation}
-Here, we will present the results obtained on real devices. For this work we chose IMBQ software. \todo[inline]{tu dokladne informacje o maszynie i rysuneczki}
+For a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
+The workflow is best describe as a list of steps:
+
+\begin{enumerate}
+
+\item Preparing configuration files describing backend and the experiment scenario.
+\item Submitting/running experiments. Depending on the experiment scenario, execution can be synchronous, or asynchronous.
+\item (optional) Checking status of the submitted jobs if the execution is asynchronous.
+\item For asynchronous jobs, 
+resolve jobs into actual measurements.
+\item Computing discrimination probabilities and outputting the resulting table.
+\end{enumerate} 
+\subsubsection{Preparing configuration files}
+To prepare configyurartion files we need to define the experiment and the   backend 
+which we want to benchmark. Experiments and backends are defined in YAML files. An example experiment definition looks as follows.
+
+\begin{lstlisting}[language=Python, caption=Defining the experiment]
+type: discrimination-fourier
+qubits:
+	- target: 0
+	  ancilla: 1
+	- target: 2
+      ancilla: 3
+angles:
+	start: 0
+	stop: 2 * pi
+	num_steps: 50
+gateset: ibmq
+method: direct_sum
+num_shots: 100
+\end{lstlisting}
+
+The components of the experiment is as follows:
+\begin{itemize}
+	\item The \textit{type} describes type of the experiment.
+Currently, the only option for \textit{type} is \textit{discrimination-fourier}.
+In the future, other benchmarks may be added, in which keys the \textit{types} key should contain their name.
+	\begin{lstlisting}[language=Python]
+type: discrimination-fourier
+	\end{lstlisting}
+	\item The \textit{qubits} list describes pair of qubits on which the experiment should be run.
+In our example, the benchmark will run on two pairs of qubits.
+First pair is 0 and 1, second pair is 2 and 3.
+	Notice that we distinguish between ancilla and target qubit, so e.g
+
+	\begin{lstlisting}[language=Python]
+qubits:
+	- target: 0
+      ancilla: 1
+	\end{lstlisting}
+	is not the same as 
+	\begin{lstlisting}[language=Python]
+qubits:
+	- target: 1
+      ancilla: 0
+	\end{lstlisting}
+\item The \textit{angles} key describe range of angles for Fourier parametrized family.
+The range is always uniform, starts at the \textit{start}, ends at \textit{stop} and contains \textit{num\_steps} points, including both start and stop.
+The start and stop can be arithmetic expressions using \textit{pi} literal.
+For instance range defined as:
+\begin{lstlisting}[language=Python]
+angles:
+	start: 0
+	stop: 2 *pi
+	num_steps: 3
+\end{lstlisting}
+ would contain three angles $0, \pi$  and $2\pi$.
+ \item 
+ The \textit{gateset} key describes the gate decomposition of the experiment.
+The possible options are \textit{[ibmq, lucy, rigetti, generic]}.
+If the user choose the device-dependent key, that is one of the options \textit{ibmq, lucy, rigetti}, then the experiment will be implemented by using predefined sequence of native gates.
+If the user choose the \textit{generic} key, then the compiler  will automatically decompose given circuit in the way that is suitable for the device in use.
+ \begin{lstlisting}[language=Python]
+gateset: ibmq
+ \end{lstlisting}
+ \item The \textit{method} can take one of two values: \textit{direct\_sum} or \textit{postselection}, and as the name suggests, defines which method is used to implement the experiment.
+ \begin{lstlisting}[language=Python]
+method: direct_sum
+ \end{lstlisting}
+ \item The \textit{num\_shots} defines how many shots are performed in the experiment for particular angle, qubit pair and circuit.
+For the purpose of calculating possible costs, this is how you compute total number of shots and executed circuits.
+Let $N$ be the number of qubit pairs in \textit{qubits} key and let $M$ be the number of steps defined in the \textit{angles} key.
+Then number of executed circuits is $2MN$ for the \textit{direct\_sum} method and $4MN$ for the \textit{postselection} method.
+Each of those circuits is executed \textit{num\_shots} times.
+ \begin{lstlisting}[language=Python]
+num_shots: 100
+ \end{lstlisting}
+\end{itemize}
+
+Observe that the experiment file does not specify what backend to use. This way, the same experiment file can be used on multiple backends.
+ Different backends may require different information to be used.
+For instance, IBMQ backends might require hub, group and project, whereas backends from the \textit{Aer} package do not.
+Hence, the exact format of the YAML file depends on what backend one wants to use.
+Below we present
+ YAML file defining the IMBQ backend named Quito. 
+\begin{lstlisting}[language=Python, caption=IBMQ backend]
+name: ibmq_quito
+asynchronous: true
+provider:
+	hub: ibm-q
+	group: open
+	project: main
+\end{lstlisting}
+
+IBMQ backends typically require and access token to IBM Quantum Experience.
+It would be unsafe to store them in plain text, and therefore the token is configured separately.
+Before running the experiment, you should place your token in the \textit{IBMQ\_TOKEN} environmental variable.
+
+\subsubsection{Notes on using the asynchronous flag}
+In our example, the only key that requires the explanation is \textit{asynchronous} which determines whether experiments will be run asynchronously  (\textit{true}) or not (\textit{false}).
+ We recommend setting it to true, unless your experiment is really small (several circuits total).
+However, some backends may not support asynchronous execution.
+This might be especially the case with local simulators.
+
+For asynchronous execution to work, the following conditions have to be met:
+\begin{itemize}
+\item Jobs returned by the backend have unique \textit{job\_id}, 
+\item Job object is retrievable from the backend using \textit{backend.retrieve\_job} method, even from another process (e.g. if the original process running the experiment has finished).
+\end{itemize}
+Since PyQBench cannot determine if the job retrieval works for given backend, the user is responsible for checking it yourself.
+
+\todo[inline]{co z tymi sekcjami?}
+\subsubsection{Backends obtainable from simple providers???}
+\subsubsection{Backends constructed from a simple function call???}
+\todo[inline]{co z tymi sekcjami?}
+
+\subsubsection{Running the experiment and collecting measurements data}
+After preparing YAML files with defined experiment and backend, 
+running the experiment is done by using the following command line invocation:
+\begin{lstlisting}[language=Python]
+qbench disc-fourier benchmark experiment_file.yaml backend_file.yaml
+\end{lstlisting}
+The output file will be printed to stdout. Optionally, the \textit{- -output OUTPUT} flag might be provided to write the output to the \textit{OUTPUT} file instead.
+\begin{lstlisting}[language=Python]
+qbench disc-fourier benchmark experiment_file.yaml backend_file.yaml --async-results.yml
+\end{lstlisting}
+The result of running the above command can be twofold:
+\begin{itemize}
+	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, job$\_$ids correlated with the circuit they correspond to.
+	\item If the backend is synchronous, the output will contain measurement data (bitstrings) for each of the circuits run.
+\end{itemize}
+For asynchronous experiments, the output looks similar to the one below:
+\todo[inline]{result}
+
+For synchronous experiment, this looks as follows:
+\todo[inline]{result}
+
+\subsubsection{(Optional) Getting status of asynchronous jobs}
+The whole point of running the asynchronous jobs is to be able to retrieve the results at a later point in time.
+But how do we know that the jobs you submitted to the backend have completed or not?
+We can inspect the file manually and check e.g.
+IBMQ dashboard to see the statuses of the jobs.
+However, PyQBench provides a helper command that will fetch the statuses for you.
+The command is:
+\begin{lstlisting}[language=Python]
+qbench disc-fourier status async-results.yml
+\end{lstlisting}
+and it will display dictionary with histogram of statuses.
+
+\subsubsection{Resolving asynchronous jobs}
+If the status of jobs is \textit{DONE}, we have to obtain measurements from the submitted jobs. This is done using the following command:
+\begin{lstlisting}[language=Python]
+qbench disc-fourier resolve async-results.yml resolved.yml
+\end{lstlisting}
+The resolved results, stored in \textit{resolved.yml}, would look just like the experiment was run synchronously.
+In other words, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment.
+After this step, we are ready to computing probabilities.
+
+\subsubsection{Computing probabilities}
+To construct a table with discrimination probabilities, you can use the following command
+\begin{lstlisting}[language=Python]
+qbench disc-fourier tabulate resolved.yml results.csv 
+\end{lstlisting}
+The results are saved as file csv as a table.
+A single row for each tuple of \textit{(target, ancilla, phi)}.
+The \textit{disc\_prob} column will contain the discrimination probability for given configuration.
+The \textit{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
 
 \section{Impact}
-\todo[inline]{OJCIEC WYKAZ SIE, bo trzeba to dobrze sprzedac, nizej tekst z formatki softwarex}
+\todo[inline]{OJCIEC WYKAZ SIE, bo trzeba to dobrze sprzedac, nizej tekst z formatki softwarex co powinna zawierac ta sekcja}
 This software has two main contributions.
@@
 \bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
+\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
+\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
 \end{thebibliography}
@@
 
-\section{Optimal probability} \label{app:optimal-probability}
+\section{Discrimination task for Hadamard gate}\label{app:hadamard}
+\todo[inline]{!!!!!!}
+
+\section{Optimal probability for parametrized Fourier family} \label{app:optimal-probability}
 
@@
 
-\section{Optimal discrimination strategy} \label{app:optimal-strategy}
+\section{Optimal discrimination strategy for parametrized Fourier family} \label{app:optimal-strategy}
 

### 2023-02-11 txt/manuscript.tex
ehh

@@
 \begin{lstlisting}[language=Python]
-qbench disc-fourier benchmark experiment_file.yaml backend_file.yaml
+qbench disc-fourier benchmark experiment_file.yml backend_file.yml
 \end{lstlisting}
@@
 \begin{lstlisting}[language=Python]
-qbench disc-fourier benchmark experiment_file.yaml backend_file.yaml --async-results.yml
+qbench disc-fourier benchmark experiment_file.yml backend_file.yml --output async_results.yml
 \end{lstlisting}
@@
 \end{itemize}
-For asynchronous experiments, the output looks similar to the one below:
+For asynchronous experiments, the output is as follows:
 \todo[inline]{result}
 
-For synchronous experiment, this looks as follows:
+For synchronous experiment, the output looks similar to the one below: 
 \todo[inline]{result}
@@
 \begin{lstlisting}[language=Python]
-qbench disc-fourier status async-results.yml
+qbench disc-fourier status async_results.yml
 \end{lstlisting}

### 2023-02-13 txt/manuscript.tex
add examples

@@
 	basicstyle={\small\ttfamily},
-	numberstyle=\color{blue},
-	keywordstyle=\color{blue},
-	commentstyle=\color{PineGreen},
-	stringstyle=\color{ForestGreen},
+%	numberstyle=\color{blue},
+%	keywordstyle=\color{blue},
+%	commentstyle=\color{PineGreen},
+%	stringstyle=\color{ForestGreen},
 	breaklines=true,
@@
 	escapeinside={@}{@},
-	literate=
-	{0}{{{\color{red}0}}}1
-	{1}{{{\color{red}1}}}1
-	{2}{{{\color{red}2}}}1
-	{3}{{{\color{red}3}}}1
-	{4}{{{\color{red}4}}}1
-	{5}{{{\color{red}5}}}1
-	{6}{{{\color{red}6}}}1
-	{7}{{{\color{red}7}}}1
-	{8}{{{\color{red}8}}}1
-	{9}{{{\color{red}9}}}1
-    {v0}{{{\color{black}v0}}}1 %% we can not style only numeric literals
-    {v1}{{{\color{black}v1}}}1
+%	literate=
+%	{0}{{{\color{red}0}}}1
+%	{1}{{{\color{red}1}}}1
+%	{2}{{{\color{red}2}}}1
+%	{3}{{{\color{red}3}}}1
+%	{4}{{{\color{red}4}}}1
+%	{5}{{{\color{red}5}}}1
+%	{6}{{{\color{red}6}}}1
+%	{7}{{{\color{red}7}}}1
+%	{8}{{{\color{red}8}}}1
+%	{9}{{{\color{red}9}}}1
+%    {v0}{{{\color{black}v0}}}1 %% we can not style only numeric literals
+%    {v1}{{{\color{black}v1}}}1
 }
@@
 Now we simulate  theoretical framework using PyQBench. We will start with simulation in Qiskit SDK with Aer simulator. First, we import necessary modules. \todo[inline]{czy to zdanie jest poprawne?}
-\todo[inline]{listingi swieca sie na razie jak choinka ale bedziemy kolorki drasowac}
 
@@
 	  ancilla: 1
-	- target: 2
-      ancilla: 3
+	- target: 1
+      ancilla: 2
 angles:
@@
 	stop: 2 * pi
-	num_steps: 50
+	num_steps: 3
 gateset: ibmq
@@
 In our example, the benchmark will run on two pairs of qubits.
-First pair is 0 and 1, second pair is 2 and 3.
+First pair is 0 and 1, second pair is 1 and 2.
 	Notice that we distinguish between ancilla and target qubit, so e.g
@@
 name: ibmq_quito
-asynchronous: true
+asynchronous: false
 provider:
@@
 \end{itemize}
-For asynchronous experiments, the output is as follows:
-\todo[inline]{result}
 
 For synchronous experiment, the output looks similar to the one below: 
-\todo[inline]{result}
+\begin{lstlisting}[language=Python]
+metadata:
+	experiments:
+		type: discrimination-fourier
+		qubits:
+		- {target: 0, ancilla: 1}
+		- {target: 1, ancilla: 2}
+		angles: {start: 0.0, stop: 6.283185307179586, num_steps: 3}
+		gateset: ibmq
+		method: direct_sum
+		num_shots: 100
+	backend_description:
+		name: ibmq_quito
+		asynchronous: false
+		provider: {group: open, hub: ibm-q, project: main}
+data:
+- target: 0
+  ancilla: 1
+  phi: 0.0
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
+  - name: u
+  histogram: {'00': 30, '01': 16, '10': 28, '11': 26}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.2857378991684036, '01': 0.14975297832942433, '10': 0.28142307224788693, '11': 0.2830860502542851}
+- target: 0
+  ancilla: 1
+  phi: 3.141592653589793
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 4, '01': 5, '10': 45, '11': 46}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.011053610583159325, '01': 0.02261276648026373, '10': 0.4593955619936729, '11': 0.5069380609429042}
+  - name: u
+  histogram: {'00': 56, '01': 43, '10': 1}
+  mitigation_info:
+  target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+  ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.5573987337172156, '01': 0.44424718645642625, '10': -0.0016459201736417181}
+  - target: 0
+    ancilla: 1
+  phi: 6.283185307179586
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 36, '01': 18, '10': 25, '11': 21}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.3488190312089973, '01': 0.17355281935572894, '10': 0.2505792064871127, '11': 0.22704894294816103}
+  - name: u
+  histogram: {'00': 32, '01': 27, '10': 24, '11': 17}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.3025357275361897, '01': 0.27413673119534815, '10': 0.24313373302688793, '11': 0.18019380824157433}
+- target: 1
+  ancilla: 2
+  phi: 0.0
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 27, '01': 20, '10': 24, '11': 29}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+	ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
+  mitigated_histogram: {'00': 0.2594378169217188, '01': 0.19318893233269735, '10': 0.23035366874292057, '11': 0.3170195820026633}
+  - name: u
+  histogram: {'00': 31, '01': 24, '10': 23, '11': 22}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+	ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
+  mitigated_histogram: {'00': 0.30056875246775644, '01': 0.2438221628798003, '10': 0.22180309809696985, '11': 0.23380598655547338}
+- target: 1
+  ancilla: 2
+  phi: 3.141592653589793
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 5, '01': 4, '10': 50, '11': 41}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+	ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
+  mitigated_histogram: {'00': 0.009552870928837118, '01': 0.007194089383161034,
+  '10': 0.5236791012692514, '11': 0.4595739384187503}
+  - name: u
+  histogram: {'00': 41, '01': 51, '10': 3, '11': 5}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+	ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
+  mitigated_histogram: {'00': 0.4073387714165384, '01': 0.5614614121117936, '10': 0.006431862814564833, '11': 0.024767953657102992}
+- target: 1
+  ancilla: 2
+  phi: 6.283185307179586
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 30, '01': 28, '10': 23, '11': 19}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+	ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
+  mitigated_histogram: {'00': 0.2868459834940102, '01': 0.2919564941384742, '10': 0.22466574543735374, '11': 0.19653177693016174}
+  - name: u
+  histogram: {'00': 15, '01': 20, '10': 36, '11': 29}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+	ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
+  mitigated_histogram: {'00': 0.1187719606657805, '01': 0.1962085394489247, '10': 0.3710195249988589, '11': 0.31399997488643583}
+\end{lstlisting}
+Consider the particular experiment data
+\begin{lstlisting}[language=Python]
+data:
+- target: 0
+  ancilla: 1
+  phi: 0.0
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
+\end{lstlisting}
+	The data includes \textit{target, ancilla, phi},
+	and \textit{results\_pre\_circuit}.   The first three pieces of information have already been described. The last data  \textit{results\_pre\_circuit} gives us 
+	the following additional informations: 
+	\begin{itemize}
+		\item  name: id:  the information which measurement is used during experiment,   $\PP_{U}$ or $\PP_{\Id}$. In this example we consider  $\PP_{\Id}$. 
+		\item histogram: {'00': 28, '01': 26, '10': 21, '11': 25}: the dictionary with measurement's outcomes.
+The keys represent possible measurement oucomes, whereas the values present number of occurrences.
+		\item mitigation\_info:  ??????????  ~\cite{mthree, mthreepublication}
+		\item mitigated\_histogram:  the histogram with measurement's outcomes after mitigation.
+	\end{itemize}
 
@@
 \end{lstlisting}
+
 The resolved results, stored in \textit{resolved.yml}, would look just like the experiment was run synchronously.
-In other words, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment.
-After this step, we are ready to computing probabilities.
+In other words, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment (see \ref{app:example}).
+Now, we are ready to computing probabilities.
 
 \subsubsection{Computing probabilities}
-To construct a table with discrimination probabilities, you can use the following command
+Regardless of whether we use a synchronous or asynchronous approach, we can convert the resulting YML file \textit{results.yml} to a CSV file by creating a result table in which we place the results of discrimination probabilities.
+To construct a table with probabilities, you can use the following command
 \begin{lstlisting}[language=Python]
-qbench disc-fourier tabulate resolved.yml results.csv 
-\end{lstlisting}
-The results are saved as file csv as a table.
+qbench disc-fourier tabulate results.yml results.csv 
+\end{lstlisting}
 A single row for each tuple of \textit{(target, ancilla, phi)}.
@@
 The \textit{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
+A sample csv file is provided below:
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1]{results/async_result}
+	\caption{Tabulate results}
+	\label{fig:tabulateresults}
+\end{figure}
 
@@
 
+\section{Example of files} \label{app:example}
+
 \end{document}

### 2023-02-14 txt/manuscript.tex
write appendix about discrtimination hadamard

@@
 \bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
+\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
+(2021).
+On the optimal certification of von Neumann measurements.
+Scientific Reports, 11(1), 3623.
+\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
 \end{thebibliography}
@@
 \section{Discrimination task for Hadamard gate}\label{app:hadamard}
-\todo[inline]{!!!!!!}
+For the discrimination task between von Neumann measurements $\PP_{U}$ and $\PP_\Id$, where $U = H$ (the Hadamard gate) the key is to determine the discriminator $\psi_0$ and calculate the diamond norm $\| \mathcal{P}_H - \PP_\Id \|_\diamond$.
+Using semidefinite programming \cite{lewandowska2021certification, watrous2021simplier}, we obtain 
+\begin{equation}
+\| \mathcal{P}_H - \PP_\Id \|_\diamond = \sqrt{2}. 
+\end{equation}
+Observe that matrix $E_0$ minimizing Eq.~\eqref{}
+is of the form
+\begin{equation}
+E_0 = \frac{1}{2} \left( \begin{matrix} 
+1 + i & 0  \\  0 & -1-i 
+\end{matrix} \right), 
+\end{equation}
+which means 
+\begin{equation}
+\| \PP_{H} - \PP_{\Id} \|_\diamond = \| \Phi_{HE_0} - \Phi_{\Id}\|_\diamond,
+\end{equation}
+where $\Phi_{U}$ is a unitary channel. 
+Next, in order to construct the discriminator $\ket{\psi_0}$ we use Lemma 5 and the proof of Theorem 1 in ~\cite{puchala2018strategies}. We show that there exist states 
+ $\rho_1 $  and $\rho_2$ of the form $ \rho_1  = \frac{1}{2} \left( \begin{matrix} 
+ 1  & i  \\  -i & 1
+ \end{matrix} \right)  $  and $\rho_2 = \frac{1}{2} \left( \begin{matrix} 
+ 1 & -i \\  i & 1 
+ \end{matrix} \right), $ respectively. Thus, form 
+ the proof of Theorem 1 in ~\cite{puchala2018strategies} we have 
+ \begin{equation}
+ \rho_0 = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2 = \frac{1}{2} \left( \begin{matrix} 
+ 1  &  0  \\  0  & 1
+ \end{matrix} \right).
+ \end{equation}
+ It direcly implies that 
+ \begin{equation}
+ \ket{\psi_0} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}).  \end{equation}
+ Next, from Holevo-Helstrom theorem~\cite{watrous}, we determine a final optimal measurement $\PP_{V_i}$. 
+ Let us consider \begin{equation}
+ X = \left(\PP_{H} \otimes \Id \right)(\proj{\psi_0}) - \left(\PP_{\Id} \otimes \Id \right) (\proj{\psi_0})
+  \end{equation}
+ From the Hahn-Jordan decomposition, let us note
+ \begin{equation}
+ X = P - Q
+ \end{equation}
+ where $P, Q \ge 0 $.
+ Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
+ respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
+ \begin{equation}
+ \Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
+ \end{equation}
+ and
+ \begin{equation}
+ \Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
+ \end{equation}
+ Hence, we define $V_0$ as
+ \begin{equation}
+ \begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
+ \end{equation}
+ and $V_1$ as
+ \begin{equation}
+ \begin{cases}
+ V_1 \ket{y_p} = \ket{0} \\
+ V_1 \ket{y_q} = \ket{1}
+ \end{cases}.
+ \end{equation}
+ For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as
+ follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
+ \begin{equation}
+ V_0 =
+ \left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
+ \end{equation}
+ and \begin{equation}
+ V_1 =
+ \left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
+ \end{equation}
+ where \begin{equation}
+ \alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} \cos\left( \frac{3}{8} \pi \right),
+ \end{equation}
+ \begin{equation}
+ \beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} \sin\left( \frac{3}{8} \pi \right).
+ \end{equation}
 
@@
 	\end{equation}
-	From Holevo-Helstrom theorem~\cite{watrous}, we constrain a conditional measurement $\mu$.
-	Let us define
-	\begin{equation}
-	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id
-	\otimes \Id_2 \right)(\proj{\psi_0}).
-	\end{equation}
-	From the Hahn-Jordan decomposition, let us note
-	\begin{equation}
-	X = P - Q
-	\end{equation}
-	where $P, Q \ge 0 $.
-	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
-	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
-	\begin{equation}
-	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
-	\end{equation}
-	and
-	\begin{equation}
-	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
-	\end{equation}
-	Hence, we define $V_0$ as
-	\begin{equation}
-	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
-	\end{equation}
-	and $V_1$ as
-	\begin{equation}
-	\begin{cases}
-	V_1 \ket{y_p} = \ket{0} \\
-	V_1 \ket{y_q} = \ket{1}
-	\end{cases}.
-	\end{equation}
-	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H
-	\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as
+	Repeating the scheme used to distinguish the von Neumann measurements in the Hadamard basis (see \ref{app:hadamard}), we use the Hahn Jordan decomposition and then we create the projective operators into the positive and negative part of $X$ matrix.
+%	From Holevo-Helstrom theorem~\cite{watrous}, we constrain a final optimal measurement $\PP_{V_i}$.
+%	Let us define
+%	\begin{equation}
+%	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id
+%	\otimes \Id_2 \right)(\proj{\psi_0}).
+%	\end{equation}
+%	
+%	
+%	
+%	From the Hahn-Jordan decomposition, let us note
+%	\begin{equation}
+%	X = P - Q
+%	\end{equation}
+%	where $P, Q \ge 0 $.
+%	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
+%	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
+%	\begin{equation}
+%	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
+%	\end{equation}
+%	and
+%	\begin{equation}
+%	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
+%	\end{equation}
+%	Hence, we define $V_0$ as
+%	\begin{equation}
+%	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
+%	\end{equation}
+%	and $V_1$ as
+%	\begin{equation}
+%	\begin{cases}
+%	V_1 \ket{y_p} = \ket{0} \\
+%	V_1 \ket{y_q} = \ket{1}
+%	\end{cases}.
+%	\end{equation}
+%	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H
+%	\diag(1, e^{i \phi })H$, 
+	Hence, the explicit form of $V_0$ and $V_1$ is given as
 	follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
-	the unitary $V_0$ has the form
 	\begin{equation}
@@
 	\end{equation}
-	whereas the unitary  $V_1$  has the form
+and
 	\begin{equation}
@@
 	\end{equation}
-	for all $\phi \in [0,2\pi)$.
+	where $\phi \in [0,2\pi)$.
 \end{proof}

### 2023-02-17 txt/manuscript.tex
?
reading again and add some cite - tommorrow add more cite and check appendix last time

@@
 \author{Paulina Lewandowska}
-\author{Profesor Kierownik \L ukasz Pawela}
+\author{\L ukasz Pawela}
 
@@
 
+\todo[inline]{lewandowska add cite !!!}
+
 Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market,
@@
 different paradigms. Notably, one could mention D-Wave and their quantum
-annealers, or QuEra devices based on neural atoms. \todo[inline]{Expand this list and provide short
-description of those architectures}. Most vendors provide their own software stack and
+annealers, or QuEra devices based on neural atoms.  Most vendors provide their own software stack and
 application programming interface for accessing their devices. To name a few, Rigetti's computers
@@
 
-It is well known that NISQ devices have their limitations. The question is to what extent those
+It is well known that NISQ devices have their limitations \cite{}. The question is to what extent those
 devices can perform meaningful computations? To answer this question, one has to devise a
 methodology for benchmarking them. For gate--based computers, on which this paper focuses, there
-already exist several approaches. \todo[inline]{List the methods}
-
-\begin{itemize}
-	\item several examples of benchmarks -- all our metrics are readily available for devices with two qubits only and circuit depths $< 10$  for all benchmarks it should be possible to execute
-	tweaked variants on larger devices when they become available \cite{cornelissen2021scalable}
-	\item random benchmarking \cite{liu2022sampling, knill2007randomized, wallman2014randomized} and general overwiev see here \cite{helsen2022general}
-	\item MQT Bench: Benchmarking Software and
-	Design Automation Tools for Quantum Computing \cite{mqt2022} -- przejebane 
-	\item QUARK framework for quantum compjuting application benchmarking for QUBO using D-QAwe ? \cite{quark2022} --  (e. g., a novel QUBO formulation
-	of the partial MAX-SAT problem) and benchmark these on
-	different infrastructures (e. g., D-Wave and simulation). 
-	\item SupermarQ: A Scalable Quantum Benchmark Suite -- Recent works within the quantum computer architecture
-	community have taken the first steps towards quantum
-	benchmarking. The PPL+2020 [16] suite was evaluated on
-	seven superconducting QPUs, focused on characterizing the
-	error rates of different operations, and demonstrated the
-	time dependence of their performance. The TriQ [17] suite
-	was used to perform a cross-platform comparison between
-	superconducting and trapped-ion systems and revealed the
-	importance of software visibility into the hardware’s native
-	gates. However, the scalability of these suites is limited by
-	their reliance on circuit simulation to estimate how well the
-	QPUs are performing. SupermarQ extends these works by
-	introducing a systematic and principled approach to building
-	a scalable quantum benchmark suite \cite{supermarq2022}
-
-\end{itemize}
-\todo[inline]{What benchmarking techniques are readily available?}
+already exist several approaches. 
+One could mention randomized benchmarking  \cite{knill2008randomized} , benchmarks based on the quantum volume\cite{cross2019validating, moll2018quantum} or or cross-entropy benchmarking ~\cite{arute2019quantum, neill2018blueprint}.
 
@@
 library, and thus can be used with providers such as IBM Q or Amazon Braket. Along with the library,
-the PyQBench package contains a command line tool for running benchmarks in most common scenarios.
-
-\begin{itemize}
-	\item NISQs are becoming widespread and easily available for the general audience
-	\item As with any computational technology, there's a need for benchmarking NISQs to assess
-	their potential usability.
-	\item Our work aims to provide a new benchmarking scheme for gate-based devices.
-	\item Why is PyQBench important?
-	\begin{itemize}
-		\item There exist multiple benchmarking methods already on the market
-		\item Most of them have the following drawbacks:
-		\begin{itemize}
-			\item Their interpretation is not very intuitive (We cannot phrase it like this without
-			explaining why it is so)
-			\item Hard to use (is this true?)
-			\item No libraries are readily available in Python (needs to be checked).
-		\end{itemize}
-		\item PyQBench is easy to install, it works with any Qiskit backend, and its results are
-		easy to understand and interpret.
-	\end{itemize}
-\end{itemize}
-
-\todo[inline]{In particular, we compile circuits to standard gate sets of the vendor using compiler RECZNEGO?, and we perform experiments across different qubit subsets.}
-
-quantum volume - '' has become the de-facto standard benchmark to quantify the capability of Noisy Intermediate-Scale Quantum (NISQ) devices '' \cite{pelofske2022volume}
-
-Noisy intermediate-scale quantum
-(NISQ)~\cite{preskill} devices are currently storming the market. We
-have a selection of readily available quantum computers based on different
-architectures. Historically, the first widely introduced quantum computing
-architecture is D-Wave's quantum annealer.
-
-Additional approaches to quantum computing are currently in development. For
-instance we have Ionq's computer based on ion traps and Xanadu's optical
-lattices. As they are in prototype versions no access to general public is
-provided.
-
-Next, we have computers implementing the gate model of quantum computation.
-These are the best potentially developed machines, which can be thought
-of as fully quantum computers, by which we understand that the qubits can be in
-an entangled state.
-
-Currently one of the main providers of such architectures is Rigetti and its
-Quantum Cloud Services platform. The company has
-released three generations of QPUs so far: Rigetti 8Q Agave, Rigetti 19Q Acorn
-and Rigetti 16Q Aspen-1. The most recent one was deployed in November 2018 and
-is a downgrade in terms of number of qubits compared to the previous 19 qubit
-one. However, the new chip is reportedly much more robust to noise and the
-proposed architecture is much easier to scale up. The new unit is supposed to
-serve as a building block for a 128 qubit
-system~\footnote{https://medium.com/rigetti/the-rigetti-128-qubit-chip-and-what-it-means-for-quantum-df757d1b71ea}.
-As was the case for IBM, Rigetti also provides a \texttt{Python} library,
-\texttt{pyquil}~\cite{}, which enables easy access to the machine.
-
-\todo[inline]{co napisac o tym Amazonie, czy nic ?}
-
-\todo[inline]{rysunki architektur}
-
-%
-%\begin{figure}[h]
-%	\centering
-%
-%	\includegraphics[width=0.9\linewidth]{aspen.png}
-%	\caption{?}
-%	\label{fig:aspen}
-%\end{figure}
-
-Now the natural question arises: how to construct a good metric of the
-computational power of such devices?
-Lately, there have emerged propositions from the scientific community on how to
-benchmark such devices.
-
- First let us mention the work by Michielsen
-\emph{et.al.}~\cite{michielsen2017benchmarking}. In there the authors study the
-IBM-QE device. Their first test is the creation of the entangled state
-$\frac{1}{\sqrt{2}} (\ket{01} - \ket{10})$. Next they implement a
-two-qubit+two-qubit adder. Another test is an identity operation, realized by an
-even number of CNOT operations. Their final test is a quantum error correction
-scheme (is it possible with measurement-controlled-operations?). The final
-conclusion is that, except for simple circuits, the device fails to return
-correct results.
-
-Another, recent approach is utilizing quantum communication protocols in testing
-of quantum architectures~\cite{zhukov2019quantum}. Here, the authors decide to
-utilize superdense coding and the BB84 quantum cryptography protocol as
-benchmarks for the IBM Q devices. They utilize the mutual information of the
-transferred bits as a figure of merit for the quantum computer.
-
-Other approaches focus on generative model training. One of these
-works~\cite{hamilton2018generative} is aimed at small architectures, up to 5
-qubits. Another recently presented is much more
-robust~\cite{benedetti2018generative}. The main drawback of both of them is the
-level of complication.
-
-The goal of this work is to introduce a new benchmark for Rigetti
-architecture...
-
-\label{}
-\todo[inline]{
-	Introduce the scientific background and the motivation for developing the
-	software. - motywacje
-
-	Explain why the software is important, and describe the exact (scientific)
-	problem(s) it solves. - czemu ejst wazne, jakie problemy rozwiazuje
-
-	Indicate in what way the software has contributed (or how it will
-	contribute in the future) to the process of scientific discovery; if
-	available, this is to be supported by citing a research paper using the
-	software. - do czego sie to przyczyni w przyszlosci
-
-	Provide a description of the experimental setting (how does the user use
-	the software?). - w jaki sposób użytkownik korzysta z oprogramowania?
-
-	Introduce related work in literature (cite or list algorithms used, other
-	software etc.). - inne oprogramowania i algorytmy }
-
-!!!!!!!
-
-Suppose we have access to a device performing one of the predefined von Neumann
-measurements, $\PP$ or $\QQ$. In PyQBench, we restrict ourselves to discriminating von Neumann measurements.
-This is because, unlike other measurement types, they can be implemented on actual hardware. While the $\PP$ and $\QQ$ are known, it is not known which of them is
-performed when the device executes. Based on the measurement outcome, you have to guess which
-measurement was performed (but you can perform arbitrary unitary operations before and after the
-measurement). What is the highest probability of making a correct guess? And what do you have to do
-to achieve it? And, most importantly, why would we want to do this?
-
-Suppose that you know a strategy that, for an ideal device, would yield a probability
-$p_{\text{succ}}$ of successfully discriminating between two measurements. Will the probability be
-the same on an actual physical device? For current, Noisy Intermediate Scale Quantum devices
-(NISQs), the answer is: certainly not. However, the error rate that you make when guessing can be
-used as a benchmarking metric. PyQBench helps you in organizing such discrimination experiments for
-a single qubit system, executing them on real hardware or simulators, and
-computing discrimination probabilities based on the measured bitstrings.
+the PyQBench package contains a command line tool for running most common benchmarking scenarios.
+
+\section{Existing benchmarking methodologies and software}
+Unsurprisingly, PyQBench is not the only software package for benchmarking gate--based devices.
+While we believe that our approach has significant benefits over other benchmarking techniques, for
+completeness, in this section we discuss some of the currently available similar software.
+
+Probably the simplest benchmarking method one could devise is simply running known algorithms and
+comparing outputs with the expected ones. Analyzing the frequency of the correct outputs, or the
+deviation between actual and expected outputs distribution provides then a metric of the performance
+of a given device. Libraries such as Munich Quantum Toolkit (MQT) Benchmark library contain
+benchmarks leveraging multiple algorithms, such as Shor's algorithm or Grover's algorithm, 
+Despite being intuitive and easily interpretable, such benchmarks may have some problems. Most
+importantly, they assess the usefulness of a quantum device only for a very particular algorithm,
+and it might be hard to extrapolate their results to other algorithms and applications. For
+instance, the inability of a device to consistently find factorizations using Shor's algirithms
+does not tell anything about its usefulness in Variational Quantum Algorithm's.
+
+Another possible approach to benchmarking quantum computers is randomized benchmarking
+\cite{liu2022sampling, knill2007randomized, wallman2014randomized, helsen2022general,
+	cornelissen2021scalable}. In this approach, one samples circuits to be run from some predefined set
+of gates (e.g. from the Clifford group) and tests how much the output distribution obtained from the
+device running these circuits differs from the ideal one. It is also common to concatenate randomly
+chosen circuits with their inverses (which should yield the identity circuit) and run those
+concatenated circuits on the device. Libraries implementing this approach include Qiskit \cite{},
+\todo[inline]{enumerate other libraries and summary}
 
@@
 some state $\ket{\psi_0}$. Then, the unknown measurement is performed on the first part of the
-system. Based on its outcome $i$, another measurement $\mathcal{P}_{V_i}$ is performed to obtain an
-outcome $j$. Finally, if $j=0$ we guess that the performed measurement is $\mathcal{P}_U$, otherwise
-we guess that it was $\mathcal{P}_\Id$.
+system. Based on its outcome $i$, the final measurement $\mathcal{P}_{V_i}$ is performed to obtain an
+outcome $j$. Finally, if $j=0$ we guess that the performed measurement is $\mathcal{P}_U$, otherwise we guess that it was $\mathcal{P}_\Id$.
 
@@
 Current NISQ devices are unable to perform conditional measurements, which is the biggest
-obstacle to implementing our scheme on real hardware. Luckily, we can overcome it by
-cleverly adjusting our scheme so that it only uses components available on current devices.
-We have two possible choices here: using a postselection or a direct sum
+obstacle to implementing our scheme on real hardware. However, we can adjusting our scheme so that it only uses components available on current devices.
+For this purpose, we use two possible options: using a postselection or a direct sum
 $V_0^\dagger\oplus V_1^\dagger$.
@@
 
-	The first idea uses a postselection. Instead of performing a conditional measurement, for each
-	measurement $\PP_U, \PP_\Id$ to be discriminated and each choice of $k \in \{0, 1\}$ we run circuit presented in Fig. \ref{fig:postselection}.
+	The first idea uses a postselection scheme. Instead of performing a conditional measurement $\PP_{V_k}$, for each
+	measurement $\PP_U, \PP_\Id$ to be discriminated and each choice of $k \in \{0, 1\}$ we run circuits presented in Fig. \ref{fig:postselection}.
 
@@
 			A schematic representation of the setup for distinguishing
-			measurements $\PP_{U}$ and $\PP_{\Id}$ using direct sum.
+			measurements $\PP_{U}$ and $\PP_{\Id}$ using postselection approach.
 		}\label{fig:postselection}
@@
 
-%	But now our experiment does not match the previously described scheme, right?
-%	Yes, unless we discard all the outcomes for which $i\ne k$ (hence the name \emph{postselection},
-%	we are selecting valid outcomes after the experiment is performed).
-
-	% \begin{scheme}(Postselection)
-
-	% %\begin{figure}[h!]
-	% %	\includegraphics[scale=1.5]{onequbit.pdf}
-	% %	\caption{A schematic representation of the setup for distinguishing
-	% %		measurements using postselection.}
-	% %	\label{postselection}
-	% %\end{figure}
-
-	% \begin{enumerate}
-	% \item We prepare  the discriminator $\ket{\psi_{0}}$ on bipartite system.
-	% \item We perform one of two quantum channels, either $\Phi_{\Id}$ or
-	% $\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left( \Phi \otimes \Id\right)(\proj{\psi_0})$.
-	% \item We measure the first part of the input state  $\ket{\psi_{0}}$ and
-	% receive an output label $i$.
-	% \item
-	% Based on Holevo--Helstrom theorem, we perform a conditional binary
-	% measurement	$\PP_{V_j}$ and hence, we implement the quantum channel $\Phi_{V_j^\dagger}$ on the second part.
-	% \item To calculate the probability of correct discrimination, we include just those cases for which $i = j$.
-	% \item We measure the second part of the input state  $\ket{\psi_{0}}$ and make a
-	% decision based on received label $j$. If $i=j=0$, then we decide that
-	% $\PP_U$ occurs.  If $i=j=1$, we decide that
-	% $\PP_{\Id}$ occurs.
-	% \end{enumerate}
 The experiments can be grouped into classes identified by tuples of the form
@@
 
-	Finally, we count the experiments (among the valid ones) resulting in successful discrimination.
+	Finally, we count the valid experiments resulting in successful discrimination.
 	If we have chosen $\PP_U$, then we guess correctly iff $j=0$. Similarly, for
@@
 
-The second idea uses  the direct sum $V_0^\dagger \oplus V_1^\dagger.$    Here, instead of performing a conditional
-measurement $\PP_{V_k}$, where $k\in \{0,1\}$ we run circuit presented in	Fig.~\ref{fig:controlled}.
-%	\begin{enumerate}
-%		\item We prepare the discriminator $\ket{\psi_{0}}$ on bipartite
-%		system.
-%		%\item We perform one of two quantum channels, either $\Phi_{\Id}$ or
-%		%$\Phi_{U^\dagger}$,  on  the first part of the input state  $\ket{\psi_{0}}$, that means $\left(\Phi \otimes \Id\right)(\proj{\psi_0})$.
-%		\item We apply one of unitary,   either $U^\dagger$ or
-%		$\Id$, on the first system.
-%		%\item Based on Holevo--Helstrom theorem, we perform a conditional binary measurement $\PP_{V_j}$, and hence, we implement the direct sum of quantum channels $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger}$.
-Observe that   $\Phi_{V_0^\dagger} \oplus \Phi_{V_1^\dagger} = \proj{0} \otimes \Phi_{V_0^\dagger}  + \proj{1} \otimes \Phi_{V_1^\dagger}.
-$
-%		\item We apply direct sum $V_0^\dagger \oplus V_1^\dagger$ on the whole systems.
-%		\item We measure both systems in computational basis $\Delta$.
-%		\item We make a decision based on the received label $j$ on the second system. If $j=0$, then we
-%		decide that $\PP_U$ occurs. Otherwise, we decide that $\PP_{\Id}$ occurs.
-%	\end{enumerate}
-
-%	The schematic representation of this setup is depicted in
-%	Fig.~\ref{fig:controlled}.
+The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation.     Here, instead of performing a conditional
+measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits presented in	Fig.~\ref{fig:controlled}.
+
 	\begin{figure}[h!]
@@
 However,
-sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
+determining the analytical form of the discriminator $\ket{\psi_{0}}$
 is, in general, NP-hard problem.
@@
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this case, the optimal input state is Bell state of the form
+In this case, the optimal input state is the Bell state of the form
 \begin{equation}
@@
 \end{equation}
-And, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
+Observe that the discriminator does not depend on the angle $\phi$. 
+Nevertheless, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
 have the following form
@@
 \section{PyQBench as a library}\label{sec:pyqbench-as-library}
-This guide introduces basic concepts needed for using PyQBench as a library from a Python script. In particular, we will cover the following topics:
+This guide introduces basic concepts needed for using PyQBench as a library from a Python script. In particular, we will consider the following topics:
 \begin{enumerate}
@@
 \end{enumerate}
-%Currently available quantum computers typically cannot start execution from an arbitrary state.
-Instead, we have to prepare it ourselves.
-Hence, to execute experiment using postselection scheme, we need an instruction taking to the desired discriminator $\ket{\psi_0}$
-%and instructions implementing $U^\dagger$, $V_0^\dagger$ and $V_1^\dagger$.
-Whereas, execute experiment using direct sum approach, we need an instruction taking to the desired discriminator  $\ket{\psi_0}$
-%and instructions implementing $U^\dagger$, $V_0^\dagger \oplus V_1^\dagger$.
 
 \subsubsection{Example of usage}
-In our example, we will use $U =  H$ (the Hadamard gate).
-% To keep us focused on the implementation in PyQBench and not delve too deep into mathematical explanation, we simply provide explicit formulas for discriminator $\ket{\Psi_0} $, $V_0$ and $V_1$, leaving the calculations to the interested reader.
+In  this example, we will use $U =  H$ (the Hadamard gate).
 The explicit formula for discriminator in this model reads
@@
 As a next step, we need decompose our matrices into actual sequences of gates.
-The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$ is well known, and comprises Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
+The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
 \begin{figure}[h!]
@@
 \end{equation}
-To obtain $V_1$  we need only to swap the columns, which is equivalent to following $V_0$ by $X$ matrix, more precisely
+To obtain $V_1$  we need only to swap the columns, which is equivalent to 
 \begin{equation}
@@
 \end{equation}
-Finally, the optimal probability of correct discrimination between $\PP_{U}$, where $U=H$ and $\PP_{\Id}$ is given by 
+Finally, calculate the optimal probability of correct discrimination which is equal to
 \begin{equation}
@@
 The detailed calculation we can see in \ref{app:hadamard}. 
-
-Now we simulate  theoretical framework using PyQBench. We will start with simulation in Qiskit SDK with Aer simulator. First, we import necessary modules. \todo[inline]{czy to zdanie jest poprawne?}
+Now we simulate the  theoretical framework using PyQBench. We will start with simulation in Qiskit SDK with Aer simulator. First, we import necessary modules and needed functions from PyQBench.
 
 \begin{lstlisting}[language=Python]
+import numpy as np
 from qiskit import QuantumCircuit, Aer
-import numpy as np
-\end{lstlisting}
-Next we import needed functions from PyQBench. For our example we will need two functions. 
-\begin{lstlisting}[language=Python]
 from qbench.schemes.postselection import benchmark_using_postselection
@@
 \end{lstlisting}
-To run any of these functions, we need to define components that we discussed below.
-Most importantly, we need to create Qiskit instructions, not circuits.
-We can conveniently do so by constructing circuit acting on qubits 0 and 1 and then converting them using \textit{to\_instruction()} method.
+To run a function from PyQBench, we need to define Qiskit instructions.  We can do so by constructing circuit acting on qubits 0 and 1 and then converting them using \textit{to\_instruction()} method.
 \begin{lstlisting}[language=Python, caption= Defining components for Hadamard experiment]
@@
 \end{lstlisting}
-For the purpose of this example,  we define Qiskit Aer simulator.
+For the purpose of this example,  we run experiments on Qiskit Aer simulator.
 \begin{lstlisting}[language=Python, caption= Defining a backend]
@@
 Finally, we calculate the empirical probability obtained from postselection and direct sum experiment and calculate the absolute error between analytical and empirical results. 
-\begin{lstlisting}[language=Python, caption=Computation of probability]
+\begin{lstlisting}[language=Python, caption=Computation of discrimination probability]
 p_succ = (2 + np.sqrt(2)) / 4
@@
 But what if we want more control over some parts of this process?
-One possibility would be to add more and more parameters to \textit{benchmark\_using\_xyz} functions, but this approach clearly is not very scalable.
-Also, there is no way we can anticipate all the possible use cases.
+One possibility would be to add some additional parameters to \textit{benchmark\_using\_xyz} functions, but this approach is not scalable.
+Moreover, there is no way we can anticipate all the possible use cases.
  We decided on another approach.  PyQBench provides functions performing:
@@
 By choosing this approach we need to divide the experiment into two parts:
-\begin{enumerate}
-	\item Assembling  circuits
-	\item Running  circuits
-\end{enumerate}
+assembling  circuits and running  circuits.
+
 Let us focus only on the postselection case, as the direct sum case is analogous. In addition, we need to import two more functions from PyQBench.
-\begin{lstlisting}[language=Python, caption=Assembling circuits]
+\begin{lstlisting}[language=Python, caption= Assembling circuits]
 from qbench.schemes.postselection import (
@@
 )
-\end{lstlisting}
-The function \textit{assemble\_postselection\_circuits} creates all of neceserry circuits, nicely packed in a dictionary.
-Each informs if the circuit implements identity or alternative measurement on the target qubit, and which of $V_0$ and
-$V_1$ is used.
-\begin{lstlisting}[language=Python]
+
 circuits = assemble_postselection_circuits(
@@
 \end{lstlisting}
-%
-%\begin{lstlisting}[language=Python, caption=Python example]
-%{'id_v0': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b1585b9a0>,
-%'id_v1': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b37fbfa90>,
-%'u_v0': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b1585bf40>,
-%'u_v1': <qiskit.circuit.quantumcircuit.QuantumCircuit at 0x7f8b1585bf10>}
-%\end{lstlisting}
-Now we only need to run the circuits.
-To make this example more interesting, we will run a noisy and noiseless simulation of our circuits.
-We will use the same backend as before, and our noise model will only comprise readout errors on both qubits.
-\begin{lstlisting}[language=Python, caption=Noise models]
+The function \textit{assemble\_postselection\_circuits} creates all of neceserry circuits as a dictionary.
+Each informs if the circuit implements $U^\dagger$ or $\Id$ on the target qubit, and which of $V_0$ and
+$V_1$ is used.
+
+Now we need to run the circuits. We will run a noisy and noiseless simulation of our circuits.
+
+\begin{lstlisting}[language=Python, caption=Adding noise model]
 from qiskit.providers.aer import noise
@@
 \end{lstlisting}
-Finally, we compute the success probabilities. We do so by passing bitstring counts to  \textit{compute\_probabilities\_from\_postselection\_measurements} function.
-
-\begin{lstlisting}[language=Python, caption=Computation probability without noise]
+Finally, we compute the success probabilities using  \textit{compute\_probabilities\_from\_\\postselection\_measurements} function.
+
+\begin{lstlisting}[language=Python, caption=Computation probabilities]
 prob_succ_noiseless = compute_probabilities_from_postselection_measurements(
@@
 
-print(prob_succ_noiseless)
-\end{lstlisting}
-
-\begin{lstlisting}[language=Python, caption=Computation probability including noise]
 prob_succ_noisy = compute_probabilities_from_postselection_measurements(
@@
 
-print(prob_succ_noisy)
-\end{lstlisting}
-The success probability is 0.8524401115559386, whereas if we obtain some noise, the success probability is equal to 0.5017958400693446
+\end{lstlisting}
+The success probability is 0.8524401115559386. Whereas if we obtain a readout error, the success probability is equal to 0.5017958400693446. 
 As expected, noisy simulations gave us results that are further away from the exact ones.
@@
 \section{PyQBench as a CLI tool}\label{sec:pyqbench-as-cli}
-Using PyQBench as a library allows one to conduct, in principle, arbitrary two-qubit von Neumann measurement experiment.
-However, as discussed in the previous guide, it requires some amount of boilerplate code.
+Using PyQBench as a library allows one to conduct arbitrary two-qubit von Neumann measurement experiment. However, as discussed in the previous guide, it requires some amount of boilerplate code.
 For a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
-The workflow is best describe as a list of steps:
+The workflow is describe as a list of steps:
 
@@
 which we want to benchmark. Experiments and backends are defined in YAML files. An example experiment definition looks as follows.
-
 \begin{lstlisting}[language=Python, caption=Defining the experiment]
@@
 \begin{itemize}
-	\item The \textit{type} describes type of the experiment.
-Currently, the only option for \textit{type} is \textit{discrimination-fourier}.
-In the future, other benchmarks may be added, in which keys the \textit{types} key should contain their name.
+	\item The \textit{type} describes type of the experiment. Currently, the only option of  \textit{type} is \textit{discrimination-fourier}. 
 	\begin{lstlisting}[language=Python]
@@
 	\item The \textit{qubits} list describes pair of qubits on which the experiment should be run.
-In our example, the benchmark will run on two pairs of qubits.
+In this example, the benchmark will run on two pairs of qubits.
 First pair is 0 and 1, second pair is 1 and 2.
-	Notice that we distinguish between ancilla and target qubit, so e.g
-
+%	Notice that we distinguish between ancilla and target qubit, so e.g
+%	\begin{lstlisting}[language=Python]
+%qubits:
+%	- target: 0
+%      ancilla: 1
+%	\end{lstlisting}
+%	is not the same as 
+%	\begin{lstlisting}[language=Python]
+%qubits:
+%	- target: 1
+%      ancilla: 0
+%	\end{lstlisting}
 \begin{lstlisting}[language=Python]
@@
 	  ancilla: 1
-	\end{lstlisting}
-	is not the same as 
-	\begin{lstlisting}[language=Python]
-qubits:
 	- target: 1
-      ancilla: 0
+	  ancilla: 2
 	\end{lstlisting}
@@
 \subsubsection{Notes on using the asynchronous flag}
-In our example, the only key that requires the explanation is \textit{asynchronous} which determines whether experiments will be run asynchronously  (\textit{true}) or not (\textit{false}).
- We recommend setting it to true, unless your experiment is really small (several circuits total).
+In this example, the only key that requires the explanation is \textit{asynchronous} which determines whether experiments will be run asynchronously  (\textit{true}) or not (\textit{false}).
+% We recommend setting it to true, unless your experiment is really small (several circuits total).
 However, some backends may not support asynchronous execution.
@@
 
-For synchronous experiment, the output looks similar to the one below: 
+For synchronous experiment, the part of output looks similar to the one below. The whole YAML file can be seen in \ref{app:example}.
+%Consider the particular experiment data
+\begin{lstlisting}[language=Python]
+data:
+- target: 0
+  ancilla: 1
+  phi: 0.0
+  results_per_circuit:
+  - name: id
+  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
+  mitigation_info:
+	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
+	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
+  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
+\end{lstlisting}
+	The data includes \textit{target, ancilla, phi},
+	and \textit{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \textit{results\_per\_circuit} gives us 
+	the following additional informations: 
+	\begin{itemize}
+		\item  name: id:  the information which measurement is used during experiment,   $\PP_{U}$ or $\PP_{\Id}$. In this example we consider  $\PP_{\Id}$. 
+		\item histogram: {'00': 28, '01': 26, '10': 21, '11': 25}: the dictionary with measurement's outcomes.
+The keys represent possible measurement oucomes, whereas the values present number of occurrences.
+		\item mitigation\_info:  \textit{system.properties().qubits} contains information on the physical attributes of the qubits.
+This includes e.g.
+information about readout error.
+As shown below, the \textit{readout\_error} is further partitioned into \textit{prob\_meas0\_prep1} and \textit{prob\_meas1\_prep0}, indicating the probability of preparing a given computational basis state, but measuring the orthogonal state.
+The readout error is taken to be the average of these two values.
+Note that \textit{prob\_meas0\_prep1} is usually the dominant factor in the readout error due to relaxation during the measurement process.
+~\cite{mthree, mthreepublication}
+		\item mitigated\_histogram:  the histogram with measurement's outcomes after mitigation.
+	\end{itemize}
+
+\subsubsection{(Optional) Getting status of asynchronous jobs}
+ PyQBench provides also a helper command that will fetch the statuses of asynchronous jobs. The command is:
+\begin{lstlisting}[language=Python]
+qbench disc-fourier status async_results.yml
+\end{lstlisting}
+and it will display dictionary with histogram of statuses.
+
+\subsubsection{Resolving asynchronous jobs}
+If the status of jobs is \textit{DONE}, we have to obtain measurements from the submitted jobs. This is done using the following command:
+\begin{lstlisting}[language=Python]
+qbench disc-fourier resolve async-results.yml resolved.yml
+\end{lstlisting}
+The resolved results, stored in \textit{resolved.yml}, would look just like the experiment was run synchronously.
+More precisely, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment (see \ref{app:example}).
+Next, we can compute the discrimination probabilities.
+
+\subsubsection{Computing probabilities}
+Regardless of whether we use a synchronous or asynchronous approach, we can convert the resulting YML file \textit{results.yml} to a CSV file by creating a result table in which we place the results of discrimination probabilities.
+To construct a table with probabilities, you can use the following command
+\begin{lstlisting}[language=Python]
+qbench disc-fourier tabulate results.yml results.csv 
+\end{lstlisting}
+A single row for each tuple of \textit{(target, ancilla, phi)}.
+The \textit{disc\_prob} column will contain the discrimination probability for given configuration.
+The \textit{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
+A sample csv file is provided below:
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1]{results/async_result}
+	\caption{Tabulate results}
+	\label{fig:tabulateresults}
+\end{figure}
+
+\section{Impact}
+\todo[inline]{OJCIEC WYKAZ SIE, bo trzeba to dobrze sprzedac, nizej tekst z formatki softwarex co powinna zawierac ta sekcja}
+This software has two main contributions.
+
+\textbf{This is the main section of the article and the reviewers weight the
+description here appropriately}
+
+Indicate in what way new research questions can be pursued as a result of the
+software (if any).
+
+Indicate in what way, and to what extent, the pursuit of existing research
+questions is improved (if so).
+
+Indicate in what way the software has changed the daily practice of its users
+(if so).
+
+Indicate how widespread the use of the software is within and outside the
+intended user group.
+
+Indicate in what way the software is used in commercial settings and/or how it
+led to the creation of spin-off companies (if so).
+
+\section{Conclusions}
+\label{}
+
+In this study, we develop  a Python library PyQBench, an innovative open-source framework for benchmarking
+gate-based quantum computers.
+
+%%%%%%%%%%%%%%
+PyQBench can benchmark NISQ devices by verifying their capability of
+discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
+command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
+family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
+measurements instead of predefined ones.
+\section{Conflict of Interest}
+No conflict of interest exists: We wish to confirm that there are no known
+conflicts of interest associated with this publication and there has been no
+significant financial support for this work that could have influenced its out-
+come.
+
+\section*{Acknowledgements}
+
+This work is  supported by
+the project “Near-term quantum computers Challenges, optimal implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the Team-Net programme of the Foundation for Polish Science co-financed by the European Union under the European Regional Development Fund.
+PL is also a holder of European Union scholarship through the European Social Fund,
+grant InterPOWER (POWR.03.05.00-00-Z305).
+
+\begin{thebibliography}{00}
+	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
+S., Smith, K.
+N., Viszlai, J., ...
+Chong, F.
+T.
+(2022, April).
+Supermarq: A scalable quantum benchmark suite.
+In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp.
+587-603).
+IEEE.
+	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
+	\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
+B., Jost, J.
+D., ...
+Wineland, D.
+J.
+(2008).
+Randomized benchmarking of quantum gates.
+Physical Review A, 77(1), 012307.
+	\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
+	\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
+ \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
+(2021).
+Benchmarking near-term quantum computers via random circuit sampling.
+arXiv preprint arXiv:2105.05232.
+\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
+\bibitem{quark2022} Finžgar, J.
+R., Ross, P., Hölscher, L., Klepsch, J.,  Luckow, A.
+(2022, September).
+QUARK: A framework for quantum computing application benchmarking.
+In 2022 IEEE International Conference on Quantum Computing and Engineering (QCE) (pp.
+226-237).
+IEEE.
+\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and
+beyond." Quantum 2 (2018): 79.
+\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking
+gate-based quantum computers." Computer Physics Communications 220 (2017):
+44-55.
+\bibitem{cross2019validating}
+Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
+\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication
+protocols as a benchmark for programmable quantum computers." Quantum
+Information Processing 18.1 (2019): 1-23.
+\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
+and Raphael C. Pooser. "Generative model benchmarks for superconducting
+qubits." Physical Review A 99.6 (2019): 062323.
+\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative
+modeling approach for benchmarking and training shallow quantum circuits." npj
+Quantum Information 5.1 (2019): 1-9.
+\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for
+optimal single-shot discrimination of quantum measurements." Physical Review A
+98.4 (2018): 042103.
+\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
+\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
+\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
+\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
+\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
+
+\bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
+\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
+\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
+\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
+(2021).
+On the optimal certification of von Neumann measurements.
+Scientific Reports, 11(1), 3623.
+\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
+\bibitem{arute2019quantum}Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
+C., Barends, R., ...
+Martinis, J.
+M.
+(2019).
+Quantum supremacy using a programmable superconducting processor.
+Nature, 574(7779), 505-510.
+\bibitem{knill2008randomized}
+Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., ...  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.
+\bibitem{moll2018quantum}
+Moll, N., Barkoutsos, P., Bishop, L.
+S., Chow, J.
+M., Cross, A., Egger, D.
+J., ...
+Temme, K.
+(2018).
+Quantum optimization using variational algorithms on near-term quantum devices.
+Quantum Science and Technology, 3(3), 030503.
+
+\bibitem{neill2018blueprint}
+Neill, C., Roushan, P., Kechedzhi, K., Boixo, S., Isakov, S.
+V., Smelyanskiy, V., ...
+Martinis, J.
+M.
+(2018).
+A blueprint for demonstrating quantum supremacy with superconducting qubits.
+Science, 360(6385), 195-199.
+
+\end{thebibliography}
+
+\todo[inline]{Please add the reference to the software repository if DOI for
+software  is available. }
+
+\section*{Current executable software version}
+\label{}
+
+Ancillary data table required for sub version of the executable software: (x.1,
+x.2 etc.) kindly replace examples in right column with the correct information
+about your executables, and leave the left column as it is.
+
+\begin{table}[!h]
+\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
+\hline
+\textbf{Nr.} & \textbf{(Executable) software metadata description} &
+\textbf{Please fill in this column} \\
+\hline
+S1 & Current software version & For example 1.1, 2.4 etc. \\
+\hline
+S2 & Permanent link to executables of this version  & For example:
+$https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
+\hline
+S3 & Legal Software License & List one of the approved licenses \\
+\hline
+S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS,
+Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based
+etc. \\
+\hline
+S5 & Installation requirements \& dependencies & \\
+\hline
+S6 & If available, link to user manual - if formally published include a
+reference to the publication in the reference list & For example:
+$http://mozart.github.io/documentation/$ \\
+\hline
+S7 & Support email for questions & \\
+\hline
+\end{tabular}
+\caption{Software metadata (optional)}
+\label{}
+\end{table}
+
+\appendix
+\section{Mathematical preliminaries} \label{app:preliminaries}
+
+Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
+the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
+$M_d$.
+%The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
+%will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
+%matrices of dimension $d$ by $\HH_d^+$.
+By $\Omega_d$, we will denote the set of quantum states, that is
+positive semidefinite operators having trace equal to one.
+The subset of $M_d$ consisting of unitary matrices will be denoted
+by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
+$\DD \UU_d$.
+%An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$, whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
+
+We will also need a linear mapping transforming $M_{d_1}$ into
+$M_{d_2}$, which will be denoted
+\begin{equation}
+\Phi: M_{d_1 } \rightarrow M_{d_2}.
+\end{equation}
+There
+exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $M_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism.
+For a given linear mapping $\Phi$ the corresponding Choi operator $J(\Phi)$ is explicitly written as
+\begin{equation}
+J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
+
+We introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
+and trace preserving (CPTP).
+In this work we will consider a special class of quantum channels, called unitary channels.  A
+channel
+$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for any $U \in
+\UU_d$.
+
+The action of
+von Neumann measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
+seen as  a measure-and-prepare quantum channel as follows \begin{equation}
+\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
+\end{equation}
+Moreover, observe that each von Neumann measuement $\PP_{U}$ poses a  composition of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
+
+We need to also briefly discuss about the distance between unitary channels and von Neumann measurements. From \cite[Theorem 1]{puchala2018strategies}, the distance between measurements $\PP_U$ and
+$\PP_\Id$ ie equal to
+\begin{equation}
+\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} -
+\Phi_\Id\|_\diamond,
+\end{equation} whereas to express the distance between unitary channels, we need to introduce the notion of numerical range. The set \begin{equation}
+W(A) =\{\bra{x}A\ket{x}: \ket{x} \in
+\mathbb{C}^d, \;
+\;\braket{x}{x}=1\}.
+\end{equation}
+is called numerical range of  a matrix $A \in M_d$.
+The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.
+Due to the definition of $W(A)$, the distance between two unitary channels $\Phi_{U} $ and $\Phi_\Id$
+can be written as
+\begin{equation}
+\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
+\end{equation}
+where $\nu = \min_{x \in W(U^\dagger)} |x|  $.
+
+\section{Discrimination task for Hadamard gate}\label{app:hadamard}
+For the discrimination task between von Neumann measurements $\PP_{U}$ and $\PP_\Id$, where $U = H$ (the Hadamard gate) the key is to calculate the diamond norm $\| \mathcal{P}_H - \PP_\Id \|_\diamond$ and
+determine the discriminator $\ket{\psi_0}$.
+Using semidefinite programming \cite{watrous2021simplier}, we obtain 
+\begin{equation}
+\| \mathcal{P}_H - \PP_\Id \|_\diamond = \sqrt{2}. 
+\end{equation}
+From \cite{lewandowska2021certification} we have 
+\begin{equation}
+\| \PP_{H} - \PP_{\Id} \|_\diamond = \| \Phi_{HE_0} - \Phi_{\Id}\|_\diamond,
+\end{equation}
+where $\Phi_{U}$ is a unitary channel and 
+ $E_0$ 
+is of the form
+\begin{equation}
+E_0 = \frac{1}{2} \left( \begin{matrix} 
+1 + i & 0  \\  0 & -1-i 
+\end{matrix} \right). 
+\end{equation}
+Next, in order to construct the discriminator $\ket{\psi_0}$ we use Lemma 5 and the proof of Theorem 1 in \cite{puchala2018strategies}. We show that there exist states 
+ $\rho_1 $  and $\rho_2$ of the form $ \rho_1  = \frac{1}{2} \left( \begin{matrix} 
+ 1  & i  \\  -i & 1
+ \end{matrix} \right)  $  and $\rho_2 = \frac{1}{2} \left( \begin{matrix} 
+ 1 & -i \\  i & 1 
+ \end{matrix} \right), $ respectively. Thus, we construct the quantum state $\rho_0$ as follows:
+ \begin{equation}
+ \rho_0 = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2 = \frac{1}{2} \left( \begin{matrix} 
+ 1  &  0  \\  0  & 1
+ \end{matrix} \right).
+ \end{equation}
+ According to the Lemma 5 and the proof of Theorem 1 in \cite{puchala2018strategies} we assume that \begin{equation}
+ \ket{\psi_0} = | \rho_0 \rangle \rangle. 
+ \end{equation}
+ It direcly implies that 
+ \begin{equation}
+ \ket{\psi_0} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}).  \end{equation}
+ Next, from Holevo-Helstrom theorem~\cite{watrous}, we determine the final measurement $\PP_{V_i}$. 
+ Let us consider \begin{equation}
+ X = \left(\PP_{H} \otimes \Id \right)(\proj{\psi_0}) - \left(\PP_{\Id} \otimes \Id \right) (\proj{\psi_0})
+  \end{equation}
+ From the Hahn-Jordan decomposition, let us note
+ \begin{equation}
+ X = P - Q
+ \end{equation}
+ where $P, Q \ge 0 $.
+ Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
+ respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
+ \begin{equation}
+ \Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
+ \end{equation}
+ and
+ \begin{equation}
+ \Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
+ \end{equation}
+ Hence, we define $V_0$ as
+ \begin{equation}
+ \begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
+ \end{equation}
+ and $V_1$ as
+ \begin{equation}
+ \begin{cases}
+ V_1 \ket{y_p} = \ket{0} \\
+ V_1 \ket{y_q} = \ket{1}
+ \end{cases}.
+ \end{equation}
+ For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as
+ follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
+ \begin{equation}
+ V_0 =
+ \left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
+ \end{equation}
+ and \begin{equation}
+ V_1 =
+ \left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
+ \end{equation}
+ where \begin{equation}
+ \alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} \cos\left( \frac{3}{8} \pi \right),
+ \end{equation}
+ \begin{equation}
+ \beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} \sin\left( \frac{3}{8} \pi \right).
+ \end{equation}
+
+\section{Optimal probability for parametrized Fourier family} \label{app:optimal-probability}
+
+Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
+Assume that the unitary matrix $U$ is of the form
+\begin{equation}
+U = H
+\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
+\end{equation}
+%\begin{equation}
+%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
+%\end{equation}
+where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
+In this section we present theoretical probability of correct
+discrimination between these measurements. To do that, we will present an auxiliary lemma.
+\begin{lemma}\label{lemma:min-e-optimal}
+	Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let
+	$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds
+	\begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} -
+	\Phi_\Id\|_\diamond = \|\Phi_{U} -
+	\Phi_\Id\|_\diamond,
+	\end{equation}
+\end{lemma}
+
+\begin{proof} Recall that the distance between two unitary channels is given by
+	$
+	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
+	$
+	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$.
+	For $U = H
+	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So,
+	\begin{equation}
+	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |.
+	\end{equation}
+	It implies that it is enough to prove  \begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} -
+	\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
+	\end{equation}
+	%		It implies that we can prove  equivalently  the following condition
+	%		\begin{equation}
+	%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
+	%		\end{equation}
+	This condition is equivalent to show
+	\begin{equation}
+	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
+	\end{equation}
+	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
+
+	%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
+	The celebrated Hausdorf-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
+	$W(A)$ of any matrix $A \in M_d$ is a convex set, and therefore we have
+	\begin{equation}
+	W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}.
+	\end{equation}
+	So, we can assume that
+	\begin{equation}
+	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| =
+	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|.
+	\end{equation}
+	Then, we have
+	\begin{equation}
+	\max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in
+		\Omega_2} \left| \tr \left( \rho U E \right) \right|.
+	\end{equation}
+	For that, our task is reduced to show that
+	\begin{equation}
+	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \max_{E \in \diaguni_2 } \nu_{E}.
+	\end{equation}
+
+	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $
+	and take $\rho =
+	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $.
+	From spectral theorem, let us decompose $U$ as
+	\begin{equation}
+	U= \lambda_0 \ketbra{x_0}{x_0} + \lambda_1 \ketbra{x_1}{x_1},
+	\end{equation}
+	where  for eigenvalue $\lambda_0 = 1$, the corresponding
+	eigenvector is
+	of the form $\ket{x_0} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	$,
+	whereas for  $\lambda_1= e^{i \phi}$ we have $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
+	$.
+	Then, we have
+	\begin{equation}
+	\begin{split}
+	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
+	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
+	\frac{1}{2} \left| \tr\left((   \proj{x_0} +e^{i \phi}\proj{x_1} ) E \right)
+	\right|  =
+	\frac{1}{2} \left|  \bra{x_0} E \ket{x_0} +  e^{i \phi}\bra{x_1} E \ket{x_1}
+	\right| = \\&
+	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right|
+	=
+	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le
+	\max_{E \in \diaguni_2 } \nu_{E},
+	\end{split}
+	\end{equation}
+	which completes the proof.
+\end{proof}
+
+\begin{theorem}\label{th:probability}
+	The optimal probability of correct discrimination between von Neumann
+	measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
+	where $\phi \in [0, 2\pi)$ is given by
+	\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
+	\end{equation}
+\end{theorem}
+
+\begin{proof}
+	From Holevo-Helstrom theorem, we obtain
+	\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
+	\end{equation}
+	From~\cite[Theorem 1]{puchala2018strategies}, we have
+	\begin{equation}
+	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} -
+	\Phi_\Id\|_\diamond.
+	\end{equation}
+	From Lemma~\ref{lemma:min-e-optimal},  we know that for
+	$U =  H \diag(1, e^{i \phi}) H^\dagger$,  it also holds that
+	\begin{equation}
+	\min_{E \in \diaguni_2} \|\Phi_{UE} -
+	\Phi_\Id\|_\diamond = \|\Phi_{U} -
+	\Phi_\Id\|_\diamond,
+	\end{equation} which is exactly equal to
+	\begin{equation}
+	\|\Phi_{U} -
+	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|.
+	\end{equation}
+	%	Finally, we obtain that
+	%	\begin{equation}
+	%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
+	%	\end{equation}
+	It implies that
+	\begin{equation}
+	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
+	\end{equation} which completes the proof.
+\end{proof}
+
+\section{Optimal discrimination strategy for parametrized Fourier family} \label{app:optimal-strategy}
+
+In this Appendix we create the optimal
+theoretical strategy of  discrimination between $\PP_{U}$ and $\PP_{\Id}$.
+To indicate the optimal strategy, we will present two propositions.
+The first one is concentrated around the discriminator as the optimal input state of discrimination strategy, whereas the second one describes the optimal final measurement.
+
+\begin{proposition}\label{prop-discrim}
+	Consider the problem of discrimination between von Neumann measurements $\PP_U$
+	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0,
+	2\pi)$.  The  discriminator has the form
+	\begin{equation}
+	\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
+	\end{equation}
+\end{proposition}
+
+\begin{proof}
+	Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0,
+	2\pi)$ be decomposed as
+	\begin{equation}
+	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2},
+	\end{equation}
+	where  for eigenvalue $\lambda_1 = 1$, the corresponding
+	eigenvector is
+	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	$,
+	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
+	$.
+	For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
+	\begin{equation}
+	\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) J(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
+	Hence, we obtain
+	\begin{equation}
+	\begin{split}
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond
+	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right)
+	J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1
+	\\
+	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right)
+	\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top
+	\right\|_1  \\
+	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes
+	\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
+	\\
+	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left(
+	\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
+	\end{split}
+	\end{equation}
+	One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x},
+	\ket{y}$ the following equation holds~\cite{watrous}
+	\begin{equation}
+	\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha
+		\beta |\braket{x}{y}|^2}.
+	\end{equation}
+	By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho}
+		\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho}
+		\ket{i} \|}$ we have
+	\begin{equation}
+	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2}
+	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i
+		}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
+	\end{equation}
+	Let us take  $\rho_0 =   \frac{1}{2}
+	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
+	\begin{equation}
+	\begin{split}
+	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond
+	&= \sum_{i=0}^1
+	\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 -
+		4|\bra{i}\rho_0\ket{u_i}|^2}  \\
+	&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2}
+	\\
+	&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1}
+		\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
+	&= \sum_{i=0}^1
+	\sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 }
+	= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
+	&= |1-e^{i \phi }|.
+	\end{split}
+	\end{equation}
+	Observe that
+	\begin{equation}
+	\begin{split}
+ \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left(
+	\Id \otimes \sqrt{\rho} \right) \|_1 = \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top
+	\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
+	\end{split}
+	\end{equation}
+	Due to that, we know
+	that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ equals $\frac{1}{\sqrt{2} } |
+	\Id_2 \rangle \rangle$ is the discriminator of the problem
+	of discrimination between
+	$\PP_{\Id} $ and $\PP_U$ for
+	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm).      Hence, we obtain that \begin{equation}
+	\ket{\psi_{0}} =  \frac{1}{\sqrt{2} } |
+	\Id_2 \rangle \rangle,
+	\end{equation}
+	which completes the proof.
+\end{proof}
+
+\begin{proposition}\label{prop:optimal-measurement}
+	Consider the problem of discrimination between von Neumann measurements $\PP_U$
+	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0,
+	2\pi)$.
+	The   controlled unitaries $V_0$ and $V_1$
+	have the form
+	\begin{equation}
+	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
+	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
+		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
+	\end{equation}
+	and
+	\begin{equation}
+	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
+	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
+	&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
+	\end{equation}
+\end{proposition}
+
+\begin{proof}
+	From Proposition~\ref{prop-discrim} we obtain the exact form of discriminator given by
+	\begin{equation}
+	\ket{\psi_0}  = \frac{1}{\sqrt{2}} |\Id_2
+	\rangle \rangle.
+	\end{equation}
+	Repeating the scheme used to distinguish the von Neumann measurements in the Hadamard basis (see \ref{app:hadamard}), we use the Hahn Jordan decomposition and then we create the projective operators into the positive and negative part of $X$ matrix.
+%	From Holevo-Helstrom theorem~\cite{watrous}, we constrain a final optimal measurement $\PP_{V_i}$.
+%	Let us define
+%	\begin{equation}
+%	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id
+%	\otimes \Id_2 \right)(\proj{\psi_0}).
+%	\end{equation}
+%	
+%	
+%	
+%	From the Hahn-Jordan decomposition, let us note
+%	\begin{equation}
+%	X = P - Q
+%	\end{equation}
+%	where $P, Q \ge 0 $.
+%	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
+%	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
+%	\begin{equation}
+%	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
+%	\end{equation}
+%	and
+%	\begin{equation}
+%	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
+%	\end{equation}
+%	Hence, we define $V_0$ as
+%	\begin{equation}
+%	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
+%	\end{equation}
+%	and $V_1$ as
+%	\begin{equation}
+%	\begin{cases}
+%	V_1 \ket{y_p} = \ket{0} \\
+%	V_1 \ket{y_q} = \ket{1}
+%	\end{cases}.
+%	\end{equation}
+%	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H
+%	\diag(1, e^{i \phi })H$, 
+	Hence, the explicit form of $V_0$ and $V_1$ is given as
+	follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
+	\begin{equation}
+	V_0 = \left(
+	\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
+	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
+		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
+	\end{array}
+	\right),
+	\end{equation}
+and
+	\begin{equation}
+	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
+	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4}
+	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right),
+	\end{equation}
+	where $\phi \in [0,2\pi)$.
+\end{proof}
+
+\section{Output YAML files} \label{app:example}
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-Consider the particular experiment data
-\begin{lstlisting}[language=Python]
-data:
-- target: 0
-  ancilla: 1
-  phi: 0.0
-  results_per_circuit:
-  - name: id
-  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
-  mitigation_info:
-	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
-\end{lstlisting}
-	The data includes \textit{target, ancilla, phi},
-	and \textit{results\_pre\_circuit}.   The first three pieces of information have already been described. The last data  \textit{results\_pre\_circuit} gives us 
-	the following additional informations: 
-	\begin{itemize}
-		\item  name: id:  the information which measurement is used during experiment,   $\PP_{U}$ or $\PP_{\Id}$. In this example we consider  $\PP_{\Id}$. 
-		\item histogram: {'00': 28, '01': 26, '10': 21, '11': 25}: the dictionary with measurement's outcomes.
-The keys represent possible measurement oucomes, whereas the values present number of occurrences.
-		\item mitigation\_info:  ??????????  ~\cite{mthree, mthreepublication}
-		\item mitigated\_histogram:  the histogram with measurement's outcomes after mitigation.
-	\end{itemize}
-
-\subsubsection{(Optional) Getting status of asynchronous jobs}
-The whole point of running the asynchronous jobs is to be able to retrieve the results at a later point in time.
-But how do we know that the jobs you submitted to the backend have completed or not?
-We can inspect the file manually and check e.g.
-IBMQ dashboard to see the statuses of the jobs.
-However, PyQBench provides a helper command that will fetch the statuses for you.
-The command is:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier status async_results.yml
-\end{lstlisting}
-and it will display dictionary with histogram of statuses.
-
-\subsubsection{Resolving asynchronous jobs}
-If the status of jobs is \textit{DONE}, we have to obtain measurements from the submitted jobs. This is done using the following command:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier resolve async-results.yml resolved.yml
-\end{lstlisting}
-
-The resolved results, stored in \textit{resolved.yml}, would look just like the experiment was run synchronously.
-In other words, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment (see \ref{app:example}).
-Now, we are ready to computing probabilities.
-
-\subsubsection{Computing probabilities}
-Regardless of whether we use a synchronous or asynchronous approach, we can convert the resulting YML file \textit{results.yml} to a CSV file by creating a result table in which we place the results of discrimination probabilities.
-To construct a table with probabilities, you can use the following command
-\begin{lstlisting}[language=Python]
-qbench disc-fourier tabulate results.yml results.csv 
-\end{lstlisting}
-A single row for each tuple of \textit{(target, ancilla, phi)}.
-The \textit{disc\_prob} column will contain the discrimination probability for given configuration.
-The \textit{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
-A sample csv file is provided below:
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1]{results/async_result}
-	\caption{Tabulate results}
-	\label{fig:tabulateresults}
-\end{figure}
-
-\section{Impact}
-\todo[inline]{OJCIEC WYKAZ SIE, bo trzeba to dobrze sprzedac, nizej tekst z formatki softwarex co powinna zawierac ta sekcja}
-This software has two main contributions.
-
-\textbf{This is the main section of the article and the reviewers weight the
-description here appropriately}
-
-Indicate in what way new research questions can be pursued as a result of the
-software (if any).
-
-Indicate in what way, and to what extent, the pursuit of existing research
-questions is improved (if so).
-
-Indicate in what way the software has changed the daily practice of its users
-(if so).
-
-Indicate how widespread the use of the software is within and outside the
-intended user group.
-
-Indicate in what way the software is used in commercial settings and/or how it
-led to the creation of spin-off companies (if so).
-
-\section{Conclusions}
-\label{}
-
-In this study, we develop  a Python library PyQBench, an innovative open-source framework for benchmarking
-gate-based quantum computers.
-
-%%%%%%%%%%%%%%
-PyQBench can benchmark NISQ devices by verifying their capability of
-discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
-family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
-measurements instead of predefined ones.
-\section{Conflict of Interest}
-No conflict of interest exists: We wish to confirm that there are no known
-conflicts of interest associated with this publication and there has been no
-significant financial support for this work that could have influenced its out-
-come.
-
-\section*{Acknowledgements}
-
-This work is  supported by
-the project “Near-term quantum computers Challenges, optimal implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the Team-Net programme of the Foundation for Polish Science co-financed by the European Union under the European Regional Development Fund.
-PL is also a holder of European Union scholarship through the European Social Fund,
-grant InterPOWER (POWR.03.05.00-00-Z305).
-
-\begin{thebibliography}{00}
-	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
-S., Smith, K.
-N., Viszlai, J., ...
-Chong, F.
-T.
-(2022, April).
-Supermarq: A scalable quantum benchmark suite.
-In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp.
-587-603).
-IEEE.
-	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
-	\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
-B., Jost, J.
-D., ...
-Wineland, D.
-J.
-(2008).
-Randomized benchmarking of quantum gates.
-Physical Review A, 77(1), 012307.
-	\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
-	\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
- \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
-(2021).
-Benchmarking near-term quantum computers via random circuit sampling.
-arXiv preprint arXiv:2105.05232.
-\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
-\bibitem{quark2022} Finžgar, J.
-R., Ross, P., Hölscher, L., Klepsch, J.,  Luckow, A.
-(2022, September).
-QUARK: A framework for quantum computing application benchmarking.
-In 2022 IEEE International Conference on Quantum Computing and Engineering (QCE) (pp.
-226-237).
-IEEE.
-\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and
-beyond." Quantum 2 (2018): 79.
-\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking
-gate-based quantum computers." Computer Physics Communications 220 (2017):
-44-55.
-\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication
-protocols as a benchmark for programmable quantum computers." Quantum
-Information Processing 18.1 (2019): 1-23.
-\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
-and Raphael C. Pooser. "Generative model benchmarks for superconducting
-qubits." Physical Review A 99.6 (2019): 062323.
-\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative
-modeling approach for benchmarking and training shallow quantum circuits." npj
-Quantum Information 5.1 (2019): 1-9.
-\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for
-optimal single-shot discrimination of quantum measurements." Physical Review A
-98.4 (2018): 042103.
-\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
-\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
-\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
-\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
-
-\bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
-\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
-\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
-\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
-(2021).
-On the optimal certification of von Neumann measurements.
-Scientific Reports, 11(1), 3623.
-\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
-\end{thebibliography}
-
-\todo[inline]{Please add the reference to the software repository if DOI for
-software  is available. }
-
-\section*{Current executable software version}
-\label{}
-
-Ancillary data table required for sub version of the executable software: (x.1,
-x.2 etc.) kindly replace examples in right column with the correct information
-about your executables, and leave the left column as it is.
-
-\begin{table}[!h]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-\hline
-\textbf{Nr.} & \textbf{(Executable) software metadata description} &
-\textbf{Please fill in this column} \\
-\hline
-S1 & Current software version & For example 1.1, 2.4 etc. \\
-\hline
-S2 & Permanent link to executables of this version  & For example:
-$https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
-\hline
-S3 & Legal Software License & List one of the approved licenses \\
-\hline
-S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS,
-Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based
-etc. \\
-\hline
-S5 & Installation requirements \& dependencies & \\
-\hline
-S6 & If available, link to user manual - if formally published include a
-reference to the publication in the reference list & For example:
-$http://mozart.github.io/documentation/$ \\
-\hline
-S7 & Support email for questions & \\
-\hline
-\end{tabular}
-\caption{Software metadata (optional)}
-\label{}
-\end{table}
-
-\appendix
-\section{Mathematical preliminaries} \label{app:preliminaries}
-
-Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
-the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
-$M_d$.
-%The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
-%will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
-%matrices of dimension $d$ by $\HH_d^+$.
-By $\Omega_d$, we will denote the set of quantum states, that is
-positive semidefinite operators having trace equal to one.
-The subset of $M_d$ consisting of unitary matrices will be denoted
-by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$.
-%An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$, whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
-
-We will also need a linear mapping transforming $M_{d_1}$ into
-$M_{d_2}$, which will be denoted
-\begin{equation}
-\Phi: M_{d_1 } \rightarrow M_{d_2}.
-\end{equation}
-There
-exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $M_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism.
-For a given linear mapping $\Phi$ the corresponding Choi operator $J(\Phi)$ is explicitly written as
-\begin{equation}
-J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
-
-We introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
-and trace preserving (CPTP).
-In this work we will consider a special class of quantum channels, called unitary channels.  A
-channel
-$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for any $U \in
-\UU_d$.
-
-The action of
-von Neumann measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
-seen as  a measure-and-prepare quantum channel as follows \begin{equation}
-\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-\end{equation}
-Moreover, observe that each von Neumann measuement $\PP_{U}$ poses a  composition of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
-
-We need to also briefly discuss about the distance between unitary channels and von Neumann measurements. From \cite[Theorem 1]{puchala2018strategies}, the distance between measurements $\PP_U$ and
-$\PP_\Id$ ie equal to
-\begin{equation}
-\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} -
-\Phi_\Id\|_\diamond,
-\end{equation} whereas to express the distance between unitary channels, we need to introduce the notion of numerical range. The set \begin{equation}
-W(A) =\{\bra{x}A\ket{x}: \ket{x} \in
-\mathbb{C}^d, \;
-\;\braket{x}{x}=1\}.
-\end{equation}
-is called numerical range of  a matrix $A \in M_d$.
-The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.
-Due to the definition of $W(A)$, the distance between two unitary channels $\Phi_{U} $ and $\Phi_\Id$
-can be written as
-\begin{equation}
-\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-\end{equation}
-where $\nu = \min_{x \in W(U^\dagger)} |x|  $.
-
-\section{Discrimination task for Hadamard gate}\label{app:hadamard}
-For the discrimination task between von Neumann measurements $\PP_{U}$ and $\PP_\Id$, where $U = H$ (the Hadamard gate) the key is to determine the discriminator $\psi_0$ and calculate the diamond norm $\| \mathcal{P}_H - \PP_\Id \|_\diamond$.
-Using semidefinite programming \cite{lewandowska2021certification, watrous2021simplier}, we obtain 
-\begin{equation}
-\| \mathcal{P}_H - \PP_\Id \|_\diamond = \sqrt{2}. 
-\end{equation}
-Observe that matrix $E_0$ minimizing Eq.~\eqref{}
-is of the form
-\begin{equation}
-E_0 = \frac{1}{2} \left( \begin{matrix} 
-1 + i & 0  \\  0 & -1-i 
-\end{matrix} \right), 
-\end{equation}
-which means 
-\begin{equation}
-\| \PP_{H} - \PP_{\Id} \|_\diamond = \| \Phi_{HE_0} - \Phi_{\Id}\|_\diamond,
-\end{equation}
-where $\Phi_{U}$ is a unitary channel. 
-Next, in order to construct the discriminator $\ket{\psi_0}$ we use Lemma 5 and the proof of Theorem 1 in ~\cite{puchala2018strategies}. We show that there exist states 
- $\rho_1 $  and $\rho_2$ of the form $ \rho_1  = \frac{1}{2} \left( \begin{matrix} 
- 1  & i  \\  -i & 1
- \end{matrix} \right)  $  and $\rho_2 = \frac{1}{2} \left( \begin{matrix} 
- 1 & -i \\  i & 1 
- \end{matrix} \right), $ respectively. Thus, form 
- the proof of Theorem 1 in ~\cite{puchala2018strategies} we have 
- \begin{equation}
- \rho_0 = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2 = \frac{1}{2} \left( \begin{matrix} 
- 1  &  0  \\  0  & 1
- \end{matrix} \right).
- \end{equation}
- It direcly implies that 
- \begin{equation}
- \ket{\psi_0} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}).  \end{equation}
- Next, from Holevo-Helstrom theorem~\cite{watrous}, we determine a final optimal measurement $\PP_{V_i}$. 
- Let us consider \begin{equation}
- X = \left(\PP_{H} \otimes \Id \right)(\proj{\psi_0}) - \left(\PP_{\Id} \otimes \Id \right) (\proj{\psi_0})
-  \end{equation}
- From the Hahn-Jordan decomposition, let us note
- \begin{equation}
- X = P - Q
- \end{equation}
- where $P, Q \ge 0 $.
- Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
- respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
- \begin{equation}
- \Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
- \end{equation}
- and
- \begin{equation}
- \Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
- \end{equation}
- Hence, we define $V_0$ as
- \begin{equation}
- \begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
- \end{equation}
- and $V_1$ as
- \begin{equation}
- \begin{cases}
- V_1 \ket{y_p} = \ket{0} \\
- V_1 \ket{y_q} = \ket{1}
- \end{cases}.
- \end{equation}
- For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as
- follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
- \begin{equation}
- V_0 =
- \left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
- \end{equation}
- and \begin{equation}
- V_1 =
- \left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
- \end{equation}
- where \begin{equation}
- \alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} \cos\left( \frac{3}{8} \pi \right),
- \end{equation}
- \begin{equation}
- \beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} \sin\left( \frac{3}{8} \pi \right).
- \end{equation}
-
-\section{Optimal probability for parametrized Fourier family} \label{app:optimal-probability}
-
-Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
-Assume that the unitary matrix $U$ is of the form
-\begin{equation}
-U = H
-\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
-\end{equation}
-%\begin{equation}
-%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
-%\end{equation}
-where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this section we present theoretical probability of correct
-discrimination between these measurements. To do that, we will present an auxiliary lemma.
-\begin{lemma}\label{lemma:min-e-optimal}
-	Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let
-	$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds
-	\begin{equation}
-	\min_{E \in \diaguni_2} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond = \|\Phi_{U} -
-	\Phi_\Id\|_\diamond,
-	\end{equation}
-\end{lemma}
-
-\begin{proof} Recall that the distance between two unitary channels is given by
-	$
-	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-	$
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$.
-	For $U = H
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So,
-	\begin{equation}
-	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |.
-	\end{equation}
-	It implies that it is enough to prove  \begin{equation}
-	\min_{E \in \diaguni_2} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
-	\end{equation}
-	%		It implies that we can prove  equivalently  the following condition
-	%		\begin{equation}
-	%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
-	%		\end{equation}
-	This condition is equivalent to show
-	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
-	\end{equation}
-	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
-
-	%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
-	The celebrated Hausdorf-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
-	$W(A)$ of any matrix $A \in M_d$ is a convex set, and therefore we have
-	\begin{equation}
-	W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}.
-	\end{equation}
-	So, we can assume that
-	\begin{equation}
-	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| =
-	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|.
-	\end{equation}
-	Then, we have
-	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in
-		\Omega_2} \left| \tr \left( \rho U E \right) \right|.
-	\end{equation}
-	For that, our task is reduced to show that
-	\begin{equation}
-	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \max_{E \in \diaguni_2 } \nu_{E}.
-	\end{equation}
-
-	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $
-	and take $\rho =
-	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $.
-	From spectral theorem, let us decompose $U$ as
-	\begin{equation}
-	U= \lambda_0 \ketbra{x_0}{x_0} + \lambda_1 \ketbra{x_1}{x_1},
-	\end{equation}
-	where  for eigenvalue $\lambda_0 = 1$, the corresponding
-	eigenvector is
-	of the form $\ket{x_0} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_1= e^{i \phi}$ we have $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
-	$.
-	Then, we have
-	\begin{equation}
-	\begin{split}
-	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
-	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
-	\frac{1}{2} \left| \tr\left((   \proj{x_0} +e^{i \phi}\proj{x_1} ) E \right)
-	\right|  =
-	\frac{1}{2} \left|  \bra{x_0} E \ket{x_0} +  e^{i \phi}\bra{x_1} E \ket{x_1}
-	\right| = \\&
-	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right|
-	=
-	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le
-	\max_{E \in \diaguni_2 } \nu_{E},
-	\end{split}
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-\begin{theorem}\label{th:probability}
-	The optimal probability of correct discrimination between von Neumann
-	measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
-	where $\phi \in [0, 2\pi)$ is given by
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
-	\end{equation}
-\end{theorem}
-
-\begin{proof}
-	From Holevo-Helstrom theorem, we obtain
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
-	\end{equation}
-	From~\cite[Theorem 1]{puchala2018strategies}, we have
-	\begin{equation}
-	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond.
-	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal},  we know that for
-	$U =  H \diag(1, e^{i \phi}) H^\dagger$,  it also holds that
-	\begin{equation}
-	\min_{E \in \diaguni_2} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond = \|\Phi_{U} -
-	\Phi_\Id\|_\diamond,
-	\end{equation} which is exactly equal to
-	\begin{equation}
-	\|\Phi_{U} -
-	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|.
-	\end{equation}
-	%	Finally, we obtain that
-	%	\begin{equation}
-	%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
-	%	\end{equation}
-	It implies that
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
-	\end{equation} which completes the proof.
-\end{proof}
-
-\section{Optimal discrimination strategy for parametrized Fourier family} \label{app:optimal-strategy}
-
-In this Appendix we create the optimal
-theoretical strategy of  discrimination between $\PP_{U}$ and $\PP_{\Id}$.
-To indicate the optimal strategy, we will present two propositions.
-The first one is concentrated around the discriminator as the optimal input state of discrimination strategy, whereas the second one describes the optimal final measurement.
-
-\begin{proposition}\label{prop-discrim}
-	Consider the problem of discrimination between von Neumann measurements $\PP_U$
-	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0,
-	2\pi)$.  The  discriminator has the form
-	\begin{equation}
-	\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
-	\end{equation}
-\end{proposition}
-
-\begin{proof}
-	Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0,
-	2\pi)$ be decomposed as
-	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2},
-	\end{equation}
-	where  for eigenvalue $\lambda_1 = 1$, the corresponding
-	eigenvector is
-	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
-	$.
-	For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
-	\begin{equation}
-	\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) J(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
-	Hence, we obtain
-	\begin{equation}
-	\begin{split}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond
-	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right)
-	J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1
-	\\
-	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right)
-	\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top
-	\right\|_1  \\
-	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes
-	\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
-	\\
-	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left(
-	\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
-	\end{split}
-	\end{equation}
-	One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x},
-	\ket{y}$ the following equation holds~\cite{watrous}
-	\begin{equation}
-	\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha
-		\beta |\braket{x}{y}|^2}.
-	\end{equation}
-	By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho}
-		\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho}
-		\ket{i} \|}$ we have
-	\begin{equation}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2}
-	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i
-		}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
-	\end{equation}
-	Let us take  $\rho_0 =   \frac{1}{2}
-	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
-	\begin{equation}
-	\begin{split}
-	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond
-	&= \sum_{i=0}^1
-	\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 -
-		4|\bra{i}\rho_0\ket{u_i}|^2}  \\
-	&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2}
-	\\
-	&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1}
-		\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
-	&= \sum_{i=0}^1
-	\sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 }
-	= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
-	&= |1-e^{i \phi }|.
-	\end{split}
-	\end{equation}
-	Observe that
-	\begin{equation}
-	\begin{split}
- \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left(
-	\Id \otimes \sqrt{\rho} \right) \|_1 = \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top
-	\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
-	\end{split}
-	\end{equation}
-	Due to that, we know
-	that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ equals $\frac{1}{\sqrt{2} } |
-	\Id_2 \rangle \rangle$ is the discriminator of the problem
-	of discrimination between
-	$\PP_{\Id} $ and $\PP_U$ for
-	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm).      Hence, we obtain that \begin{equation}
-	\ket{\psi_{0}} =  \frac{1}{\sqrt{2} } |
-	\Id_2 \rangle \rangle,
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-\begin{proposition}\label{prop:optimal-measurement}
-	Consider the problem of discrimination between von Neumann measurements $\PP_U$
-	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0,
-	2\pi)$.
-	The   controlled unitaries $V_0$ and $V_1$
-	have the form
-	\begin{equation}
-	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
-	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
-		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
-	\end{equation}
-	and
-	\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
-	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
-	&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
-	\end{equation}
-\end{proposition}
-
-\begin{proof}
-	From Proposition~\ref{prop-discrim} we obtain the exact form of discriminator given by
-	\begin{equation}
-	\ket{\psi_0}  = \frac{1}{\sqrt{2}} |\Id_2
-	\rangle \rangle.
-	\end{equation}
-	Repeating the scheme used to distinguish the von Neumann measurements in the Hadamard basis (see \ref{app:hadamard}), we use the Hahn Jordan decomposition and then we create the projective operators into the positive and negative part of $X$ matrix.
-%	From Holevo-Helstrom theorem~\cite{watrous}, we constrain a final optimal measurement $\PP_{V_i}$.
-%	Let us define
-%	\begin{equation}
-%	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id
-%	\otimes \Id_2 \right)(\proj{\psi_0}).
-%	\end{equation}
-%	
-%	
-%	
-%	From the Hahn-Jordan decomposition, let us note
-%	\begin{equation}
-%	X = P - Q
-%	\end{equation}
-%	where $P, Q \ge 0 $.
-%	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
-%	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
-%	\begin{equation}
-%	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
-%	\end{equation}
-%	and
-%	\begin{equation}
-%	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
-%	\end{equation}
-%	Hence, we define $V_0$ as
-%	\begin{equation}
-%	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
-%	\end{equation}
-%	and $V_1$ as
-%	\begin{equation}
-%	\begin{cases}
-%	V_1 \ket{y_p} = \ket{0} \\
-%	V_1 \ket{y_q} = \ket{1}
-%	\end{cases}.
-%	\end{equation}
-%	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H
-%	\diag(1, e^{i \phi })H$, 
-	Hence, the explicit form of $V_0$ and $V_1$ is given as
-	follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
-	\begin{equation}
-	V_0 = \left(
-	\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
-	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
-		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
-	\end{array}
-	\right),
-	\end{equation}
-and
-	\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
-	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4}
-	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right),
-	\end{equation}
-	where $\phi \in [0,2\pi)$.
-\end{proof}
-
-\section{Example of files} \label{app:example}
 

### 2023-02-18 txt/manuscript.tex
doneeee ole ole ole

@@
 \address{Institute of Theoretical and Applied Informatics, Polish Academy
-	of Sciences, Ba{\l}tycka 5, 44-100 Gliwice, Poland}
+	of Sciences, Ba{\l}tycka~5, 44-100 Gliwice, Poland}
 
@@
 \begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
 Quantum computing \sep
@@
 Discrimination of quantum measurements \sep
-Discrimination of von Neumann Measurements \sep
+Discrimination of von Neumann measurements \sep
 Open-source \sep
@@
 
-\todo[inline]{lewandowska add cite !!!}
-
 Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market,
@@
 solutions. Among hardware providers offering public access to their gate--based devices, one could
-mention Rigetti, IBM, Oxford Quantum Group, IonQ or Xanadu. Other vendors offer devices operating in
-different paradigms. Notably, one could mention D-Wave and their quantum
-annealers, or QuEra devices based on neural atoms.  Most vendors provide their own software stack and
+mention Rigetti \cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu \cite{xanadu}. Other vendors offer devices operating in
+different paradigms. Notably, one could mention D-Wave \cite{dwave} and their quantum
+annealers, or QuEra devices \cite{quera} based on neural atoms.  Most vendors provide their own software stack and
 application programming interface for accessing their devices. To name a few, Rigetti's computers
-are available through their Forest SDK and PyQuil library and IBM Q computers can be accessed
-through Qiskit or IBM Quantum Experience web interface. Some cloud services, like Amazon Braket, offer access to several quantum devices under a unified API. On top of that, several
+are available through their Forest SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
+through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}.
+Some cloud services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified API.
+On top of that, several
 libraries and frameworks can integrate with different hardware vendors. Examples of such frameworks
-include IBM Q's Qiskit or Zapata Computing's Orquestra.
-
-It is well known that NISQ devices have their limitations \cite{}. The question is to what extent those
+include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.
+
+It is well known that NISQ devices have their limitations \cite{preskillnew}. The question is to what extent those
 devices can perform meaningful computations? To answer this question, one has to devise a
@@
 already exist several approaches. 
-One could mention randomized benchmarking  \cite{knill2008randomized} , benchmarks based on the quantum volume\cite{cross2019validating, moll2018quantum} or or cross-entropy benchmarking ~\cite{arute2019quantum, neill2018blueprint}.
+One could mention randomized benchmarking  \cite{knill2008randomized}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume} or or cross-entropy benchmarking \cite{arute2019quantum, neill2018blueprint}.
 
@@
 First pair is 0 and 1, second pair is 1 and 2.
-%	Notice that we distinguish between ancilla and target qubit, so e.g
-%	\begin{lstlisting}[language=Python]
-%qubits:
-%	- target: 0
-%      ancilla: 1
-%	\end{lstlisting}
-%	is not the same as 
-%	\begin{lstlisting}[language=Python]
-%qubits:
-%	- target: 1
-%      ancilla: 0
-%	\end{lstlisting}
 \begin{lstlisting}[language=Python]
@@
 \section{Conflict of Interest}
-No conflict of interest exists: We wish to confirm that there are no known
+We wish to confirm that there are no known
 conflicts of interest associated with this publication and there has been no
@@
 \begin{thebibliography}{00}
+\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and beyond." Quantum 2 (2018): 79.
+\bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
+\bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
+\bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
+\bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18. 
+\bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
+\bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
+\bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
+\bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
+\bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
+\bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
+\bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
+\bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
+\bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
+\bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
+\bibitem{knill2008randomized}
+Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., ...  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.	
+\bibitem{cross2019validating}
+Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
+\bibitem{moll2018quantum}
+Moll, N., Barkoutsos, P., Bishop, L.
+S., Chow, J.
+M., Cross, A., Egger, D.
+J., ...
+Temme, K.
+(2018).
+Quantum optimization using variational algorithms on near-term quantum devices.
+Quantum Science and Technology, 3(3), 030503.
+\bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
+\bibitem{arute2019quantum}Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
+C., Barends, R., ...
+Martinis, J.
+M.
+(2019).
+Quantum supremacy using a programmable superconducting processor.
+Nature, 574(7779), 505-510.
+\bibitem{neill2018blueprint}
+Neill, C., Roushan, P., Kechedzhi, K., Boixo, S., Isakov, S.
+V., Smelyanskiy, V., ...
+Martinis, J.
+M.
+(2018).
+A blueprint for demonstrating quantum supremacy with superconducting qubits.
+Science, 360(6385), 195-199.
+\bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
+(2021).
+Benchmarking near-term quantum computers via random circuit sampling.
+arXiv preprint arXiv:2105.05232.
+\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
+B., Jost, J.
+D., ...
+Wineland, D.
+J.
+(2008).
+Randomized benchmarking of quantum gates.
+Physical Review A, 77(1), 012307.
+\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
+\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
+\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
+\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for
+optimal single-shot discrimination of quantum measurements." Physical Review A
+98.4 (2018): 042103.
+\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
+\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
+\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
+\bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
+\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
+\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
+\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
+(2021).
+On the optimal certification of von Neumann measurements.
+Scientific Reports, 11(1), 3623.
+\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
+\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
+\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
+
+	\todo[inline]{do wykorzystania cite}
+
 	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
@@
 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
-	\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
-B., Jost, J.
-D., ...
-Wineland, D.
-J.
-(2008).
-Randomized benchmarking of quantum gates.
-Physical Review A, 77(1), 012307.
-	\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
-	\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
- \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
-(2021).
-Benchmarking near-term quantum computers via random circuit sampling.
-arXiv preprint arXiv:2105.05232.
-\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
+
 \bibitem{quark2022} Finžgar, J.
@@
 IEEE.
-\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and
-beyond." Quantum 2 (2018): 79.
 \bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking
@@
 44-55.
-\bibitem{cross2019validating}
-Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
+
 \bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication
@@
 Quantum Information 5.1 (2019): 1-9.
-\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for
-optimal single-shot discrimination of quantum measurements." Physical Review A
-98.4 (2018): 042103.
-\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
-\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
-\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
-\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
-
-\bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
-\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
-\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
-\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
-(2021).
-On the optimal certification of von Neumann measurements.
-Scientific Reports, 11(1), 3623.
-\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
-\bibitem{arute2019quantum}Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
-C., Barends, R., ...
-Martinis, J.
-M.
-(2019).
-Quantum supremacy using a programmable superconducting processor.
-Nature, 574(7779), 505-510.
-\bibitem{knill2008randomized}
-Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., ...  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.
-\bibitem{moll2018quantum}
-Moll, N., Barkoutsos, P., Bishop, L.
-S., Chow, J.
-M., Cross, A., Egger, D.
-J., ...
-Temme, K.
-(2018).
-Quantum optimization using variational algorithms on near-term quantum devices.
-Quantum Science and Technology, 3(3), 030503.
-
-\bibitem{neill2018blueprint}
-Neill, C., Roushan, P., Kechedzhi, K., Boixo, S., Isakov, S.
-V., Smelyanskiy, V., ...
-Martinis, J.
-M.
-(2018).
-A blueprint for demonstrating quantum supremacy with superconducting qubits.
-Science, 360(6385), 195-199.
 
@@
 
-\todo[inline]{Please add the reference to the software repository if DOI for
-software  is available. }
-
-\section*{Current executable software version}
-\label{}
-
-Ancillary data table required for sub version of the executable software: (x.1,
-x.2 etc.) kindly replace examples in right column with the correct information
-about your executables, and leave the left column as it is.
-
-\begin{table}[!h]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-\hline
-\textbf{Nr.} & \textbf{(Executable) software metadata description} &
-\textbf{Please fill in this column} \\
-\hline
-S1 & Current software version & For example 1.1, 2.4 etc. \\
-\hline
-S2 & Permanent link to executables of this version  & For example:
-$https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
-\hline
-S3 & Legal Software License & List one of the approved licenses \\
-\hline
-S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS,
-Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based
-etc. \\
-\hline
-S5 & Installation requirements \& dependencies & \\
-\hline
-S6 & If available, link to user manual - if formally published include a
-reference to the publication in the reference list & For example:
-$http://mozart.github.io/documentation/$ \\
-\hline
-S7 & Support email for questions & \\
-\hline
-\end{tabular}
-\caption{Software metadata (optional)}
-\label{}
-\end{table}
+%\section*{Current executable software version}
+%\label{}
+%
+%Ancillary data table required for sub version of the executable software: (x.1,
+%x.2 etc.) kindly replace examples in right column with the correct information
+%about your executables, and leave the left column as it is.
+%
+%\begin{table}[!h]
+%\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
+%\hline
+%\textbf{Nr.} & \textbf{(Executable) software metadata description} &
+%\textbf{Please fill in this column} \\
+%\hline
+%S1 & Current software version & For example 1.1, 2.4 etc. \\
+%\hline
+%S2 & Permanent link to executables of this version  & For example:
+%$https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
+%\hline
+%S3 & Legal Software License & List one of the approved licenses \\
+%\hline
+%S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS,
+%Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based
+%etc. \\
+%\hline
+%S5 & Installation requirements \& dependencies & \\
+%\hline
+%S6 & If available, link to user manual - if formally published include a
+%reference to the publication in the reference list & For example:
+%$http://mozart.github.io/documentation/$ \\
+%\hline
+%S7 & Support email for questions & \\
+%\hline
+%\end{tabular}
+%\caption{Software metadata (optional)}
+%\label{}
+%\end{table}
 
@@
 \Phi_\Id\|_\diamond,
-\end{equation} whereas to express the distance between unitary channels, we need to introduce the notion of numerical range. The set \begin{equation}
+\end{equation} whereas to express the distance between unitary channels, we need to introduce the notion of numerical range \cite{numericalrangle}. The set \begin{equation}
 W(A) =\{\bra{x}A\ket{x}: \ket{x} \in
@@
  where \begin{equation}
- \alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} \cos\left( \frac{3}{8} \pi \right),
- \end{equation}
- \begin{equation}
- \beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} \sin\left( \frac{3}{8} \pi \right).
+ \alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} = \cos\left( \frac{3}{8} \pi \right),
+ \end{equation}
+ \begin{equation}
+ \beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} = \sin\left( \frac{3}{8} \pi \right).
  \end{equation}
@@
 \section{Optimal probability for parametrized Fourier family} \label{app:optimal-probability}
-
 Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
@@
 	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left(
-	\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
+	\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1. 
 	\end{split}
@@
 \section{Output YAML files} \label{app:example}
-\begin{lstlisting}[language=Python]
+In this appendix we present examples of YAML's files obtained from synchronous ans asynchronous experiments. We will start at synchronous case.
+
+\begin{lstlisting}[language=Python, caption=Defining experiment file]
+type: discrimination-fourier
+qubits:
+	- target: 0
+	  ancilla: 1
+	- target: 1
+	  ancilla: 2
+angles:
+	start: 0
+	stop: 2 * pi
+	num_steps: 3
+gateset: ibmq
+method: direct_sum
+num_shots: 100
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python, caption=Defining backend file]
+name: ibmq_quito
+asynchronous: false
+provider:
+	hub: ibm-q
+	group: open
+	project: main
+
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python, caption=Results (synchronous)]
 metadata:
@@
 		ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
-mitigated_histogram: {'00': 0.009552870928837118, '01': 0.007194089383161034,
-'10': 0.5236791012692514, '11': 0.4595739384187503}
+	mitigated_histogram: {'00': 0.009552870928837118, '01': 0.007194089383161034, '10': 0.5236791012692514, '11': 0.4595739384187503}
   - name: u
@@
 \end{lstlisting}
+For the same experiment file, we use the flag \textit{asynchronous: true} to define asynchronous experiment.
+
+\begin{lstlisting}[language=Python, caption=Backend file]
+name: ibmq_quito
+asynchronous: true
+provider:
+	hub: ibm-q
+	group: open
+	project: main
+
+\end{lstlisting}
+If backend is asynchronous, the output will contain intermediate data
+containing, amongst others, job ids correlated with the circuit they
+correspond to.
+
+\begin{lstlisting}[language=Python, caption=Resolved results]
+metadata:
+	experiments:
+		type: discrimination-fourier
+		qubits:
+		- {target: 0, ancilla: 1}
+		- {target: 1, ancilla: 2}
+		angles: {start: 0.0, stop: 6.283185307179586, num_steps: 3}
+		gateset: ibmq
+		method: direct_sum
+		num_shots: 100
+	backend_description:
+		name: ibmq_quito
+		asynchronous: true
+		provider: {group: open, hub: ibm-q, project: main}
+data:
+- job_id: 63e7f17a17b7ed49ca24e05b
+  keys:
+  - [0, 1, id, 0.0]
+  - [0, 1, u, 0.0]
+  - [0, 1, id, 3.141592653589793]
+  - [0, 1, u, 3.141592653589793]
+  - [0, 1, id, 6.283185307179586]
+  - [0, 1, u, 6.283185307179586]
+  - [1, 2, id, 0.0]
+  - [1, 2, u, 0.0]
+  - [1, 2, id, 3.141592653589793]
+  - [1, 2, u, 3.141592653589793]
+  - [1, 2, id, 6.283185307179586]
+  - [1, 2, u, 6.283185307179586]
+
+\end{lstlisting}
+Finally, if the status of jobs is DONE, we resolve the measurements from the
+submitted jobs obtaining the following file.
+\begin{lstlisting}[language=Python, caption=Results (asynchronous)]
+metadata:
+  experiments:
+	type: discrimination-fourier
+	qubits:
+	- target: 0
+	  ancilla: 1
+	- target: 1
+	  ancilla: 2
+	angles:
+	  start: 0.0
+	  stop: 6.283185307179586
+	  num_steps: 3
+	gateset: ibmq
+	method: direct_sum
+	num_shots: 100
+  backend_description:
+	name: ibmq_quito
+	asynchronous: true
+	provider:
+		group: open
+		hub: ibm-q
+		project: main
+data:
+- target: 0
+  ancilla: 1
+  phi: 0.0
+  results_per_circuit:
+  - name: id
+	histogram:
+		'00': 27
+		'01': 28
+		'10': 18
+		'11': 27
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.052200000000000024
+		prob_meas1_prep0: 0.0172
+	  ancilla:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	mitigated_histogram:
+		'00': 0.254196166145997
+		'01': 0.2790358060520916
+		'10': 0.1732699847244092
+		'11': 0.29349804307750227
+  - name: u
+	histogram:
+		'00': 29
+		'01': 17
+		'10': 30
+		'11': 24
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.052200000000000024
+		prob_meas1_prep0: 0.0172
+	  ancilla:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	mitigated_histogram:
+		'00': 0.2733793468261183
+		'01': 0.1621115306717096
+		'10': 0.3045273800167787
+		'11': 0.2599817424853933
+- target: 0
+  ancilla: 1
+  phi: 3.141592653589793
+  results_per_circuit:
+  - name: id
+	histogram:
+		'00': 3
+		'01': 5
+		'10': 37
+		'11': 55
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.052200000000000024
+		prob_meas1_prep0: 0.0172
+	  ancilla:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	mitigated_histogram:
+		'00': 0.006189545789708441
+		'01': 0.016616709640352317
+		'10': 0.3675478279476653
+		'11': 0.6096459166222741
+  - name: u
+	histogram:
+		'00': 56
+		'01': 42
+		'10': 2
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.052200000000000024
+		prob_meas1_prep0: 0.0172
+	  ancilla:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	mitigated_histogram:
+		'00': 0.55731929321128
+		'01': 0.43367489257574243
+		'10': 0.009005814212977551
+- target: 0
+  ancilla: 1
+  phi: 6.283185307179586
+  results_per_circuit:
+  - name: id
+	histogram:
+		'00': 18
+		'01': 28
+		'10': 30
+		'11': 24
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.052200000000000024
+		prob_meas1_prep0: 0.0172
+	  ancilla:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	mitigated_histogram:
+		'00': 0.15258295844557557
+		'01': 0.2829079190522524
+		'10': 0.3071204587046501
+		'11': 0.25738866379752195
+  - name: u
+	histogram:
+		'00': 32
+		'01': 28
+		'10': 23
+		'11': 17
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.052200000000000024
+		prob_meas1_prep0: 0.0172
+	  ancilla:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	mitigated_histogram:
+		'00': 0.3026150836796529
+		'01': 0.28491749668524724
+		'10': 0.23230862145681827
+		'11': 0.18015879817828173
+- target: 1
+  ancilla: 2
+  phi: 0.0
+  results_per_circuit:
+  - name: id
+	histogram:
+		'00': 27
+		'01': 16
+		'10': 30
+		'11': 27
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	  ancilla:
+		prob_meas0_prep1: 0.07540000000000002
+		prob_meas1_prep0: 0.0528
+	mitigated_histogram:
+		'00': 0.256742095057232
+		'01': 0.15000257115061383
+		'10': 0.29821012040758116
+		'11': 0.29504521338457296
+  - name: u
+	histogram:
+		'00': 34
+		'01': 22
+		'10': 25
+		'11': 19
+	mitigation_info:
+	 target:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	  ancilla:
+		prob_meas0_prep1: 0.07540000000000002
+		prob_meas1_prep0: 0.0528
+	mitigated_histogram:
+		'00': 0.3325088211394024
+		'01': 0.22335261496979697
+		'10': 0.2441636375921354
+		'11': 0.19997492629866526
+- target: 1
+  ancilla: 2
+  phi: 3.141592653589793
+  results_per_circuit:
+  - name: id
+	histogram:
+		'00': 3
+		'01': 9
+		'10': 51
+		'11': 37
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	  ancilla:
+		prob_meas0_prep1: 0.07540000000000002
+		prob_meas1_prep0: 0.0528
+	mitigated_histogram:
+		'00': -0.016627023111853642
+		'01': 0.06778554570877951
+		'10': 0.53899887367658
+		'11': 0.40984260372649417
+  - name: u
+	histogram:
+		'00': 43
+		'01': 45
+		'10': 7
+		'11': 5
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	  ancilla:
+		prob_meas0_prep1: 0.07540000000000002
+		prob_meas1_prep0: 0.0528
+	mitigated_histogram:
+		'00': 0.42955729968594086
+		'01': 0.49336080079582095
+		'10': 0.04937406434533623
+		'11': 0.02770783517290191
+- target: 1
+  ancilla: 2
+  phi: 6.283185307179586
+  results_per_circuit:
+  - name: id
+	histogram:
+		'00': 22
+		'01': 19
+		'10': 35
+		'11': 24
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	  ancilla:
+		prob_meas0_prep1: 0.07540000000000002
+		prob_meas1_prep0: 0.0528
+	mitigated_histogram:
+		'00': 0.19592641048040849
+		'01': 0.18787721420415215
+		'10': 0.3590258049844047
+		'11': 0.25717057033103463
+  - name: u
+		histogram:
+		'00': 27
+		'01': 24
+		'10': 25
+		'11': 24
+	mitigation_info:
+	  target:
+		prob_meas0_prep1: 0.05900000000000005
+		prob_meas1_prep0: 0.0202
+	  ancilla:
+		prob_meas0_prep1: 0.07540000000000002
+		prob_meas1_prep0: 0.0528
+	mitigated_histogram:
+		'00': 0.25555866817587225
+		'01': 0.2429501641251142
+		'10': 0.24509293912212946
+		'11': 0.2563982285768841
+\end{lstlisting}
 

### 2023-02-20 txt/manuscript.tex
Update manuscript

@@
 \newtheorem{remark}{Remark}
+\newtheorem{lemma}{Lemma}
+\theoremstyle{definition}
 \newtheorem{scheme}{Scheme}
-\newtheorem{lemma}{Lemma}
 
@@
 \section{Preliminaries and discrimination scheme approach}
-This section is divided into two parts.
-In Section~\ref{sec:maths}, we introduce the necessary notation and preliminaries needed to understand the concept of PyQBench. Next, in Section~\ref{sec:discrimination-scheme},
-we will present a general overview of the discrimination scheme in theoretical terms. We will also mention NISQ devices' limitations and possible practical solutions during implementation process.
+
+In this section we describe how the benchmarking process in PyQBench works. To do so, we first
+discuss necessary mathematical preliminatries. Then, we present the general form of the
+discrimination scheme used in PyQBench and practical considerations on how to implement it taking
+into account limitations of the current NISQ devices.
 
 \subsection{Mathematical preliminaries}\label{sec:maths}
-A general quantum
-measurement, that is a positive operator valued measure (POVM) $\PP$ is a
-collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
-\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$.
-In PyQBench, we are interested only in von Neumann measurements, i.e. measurements
-for which all the effects are rank-one projectors. Every such measurement can be
-parameterized by a unitary matrix $U$ which effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
-are created by taking $\ket{u_i}$ as  $(i+1)$-th column of the unitary matrix $U$.
-We will denote von Neumann measurements described by the matrix $U$ by $\PP_{U}$.
-
-Typically, NISQ devices can only perform measurements in computational $Z$-basis.
-To perform an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$
-to the measured system and then follow with $Z$-basis measurement. Hence, the following two
-circuits are equivalent.
+
+Let us first recall the definition of a von Neumann measurement, which is the only type of
+measurement used in PyQBench. A von Neumann measurement $\PP$ is a collection of rank--one projectors
+$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to identity, 
+i.e. $ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$,
+one can construct a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this
+case we say that $\PP_{U}$ is described by the matrix $U$.
+
+Typically, NISQ devices can only perform measurements in computational $Z$-basis, i.e. $U=\1$.
+To implement an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$
+to the measured system and then follow with $Z$-basis measurement. This process, depicted in Fig.
+\ref{fig:vonneumann}, can be viewed as performing a change of basis in which measurement is
+performed prior to measurement in the computational basis.
 
@@
 	\includegraphics[scale=1.7]{pics/vonneuman}
-	\caption{Decomposition of a von Neumann measurement $\PP_{U}$. }
-	\label{fig:vonnneuman}
+	\caption{Implementation of a von Neumann measurement using measurement in computational basis.
+	The upper circuit shows a symbolic representation of von Neumann measurement $\PP_{U}$. The
+	bottom, equivalent circuit depicts its decomposition into a change of basis followed
+	by measurement in the $Z$ basis.}
+	\label{fig:vonneumann}
 \end{figure}
 
-Note that the decomposition above is basically a change of basis in which the measurement
-is performed.
-
 \subsection{Discrimination scheme}\label{sec:discrimination-scheme}
 
-Without loss of generality, we consider discrimination task between a measurement in the computational
-Z-basis ($\PP_\Id$), and an alternative measurement performed in the basis $U$
-($\PP_U$)\footnote{Explaining why we can consider only Z-basis and alternative measurement $\PP_{U}$ is beyond
-	the scope of this technical documentation. See \cite{puchala2018strategies} if you are interested in
-	the explanation.}. In PyQBench, we operate only on two-level systems, but the discrimination scheme,
-described in detail in \cite{puchala2018strategies}, makes no assumptions about the dimensionality.
+Benchmarks in PyQBench work by experimentally determining the probability of correct discrimination
+between two von Neumann measurements by the device under test and comparing the result with the
+ideal, theoretical predictions.
+
+Without loss of generality\footnote{Explaining why we can consider only Z-basis and alternative
+measurement $\PP_{U}$ is beyond the scope of this paper. See \cite{puchala2018strategies} if you are
+interested in the explanation.}, we consider discrimination task between single qubit measurements
+$\PP_\Id$, performed in the computational Z-basis, and an alternative measurement $\PP_U$ performed
+in the basis $U$. Note, however, that the discrimination scheme described below can work
+regardless of dimensionality of the system, see \cite{puchala2018strategies} for details.
 
 In general, the discrimination scheme, presented in Fig.~\ref{fig:theoretical_scheme}, requires an
-auxiliary system of the same dimensionality as the measured one. First, the joint system is prepared in
-some state $\ket{\psi_0}$. Then, the unknown measurement is performed on the first part of the
-system. Based on its outcome $i$, the final measurement $\mathcal{P}_{V_i}$ is performed to obtain an
-outcome $j$. Finally, if $j=0$ we guess that the performed measurement is $\mathcal{P}_U$, otherwise we guess that it was $\mathcal{P}_\Id$.
+auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of
+measurements, $\PP_\1$ or $\PP_U$, is performed on the first part of the system. Based on its
+outcome $i$, one chooses another measurement $\mathcal{P}_{V_i}$ and performs it on the second
+qubit, storing the output in $j$. Finally, if $j=0$, we guess that the performed measurement is
+$\mathcal{P}_U$, otherwise we guess that it was $\mathcal{P}_\Id$. Naturally, one have to repeat the
+same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
+probability distribution. In PyQBench, we assume that experiment is repeated the same number of
+times for both $\PP_U$ and $\PP_\Id$.
+
+Unsurprisingly, both the
+$\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be chosen specifically for
+given $U$ to maximize the probability of a correct guess. We will describe in detail how these
+choices are made in \todo{add reference to section that describes that}, and for now we will focus
+only how this scheme can be implemented on the actual devices, assuming that all the components are known.
 
@@
 
-\subsubsection{Limitations of NISQ devices and practical discrimination schemes}
+\subsubsection{Implementation of discrimination scheme on actual NISQ devices}
 
 Current NISQ devices are unable to perform conditional measurements, which is the biggest
-obstacle to implementing our scheme on real hardware. However, we can adjusting our scheme so that it only uses components available on current devices.
-For this purpose, we use two possible options: using a postselection or a direct sum
-$V_0^\dagger\oplus V_1^\dagger$.
-
-\begin{scheme}(By using postselection)
-
-	The first idea uses a postselection scheme. Instead of performing a conditional measurement $\PP_{V_k}$, for each
-	measurement $\PP_U, \PP_\Id$ to be discriminated and each choice of $k \in \{0, 1\}$ we run circuits presented in Fig. \ref{fig:postselection}.
+obstacle to implementing our scheme on real hardware. However, we circumvent this problem by
+slightly adjusting our scheme so that it only uses components available on current devices.
+For this purpose, we use two possible options: using a postselection or a direct sum $V_0^\dagger\oplus V_1^\dagger$.
+
+\begin{scheme}(Postselection)
+
+	The first idea uses a postselection scheme. In the original scheme, we measure the first qubit
+	and only then determine which measurement should be performed on the second one. Instead of 
+	doing this choice, we can run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and
+	measure both qubits. We then discard the results of the circuit for which label $i$ does match
+	measurement label $k$. Hence, the circuit for postselection looks as depicted in Fig.
+	\ref{fig:postselection}.
 
@@
 			measurements $\PP_{U}$ and $\PP_{\Id}$ using postselection approach.
+			In postselection scheme, one runs such circuits for both $k=0,1$ and discards results for cases when there is a mismatch between $k$ and $i$.
 		}\label{fig:postselection}
@@
 
-The experiments can be grouped into classes identified by tuples of the form
-	$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen measurement, $k \in \{0,1\}$, $i \in \{0,1\}$ and $j \in \{0,1\}$.
-	In postselection approach, we discard all the experiments for which $k \ne i$. Hence, the total number of valid experiments is
+	To perform the benchmark, one needs to run multiple copies of the postselection circuit,
+	with both $\PP_U$ and $\PP_\1$. Each circuit has to be run in both variants, one with final
+	measurement $\PP_{V_0}$ and the second with final measurement $\PP_{V_1}$.
+	The experiments can thus be grouped into classes identified by tuples of the form
+	$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen
+	measurement, $k \in \{0,1\}$ designates the final measurement used, and $i \in \{0,1\}$ and $j
+	\in \{0,1\}$ being the labels of outcomes as presented in Fig. \ref{fig:postselection}.
+	We then discard all the experiments for which $i \ne k$. The total number of valid experiments
+	is thus:
 
@@
 	\end{equation}
-
+	The $p_{\text{succ}}$ is the quantity reported to the user as the result of the benchmark.
 \end{scheme}
 
-\begin{scheme}(By using direct sum)
+\begin{scheme}(Direct sum)
 
 The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation.     Here, instead of performing a conditional
-measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits presented in	Fig.~\ref{fig:controlled}.
+measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits presented in
+Fig.~\ref{fig:controlled}.
 
@@
 		\caption{ A schematic representation of the setup for distinguishing
-			measurements $\PP_{U}$ and $\PP_{\Id}$ using direct sum.
+			measurements $\PP_{U}$ and $\PP_{\Id}$ using the $V_0^\dagger \oplus V_1^\dagger$ direct sum.
 		}\label{fig:controlled}
@@
 
-	In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where $\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$.
-The number of successful trials for $U$ and $\Id$, respectively, can be written  as
+	One can see why such a circuit is equivalent to the original discrimination scheme.
+	If we rewrite the $V_0^\dagger \oplus V_1^\dagger$ as follows:	
+	\begin{equation}
+		\label{eq:directsum}
+		V_0^\dagger \oplus V_1^\dagger = \proj{0}\otimes V_0^\dagger + \proj{1} \otimes V_1^\dagger
+	\end{equation}
+	We can see that the direct sum in \eqref{eq:directsum} commutes with the measurement on the
+	first qubit. Thanks to this, we can switch the order of operations to obtain the circuit from
+	Fig. \ref{fig:directsum}. Now, depending on the outcome $i$, one of the summands in
+	\eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in the
+	original scheme.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=\textwidth]{pics/direct_sum}
+		\caption{Rewritten representation of the setup for distinguishing
+		measurements $\PP_{U}$ and $\PP_{\Id}$ using the $V_0^\dagger \oplus V_1^\dagger$ direct
+		sum.
+		}\label{fig:directsum}
+	\end{figure}
+
+	In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where
+	$\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$ and $i,j \in \{0,1\}$ are the output labels. The number of successful trials for $U$ and $\Id$,
+	respectively, can be written  as
 	\begin{eqnarray}
@@
 
-\subsubsection{Optimal discrimination scheme}
+\subsubsection{Constructing optimal discrimination scheme}
+
+In principle, the schemes described in the previous section could be used with any choice of
+$\ket{\psi_0}$ and final measurements $\PP_{V_i}$. However, we argue that it is best to choose those
+components in such a way that they maximize the probability of correct discrimination. To see that,
+suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ yields the theoretical upper bound
+of discriminating between two measurements of 1, i.e. on a perfect quantum computer you will always
+make a correct guess. Then, on real hardware, we might obtain any empirical value in range $[0.5,
+1]$. On the other hand, if we choose the components of our scheme such that the successful
+discrimination probability is only 0.6, the possible range of empirically obtainable probabilities
+is only $[0.5, 0.6]$. Hence, in the second case, the discrepancy between theoretical and empirical
+results will be less pronounced.
 
@@
 \end{equation}
-The quantum state $\ket{\psi}$ which maximizes the diamond norm is called as discriminator.
-Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is possible to construct the necessary components  ($\ket{\psi_0}$, $V_0$, $V_1$) to create the optimal discrimination strategy.
+The quantum state $\ket{\psi_0}$ which maximizes the diamond norm is called the
+\emph{discriminator}. Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is
+possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
+discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
+interested reader to the \todo[inline]{refer to the correct section in appendix}
 
 \section{Discrimination scheme for parameterized Fourier family and implementation}
-
-So far, we only discussed how the discrimination is performed using two different
-schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known.
-It turned out that the determination of $V_0$ and $V_1$ is a simple task while the discriminator $\ket{\psi_{0}}$ is known.
-However,
-determining the analytical form of the discriminator $\ket{\psi_{0}}$
-is, in general, NP-hard problem.
-We have found the analytical solution of the discrimination scheme for a particular class of von Neumann measurements.
-
-Here,  we will show how all the necessary ingredients look like for
-von Neumann measurements defined by the parameterized Fourier family:
-
-\begin{equation}
-U = H
-\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger,
-\end{equation}
-where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this case, the optimal input state is the Bell state of the form
+\label{sec:fourier}
+So far, we only discussed how the discrimination is performed assuming that all needed components
+($\ket{\psi_0}$, $V_0$, $V_1$) are known. In this section, we provide a concrete example using
+parametrized Fourier family of measurements.
+
+The parametrized Fourier family of measurements is defined as a set of the measurements
+$\{\PP_{U_\phi}\colon \phi \in [0, 2\pi]\}$, where $U_\phi$ is defined as follows:
+\begin{equation}
+U_\phi = H
+\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger.
+\end{equation}
+and $H$ is the Hadamard matrix. For each element of this family, the discriminator is a Bell state:
 \begin{equation}
@@
 \end{equation}
-Observe that the discriminator does not depend on the angle $\phi$. 
-Nevertheless, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
-have the following form
+Observe that $\ket{\psi_0}$ does not depend on the angle $\phi$. However, the unitaries $V_0$,
+$V_1$ depend on $\phi$ and take the following form:
 \begin{equation}
@@
 \end{equation}
-Finally, we have also calculated the theoretical probability of correct discrimination between von Neumann
-measurements $\PP_U$ and $\PP_{\Id}$ is given by
-\begin{equation}
-p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
-\end{equation}
-More details and proofs of the construction's validity   we can find in the \ref{app:optimal-probability} and \ref{app:optimal-strategy}.
+Finally, the theoretical probability of correct discrimination between von Neumann
+measurements $\PP_{U_\phi}$ and $\PP_{\Id}$ is given by
+\begin{equation}
+p_{\text{succ}}(\PP_{U_\phi}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
+\end{equation}
+We explore the construction of $\ket{\phi_0}$, $V_0$ and $V_1$ for parametrized Fourier family in
+\ref{app:optimal-probability} and \ref{app:optimal-strategy}.
 
@@
  This section is divided into two parts.
- In Section~\ref{sec:sortware-functionalities} we present the details of PyQBench functionality. Next, in Section~\ref{sec:sortware-architecture},
- we will give a general overview of the software architecture.
+ In Section~\ref{sec:sortware-functionalities} we describe functionalities of PyQBench
+ package.Next, in Section~\ref{sec:sortware-architecture}, we give a general overview of the
+ software architecture.
 
@@
 
-In the scope of this Paper, we aim at  exploring ideas revolving around quantum
-gate model-inspired computing devices, and assess their feasibility to
-benchmark a modern quantum architectures. The main idea that we have envisioned
-for this project is  introducing new concepts of benchmarks for NISQ devices
-benchmarking. This project aims to characterize the computing power and
-investigate possible practical applications of such devices having access by
-Amazon Braket.
+The PyQBench can be used in two modes: as a Python library and as a CLI script. When used as a
+library, PyQBench allows using user--defined discrimination schemes. The user is supposed to provide
+a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\phi_0}$,
+and unitaries $V_0$ and $V_1$ describing the final measurement. The PyQBench library provides then
+the following functionalities.
+
+\begin{enumerate}
+	\item Assembling circuits for both postselection and direct sum--based discrimination schemes.
+	\item Executing the whole benchmarking scenario on specified hardware.
+	\item Interpreting the obtained measurements in terms of discrimination probabilities.
+\end{enumerate}
+Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt-in for
+fine--grained control over the execution of the circuits, For instance, suppose the user wants to
+simulate the discrimination experiment on a noisy simulator. In such a case, he or she can define
+the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
+e.g. to add noise to particular gates, and then run using any Qiskit backend. Finally, the user can
+use PyQBench to interpret the measurements to obtain discrimination probability.
+
+The PyQBench library also contains a readily available implementation of all necessary components
+needed to run discrimination experiments for parametrized Fourier family of measurements defined in
+section \ref{sec:fourier}. However, if one only wishes to use this particular family in benchmarks, then using
+PyQBench as a CLI tool might be a simpler choice. When operating as CLI, PyQBench can currently only
+run experiments that use parametrized Fourier family, but the whole process is greatly simplified.
+Essentially, the CLI tool can be used in two types of workflows:
+
+\begin{itemize}
+	\item \emph{synchronous}: in this scenario PyQBench submits circuits to the given device and
+	waits for the results.
+	\item \emph{asynchronous}: PyQBench submits circuits to the device and then produces
+	an intermediate file containing, among others, metadata allowing for querying results later on.
+\end{itemize}
+
+The execution of the experiment is driven by configuration files written in YAML \cite{}. Examples
+of such files can be found in \ref{sec:examples}, and their detailed description can be found at
+PyQBench's documentation website \cite{}.
 
 \subsection{Software Architecture}\label{sec:sortware-architecture}
-PyQBench can be used in two different ways:
+
+\subsubsection{Overview of the software structure}
+As already described, PyQBench can be used both as a library and a CLI. Both functionalities are
+implemented as a part of \texttt{qbench} Python package. The exposed CLI tool is also named
+\texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead
+refer an interested reader to the source code available at GitHub \cite{} or at the reference manual
+\cite{}.
+
+\subsubsection{Integration with devices and hardware providers}
+
+PyQBench is built around the Qiskit\cite{qiskit} ecosystem. Hence, both the CLI tool and the
+\texttt{qbench} library can use any Qiskit--compatible backend. This includes, in particular, IBM Q
+backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
+through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider}).
+
+When using PyQBench as library, instances of Qiskit backends can be passed to functions that expect
+them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
+backend. An xample of such file can be found in \ref{sec:examples}, and the detailed description of
+the expected format can be found at PyQBench's documentation.
+
+\subsubsection{Command Line Interface}
+\label{sec:cli}
+
+The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
+invocation is shown in listing \ref{lst:cli}.
+\begin{lstlisting}[caption=Invocation of \texttt{qbench} script, label=lst:cli]
+qbench <benchmark-type> <command> <parameters>
+\end{lstlisting}
+Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
+Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
+fashion will allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
+is \texttt{disc-fourier}.
+
+The \texttt{qbench disc-fourier} command has four subcommands:
+
 \begin{itemize}
-\item As a library. This way allows for more advanced scripting defining your own measurements scheme.
-
-\item As a CLI tool. This mode of operation trades extensibility for simplicity of usage, as it allows only for running Fourier-discrimination experiments defined with  YAML input files.
+	\item \texttt{benchmark}: run benchmarks. This creates either a result YAML file containing
+	the measurements or an intermediate YAML file for asynchronous experiments.
+	\item \texttt{status}: query status of experiments submitted for given benchmark. This command
+	is only valid for asynchronous experiments.
+	\item \texttt{resolve}: query the results of asynchronously submitted experiments and write the
+	result YAML file. The output of this command is almost identical to the result obtained from
+	synchronous experiments.
+	\item \texttt{tabulate}: interpret the results of a benchamrk and summarize them in the CSV file.
 \end{itemize}
 
-\section{PyQBench as a library}\label{sec:pyqbench-as-library}
-This guide introduces basic concepts needed for using PyQBench as a library from a Python script. In particular, we will consider the following topics:
-\begin{enumerate}
-\item Defining experiment using circuit components.
-\item Assembling circuits needed for given benchmarking scheme.
-\item Running experiment on a simulator or a hardware.
-\item Obtaining empirical probability of successful discrimination between measurements.
-\end{enumerate}
-
-On the conceptual level, every discrimination experiment performed in PyQBench needs the following:
-\begin{enumerate}
-\item Discriminator, i.e. optimal initial state for the circuit.
-\item Unitary $U^\dagger$ defining alternative measurement to be discriminated from the measurement in Z-basis.
-\item $V_0^\dagger$ and $V_1^\dagger$, positive and negative parts of optimal measurement from Holevo-Helstrom theorem.
-\end{enumerate}
-
-\subsubsection{Example of usage}
-In  this example, we will use $U =  H$ (the Hadamard gate).
-The explicit formula for discriminator in this model reads
+\subsubsection{Asynchronous vs. synchronous execution}
+As stated in previous sections, PyQBench CLI can be used in synchronous and asynchronous modes. The
+mode of execution is defined in the YAML file describing the backend (see \ref{sec:examples}). We
+decided to couple the mode of execution to the backend description because some backends cannot work
+in asynchronous mode.
+
+When running \texttt{qbench disc-fourier benchmark}, an intermediate file containing metadata of
+submitted experiments is created. This metadata contains, in particular, identifiers of the
+submitted jobs. The intermediate file can be used to query the status of the submitted jobs or to
+resolve them, i.e. to wait for their completion and get the measurement outcomes.
+
+In synchronous mode, PyQBench first submits all jobs required to run the benchmark, and then
+immediately waits for their completion. The advantage of this approach is that no separate
+invocation of \texttt{qbench} command is needed to actually download the measurement outcomes. The
+downside, however, is that if the script is interrupted while the command is running, the
+intermediate results will be lost. This might result, in particular, in financial loss if the
+backend used is available as a paid service. Therefore, we recommend using asynchronous mode
+whenever possible.
+
+\section{Illustrative examples}
+
+In this section, we present two examples demonstrating the usage of PyQBench. In the first example,
+we show how to implement a benchmarking scheme for a user--defined measurement and possible ways of
+using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
+CLI. We show how to prepare the input files for the experiment and how to run it using the
+\texttt{qbench} tool.
+
+\subsection{Using user-defined measurement with \texttt{qbench} library}
+
+\subsection{Using \texttt{qbench} CLI}
+
+In this example, we will use $U = H$ (the Hadamard gate). Since our aim in this section is to
+demonstrate the use of PyQBench as a library, we leave out the mathematical details, which can be
+found in \ref{app:hadamard}. The explicit formula for discriminator in this example reads:
 \begin{equation}
@@
 \end{equation}
-with corresponding parts of optimal measurement being equal to
+with final measurements being equal to
 \begin{equation}
@@
 where \begin{equation}
-\alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} \cos\left( \frac{3}{8} \pi \right),
-\end{equation}
-\begin{equation}
-\beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} \sin\left( \frac{3}{8} \pi \right).
-\end{equation}
-As a next step, we need decompose our matrices into actual sequences of gates.
+\alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} = \cos\left( \frac{3}{8} \pi \right),
+\end{equation}
+\begin{equation}
+\beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} = \sin\left( \frac{3}{8} \pi \right).
+\end{equation}
+To use the above benchmarking scheme in PyQBench, we first need to decompose the unitary matrices
+above into sequences of gates.
 The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
@@
 \end{figure}
-For $V_0$ and $V_1$ observe that $V_0 = RY\left(\frac{3}{4} \pi \right) $, where $RY$ is rotation gate around the $Y$ axis defined by
-\begin{equation}
-RY(\theta) =
+For $V_0$ and $V_1$ observe that $V_0 = \operatorname{RY}\left(\frac{3}{4} \pi \right) $, where $\operatorname{RY}$ is rotation gate around the $Y$ axis defined by
+\begin{equation}
+\operatorname{RY}(\theta) =
 \left(\begin{array}{cc} \cos\frac{\theta}{2} & -\sin\frac{\theta}{2} \\ \sin\frac{\theta}{2} & \cos\frac{\theta}{2} \end{array}\right).
 \end{equation}
-To obtain $V_1$  we need only to swap the columns, which is equivalent to 
-\begin{equation}
-V_1 =  RY\left(\frac{3}{4} \pi \right) \cdot X.
-\end{equation}
-Finally, calculate the optimal probability of correct discrimination which is equal to
+To obtain $V_1$  we need only to swap the columns, i.e.
+\begin{equation}
+V_1 = \operatorname{RY}\left(\frac{3}{4} \pi \right) \cdot \operatorname{X}.
+\end{equation}
+Finally, the optimal probability of correct discrimination is equal to
 \begin{equation}
@@
 \end{equation}
-The detailed calculation we can see in \ref{app:hadamard}. 
-Now we simulate the  theoretical framework using PyQBench. We will start with simulation in Qiskit SDK with Aer simulator. First, we import necessary modules and needed functions from PyQBench.
-
-\begin{lstlisting}[language=Python]
+We will now demonstrate how to implement this theoretical scheme in PyQBench. For this example we
+will use the Qiskit Aer simulator \cite{}. First, we import the necessary functions and classes from
+PyQBench and Qiskit. We also import \texttt{numpy} for the definition of \texttt{np.pi} constant and
+the exponential function. The exact purpose of the imported functions will be described at the point
+of their usage.
+\begin{lstlisting}[language=Python, caption=Imports needed for running benchmarking example]
 import numpy as np
@@
 \end{lstlisting}
-To run a function from PyQBench, we need to define Qiskit instructions.  We can do so by constructing circuit acting on qubits 0 and 1 and then converting them using \textit{to\_instruction()} method.
+To implement the discrimination scheme in PyQBench, we need to define all the necessary components
+as Qiskit instructions. We can do so by constructing a circuit object acting on qubits 0 and 1 and
+then converting them using \texttt{to\_instruction()} method.
 \begin{lstlisting}[language=Python, caption= Defining components for Hadamard experiment]
@@
 	return circuit.to_instruction()
-
-\end{lstlisting}
-For the purpose of this example,  we run experiments on Qiskit Aer simulator.
-\begin{lstlisting}[language=Python, caption= Defining a backend]
+\end{lstlisting}
+We now construct a backend object, which in this case is an instance of Aer simulator.
+
+\begin{lstlisting}[language=Python, caption=Defining a backend]
 simulator = Aer.get_backend("aer_simulator")
-
-\end{lstlisting}
-Now running the simulation is as simple as invoking functions imported from PyQBench package.
+\end{lstlisting}
+
+In the simplest scenario, when one does not want to tweak execution details and simply wishes to run
+the experiment on a given backend, everything that is required is now to run
+\texttt{benchmark\_using\_postselection} function.
+
 \begin{lstlisting}[language=Python, caption=Simulation benchmark by using postselection]
@@
 \appendix
+
+Let us first recall the general form of a quantum measurement, so called Positive Operator Valued
+Measure (POVM). A POVM $\PP$ is a collection of positive semidefinite operators $\{E_1, \ldots, E_m
+\}$, called effects, that sum up to the identity operator, \ie $ \, \, \sum_{i=1}^m E_i = \1$.
+In PyQBench, we are interested only in von Neumann measurements, that is measurements
+for which all the effects are rank-one projectors. Every such measurement can be
+parameterized by a unitary matrix $U$ with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+are created by taking $\ket{u_i}$ as  $(i+1)$-th column of the unitary matrix $U$.
+We will denote von Neumann measurements described by the matrix $U$ by $\PP_{U}$.
+
 \section{Mathematical preliminaries} \label{app:preliminaries}

### 2023-02-21 txt/manuscript.tex
Update first example

@@
 The PyQBench can be used in two modes: as a Python library and as a CLI script. When used as a
-library, PyQBench allows using user--defined discrimination schemes. The user is supposed to provide
+library, PyQBench allows customization of discrimination scheme. The user provides
 a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\phi_0}$,
@@
 	\item Assembling circuits for both postselection and direct sum--based discrimination schemes.
-	\item Executing the whole benchmarking scenario on specified hardware.
-	\item Interpreting the obtained measurements in terms of discrimination probabilities.
+	\item Executing the whole benchmarking scenario on specified backend (either real hardware or
+	software simulator).
+	\item Interpreting the obtained outputs in terms of discrimination probabilities.
 \end{enumerate}
@@
 the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
-e.g. to add noise to particular gates, and then run using any Qiskit backend. Finally, the user can
-use PyQBench to interpret the measurements to obtain discrimination probability.
+e.g. to add noise to particular gates, and then run using any Qiskit backend by the user. Finally,
+PyQBench can be used to interpret the measurements to obtain discrimination probability.
 
 The PyQBench library also contains a readily available implementation of all necessary components
-needed to run discrimination experiments for parametrized Fourier family of measurements defined in
-section \ref{sec:fourier}. However, if one only wishes to use this particular family in benchmarks, then using
-PyQBench as a CLI tool might be a simpler choice. When operating as CLI, PyQBench can currently only
-run experiments that use parametrized Fourier family, but the whole process is greatly simplified.
-Essentially, the CLI tool can be used in two types of workflows:
-
-\begin{itemize}
-	\item \emph{synchronous}: in this scenario PyQBench submits circuits to the given device and
-	waits for the results.
-	\item \emph{asynchronous}: PyQBench submits circuits to the device and then produces
-	an intermediate file containing, among others, metadata allowing for querying results later on.
-\end{itemize}
-
-The execution of the experiment is driven by configuration files written in YAML \cite{}. Examples
-of such files can be found in \ref{sec:examples}, and their detailed description can be found at
-PyQBench's documentation website \cite{}.
+needed to run discrimination experiments for parametrized Fourier family of measurements, defined
+previously in section \ref{sec:fourier}. However, if one only wishes to use this particular family
+of measurements in their benchmarks, then using PyQBench as a command line tool might be a simpler
+choice. PyQBench's command line interface allows for running the whole benchmarking process without
+writing Python code. The configuration of CLI is done by YAML \cite{} files describing the benchmark
+to be performed and the description of backend on which the benchmark should be run. Importantly,
+the YAML configuration files are reusable. The same benchmark can be used with different backends
+and vice versa.
+
+The next section describes important architectural decisions taken when creating PyQBench, and
+how they affect the end user experience.
 
@@
 
-\subsubsection{Integration with devices and hardware providers}
+PyQBench can be installed from official Python Package Index (PyPI) by running \texttt{pip install
+pyqbench}. In a properly configured Python environment the installation process should also make the
+\texttt{qbench} command available to the user without a need for further configuration.
+
+\subsubsection{Integration with hardware providers and software simulators}
 
 PyQBench is built around the Qiskit\cite{qiskit} ecosystem. Hence, both the CLI tool and the
-\texttt{qbench} library can use any Qiskit--compatible backend. This includes, in particular, IBM Q
+\texttt{qbench} library can use any Qiskit--compatible backend. This includes, IBM Q
 backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
@@
 them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
-backend. An xample of such file can be found in \ref{sec:examples}, and the detailed description of
+backend. An example of such file can be found in \ref{sec:examples}, and the detailed description of
 the expected format can be found at PyQBench's documentation.
@@
 Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
-fashion will allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
+fashion to allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
 is \texttt{disc-fourier}.
-
+%
 The \texttt{qbench disc-fourier} command has four subcommands:
@@
 \end{itemize}
+%
+We present usage of each of the above commands later in section \ref{sec:examples}.
 
 \subsubsection{Asynchronous vs. synchronous execution}
-As stated in previous sections, PyQBench CLI can be used in synchronous and asynchronous modes. The
-mode of execution is defined in the YAML file describing the backend (see \ref{sec:examples}). We
-decided to couple the mode of execution to the backend description because some backends cannot work
-in asynchronous mode.
-
-When running \texttt{qbench disc-fourier benchmark}, an intermediate file containing metadata of
-submitted experiments is created. This metadata contains, in particular, identifiers of the
-submitted jobs. The intermediate file can be used to query the status of the submitted jobs or to
-resolve them, i.e. to wait for their completion and get the measurement outcomes.
+PyQBench's CLI can be used in synchronous and asynchronous modes. The
+mode of execution is defined in the YAML file describing the backend (see section
+\ref{sec:examples} for example of this configuratoin). We decided to couple the mode of execution to
+the backend description because some backends cannot work in asynchronous mode.
+
+When running \texttt{qbench disc-fourier benchmark} in asynchronous mode, the PyQBench submits all
+the circuits needed to perform a benchmark and then wirte an intermediate YAML file
+containing metadata of submitted experiments. In particular, this metadata contains information on
+how to correlate submitted job identifiers with particular circuits. The intermediate file can be
+used to query the status of the submitted jobs or to resolve them, i.e. to wait for their completion
+and get the measurement outcomes.
 
@@
 downside, however, is that if the script is interrupted while the command is running, the
-intermediate results will be lost. This might result, in particular, in financial loss if the
-backend used is available as a paid service. Therefore, we recommend using asynchronous mode
+intermediate results will be lost. Therefore, we recommend using asynchronous mode
 whenever possible.
@@
 \section{Illustrative examples}
-
+\label{sec:examples}
 In this section, we present two examples demonstrating the usage of PyQBench. In the first example,
-we show how to implement a benchmarking scheme for a user--defined measurement and possible ways of
-using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
-CLI. We show how to prepare the input files for the experiment and how to run it using the
+we show how to implement a discrimination scheme for a user--defined measurement and possible ways
+of using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
+CLI. We show how to prepare the input files for the benchmark and how to run it using the
 \texttt{qbench} tool.
 
-\subsection{Using user-defined measurement with \texttt{qbench} library}
-
-\subsection{Using \texttt{qbench} CLI}
-
-In this example, we will use $U = H$ (the Hadamard gate). Since our aim in this section is to
-demonstrate the use of PyQBench as a library, we leave out the mathematical details, which can be
-found in \ref{app:hadamard}. The explicit formula for discriminator in this example reads:
+\subsection{Using user-defined measurement with \texttt{qbench} package}
+In this example, we will demonstrate how \texttt{qbench} package can be used with user--defined
+measurement. For this purpose, we will use $U = H$ (the Hadamard gate). The detailed calculations
+that lead to the particular form of the discriminator and final measurements can be found in
+\ref{app:hadamard}. 
+\noindent
+The explicit formula for discriminator in this example reads:
 \begin{equation}
@@
 the experiment on a given backend, everything that is required is now to run
-\texttt{benchmark\_using\_postselection} function.
+\texttt{benchmark\_using\_postselection} or \texttt{benchmark\_using\_direct\_sum} function,
+depending on the user preference.
 
@@
 \end{lstlisting}
-Finally, we calculate the empirical probability obtained from postselection and direct sum experiment and calculate the absolute error between analytical and empirical results. 
-\begin{lstlisting}[language=Python, caption=Computation of discrimination probability]
+The \texttt{postselection\_result} and  \texttt{direct\_sum\_result} variables contain now the
+empirical probabilities of correct discrimination. We can compare them to the theoretical value and
+compute the absolute error.
+
+\begin{lstlisting}[language=Python, caption=Examining the benchmark results]
 p_succ = (2 + np.sqrt(2)) / 4
@@
 print(f"Direct sum: p_succ = {direct_sum_result}, abs. error = {p_succ - direct_sum_result}")
-
 \end{lstlisting}
@@
 
-\subsubsection{Gaining more control over the benchmarking process}
-In the example presented above we used functions that automate the whole process - from the circuit assembly, through running the simulations to interpreting the results.
+In the example presented above we used functions that automate the whole process -- from the circuit assembly, through running the simulations to interpreting the results.
 But what if we want more control over some parts of this process?
-One possibility would be to add some additional parameters to \textit{benchmark\_using\_xyz} functions, but this approach is not scalable.
-Moreover, there is no way we can anticipate all the possible use cases.
- We decided on another approach.  PyQBench provides functions performing:
+One possibility would be to add some additional parameters to \texttt{benchmark\_using\_xyz}
+functions, but this approach is not scalable. Moreover, anticipating all possible uses cases
+isimpossible. Therefore, we decided on another approach. PyQBench provides functions performing:
 \begin{enumerate}
-\item assembly of circuits needed for experiment, provided the components discussed above
-\item interpretation of the obtained measurements
+\item Assembly of circuits needed for experiment, provided the components discussed above.
+\item Interpretation of the obtained measurements.
 \end{enumerate}
- The difference between the two approaches is illustrated on the diagrams below.
+ The difference between the two approaches is illustrated on the diagrams in Fig. \ref{fig:diagrams}.
 
@@
 	\centering
-	\begin{subfigure}[b]{\textwidth}
+	\begin{subfigure}[b]{0.9\textwidth}
 		\centering
@@
 	\vfill
-	\begin{subfigure}[b]{\textwidth}
+	\begin{subfigure}[b]{0.9\textwidth}
 		\centering
@@
 	\end{subfigure}
+	\caption{Differences between simplified (top) and user--controlled (bottom) execution of
+	benchmarks in PyQBench. Compared to simplified benchmarking, in user--controlled benchmarks the
+	user has direct access to the circuits being run, and hence can alter them (e.g. by adding
+	noise) and/or choose the parameters used for executing them on the backend.}
+	\label{fig:diagrams}
 \end{figure}
@@
 
-By choosing this approach we need to divide the experiment into two parts:
-assembling  circuits and running  circuits.
-
-Let us focus only on the postselection case, as the direct sum case is analogous. In addition, we need to import two more functions from PyQBench.
+For the rest of this example, Let us focus only on the postselection case, as the direct sum case is
+analogous. We continue by importing two more functions from PyQBench.
 \begin{lstlisting}[language=Python, caption= Assembling circuits]
@@
 \end{lstlisting}
-The function \textit{assemble\_postselection\_circuits} creates all of neceserry circuits as a dictionary.
-Each informs if the circuit implements $U^\dagger$ or $\Id$ on the target qubit, and which of $V_0$ and
-$V_1$ is used.
-
-Now we need to run the circuits. We will run a noisy and noiseless simulation of our circuits.
+Recall that for a postselection scheme we have two possible choices of the "unknown" measurement and
+two possible choices of a final measurement, which gives a total of four circuits needed to run the
+benchmark. The function \texttt{assemble\_postselection\_circuits} creates all four circuits and
+places them in a dictionary with keys \texttt{"id\_v0"}, \texttt{"id\_v1"}, \texttt{"u\_v0"},
+\texttt{"u\_v1"}.
+
+We will now run our circuits using noisy and noiseless simulation. We start by creating a noise
+model using Qiskit.
 
@@
 \end{lstlisting}
-Once we have our noise model ready, we can execute our circuits with and without noise.
-To this end, we will use Qiskit’s execute function.
-One caveat is that we have to keep track which measurements correspond to which circuit.
-We do so by fixing an ordering on the keys in \textit{circuits} dictionary.
+Once we have our noise model ready, we can execute the circuits with and without noise. To this end,
+we will use Qiskit’s \texttt{execute} function. One caveat is that we have to keep track which
+measurements correspond to which circuit. We do so by fixing an ordering on the keys in the \texttt{circuits} dictionary.
 \begin{lstlisting}[language=Python, caption=Running  circuits]
@@
 
-counts_noisy = (
-	execute(all_circuits, backend=simulator, noise_model=noise_model, shots=10000).result().get_counts()
-)
-
-counts_noiseless = execute(all_circuits, backend=simulator, shots=10000).result().get_counts()
-\end{lstlisting}
-Finally, we compute the success probabilities using  \textit{compute\_probabilities\_from\_\\postselection\_measurements} function.
+counts_noisy = execute(
+	all_circuits, 
+	backend=simulator, 
+	noise_model=noise_model, 
+	shots=10000
+).result().get_counts()
+
+counts_noiseless = execute(
+	all_circuits, 
+	backend=simulator, 
+	shots=10000
+).result().get_counts()
+\end{lstlisting}
+Finally, we use the measurement counts to compute discrimination probabilities using \texttt{compute\_probabilities\_from\_postselection\_measurements} function.
 
@@
 \end{lstlisting}
-The success probability is 0.8524401115559386. Whereas if we obtain a readout error, the success probability is equal to 0.5017958400693446. 
-As expected, noisy simulations gave us results that are further away from the exact ones.
-This concludes introduction to PyQBench library.
-
-\section{PyQBench as a CLI tool}\label{sec:pyqbench-as-cli}
+We can now examine the results. We expect that for noisy simulations, the result will be further
+away from the target value of \texttt{0.8535533905932737}. For example, in one of our runs we
+obtained \texttt{prob\_succ\_noiseless = 0.8524401115559386} and \texttt{prob\_succ\_noisy =
+0.5017958400693446}. 
+\noindent
+This concludes our example. In the next section, we will show how to use PyQBench's CLI.
+
+\subsection{Using \texttt{qbench} CLI} 
 Using PyQBench as a library allows one to conduct arbitrary two-qubit von Neumann measurement experiment. However, as discussed in the previous guide, it requires some amount of boilerplate code.

### 2023-02-25 txt/manuscript.tex
appendix chdoneeee

@@
 already exist several approaches. 
-One could mention randomized benchmarking  \cite{knill2008randomized}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume} or or cross-entropy benchmarking \cite{arute2019quantum, neill2018blueprint}.
+One could mention randomized benchmarking \cite{liu2022sampling, knill2007randomized, knill2008randomized, wallman2014randomized, helsen2022general,
+	cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume} or cross-entropy benchmarking \cite{arute2019quantum, neill2018blueprint}.
 
@@
 deviation between actual and expected outputs distribution provides then a metric of the performance
-of a given device. Libraries such as Munich Quantum Toolkit (MQT) Benchmark library contain
-benchmarks leveraging multiple algorithms, such as Shor's algorithm or Grover's algorithm, 
+of a given device.
+ Libraries such as Munich Quantum Toolkit (MQT) \cite{mqt2022, mqt-bench}
+or
+ SupermarQ \cite{supermarq, supermarkq-github} 
+  contain
+benchmarks leveraging multiple algorithms, such as Shor's algorithm or Grover's algorithm.
+% or  implementing e.g. GHZ state \cite{ghz}.  
 Despite being intuitive and easily interpretable, such benchmarks may have some problems. Most
@@
 and it might be hard to extrapolate their results to other algorithms and applications. For
-instance, the inability of a device to consistently find factorizations using Shor's algirithms
+instance, the inability of a device to consistently find factorizations using Shor's algorithms
 does not tell anything about its usefulness in Variational Quantum Algorithm's.
 
-Another possible approach to benchmarking quantum computers is randomized benchmarking
-\cite{liu2022sampling, knill2007randomized, wallman2014randomized, helsen2022general,
-	cornelissen2021scalable}. In this approach, one samples circuits to be run from some predefined set
+Another possible approach to benchmarking quantum computers is randomized benchmarking. In this approach, one samples circuits to be run from some predefined set
 of gates (e.g. from the Clifford group) and tests how much the output distribution obtained from the
@@
 chosen circuits with their inverses (which should yield the identity circuit) and run those
-concatenated circuits on the device. Libraries implementing this approach include Qiskit \cite{},
-\todo[inline]{enumerate other libraries and summary}
+concatenated circuits on the device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil \cite{forest-benchmarking}.
+
+\todo[inline]{cos tu dopisac o tych metodach}
+A further approach used to benchmark NISQ	 devices is  
+quantum volume \cite{volume-in-practice}
+or cross-entropy benchmarking \cite{cross-entropy-bench}
+\todo[inline]{summary}
 
@@
 In this section we describe how the benchmarking process in PyQBench works. To do so, we first
-discuss necessary mathematical preliminatries. Then, we present the general form of the
+discuss necessary mathematical preliminaries. Then, we present the general form of the
 discrimination scheme used in PyQBench and practical considerations on how to implement it taking
@@
 	\caption{Implementation of a von Neumann measurement using measurement in computational basis.
-	The upper circuit shows a symbolic representation of von Neumann measurement $\PP_{U}$. The
+	The upper circuit shows a symbolic representation of a von Neumann measurement $\PP_{U}$. The
 	bottom, equivalent circuit depicts its decomposition into a change of basis followed
@@
 
-Without loss of generality\footnote{Explaining why we can consider only Z-basis and alternative
-measurement $\PP_{U}$ is beyond the scope of this paper. See \cite{puchala2018strategies} if you are
+Without loss of generality\footnote{Explaining why we can consider only discrimination scheme between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper.
+See \cite{puchala2018strategies} if you are
 interested in the explanation.}, we consider discrimination task between single qubit measurements
@@
 auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of
-measurements, $\PP_\1$ or $\PP_U$, is performed on the first part of the system. Based on its
-outcome $i$, one chooses another measurement $\mathcal{P}_{V_i}$ and performs it on the second
+measurements,   $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
+outcome $i$, one chooses another POVM $\mathcal{P}_{V_i}$ and performs it on the second
 qubit, storing the output in $j$. Finally, if $j=0$, we guess that the performed measurement is
@@
 $\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be chosen specifically for
-given $U$ to maximize the probability of a correct guess. We will describe in detail how these
-choices are made in \todo{add reference to section that describes that}, and for now we will focus
+given $U$ to maximize the probability of a correct guess. The detailed description  how these
+choices are made in \cite{watrous}, and for now we will focus
 only how this scheme can be implemented on the actual devices, assuming that all the components are known.
@@
 	\end{equation}
-	We can see that the direct sum in \eqref{eq:directsum} commutes with the measurement on the
+	We can see that the direct sum in Eq. \eqref{eq:directsum} commutes with the measurement on the
 	first qubit. Thanks to this, we can switch the order of operations to obtain the circuit from
 	Fig. \ref{fig:directsum}. Now, depending on the outcome $i$, one of the summands in
-	\eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in the
+	Eq. \eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in the
 	original scheme.
@@
 discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
-interested reader to the \todo[inline]{refer to the correct section in appendix}
+interested reader to \cite{watrous}.
 
@@
 So far, we only discussed how the discrimination is performed assuming that all needed components
-($\ket{\psi_0}$, $V_0$, $V_1$) are known. In this section, we provide a concrete example using
+$\ket{\psi_0}$, $V_0$, and $V_1$ are known. In this section, we provide a concrete example using
 parametrized Fourier family of measurements.
@@
 U_\phi = H
-\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger.
-\end{equation}
-and $H$ is the Hadamard matrix. For each element of this family, the discriminator is a Bell state:
-\begin{equation}
-\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \ket{00} + \ket{11}.
+\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger, 
+\end{equation}
+and $H$ is the Hadamard matrix. For each element of this set, the discriminator is a Bell state:
+\begin{equation}
+\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \left( \ket{00} + \ket{11} \right).
 \end{equation}
@@
 \end{equation}
-We explore the construction of $\ket{\phi_0}$, $V_0$ and $V_1$ for parametrized Fourier family in
-\ref{app:optimal-probability} and \ref{app:optimal-strategy}.
+We explore the construction of $\ket{\psi_0}$, $V_0$ and $V_1$ for parametrized Fourier family of measurements in
+\ref{app:optimal-probability}.
 
@@
  In Section~\ref{sec:sortware-functionalities} we describe functionalities of PyQBench
- package.Next, in Section~\ref{sec:sortware-architecture}, we give a general overview of the
+ package. Next, in Section~\ref{sec:sortware-architecture}, we give a general overview of the
  software architecture.
@@
 The PyQBench can be used in two modes: as a Python library and as a CLI script. When used as a
-library, PyQBench allows customization of discrimination scheme. The user provides
-a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\phi_0}$,
+library, PyQBench allows the customization of discrimination scheme. The user provides
+a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\psi_0}$,
 and unitaries $V_0$ and $V_1$ describing the final measurement. The PyQBench library provides then
@@
 \end{enumerate}
-Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt-in for
-fine--grained control over the execution of the circuits, For instance, suppose the user wants to
+Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt in for
+fine-grained control over the execution of the circuits. For instance, suppose the user wants to
 simulate the discrimination experiment on a noisy simulator. In such a case, he or she can define
@@
 needed to run discrimination experiments for parametrized Fourier family of measurements, defined
-previously in section \ref{sec:fourier}. However, if one only wishes to use this particular family
-of measurements in their benchmarks, then using PyQBench as a command line tool might be a simpler
-choice. PyQBench's command line interface allows for running the whole benchmarking process without
-writing Python code. The configuration of CLI is done by YAML \cite{} files describing the benchmark
-to be performed and the description of backend on which the benchmark should be run. Importantly,
+previously in Section \ref{sec:fourier}. However, if one only wishes to use this particular family
+of measurements in their benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's command line interface allows running the benchmarking process without
+writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the benchmark
+to be performed and the description of the backend on which the benchmark should be run. Notably,
 the YAML configuration files are reusable. The same benchmark can be used with different backends
@@
 
-The next section describes important architectural decisions taken when creating PyQBench, and
-how they affect the end user experience.
+The following section describes important architectural decisions taken when creating PyQBench, and
+how they affect the end-user experience.
 
@@
 \texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead
-refer an interested reader to the source code available at GitHub \cite{} or at the reference manual
-\cite{}.
+refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the reference manual
+\cite{pyqbenchdocs}.
 
@@
 
-PyQBench is built around the Qiskit\cite{qiskit} ecosystem. Hence, both the CLI tool and the
+PyQBench is built around the Qiskit \cite{qiskit} ecosystem. Hence, both the CLI tool and the
 \texttt{qbench} library can use any Qiskit--compatible backend. This includes, IBM Q
 backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
-through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider}).
+through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider, qiskit-braket-provider-github}).
 
@@
 	synchronous experiments.
-	\item \texttt{tabulate}: interpret the results of a benchamrk and summarize them in the CSV file.
+	\item \texttt{tabulate}: interpret the results of a benchmark and summarize them in the CSV file.
 \end{itemize}
@@
 PyQBench's CLI can be used in synchronous and asynchronous modes. The
-mode of execution is defined in the YAML file describing the backend (see section
-\ref{sec:examples} for example of this configuratoin). We decided to couple the mode of execution to
+mode of execution is defined in the YAML file describing the backend (see Section
+\ref{sec:examples} for an example of this configuration). We decided to couple the mode of execution to
 the backend description because some backends cannot work in asynchronous mode.
@@
 When running \texttt{qbench disc-fourier benchmark} in asynchronous mode, the PyQBench submits all
-the circuits needed to perform a benchmark and then wirte an intermediate YAML file
+the circuits needed to perform a benchmark and then writes an intermediate YAML file
 containing metadata of submitted experiments. In particular, this metadata contains information on
-how to correlate submitted job identifiers with particular circuits. The intermediate file can be
+correlating submitted job identifiers with particular circuits. The intermediate file can be
 used to query the status of the submitted jobs or to resolve them, i.e. to wait for their completion
@@
 
-In synchronous mode, PyQBench first submits all jobs required to run the benchmark, and then
+In synchronous mode, PyQBench first submits all jobs required to run the benchmark and then
 immediately waits for their completion. The advantage of this approach is that no separate
@@
 We will now demonstrate how to implement this theoretical scheme in PyQBench. For this example we
-will use the Qiskit Aer simulator \cite{}. First, we import the necessary functions and classes from
+will use the Qiskit Aer simulator \cite{aer}. First, we import the necessary functions and classes from
 PyQBench and Qiskit. We also import \texttt{numpy} for the definition of \texttt{np.pi} constant and
@@
 	\caption{Differences between simplified (top) and user--controlled (bottom) execution of
-	benchmarks in PyQBench. Compared to simplified benchmarking, in user--controlled benchmarks the
+	benchmarks in PyQBench. Compared to simplified benchmarking, in user-controlled benchmarks the
 	user has direct access to the circuits being run, and hence can alter them (e.g. by adding
@@
 \end{lstlisting}
+
+\todo[inline]{ponizej dokonczycccccc}
+
 We can now examine the results. We expect that for noisy simulations, the result will be further
@@
 \subsubsection{Preparing configuration files}
-To prepare configyurartion files we need to define the experiment and the   backend 
+To prepare configuration files we need to define the experiment and the   backend 
 which we want to benchmark. Experiments and backends are defined in YAML files. An example experiment definition looks as follows.
@@
 	\end{lstlisting}
-\item The \textit{angles} key describe range of angles for Fourier parametrized family.
+\item The \textit{angles} key describe range of angles for Fourier parameterized family.
 The range is always uniform, starts at the \textit{start}, ends at \textit{stop} and contains \textit{num\_steps} points, including both start and stop.
@@
 	and \textit{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \textit{results\_per\_circuit} gives us 
-	the following additional informations: 
+	the following additional information: 
 	\begin{itemize}
@@
 discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
+command line interface (CLI) for running benchmarks using a predefined parameterized Fourier
 family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
@@
 \bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
+\bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
+(2021).
+Benchmarking near-term quantum computers via random circuit sampling.
+arXiv preprint arXiv:2105.05232.
+\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
+B., Jost, J.
+D., ...
+Wineland, D.
+J.
+(2008).
+Randomized benchmarking of quantum gates.
+Physical Review A, 77(1), 012307.
 \bibitem{knill2008randomized}
 Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., ...  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.	
+\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
+\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
+\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
 \bibitem{cross2019validating}
@@
 \bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
-\bibitem{arute2019quantum}Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
+\bibitem{arute2019quantum} Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
 C., Barends, R., ...
@@
 Science, 360(6385), 195-199.
-\bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
-(2021).
-Benchmarking near-term quantum computers via random circuit sampling.
-arXiv preprint arXiv:2105.05232.
-\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
-B., Jost, J.
-D., ...
-Wineland, D.
-J.
-(2008).
-Randomized benchmarking of quantum gates.
-Physical Review A, 77(1), 012307.
-\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
-\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
-\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
-\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for
-optimal single-shot discrimination of quantum measurements." Physical Review A
-98.4 (2018): 042103.
-\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
-\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
-\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
-\bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
-\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
-\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
-(2021).
-On the optimal certification of von Neumann measurements.
-Scientific Reports, 11(1), 3623.
-\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
-\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
-\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
-
-	\todo[inline]{do wykorzystania cite}
-
+	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
+\bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
 	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
@@
 IEEE.
-	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
-
-\bibitem{quark2022} Finžgar, J.
-R., Ross, P., Hölscher, L., Klepsch, J.,  Luckow, A.
-(2022, September).
-QUARK: A framework for quantum computing application benchmarking.
-In 2022 IEEE International Conference on Quantum Computing and Engineering (QCE) (pp.
-226-237).
-IEEE.
+\bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
+\bibitem{qiskit-randomized} The web resource at
+\url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
+\bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
+\bibitem{volume-in-practice} The web resource at\url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
+\bibitem{cross-entropy-bench} The web resource at
+\url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
+%
+%\bibitem{ghz} 
+%Greenberger, D. M., Horne, M. A., Zeilinger, A. (1989). Bell’s theorem, Quantum Theory, and Conceptions of the Universe. 
+\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for
+optimal single-shot discrimination of quantum measurements." Physical Review A
+98.4 (2018): 042103.
+\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
+\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
+\bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
+\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
+\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
+\bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
+\bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
+\bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
+\bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
+\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
+\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
+\bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
+\bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
+\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
+\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
+(2021).
+On the optimal certification of von Neumann measurements.
+Scientific Reports, 11(1), 3623.
+\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
+\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
+
 \bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking
@@
 
-%\section*{Current executable software version}
-%\label{}
-%
-%Ancillary data table required for sub version of the executable software: (x.1,
-%x.2 etc.) kindly replace examples in right column with the correct information
-%about your executables, and leave the left column as it is.
-%
-%\begin{table}[!h]
-%\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-%\hline
-%\textbf{Nr.} & \textbf{(Executable) software metadata description} &
-%\textbf{Please fill in this column} \\
-%\hline
-%S1 & Current software version & For example 1.1, 2.4 etc. \\
-%\hline
-%S2 & Permanent link to executables of this version  & For example:
-%$https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
-%\hline
-%S3 & Legal Software License & List one of the approved licenses \\
-%\hline
-%S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS,
-%Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based
-%etc. \\
-%\hline
-%S5 & Installation requirements \& dependencies & \\
-%\hline
-%S6 & If available, link to user manual - if formally published include a
-%reference to the publication in the reference list & For example:
-%$http://mozart.github.io/documentation/$ \\
-%\hline
-%S7 & Support email for questions & \\
-%\hline
-%\end{tabular}
-%\caption{Software metadata (optional)}
-%\label{}
-%\end{table}
-
 \appendix
 
-Let us first recall the general form of a quantum measurement, so called Positive Operator Valued
+\section{Mathematical preliminaries} \label{app:preliminaries}
+
+Let $\mathcal{M}_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
+the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
+$\mathcal{M}_d$.
+By $\Omega_d$, we will denote the set of quantum states, that is
+positive semidefinite operators having trace equal to one.
+The subset of $\mathcal{M}_d$ consisting of unitary matrices will be denoted
+by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
+$\DD \UU_d$.
+
+We will also need a linear mapping transforming $\mathcal{M}_{d_1}$ into
+$\mathcal{M}_{d_2}$, which will be denoted
+\begin{equation}
+\Phi: \mathcal{M}_{d_1 } \rightarrow \mathcal{M}_{d_2}.
+\end{equation}
+There
+exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $\mathcal{M}_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism.
+For a given linear mapping $\Phi$ the corresponding Choi operator $J(\Phi)$ is explicitly written as
+\begin{equation}
+J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
+
+We also introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
+and trace preserving (CPTP).
+In this work we will consider a special class of quantum channels, called unitary channels.  A
+quantum channel
+$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for any $U \in
+\UU_d$.
+
+Let us recall a  general form of a quantum measurement, so called Positive Operator Valued
 Measure (POVM). A POVM $\PP$ is a collection of positive semidefinite operators $\{E_1, \ldots, E_m
@@
 for which all the effects are rank-one projectors. Every such measurement can be
-parameterized by a unitary matrix $U$ with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
+parameterized by a unitary matrix $U \in \mathcal{U}_d$ with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
 are created by taking $\ket{u_i}$ as  $(i+1)$-th column of the unitary matrix $U$.
 We will denote von Neumann measurements described by the matrix $U$ by $\PP_{U}$. 
-
-\section{Mathematical preliminaries} \label{app:preliminaries}
-
-Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
-the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
-$M_d$.
-%The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
-%will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
-%matrices of dimension $d$ by $\HH_d^+$.
-By $\Omega_d$, we will denote the set of quantum states, that is
-positive semidefinite operators having trace equal to one.
-The subset of $M_d$ consisting of unitary matrices will be denoted
-by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$.
-%An operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a stochastic matrix if $a_{i,j} \ge 0$   and $\sum_{i} a_{i,j} = 1$, whereas an operator $A = \left( a_{i,j}\right)_{i,j} \in M_d$ is said to be a double stochastic matrix if $A$ is a stochastic matrix and $\sum_{j} a_{i,j} = 1$.
-
-We will also need a linear mapping transforming $M_{d_1}$ into
-$M_{d_2}$, which will be denoted
-\begin{equation}
-\Phi: M_{d_1 } \rightarrow M_{d_2}.
-\end{equation}
-There
-exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $M_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism.
-For a given linear mapping $\Phi$ the corresponding Choi operator $J(\Phi)$ is explicitly written as
-\begin{equation}
-J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
-
-We introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
-and trace preserving (CPTP).
-In this work we will consider a special class of quantum channels, called unitary channels.  A
-channel
-$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for any $U \in
-\UU_d$.
-
 The action of
@@
 \end{equation}
-Moreover, observe that each von Neumann measuement $\PP_{U}$ poses a  composition of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
-
-We need to also briefly discuss about the distance between unitary channels and von Neumann measurements. From \cite[Theorem 1]{puchala2018strategies}, the distance between measurements $\PP_U$ and
-$\PP_\Id$ ie equal to
+Moreover, observe that each von Neumann measurement $\PP_{U}$ poses a  composition of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
+
+We need to also briefly discuss about the distance between quantum operations. From \cite[Theorem 1]{puchala2018strategies}, the distance between measurements $\PP_U$ and
+$\PP_\Id$ can be expressed in the notion of diamond norm, that is
 \begin{equation}
 \|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} -
-\Phi_\Id\|_\diamond,
-\end{equation} whereas to express the distance between unitary channels, we need to introduce the notion of numerical range \cite{numericalrangle}. The set \begin{equation}
+\Phi_\Id\|_\diamond.
+\end{equation} To express the distance between unitary channels, we need to introduce the definition of numerical range \cite{numericalrangle}. The set \begin{equation}
 W(A) =\{\bra{x}A\ket{x}: \ket{x} \in
 \mathbb{C}^d, \;
-\;\braket{x}{x}=1\}.
-\end{equation}
-is called numerical range of  a matrix $A \in M_d$.
-The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.
+\;\braket{x}{x}=1\}
+\end{equation}
+is called the numerical range of  a given matrix $A \in \mathcal{M}_d$.
+The detailed properties of the numerical range and its generalizations we can read on the website~\cite{nr}.
+
 Due to the definition of $W(A)$, the distance between two unitary channels $\Phi_{U} $ and $\Phi_\Id$
@@
 \section{Discrimination task for Hadamard gate}\label{app:hadamard}
-For the discrimination task between von Neumann measurements $\PP_{U}$ and $\PP_\Id$, where $U = H$ (the Hadamard gate) the key is to calculate the diamond norm $\| \mathcal{P}_H - \PP_\Id \|_\diamond$ and
+For the discrimination task between von Neumann measurements $\PP_{U}$ and $\PP_\Id$, where $U = H$ (the Hadamard gate),  the key is to calculate the diamond norm $\| \mathcal{P}_H - \PP_\Id \|_\diamond$ and
 determine the discriminator $\ket{\psi_0}$.
@@
 \begin{equation}
-E_0 = \frac{1}{2} \left( \begin{matrix} 
+E_0 = \frac{1}{\sqrt{2}} \left( \begin{matrix} 
 1 + i & 0  \\  0 & -1-i 
@@
  According to the Lemma 5 and the proof of Theorem 1 in \cite{puchala2018strategies} we assume that \begin{equation}
- \ket{\psi_0} = | \rho_0 \rangle \rangle. 
- \end{equation}
- It direcly implies that 
+ \ket{\psi_0} = \left.\left| \sqrt{\rho_0^\top}\right\rangle \right\rangle. 
+ \end{equation}
+ It directly implies that 
  \begin{equation}
@@
  Let us consider \begin{equation}
- X = \left(\PP_{H} \otimes \Id \right)(\proj{\psi_0}) - \left(\PP_{\Id} \otimes \Id \right) (\proj{\psi_0})
-  \end{equation}
- From the Hahn-Jordan decomposition, let us note
- \begin{equation}
- X = P - Q
+ X = \left(\PP_{H} \otimes \Id \right)(\proj{\psi_0}) - \left(\PP_{\Id} \otimes \Id \right) (\proj{\psi_0}).
+  \end{equation}
+ From the Hahn-Jordan decomposition \cite{watrous}, let us note
+ \begin{equation}
+ X = P - Q,
  \end{equation}
@@
  \begin{equation}
- \Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
+ \Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right),
  \end{equation}
@@
  \begin{equation}
- \begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
+ \begin{cases} \ket{x_p} =  V_0  \ket{0} \\  \ket{x_q} =  V_0 \ket{1} \end{cases}
  \end{equation}
@@
  \begin{cases}
- V_1 \ket{y_p} = \ket{0} \\
- V_1 \ket{y_q} = \ket{1}
+ \ket{y_p} =   V_1 \ket{0} \\
+  \ket{y_q} = V_1  \ket{1}
  \end{cases}.
@@
  \end{equation}
+ and
  \begin{equation}
@@
 
-\section{Optimal probability for parametrized Fourier family} \label{app:optimal-probability}
+\section{Optimal probability for parameterized Fourier family} \label{app:optimal-probability}
 Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
@@
 \end{equation}
-%\begin{equation}
-%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
-%\end{equation}
 where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
@@
 	\end{equation}
-	%		It implies that we can prove  equivalently  the following condition
-	%		\begin{equation}
-	%		\max_{E \in \diaguni_2 } \nu_{UE} = \nu_U
-	%		\end{equation}
-	This condition is equivalent to show
-	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{E} = \frac{|1 + e^{i \phi} | }{2},
+	This condition is equivalent to show that for every $E \in \diaguni_2$
+	\begin{equation}
+	 \nu_{E} \le  \frac{|1 + e^{i \phi} | }{2},
 	\end{equation}
@@
 
-	%	For simplify notation, let 	$ \nu \coloneqq \max_{E \in \diaguni_2 } \nu_{E} $.
 	The celebrated Hausdorf-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
-	$W(A)$ of any matrix $A \in M_d$ is a convex set, and therefore we have
+	$W(A)$ of any matrix $A \in \mathcal{M}_d$ is a convex set, and therefore we have
 	\begin{equation}
@@
 	\begin{equation}
-	\max_{E \in \diaguni_2 } \nu_{E}  = \max_{E \in \diaguni_2 }  \min_{\rho \in
+	 \nu_{E}  =   \min_{\rho \in
 		\Omega_2} \left| \tr \left( \rho U E \right) \right|.
 	\end{equation}
-	For that, our task is reduced to show that
-	\begin{equation}
-	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \max_{E \in \diaguni_2 } \nu_{E}.
+	For that, our task is reduced to show that for every  $E \in \diaguni_2$ there exists $\rho \in \Omega_2$ such that
+	\begin{equation}
+ | \tr \left(\rho U E\right) | \le \frac{|1 + e^{i \phi} | }{2}. 
 	\end{equation}
@@
 	$.
-	Then, we have
+	Then, for every $ E \in \diaguni_2 $ we have
 	\begin{equation}
 	\begin{split}
-	& \forall E \in \diaguni_2 \,\,\, | \tr (\rho U E) | = \frac{1}{2}  \left| \tr \left(
-	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  \\ &
+ | \tr (\rho U E) | & =   \frac{1}{2}  \left| \tr \left(
+	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =  
 	\frac{1}{2} \left| \tr\left((   \proj{x_0} +e^{i \phi}\proj{x_1} ) E \right)
+	\right| \\& =
+	\frac{1}{2} \left|  \bra{x_0} E \ket{x_0} +  e^{i \phi}\bra{x_1} E \ket{x_1}
 	\right| = 
-	\frac{1}{2} \left|  \bra{x_0} E \ket{x_0} +  e^{i \phi}\bra{x_1} E \ket{x_1}
-	\right| = \\&
 	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right|
-	=
+	\\& =
 	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le
-	\max_{E \in \diaguni_2 } \nu_{E},
+\frac{|1 + e^{i \phi} | }{2}, 
 	\end{split}
@@
 	\end{equation}
-	%	Finally, we obtain that
-	%	\begin{equation}
-	%	\| \PP_{U} - \PP_{\Id} \|_\diamond =  |1-e^{i   \phi }|.
-	%	\end{equation}
 	It implies that
@@
 
-\section{Optimal discrimination strategy for parametrized Fourier family} \label{app:optimal-strategy}
+\section{Optimal discrimination strategy for parameterized Fourier family} \label{app:optimal-strategy}
 
@@
 	\begin{equation}
-	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2},
-	\end{equation}
-	where  for eigenvalue $\lambda_1 = 1$, the corresponding
+	U= \lambda_0 \ketbra{x_0}{x_0} + \lambda_1 \ketbra{x_1}{x_1},
+	\end{equation}
+	where  for eigenvalue $\lambda_0 = 1$, the corresponding
 	eigenvector is
-	of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
+	of the form $\ket{x_0} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
 	$,
-	whereas for  $\lambda_2 = e^{i \phi}$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
+	whereas for  $\lambda_1 = e^{i \phi}$ we have $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
 	$.
@@
 	\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top
-	\right\|_1  \\
+\left( \Id \otimes \sqrt{\rho} \right) 	\right\|_1  \\
 	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes
@@
 	\\
-	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left(
+	& = \max_{\rho \in \Omega_2} \sum_{i=0}^{1} \left\| \sqrt{\rho}  \left(
 	\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1. 
@@
 	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2}
-	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i
-		}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
+	\sum_{i=0}^{1} \sqrt{\left( \bra{\bar{u_i}} \rho \ket{\bar{u_i}} + \bra{i} \rho \ket{i
+		}\right)^2 - 4 | \bra{\bar{u_i}} \rho \ket{i} |^2}.
 	\end{equation}
@@
 	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond
-	&= \sum_{i=0}^1
-	\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 -
-		4|\bra{i}\rho_0\ket{u_i}|^2}  \\
+	&\ge \sum_{i=0}^1
+	\sqrt{\left(\bra{\bar{u_i}}\rho_0\ket{\bar{u_i}} + \bra{i} \rho_0 \ket{i} \right)^2 -
+		4|\bra{i}\rho_0\ket{\bar{u_i}}|^2}  \\
 	&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2}
 	\\
-	&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \bra{i} \proj{u_1}
-		\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
+	&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \braket{i}{u_0} 
+		\braket{u_0}{i} + e^{i \phi} \cdot\braket{i}{u_1} \braket{u_1}{i}\right|^2} \\
 	&= \sum_{i=0}^1
@@
 	\end{equation}
-	Observe that
+	Due to Theorem \ref{th:probability} and the following equality
 	\begin{equation}
@@
 	\Id \otimes \sqrt{\rho} \right) \|_1 = \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top
-	\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
+	\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1, 
 	\end{split}
 	\end{equation}
-	Due to that, we know
-	that $\left| \sqrt{\rho_0}^{\top} \rangle \right\rangle$ equals $\frac{1}{\sqrt{2} } |
-	\Id_2 \rangle \rangle$ is the discriminator of the problem
-	of discrimination between
-	$\PP_{\Id} $ and $\PP_U$ for
-	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm).      Hence, we obtain that \begin{equation}
-	\ket{\psi_{0}} =  \frac{1}{\sqrt{2} } |
+the discriminator $\ket{\psi_0}$
+ is equal to  \begin{equation}
+	\ket{\psi_{0}} =  | \sqrt{\rho_0}^\top
+	\rangle \rangle  = \frac{1}{\sqrt{2} } |
 	\Id_2 \rangle \rangle,
@@
 	\end{equation}
-	Repeating the scheme used to distinguish the von Neumann measurements in the Hadamard basis (see \ref{app:hadamard}), we use the Hahn Jordan decomposition and then we create the projective operators into the positive and negative part of $X$ matrix.
-%	From Holevo-Helstrom theorem~\cite{watrous}, we constrain a final optimal measurement $\PP_{V_i}$.
-%	Let us define
-%	\begin{equation}
-%	X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi_0}) -  \left( \PP_\Id
-%	\otimes \Id_2 \right)(\proj{\psi_0}).
-%	\end{equation}
-%	
-%	
-%	
-%	From the Hahn-Jordan decomposition, let us note
-%	\begin{equation}
-%	X = P - Q
-%	\end{equation}
-%	where $P, Q \ge 0 $.
-%	Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
-%	respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
-%	\begin{equation}
-%	\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right)
-%	\end{equation}
-%	and
-%	\begin{equation}
-%	\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
-%	\end{equation}
-%	Hence, we define $V_0$ as
-%	\begin{equation}
-%	\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
-%	\end{equation}
-%	and $V_1$ as
-%	\begin{equation}
-%	\begin{cases}
-%	V_1 \ket{y_p} = \ket{0} \\
-%	V_1 \ket{y_q} = \ket{1}
-%	\end{cases}.
-%	\end{equation}
-%	For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H
-%	\diag(1, e^{i \phi })H$, 
+	Repeating the procedure used to distinguish the von Neumann measurements in the Hadamard basis (see \ref{app:hadamard}), we use the Hahn-Jordan decomposition and then we create the projective operators into the positive and negative part of $X$ matrix.
 	Hence, the explicit form of $V_0$ and $V_1$ is given as

### 2023-02-28 txt/manuscript.tex
Update CLI description (it's not yet finished)

@@
 
-We can now examine the results. We expect that for noisy simulations, the result will be further
-away from the target value of \texttt{0.8535533905932737}. For example, in one of our runs we
-obtained \texttt{prob\_succ\_noiseless = 0.8524401115559386} and \texttt{prob\_succ\_noisy =
-0.5017958400693446}. 
-\noindent
+We can now examine the results. As an example, in one of our runs, we obtained
+\texttt{prob\_succ\_noiseless = 0.8524401115559386} and \texttt{prob\_succ\_noisy =
+0.5017958400693446}. As expected, for noisy simulations, the result lies further
+away from the target value of \texttt{0.8535533905932737}.
+
 This concludes our example. In the next section, we will show how to use PyQBench's CLI.
@@
 \subsection{Using \texttt{qbench} CLI}
-Using PyQBench as a library allows one to conduct arbitrary two-qubit von Neumann measurement experiment. However, as discussed in the previous guide, it requires some amount of boilerplate code.
-For a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
-The workflow is describe as a list of steps:
+Using PyQBench as a library allows one to conduct a two--qubits benchmark with arbitrary von Neumann
+measurement. However, as discussed in the previous guide, it requires writing some amount of code.
+For a Fourier parametrized family of measurements, PyQBench offers a simplified way of conducting
+benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
+as the following list of steps::
 
@@
 
-\item Preparing configuration files describing backend and the experiment scenario.
+\item Preparing configuration files describing the backend and the experiment scenario.
 \item Submitting/running experiments. Depending on the experiment scenario, execution can be synchronous, or asynchronous.
-\item (optional) Checking status of the submitted jobs if the execution is asynchronous.
-\item For asynchronous jobs, 
-resolve jobs into actual measurements.
-\item Computing discrimination probabilities and outputting the resulting table.
+\item (optional) Checking the status of the submitted jobs if the execution is asynchronous.
+\item Resolving asynchronous jobs into the actual measurement outcomes.
+\item Converting obtained measurement outcomes into tabulated form.
 \end{enumerate}
 \subsubsection{Preparing configuration files}
-To prepare configuration files we need to define the experiment and the   backend 
-which we want to benchmark. Experiments and backends are defined in YAML files. An example experiment definition looks as follows.
-\begin{lstlisting}[language=Python, caption=Defining the experiment]
+The configuration of PyQBench CLI is driven by YAML files. The first configuration file
+describes the experiment scenario to be executed. The second file describes the backend.
+Typically, this backend will correspond to the physical device to be benchmarked, but for testing
+purposes one might as well use any other Qiskit--compatible backend including simulators.
+Let us first describe the experiment configuration file, which might look as follow.
+\begin{lstlisting}[language=Python, caption=Defining the experiment, label=lst:experiment]
 type: discrimination-fourier
@@
 \end{lstlisting}
-
-The components of the experiment is as follows:
+The experiment file contains the following fields:
 \begin{itemize}
-	\item The \textit{type} describes type of the experiment. Currently, the only option of  \textit{type} is \textit{discrimination-fourier}. 
-	\begin{lstlisting}[language=Python]
-type: discrimination-fourier
-	\end{lstlisting}
-	\item The \textit{qubits} list describes pair of qubits on which the experiment should be run.
-In this example, the benchmark will run on two pairs of qubits.
-First pair is 0 and 1, second pair is 1 and 2.
-\begin{lstlisting}[language=Python]
-qubits:
-	- target: 0
-	  ancilla: 1
-	- target: 1
-	  ancilla: 2
-	\end{lstlisting}
-\item The \textit{angles} key describe range of angles for Fourier parameterized family.
-The range is always uniform, starts at the \textit{start}, ends at \textit{stop} and contains \textit{num\_steps} points, including both start and stop.
-The start and stop can be arithmetic expressions using \textit{pi} literal.
-For instance range defined as:
-\begin{lstlisting}[language=Python]
-angles:
-	start: 0
-	stop: 2 *pi
-	num_steps: 3
-\end{lstlisting}
- would contain three angles $0, \pi$  and $2\pi$.
- \item 
- The \textit{gateset} key describes the gate decomposition of the experiment.
-The possible options are \textit{[ibmq, lucy, rigetti, generic]}.
-If the user choose the device-dependent key, that is one of the options \textit{ibmq, lucy, rigetti}, then the experiment will be implemented by using predefined sequence of native gates.
-If the user choose the \textit{generic} key, then the compiler  will automatically decompose given circuit in the way that is suitable for the device in use.
- \begin{lstlisting}[language=Python]
-gateset: ibmq
- \end{lstlisting}
- \item The \textit{method} can take one of two values: \textit{direct\_sum} or \textit{postselection}, and as the name suggests, defines which method is used to implement the experiment.
- \begin{lstlisting}[language=Python]
-method: direct_sum
- \end{lstlisting}
- \item The \textit{num\_shots} defines how many shots are performed in the experiment for particular angle, qubit pair and circuit.
-For the purpose of calculating possible costs, this is how you compute total number of shots and executed circuits.
-Let $N$ be the number of qubit pairs in \textit{qubits} key and let $M$ be the number of steps defined in the \textit{angles} key.
-Then number of executed circuits is $2MN$ for the \textit{direct\_sum} method and $4MN$ for the \textit{postselection} method.
-Each of those circuits is executed \textit{num\_shots} times.
- \begin{lstlisting}[language=Python]
-num_shots: 100
- \end{lstlisting}
+	\item \texttt{type}: a string describing the type of the experiment. Currently, the only option of  \textit{type} is \texttt{discrimination-fourier}.
+	\item \texttt{qubits}: a list enumerating pairs of qubits on which the experiment should be run.
+	For configuration in listing \ref{lst:experiment}, the benchmark will run on two pairs of qubits. The first pair is 0 and 1, and
+	the second one is 1 and 2. We decided to describe a pair by using \texttt{target} and
+	\texttt{ancilla} keys rather than using a plain list to emphasize that the role of qubits in the
+	experiment is not symmetric.
+	\item \texttt{angles}: an object describing the range of angles for Fourier parameterized
+	family. The described range is always uniform, starts at the \texttt{start}, ends at
+	\texttt{stop} and contains \texttt{num\_steps} points, including both \texttt{start} and
+	\texttt{stop}. The \texttt{start} and \texttt{stop} can be arithmetic expressions using
+	\texttt{pi} literal. For instance, the range defined in listing \ref{lst:experiment} contains
+	three points: 0, $\pi$ and $2\pi$.
+ 	 \item \texttt{gateset}: a string describing the set of gates used in the decomposition of
+ 	 circuits in the experiment. The PyQBench contains explicit implementations of circuits The
+ 	 possible options are \textit{[ibmq, lucy, rigetti]}, corresponding to decompositions
+ 	 compatible with IBM Q devices, OQC Lucy device, and Rigetti devices. Alternatively, one might
+ 	 wish to turn off the decomposition by using a special value \texttt{generic}. However, for this
+ 	 to work a backend used for the experiment must natively implement all the gates needed for the
+ 	 experiment, as described in \ref{sec:fourier}.
+ 	\item \texttt{method}: a string, either \texttt{postselection} or \texttt{direct\_sum}
+ 	determining which implementation of the conditional measurement is used.
+ 	\item \texttt{num\_shots}: an integer defines how many shots are performed in the experiment for
+ 	a particular angle, qubit pair and circuit. Note that if one wishes to compute the total number
+ 	of shots in the experiment, it is necessary to take into account that the \texttt{postselection}
+ 	method uses twice as many circuits as the \texttt{direct\_sum} method.
 \end{itemize}
 
-Observe that the experiment file does not specify what backend to use. This way, the same experiment file can be used on multiple backends.
- Different backends may require different information to be used.
-For instance, IBMQ backends might require hub, group and project, whereas backends from the \textit{Aer} package do not.
-Hence, the exact format of the YAML file depends on what backend one wants to use.
-Below we present
- YAML file defining the IMBQ backend named Quito. 
-\begin{lstlisting}[language=Python, caption=IBMQ backend]
+The second configuration file describes the backend. We decided to decouple the
+experiment and the backend files because it facilitates their reuse. For instance, the same
+experiment file can be used to run benchmarks on multiple backends, and the same backend description
+file can be used with multiple experiments.
+
+Different Qiskit backends typically require different data for their initialization. Hence, there
+are multiple possible formats of the backend configuration files understood by PyQBench. We refer
+the interested reader to the PyQBench's documentation. Below we describe an example YAML file
+describing IBM Q backend named
+Quito.
+\begin{lstlisting}[language=Python, caption=IBMQ backend, label=lst:backend]
 name: ibmq_quito
@@
 \end{lstlisting}
-
-IBMQ backends typically require and access token to IBM Quantum Experience.
-It would be unsafe to store them in plain text, and therefore the token is configured separately.
-Before running the experiment, you should place your token in the \textit{IBMQ\_TOKEN} environmental variable.
-
-\subsubsection{Notes on using the asynchronous flag}
-In this example, the only key that requires the explanation is \textit{asynchronous} which determines whether experiments will be run asynchronously  (\textit{true}) or not (\textit{false}).
-% We recommend setting it to true, unless your experiment is really small (several circuits total).
-However, some backends may not support asynchronous execution.
-This might be especially the case with local simulators.
-
+IBMQ backends typically require an access token to IBM Quantum Experience. Since it would be unsafe
+to store it in plain text, the token has to be configured separately in \texttt{IBMQ\_TOKEN}
+environmental variable.
+
+\subsubsection{Remarks on using the asynchronous flag}
+For backends supporting asynchronous execution, the \texttt{asynchronous} setting can be configured
+to toggle it.
 For asynchronous execution to work, the following conditions have to be met:
 \begin{itemize}
-\item Jobs returned by the backend have unique \textit{job\_id}, 
-\item Job object is retrievable from the backend using \textit{backend.retrieve\_job} method, even from another process (e.g. if the original process running the experiment has finished).
+\item Jobs returned by the backend have unique \texttt{job\_id}.
+\item Jobs are retrievable from the backend using the \texttt{backend.retrieve\_job} method, even from another process (e.g. if the original process running the experiment has finished).
 \end{itemize}
-Since PyQBench cannot determine if the job retrieval works for given backend, the user is responsible for checking it yourself.
-
-\todo[inline]{co z tymi sekcjami?}
-\subsubsection{Backends obtainable from simple providers???}
-\subsubsection{Backends constructed from a simple function call???}
-\todo[inline]{co z tymi sekcjami?}
+Since PyQBench cannot determine if the job retrieval works for a given backend, it is the user's
+responsibility to ensure that this is the case before setting \texttt{asynchronous} to \texttt{true}.
 

### 2023-02-28 txt/manuscript.tex
Update manuscript.tex

@@
 \begin{table}[H]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
+\begin{tabular}{|l|p{5.5cm}|p{7.5cm}|}
 \hline
-\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this
-column} \\
-\hline
-C1 & Current code version & 0.1.0 \\
+C1 & Current code version & 0.1.1 \\
 \hline
@@
 
-%% main text
-
-%The permanent link to code/repository or the zip archive should include the
-%following requirements:
-%
-%README.txt and LICENSE.txt.
-%
-%Source code in a src/ directory, not the root of the repository.
-%
-%Tag corresponding with the version of the software that is reviewed.
-%
-%Documentation in the repository in a docs/ directory, and/or READMEs, as
-%appropriate.
-
 \section{Motivation and significance}
@@
 On top of that, several
-libraries and frameworks can integrate with different hardware vendors. Examples of such frameworks
+libraries and frameworks can integrate with multiple hardware vendors. Examples of such frameworks
 include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.
@@
 In this paper, we introduce yet another method for benchmarking gate--based devices with a simple
-operational interpretation. In our method, we test how well the given device can distinguish between
-two von Neumann measurements performed in different bases. We implemented our method in an
-open-source Python library called PyQBench. The library supports any device available through Qiskit
-library, and thus can be used with providers such as IBM Q or Amazon Braket. Along with the library,
-the PyQBench package contains a command line tool for running most common benchmarking scenarios.
+operational interpretation. In our method, we test how well the given device is at guessing which of
+the two known von Neumann measurements were performed during the experiment. We implemented our
+approach in an open-source Python library called PyQBench. The library supports any device available
+through the Qiskit library, and thus can be used with providers such as IBM Q or Amazon Braket.
+Along with the library, the PyQBench package contains a command line tool for running most common
+benchmarking scenarios.
 
@@
 \todo[inline]{cos tu dopisac o tych metodach}
-A further approach used to benchmark NISQ	 devices is
-quantum volume \cite{volume-in-practice}
-or cross-entropy benchmarking \cite{cross-entropy-bench}
-\todo[inline]{summary}
+Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
+characterizes capacity of a device for solving computational problems. It takes into account
+multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library allows one to
+measure quantum volume of a device by using its \texttt{qiskit.ignis.verification.quantum\_volume}.
+Other implementations of Quantum Volume can be found as well, see e.g. \cite{volume-in-practice}.
+
+% In
+% cross--entropy benchmarkig a random quantum circuit is executed on a quantum computer multiple
+% times. Then, the obtained measurement outcomes are used for computing cross--entropy fidelity
+% $F_{XEB} \in [0, 1]$. A value of 0 means that results obtained from the device are no better then
+% random guessing, whereas value of 1 correspond to a perfect, noiseless execution of the circuit.
+% Packages implementing cross--entropy benchmarking include e.g. \cite{cross-entropy-bench}.
 
@@
 \end{lstlisting}
-
-\todo[inline]{ponizej dokonczycccccc}
 
@@
 \subsubsection{Running the experiment and collecting measurements data}
-After preparing YAML files with defined experiment and backend,
-running the experiment is done by using the following command line invocation:
+After preparing YAML files defining experiment and backend,
+running the benchmark can be launched by using the following command line invocation:
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-The output file will be printed to stdout. Optionally, the \textit{- -output OUTPUT} flag might be provided to write the output to the \textit{OUTPUT} file instead.
+The output file will be printed to stdout. Optionally, the \texttt{- -output OUTPUT} parameter might be provided to write the output to the \texttt{OUTPUT} file instead.
 \begin{lstlisting}[language=Python]
@@
 \begin{itemize}
-	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, job$\_$ids correlated with the circuit they correspond to.
-	\item If the backend is synchronous, the output will contain measurement data (bitstrings) for each of the circuits run.
+	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, \texttt{job\_ids} correlated with the circuit they correspond to.
+	\item If the backend is synchronous, the output will contain measurement outcomes (bitstrings) for each of the circuits run.
 \end{itemize}
@@
 	\begin{itemize}
-		\item  name: id:  the information which measurement is used during experiment,   $\PP_{U}$ or $\PP_{\Id}$. In this example we consider  $\PP_{\Id}$.
-		\item histogram: {'00': 28, '01': 26, '10': 21, '11': 25}: the dictionary with measurement's outcomes.
-The keys represent possible measurement oucomes, whereas the values present number of occurrences.
-		\item mitigation\_info:  \textit{system.properties().qubits} contains information on the physical attributes of the qubits.
+		\item  \texttt{name}:  the information which measurement is used during experiment, either
+		string \texttt{"u"} for $\PP_{U}$ or string \texttt{"id"} for $\PP_{\Id}$. In this example
+		we consider $\PP_{\Id}$.
+		\item \texttt{histogram}: the dictionary with measurement's outcomes. The keys represent possible bitstrings, whereas the values present number of occurrences.
+		\item \texttt{mitigation\_info}:  \textit{system.properties().qubits} contains information on the physical attributes of the qubits.
 This includes e.g.

### 2023-02-28 txt/manuscript.tex
add ocean

@@
 \hline
-C3 & Code Ocean compute capsule & \todo[inline]{???}\\
+C3 & Code Ocean compute capsule & \texttt{https://codeocean.com/capsule/ 89088992-9a27-4712-8525-} \texttt{d92a9b23060f/tree}\\
 \hline
@@
 One could mention randomized benchmarking \cite{liu2022sampling, knill2007randomized, knill2008randomized, wallman2014randomized, helsen2022general,
-	cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume} or cross-entropy benchmarking \cite{arute2019quantum, neill2018blueprint}.
+	cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume}. 
+%or cross-entropy benchmarking \cite{arute2019quantum, neill2018blueprint}.
 
@@
 
-\todo[inline]{cos tu dopisac o tych metodach}
 Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
@@
 multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library allows one to
-measure quantum volume of a device by using its \texttt{qiskit.ignis.verification.quantum\_volume}.
+measure quantum volume of a device by using its \texttt{qiskit.ignis.verifica \\ tion.quantum\_volume}.
 Other implementations of Quantum Volume can be found as well, see e.g. \cite{volume-in-practice}.
@@
 \begin{itemize}
-	\item \texttt{type}: a string describing the type of the experiment. Currently, the only option of  \textit{type} is \texttt{discrimination-fourier}.
+	\item \texttt{type}: a string describing the type of the experiment. Currently, the only option of  \texttt{type} is \texttt{discrimination-fourier}.
 	\item \texttt{qubits}: a list enumerating pairs of qubits on which the experiment should be run.
@@
  	 circuits in the experiment. The PyQBench contains explicit implementations of circuits The
- 	 possible options are \textit{[ibmq, lucy, rigetti]}, corresponding to decompositions
+ 	 possible options are \texttt{[ibmq, lucy, rigetti]}, corresponding to decompositions
  	 compatible with IBM Q devices, OQC Lucy device, and Rigetti devices. Alternatively, one might
@@
 \end{lstlisting}
-	The data includes \textit{target, ancilla, phi},
-	and \textit{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \textit{results\_per\_circuit} gives us
+	The data includes \texttt{target, ancilla, phi},
+	and \texttt{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \texttt{results\_per\_circuit} gives us
 	the following additional information:
@@
 		\item \texttt{histogram}: the dictionary with measurement's outcomes. The keys represent possible bitstrings, whereas the values present number of occurrences.
-		\item \texttt{mitigation\_info}:  \textit{system.properties().qubits} contains information on the physical attributes of the qubits.
+		\item \texttt{mitigation\_info}:  \texttt{system.properties().qubits} contains information on the physical attributes of the qubits.
 This includes e.g.
 information about readout error.
-As shown below, the \textit{readout\_error} is further partitioned into \textit{prob\_meas0\_prep1} and \textit{prob\_meas1\_prep0}, indicating the probability of preparing a given computational basis state, but measuring the orthogonal state.
+As shown below, the \texttt{readout\_error} is further partitioned into \texttt{prob\_meas0\_prep1} and \texttt{prob\_meas1\_prep0}, indicating the probability of preparing a given computational basis state, but measuring the orthogonal state.
 The readout error is taken to be the average of these two values.
-Note that \textit{prob\_meas0\_prep1} is usually the dominant factor in the readout error due to relaxation during the measurement process.
+Note that \texttt{prob\_meas0\_prep1} is usually the dominant factor in the readout error due to relaxation during the measurement process.
 ~\cite{mthree, mthreepublication}
@@
 \subsubsection{Resolving asynchronous jobs}
-If the status of jobs is \textit{DONE}, we have to obtain measurements from the submitted jobs. This is done using the following command:
+If the status of jobs is \texttt{DONE}, we have to obtain measurements from the submitted jobs. This is done using the following command:
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-The resolved results, stored in \textit{resolved.yml}, would look just like the experiment was run synchronously.
+The resolved results, stored in \texttt{resolved.yml}, would look just like the experiment was run synchronously.
 More precisely, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment (see \ref{app:example}).
@@
 \subsubsection{Computing probabilities}
-Regardless of whether we use a synchronous or asynchronous approach, we can convert the resulting YML file \textit{results.yml} to a CSV file by creating a result table in which we place the results of discrimination probabilities.
+Regardless of whether we use a synchronous or asynchronous approach, we can convert the resulting YML file \texttt{results.yml} to a CSV file by creating a result table in which we place the results of discrimination probabilities.
 To construct a table with probabilities, you can use the following command
@@
 \end{lstlisting}
-A single row for each tuple of \textit{(target, ancilla, phi)}.
-The \textit{disc\_prob} column will contain the discrimination probability for given configuration.
-The \textit{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
+A single row for each tuple of \texttt{(target, ancilla, phi)}.  The \texttt{ideal\_prob} 
+column says the theoretical probability of correct discrimination whereas
+the \texttt{disc\_prob} column contains the empirical discrimination probability.
+The \texttt{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
 A sample csv file is provided below:
@@
 \bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
-\bibitem{arute2019quantum} Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
+%\bibitem{arute2019quantum} Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
 C., Barends, R., ...
@@
 Nature, 574(7779), 505-510.
-\bibitem{neill2018blueprint}
-Neill, C., Roushan, P., Kechedzhi, K., Boixo, S., Isakov, S.
+%\bibitem{neill2018blueprint}
+%Neill, C., Roushan, P., Kechedzhi, K., Boixo, S., Isakov, S.
 V., Smelyanskiy, V., ...
@@
 \end{lstlisting}
-For the same experiment file, we use the flag \textit{asynchronous: true} to define asynchronous experiment.
+For the same experiment file, we use the flag \texttt{asynchronous: true} to define asynchronous experiment.
 

### 2023-02-28 txt/manuscript.tex
Update last part of the CLI description

@@
 		we consider $\PP_{\Id}$.
-		\item \texttt{histogram}: the dictionary with measurement's outcomes. The keys represent possible bitstrings, whereas the values present number of occurrences.
-		\item \texttt{mitigation\_info}:  \texttt{system.properties().qubits} contains information on the physical attributes of the qubits.
-This includes e.g.
-information about readout error.
-As shown below, the \texttt{readout\_error} is further partitioned into \texttt{prob\_meas0\_prep1} and \texttt{prob\_meas1\_prep0}, indicating the probability of preparing a given computational basis state, but measuring the orthogonal state.
-The readout error is taken to be the average of these two values.
-Note that \texttt{prob\_meas0\_prep1} is usually the dominant factor in the readout error due to relaxation during the measurement process.
-~\cite{mthree, mthreepublication}
-		\item mitigated\_histogram:  the histogram with measurement's outcomes after mitigation.
+		\item \texttt{histogram}: the dictionary with measurements' outcomes. The keys represent
+		possible bitstrings, whereas the values are the number of occurrences.
+		\item \texttt{mitigation\_info}:  for some backends (notably for backends corresponding to
+		IBM Q devices), \texttt{backends.properties().qubits} contains information that might be
+		used for error mitigation using the MThree method \cite{mthree, mthreepublication}. If this
+		info is available, it will be stored in the \texttt{mitigation\_info} field, otherwise this field will be absent.
+		\item \texttt{mitigated\_histogram}: the histogram with measurements' outcomes after the error mitigation.
 	\end{itemize}
@@
 \subsubsection{Resolving asynchronous jobs}
-If the status of jobs is \texttt{DONE}, we have to obtain measurements from the submitted jobs. This is done using the following command:
+For asynchronous experiments, the stored intermediate data has to be resolved in actual
+measurements' outcomes. The following command will wait until all jobs are completed and then write
+a result file.
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-The resolved results, stored in \texttt{resolved.yml}, would look just like the experiment was run synchronously.
-More precisely, we should have a file containing measurement histograms, no matter if we run a synchronous or asynchronous experiment (see \ref{app:example}).
-Next, we can compute the discrimination probabilities.
+The resolved results, stored in \texttt{resolved.yml}, would look just like if the experiment was
+run synchronously. Therefore, the final results will look the same no matter in which mode the
+benchmark was run, and hence in both cases the final output file is suitable for being an input for
+the command computing the discrimination probabilities.
 
 \subsubsection{Computing probabilities}
-Regardless of whether we use a synchronous or asynchronous approach, we can convert the resulting YML file \texttt{results.yml} to a CSV file by creating a result table in which we place the results of discrimination probabilities.
-To construct a table with probabilities, you can use the following command
+As a last step in the processing workflow, the results file has to be passed to \texttt{tabulate}
+command:
 \begin{lstlisting}[language=Python]
@@
 \end{lstlisting}
-A single row for each tuple of \texttt{(target, ancilla, phi)}.  The \texttt{ideal\_prob} 
-column says the theoretical probability of correct discrimination whereas
-the \texttt{disc\_prob} column contains the empirical discrimination probability.
-The \texttt{mit\_disc\_prob} column contains discrimination probability if Mthree mitigation was applied~\cite{mthree, mthreepublication}.
-A sample csv file is provided below:
+The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
+\texttt{ideal\_prob}, \texttt{disc\_prob} and, optionally, \texttt{mit\_disc\_prob}. Each row in the
+table describes results for a tuple of \texttt{(target, ancilla, phi)}.  The reference optimal value
+of discrimination probability is present in \texttt{ideal\_prob} column, whereas the obtained,
+empirical discrimination probability can be found in the \texttt{disc\_prob} column. The
+\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
+Mthree error mitigation \cite{mthree, mthreepublication}, if it was applied.
+A sample CSV file is provided below:
 \begin{figure}[h!]
@@
 	\includegraphics[scale=1]{results/async_result}
-	\caption{Tabulate results}
+	\caption{Tabulated results}
 	\label{fig:tabulateresults}

### 2023-03-05 txt/manuscript.tex
add impact

@@
 \section{Impact}
-\todo[inline]{OJCIEC WYKAZ SIE, bo trzeba to dobrze sprzedac, nizej tekst z formatki softwarex co powinna zawierac ta sekcja}
-This software has two main contributions.
-
-\textbf{This is the main section of the article and the reviewers weight the
-description here appropriately}
-
-Indicate in what way new research questions can be pursued as a result of the
-software (if any).
-
-Indicate in what way, and to what extent, the pursuit of existing research
-questions is improved (if so).
-
-Indicate in what way the software has changed the daily practice of its users
-(if so).
-
-Indicate how widespread the use of the software is within and outside the
-intended user group.
-
-Indicate in what way the software is used in commercial settings and/or how it
-led to the creation of spin-off companies (if so).
+With the surge of availability of quantum computing architectures in recent
+years it becomes increasingly difficult to keep track of their relative
+performance. To make this case even more difficult, various providers give
+access to different figures of merit for their architectures. Our package allows
+the user to test various architectures, available through \texttt{qiskit} and
+Amazon BraKet using problems with simple operational interpretation. We provide
+one example built-in in the package. Furthermore, we provide a powerful tool for
+the users to extend the range of available problems in a way that suits their
+needs.
+
+Due to this possibility of extension, the users are able to test specific
+aspects of their architecture of interest. For example, if their problem is
+related to the amount of coherence (the sum of absolute value of off-diagonal
+elements) of the states present during computation, they are able to quickly
+prepare a custom experiment, launch it on desired architectures, gather the
+result, based on which they can decide which specific architecture they should
+use.
+
+Finally, we provide the source code of PyQBench on GitHub~\cite{} under on open
+source license which will allow users to utilize and extend our package in their
+specific applications.
 

### 2023-03-14 txt/manuscript.tex
poprawki

@@
 \begin{abstract}
+	\todo[inline]{kod w mathematice final measurement.nb --> zczekałtować}
 We introduce PyQBench, an innovative open-source framework for benchmarking
@@
 
-In this paper, we introduce yet another method for benchmarking gate--based devices with a simple
+In this paper, we introduce a different approach to benchmarking gate--based devices with a simple
 operational interpretation. In our method, we test how well the given device is at guessing which of
@@
 Without loss of generality\footnote{Explaining why we can consider only discrimination scheme between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper.
-See \cite{puchala2018strategies} if you are
-interested in the explanation.}, we consider discrimination task between single qubit measurements
+See \cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between single qubit measurements
 $\PP_\Id$, performed in the computational Z-basis, and an alternative measurement $\PP_U$ performed
@@
 
-In general, the discrimination scheme, presented in Fig.~\ref{fig:theoretical_scheme}, requires an
-auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of
-measurements,   $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
-outcome $i$, one chooses another POVM $\mathcal{P}_{V_i}$ and performs it on the second
-qubit, storing the output in $j$. Finally, if $j=0$, we guess that the performed measurement is
-$\mathcal{P}_U$, otherwise we guess that it was $\mathcal{P}_\Id$. Naturally, one have to repeat the
+In general, the discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme}, requires an
+auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the 
+measurements,  either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
+outcome $i$, we choose another POVM $\mathcal{P}_{V_i}$ and perform it on the second
+qubit, obtaining the output in $j$. Finally, if $j=0$, we say that the performed measurement is
+$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
 same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
-probability distribution. In PyQBench, we assume that experiment is repeated the same number of
+probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
 times for both $\PP_U$ and $\PP_\Id$.
@@
 	doing this choice, we can run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and
-	measure both qubits. We then discard the results of the circuit for which label $i$ does match
+	measure both qubits. We then discard the results of the circuit for which label $i$ does not match
 	measurement label $k$. Hence, the circuit for postselection looks as depicted in Fig.
@@
 	with both $\PP_U$ and $\PP_\1$. Each circuit has to be run in both variants, one with final
-	measurement $\PP_{V_0}$ and the second with final measurement $\PP_{V_1}$.
+	measurement $\PP_{V_0}$ and the second with the final measurement $\PP_{V_1}$.
 	The experiments can thus be grouped into classes identified by tuples of the form
@@
 
+\todo[inline]{ja rysunki zrobie}
 	\begin{figure}[h!]
@@
 
-\subsubsection{Constructing optimal discrimination scheme}
-
+\todo[inline]{Konrad + ta nazwa sekcji}
+\subsubsection{Importance of the optimal discrimination scheme}
 In principle, the schemes described in the previous section could be used with any choice of
@@
 suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ yields the theoretical upper bound
-of discriminating between two measurements of 1, i.e. on a perfect quantum computer you will always
-make a correct guess. Then, on real hardware, we might obtain any empirical value in range $[0.5,
-1]$. On the other hand, if we choose the components of our scheme such that the successful
-discrimination probability is only 0.6, the possible range of empirically obtainable probabilities
-is only $[0.5, 0.6]$. Hence, in the second case, the discrepancy between theoretical and empirical
+of discriminating between two measurements of one, i.e. on a perfect quantum computer you will always
+make a correct guess. Then, on real hardware, we might obtain any empirical value in range $\left[\frac{1}{2},
+1\right]$. On the other hand, if we choose the components of our scheme such that the successful
+discrimination probability is only $\frac{3}{5}$, the possible range of empirically obtainable probabilities
+is only $\left[\frac{1}{2}, \frac{3}{5}\right]$. Hence, in the second case, the discrepancy between theoretical and empirical
 results will be less pronounced.
 
+\subsubsection{Constructing optimal discrimination scheme}
 The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$,
@@
 \begin{equation}
-\|\PP\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left(\PP \otimes \1\right) (\proj{\psi}) \|_1.
+\|\PP - \QQ\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left( (\PP - \QQ) \otimes \1\right) (\proj{\psi}) \|_1.
 \end{equation}
@@
 The parametrized Fourier family of measurements is defined as a set of the measurements
-$\{\PP_{U_\phi}\colon \phi \in [0, 2\pi]\}$, where $U_\phi$ is defined as follows:
+$\{\PP_{U_\phi}\colon \phi \in [0, 2\pi]\}$, where 
 \begin{equation}
@@
 \end{equation}
-and $H$ is the Hadamard matrix. For each element of this set, the discriminator is a Bell state:
+and $H$ is the Hadamard matrix od dimension two. For each element of this set, the discriminator is a Bell state:
 \begin{equation}
@@
 fine-grained control over the execution of the circuits. For instance, suppose the user wants to
-simulate the discrimination experiment on a noisy simulator. In such a case, he or she can define
+simulate the discrimination experiment on a noisy simulator. In such a case, they can define
 the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
@@
 them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
-backend. An example of such file can be found in \ref{sec:examples}, and the detailed description of
+backend. An example of such file can be found in Section \ref{sec:examples}, and the detailed description of
 the expected format can be found at PyQBench's documentation.
@@
 above into sequences of gates.
+In standard approach, a circuit \todo[inline]{napisac ze circuit zaczyna w stanie 00, lukasz chcial cos o bramkach dosteonych na urzadzeniach, ktore sa typowe itd}
 The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
@@
 	\includegraphics[scale=1.7]{pics/discriminator}
-	\caption{Decomposition of the discriminator $\ket{\psi_0}$. }
+	\caption{Decomposition of the Bell state $\ket{\psi_0}$. }
 	\label{fig:discriminator}
@@
 \begin{equation}
-V_1 = \operatorname{RY}\left(\frac{3}{4} \pi \right) \cdot \operatorname{X}.
+V_1 = \operatorname{RY}\left(\frac{3}{4} \pi \right) \operatorname{X}.
 \end{equation}
@@
 
-For the rest of this example, Let us focus only on the postselection case, as the direct sum case is
+For the rest of this example we focus only on the postselection case, as the direct sum case is
 analogous. We continue by importing two more functions from PyQBench.
@@
 \end{lstlisting}
-The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
+A sample CSV file is provided below:
+\begin{table}[ht!]
+\begin{center}
+	\begin{tabular}{|c c c c c c|} 
+		\hline
+		target & ancilla & phi & ideal$\_$prob  & disc$\_$prob & mit$\_$disc$\_$prob \\ [0.5ex] 
+		\hline\hline
+		0 & 1 & 0 & 0.5 & 0.46 & 0.45  \\ 
+		\hline
+		0 & 1 & 3.14 & 1 & 0.95 & 0.98  \\
+		\hline
+		0 & 1 & 6.28 & 0.5 & 0.57 & 0.58  \\
+		\hline
+		1 & 2 & 0 & 0.5  & 0.57 & 0.57 \\
+		\hline
+		1 & 2 & 3.14 & 1 & 0.88 & 0.94  \\ 
+		\hline
+		1 & 2 & 6.28 & 0.5 & 0.55 & 0.56  \\ 
+		\hline
+	\end{tabular}
+\caption{The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
 	\texttt{ideal\_prob}, \texttt{disc\_prob} and, optionally, \texttt{mit\_disc\_prob}. Each row in the
@@
 	\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
-Mthree error mitigation \cite{mthree, mthreepublication}, if it was applied.
-A sample CSV file is provided below:
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1]{results/async_result}
-	\caption{Tabulated results}
+	Mthree error mitigation \cite{mthree, mthreepublication}, if it was applied.}
 \label{fig:tabulateresults}
-\end{figure}
+\end{center}
+\end{table}
 
@@
 
-Finally, we provide the source code of PyQBench on GitHub~\cite{} under on open
+Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under on open
 source license which will allow users to utilize and extend our package in their
@@
 \begin{thebibliography}{00}
-\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and beyond." Quantum 2 (2018): 79.
+\bibitem{preskill} Preskill, J. "Quantum Computing in the NISQ era and beyond." Quantum 2 (2018): 79.
 \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
@@
 Quantum Science and Technology, 3(3), 030503.
-\bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
-%\bibitem{arute2019quantum} Arute, F., Arya, K., Babbush, R., Bacon, D., Bardin, J.
-C., Barends, R., ...
-Martinis, J.
-M.
-(2019).
-Quantum supremacy using a programmable superconducting processor.
-Nature, 574(7779), 505-510.
-%\bibitem{neill2018blueprint}
-%Neill, C., Roushan, P., Kechedzhi, K., Boixo, S., Isakov, S.
-V., Smelyanskiy, V., ...
-Martinis, J.
-M.
-(2018).
-A blueprint for demonstrating quantum supremacy with superconducting qubits.
-Science, 360(6385), 195-199.
+\bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from nisq devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
@@
 \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
-%
-%\bibitem{ghz}
-%Greenberger, D. M., Horne, M. A., Zeilinger, A. (1989). Bell’s theorem, Quantum Theory, and Conceptions of the Universe.
-\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for
+\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. "Strategies for
 optimal single-shot discrimination of quantum measurements." Physical Review A
 98.4 (2018): 042103.
-\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
+\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge university press.
 \bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
@@
 Scientific Reports, 11(1), 3623.
-\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
-\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
-
-\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking
-gate-based quantum computers." Computer Physics Communications 220 (2017):
-44-55.
-
-\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication
-protocols as a benchmark for programmable quantum computers." Quantum
-Information Processing 18.1 (2019): 1-23.
+\bibitem{hausdorff} Hausdorff, F. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
+\bibitem{toeplitz} Toeplitz, O. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
+\bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H.
+(2017).
+Benchmarking gate-based quantum computers.
+Computer Physics Communications, 220, 44-55.
+\bibitem{zhukov2019quantum} Zhukov, A.
+A., Kiktenko, E.
+O., Elistratov, A.
+A., Pogosov, W.
+V.,  Lozovik, Y.
+E.
+(2019).
+Quantum communication protocols as a benchmark for programmable quantum computers.
+Quantum Information Processing, 18(1), 31.
 \bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
@@
 qubits." Physical Review A 99.6 (2019): 062323.
-\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative
-modeling approach for benchmarking and training shallow quantum circuits." npj
-Quantum Information 5.1 (2019): 1-9.
+\bibitem{benedetti2018generative} BBenedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y.,  Perdomo-Ortiz, A.
+(2019).
+A generative modeling approach for benchmarking and training shallow quantum circuits.
+npj Quantum Information, 5(1), 45.
 
@@
 \end{lstlisting}
-If backend is asynchronous, the output will contain intermediate data
+If the backend is asynchronous, the output will contain intermediate data
 containing, amongst others, job ids correlated with the circuit they

### 2023-03-21 txt/manuscript.tex
change picyures
Remove TODO about mathematica notebook

@@
 \begin{abstract}
-	\todo[inline]{kod w mathematice final measurement.nb --> zczekałtować}
+
 We introduce PyQBench, an innovative open-source framework for benchmarking
@@
 
-\todo[inline]{ja rysunki zrobie}
 	\begin{figure}[h!]
@@
 	One can see why such a circuit is equivalent to the original discrimination scheme.
-	If we rewrite the $V_0^\dagger \oplus V_1^\dagger$ as follows:
+	If we rewrite the block-diagonal matrix $V_0^\dagger \oplus V_1^\dagger$ as follows:
 	\begin{equation}
 		\label{eq:directsum}
-		V_0^\dagger \oplus V_1^\dagger = \proj{0}\otimes V_0^\dagger + \proj{1} \otimes V_1^\dagger
-	\end{equation}
-	We can see that the direct sum in Eq. \eqref{eq:directsum} commutes with the measurement on the
+		V_0^\dagger \oplus V_1^\dagger = \proj{0}\otimes V_0^\dagger + \proj{1} \otimes V_1^\dagger,
+	\end{equation}
+	we can see that the direct sum in Eq. \eqref{eq:directsum} commutes with the measurement on the
 	first qubit. Thanks to this, we can switch the order of operations to obtain the circuit from

### 2023-03-21 txt/manuscript.tex
Remove bunch of other todos

@@
  \end{equation}
- For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as
- follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
+ For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as follows (see also \texttt{mathematics/optimal\_final\_measurement\_discrimination.nb} in the source code repository):
  \begin{equation}
@@
 	Hence, the explicit form of $V_0$ and $V_1$ is given as
-	follows: \todo[inline]{udostepniamy ten plik nb z obliczeniami? (see also \texttt{one-qubit.nb}}
+	follows:
 	\begin{equation}

### 2023-03-21 txt/manuscript.tex
Address the remaining todos

@@
 
-\todo[inline]{Konrad + ta nazwa sekcji}
-\subsubsection{Importance of the optimal discrimination scheme}
+\subsubsection{Importance of choosing the optimal discrimination scheme}
 In principle, the schemes described in the previous section could be used with any choice of
@@
 \subsubsection{Constructing optimal discrimination scheme}
-The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$,
-in terms of their distance with the use of the diamond norm
+To construct the optimal discrimination scheme, one starts by calculating the probability of correct discrimination.
+Using the celebrated result by Helstrom~\cite{helstrom1976quantum}, one finds that the  optimal probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$, is
 \begin{equation}
@@
 \end{equation}
-The quantum state $\ket{\psi_0}$ which maximizes the diamond norm is called the
-\emph{discriminator}. Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is
+The quantum state $\ket{\psi_0}$ maximizing the diamond norm above is called the
+\emph{discriminator}, and can be computed e.g. using semidefinite programming (SDP)
+\cite{watrous,watrous2021simplier}. Furthermore,  using the proof of the Holevo-Helstrom theorem, it is
 possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
@@
 \end{equation}
-To use the above benchmarking scheme in PyQBench, we first need to decompose the unitary matrices
-above into sequences of gates.
-In standard approach, a circuit \todo[inline]{napisac ze circuit zaczyna w stanie 00, lukasz chcial cos o bramkach dosteonych na urzadzeniach, ktore sa typowe itd}
+To use the above benchmarking scheme in PyQBench, we first need to construct circuits that can be executed by actual hardware.
+To this end, we need to represent each of the unitaries as a sequence of standard gates, keeping in mind that quantum circuits start execution from  $\ket{00}$ state.
 The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).

### 2023-03-21 txt/manuscript.tex
Remove outrageous pagebreak
Fix typo

@@
 		\centering
-		\includegraphics[scale=1.5]{pics/controlled_unitary}
+		\includegraphics[width=0.8\textwidth]{pics/controlled_unitary}
 
@@
 \end{figure}
-
-\pagebreak
 
@@
 
-Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under on open
+Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under an open
 source license which will allow users to utilize and extend our package in their

### 2023-03-22 txt/manuscript.tex
Add missing article

@@
 To use the above benchmarking scheme in PyQBench, we first need to construct circuits that can be executed by actual hardware.
-To this end, we need to represent each of the unitaries as a sequence of standard gates, keeping in mind that quantum circuits start execution from  $\ket{00}$ state.
+To this end, we need to represent each of the unitaries as a sequence of standard gates, keeping in mind that quantum circuits start execution from the  $\ket{00}$ state.
 The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).

### 2023-03-23 txt/manuscript.tex
poprawki

@@
 already exist several approaches.
-One could mention randomized benchmarking \cite{liu2022sampling, knill2007randomized, knill2008randomized, wallman2014randomized, helsen2022general,
+One could mention randomized benchmarking \cite{liu2022sampling, knill2008randomized, wallman2014randomized, helsen2022general,
 	cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume}.
-%or cross-entropy benchmarking \cite{arute2019quantum, neill2018blueprint}.
 
@@
 \end{equation}
-and $H$ is the Hadamard matrix od dimension two. For each element of this set, the discriminator is a Bell state:
+and $H$ is the Hadamard matrix of dimension two. For each element of this set, the discriminator is a Bell state:
 \begin{equation}
@@
 	\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
-	Mthree error mitigation \cite{mthree, mthreepublication}, if it was applied.}
+	\texttt{Mthree} error mitigation \cite{mthree, mthreepublication}, if it was applied.}
 \label{fig:tabulateresults}
@@
 arXiv preprint arXiv:2105.05232.
-\bibitem{knill2007randomized} Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
+\bibitem{knill2008randomized}
+Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
 B., Jost, J.
-D., ...
-Wineland, D.
+D., Langer, C., Ozeri, R., Seidelin, S.,  Wineland, D.
 J.
@@
 Physical Review A, 77(1), 012307.
-\bibitem{knill2008randomized}
-Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., ...  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.
 \bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
@@
 M., Cross, A., Egger, D.
-J., ...
-Temme, K.
+J., Filipp, S., Fuhrer, A., Gambetta, J.
+M., Ganzhorn, M., Kandala, A., Mezzacapo, A., M{\"u}ller, P., Riess, W., Salis, G., Smolin, J., Tavernelli, I.,  Temme, K.
 (2018).
@@
 Quantum Science and Technology, 3(3), 030503.
-\bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from nisq devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
+\bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
@@
 S., Smith, K.
-N., Viszlai, J., ...
-Chong, F.
+N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F.
 T.
-(2022, April).
+(2022).
 Supermarq: A scalable quantum benchmark suite.
@@
 and Raphael C. Pooser. "Generative model benchmarks for superconducting
-qubits." Physical Review A 99.6 (2019): 062323.
+qubits." Physical Review A 99.6 (2019).
 \bibitem{benedetti2018generative} BBenedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y.,  Perdomo-Ortiz, A.
@@
 A generative modeling approach for benchmarking and training shallow quantum circuits.
-npj Quantum Information, 5(1), 45.
+Quantum Information, 5(1), 45.
 
@@
  \end{equation}
- For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as follows (see also \texttt{mathematics/optimal\_final\_measurement\_discrimination.nb} in the source code repository):
+ For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as follows (see also \texttt{mathematics/optimal\_final\_measurement\_ \\ discrimination.nb} in the source code repository):
  \begin{equation}
@@
 \end{lstlisting}
-Finally, if the status of jobs is DONE, we resolve the measurements from the
+Finally, if the status of jobs is \texttt{DONE}, we resolve the measurements from the
 submitted jobs obtaining the following file.

### 2023-03-23 txt/manuscript.tex
Fix biblio

@@
 \begin{thebibliography}{00}
-\bibitem{preskill} Preskill, J. "Quantum Computing in the NISQ era and beyond." Quantum 2 (2018): 79.
+\bibitem{preskill} Preskill, J. Quantum Computing in the NISQ era and beyond. Quantum 2 (2018): 79.
 \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
@@
 Supermarq: A scalable quantum benchmark suite.
-In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp.
-587-603).
+In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) 587-603.
 IEEE.
@@
 \bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
-\bibitem{volume-in-practice} The web resource at\url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
+\bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
 \bibitem{cross-entropy-bench} The web resource at
 \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
-\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. "Strategies for
-optimal single-shot discrimination of quantum measurements." Physical Review A
+\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. Strategies for
+optimal single-shot discrimination of quantum measurements. Physical Review A
 98.4 (2018): 042103.
 \bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge university press.
-\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
+\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
 \bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
@@
 Scientific Reports, 11(1), 3623.
-\bibitem{hausdorff} Hausdorff, F. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
-\bibitem{toeplitz} Toeplitz, O. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
+\bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
+\bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
 \bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H.
@@
 \bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
-and Raphael C. Pooser. "Generative model benchmarks for superconducting
-qubits." Physical Review A 99.6 (2019).
+and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
+qubits. Physical Review A 99(6), 062323.
 \bibitem{benedetti2018generative} BBenedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y.,  Perdomo-Ortiz, A.

### 2023-03-24 txt/manuscript.tex
Fix last bibitem
bibliografia
biblio

@@
 \begin{thebibliography}{00}
-\bibitem{preskill} Preskill, J. Quantum Computing in the NISQ era and beyond. Quantum 2 (2018): 79.
+\bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.
 \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
@@
 \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
-\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. Strategies for
+\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for
 optimal single-shot discrimination of quantum measurements. Physical Review A
-98.4 (2018): 042103.
-\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge university press.
+98.4, 042103.
+\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.
 \bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
@@
 \bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
+\bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.
 \bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
@@
 qubits. Physical Review A 99(6), 062323.
-\bibitem{benedetti2018generative} BBenedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y.,  Perdomo-Ortiz, A.
+\bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A.
 (2019).
 A generative modeling approach for benchmarking and training shallow quantum circuits.
-Quantum Information, 5(1), 45.
+npj Quantum Information, 5(1), 45.
 

### 2023-03-31 software_x_submission/manuscript.tex
Prepare files for software_x_submission

--- 2023-03-23 txt/manuscript.tex
@@
 
-\begin{thebibliography}{00}
-\bibitem{preskill} Preskill, J. Quantum Computing in the NISQ era and beyond. Quantum 2 (2018): 79.
-\bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
-\bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
-\bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
-\bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
-\bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
-\bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
-\bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
-\bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
-\bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
-\bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
-\bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
-\bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
-\bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
-\bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
-\bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
+% \begin{thebibliography}{00}
+% \bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.
+% \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
+% \bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
+% \bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
+% \bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
+% \bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
+% \bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
+% \bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
+% \bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
+% \bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
+% \bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
+% \bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
+% \bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
+% \bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
+% \bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
+% \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
 (2021).
@@
 arXiv preprint arXiv:2105.05232.
-\bibitem{knill2008randomized}
-Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
+% \bibitem{knill2008randomized}
+% Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
 B., Jost, J.
@@
 Physical Review A, 77(1), 012307.
-\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
-\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
-\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
-\bibitem{cross2019validating}
-Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
-\bibitem{moll2018quantum}
-Moll, N., Barkoutsos, P., Bishop, L.
+% \bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
+% \bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
+% \bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
+% \bibitem{cross2019validating}
+% Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
+% \bibitem{moll2018quantum}
+% Moll, N., Barkoutsos, P., Bishop, L.
 S., Chow, J.
@@
 Quantum Science and Technology, 3(3), 030503.
-\bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
-	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
-\bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
-	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
+% \bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S.
+(2022).
+Quantum volume in practice: What users can expect from NISQ devices.
+IEEE Transactions on Quantum Engineering, 3, 1-19.
+% 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
+% \bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
+% 	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
 S., Smith, K.
@@
 Supermarq: A scalable quantum benchmark suite.
-In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) 587-603.
+In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp.
+587-603).
 IEEE.
-\bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
-\bibitem{qiskit-randomized} The web resource at
-\url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
-\bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
-\bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
-\bibitem{cross-entropy-bench} The web resource at
-\url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
-\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. Strategies for
-optimal single-shot discrimination of quantum measurements. Physical Review A
-98.4 (2018): 042103.
-\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge university press.
-\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
-\bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
-\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-\bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
-\bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
-\bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
-\bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
-\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
-\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
-\bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
-\bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
-\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
+% \bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
+% \bibitem{qiskit-randomized} The web resource at
+% \url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
+% \bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
+% \bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
+% \bibitem{cross-entropy-bench} The web resource at
+% \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
+% \bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for
+% optimal single-shot discrimination of quantum measurements. Physical Review A
+% 98.4, 042103.
+% \bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.
+% \bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
+% \bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
+% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
+% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
+% \bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
+% \bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
+% \bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
+% \bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
+% \bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
+% \bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
+% \bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
+% \bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
+% \bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.
+% \bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
 (2021).
@@
 Scientific Reports, 11(1), 3623.
-\bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
-\bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
-\bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H.
+% \bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
+% \bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
+% \bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H.
 (2017).
@@
 Computer Physics Communications, 220, 44-55.
-\bibitem{zhukov2019quantum} Zhukov, A.
+% \bibitem{zhukov2019quantum} Zhukov, A.
 A., Kiktenko, E.
@@
 Quantum Information Processing, 18(1), 31.
-\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
-and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
-qubits. Physical Review A 99(6), 062323.
-\bibitem{benedetti2018generative} BBenedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y.,  Perdomo-Ortiz, A.
+% \bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
+% and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
+% qubits. Physical Review A 99(6), 062323.
+% \bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A.
 (2019).
 A generative modeling approach for benchmarking and training shallow quantum circuits.
-Quantum Information, 5(1), 45.
-
-\end{thebibliography}
+npj Quantum Information, 5(1), 45.
+
+% \end{thebibliography}
+
+\bibliographystyle{unsrt}
+\bibliography{references}
 

### 2023-04-11 txt/manuscript2.tex
Initial work on cutting irrelevant part from the manuscript

--- 2023-03-31 software_x_submission/manuscript.tex
@@
 
-\section{Discrimination scheme for parameterized Fourier family and implementation}
-\label{sec:fourier}
-So far, we only discussed how the discrimination is performed assuming that all needed components
-$\ket{\psi_0}$, $V_0$, and $V_1$ are known. In this section, we provide a concrete example using
-parametrized Fourier family of measurements.
-
-The parametrized Fourier family of measurements is defined as a set of the measurements
-$\{\PP_{U_\phi}\colon \phi \in [0, 2\pi]\}$, where 
-\begin{equation}
-U_\phi = H
-\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger,
-\end{equation}
-and $H$ is the Hadamard matrix of dimension two. For each element of this set, the discriminator is a Bell state:
-\begin{equation}
-\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \left( \ket{00} + \ket{11} \right).
-\end{equation}
-Observe that $\ket{\psi_0}$ does not depend on the angle $\phi$. However, the unitaries $V_0$,
-$V_1$ depend on $\phi$ and take the following form:
-\begin{equation}
-V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
-\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
-	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
-\end{equation}
-\begin{equation}
-V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
-\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
-&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
-\end{equation}
-Finally, the theoretical probability of correct discrimination between von Neumann
-measurements $\PP_{U_\phi}$ and $\PP_{\Id}$ is given by
-\begin{equation}
-p_{\text{succ}}(\PP_{U_\phi}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
-\end{equation}
-We explore the construction of $\ket{\psi_0}$, $V_0$ and $V_1$ for parametrized Fourier family of measurements in
-\ref{app:optimal-probability}.
-
  \section{Software description}
@@
 \texttt{qbench} tool.
-
-\subsection{Using user-defined measurement with \texttt{qbench} package}
-In this example, we will demonstrate how \texttt{qbench} package can be used with user--defined
-measurement. For this purpose, we will use $U = H$ (the Hadamard gate). The detailed calculations
-that lead to the particular form of the discriminator and final measurements can be found in
-\ref{app:hadamard}.
-\noindent
-The explicit formula for discriminator in this example reads:
-\begin{equation}
-\ket{\psi_0} = \frac{1}{\sqrt{2}} (\ket{00} + \ket{11}),
-\end{equation}
-with final measurements being equal to
-\begin{equation}
-V_0 =
-\left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
-\end{equation}
-and \begin{equation}
-V_1 =
-\left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
-\end{equation}
-where \begin{equation}
-\alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} = \cos\left( \frac{3}{8} \pi \right),
-\end{equation}
-\begin{equation}
-\beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} = \sin\left( \frac{3}{8} \pi \right).
-\end{equation}
-To use the above benchmarking scheme in PyQBench, we first need to construct circuits that can be executed by actual hardware.
-To this end, we need to represent each of the unitaries as a sequence of standard gates, keeping in mind that quantum circuits start execution from the  $\ket{00}$ state.
-The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.7]{pics/discriminator}
-	\caption{Decomposition of the Bell state $\ket{\psi_0}$. }
-	\label{fig:discriminator}
-\end{figure}
-For $V_0$ and $V_1$ observe that $V_0 = \operatorname{RY}\left(\frac{3}{4} \pi \right) $, where $\operatorname{RY}$ is rotation gate around the $Y$ axis defined by
-\begin{equation}
-\operatorname{RY}(\theta) =
-\left(\begin{array}{cc} \cos\frac{\theta}{2} & -\sin\frac{\theta}{2} \\ \sin\frac{\theta}{2} & \cos\frac{\theta}{2} \end{array}\right).
-\end{equation}
-To obtain $V_1$  we need only to swap the columns, i.e.
-\begin{equation}
-V_1 = \operatorname{RY}\left(\frac{3}{4} \pi \right) \operatorname{X}.
-\end{equation}
-Finally, the optimal probability of correct discrimination is equal to
-\begin{equation}
-p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{\sqrt{2}}{4}.
-\end{equation}
-We will now demonstrate how to implement this theoretical scheme in PyQBench. For this example we
-will use the Qiskit Aer simulator \cite{aer}. First, we import the necessary functions and classes from
-PyQBench and Qiskit. We also import \texttt{numpy} for the definition of \texttt{np.pi} constant and
-the exponential function. The exact purpose of the imported functions will be described at the point
-of their usage.
-\begin{lstlisting}[language=Python, caption=Imports needed for running benchmarking example]
-import numpy as np
-from qiskit import QuantumCircuit, Aer
-from qbench.schemes.postselection import benchmark_using_postselection
-from qbench.schemes.direct_sum import benchmark_using_direct_sum
-\end{lstlisting}
-To implement the discrimination scheme in PyQBench, we need to define all the necessary components
-as Qiskit instructions. We can do so by constructing a circuit object acting on qubits 0 and 1 and
-then converting them using \texttt{to\_instruction()} method.
-\begin{lstlisting}[language=Python, caption= Defining components for Hadamard experiment]
-def state_prep():
-	circuit = QuantumCircuit(2)
-	circuit.h(0)
-	circuit.cnot(0, 1)
-	return circuit.to_instruction()
-
-def u_dag():
-	circuit = QuantumCircuit(1)
-	circuit.h(0)
-	return circuit.to_instruction()
-
-def v0_dag():
-	circuit = QuantumCircuit(1)
-	circuit.ry(-np.pi * 3 / 4, 0)
-	return circuit.to_instruction()
-
-def v1_dag():
-	circuit = QuantumCircuit(1)
-	circuit.ry(-np.pi * 3 / 4, 0)
-	circuit.x(0)
-	return circuit.to_instruction()
-
-def v0_v1_direct_sum_dag():
-	circuit = QuantumCircuit(2)
-	circuit.ry(-np.pi * 3 / 4, 0)
-	circuit.cnot(0, 1)
-	return circuit.to_instruction()
-\end{lstlisting}
-We now construct a backend object, which in this case is an instance of Aer simulator.
-
-\begin{lstlisting}[language=Python, caption=Defining a backend]
-simulator = Aer.get_backend("aer_simulator")
-\end{lstlisting}
-
-In the simplest scenario, when one does not want to tweak execution details and simply wishes to run
-the experiment on a given backend, everything that is required is now to run
-\texttt{benchmark\_using\_postselection} or \texttt{benchmark\_using\_direct\_sum} function,
-depending on the user preference.
-
-\begin{lstlisting}[language=Python, caption=Simulation benchmark by using postselection]
-postselection_result = benchmark_using_postselection(
-	backend=simulator,
-	target=0,
-	ancilla=1,
-	state_preparation=state_prep(),
-	u_dag=u_dag(),
-	v0_dag=v0_dag(),
-	v1_dag=v1_dag(),
-	num_shots_per_measurement=10000,
-)
-\end{lstlisting}
-
-\begin{lstlisting}[language=Python, caption=Simulation benchmark by using direct sum]
-direct_sum_result = benchmark_using_direct_sum(
-	backend=simulator,
-	target=1,
-	ancilla=2,
-	state_preparation=state_prep(),
-	u_dag=u_dag(),
-	v0_v1_direct_sum_dag=v0_v1_direct_sum_dag(),
-	num_shots_per_measurement=10000,
-)
-\end{lstlisting}
-The \texttt{postselection\_result} and  \texttt{direct\_sum\_result} variables contain now the
-empirical probabilities of correct discrimination. We can compare them to the theoretical value and
-compute the absolute error.
-
-\begin{lstlisting}[language=Python, caption=Examining the benchmark results]
-p_succ = (2 + np.sqrt(2)) / 4
-print(f"Analytical p_succ = {p_succ}")
-print(
-f"Postselection: p_succ = {postselection_result}, abs. error = {p_succ - postselection_result}"
-)
-print(f"Direct sum: p_succ = {direct_sum_result}, abs. error = {p_succ - direct_sum_result}")
-\end{lstlisting}
-
-\begin{lstlisting}
-Analytical p_succ = 0.8535533905932737
-Postselection: p_succ = 0.8559797193791593, abs. error = -0.0024263287858855564
-Direct sum: p_succ = 0.85605, abs. error = -0.0024966094067262468
-\end{lstlisting}
-
-In the example presented above we used functions that automate the whole process -- from the circuit assembly, through running the simulations to interpreting the results.
-But what if we want more control over some parts of this process?
-One possibility would be to add some additional parameters to \texttt{benchmark\_using\_xyz}
-functions, but this approach is not scalable. Moreover, anticipating all possible uses cases
-isimpossible. Therefore, we decided on another approach. PyQBench provides functions performing:
-\begin{enumerate}
-\item Assembly of circuits needed for experiment, provided the components discussed above.
-\item Interpretation of the obtained measurements.
-\end{enumerate}
- The difference between the two approaches is illustrated on the diagrams in Fig. \ref{fig:diagrams}.
-
-\begin{figure}[ht!]
-	\centering
-	\begin{subfigure}[b]{0.9\textwidth}
-		\centering
-		\includegraphics[width=0.8\textwidth]{pics/scheme1}
-%		\caption{$y=x$}
-		\label{fig:simplified}
-	\end{subfigure}
-	\vfill
-	\begin{subfigure}[b]{0.9\textwidth}
-		\centering
-	\includegraphics[width=0.8\textwidth]{pics/scheme2}
-		\label{fig:execution}
-	\end{subfigure}
-	\caption{Differences between simplified (top) and user--controlled (bottom) execution of
-	benchmarks in PyQBench. Compared to simplified benchmarking, in user-controlled benchmarks the
-	user has direct access to the circuits being run, and hence can alter them (e.g. by adding
-	noise) and/or choose the parameters used for executing them on the backend.}
-	\label{fig:diagrams}
-\end{figure}
-
-For the rest of this example we focus only on the postselection case, as the direct sum case is
-analogous. We continue by importing two more functions from PyQBench.
-\begin{lstlisting}[language=Python, caption= Assembling circuits]
-from qbench.schemes.postselection import (
-    assemble_postselection_circuits,
-    compute_probabilities_from_postselection_measurements,
-)
-
-circuits = assemble_postselection_circuits(
-	target=0,
-	ancilla=1,
-	state_preparation=state_prep(),
-	u_dag=u_dag(),
-	v0_dag=v0_dag(),
-	v1_dag=v1_dag(),
-)
-
-\end{lstlisting}
-Recall that for a postselection scheme we have two possible choices of the "unknown" measurement and
-two possible choices of a final measurement, which gives a total of four circuits needed to run the
-benchmark. The function \texttt{assemble\_postselection\_circuits} creates all four circuits and
-places them in a dictionary with keys \texttt{"id\_v0"}, \texttt{"id\_v1"}, \texttt{"u\_v0"},
-\texttt{"u\_v1"}.
-
-We will now run our circuits using noisy and noiseless simulation. We start by creating a noise
-model using Qiskit.
-
-\begin{lstlisting}[language=Python, caption=Adding noise model]
-from qiskit.providers.aer import noise
-
-error = noise.ReadoutError([[0.75, 0.25], [0.8, 0.2]])
-
-noise_model = noise.NoiseModel()
-noise_model.add_readout_error(error, [0])
-noise_model.add_readout_error(error, [1])
-\end{lstlisting}
-Once we have our noise model ready, we can execute the circuits with and without noise. To this end,
-we will use Qiskit’s \texttt{execute} function. One caveat is that we have to keep track which
-measurements correspond to which circuit. We do so by fixing an ordering on the keys in the \texttt{circuits} dictionary.
-\begin{lstlisting}[language=Python, caption=Running  circuits]
-from qiskit import execute
-
-keys_ordering = ["id_v0", "id_v1", "u_v0", "u_v1"]
-all_circuits = [circuits[key] for key in keys_ordering]
-
-counts_noisy = execute(
-	all_circuits,
-	backend=simulator,
-	noise_model=noise_model,
-	shots=10000
-).result().get_counts()
-
-counts_noiseless = execute(
-	all_circuits,
-	backend=simulator,
-	shots=10000
-).result().get_counts()
-\end{lstlisting}
-Finally, we use the measurement counts to compute discrimination probabilities using \texttt{compute\_probabilities\_from\_postselection\_measurements} function.
-
-\begin{lstlisting}[language=Python, caption=Computation probabilities]
-prob_succ_noiseless = compute_probabilities_from_postselection_measurements(
-	id_v0_counts=counts_noiseless[0],
-	id_v1_counts=counts_noiseless[1],
-	u_v0_counts=counts_noiseless[2],
-	u_v1_counts=counts_noiseless[3],
-)
-
-prob_succ_noisy = compute_probabilities_from_postselection_measurements(
-	id_v0_counts=counts_noisy[0],
-	id_v1_counts=counts_noisy[1],
-	u_v0_counts=counts_noisy[2],
-	u_v1_counts=counts_noisy[3],
-)
-
-\end{lstlisting}
-
-We can now examine the results. As an example, in one of our runs, we obtained
-\texttt{prob\_succ\_noiseless = 0.8524401115559386} and \texttt{prob\_succ\_noisy =
-0.5017958400693446}. As expected, for noisy simulations, the result lies further
-away from the target value of \texttt{0.8535533905932737}.
-
-This concludes our example. In the next section, we will show how to use PyQBench's CLI.
 
@@
 \end{lstlisting}
-The experiment file contains the following fields:
-\begin{itemize}
-	\item \texttt{type}: a string describing the type of the experiment. Currently, the only option of  \texttt{type} is \texttt{discrimination-fourier}.
-	\item \texttt{qubits}: a list enumerating pairs of qubits on which the experiment should be run.
-	For configuration in listing \ref{lst:experiment}, the benchmark will run on two pairs of qubits. The first pair is 0 and 1, and
-	the second one is 1 and 2. We decided to describe a pair by using \texttt{target} and
-	\texttt{ancilla} keys rather than using a plain list to emphasize that the role of qubits in the
-	experiment is not symmetric.
-	\item \texttt{angles}: an object describing the range of angles for Fourier parameterized
-	family. The described range is always uniform, starts at the \texttt{start}, ends at
-	\texttt{stop} and contains \texttt{num\_steps} points, including both \texttt{start} and
-	\texttt{stop}. The \texttt{start} and \texttt{stop} can be arithmetic expressions using
-	\texttt{pi} literal. For instance, the range defined in listing \ref{lst:experiment} contains
-	three points: 0, $\pi$ and $2\pi$.
- 	 \item \texttt{gateset}: a string describing the set of gates used in the decomposition of
- 	 circuits in the experiment. The PyQBench contains explicit implementations of circuits The
- 	 possible options are \texttt{[ibmq, lucy, rigetti]}, corresponding to decompositions
- 	 compatible with IBM Q devices, OQC Lucy device, and Rigetti devices. Alternatively, one might
- 	 wish to turn off the decomposition by using a special value \texttt{generic}. However, for this
- 	 to work a backend used for the experiment must natively implement all the gates needed for the
- 	 experiment, as described in \ref{sec:fourier}.
- 	\item \texttt{method}: a string, either \texttt{postselection} or \texttt{direct\_sum}
- 	determining which implementation of the conditional measurement is used.
- 	\item \texttt{num\_shots}: an integer defines how many shots are performed in the experiment for
- 	a particular angle, qubit pair and circuit. Note that if one wishes to compute the total number
- 	of shots in the experiment, it is necessary to take into account that the \texttt{postselection}
- 	method uses twice as many circuits as the \texttt{direct\_sum} method.
-\end{itemize}
 
@@
 
-\subsubsection{Remarks on using the asynchronous flag}
-For backends supporting asynchronous execution, the \texttt{asynchronous} setting can be configured
-to toggle it.
-For asynchronous execution to work, the following conditions have to be met:
-\begin{itemize}
-\item Jobs returned by the backend have unique \texttt{job\_id}.
-\item Jobs are retrievable from the backend using the \texttt{backend.retrieve\_job} method, even from another process (e.g. if the original process running the experiment has finished).
-\end{itemize}
-Since PyQBench cannot determine if the job retrieval works for a given backend, it is the user's
-responsibility to ensure that this is the case before setting \texttt{asynchronous} to \texttt{true}.
-
 \subsubsection{Running the experiment and collecting measurements data}
@@
 \end{lstlisting}
-	The data includes \texttt{target, ancilla, phi},
-	and \texttt{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \texttt{results\_per\_circuit} gives us
-	the following additional information:
-	\begin{itemize}
-		\item  \texttt{name}:  the information which measurement is used during experiment, either
-		string \texttt{"u"} for $\PP_{U}$ or string \texttt{"id"} for $\PP_{\Id}$. In this example
-		we consider $\PP_{\Id}$.
-		\item \texttt{histogram}: the dictionary with measurements' outcomes. The keys represent
-		possible bitstrings, whereas the values are the number of occurrences.
-		\item \texttt{mitigation\_info}:  for some backends (notably for backends corresponding to
-		IBM Q devices), \texttt{backends.properties().qubits} contains information that might be
-		used for error mitigation using the MThree method \cite{mthree, mthreepublication}. If this
-		info is available, it will be stored in the \texttt{mitigation\_info} field, otherwise this field will be absent.
-		\item \texttt{mitigated\_histogram}: the histogram with measurements' outcomes after the error mitigation.
-	\end{itemize}
 
@@
 \bibliography{references}
-
-\appendix
-
-\section{Mathematical preliminaries} \label{app:preliminaries}
-
-Let $\mathcal{M}_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
-the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
-$\mathcal{M}_d$.
-By $\Omega_d$, we will denote the set of quantum states, that is
-positive semidefinite operators having trace equal to one.
-The subset of $\mathcal{M}_d$ consisting of unitary matrices will be denoted
-by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
-$\DD \UU_d$.
-
-We will also need a linear mapping transforming $\mathcal{M}_{d_1}$ into
-$\mathcal{M}_{d_2}$, which will be denoted
-\begin{equation}
-\Phi: \mathcal{M}_{d_1 } \rightarrow \mathcal{M}_{d_2}.
-\end{equation}
-There
-exists a bijection between the set of linear mappings $\Phi$ and the set of matrices $\mathcal{M}_{d_1d_2}$,  known as the Choi-Jamio{\l}kowski isomorphism.
-For a given linear mapping $\Phi$ the corresponding Choi operator $J(\Phi)$ is explicitly written as
-\begin{equation}
-J(\Phi) \coloneqq \sum_{i,j=0}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
-
-We also introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
-and trace preserving (CPTP).
-In this work we will consider a special class of quantum channels, called unitary channels.  A
-quantum channel
-$\Phi_{U}$ is said to be a unitary channel if it has the following form $\Phi_U(\cdot) = U \cdot U^\dagger$ for any $U \in
-\UU_d$.
-
-Let us recall a  general form of a quantum measurement, so called Positive Operator Valued
-Measure (POVM). A POVM $\PP$ is a collection of positive semidefinite operators $\{E_1, \ldots, E_m
-\}$, called effects, that sum up to the identity operator, \ie $ \, \, \sum_{i=1}^m E_i = \1$.
-In PyQBench, we are interested only in von Neumann measurements, that is measurements
-for which all the effects are rank-one projectors. Every such measurement can be
-parameterized by a unitary matrix $U \in \mathcal{U}_d$ with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
-are created by taking $\ket{u_i}$ as  $(i+1)$-th column of the unitary matrix $U$.
-We will denote von Neumann measurements described by the matrix $U$ by $\PP_{U}$.
-The action of
-von Neumann measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
-seen as  a measure-and-prepare quantum channel as follows \begin{equation}
-\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
-\end{equation}
-Moreover, observe that each von Neumann measurement $\PP_{U}$ poses a  composition of a unitary channel $\Phi_{U^\dagger}$ and the maximally dephasing channel $\Delta$, that means $\PP_{U} = \Delta \circ \Phi_{U^\dagger}$.
-
-We need to also briefly discuss about the distance between quantum operations. From \cite[Theorem 1]{puchala2018strategies}, the distance between measurements $\PP_U$ and
-$\PP_\Id$ can be expressed in the notion of diamond norm, that is
-\begin{equation}
-\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} -
-\Phi_\Id\|_\diamond.
-\end{equation} To express the distance between unitary channels, we need to introduce the definition of numerical range \cite{numericalrangle}. The set \begin{equation}
-W(A) =\{\bra{x}A\ket{x}: \ket{x} \in
-\mathbb{C}^d, \;
-\;\braket{x}{x}=1\}
-\end{equation}
-is called the numerical range of  a given matrix $A \in \mathcal{M}_d$.
-The detailed properties of the numerical range and its generalizations we can read on the website~\cite{nr}.
-
-Due to the definition of $W(A)$, the distance between two unitary channels $\Phi_{U} $ and $\Phi_\Id$
-can be written as
-\begin{equation}
-\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-\end{equation}
-where $\nu = \min_{x \in W(U^\dagger)} |x|  $.
-
-\section{Discrimination task for Hadamard gate}\label{app:hadamard}
-For the discrimination task between von Neumann measurements $\PP_{U}$ and $\PP_\Id$, where $U = H$ (the Hadamard gate),  the key is to calculate the diamond norm $\| \mathcal{P}_H - \PP_\Id \|_\diamond$ and
-determine the discriminator $\ket{\psi_0}$.
-Using semidefinite programming \cite{watrous2021simplier}, we obtain
-\begin{equation}
-\| \mathcal{P}_H - \PP_\Id \|_\diamond = \sqrt{2}.
-\end{equation}
-From \cite{lewandowska2021certification} we have
-\begin{equation}
-\| \PP_{H} - \PP_{\Id} \|_\diamond = \| \Phi_{HE_0} - \Phi_{\Id}\|_\diamond,
-\end{equation}
-where $\Phi_{U}$ is a unitary channel and
- $E_0$
-is of the form
-\begin{equation}
-E_0 = \frac{1}{\sqrt{2}} \left( \begin{matrix}
-1 + i & 0  \\  0 & -1-i
-\end{matrix} \right).
-\end{equation}
-Next, in order to construct the discriminator $\ket{\psi_0}$ we use Lemma 5 and the proof of Theorem 1 in \cite{puchala2018strategies}. We show that there exist states
- $\rho_1 $  and $\rho_2$ of the form $ \rho_1  = \frac{1}{2} \left( \begin{matrix}
- 1  & i  \\  -i & 1
- \end{matrix} \right)  $  and $\rho_2 = \frac{1}{2} \left( \begin{matrix}
- 1 & -i \\  i & 1
- \end{matrix} \right), $ respectively. Thus, we construct the quantum state $\rho_0$ as follows:
- \begin{equation}
- \rho_0 = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2 = \frac{1}{2} \left( \begin{matrix}
- 1  &  0  \\  0  & 1
- \end{matrix} \right).
- \end{equation}
- According to the Lemma 5 and the proof of Theorem 1 in \cite{puchala2018strategies} we assume that \begin{equation}
- \ket{\psi_0} = \left.\left| \sqrt{\rho_0^\top}\right\rangle \right\rangle.
- \end{equation}
- It directly implies that
- \begin{equation}
- \ket{\psi_0} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}).  \end{equation}
- Next, from Holevo-Helstrom theorem~\cite{watrous}, we determine the final measurement $\PP_{V_i}$.
- Let us consider \begin{equation}
- X = \left(\PP_{H} \otimes \Id \right)(\proj{\psi_0}) - \left(\PP_{\Id} \otimes \Id \right) (\proj{\psi_0}).
-  \end{equation}
- From the Hahn-Jordan decomposition \cite{watrous}, let us note
- \begin{equation}
- X = P - Q,
- \end{equation}
- where $P, Q \ge 0 $.
- Let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$,
- respectively. Observe, that $P $ and $Q$ are block-diagonal.  Then,  $\Pi_P$ and $\Pi_Q$ have the following forms
- \begin{equation}
- \Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right),
- \end{equation}
- and
- \begin{equation}
- \Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right).
- \end{equation}
- Hence, we define $V_0$ as
- \begin{equation}
- \begin{cases} \ket{x_p} =  V_0  \ket{0} \\  \ket{x_q} =  V_0 \ket{1} \end{cases}
- \end{equation}
- and $V_1$ as
- \begin{equation}
- \begin{cases}
- \ket{y_p} =   V_1 \ket{0} \\
-  \ket{y_q} = V_1  \ket{1}
- \end{cases}.
- \end{equation}
- For the discrimination task between $\PP_{H}$ and $\PP_{\Id}$ the explicit form of $V_0$ and $V_1$ is given as follows (see also \texttt{mathematics/optimal\_final\_measurement\_ \\ discrimination.nb} in the source code repository):
- \begin{equation}
- V_0 =
- \left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
- \end{equation}
- and \begin{equation}
- V_1 =
- \left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
- \end{equation}
- where \begin{equation}
- \alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} = \cos\left( \frac{3}{8} \pi \right),
- \end{equation}
- and
- \begin{equation}
- \beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} = \sin\left( \frac{3}{8} \pi \right).
- \end{equation}
-
-\section{Optimal probability for parameterized Fourier family} \label{app:optimal-probability}
-Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
-Assume that the unitary matrix $U$ is of the form
-\begin{equation}
-U = H
-\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
-\end{equation}
-where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
-In this section we present theoretical probability of correct
-discrimination between these measurements. To do that, we will present an auxiliary lemma.
-\begin{lemma}\label{lemma:min-e-optimal}
-	Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let
-	$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds
-	\begin{equation}
-	\min_{E \in \diaguni_2} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond = \|\Phi_{U} -
-	\Phi_\Id\|_\diamond,
-	\end{equation}
-\end{lemma}
-
-\begin{proof} Recall that the distance between two unitary channels is given by
-	$
-	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
-	$
-	where $\nu = \min_{x \in W(U^\dagger)} |x|  $ for any $U \in \mathcal{U}_d$.
-	For $U = H
-	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger$ the readers briefly observe that  $\nu^2 = 1 - \frac{|1 - e^{-i \phi} |^2 }{4} = 1 - \frac{|1 - e^{i \phi} |^2 }{4}$. So,
-	\begin{equation}
-	\|  \Phi_U  - \Phi_{\1} \|_\diamond = | 1 - e^{i \phi} |.
-	\end{equation}
-	It implies that it is enough to prove  \begin{equation}
-	\min_{E \in \diaguni_2} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond  = | 1 - e^{i \phi} |.
-	\end{equation}
-	This condition is equivalent to show that for every $E \in \diaguni_2$
-	\begin{equation}
-	 \nu_{E} \le  \frac{|1 + e^{i \phi} | }{2},
-	\end{equation}
-	where $\nu_E = \min_{x \in W(U^\dagger E)} |x|. $
-
-	The celebrated Hausdorf-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
-	$W(A)$ of any matrix $A \in \mathcal{M}_d$ is a convex set, and therefore we have
-	\begin{equation}
-	W(A) = \{ \tr(A \rho): \rho \in \Omega_d\}.
-	\end{equation}
-	So, we can assume that
-	\begin{equation}
-	\min_{\ket{x} \in \mathbb{C}^2:   \proj{x} = 1} |\bra{x}U^\dagger\ket{x}| =
-	\min_{\rho \in \Omega_2} |\tr(U^\dagger\rho)|.
-	\end{equation}
-	Then, we have
-	\begin{equation}
-	 \nu_{E}  =   \min_{\rho \in
-		\Omega_2} \left| \tr \left( \rho U E \right) \right|.
-	\end{equation}
-	For that, our task is reduced to show that for every  $E \in \diaguni_2$ there exists $\rho \in \Omega_2$ such that
-	\begin{equation}
- | \tr \left(\rho U E\right) | \le \frac{|1 + e^{i \phi} | }{2}.
-	\end{equation}
-
-	Let us define $E = \left(\begin{array}{cc}E_0&0\\0&E_1\end{array}\right)  $
-	and take $\rho =
-	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right) $.
-	From spectral theorem, let us decompose $U$ as
-	\begin{equation}
-	U= \lambda_0 \ketbra{x_0}{x_0} + \lambda_1 \ketbra{x_1}{x_1},
-	\end{equation}
-	where  for eigenvalue $\lambda_0 = 1$, the corresponding
-	eigenvector is
-	of the form $\ket{x_0} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_1= e^{i \phi}$ we have $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
-	$.
-	Then, for every $ E \in \diaguni_2 $ we have
-	\begin{equation}
-	\begin{split}
- | \tr (\rho U E) | & =   \frac{1}{2}  \left| \tr \left(
-	H \diag(1, e^{i\phi}) H^\dagger E \right) \right| =
-	\frac{1}{2} \left| \tr\left((   \proj{x_0} +e^{i \phi}\proj{x_1} ) E \right)
-	\right| \\& =
-	\frac{1}{2} \left|  \bra{x_0} E \ket{x_0} +  e^{i \phi}\bra{x_1} E \ket{x_1}
-	\right| =
-	\frac{1}{2} \left| \frac{E_0 + E_1}{2} + e^{i \phi } \frac{E_0+E_1}{2} \right|
-	\\& =
-	\frac{\left| 1+ e^{i \phi } \right|}{2} \left| \frac{E_0 + E_1}{2} \right| \le
-\frac{|1 + e^{i \phi} | }{2},
-	\end{split}
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-\begin{theorem}\label{th:probability}
-	The optimal probability of correct discrimination between von Neumann
-	measurements $\PP_U$ and $\PP_{\Id}$ for $U = H \diag(1, e^{i \phi}) H^\dagger$,
-	where $\phi \in [0, 2\pi)$ is given by
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
-	\end{equation}
-\end{theorem}
-
-\begin{proof}
-	From Holevo-Helstrom theorem, we obtain
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{1}{4} \| \PP_{U} - \PP_{\Id} \|_\diamond.
-	\end{equation}
-	From~\cite[Theorem 1]{puchala2018strategies}, we have
-	\begin{equation}
-	\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond.
-	\end{equation}
-	From Lemma~\ref{lemma:min-e-optimal},  we know that for
-	$U =  H \diag(1, e^{i \phi}) H^\dagger$,  it also holds that
-	\begin{equation}
-	\min_{E \in \diaguni_2} \|\Phi_{UE} -
-	\Phi_\Id\|_\diamond = \|\Phi_{U} -
-	\Phi_\Id\|_\diamond,
-	\end{equation} which is exactly equal to
-	\begin{equation}
-	\|\Phi_{U} -
-	\Phi_\Id\|_\diamond = 2\sqrt{1 - \nu^2} = |1-e^{i   \phi }|.
-	\end{equation}
-	It implies that
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1-e^{i \phi}|}{4},
-	\end{equation} which completes the proof.
-\end{proof}
-
-\section{Optimal discrimination strategy for parameterized Fourier family} \label{app:optimal-strategy}
-
-In this Appendix we create the optimal
-theoretical strategy of  discrimination between $\PP_{U}$ and $\PP_{\Id}$.
-To indicate the optimal strategy, we will present two propositions.
-The first one is concentrated around the discriminator as the optimal input state of discrimination strategy, whereas the second one describes the optimal final measurement.
-
-\begin{proposition}\label{prop-discrim}
-	Consider the problem of discrimination between von Neumann measurements $\PP_U$
-	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0,
-	2\pi)$.  The  discriminator has the form
-	\begin{equation}
-	\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
-	\end{equation}
-\end{proposition}
-
-\begin{proof}
-	Let $U = H\diag(1, e^{i \phi}) H^\dagger, \phi \in [0,
-	2\pi)$ be decomposed as
-	\begin{equation}
-	U= \lambda_0 \ketbra{x_0}{x_0} + \lambda_1 \ketbra{x_1}{x_1},
-	\end{equation}
-	where  for eigenvalue $\lambda_0 = 1$, the corresponding
-	eigenvector is
-	of the form $\ket{x_0} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]
-	$,
-	whereas for  $\lambda_1 = e^{i \phi}$ we have $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]
-	$.
-	For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
-	\begin{equation}
-	\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) J(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
-	Hence, we obtain
-	\begin{equation}
-	\begin{split}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond
-	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right)
-	J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1
-	\\
-	& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right)
-	\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top
-\left( \Id \otimes \sqrt{\rho} \right) 	\right\|_1  \\
-	& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes
-	\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
-	\\
-	& = \max_{\rho \in \Omega_2} \sum_{i=0}^{1} \left\| \sqrt{\rho}  \left(
-	\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1.
-	\end{split}
-	\end{equation}
-	One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x},
-	\ket{y}$ the following equation holds~\cite{watrous}
-	\begin{equation}
-	\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha
-		\beta |\braket{x}{y}|^2}.
-	\end{equation}
-	By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho}
-		\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho}
-		\ket{i} \|}$ we have
-	\begin{equation}
-	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2}
-	\sum_{i=0}^{1} \sqrt{\left( \bra{\bar{u_i}} \rho \ket{\bar{u_i}} + \bra{i} \rho \ket{i
-		}\right)^2 - 4 | \bra{\bar{u_i}} \rho \ket{i} |^2}.
-	\end{equation}
-	Let us take  $\rho_0 =   \frac{1}{2}
-	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
-	\begin{equation}
-	\begin{split}
-	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond
-	&\ge \sum_{i=0}^1
-	\sqrt{\left(\bra{\bar{u_i}}\rho_0\ket{\bar{u_i}} + \bra{i} \rho_0 \ket{i} \right)^2 -
-		4|\bra{i}\rho_0\ket{\bar{u_i}}|^2}  \\
-	&= \sum_{i=0}^1  \sqrt{ 1 -  \left| \bra{i}  U \ket{i }\right|^2}
-	\\
-	&=\sum_{i=0}^1  \sqrt{1 -  \left| 1 \cdot \braket{i}{u_0}
-		\braket{u_0}{i} + e^{i \phi} \cdot\braket{i}{u_1} \braket{u_1}{i}\right|^2} \\
-	&= \sum_{i=0}^1
-	\sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 }
-	= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
-	&= |1-e^{i \phi }|.
-	\end{split}
-	\end{equation}
-	Due to Theorem \ref{th:probability} and the following equality
-	\begin{equation}
-	\begin{split}
- \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left(
-	\Id \otimes \sqrt{\rho} \right) \|_1 = \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top
-	\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1,
-	\end{split}
-	\end{equation}
-the discriminator $\ket{\psi_0}$
- is equal to  \begin{equation}
-	\ket{\psi_{0}} =  | \sqrt{\rho_0}^\top
-	\rangle \rangle  = \frac{1}{\sqrt{2} } |
-	\Id_2 \rangle \rangle,
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-\begin{proposition}\label{prop:optimal-measurement}
-	Consider the problem of discrimination between von Neumann measurements $\PP_U$
-	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0,
-	2\pi)$.
-	The   controlled unitaries $V_0$ and $V_1$
-	have the form
-	\begin{equation}
-	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
-	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
-		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
-	\end{equation}
-	and
-	\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
-	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
-	&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
-	\end{equation}
-\end{proposition}
-
-\begin{proof}
-	From Proposition~\ref{prop-discrim} we obtain the exact form of discriminator given by
-	\begin{equation}
-	\ket{\psi_0}  = \frac{1}{\sqrt{2}} |\Id_2
-	\rangle \rangle.
-	\end{equation}
-	Repeating the procedure used to distinguish the von Neumann measurements in the Hadamard basis (see \ref{app:hadamard}), we use the Hahn-Jordan decomposition and then we create the projective operators into the positive and negative part of $X$ matrix.
-	Hence, the explicit form of $V_0$ and $V_1$ is given as
-	follows:
-	\begin{equation}
-	V_0 = \left(
-	\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
-	\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
-		\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
-	\end{array}
-	\right),
-	\end{equation}
-and
-	\begin{equation}
-	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
-	\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4}
-	\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right),
-	\end{equation}
-	where $\phi \in [0,2\pi)$.
-\end{proof}
-
-\section{Output YAML files} \label{app:example}
-In this appendix we present examples of YAML's files obtained from synchronous ans asynchronous experiments. We will start at synchronous case.
-
-\begin{lstlisting}[language=Python, caption=Defining experiment file]
-type: discrimination-fourier
-qubits:
-	- target: 0
-	  ancilla: 1
-	- target: 1
-	  ancilla: 2
-angles:
-	start: 0
-	stop: 2 * pi
-	num_steps: 3
-gateset: ibmq
-method: direct_sum
-num_shots: 100
-\end{lstlisting}
-
-\begin{lstlisting}[language=Python, caption=Defining backend file]
-name: ibmq_quito
-asynchronous: false
-provider:
-	hub: ibm-q
-	group: open
-	project: main
-
-\end{lstlisting}
-
-\begin{lstlisting}[language=Python, caption=Results (synchronous)]
-metadata:
-	experiments:
-		type: discrimination-fourier
-		qubits:
-		- {target: 0, ancilla: 1}
-		- {target: 1, ancilla: 2}
-		angles: {start: 0.0, stop: 6.283185307179586, num_steps: 3}
-		gateset: ibmq
-		method: direct_sum
-		num_shots: 100
-	backend_description:
-		name: ibmq_quito
-		asynchronous: false
-		provider: {group: open, hub: ibm-q, project: main}
-data:
-- target: 0
-  ancilla: 1
-  phi: 0.0
-  results_per_circuit:
-  - name: id
-	histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-		ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-	mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
-  - name: u
-	histogram: {'00': 30, '01': 16, '10': 28, '11': 26}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-		ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-	mitigated_histogram: {'00': 0.2857378991684036, '01': 0.14975297832942433, '10': 0.28142307224788693, '11': 0.2830860502542851}
-- target: 0
-  ancilla: 1
-  phi: 3.141592653589793
-  results_per_circuit:
-  - name: id
-	histogram: {'00': 4, '01': 5, '10': 45, '11': 46}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-		ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-	mitigated_histogram: {'00': 0.011053610583159325, '01': 0.02261276648026373, '10': 0.4593955619936729, '11': 0.5069380609429042}
-  - name: u
-	histogram: {'00': 56, '01': 43, '10': 1}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-		ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-	mitigated_histogram: {'00': 0.5573987337172156, '01': 0.44424718645642625, '10': -0.0016459201736417181}
-- target: 0
-  ancilla: 1
-  phi: 6.283185307179586
-  results_per_circuit:
-  - name: id
-	histogram: {'00': 36, '01': 18, '10': 25, '11': 21}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-		ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-	mitigated_histogram: {'00': 0.3488190312089973, '01': 0.17355281935572894, '10': 0.2505792064871127, '11': 0.22704894294816103}
-  - name: u
-	histogram: {'00': 32, '01': 27, '10': 24, '11': 17}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-		ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-	mitigated_histogram: {'00': 0.3025357275361897, '01': 0.27413673119534815, '10': 0.24313373302688793, '11': 0.18019380824157433}
-- target: 1
-  ancilla: 2
-  phi: 0.0
-  results_per_circuit:
-  - name: id
-	histogram: {'00': 27, '01': 20, '10': 24, '11': 29}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-		ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
-	mitigated_histogram: {'00': 0.2594378169217188, '01': 0.19318893233269735, '10': 0.23035366874292057, '11': 0.3170195820026633}
-  - name: u
-	histogram: {'00': 31, '01': 24, '10': 23, '11': 22}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-		ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
-	mitigated_histogram: {'00': 0.30056875246775644, '01': 0.2438221628798003, '10': 0.22180309809696985, '11': 0.23380598655547338}
-- target: 1
-  ancilla: 2
-  phi: 3.141592653589793
-  results_per_circuit:
-  - name: id
-	histogram: {'00': 5, '01': 4, '10': 50, '11': 41}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-		ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
-	mitigated_histogram: {'00': 0.009552870928837118, '01': 0.007194089383161034, '10': 0.5236791012692514, '11': 0.4595739384187503}
-  - name: u
-	histogram: {'00': 41, '01': 51, '10': 3, '11': 5}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-		ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
-	mitigated_histogram: {'00': 0.4073387714165384, '01': 0.5614614121117936, '10': 0.006431862814564833, '11': 0.024767953657102992}
-- target: 1
-  ancilla: 2
-  phi: 6.283185307179586
-  results_per_circuit:
-  - name: id
-	histogram: {'00': 30, '01': 28, '10': 23, '11': 19}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-		ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
-	mitigated_histogram: {'00': 0.2868459834940102, '01': 0.2919564941384742, '10': 0.22466574543735374, '11': 0.19653177693016174}
-  - name: u
-	histogram: {'00': 15, '01': 20, '10': 36, '11': 29}
-	mitigation_info:
-		target: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-		ancilla: {prob_meas0_prep1: 0.07540000000000002, prob_meas1_prep0: 0.0528}
-	mitigated_histogram: {'00': 0.1187719606657805, '01': 0.1962085394489247, '10': 0.3710195249988589, '11': 0.31399997488643583}
-\end{lstlisting}
-For the same experiment file, we use the flag \texttt{asynchronous: true} to define asynchronous experiment.
-
-\begin{lstlisting}[language=Python, caption=Backend file]
-name: ibmq_quito
-asynchronous: true
-provider:
-	hub: ibm-q
-	group: open
-	project: main
-
-\end{lstlisting}
-If the backend is asynchronous, the output will contain intermediate data
-containing, amongst others, job ids correlated with the circuit they
-correspond to.
-
-\begin{lstlisting}[language=Python, caption=Resolved results]
-metadata:
-	experiments:
-		type: discrimination-fourier
-		qubits:
-		- {target: 0, ancilla: 1}
-		- {target: 1, ancilla: 2}
-		angles: {start: 0.0, stop: 6.283185307179586, num_steps: 3}
-		gateset: ibmq
-		method: direct_sum
-		num_shots: 100
-	backend_description:
-		name: ibmq_quito
-		asynchronous: true
-		provider: {group: open, hub: ibm-q, project: main}
-data:
-- job_id: 63e7f17a17b7ed49ca24e05b
-  keys:
-  - [0, 1, id, 0.0]
-  - [0, 1, u, 0.0]
-  - [0, 1, id, 3.141592653589793]
-  - [0, 1, u, 3.141592653589793]
-  - [0, 1, id, 6.283185307179586]
-  - [0, 1, u, 6.283185307179586]
-  - [1, 2, id, 0.0]
-  - [1, 2, u, 0.0]
-  - [1, 2, id, 3.141592653589793]
-  - [1, 2, u, 3.141592653589793]
-  - [1, 2, id, 6.283185307179586]
-  - [1, 2, u, 6.283185307179586]
-
-\end{lstlisting}
-Finally, if the status of jobs is \texttt{DONE}, we resolve the measurements from the
-submitted jobs obtaining the following file.
-\begin{lstlisting}[language=Python, caption=Results (asynchronous)]
-metadata:
-  experiments:
-	type: discrimination-fourier
-	qubits:
-	- target: 0
-	  ancilla: 1
-	- target: 1
-	  ancilla: 2
-	angles:
-	  start: 0.0
-	  stop: 6.283185307179586
-	  num_steps: 3
-	gateset: ibmq
-	method: direct_sum
-	num_shots: 100
-  backend_description:
-	name: ibmq_quito
-	asynchronous: true
-	provider:
-		group: open
-		hub: ibm-q
-		project: main
-data:
-- target: 0
-  ancilla: 1
-  phi: 0.0
-  results_per_circuit:
-  - name: id
-	histogram:
-		'00': 27
-		'01': 28
-		'10': 18
-		'11': 27
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.052200000000000024
-		prob_meas1_prep0: 0.0172
-	  ancilla:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	mitigated_histogram:
-		'00': 0.254196166145997
-		'01': 0.2790358060520916
-		'10': 0.1732699847244092
-		'11': 0.29349804307750227
-  - name: u
-	histogram:
-		'00': 29
-		'01': 17
-		'10': 30
-		'11': 24
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.052200000000000024
-		prob_meas1_prep0: 0.0172
-	  ancilla:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	mitigated_histogram:
-		'00': 0.2733793468261183
-		'01': 0.1621115306717096
-		'10': 0.3045273800167787
-		'11': 0.2599817424853933
-- target: 0
-  ancilla: 1
-  phi: 3.141592653589793
-  results_per_circuit:
-  - name: id
-	histogram:
-		'00': 3
-		'01': 5
-		'10': 37
-		'11': 55
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.052200000000000024
-		prob_meas1_prep0: 0.0172
-	  ancilla:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	mitigated_histogram:
-		'00': 0.006189545789708441
-		'01': 0.016616709640352317
-		'10': 0.3675478279476653
-		'11': 0.6096459166222741
-  - name: u
-	histogram:
-		'00': 56
-		'01': 42
-		'10': 2
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.052200000000000024
-		prob_meas1_prep0: 0.0172
-	  ancilla:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	mitigated_histogram:
-		'00': 0.55731929321128
-		'01': 0.43367489257574243
-		'10': 0.009005814212977551
-- target: 0
-  ancilla: 1
-  phi: 6.283185307179586
-  results_per_circuit:
-  - name: id
-	histogram:
-		'00': 18
-		'01': 28
-		'10': 30
-		'11': 24
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.052200000000000024
-		prob_meas1_prep0: 0.0172
-	  ancilla:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	mitigated_histogram:
-		'00': 0.15258295844557557
-		'01': 0.2829079190522524
-		'10': 0.3071204587046501
-		'11': 0.25738866379752195
-  - name: u
-	histogram:
-		'00': 32
-		'01': 28
-		'10': 23
-		'11': 17
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.052200000000000024
-		prob_meas1_prep0: 0.0172
-	  ancilla:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	mitigated_histogram:
-		'00': 0.3026150836796529
-		'01': 0.28491749668524724
-		'10': 0.23230862145681827
-		'11': 0.18015879817828173
-- target: 1
-  ancilla: 2
-  phi: 0.0
-  results_per_circuit:
-  - name: id
-	histogram:
-		'00': 27
-		'01': 16
-		'10': 30
-		'11': 27
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	  ancilla:
-		prob_meas0_prep1: 0.07540000000000002
-		prob_meas1_prep0: 0.0528
-	mitigated_histogram:
-		'00': 0.256742095057232
-		'01': 0.15000257115061383
-		'10': 0.29821012040758116
-		'11': 0.29504521338457296
-  - name: u
-	histogram:
-		'00': 34
-		'01': 22
-		'10': 25
-		'11': 19
-	mitigation_info:
-	 target:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	  ancilla:
-		prob_meas0_prep1: 0.07540000000000002
-		prob_meas1_prep0: 0.0528
-	mitigated_histogram:
-		'00': 0.3325088211394024
-		'01': 0.22335261496979697
-		'10': 0.2441636375921354
-		'11': 0.19997492629866526
-- target: 1
-  ancilla: 2
-  phi: 3.141592653589793
-  results_per_circuit:
-  - name: id
-	histogram:
-		'00': 3
-		'01': 9
-		'10': 51
-		'11': 37
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	  ancilla:
-		prob_meas0_prep1: 0.07540000000000002
-		prob_meas1_prep0: 0.0528
-	mitigated_histogram:
-		'00': -0.016627023111853642
-		'01': 0.06778554570877951
-		'10': 0.53899887367658
-		'11': 0.40984260372649417
-  - name: u
-	histogram:
-		'00': 43
-		'01': 45
-		'10': 7
-		'11': 5
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	  ancilla:
-		prob_meas0_prep1: 0.07540000000000002
-		prob_meas1_prep0: 0.0528
-	mitigated_histogram:
-		'00': 0.42955729968594086
-		'01': 0.49336080079582095
-		'10': 0.04937406434533623
-		'11': 0.02770783517290191
-- target: 1
-  ancilla: 2
-  phi: 6.283185307179586
-  results_per_circuit:
-  - name: id
-	histogram:
-		'00': 22
-		'01': 19
-		'10': 35
-		'11': 24
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	  ancilla:
-		prob_meas0_prep1: 0.07540000000000002
-		prob_meas1_prep0: 0.0528
-	mitigated_histogram:
-		'00': 0.19592641048040849
-		'01': 0.18787721420415215
-		'10': 0.3590258049844047
-		'11': 0.25717057033103463
-  - name: u
-		histogram:
-		'00': 27
-		'01': 24
-		'10': 25
-		'11': 24
-	mitigation_info:
-	  target:
-		prob_meas0_prep1: 0.05900000000000005
-		prob_meas1_prep0: 0.0202
-	  ancilla:
-		prob_meas0_prep1: 0.07540000000000002
-		prob_meas1_prep0: 0.0528
-	mitigated_histogram:
-		'00': 0.25555866817587225
-		'01': 0.2429501641251142
-		'10': 0.24509293912212946
-		'11': 0.2563982285768841
-\end{lstlisting}
-
 \end{document}
-\endinput
-%%
-%% End of file `SoftwareX_article_template.tex'.

### 2023-04-11 txt/tmp.tex
Initial work on cutting irrelevant part from the manuscript

--- 2023-04-11 txt/manuscript2.tex
@@
-\documentclass[preprint,12pt, a4paper, dvipsnames]{elsarticle}
-
-\usepackage{amssymb}
-
-\usepackage{amsthm}
-\usepackage{mathtools}
-
-\usepackage{lineno}
-\usepackage{listings}
-
-\usepackage{float}
-
-\usepackage{todonotes}
-\usepackage{url}
-
-\usepackage{xcolor}
-
-\usepackage{caption}
-\usepackage{subcaption}
-
-\definecolor{codegreen}{rgb}{0.25,0.93,0.31}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
-
-%
-%\lstdefinestyle{mystyle}{
-%	backgroundcolor=\color{backcolour},
-%	commentstyle=\color{codegreen},
-%	keywordstyle=\color{magenta},
-%	numberstyle=\tiny\color{codegray},
-%	stringstyle=\color{codepurple},
-%	basicstyle=\ttfamily\footnotesize,
-%	breakatwhitespace=false,
-%	breaklines=true,
-%	captionpos=b,
-%	keepspaces=true,
-%	numbers=left,
-%	numbersep=5pt,
-%	showspaces=false,
-%	showstringspaces=false,
-%	showtabs=false,
-%	tabsize=2
-%}
-%
-%\lstset{style=mystyle}
-\lstset{frame=tb,
-	language=Python,
-	aboveskip=3mm,
-	belowskip=3mm,
-	showstringspaces=false,
-	columns=flexible,
-	basicstyle={\small\ttfamily},
-%	numberstyle=\color{blue},
-%	keywordstyle=\color{blue},
-%	commentstyle=\color{PineGreen},
-%	stringstyle=\color{ForestGreen},
-	breaklines=true,
-	breakatwhitespace=true,
-	tabsize=3,
-	escapeinside={@}{@},
-%	literate=
-%	{0}{{{\color{red}0}}}1
-%	{1}{{{\color{red}1}}}1
-%	{2}{{{\color{red}2}}}1
-%	{3}{{{\color{red}3}}}1
-%	{4}{{{\color{red}4}}}1
-%	{5}{{{\color{red}5}}}1
-%	{6}{{{\color{red}6}}}1
-%	{7}{{{\color{red}7}}}1
-%	{8}{{{\color{red}8}}}1
-%	{9}{{{\color{red}9}}}1
-%    {v0}{{{\color{black}v0}}}1 %% we can not style only numeric literals
-%    {v1}{{{\color{black}v1}}}1
-}
-\restylefloat{table}
-
-\newcommand{\eg}{{\emph{e.g.\/}}}
-\newcommand{\ie}{{\emph{i.e.\/}}}
-\newcommand{\ket}[1]{\ensuremath{|#1\rangle}}
-\newcommand{\bra}[1]{\ensuremath{\langle#1|}}
-\newcommand{\ketbra}[2]{\ensuremath{\ket{#1}\bra{#2}}}
-\newcommand{\proj}[1]{\ensuremath{\ketbra{#1}{#1}}}
-\newcommand{\braket}[2]{\ensuremath{\langle{#1}|{#2}\rangle}}
-\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}
-\newcommand{\complexity}[1]{\ensuremath{\mathbf{#1}}}
-\newcommand{\new}[1]{ \textcolor{red}{#1} }
-\newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}
-\newcommand{\Id}{{\rm 1\hspace{-0.9mm}l}}
-\newcommand{\connected}{\sim}
-\newcommand{\SPAN}{\mathrm{span}}
-\newcommand{\Lrm}{\ensuremath{\mathrm{L}}}
-\newcommand{\Urm}{\ensuremath{\mathrm{U}}}
-\newcommand{\ee}{\ensuremath{\mathrm{e}}}
-\newcommand{\dd}{\ensuremath{\mathrm{d}}}
-\newcommand{\ii}{\ensuremath{\mathrm{i}}}
-\newcommand{\EE}{\mathcal{E}}
-\newcommand{\XX}{\mathcal{X}}
-\newcommand{\MM}{\mathcal{M}}
-\newcommand{\NN}{\mathcal{N}}
-\newcommand{\DD}{\mathcal{D}}
-\newcommand{\TT}{\mathcal{T}}
-\newcommand{\PP}{\mathcal{P}}
-\newcommand{\QQ}{\mathcal{Q}}
-\renewcommand{\SS}{\mathcal{S}}
-\newcommand{\UU}{\mathcal{U}}
-\newcommand{\HH}{\mathcal{H}}
-\newcommand{\DU}{\mathcal{DU}}
-\newcommand{\NOT}{\sigma_x}
-\newcommand{\idop}[1][\XX]{\ensuremath{\1_{#1}}}
-\newcommand{\diaguni}{\ensuremath{\mathcal{DU}}}
-\newcommand{\diag}{\mathrm{diag}}
-\newcommand{\tr}{\mathrm{tr}}
-\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}
-\journal{SoftwareX}
-
-\usepackage{amsmath}
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{definition}
-\newtheorem{scheme}{Scheme}
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{PyQBench: a Python library for benchmarking gate-based quantum computers}
-
-\author{Konrad Jałowiecki\corref{cor1}}
-\ead{dexter2206@gmail.com}
-\cortext[cor1]{Corresponding author}
-
-\author{Paulina Lewandowska}
-\author{\L ukasz Pawela}
-
-\address{Institute of Theoretical and Applied Informatics, Polish Academy
-	of Sciences, Ba{\l}tycka~5, 44-100 Gliwice, Poland}
-
-\begin{abstract}
-
-We introduce PyQBench, an innovative open-source framework for benchmarking
-gate-based quantum computers. PyQBench can benchmark NISQ devices by verifying their capability of
-discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
-family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
-measurements instead of predefined ones.
-
-\end{abstract}
-
-\begin{keyword}
-Quantum computing \sep
-Benchmarking quantum computers \sep
-Discrimination of quantum measurements \sep
-Discrimination of von Neumann measurements \sep
-Open-source \sep
-Python programming
-
-\PACS 03.67.-a \sep 03.67.Lx
-
-\MSC 81P68
-
-\end{keyword}
-
-\end{frontmatter}
-
-\section*{Current code version}
-\label{}
-
-\begin{table}[H]
-\begin{tabular}{|l|p{5.5cm}|p{7.5cm}|}
-\hline
-C1 & Current code version & 0.1.1 \\
-\hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/iitis/PyQBench} \\
-\hline
-C3 & Code Ocean compute capsule & \texttt{https://codeocean.com/capsule/ 89088992-9a27-4712-8525-} \texttt{d92a9b23060f/tree}\\
-\hline
-C4 & Legal Code License & Apache License 2.0\\
-\hline
-C5 & Code versioning system used & git \\
-\hline
-C6 & Software code languages, tools, and services used & Python, Qiskit, AWS Braket \\
-\hline
-C7 & Compilation requirements, operating environments \& dependencies &
-\texttt{Python >= 3.8}\newline
-\texttt{numpy \textapprox= 1.22.0}\newline
-\texttt{scipy \textapprox= 1.7.0}\newline
-\texttt{pandas \textapprox= 1.5.0}\newline
-\texttt{amazon-braket-sdk >= 1.11.1}\newline
-\texttt{pydantic \textapprox= 1.9.1}\newline
-\texttt{qiskit \textapprox= 0.37.2}\newline
-\texttt{mthree \textapprox= 1.1.0}\newline
-\texttt{tqdm \textapprox= 4.64.1}\newline
-\texttt{pyyaml \textapprox= 6.0}\newline
-\texttt{qiskit-braket-provider \textapprox= 0.0.3}\\
-\hline
-C8 & If available Link to developer documentation/manual &
-\url{https://pyqbench.readthedocs.io/en/latest/}\\
-\hline
-C9 & Support email for questions & \url{dexter2206@gmail.com}\\
-\hline
-\end{tabular}
-\caption{Code metadata}
-\label{}
-\end{table}
-
-\linenumbers
-
-\section{Motivation and significance}
-
-Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market,
-with a wide selection of devices based on different architectures and accompanying software
-solutions. Among hardware providers offering public access to their gate--based devices, one could
-mention Rigetti \cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu \cite{xanadu}. Other vendors offer devices operating in
-different paradigms. Notably, one could mention D-Wave \cite{dwave} and their quantum
-annealers, or QuEra devices \cite{quera} based on neural atoms.  Most vendors provide their own software stack and
-application programming interface for accessing their devices. To name a few, Rigetti's computers
-are available through their Forest SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
-through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}.
-Some cloud services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified API.
-On top of that, several
-libraries and frameworks can integrate with multiple hardware vendors. Examples of such frameworks
-include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.
-
-It is well known that NISQ devices have their limitations \cite{preskillnew}. The question is to what extent those
-devices can perform meaningful computations? To answer this question, one has to devise a
-methodology for benchmarking them. For gate--based computers, on which this paper focuses, there
-already exist several approaches.
-One could mention randomized benchmarking \cite{liu2022sampling, knill2008randomized, wallman2014randomized, helsen2022general,
-	cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume}.
-
-In this paper, we introduce a different approach to benchmarking gate--based devices with a simple
-operational interpretation. In our method, we test how well the given device is at guessing which of
-the two known von Neumann measurements were performed during the experiment. We implemented our
-approach in an open-source Python library called PyQBench. The library supports any device available
-through the Qiskit library, and thus can be used with providers such as IBM Q or Amazon Braket.
-Along with the library, the PyQBench package contains a command line tool for running most common
-benchmarking scenarios.
-
-\section{Existing benchmarking methodologies and software}
-Unsurprisingly, PyQBench is not the only software package for benchmarking gate--based devices.
-While we believe that our approach has significant benefits over other benchmarking techniques, for
-completeness, in this section we discuss some of the currently available similar software.
-
-Probably the simplest benchmarking method one could devise is simply running known algorithms and
-comparing outputs with the expected ones. Analyzing the frequency of the correct outputs, or the
-deviation between actual and expected outputs distribution provides then a metric of the performance
-of a given device.
- Libraries such as Munich Quantum Toolkit (MQT) \cite{mqt2022, mqt-bench}
-or
- SupermarQ \cite{supermarq, supermarkq-github}
-  contain
-benchmarks leveraging multiple algorithms, such as Shor's algorithm or Grover's algorithm.
-% or  implementing e.g. GHZ state \cite{ghz}.
-Despite being intuitive and easily interpretable, such benchmarks may have some problems. Most
-importantly, they assess the usefulness of a quantum device only for a very particular algorithm,
-and it might be hard to extrapolate their results to other algorithms and applications. For
-instance, the inability of a device to consistently find factorizations using Shor's algorithms
-does not tell anything about its usefulness in Variational Quantum Algorithm's.
-
-Another possible approach to benchmarking quantum computers is randomized benchmarking. In this approach, one samples circuits to be run from some predefined set
-of gates (e.g. from the Clifford group) and tests how much the output distribution obtained from the
-device running these circuits differs from the ideal one. It is also common to concatenate randomly
-chosen circuits with their inverses (which should yield the identity circuit) and run those
-concatenated circuits on the device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil \cite{forest-benchmarking}.
-
-Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
-characterizes capacity of a device for solving computational problems. It takes into account
-multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library allows one to
-measure quantum volume of a device by using its \texttt{qiskit.ignis.verifica \\ tion.quantum\_volume}.
-Other implementations of Quantum Volume can be found as well, see e.g. \cite{volume-in-practice}.
-
-% In
-% cross--entropy benchmarkig a random quantum circuit is executed on a quantum computer multiple
-% times. Then, the obtained measurement outcomes are used for computing cross--entropy fidelity
-% $F_{XEB} \in [0, 1]$. A value of 0 means that results obtained from the device are no better then
-% random guessing, whereas value of 1 correspond to a perfect, noiseless execution of the circuit.
-% Packages implementing cross--entropy benchmarking include e.g. \cite{cross-entropy-bench}.
-
-\section{Preliminaries and discrimination scheme approach}
-
-In this section we describe how the benchmarking process in PyQBench works. To do so, we first
-discuss necessary mathematical preliminaries. Then, we present the general form of the
-discrimination scheme used in PyQBench and practical considerations on how to implement it taking
-into account limitations of the current NISQ devices.
-
-\subsection{Mathematical preliminaries}\label{sec:maths}
-
-Let us first recall the definition of a von Neumann measurement, which is the only type of
-measurement used in PyQBench. A von Neumann measurement $\PP$ is a collection of rank--one projectors
-$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to identity,
-i.e. $ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$,
-one can construct a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this
-case we say that $\PP_{U}$ is described by the matrix $U$.
-
-Typically, NISQ devices can only perform measurements in computational $Z$-basis, i.e. $U=\1$.
-To implement an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$
-to the measured system and then follow with $Z$-basis measurement. This process, depicted in Fig.
-\ref{fig:vonneumann}, can be viewed as performing a change of basis in which measurement is
-performed prior to measurement in the computational basis.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.7]{pics/vonneuman}
-	\caption{Implementation of a von Neumann measurement using measurement in computational basis.
-	The upper circuit shows a symbolic representation of a von Neumann measurement $\PP_{U}$. The
-	bottom, equivalent circuit depicts its decomposition into a change of basis followed
-	by measurement in the $Z$ basis.}
-	\label{fig:vonneumann}
-\end{figure}
-
-\subsection{Discrimination scheme}\label{sec:discrimination-scheme}
-
-Benchmarks in PyQBench work by experimentally determining the probability of correct discrimination
-between two von Neumann measurements by the device under test and comparing the result with the
-ideal, theoretical predictions.
-
-Without loss of generality\footnote{Explaining why we can consider only discrimination scheme between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper.
-See \cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between single qubit measurements
-$\PP_\Id$, performed in the computational Z-basis, and an alternative measurement $\PP_U$ performed
-in the basis $U$. Note, however, that the discrimination scheme described below can work
-regardless of dimensionality of the system, see \cite{puchala2018strategies} for details.
-
-In general, the discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme}, requires an
-auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the 
-measurements,  either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
-outcome $i$, we choose another POVM $\mathcal{P}_{V_i}$ and perform it on the second
-qubit, obtaining the output in $j$. Finally, if $j=0$, we say that the performed measurement is
-$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
-same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
-probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
-times for both $\PP_U$ and $\PP_\Id$.
-
-Unsurprisingly, both the
-$\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be chosen specifically for
-given $U$ to maximize the probability of a correct guess. The detailed description  how these
-choices are made in \cite{watrous}, and for now we will focus
-only how this scheme can be implemented on the actual devices, assuming that all the components are known.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.7]{pics/theoretical_scheme}
-	\caption{Theoretical  scheme of discrimination  between von Neumann measurements $\PP_{U}$ and $\PP_\Id$. }
-	\label{fig:theoretical_scheme}
-\end{figure}
-
-\subsubsection{Implementation of discrimination scheme on actual NISQ devices}
-
-Current NISQ devices are unable to perform conditional measurements, which is the biggest
-obstacle to implementing our scheme on real hardware. However, we circumvent this problem by
-slightly adjusting our scheme so that it only uses components available on current devices.
-For this purpose, we use two possible options: using a postselection or a direct sum $V_0^\dagger\oplus V_1^\dagger$.
-
-\begin{scheme}(Postselection)
-
-	The first idea uses a postselection scheme. In the original scheme, we measure the first qubit
-	and only then determine which measurement should be performed on the second one. Instead of
-	doing this choice, we can run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and
-	measure both qubits. We then discard the results of the circuit for which label $i$ does not match
-	measurement label $k$. Hence, the circuit for postselection looks as depicted in Fig.
-	\ref{fig:postselection}.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[scale=1.7]{pics/postselection_no_channels}
-
-		\caption{
-			A schematic representation of the setup for distinguishing
-			measurements $\PP_{U}$ and $\PP_{\Id}$ using postselection approach.
-			In postselection scheme, one runs such circuits for both $k=0,1$ and discards results for cases when there is a mismatch between $k$ and $i$.
-		}\label{fig:postselection}
-	\end{figure}
-
-	To perform the benchmark, one needs to run multiple copies of the postselection circuit,
-	with both $\PP_U$ and $\PP_\1$. Each circuit has to be run in both variants, one with final
-	measurement $\PP_{V_0}$ and the second with the final measurement $\PP_{V_1}$.
-	The experiments can thus be grouped into classes identified by tuples of the form
-	$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen
-	measurement, $k \in \{0,1\}$ designates the final measurement used, and $i \in \{0,1\}$ and $j
-	\in \{0,1\}$ being the labels of outcomes as presented in Fig. \ref{fig:postselection}.
-	We then discard all the experiments for which $i \ne k$. The total number of valid experiments
-	is thus:
-
-	\begin{equation}
-	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}.
-	\end{equation}
-
-	Finally, we count the valid experiments resulting in successful discrimination.
-	If we have chosen $\PP_U$, then we guess correctly iff $j=0$. Similarly, for
-	$P_\Id$, we guess correctly iff $j=1$. If we define
-	\begin{eqnarray}
-	N_{\PP_U} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_U, k = i, j = 0\}, \\
-	N_{\PP_\Id} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_\Id, k = i, j = 1\},
-	\end{eqnarray}
-	then the empirical success probability can be computed as
-
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{N_{\PP_U} + N_{\PP_\Id}}{N_{\text{total}}}.
-	\end{equation}
-	The $p_{\text{succ}}$ is the quantity reported to the user as the result of the benchmark.
-\end{scheme}
-
-\begin{scheme}(Direct sum)
-
-The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation.     Here, instead of performing a conditional
-measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits presented in
-Fig.~\ref{fig:controlled}.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[width=0.8\textwidth]{pics/controlled_unitary}
-
-		\caption{ A schematic representation of the setup for distinguishing
-			measurements $\PP_{U}$ and $\PP_{\Id}$ using the $V_0^\dagger \oplus V_1^\dagger$ direct sum.
-		}\label{fig:controlled}
-	\end{figure}
-
-	One can see why such a circuit is equivalent to the original discrimination scheme.
-	If we rewrite the block-diagonal matrix $V_0^\dagger \oplus V_1^\dagger$ as follows:
-	\begin{equation}
-		\label{eq:directsum}
-		V_0^\dagger \oplus V_1^\dagger = \proj{0}\otimes V_0^\dagger + \proj{1} \otimes V_1^\dagger,
-	\end{equation}
-	we can see that the direct sum in Eq. \eqref{eq:directsum} commutes with the measurement on the
-	first qubit. Thanks to this, we can switch the order of operations to obtain the circuit from
-	Fig. \ref{fig:directsum}. Now, depending on the outcome $i$, one of the summands in
-	Eq. \eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in the
-	original scheme.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[width=\textwidth]{pics/direct_sum}
-		\caption{Rewritten representation of the setup for distinguishing
-		measurements $\PP_{U}$ and $\PP_{\Id}$ using the $V_0^\dagger \oplus V_1^\dagger$ direct
-		sum.
-		}\label{fig:directsum}
-	\end{figure}
-
-	In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where
-	$\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$ and $i,j \in \{0,1\}$ are the output labels. The number of successful trials for $U$ and $\Id$,
-	respectively, can be written  as
-	\begin{eqnarray}
-	N_{\PP_U} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_U, j = 0\}, \\
-	N_{\PP_\Id} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_\Id, j = 1\}.
-	\end{eqnarray}
-	Then, the probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is given by
-	\begin{equation}
-	p_{\text{succ}} = \frac{N_{\PP_{U}} + N_{\PP_{\Id}}}{N_{\text{total}}},
-	\end{equation}
-	where $N_{\text{total}}$ is the number of trials.
-\end{scheme}
-
-\subsubsection{Importance of choosing the optimal discrimination scheme}
-In principle, the schemes described in the previous section could be used with any choice of
-$\ket{\psi_0}$ and final measurements $\PP_{V_i}$. However, we argue that it is best to choose those
-components in such a way that they maximize the probability of correct discrimination. To see that,
-suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ yields the theoretical upper bound
-of discriminating between two measurements of one, i.e. on a perfect quantum computer you will always
-make a correct guess. Then, on real hardware, we might obtain any empirical value in range $\left[\frac{1}{2},
-1\right]$. On the other hand, if we choose the components of our scheme such that the successful
-discrimination probability is only $\frac{3}{5}$, the possible range of empirically obtainable probabilities
-is only $\left[\frac{1}{2}, \frac{3}{5}\right]$. Hence, in the second case, the discrepancy between theoretical and empirical
-results will be less pronounced.
-
-\subsubsection{Constructing optimal discrimination scheme}
-To construct the optimal discrimination scheme, one starts by calculating the probability of correct discrimination.
-Using the celebrated result by Helstrom~\cite{helstrom1976quantum}, one finds that the  optimal probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$, is
-\begin{equation}
-p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond,
-\end{equation}
-where
-\begin{equation}
-\|\PP - \QQ\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left( (\PP - \QQ) \otimes \1\right) (\proj{\psi}) \|_1.
-\end{equation}
-The quantum state $\ket{\psi_0}$ maximizing the diamond norm above is called the
-\emph{discriminator}, and can be computed e.g. using semidefinite programming (SDP)
-\cite{watrous,watrous2021simplier}. Furthermore,  using the proof of the Holevo-Helstrom theorem, it is
-possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
-discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
-interested reader to \cite{watrous}.
-
- \section{Software description}
- \label{}
- This section is divided into two parts.
- In Section~\ref{sec:sortware-functionalities} we describe functionalities of PyQBench
- package. Next, in Section~\ref{sec:sortware-architecture}, we give a general overview of the
- software architecture.
-
-\subsection{Software Functionalities}\label{sec:sortware-functionalities}
-
-The PyQBench can be used in two modes: as a Python library and as a CLI script. When used as a
-library, PyQBench allows the customization of discrimination scheme. The user provides
-a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\psi_0}$,
-and unitaries $V_0$ and $V_1$ describing the final measurement. The PyQBench library provides then
-the following functionalities.
-
-\begin{enumerate}
-	\item Assembling circuits for both postselection and direct sum--based discrimination schemes.
-	\item Executing the whole benchmarking scenario on specified backend (either real hardware or
-	software simulator).
-	\item Interpreting the obtained outputs in terms of discrimination probabilities.
-\end{enumerate}
-Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt in for
-fine-grained control over the execution of the circuits. For instance, suppose the user wants to
-simulate the discrimination experiment on a noisy simulator. In such a case, they can define
-the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
-e.g. to add noise to particular gates, and then run using any Qiskit backend by the user. Finally,
-PyQBench can be used to interpret the measurements to obtain discrimination probability.
-
-The PyQBench library also contains a readily available implementation of all necessary components
-needed to run discrimination experiments for parametrized Fourier family of measurements, defined
-previously in Section \ref{sec:fourier}. However, if one only wishes to use this particular family
-of measurements in their benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's command line interface allows running the benchmarking process without
-writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the benchmark
-to be performed and the description of the backend on which the benchmark should be run. Notably,
-the YAML configuration files are reusable. The same benchmark can be used with different backends
-and vice versa.
-
-The following section describes important architectural decisions taken when creating PyQBench, and
-how they affect the end-user experience.
-
-\subsection{Software Architecture}\label{sec:sortware-architecture}
-
-\subsubsection{Overview of the software structure}
-As already described, PyQBench can be used both as a library and a CLI. Both functionalities are
-implemented as a part of \texttt{qbench} Python package. The exposed CLI tool is also named
-\texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead
-refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the reference manual
-\cite{pyqbenchdocs}.
-
-PyQBench can be installed from official Python Package Index (PyPI) by running \texttt{pip install
-pyqbench}. In a properly configured Python environment the installation process should also make the
-\texttt{qbench} command available to the user without a need for further configuration.
-
-\subsubsection{Integration with hardware providers and software simulators}
-
-PyQBench is built around the Qiskit \cite{qiskit} ecosystem. Hence, both the CLI tool and the
-\texttt{qbench} library can use any Qiskit--compatible backend. This includes, IBM Q
-backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
-through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider, qiskit-braket-provider-github}).
-
-When using PyQBench as library, instances of Qiskit backends can be passed to functions that expect
-them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
-backend. An example of such file can be found in Section \ref{sec:examples}, and the detailed description of
-the expected format can be found at PyQBench's documentation.
-
-\subsubsection{Command Line Interface}
-\label{sec:cli}
-
-The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
-invocation is shown in listing \ref{lst:cli}.
-\begin{lstlisting}[caption=Invocation of \texttt{qbench} script, label=lst:cli]
-qbench <benchmark-type> <command> <parameters>
-\end{lstlisting}
-Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
-Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
-fashion to allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
-is \texttt{disc-fourier}.
-%
-The \texttt{qbench disc-fourier} command has four subcommands:
-
-\begin{itemize}
-	\item \texttt{benchmark}: run benchmarks. This creates either a result YAML file containing
-	the measurements or an intermediate YAML file for asynchronous experiments.
-	\item \texttt{status}: query status of experiments submitted for given benchmark. This command
-	is only valid for asynchronous experiments.
-	\item \texttt{resolve}: query the results of asynchronously submitted experiments and write the
-	result YAML file. The output of this command is almost identical to the result obtained from
-	synchronous experiments.
-	\item \texttt{tabulate}: interpret the results of a benchmark and summarize them in the CSV file.
-\end{itemize}
-%
-We present usage of each of the above commands later in section \ref{sec:examples}.
-
-\subsubsection{Asynchronous vs. synchronous execution}
-PyQBench's CLI can be used in synchronous and asynchronous modes. The
-mode of execution is defined in the YAML file describing the backend (see Section
-\ref{sec:examples} for an example of this configuration). We decided to couple the mode of execution to
-the backend description because some backends cannot work in asynchronous mode.
-
-When running \texttt{qbench disc-fourier benchmark} in asynchronous mode, the PyQBench submits all
-the circuits needed to perform a benchmark and then writes an intermediate YAML file
-containing metadata of submitted experiments. In particular, this metadata contains information on
-correlating submitted job identifiers with particular circuits. The intermediate file can be
-used to query the status of the submitted jobs or to resolve them, i.e. to wait for their completion
-and get the measurement outcomes.
-
-In synchronous mode, PyQBench first submits all jobs required to run the benchmark and then
-immediately waits for their completion. The advantage of this approach is that no separate
-invocation of \texttt{qbench} command is needed to actually download the measurement outcomes. The
-downside, however, is that if the script is interrupted while the command is running, the
-intermediate results will be lost. Therefore, we recommend using asynchronous mode
-whenever possible.
-
-\section{Illustrative examples}
-\label{sec:examples}
-In this section, we present two examples demonstrating the usage of PyQBench. In the first example,
-we show how to implement a discrimination scheme for a user--defined measurement and possible ways
-of using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
-CLI. We show how to prepare the input files for the benchmark and how to run it using the
-\texttt{qbench} tool.
-
-\subsection{Using \texttt{qbench} CLI}
-Using PyQBench as a library allows one to conduct a two--qubits benchmark with arbitrary von Neumann
-measurement. However, as discussed in the previous guide, it requires writing some amount of code.
-For a Fourier parametrized family of measurements, PyQBench offers a simplified way of conducting
-benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
-as the following list of steps::
-
-\begin{enumerate}
-
-\item Preparing configuration files describing the backend and the experiment scenario.
-\item Submitting/running experiments. Depending on the experiment scenario, execution can be synchronous, or asynchronous.
-\item (optional) Checking the status of the submitted jobs if the execution is asynchronous.
-\item Resolving asynchronous jobs into the actual measurement outcomes.
-\item Converting obtained measurement outcomes into tabulated form.
-\end{enumerate}
-\subsubsection{Preparing configuration files}
-The configuration of PyQBench CLI is driven by YAML files. The first configuration file
-describes the experiment scenario to be executed. The second file describes the backend.
-Typically, this backend will correspond to the physical device to be benchmarked, but for testing
-purposes one might as well use any other Qiskit--compatible backend including simulators.
-Let us first describe the experiment configuration file, which might look as follow.
-\begin{lstlisting}[language=Python, caption=Defining the experiment, label=lst:experiment]
-type: discrimination-fourier
-qubits:
-	- target: 0
-	  ancilla: 1
-	- target: 1
-      ancilla: 2
-angles:
-	start: 0
-	stop: 2 * pi
-	num_steps: 3
-gateset: ibmq
-method: direct_sum
-num_shots: 100
-\end{lstlisting}
-
-The second configuration file describes the backend. We decided to decouple the
-experiment and the backend files because it facilitates their reuse. For instance, the same
-experiment file can be used to run benchmarks on multiple backends, and the same backend description
-file can be used with multiple experiments.
-
-Different Qiskit backends typically require different data for their initialization. Hence, there
-are multiple possible formats of the backend configuration files understood by PyQBench. We refer
-the interested reader to the PyQBench's documentation. Below we describe an example YAML file
-describing IBM Q backend named
-Quito.
-\begin{lstlisting}[language=Python, caption=IBMQ backend, label=lst:backend]
-name: ibmq_quito
-asynchronous: false
-provider:
-	hub: ibm-q
-	group: open
-	project: main
-\end{lstlisting}
-IBMQ backends typically require an access token to IBM Quantum Experience. Since it would be unsafe
-to store it in plain text, the token has to be configured separately in \texttt{IBMQ\_TOKEN}
-environmental variable.
-
-\subsubsection{Running the experiment and collecting measurements data}
-After preparing YAML files defining experiment and backend,
-running the benchmark can be launched by using the following command line invocation:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier benchmark experiment_file.yml backend_file.yml
-\end{lstlisting}
-The output file will be printed to stdout. Optionally, the \texttt{- -output OUTPUT} parameter might be provided to write the output to the \texttt{OUTPUT} file instead.
-\begin{lstlisting}[language=Python]
-qbench disc-fourier benchmark experiment_file.yml backend_file.yml --output async_results.yml
-\end{lstlisting}
-The result of running the above command can be twofold:
-\begin{itemize}
-	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, \texttt{job\_ids} correlated with the circuit they correspond to.
-	\item If the backend is synchronous, the output will contain measurement outcomes (bitstrings) for each of the circuits run.
-\end{itemize}
-
-For synchronous experiment, the part of output looks similar to the one below. The whole YAML file can be seen in \ref{app:example}.
-%Consider the particular experiment data
-\begin{lstlisting}[language=Python]
-data:
-- target: 0
-  ancilla: 1
-  phi: 0.0
-  results_per_circuit:
-  - name: id
-  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
-  mitigation_info:
-	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
-\end{lstlisting}
-
-\subsubsection{(Optional) Getting status of asynchronous jobs}
- PyQBench provides also a helper command that will fetch the statuses of asynchronous jobs. The command is:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier status async_results.yml
-\end{lstlisting}
-and it will display dictionary with histogram of statuses.
-
-\subsubsection{Resolving asynchronous jobs}
-For asynchronous experiments, the stored intermediate data has to be resolved in actual
-measurements' outcomes. The following command will wait until all jobs are completed and then write
-a result file.
-\begin{lstlisting}[language=Python]
-qbench disc-fourier resolve async-results.yml resolved.yml
-\end{lstlisting}
-The resolved results, stored in \texttt{resolved.yml}, would look just like if the experiment was
-run synchronously. Therefore, the final results will look the same no matter in which mode the
-benchmark was run, and hence in both cases the final output file is suitable for being an input for
-the command computing the discrimination probabilities.
-
-\subsubsection{Computing probabilities}
-As a last step in the processing workflow, the results file has to be passed to \texttt{tabulate}
-command:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier tabulate results.yml results.csv
-\end{lstlisting}
-A sample CSV file is provided below:
-\begin{table}[ht!]
-\begin{center}
-	\begin{tabular}{|c c c c c c|} 
-		\hline
-		target & ancilla & phi & ideal$\_$prob  & disc$\_$prob & mit$\_$disc$\_$prob \\ [0.5ex] 
-		\hline\hline
-		0 & 1 & 0 & 0.5 & 0.46 & 0.45  \\ 
-		\hline
-		0 & 1 & 3.14 & 1 & 0.95 & 0.98  \\
-		\hline
-		0 & 1 & 6.28 & 0.5 & 0.57 & 0.58  \\
-		\hline
-		1 & 2 & 0 & 0.5  & 0.57 & 0.57 \\
-		\hline
-		1 & 2 & 3.14 & 1 & 0.88 & 0.94  \\ 
-		\hline
-		1 & 2 & 6.28 & 0.5 & 0.55 & 0.56  \\ 
-		\hline
-	\end{tabular}
-\caption{The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
-	\texttt{ideal\_prob}, \texttt{disc\_prob} and, optionally, \texttt{mit\_disc\_prob}. Each row in the
-	table describes results for a tuple of \texttt{(target, ancilla, phi)}.  The reference optimal value
-	of discrimination probability is present in \texttt{ideal\_prob} column, whereas the obtained,
-	empirical discrimination probability can be found in the \texttt{disc\_prob} column. The
-	\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
-	\texttt{Mthree} error mitigation \cite{mthree, mthreepublication}, if it was applied.}
-\label{fig:tabulateresults}
-\end{center}
-\end{table}
-
-\section{Impact}
 With the surge of availability of quantum computing architectures in recent
@@
 specific applications.
-
-\section{Conclusions}
-\label{}
-
-In this study, we develop  a Python library PyQBench, an innovative open-source framework for benchmarking
-gate-based quantum computers.
-
-%%%%%%%%%%%%%%
-PyQBench can benchmark NISQ devices by verifying their capability of
-discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parameterized Fourier
-family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
-measurements instead of predefined ones.
-\section{Conflict of Interest}
-We wish to confirm that there are no known
-conflicts of interest associated with this publication and there has been no
-significant financial support for this work that could have influenced its out-
-come.
-
-\section*{Acknowledgements}
-
-This work is  supported by
-the project “Near-term quantum computers Challenges, optimal implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the Team-Net programme of the Foundation for Polish Science co-financed by the European Union under the European Regional Development Fund.
-PL is also a holder of European Union scholarship through the European Social Fund,
-grant InterPOWER (POWR.03.05.00-00-Z305).
-
-% \begin{thebibliography}{00}
-% \bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.
-% \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
-% \bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
-% \bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
-% \bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
-% \bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
-% \bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
-% \bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
-% \bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
-% \bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
-% \bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
-% \bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
-% \bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
-% \bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
-% \bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
-% \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
-(2021).
-Benchmarking near-term quantum computers via random circuit sampling.
-arXiv preprint arXiv:2105.05232.
-% \bibitem{knill2008randomized}
-% Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
-B., Jost, J.
-D., Langer, C., Ozeri, R., Seidelin, S.,  Wineland, D.
-J.
-(2008).
-Randomized benchmarking of quantum gates.
-Physical Review A, 77(1), 012307.
-% \bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
-% \bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
-% \bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
-% \bibitem{cross2019validating}
-% Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
-% \bibitem{moll2018quantum}
-% Moll, N., Barkoutsos, P., Bishop, L.
-S., Chow, J.
-M., Cross, A., Egger, D.
-J., Filipp, S., Fuhrer, A., Gambetta, J.
-M., Ganzhorn, M., Kandala, A., Mezzacapo, A., M{\"u}ller, P., Riess, W., Salis, G., Smolin, J., Tavernelli, I.,  Temme, K.
-(2018).
-Quantum optimization using variational algorithms on near-term quantum devices.
-Quantum Science and Technology, 3(3), 030503.
-% \bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S.
-(2022).
-Quantum volume in practice: What users can expect from NISQ devices.
-IEEE Transactions on Quantum Engineering, 3, 1-19.
-% 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
-% \bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
-% 	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
-S., Smith, K.
-N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F.
-T.
-(2022).
-Supermarq: A scalable quantum benchmark suite.
-In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp.
-587-603).
-IEEE.
-% \bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
-% \bibitem{qiskit-randomized} The web resource at
-% \url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
-% \bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
-% \bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
-% \bibitem{cross-entropy-bench} The web resource at
-% \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
-% \bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for
-% optimal single-shot discrimination of quantum measurements. Physical Review A
-% 98.4, 042103.
-% \bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.
-% \bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
-% \bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
-% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-% \bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
-% \bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
-% \bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
-% \bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
-% \bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
-% \bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
-% \bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
-% \bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-% \bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.
-% \bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
-(2021).
-On the optimal certification of von Neumann measurements.
-Scientific Reports, 11(1), 3623.
-% \bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
-% \bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
-% \bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H.
-(2017).
-Benchmarking gate-based quantum computers.
-Computer Physics Communications, 220, 44-55.
-% \bibitem{zhukov2019quantum} Zhukov, A.
-A., Kiktenko, E.
-O., Elistratov, A.
-A., Pogosov, W.
-V.,  Lozovik, Y.
-E.
-(2019).
-Quantum communication protocols as a benchmark for programmable quantum computers.
-Quantum Information Processing, 18(1), 31.
-% \bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
-% and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
-% qubits. Physical Review A 99(6), 062323.
-% \bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A.
-(2019).
-A generative modeling approach for benchmarking and training shallow quantum circuits.
-npj Quantum Information, 5(1), 45.
-
-% \end{thebibliography}
-
-\bibliographystyle{unsrt}
-\bibliography{references}
-\end{document}

### 2023-04-13 txt/manuscript_short.tex
Update shortened manuscript

--- 2023-04-11 txt/manuscript2.tex
@@
 
-We introduce PyQBench, an innovative open-source framework for benchmarking
-gate-based quantum computers. PyQBench can benchmark NISQ devices by verifying their capability of
-discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
-family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
-measurements instead of predefined ones.
+We introduce PyQBench, an innovative open-source framework for benchmarking gate-based quantum
+computers. PyQBench can benchmark NISQ devices by verifying their capability of discriminating
+between two von Neumann measurements. PyQBench offers a simplified, ready-to-use, command line
+interface (CLI) for running benchmarks using a predefined family of measurements. For more advanced
+scenarios, PyQBench offers a way of employing user-defined measurements instead of predefined ones.
 
@@
 
-Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market,
-with a wide selection of devices based on different architectures and accompanying software
-solutions. Among hardware providers offering public access to their gate--based devices, one could
-mention Rigetti \cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu \cite{xanadu}. Other vendors offer devices operating in
-different paradigms. Notably, one could mention D-Wave \cite{dwave} and their quantum
-annealers, or QuEra devices \cite{quera} based on neural atoms.  Most vendors provide their own software stack and
-application programming interface for accessing their devices. To name a few, Rigetti's computers
-are available through their Forest SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
-through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}.
-Some cloud services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified API.
-On top of that, several
-libraries and frameworks can integrate with multiple hardware vendors. Examples of such frameworks
-include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.
+Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market, with a wide
+selection of devices based on different architectures and accompanying software solutions. Among
+hardware providers offering public access to their gate--based devices, one could mention Rigetti
+\cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu
+\cite{xanadu}. Other vendors offer devices operating in different paradigms. Notably, one could
+mention D-Wave \cite{dwave} and their quantum annealers, or QuEra devices \cite{quera} based on
+neural atoms. Most vendors provide their own software stack and application programming interface
+for accessing their devices. To name a few, Rigetti's computers are available through their Forest
+SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
+through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}. Some cloud
+services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified
+API. On top of that, several libraries and frameworks can integrate with multiple hardware vendors.
+Examples of such frameworks include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.
 
-It is well known that NISQ devices have their limitations \cite{preskillnew}. The question is to what extent those
-devices can perform meaningful computations? To answer this question, one has to devise a
-methodology for benchmarking them. For gate--based computers, on which this paper focuses, there
-already exist several approaches.
-One could mention randomized benchmarking \cite{liu2022sampling, knill2008randomized, wallman2014randomized, helsen2022general,
-	cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume}.
+It is well known that NISQ devices have their limitations \cite{preskillnew}. The question is to
+what extent those devices can perform meaningful computations? To answer this question, one has to
+devise a methodology for benchmarking them. For gate--based computers, on which this paper focuses,
+there already exist several approaches. One could mention randomized benchmarking
+\cite{liu2022sampling, knill2008randomized, wallman2014randomized, helsen2022general,
+cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating,
+moll2018quantum, pelofske2022volume}.
 
@@
 deviation between actual and expected outputs distribution provides then a metric of the performance
-of a given device.
- Libraries such as Munich Quantum Toolkit (MQT) \cite{mqt2022, mqt-bench}
-or
- SupermarQ \cite{supermarq, supermarkq-github}
-  contain
-benchmarks leveraging multiple algorithms, such as Shor's algorithm or Grover's algorithm.
+of a given device. Libraries such as Munich Quantum Toolkit (MQT) \cite{mqt2022, mqt-bench} or
+SupermarQ \cite{supermarq, supermarkq-github} contain benchmarks leveraging multiple algorithms,
+such as Shor's algorithm or Grover's algorithm.
 % or  implementing e.g. GHZ state \cite{ghz}.
@@
 and it might be hard to extrapolate their results to other algorithms and applications. For
-instance, the inability of a device to consistently find factorizations using Shor's algorithms
-does not tell anything about its usefulness in Variational Quantum Algorithm's.
+instance, the inability of a device to consistently find factorizations using Shor's algorithms does
+not tell anything about its usefulness in Variational Quantum Algorithm's.
 
-Another possible approach to benchmarking quantum computers is randomized benchmarking. In this approach, one samples circuits to be run from some predefined set
-of gates (e.g. from the Clifford group) and tests how much the output distribution obtained from the
-device running these circuits differs from the ideal one. It is also common to concatenate randomly
-chosen circuits with their inverses (which should yield the identity circuit) and run those
-concatenated circuits on the device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil \cite{forest-benchmarking}.
+Another possible approach to benchmarking quantum computers is randomized benchmarking. In this
+approach, one samples circuits to be run from some predefined set of gates (e.g. from the Clifford
+group) and tests how much the output distribution obtained from the device running these circuits
+differs from the ideal one. It is also common to concatenate randomly chosen circuits with their
+inverses (which should yield the identity circuit) and run those concatenated circuits on the
+device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
+\cite{forest-benchmarking}.
 
@@
 characterizes capacity of a device for solving computational problems. It takes into account
-multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library allows one to
-measure quantum volume of a device by using its \texttt{qiskit.ignis.verifica \\ tion.quantum\_volume}.
-Other implementations of Quantum Volume can be found as well, see e.g. \cite{volume-in-practice}.
-
-% In
-% cross--entropy benchmarkig a random quantum circuit is executed on a quantum computer multiple
-% times. Then, the obtained measurement outcomes are used for computing cross--entropy fidelity
-% $F_{XEB} \in [0, 1]$. A value of 0 means that results obtained from the device are no better then
-% random guessing, whereas value of 1 correspond to a perfect, noiseless execution of the circuit.
-% Packages implementing cross--entropy benchmarking include e.g. \cite{cross-entropy-bench}.
+multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library
+allows one to measure quantum volume of a device by using its \texttt{qiskit.ignis.verifica \\
+tion.quantum\_volume}. Other implementations of Quantum Volume can be found as well, see e.g.
+\cite{volume-in-practice}.
 
@@
 
-In this section we describe how the benchmarking process in PyQBench works. To do so, we first
-discuss necessary mathematical preliminaries. Then, we present the general form of the
+In this section, we describe how the benchmarking process in PyQBench works. We start by
+discussing necessary mathematical preliminaries. Then, we present the general form of the
 discrimination scheme used in PyQBench and practical considerations on how to implement it taking
-into account limitations of the current NISQ devices.
+into account the limitations of the current NISQ devices.
 
-\subsection{Mathematical preliminaries}\label{sec:maths}
+\subsection{Von Neumann Measurements}\label{sec:maths}
 
-Let us first recall the definition of a von Neumann measurement, which is the only type of
-measurement used in PyQBench. A von Neumann measurement $\PP$ is a collection of rank--one projectors
-$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to identity,
-i.e. $ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$,
-one can construct a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this
-case we say that $\PP_{U}$ is described by the matrix $U$.
+A von Neumann measurement $\PP$ is a collection of rank--one projectors
+$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to the identity operator, i.e.
+$ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$, one can construct
+a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this case we say that
+$\PP_{U}$ is described by the matrix $U$.
 
-Typically, NISQ devices can only perform measurements in computational $Z$-basis, i.e. $U=\1$.
-To implement an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$
-to the measured system and then follow with $Z$-basis measurement. This process, depicted in Fig.
+Typically, NISQ devices can only perform measurements in computational $Z$-basis, i.e. $U=\1$. To
+implement an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$ to the
+measured system and then follow with $Z$-basis measurement. This process, depicted in Fig.
 \ref{fig:vonneumann}, can be viewed as performing a change of basis in which measurement is
@@
 
-Without loss of generality\footnote{Explaining why we can consider only discrimination scheme between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper.
-See \cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between single qubit measurements
-$\PP_\Id$, performed in the computational Z-basis, and an alternative measurement $\PP_U$ performed
-in the basis $U$. Note, however, that the discrimination scheme described below can work
-regardless of dimensionality of the system, see \cite{puchala2018strategies} for details.
+Without loss of generality\footnote{Explaining why we can consider only discrimination scheme
+between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper. See
+\cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between
+single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
+measurement $\PP_U$ performed in the basis $U$. Note, however, that the discrimination scheme
+described below can work regardless of dimensionality of the system, see
+\cite{puchala2018strategies} for details.
 
-In general, the discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme}, requires an
+The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
 auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the
 measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
-outcome $i$, we choose another POVM $\mathcal{P}_{V_i}$ and perform it on the second
-qubit, obtaining the output in $j$. Finally, if $j=0$, we say that the performed measurement is
+outcome $i$, we choose another measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
+obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
 $\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
@@
 
-Unsurprisingly, both the
-$\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be chosen specifically for
-given $U$ to maximize the probability of a correct guess. The detailed description  how these
-choices are made in \cite{watrous}, and for now we will focus
-only how this scheme can be implemented on the actual devices, assuming that all the components are known.
+Unsurprisingly, both the $\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be
+chosen specifically for given $U$ to maximize the probability of a correct guess. The detailed
+description how these choices are made in \cite{watrous}, and for now we will focus only how this
+scheme can be implemented on the actual devices, assuming that all the components are known.
+
+In principle, our discrimination scheme could be used with any choice of
+$\ket{\psi_0}$ and final measurements $\PP_{V_i}$. However, we argue that it is best to choose those
+components so that they maximize the probability of correct discrimination. To see that,
+suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ allows for correctly discriminating
+between two measurements with probability equal to one, i.e. on a perfect quantum computer you will always
+make a correct guess. Then, on real hardware, we might obtain any empirical value in range $\left[\frac{1}{2},
+1\right]$. On the other hand, if we choose the components of our scheme such that the successful
+discrimination probability is $\frac{3}{5}$, the possible range of empirically obtainable probabilities
+is only $\left[\frac{1}{2}, \frac{3}{5}\right]$. Hence, in the second case, the discrepancy between theoretical and empirical
+results will be less pronounced.
 
@@
 
-Current NISQ devices are unable to perform conditional measurements, which is the biggest
-obstacle to implementing our scheme on real hardware. However, we circumvent this problem by
-slightly adjusting our scheme so that it only uses components available on current devices.
-For this purpose, we use two possible options: using a postselection or a direct sum $V_0^\dagger\oplus V_1^\dagger$.
+Current NISQ devices are unable to perform conditional measurements, which is the biggest obstacle
+to implementing our scheme on real hardware. However, we circumvent this problem by slightly
+adjusting our scheme so that it only uses components available on current devices. For this purpose,
+we use two possible options: using a postselection or a direct sum $V_0^\dagger\oplus V_1^\dagger$.
 
@@
 	The first idea uses a postselection scheme. In the original scheme, we measure the first qubit
-	and only then determine which measurement should be performed on the second one. Instead of
-	doing this choice, we can run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and
-	measure both qubits. We then discard the results of the circuit for which label $i$ does not match
-	measurement label $k$. Hence, the circuit for postselection looks as depicted in Fig.
+	and only then determine which measurement should be performed on the second one. Instead of doing
+	this choice, we can run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and measure both
+	qubits. We then discard the results of the circuit for which label $i$ does not match measurement
+	label $k$. Hence, the circuit for postselection looks as depicted in Fig.
 	\ref{fig:postselection}.
@@
 			measurements $\PP_{U}$ and $\PP_{\Id}$ using postselection approach.
-			In postselection scheme, one runs such circuits for both $k=0,1$ and discards results for cases when there is a mismatch between $k$ and $i$.
+			In postselection scheme, one runs such circuits for both $k=0,1$ and discards results
+			for cases when there is a mismatch between $k$ and $i$.
 		}\label{fig:postselection}
@@
 
-The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation.     Here, instead of performing a conditional
-measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits presented in
-Fig.~\ref{fig:controlled}.
-
+The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation. Here, instead
+of performing a conditional measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits
+presented in Fig.~\ref{fig:controlled}.
 	\begin{figure}[h!]
@@
 	Fig. \ref{fig:directsum}. Now, depending on the outcome $i$, one of the summands in
-	Eq. \eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in the
-	original scheme.
+	Eq. \eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in
+	the original scheme.
 
@@
 	In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where
-	$\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$ and $i,j \in \{0,1\}$ are the output labels. The number of successful trials for $U$ and $\Id$,
-	respectively, can be written  as
+	$\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$ and $i,j \in \{0,1\}$ are the output labels. The number
+	of successful trials for $U$ and $\Id$, respectively, can be written  as
 	\begin{eqnarray}
@@
 
-\subsubsection{Importance of choosing the optimal discrimination scheme}
-In principle, the schemes described in the previous section could be used with any choice of
-$\ket{\psi_0}$ and final measurements $\PP_{V_i}$. However, we argue that it is best to choose those
-components in such a way that they maximize the probability of correct discrimination. To see that,
-suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ yields the theoretical upper bound
-of discriminating between two measurements of one, i.e. on a perfect quantum computer you will always
-make a correct guess. Then, on real hardware, we might obtain any empirical value in range $\left[\frac{1}{2},
-1\right]$. On the other hand, if we choose the components of our scheme such that the successful
-discrimination probability is only $\frac{3}{5}$, the possible range of empirically obtainable probabilities
-is only $\left[\frac{1}{2}, \frac{3}{5}\right]$. Hence, in the second case, the discrepancy between theoretical and empirical
-results will be less pronounced.
-
-\subsubsection{Constructing optimal discrimination scheme}
-To construct the optimal discrimination scheme, one starts by calculating the probability of correct discrimination.
+% \subsubsection{Constructing optimal discrimination scheme}
+% To construct the optimal discrimination scheme, one starts by calculating the probability of correct discrimination.
 Using the celebrated result by Helstrom~\cite{helstrom1976quantum}, one finds that the  optimal probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$, is
-\begin{equation}
-p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond,
-\end{equation}
-where
-\begin{equation}
-\|\PP - \QQ\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left( (\PP - \QQ) \otimes \1\right) (\proj{\psi}) \|_1.
-\end{equation}
-The quantum state $\ket{\psi_0}$ maximizing the diamond norm above is called the
-\emph{discriminator}, and can be computed e.g. using semidefinite programming (SDP)
-\cite{watrous,watrous2021simplier}. Furthermore,  using the proof of the Holevo-Helstrom theorem, it is
-possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
-discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
-interested reader to \cite{watrous}.
+% \begin{equation}
+% p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond,
+% \end{equation}
+% where
+% \begin{equation}
+% \|\PP - \QQ\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left( (\PP - \QQ) \otimes \1\right) (\proj{\psi}) \|_1.
+% \end{equation}
+% The quantum state $\ket{\psi_0}$ maximizing the diamond norm above is called the
+% \emph{discriminator}, and can be computed e.g. using semidefinite programming (SDP)
+% \cite{watrous,watrous2021simplier}. Furthermore,  using the proof of the Holevo-Helstrom theorem, it is
+% possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
+% discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
+% interested reader to \cite{watrous}.
 
@@
 \end{enumerate}
-Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt in for
-fine-grained control over the execution of the circuits. For instance, suppose the user wants to
-simulate the discrimination experiment on a noisy simulator. In such a case, they can define
-the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
+Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt in
+for fine-grained control over the execution of the circuits. For instance, suppose the user wants to
+simulate the discrimination experiment on a noisy simulator. In such a case, they can define the
+necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
 e.g. to add noise to particular gates, and then run using any Qiskit backend by the user. Finally,
@@
 The PyQBench library also contains a readily available implementation of all necessary components
-needed to run discrimination experiments for parametrized Fourier family of measurements, defined
-previously in Section \ref{sec:fourier}. However, if one only wishes to use this particular family
-of measurements in their benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's command line interface allows running the benchmarking process without
-writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the benchmark
-to be performed and the description of the backend on which the benchmark should be run. Notably,
-the YAML configuration files are reusable. The same benchmark can be used with different backends
-and vice versa.
-
-The following section describes important architectural decisions taken when creating PyQBench, and
-how they affect the end-user experience.
+needed to run discrimination experiments for parametrized Fourier family of measurements (see
+\cite{appendix}). However, if one only wishes to use this particular family of measurements in their
+benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's
+command line interface allows running the benchmarking process without writing Python code. The
+configuration of CLI is done by YAML \cite{yaml} files describing the benchmark to be performed and
+the description of the backend on which the benchmark should be run. The same benchmark can be used
+with different backends and vice versa.
 
@@
 \texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead
-refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the reference manual
-\cite{pyqbenchdocs}.
+refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the
+reference manual \cite{pyqbenchdocs}.
 
@@
 PyQBench is built around the Qiskit \cite{qiskit} ecosystem. Hence, both the CLI tool and the
-\texttt{qbench} library can use any Qiskit--compatible backend. This includes, IBM Q
-backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
-through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider, qiskit-braket-provider-github}).
+\texttt{qbench} library can use any Qiskit--compatible backend. This includes, IBM Q backends
+(available by default in Qiskit) and Amazon Braket devices and simulators (available through
+\texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider,
+qiskit-braket-provider-github}).
 
@@
 them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
-backend. An example of such file can be found in Section \ref{sec:examples}, and the detailed description of
-the expected format can be found at PyQBench's documentation.
+backend. An example of such file can be found in Section \ref{sec:examples}, and the detailed
+description of the expected format can be found at PyQBench's documentation.
 
@@
 Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
-Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
-fashion to allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
-is \texttt{disc-fourier}.
+Fourier family of measurements), but we decided on hierarchically structuring the CL to allow for
+future extensions. Thus, the only accepted value of \texttt{<benchmark-type>} is
+\texttt{disc-fourier}.
 %
@@
 \begin{itemize}
-	\item \texttt{benchmark}: run benchmarks. This creates either a result YAML file containing
-	the measurements or an intermediate YAML file for asynchronous experiments.
+	\item \texttt{benchmark}: run benchmarks. This creates either a result YAML file containing the
+		measurements or an intermediate YAML file for asynchronous experiments.
 	\item \texttt{status}: query status of experiments submitted for given benchmark. This command
@@
 		synchronous experiments.
-	\item \texttt{tabulate}: interpret the results of a benchmark and summarize them in the CSV file.
+	\item \texttt{tabulate}: interpret the results of a benchmark and summarize them in the CSV
+	file.
 \end{itemize}
@@
 \subsubsection{Asynchronous vs. synchronous execution}
-PyQBench's CLI can be used in synchronous and asynchronous modes. The
-mode of execution is defined in the YAML file describing the backend (see Section
-\ref{sec:examples} for an example of this configuration). We decided to couple the mode of execution to
-the backend description because some backends cannot work in asynchronous mode.
+PyQBench's CLI can be used in synchronous and asynchronous modes. The mode of execution is defined
+in the YAML file describing the backend (see Section \ref{sec:examples} for an example of this
+configuration). We decided to couple the mode of execution to the backend description because some
+backends cannot work in asynchronous mode.
 
 When running \texttt{qbench disc-fourier benchmark} in asynchronous mode, the PyQBench submits all
-the circuits needed to perform a benchmark and then writes an intermediate YAML file
-containing metadata of submitted experiments. In particular, this metadata contains information on
-correlating submitted job identifiers with particular circuits. The intermediate file can be
-used to query the status of the submitted jobs or to resolve them, i.e. to wait for their completion
-and get the measurement outcomes.
+the circuits needed to perform a benchmark and then writes an intermediate YAML file containing
+metadata of submitted experiments. In particular, this metadata contains information on correlating
+submitted job identifiers with particular circuits. The intermediate file can be used to query the
+status of the submitted jobs or to resolve them, i.e. to wait for their completion and get the
+measurement outcomes.
 
@@
 downside, however, is that if the script is interrupted while the command is running, the
-intermediate results will be lost. Therefore, we recommend using asynchronous mode
-whenever possible.
+intermediate results will be lost. Therefore, we recommend using asynchronous mode whenever
+possible.
 
 \section{Illustrative examples}
-\label{sec:examples}
-In this section, we present two examples demonstrating the usage of PyQBench. In the first example,
-we show how to implement a discrimination scheme for a user--defined measurement and possible ways
-of using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
-CLI. We show how to prepare the input files for the benchmark and how to run it using the
-\texttt{qbench} tool.
+\label{sec:examples} In this section, we present two examples demonstrating the usage of PyQBench.
+In the first example, we show how to implement a discrimination scheme for a user--defined
+measurement and possible ways of using this scheme with \texttt{qbench} library. The second example
+demonstrates the usage of the CLI. We show how to prepare the input files for the benchmark and how
+to run it using the \texttt{qbench} tool.
 
@@
 benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
-as the following list of steps::
+as the following list of steps:
 
 \begin{enumerate}
-
   \item Preparing configuration files describing the backend and the experiment scenario.
-\item Submitting/running experiments. Depending on the experiment scenario, execution can be synchronous, or asynchronous.
+  \item Submitting/running experiments. Depending on the experiment scenario, execution can be
+		synchronous, or asynchronous.
   \item (optional) Checking the status of the submitted jobs if the execution is asynchronous.
@@
 \subsubsection{Preparing configuration files}
-The configuration of PyQBench CLI is driven by YAML files. The first configuration file
-describes the experiment scenario to be executed. The second file describes the backend.
-Typically, this backend will correspond to the physical device to be benchmarked, but for testing
-purposes one might as well use any other Qiskit--compatible backend including simulators.
-Let us first describe the experiment configuration file, which might look as follow.
+The configuration of PyQBench CLI is driven by YAML files. The first configuration file describes
+the experiment scenario to be executed. The second file describes the backend. Typically, this
+backend will correspond to the physical device to be benchmarked, but for testing purposes, one
+might as well use any other Qiskit--compatible backend including simulators. Let us first describe
+the experiment configuration file, which might look as follow.
 \begin{lstlisting}[language=Python, caption=Defining the experiment, label=lst:experiment]
@@
 
-The second configuration file describes the backend. We decided to decouple the
-experiment and the backend files because it facilitates their reuse. For instance, the same
-experiment file can be used to run benchmarks on multiple backends, and the same backend description
-file can be used with multiple experiments.
+The second configuration file describes the backend. We decided to decouple the experiment and the
+backend files because it facilitates their reuse. For instance, the same experiment file can be used
+to run benchmarks on multiple backends, and the same backend description file can be used with
+multiple experiments.
 
@@
 the interested reader to the PyQBench's documentation. Below we describe an example YAML file
-describing IBM Q backend named
-Quito.
+describing IBM Q backend named Quito.
 \begin{lstlisting}[language=Python, caption=IBMQ backend, label=lst:backend]
@@
 \end{lstlisting}
-The output file will be printed to stdout. Optionally, the \texttt{- -output OUTPUT} parameter might be provided to write the output to the \texttt{OUTPUT} file instead.
+The output file will be printed to stdout. Optionally, the \texttt{- -output OUTPUT} parameter might
+be provided to write the output to the \texttt{OUTPUT} file instead.
 \begin{lstlisting}[language=Python]
@@
 \begin{itemize}
-	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, \texttt{job\_ids} correlated with the circuit they correspond to.
-	\item If the backend is synchronous, the output will contain measurement outcomes (bitstrings) for each of the circuits run.
+	\item If the backend is asynchronous, the output will contain intermediate data containing, amongst
+		others, \texttt{job\_ids} correlated with the circuit they correspond to.
+	\item If the backend is synchronous, the output will contain measurement outcomes (bitstrings)
+		for each of the circuits run.
 \end{itemize}
 
-For synchronous experiment, the part of output looks similar to the one below. The whole YAML file can be seen in \ref{app:example}.
+For the synchronous experiment, the part of output looks similar to the one below. The whole YAML
+file can be seen in \ref{app:example}.
 %Consider the particular experiment data
@@
 \section{Impact}
-With the surge of availability of quantum computing architectures in recent
-years it becomes increasingly difficult to keep track of their relative
-performance. To make this case even more difficult, various providers give
-access to different figures of merit for their architectures. Our package allows
-the user to test various architectures, available through \texttt{qiskit} and
-Amazon BraKet using problems with simple operational interpretation. We provide
-one example built-in in the package. Furthermore, we provide a powerful tool for
-the users to extend the range of available problems in a way that suits their
-needs.
+With the surge of availability of quantum computing architectures in recent years it becomes
+increasingly difficult to keep track of their relative performance. To make this case even more
+difficult, various providers give access to different figures of merit for their architectures. Our
+package allows the user to test various architectures, available through \texttt{qiskit} and Amazon
+BraKet using problems with simple operational interpretation. We provide one example built-in in the
+package. Furthermore, we provide a powerful tool for the users to extend the range of available
+problems in a way that suits their needs.
 
-Due to this possibility of extension, the users are able to test specific
-aspects of their architecture of interest. For example, if their problem is
-related to the amount of coherence (the sum of absolute value of off-diagonal
-elements) of the states present during computation, they are able to quickly
-prepare a custom experiment, launch it on desired architectures, gather the
-result, based on which they can decide which specific architecture they should
-use.
+Due to this possibility of extension, the users are able to test specific aspects of their
+architecture of interest. For example, if their problem is related to the amount of coherence (the
+sum of absolute value of off-diagonal elements) of the states present during computation, they are
+able to quickly prepare a custom experiment, launch it on desired architectures, gather the result,
+based on which they can decide which specific architecture they should use.
 
-Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under an open
-source license which will allow users to utilize and extend our package in their
-specific applications.
+Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under an open source
+license which will allow users to utilize and extend our package in their specific applications.
 
@@
 
-In this study, we develop  a Python library PyQBench, an innovative open-source framework for benchmarking
-gate-based quantum computers.
+In this study, we develop a Python library PyQBench, an innovative open-source framework for
+benchmarking gate-based quantum computers.
 
 %%%%%%%%%%%%%%
-PyQBench can benchmark NISQ devices by verifying their capability of
-discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parameterized Fourier
-family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
-measurements instead of predefined ones.
+PyQBench can benchmark NISQ devices by verifying their capability of discriminating between two von
+Neumann measurements. PyQBench offers a simplified, ready-to-use, command line interface (CLI) for
+running benchmarks using a predefined parameterized Fourier family of measurements. For more
+advanced scenarios, PyQBench offers a way of employing user-defined measurements instead of
+predefined ones.
 \section{Conflict of Interest}
-We wish to confirm that there are no known
-conflicts of interest associated with this publication and there has been no
-significant financial support for this work that could have influenced its out-
-come.
+We wish to confirm that there are no known conflicts of interest associated with this publication
+and there has been no significant financial support for this work that could have influenced its
+out- come.
 
@@
 
-This work is  supported by
-the project “Near-term quantum computers Challenges, optimal implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the Team-Net programme of the Foundation for Polish Science co-financed by the European Union under the European Regional Development Fund.
-PL is also a holder of European Union scholarship through the European Social Fund,
-grant InterPOWER (POWR.03.05.00-00-Z305).
-
-% \begin{thebibliography}{00}
-% \bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.
-% \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
-% \bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
-% \bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
-% \bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
-% \bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
-% \bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
-% \bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
-% \bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
-% \bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
-% \bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
-% \bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
-% \bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
-% \bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
-% \bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
-% \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
-(2021).
-Benchmarking near-term quantum computers via random circuit sampling.
-arXiv preprint arXiv:2105.05232.
-% \bibitem{knill2008randomized}
-% Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
-B., Jost, J.
-D., Langer, C., Ozeri, R., Seidelin, S.,  Wineland, D.
-J.
-(2008).
-Randomized benchmarking of quantum gates.
-Physical Review A, 77(1), 012307.
-% \bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
-% \bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
-% \bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
-% \bibitem{cross2019validating}
-% Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
-% \bibitem{moll2018quantum}
-% Moll, N., Barkoutsos, P., Bishop, L.
-S., Chow, J.
-M., Cross, A., Egger, D.
-J., Filipp, S., Fuhrer, A., Gambetta, J.
-M., Ganzhorn, M., Kandala, A., Mezzacapo, A., M{\"u}ller, P., Riess, W., Salis, G., Smolin, J., Tavernelli, I.,  Temme, K.
-(2018).
-Quantum optimization using variational algorithms on near-term quantum devices.
-Quantum Science and Technology, 3(3), 030503.
-% \bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S.
-(2022).
-Quantum volume in practice: What users can expect from NISQ devices.
-IEEE Transactions on Quantum Engineering, 3, 1-19.
-% 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
-% \bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
-% 	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
-S., Smith, K.
-N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F.
-T.
-(2022).
-Supermarq: A scalable quantum benchmark suite.
-In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp.
-587-603).
-IEEE.
-% \bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
-% \bibitem{qiskit-randomized} The web resource at
-% \url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
-% \bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
-% \bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
-% \bibitem{cross-entropy-bench} The web resource at
-% \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
-% \bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for
-% optimal single-shot discrimination of quantum measurements. Physical Review A
-% 98.4, 042103.
-% \bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.
-% \bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
-% \bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
-% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-% \bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
-% \bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
-% \bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
-% \bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
-% \bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
-% \bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
-% \bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
-% \bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-% \bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.
-% \bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
-(2021).
-On the optimal certification of von Neumann measurements.
-Scientific Reports, 11(1), 3623.
-% \bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
-% \bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
-% \bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H.
-(2017).
-Benchmarking gate-based quantum computers.
-Computer Physics Communications, 220, 44-55.
-% \bibitem{zhukov2019quantum} Zhukov, A.
-A., Kiktenko, E.
-O., Elistratov, A.
-A., Pogosov, W.
-V.,  Lozovik, Y.
-E.
-(2019).
-Quantum communication protocols as a benchmark for programmable quantum computers.
-Quantum Information Processing, 18(1), 31.
-% \bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
-% and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
-% qubits. Physical Review A 99(6), 062323.
-% \bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A.
-(2019).
-A generative modeling approach for benchmarking and training shallow quantum circuits.
-npj Quantum Information, 5(1), 45.
-
-% \end{thebibliography}
+This work is supported by the project “Near-term quantum computers Challenges, optimal
+implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried
+out within the Team-Net programme of the Foundation for Polish Science co-financed by the European
+Union under the European Regional Development Fund. PL is also a holder of European Union
+scholarship through the European Social Fund, grant InterPOWER (POWR.03.05.00-00-Z305).
 

### 2023-04-13 txt/manuscript_short.tex
Update short manuscript and supplemental material

@@
 \newtheorem{scheme}{Scheme}
+
+\usepackage{xr}
+\externaldocument{supplemental}
 
@@
 discrimination scheme used in PyQBench and practical considerations on how to implement it taking
-into account the limitations of the current NISQ devices.
+into account the limitations of the current NISQ devices. We encourage the readers interested
+in a more in--depth discussion of the mathematical foundations behind our discrimination scheme to read
+Section \ref{app:preliminaries} in the supplemental materials.
 
@@
 times for both $\PP_U$ and $\PP_\Id$.
-
-Unsurprisingly, both the $\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be
-chosen specifically for given $U$ to maximize the probability of a correct guess. The detailed
-description how these choices are made in \cite{watrous}, and for now we will focus only how this
-scheme can be implemented on the actual devices, assuming that all the components are known.
 
@@
 needed to run discrimination experiments for parametrized Fourier family of measurements (see
-\cite{appendix}). However, if one only wishes to use this particular family of measurements in their
-benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's
-command line interface allows running the benchmarking process without writing Python code. The
-configuration of CLI is done by YAML \cite{yaml} files describing the benchmark to be performed and
-the description of the backend on which the benchmark should be run. The same benchmark can be used
-with different backends and vice versa.
+Section \ref{app:optimal-probability} in supplemental material). However, if one only wishes to use
+this particular family of measurements in their benchmarks, then using PyQBench as a command line tool
+might be more straightforward. PyQBench's command line interface allows running the benchmarking process
+without writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the
+benchmark to be performed and the description of the backend on which the benchmark should be run.
+The same benchmark can be used with different backends and vice versa.
 
@@
 \section{Illustrative examples}
-\label{sec:examples} In this section, we present two examples demonstrating the usage of PyQBench.
-In the first example, we show how to implement a discrimination scheme for a user--defined
-measurement and possible ways of using this scheme with \texttt{qbench} library. The second example
-demonstrates the usage of the CLI. We show how to prepare the input files for the benchmark and how
-to run it using the \texttt{qbench} tool.
+\label{sec:examples} In this section, we demonstrate the usage of PyQBench.
+For brevity, we decided to present only the usage of the CLI tool, as it is likely to be the most
+popular use case. We refer readers interested in implementing their discrimination schemes using
+custom measurements to PyQBench's documentation \cite{pyqbenchdocs}, where we describe the whole
+process, and to the Section \ref{app:hadamard} in the supplemental material, where we discuss
+the relevant mathematical details.
 
 \subsection{Using \texttt{qbench} CLI}
-Using PyQBench as a library allows one to conduct a two--qubits benchmark with arbitrary von Neumann
-measurement. However, as discussed in the previous guide, it requires writing some amount of code.
-For a Fourier parametrized family of measurements, PyQBench offers a simplified way of conducting
-benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
-as the following list of steps:
+PyQBench offers a simplified way of conducting benchmarks using a Command Line Interface (CLI).
+The workflow with PyQBench's CLI can be summarized as the following list of steps:
 
@@
 
-For the synchronous experiment, the part of output looks similar to the one below. The whole YAML
-file can be seen in \ref{app:example}.
+For the synchronous experiment, the part of the output looks similar to the one below. The whole YAML
+file can be seen in Section \ref{app:example.} in the supplemental material.
 %Consider the particular experiment data
@@
 \end{lstlisting}
-A sample CSV file is provided below:
+A sample CSV file is provided in Table \ref{fig:tabulateresults}.
 \begin{table}[ht!]
@@
 
-In this study, we develop a Python library PyQBench, an innovative open-source framework for
+In this paper, we presented a Python library PyQBench, an innovative open-source framework for
 benchmarking gate-based quantum computers.
-
-%%%%%%%%%%%%%%
 PyQBench can benchmark NISQ devices by verifying their capability of discriminating between two von
@@
 predefined ones.
+
 \section{Conflict of Interest}

### 2023-04-13 software_x_submission/supplemental.tex
Add shortened manuscript and supplemental material to submission package

--- 2023-03-23 txt/manuscript.tex
@@
 \usepackage{subcaption}
-
-\definecolor{codegreen}{rgb}{0.25,0.93,0.31}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
-
-%
-%\lstdefinestyle{mystyle}{
-%	backgroundcolor=\color{backcolour},
-%	commentstyle=\color{codegreen},
-%	keywordstyle=\color{magenta},
-%	numberstyle=\tiny\color{codegray},
-%	stringstyle=\color{codepurple},
-%	basicstyle=\ttfamily\footnotesize,
-%	breakatwhitespace=false,
-%	breaklines=true,
-%	captionpos=b,
-%	keepspaces=true,
-%	numbers=left,
-%	numbersep=5pt,
-%	showspaces=false,
-%	showstringspaces=false,
-%	showtabs=false,
-%	tabsize=2
-%}
-%
-%\lstset{style=mystyle}
-\lstset{frame=tb,
-	language=Python,
-	aboveskip=3mm,
-	belowskip=3mm,
-	showstringspaces=false,
-	columns=flexible,
-	basicstyle={\small\ttfamily},
-%	numberstyle=\color{blue},
-%	keywordstyle=\color{blue},
-%	commentstyle=\color{PineGreen},
-%	stringstyle=\color{ForestGreen},
-	breaklines=true,
-	breakatwhitespace=true,
-	tabsize=3,
-	escapeinside={@}{@},
-%	literate=
-%	{0}{{{\color{red}0}}}1
-%	{1}{{{\color{red}1}}}1
-%	{2}{{{\color{red}2}}}1
-%	{3}{{{\color{red}3}}}1
-%	{4}{{{\color{red}4}}}1
-%	{5}{{{\color{red}5}}}1
-%	{6}{{{\color{red}6}}}1
-%	{7}{{{\color{red}7}}}1
-%	{8}{{{\color{red}8}}}1
-%	{9}{{{\color{red}9}}}1
-%    {v0}{{{\color{black}v0}}}1 %% we can not style only numeric literals
-%    {v1}{{{\color{black}v1}}}1
-}
-\restylefloat{table}
 
@@
 
-\title{PyQBench: a Python library for benchmarking gate-based quantum computers}
+  \title{
+    PyQBench: a Python library for benchmarking gate-based quantum computers\\
+    Supplemental material
+  }
 
@@
 
-\begin{abstract}
-
-We introduce PyQBench, an innovative open-source framework for benchmarking
-gate-based quantum computers. PyQBench can benchmark NISQ devices by verifying their capability of
-discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
-family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
-measurements instead of predefined ones.
-
-\end{abstract}
-
-\begin{keyword}
-Quantum computing \sep
-Benchmarking quantum computers \sep
-Discrimination of quantum measurements \sep
-Discrimination of von Neumann measurements \sep
-Open-source \sep
-Python programming
-
-\PACS 03.67.-a \sep 03.67.Lx
-
-\MSC 81P68
-
-\end{keyword}
-
 \end{frontmatter}
-
-\section*{Current code version}
-\label{}
-
-\begin{table}[H]
-\begin{tabular}{|l|p{5.5cm}|p{7.5cm}|}
-\hline
-C1 & Current code version & 0.1.1 \\
-\hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/iitis/PyQBench} \\
-\hline
-C3 & Code Ocean compute capsule & \texttt{https://codeocean.com/capsule/ 89088992-9a27-4712-8525-} \texttt{d92a9b23060f/tree}\\
-\hline
-C4 & Legal Code License & Apache License 2.0\\
-\hline
-C5 & Code versioning system used & git \\
-\hline
-C6 & Software code languages, tools, and services used & Python, Qiskit, AWS Braket \\
-\hline
-C7 & Compilation requirements, operating environments \& dependencies &
-\texttt{Python >= 3.8}\newline
-\texttt{numpy \textapprox= 1.22.0}\newline
-\texttt{scipy \textapprox= 1.7.0}\newline
-\texttt{pandas \textapprox= 1.5.0}\newline
-\texttt{amazon-braket-sdk >= 1.11.1}\newline
-\texttt{pydantic \textapprox= 1.9.1}\newline
-\texttt{qiskit \textapprox= 0.37.2}\newline
-\texttt{mthree \textapprox= 1.1.0}\newline
-\texttt{tqdm \textapprox= 4.64.1}\newline
-\texttt{pyyaml \textapprox= 6.0}\newline
-\texttt{qiskit-braket-provider \textapprox= 0.0.3}\\
-\hline
-C8 & If available Link to developer documentation/manual &
-\url{https://pyqbench.readthedocs.io/en/latest/}\\
-\hline
-C9 & Support email for questions & \url{dexter2206@gmail.com}\\
-\hline
-\end{tabular}
-\caption{Code metadata}
-\label{}
-\end{table}
-
-\linenumbers
-
-\section{Motivation and significance}
-
-Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market,
-with a wide selection of devices based on different architectures and accompanying software
-solutions. Among hardware providers offering public access to their gate--based devices, one could
-mention Rigetti \cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu \cite{xanadu}. Other vendors offer devices operating in
-different paradigms. Notably, one could mention D-Wave \cite{dwave} and their quantum
-annealers, or QuEra devices \cite{quera} based on neural atoms.  Most vendors provide their own software stack and
-application programming interface for accessing their devices. To name a few, Rigetti's computers
-are available through their Forest SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
-through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}.
-Some cloud services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified API.
-On top of that, several
-libraries and frameworks can integrate with multiple hardware vendors. Examples of such frameworks
-include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.
-
-It is well known that NISQ devices have their limitations \cite{preskillnew}. The question is to what extent those
-devices can perform meaningful computations? To answer this question, one has to devise a
-methodology for benchmarking them. For gate--based computers, on which this paper focuses, there
-already exist several approaches.
-One could mention randomized benchmarking \cite{liu2022sampling, knill2008randomized, wallman2014randomized, helsen2022general,
-	cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating, moll2018quantum, pelofske2022volume}.
-
-In this paper, we introduce a different approach to benchmarking gate--based devices with a simple
-operational interpretation. In our method, we test how well the given device is at guessing which of
-the two known von Neumann measurements were performed during the experiment. We implemented our
-approach in an open-source Python library called PyQBench. The library supports any device available
-through the Qiskit library, and thus can be used with providers such as IBM Q or Amazon Braket.
-Along with the library, the PyQBench package contains a command line tool for running most common
-benchmarking scenarios.
-
-\section{Existing benchmarking methodologies and software}
-Unsurprisingly, PyQBench is not the only software package for benchmarking gate--based devices.
-While we believe that our approach has significant benefits over other benchmarking techniques, for
-completeness, in this section we discuss some of the currently available similar software.
-
-Probably the simplest benchmarking method one could devise is simply running known algorithms and
-comparing outputs with the expected ones. Analyzing the frequency of the correct outputs, or the
-deviation between actual and expected outputs distribution provides then a metric of the performance
-of a given device.
- Libraries such as Munich Quantum Toolkit (MQT) \cite{mqt2022, mqt-bench}
-or
- SupermarQ \cite{supermarq, supermarkq-github}
-  contain
-benchmarks leveraging multiple algorithms, such as Shor's algorithm or Grover's algorithm.
-% or  implementing e.g. GHZ state \cite{ghz}.
-Despite being intuitive and easily interpretable, such benchmarks may have some problems. Most
-importantly, they assess the usefulness of a quantum device only for a very particular algorithm,
-and it might be hard to extrapolate their results to other algorithms and applications. For
-instance, the inability of a device to consistently find factorizations using Shor's algorithms
-does not tell anything about its usefulness in Variational Quantum Algorithm's.
-
-Another possible approach to benchmarking quantum computers is randomized benchmarking. In this approach, one samples circuits to be run from some predefined set
-of gates (e.g. from the Clifford group) and tests how much the output distribution obtained from the
-device running these circuits differs from the ideal one. It is also common to concatenate randomly
-chosen circuits with their inverses (which should yield the identity circuit) and run those
-concatenated circuits on the device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil \cite{forest-benchmarking}.
-
-Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
-characterizes capacity of a device for solving computational problems. It takes into account
-multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library allows one to
-measure quantum volume of a device by using its \texttt{qiskit.ignis.verifica \\ tion.quantum\_volume}.
-Other implementations of Quantum Volume can be found as well, see e.g. \cite{volume-in-practice}.
-
-% In
-% cross--entropy benchmarkig a random quantum circuit is executed on a quantum computer multiple
-% times. Then, the obtained measurement outcomes are used for computing cross--entropy fidelity
-% $F_{XEB} \in [0, 1]$. A value of 0 means that results obtained from the device are no better then
-% random guessing, whereas value of 1 correspond to a perfect, noiseless execution of the circuit.
-% Packages implementing cross--entropy benchmarking include e.g. \cite{cross-entropy-bench}.
-
-\section{Preliminaries and discrimination scheme approach}
-
-In this section we describe how the benchmarking process in PyQBench works. To do so, we first
-discuss necessary mathematical preliminaries. Then, we present the general form of the
-discrimination scheme used in PyQBench and practical considerations on how to implement it taking
-into account limitations of the current NISQ devices.
-
-\subsection{Mathematical preliminaries}\label{sec:maths}
-
-Let us first recall the definition of a von Neumann measurement, which is the only type of
-measurement used in PyQBench. A von Neumann measurement $\PP$ is a collection of rank--one projectors
-$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to identity,
-i.e. $ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$,
-one can construct a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this
-case we say that $\PP_{U}$ is described by the matrix $U$.
-
-Typically, NISQ devices can only perform measurements in computational $Z$-basis, i.e. $U=\1$.
-To implement an arbitrary von Neumann measurement $\PP_{U}$, one has to first apply $U^\dagger$
-to the measured system and then follow with $Z$-basis measurement. This process, depicted in Fig.
-\ref{fig:vonneumann}, can be viewed as performing a change of basis in which measurement is
-performed prior to measurement in the computational basis.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.7]{pics/vonneuman}
-	\caption{Implementation of a von Neumann measurement using measurement in computational basis.
-	The upper circuit shows a symbolic representation of a von Neumann measurement $\PP_{U}$. The
-	bottom, equivalent circuit depicts its decomposition into a change of basis followed
-	by measurement in the $Z$ basis.}
-	\label{fig:vonneumann}
-\end{figure}
-
-\subsection{Discrimination scheme}\label{sec:discrimination-scheme}
-
-Benchmarks in PyQBench work by experimentally determining the probability of correct discrimination
-between two von Neumann measurements by the device under test and comparing the result with the
-ideal, theoretical predictions.
-
-Without loss of generality\footnote{Explaining why we can consider only discrimination scheme between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper.
-See \cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between single qubit measurements
-$\PP_\Id$, performed in the computational Z-basis, and an alternative measurement $\PP_U$ performed
-in the basis $U$. Note, however, that the discrimination scheme described below can work
-regardless of dimensionality of the system, see \cite{puchala2018strategies} for details.
-
-In general, the discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme}, requires an
-auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the 
-measurements,  either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
-outcome $i$, we choose another POVM $\mathcal{P}_{V_i}$ and perform it on the second
-qubit, obtaining the output in $j$. Finally, if $j=0$, we say that the performed measurement is
-$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
-same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
-probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
-times for both $\PP_U$ and $\PP_\Id$.
-
-Unsurprisingly, both the
-$\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be chosen specifically for
-given $U$ to maximize the probability of a correct guess. The detailed description  how these
-choices are made in \cite{watrous}, and for now we will focus
-only how this scheme can be implemented on the actual devices, assuming that all the components are known.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.7]{pics/theoretical_scheme}
-	\caption{Theoretical  scheme of discrimination  between von Neumann measurements $\PP_{U}$ and $\PP_\Id$. }
-	\label{fig:theoretical_scheme}
-\end{figure}
-
-\subsubsection{Implementation of discrimination scheme on actual NISQ devices}
-
-Current NISQ devices are unable to perform conditional measurements, which is the biggest
-obstacle to implementing our scheme on real hardware. However, we circumvent this problem by
-slightly adjusting our scheme so that it only uses components available on current devices.
-For this purpose, we use two possible options: using a postselection or a direct sum $V_0^\dagger\oplus V_1^\dagger$.
-
-\begin{scheme}(Postselection)
-
-	The first idea uses a postselection scheme. In the original scheme, we measure the first qubit
-	and only then determine which measurement should be performed on the second one. Instead of
-	doing this choice, we can run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and
-	measure both qubits. We then discard the results of the circuit for which label $i$ does not match
-	measurement label $k$. Hence, the circuit for postselection looks as depicted in Fig.
-	\ref{fig:postselection}.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[scale=1.7]{pics/postselection_no_channels}
-
-		\caption{
-			A schematic representation of the setup for distinguishing
-			measurements $\PP_{U}$ and $\PP_{\Id}$ using postselection approach.
-			In postselection scheme, one runs such circuits for both $k=0,1$ and discards results for cases when there is a mismatch between $k$ and $i$.
-		}\label{fig:postselection}
-	\end{figure}
-
-	To perform the benchmark, one needs to run multiple copies of the postselection circuit,
-	with both $\PP_U$ and $\PP_\1$. Each circuit has to be run in both variants, one with final
-	measurement $\PP_{V_0}$ and the second with the final measurement $\PP_{V_1}$.
-	The experiments can thus be grouped into classes identified by tuples of the form
-	$(\mathcal{Q}, k, i, j)$, where $\mathcal{Q} \in \{\PP_U, \PP_\Id\}$ denotes the chosen
-	measurement, $k \in \{0,1\}$ designates the final measurement used, and $i \in \{0,1\}$ and $j
-	\in \{0,1\}$ being the labels of outcomes as presented in Fig. \ref{fig:postselection}.
-	We then discard all the experiments for which $i \ne k$. The total number of valid experiments
-	is thus:
-
-	\begin{equation}
-	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}.
-	\end{equation}
-
-	Finally, we count the valid experiments resulting in successful discrimination.
-	If we have chosen $\PP_U$, then we guess correctly iff $j=0$. Similarly, for
-	$P_\Id$, we guess correctly iff $j=1$. If we define
-	\begin{eqnarray}
-	N_{\PP_U} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_U, k = i, j = 0\}, \\
-	N_{\PP_\Id} &= \#\{(\mathcal{Q}, k, i, j): \mathcal{Q} = \PP_\Id, k = i, j = 1\},
-	\end{eqnarray}
-	then the empirical success probability can be computed as
-
-	\begin{equation}
-	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{N_{\PP_U} + N_{\PP_\Id}}{N_{\text{total}}}.
-	\end{equation}
-	The $p_{\text{succ}}$ is the quantity reported to the user as the result of the benchmark.
-\end{scheme}
-
-\begin{scheme}(Direct sum)
-
-The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation.     Here, instead of performing a conditional
-measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits presented in
-Fig.~\ref{fig:controlled}.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[width=0.8\textwidth]{pics/controlled_unitary}
-
-		\caption{ A schematic representation of the setup for distinguishing
-			measurements $\PP_{U}$ and $\PP_{\Id}$ using the $V_0^\dagger \oplus V_1^\dagger$ direct sum.
-		}\label{fig:controlled}
-	\end{figure}
-
-	One can see why such a circuit is equivalent to the original discrimination scheme.
-	If we rewrite the block-diagonal matrix $V_0^\dagger \oplus V_1^\dagger$ as follows:
-	\begin{equation}
-		\label{eq:directsum}
-		V_0^\dagger \oplus V_1^\dagger = \proj{0}\otimes V_0^\dagger + \proj{1} \otimes V_1^\dagger,
-	\end{equation}
-	we can see that the direct sum in Eq. \eqref{eq:directsum} commutes with the measurement on the
-	first qubit. Thanks to this, we can switch the order of operations to obtain the circuit from
-	Fig. \ref{fig:directsum}. Now, depending on the outcome $i$, one of the summands in
-	Eq. \eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in the
-	original scheme.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[width=\textwidth]{pics/direct_sum}
-		\caption{Rewritten representation of the setup for distinguishing
-		measurements $\PP_{U}$ and $\PP_{\Id}$ using the $V_0^\dagger \oplus V_1^\dagger$ direct
-		sum.
-		}\label{fig:directsum}
-	\end{figure}
-
-	In this scheme, the experiment can be characterized by a pair $(\mathcal{Q}, i,j)$, where
-	$\mathcal{Q} = \{ \PP_{U}, \PP_{\Id} \}$ and $i,j \in \{0,1\}$ are the output labels. The number of successful trials for $U$ and $\Id$,
-	respectively, can be written  as
-	\begin{eqnarray}
-	N_{\PP_U} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_U, j = 0\}, \\
-	N_{\PP_\Id} &= \#\{(\mathcal{Q},  i, j): \mathcal{Q} = \PP_\Id, j = 1\}.
-	\end{eqnarray}
-	Then, the probability of correct discrimination between $\PP_{U} $ and $\PP_\Id$ is given by
-	\begin{equation}
-	p_{\text{succ}} = \frac{N_{\PP_{U}} + N_{\PP_{\Id}}}{N_{\text{total}}},
-	\end{equation}
-	where $N_{\text{total}}$ is the number of trials.
-\end{scheme}
-
-\subsubsection{Importance of choosing the optimal discrimination scheme}
-In principle, the schemes described in the previous section could be used with any choice of
-$\ket{\psi_0}$ and final measurements $\PP_{V_i}$. However, we argue that it is best to choose those
-components in such a way that they maximize the probability of correct discrimination. To see that,
-suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ yields the theoretical upper bound
-of discriminating between two measurements of one, i.e. on a perfect quantum computer you will always
-make a correct guess. Then, on real hardware, we might obtain any empirical value in range $\left[\frac{1}{2},
-1\right]$. On the other hand, if we choose the components of our scheme such that the successful
-discrimination probability is only $\frac{3}{5}$, the possible range of empirically obtainable probabilities
-is only $\left[\frac{1}{2}, \frac{3}{5}\right]$. Hence, in the second case, the discrepancy between theoretical and empirical
-results will be less pronounced.
-
-\subsubsection{Constructing optimal discrimination scheme}
-To construct the optimal discrimination scheme, one starts by calculating the probability of correct discrimination.
-Using the celebrated result by Helstrom~\cite{helstrom1976quantum}, one finds that the  optimal probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$, is
-\begin{equation}
-p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond,
-\end{equation}
-where
-\begin{equation}
-\|\PP - \QQ\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left( (\PP - \QQ) \otimes \1\right) (\proj{\psi}) \|_1.
-\end{equation}
-The quantum state $\ket{\psi_0}$ maximizing the diamond norm above is called the
-\emph{discriminator}, and can be computed e.g. using semidefinite programming (SDP)
-\cite{watrous,watrous2021simplier}. Furthermore,  using the proof of the Holevo-Helstrom theorem, it is
-possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
-discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
-interested reader to \cite{watrous}.
-
-\section{Discrimination scheme for parameterized Fourier family and implementation}
-\label{sec:fourier}
-So far, we only discussed how the discrimination is performed assuming that all needed components
-$\ket{\psi_0}$, $V_0$, and $V_1$ are known. In this section, we provide a concrete example using
-parametrized Fourier family of measurements.
-
-The parametrized Fourier family of measurements is defined as a set of the measurements
-$\{\PP_{U_\phi}\colon \phi \in [0, 2\pi]\}$, where 
-\begin{equation}
-U_\phi = H
-\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger,
-\end{equation}
-and $H$ is the Hadamard matrix of dimension two. For each element of this set, the discriminator is a Bell state:
-\begin{equation}
-\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \left( \ket{00} + \ket{11} \right).
-\end{equation}
-Observe that $\ket{\psi_0}$ does not depend on the angle $\phi$. However, the unitaries $V_0$,
-$V_1$ depend on $\phi$ and take the following form:
-\begin{equation}
-V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
-\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
-	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
-\end{equation}
-\begin{equation}
-V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
-\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
-&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
-\end{equation}
-Finally, the theoretical probability of correct discrimination between von Neumann
-measurements $\PP_{U_\phi}$ and $\PP_{\Id}$ is given by
-\begin{equation}
-p_{\text{succ}}(\PP_{U_\phi}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
-\end{equation}
-We explore the construction of $\ket{\psi_0}$, $V_0$ and $V_1$ for parametrized Fourier family of measurements in
-\ref{app:optimal-probability}.
-
- \section{Software description}
- \label{}
- This section is divided into two parts.
- In Section~\ref{sec:sortware-functionalities} we describe functionalities of PyQBench
- package. Next, in Section~\ref{sec:sortware-architecture}, we give a general overview of the
- software architecture.
-
-\subsection{Software Functionalities}\label{sec:sortware-functionalities}
-
-The PyQBench can be used in two modes: as a Python library and as a CLI script. When used as a
-library, PyQBench allows the customization of discrimination scheme. The user provides
-a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\psi_0}$,
-and unitaries $V_0$ and $V_1$ describing the final measurement. The PyQBench library provides then
-the following functionalities.
-
-\begin{enumerate}
-	\item Assembling circuits for both postselection and direct sum--based discrimination schemes.
-	\item Executing the whole benchmarking scenario on specified backend (either real hardware or
-	software simulator).
-	\item Interpreting the obtained outputs in terms of discrimination probabilities.
-\end{enumerate}
-Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt in for
-fine-grained control over the execution of the circuits. For instance, suppose the user wants to
-simulate the discrimination experiment on a noisy simulator. In such a case, they can define
-the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
-e.g. to add noise to particular gates, and then run using any Qiskit backend by the user. Finally,
-PyQBench can be used to interpret the measurements to obtain discrimination probability.
-
-The PyQBench library also contains a readily available implementation of all necessary components
-needed to run discrimination experiments for parametrized Fourier family of measurements, defined
-previously in Section \ref{sec:fourier}. However, if one only wishes to use this particular family
-of measurements in their benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's command line interface allows running the benchmarking process without
-writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the benchmark
-to be performed and the description of the backend on which the benchmark should be run. Notably,
-the YAML configuration files are reusable. The same benchmark can be used with different backends
-and vice versa.
-
-The following section describes important architectural decisions taken when creating PyQBench, and
-how they affect the end-user experience.
-
-\subsection{Software Architecture}\label{sec:sortware-architecture}
-
-\subsubsection{Overview of the software structure}
-As already described, PyQBench can be used both as a library and a CLI. Both functionalities are
-implemented as a part of \texttt{qbench} Python package. The exposed CLI tool is also named
-\texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead
-refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the reference manual
-\cite{pyqbenchdocs}.
-
-PyQBench can be installed from official Python Package Index (PyPI) by running \texttt{pip install
-pyqbench}. In a properly configured Python environment the installation process should also make the
-\texttt{qbench} command available to the user without a need for further configuration.
-
-\subsubsection{Integration with hardware providers and software simulators}
-
-PyQBench is built around the Qiskit \cite{qiskit} ecosystem. Hence, both the CLI tool and the
-\texttt{qbench} library can use any Qiskit--compatible backend. This includes, IBM Q
-backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
-through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider, qiskit-braket-provider-github}).
-
-When using PyQBench as library, instances of Qiskit backends can be passed to functions that expect
-them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
-backend. An example of such file can be found in Section \ref{sec:examples}, and the detailed description of
-the expected format can be found at PyQBench's documentation.
-
-\subsubsection{Command Line Interface}
-\label{sec:cli}
-
-The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
-invocation is shown in listing \ref{lst:cli}.
-\begin{lstlisting}[caption=Invocation of \texttt{qbench} script, label=lst:cli]
-qbench <benchmark-type> <command> <parameters>
-\end{lstlisting}
-Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
-Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
-fashion to allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
-is \texttt{disc-fourier}.
-%
-The \texttt{qbench disc-fourier} command has four subcommands:
-
-\begin{itemize}
-	\item \texttt{benchmark}: run benchmarks. This creates either a result YAML file containing
-	the measurements or an intermediate YAML file for asynchronous experiments.
-	\item \texttt{status}: query status of experiments submitted for given benchmark. This command
-	is only valid for asynchronous experiments.
-	\item \texttt{resolve}: query the results of asynchronously submitted experiments and write the
-	result YAML file. The output of this command is almost identical to the result obtained from
-	synchronous experiments.
-	\item \texttt{tabulate}: interpret the results of a benchmark and summarize them in the CSV file.
-\end{itemize}
-%
-We present usage of each of the above commands later in section \ref{sec:examples}.
-
-\subsubsection{Asynchronous vs. synchronous execution}
-PyQBench's CLI can be used in synchronous and asynchronous modes. The
-mode of execution is defined in the YAML file describing the backend (see Section
-\ref{sec:examples} for an example of this configuration). We decided to couple the mode of execution to
-the backend description because some backends cannot work in asynchronous mode.
-
-When running \texttt{qbench disc-fourier benchmark} in asynchronous mode, the PyQBench submits all
-the circuits needed to perform a benchmark and then writes an intermediate YAML file
-containing metadata of submitted experiments. In particular, this metadata contains information on
-correlating submitted job identifiers with particular circuits. The intermediate file can be
-used to query the status of the submitted jobs or to resolve them, i.e. to wait for their completion
-and get the measurement outcomes.
-
-In synchronous mode, PyQBench first submits all jobs required to run the benchmark and then
-immediately waits for their completion. The advantage of this approach is that no separate
-invocation of \texttt{qbench} command is needed to actually download the measurement outcomes. The
-downside, however, is that if the script is interrupted while the command is running, the
-intermediate results will be lost. Therefore, we recommend using asynchronous mode
-whenever possible.
-
-\section{Illustrative examples}
-\label{sec:examples}
-In this section, we present two examples demonstrating the usage of PyQBench. In the first example,
-we show how to implement a discrimination scheme for a user--defined measurement and possible ways
-of using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
-CLI. We show how to prepare the input files for the benchmark and how to run it using the
-\texttt{qbench} tool.
-
-\subsection{Using user-defined measurement with \texttt{qbench} package}
-In this example, we will demonstrate how \texttt{qbench} package can be used with user--defined
-measurement. For this purpose, we will use $U = H$ (the Hadamard gate). The detailed calculations
-that lead to the particular form of the discriminator and final measurements can be found in
-\ref{app:hadamard}.
-\noindent
-The explicit formula for discriminator in this example reads:
-\begin{equation}
-\ket{\psi_0} = \frac{1}{\sqrt{2}} (\ket{00} + \ket{11}),
-\end{equation}
-with final measurements being equal to
-\begin{equation}
-V_0 =
-\left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
-\end{equation}
-and \begin{equation}
-V_1 =
-\left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
-\end{equation}
-where \begin{equation}
-\alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} = \cos\left( \frac{3}{8} \pi \right),
-\end{equation}
-\begin{equation}
-\beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} = \sin\left( \frac{3}{8} \pi \right).
-\end{equation}
-To use the above benchmarking scheme in PyQBench, we first need to construct circuits that can be executed by actual hardware.
-To this end, we need to represent each of the unitaries as a sequence of standard gates, keeping in mind that quantum circuits start execution from the  $\ket{00}$ state.
-The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
-\begin{figure}[h!]
-	\centering
-	\includegraphics[scale=1.7]{pics/discriminator}
-	\caption{Decomposition of the Bell state $\ket{\psi_0}$. }
-	\label{fig:discriminator}
-\end{figure}
-For $V_0$ and $V_1$ observe that $V_0 = \operatorname{RY}\left(\frac{3}{4} \pi \right) $, where $\operatorname{RY}$ is rotation gate around the $Y$ axis defined by
-\begin{equation}
-\operatorname{RY}(\theta) =
-\left(\begin{array}{cc} \cos\frac{\theta}{2} & -\sin\frac{\theta}{2} \\ \sin\frac{\theta}{2} & \cos\frac{\theta}{2} \end{array}\right).
-\end{equation}
-To obtain $V_1$  we need only to swap the columns, i.e.
-\begin{equation}
-V_1 = \operatorname{RY}\left(\frac{3}{4} \pi \right) \operatorname{X}.
-\end{equation}
-Finally, the optimal probability of correct discrimination is equal to
-\begin{equation}
-p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{\sqrt{2}}{4}.
-\end{equation}
-We will now demonstrate how to implement this theoretical scheme in PyQBench. For this example we
-will use the Qiskit Aer simulator \cite{aer}. First, we import the necessary functions and classes from
-PyQBench and Qiskit. We also import \texttt{numpy} for the definition of \texttt{np.pi} constant and
-the exponential function. The exact purpose of the imported functions will be described at the point
-of their usage.
-\begin{lstlisting}[language=Python, caption=Imports needed for running benchmarking example]
-import numpy as np
-from qiskit import QuantumCircuit, Aer
-from qbench.schemes.postselection import benchmark_using_postselection
-from qbench.schemes.direct_sum import benchmark_using_direct_sum
-\end{lstlisting}
-To implement the discrimination scheme in PyQBench, we need to define all the necessary components
-as Qiskit instructions. We can do so by constructing a circuit object acting on qubits 0 and 1 and
-then converting them using \texttt{to\_instruction()} method.
-\begin{lstlisting}[language=Python, caption= Defining components for Hadamard experiment]
-def state_prep():
-	circuit = QuantumCircuit(2)
-	circuit.h(0)
-	circuit.cnot(0, 1)
-	return circuit.to_instruction()
-
-def u_dag():
-	circuit = QuantumCircuit(1)
-	circuit.h(0)
-	return circuit.to_instruction()
-
-def v0_dag():
-	circuit = QuantumCircuit(1)
-	circuit.ry(-np.pi * 3 / 4, 0)
-	return circuit.to_instruction()
-
-def v1_dag():
-	circuit = QuantumCircuit(1)
-	circuit.ry(-np.pi * 3 / 4, 0)
-	circuit.x(0)
-	return circuit.to_instruction()
-
-def v0_v1_direct_sum_dag():
-	circuit = QuantumCircuit(2)
-	circuit.ry(-np.pi * 3 / 4, 0)
-	circuit.cnot(0, 1)
-	return circuit.to_instruction()
-\end{lstlisting}
-We now construct a backend object, which in this case is an instance of Aer simulator.
-
-\begin{lstlisting}[language=Python, caption=Defining a backend]
-simulator = Aer.get_backend("aer_simulator")
-\end{lstlisting}
-
-In the simplest scenario, when one does not want to tweak execution details and simply wishes to run
-the experiment on a given backend, everything that is required is now to run
-\texttt{benchmark\_using\_postselection} or \texttt{benchmark\_using\_direct\_sum} function,
-depending on the user preference.
-
-\begin{lstlisting}[language=Python, caption=Simulation benchmark by using postselection]
-postselection_result = benchmark_using_postselection(
-	backend=simulator,
-	target=0,
-	ancilla=1,
-	state_preparation=state_prep(),
-	u_dag=u_dag(),
-	v0_dag=v0_dag(),
-	v1_dag=v1_dag(),
-	num_shots_per_measurement=10000,
-)
-\end{lstlisting}
-
-\begin{lstlisting}[language=Python, caption=Simulation benchmark by using direct sum]
-direct_sum_result = benchmark_using_direct_sum(
-	backend=simulator,
-	target=1,
-	ancilla=2,
-	state_preparation=state_prep(),
-	u_dag=u_dag(),
-	v0_v1_direct_sum_dag=v0_v1_direct_sum_dag(),
-	num_shots_per_measurement=10000,
-)
-\end{lstlisting}
-The \texttt{postselection\_result} and  \texttt{direct\_sum\_result} variables contain now the
-empirical probabilities of correct discrimination. We can compare them to the theoretical value and
-compute the absolute error.
-
-\begin{lstlisting}[language=Python, caption=Examining the benchmark results]
-p_succ = (2 + np.sqrt(2)) / 4
-print(f"Analytical p_succ = {p_succ}")
-print(
-f"Postselection: p_succ = {postselection_result}, abs. error = {p_succ - postselection_result}"
-)
-print(f"Direct sum: p_succ = {direct_sum_result}, abs. error = {p_succ - direct_sum_result}")
-\end{lstlisting}
-
-\begin{lstlisting}
-Analytical p_succ = 0.8535533905932737
-Postselection: p_succ = 0.8559797193791593, abs. error = -0.0024263287858855564
-Direct sum: p_succ = 0.85605, abs. error = -0.0024966094067262468
-\end{lstlisting}
-
-In the example presented above we used functions that automate the whole process -- from the circuit assembly, through running the simulations to interpreting the results.
-But what if we want more control over some parts of this process?
-One possibility would be to add some additional parameters to \texttt{benchmark\_using\_xyz}
-functions, but this approach is not scalable. Moreover, anticipating all possible uses cases
-isimpossible. Therefore, we decided on another approach. PyQBench provides functions performing:
-\begin{enumerate}
-\item Assembly of circuits needed for experiment, provided the components discussed above.
-\item Interpretation of the obtained measurements.
-\end{enumerate}
- The difference between the two approaches is illustrated on the diagrams in Fig. \ref{fig:diagrams}.
-
-\begin{figure}[ht!]
-	\centering
-	\begin{subfigure}[b]{0.9\textwidth}
-		\centering
-		\includegraphics[width=0.8\textwidth]{pics/scheme1}
-%		\caption{$y=x$}
-		\label{fig:simplified}
-	\end{subfigure}
-	\vfill
-	\begin{subfigure}[b]{0.9\textwidth}
-		\centering
-	\includegraphics[width=0.8\textwidth]{pics/scheme2}
-		\label{fig:execution}
-	\end{subfigure}
-	\caption{Differences between simplified (top) and user--controlled (bottom) execution of
-	benchmarks in PyQBench. Compared to simplified benchmarking, in user-controlled benchmarks the
-	user has direct access to the circuits being run, and hence can alter them (e.g. by adding
-	noise) and/or choose the parameters used for executing them on the backend.}
-	\label{fig:diagrams}
-\end{figure}
-
-For the rest of this example we focus only on the postselection case, as the direct sum case is
-analogous. We continue by importing two more functions from PyQBench.
-\begin{lstlisting}[language=Python, caption= Assembling circuits]
-from qbench.schemes.postselection import (
-    assemble_postselection_circuits,
-    compute_probabilities_from_postselection_measurements,
-)
-
-circuits = assemble_postselection_circuits(
-	target=0,
-	ancilla=1,
-	state_preparation=state_prep(),
-	u_dag=u_dag(),
-	v0_dag=v0_dag(),
-	v1_dag=v1_dag(),
-)
-
-\end{lstlisting}
-Recall that for a postselection scheme we have two possible choices of the "unknown" measurement and
-two possible choices of a final measurement, which gives a total of four circuits needed to run the
-benchmark. The function \texttt{assemble\_postselection\_circuits} creates all four circuits and
-places them in a dictionary with keys \texttt{"id\_v0"}, \texttt{"id\_v1"}, \texttt{"u\_v0"},
-\texttt{"u\_v1"}.
-
-We will now run our circuits using noisy and noiseless simulation. We start by creating a noise
-model using Qiskit.
-
-\begin{lstlisting}[language=Python, caption=Adding noise model]
-from qiskit.providers.aer import noise
-
-error = noise.ReadoutError([[0.75, 0.25], [0.8, 0.2]])
-
-noise_model = noise.NoiseModel()
-noise_model.add_readout_error(error, [0])
-noise_model.add_readout_error(error, [1])
-\end{lstlisting}
-Once we have our noise model ready, we can execute the circuits with and without noise. To this end,
-we will use Qiskit’s \texttt{execute} function. One caveat is that we have to keep track which
-measurements correspond to which circuit. We do so by fixing an ordering on the keys in the \texttt{circuits} dictionary.
-\begin{lstlisting}[language=Python, caption=Running  circuits]
-from qiskit import execute
-
-keys_ordering = ["id_v0", "id_v1", "u_v0", "u_v1"]
-all_circuits = [circuits[key] for key in keys_ordering]
-
-counts_noisy = execute(
-	all_circuits,
-	backend=simulator,
-	noise_model=noise_model,
-	shots=10000
-).result().get_counts()
-
-counts_noiseless = execute(
-	all_circuits,
-	backend=simulator,
-	shots=10000
-).result().get_counts()
-\end{lstlisting}
-Finally, we use the measurement counts to compute discrimination probabilities using \texttt{compute\_probabilities\_from\_postselection\_measurements} function.
-
-\begin{lstlisting}[language=Python, caption=Computation probabilities]
-prob_succ_noiseless = compute_probabilities_from_postselection_measurements(
-	id_v0_counts=counts_noiseless[0],
-	id_v1_counts=counts_noiseless[1],
-	u_v0_counts=counts_noiseless[2],
-	u_v1_counts=counts_noiseless[3],
-)
-
-prob_succ_noisy = compute_probabilities_from_postselection_measurements(
-	id_v0_counts=counts_noisy[0],
-	id_v1_counts=counts_noisy[1],
-	u_v0_counts=counts_noisy[2],
-	u_v1_counts=counts_noisy[3],
-)
-
-\end{lstlisting}
-
-We can now examine the results. As an example, in one of our runs, we obtained
-\texttt{prob\_succ\_noiseless = 0.8524401115559386} and \texttt{prob\_succ\_noisy =
-0.5017958400693446}. As expected, for noisy simulations, the result lies further
-away from the target value of \texttt{0.8535533905932737}.
-
-This concludes our example. In the next section, we will show how to use PyQBench's CLI.
-
-\subsection{Using \texttt{qbench} CLI}
-Using PyQBench as a library allows one to conduct a two--qubits benchmark with arbitrary von Neumann
-measurement. However, as discussed in the previous guide, it requires writing some amount of code.
-For a Fourier parametrized family of measurements, PyQBench offers a simplified way of conducting
-benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
-as the following list of steps::
-
-\begin{enumerate}
-
-\item Preparing configuration files describing the backend and the experiment scenario.
-\item Submitting/running experiments. Depending on the experiment scenario, execution can be synchronous, or asynchronous.
-\item (optional) Checking the status of the submitted jobs if the execution is asynchronous.
-\item Resolving asynchronous jobs into the actual measurement outcomes.
-\item Converting obtained measurement outcomes into tabulated form.
-\end{enumerate}
-\subsubsection{Preparing configuration files}
-The configuration of PyQBench CLI is driven by YAML files. The first configuration file
-describes the experiment scenario to be executed. The second file describes the backend.
-Typically, this backend will correspond to the physical device to be benchmarked, but for testing
-purposes one might as well use any other Qiskit--compatible backend including simulators.
-Let us first describe the experiment configuration file, which might look as follow.
-\begin{lstlisting}[language=Python, caption=Defining the experiment, label=lst:experiment]
-type: discrimination-fourier
-qubits:
-	- target: 0
-	  ancilla: 1
-	- target: 1
-      ancilla: 2
-angles:
-	start: 0
-	stop: 2 * pi
-	num_steps: 3
-gateset: ibmq
-method: direct_sum
-num_shots: 100
-\end{lstlisting}
-The experiment file contains the following fields:
-\begin{itemize}
-	\item \texttt{type}: a string describing the type of the experiment. Currently, the only option of  \texttt{type} is \texttt{discrimination-fourier}.
-	\item \texttt{qubits}: a list enumerating pairs of qubits on which the experiment should be run.
-	For configuration in listing \ref{lst:experiment}, the benchmark will run on two pairs of qubits. The first pair is 0 and 1, and
-	the second one is 1 and 2. We decided to describe a pair by using \texttt{target} and
-	\texttt{ancilla} keys rather than using a plain list to emphasize that the role of qubits in the
-	experiment is not symmetric.
-	\item \texttt{angles}: an object describing the range of angles for Fourier parameterized
-	family. The described range is always uniform, starts at the \texttt{start}, ends at
-	\texttt{stop} and contains \texttt{num\_steps} points, including both \texttt{start} and
-	\texttt{stop}. The \texttt{start} and \texttt{stop} can be arithmetic expressions using
-	\texttt{pi} literal. For instance, the range defined in listing \ref{lst:experiment} contains
-	three points: 0, $\pi$ and $2\pi$.
- 	 \item \texttt{gateset}: a string describing the set of gates used in the decomposition of
- 	 circuits in the experiment. The PyQBench contains explicit implementations of circuits The
- 	 possible options are \texttt{[ibmq, lucy, rigetti]}, corresponding to decompositions
- 	 compatible with IBM Q devices, OQC Lucy device, and Rigetti devices. Alternatively, one might
- 	 wish to turn off the decomposition by using a special value \texttt{generic}. However, for this
- 	 to work a backend used for the experiment must natively implement all the gates needed for the
- 	 experiment, as described in \ref{sec:fourier}.
- 	\item \texttt{method}: a string, either \texttt{postselection} or \texttt{direct\_sum}
- 	determining which implementation of the conditional measurement is used.
- 	\item \texttt{num\_shots}: an integer defines how many shots are performed in the experiment for
- 	a particular angle, qubit pair and circuit. Note that if one wishes to compute the total number
- 	of shots in the experiment, it is necessary to take into account that the \texttt{postselection}
- 	method uses twice as many circuits as the \texttt{direct\_sum} method.
-\end{itemize}
-
-The second configuration file describes the backend. We decided to decouple the
-experiment and the backend files because it facilitates their reuse. For instance, the same
-experiment file can be used to run benchmarks on multiple backends, and the same backend description
-file can be used with multiple experiments.
-
-Different Qiskit backends typically require different data for their initialization. Hence, there
-are multiple possible formats of the backend configuration files understood by PyQBench. We refer
-the interested reader to the PyQBench's documentation. Below we describe an example YAML file
-describing IBM Q backend named
-Quito.
-\begin{lstlisting}[language=Python, caption=IBMQ backend, label=lst:backend]
-name: ibmq_quito
-asynchronous: false
-provider:
-	hub: ibm-q
-	group: open
-	project: main
-\end{lstlisting}
-IBMQ backends typically require an access token to IBM Quantum Experience. Since it would be unsafe
-to store it in plain text, the token has to be configured separately in \texttt{IBMQ\_TOKEN}
-environmental variable.
-
-\subsubsection{Remarks on using the asynchronous flag}
-For backends supporting asynchronous execution, the \texttt{asynchronous} setting can be configured
-to toggle it.
-For asynchronous execution to work, the following conditions have to be met:
-\begin{itemize}
-\item Jobs returned by the backend have unique \texttt{job\_id}.
-\item Jobs are retrievable from the backend using the \texttt{backend.retrieve\_job} method, even from another process (e.g. if the original process running the experiment has finished).
-\end{itemize}
-Since PyQBench cannot determine if the job retrieval works for a given backend, it is the user's
-responsibility to ensure that this is the case before setting \texttt{asynchronous} to \texttt{true}.
-
-\subsubsection{Running the experiment and collecting measurements data}
-After preparing YAML files defining experiment and backend,
-running the benchmark can be launched by using the following command line invocation:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier benchmark experiment_file.yml backend_file.yml
-\end{lstlisting}
-The output file will be printed to stdout. Optionally, the \texttt{- -output OUTPUT} parameter might be provided to write the output to the \texttt{OUTPUT} file instead.
-\begin{lstlisting}[language=Python]
-qbench disc-fourier benchmark experiment_file.yml backend_file.yml --output async_results.yml
-\end{lstlisting}
-The result of running the above command can be twofold:
-\begin{itemize}
-	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, \texttt{job\_ids} correlated with the circuit they correspond to.
-	\item If the backend is synchronous, the output will contain measurement outcomes (bitstrings) for each of the circuits run.
-\end{itemize}
-
-For synchronous experiment, the part of output looks similar to the one below. The whole YAML file can be seen in \ref{app:example}.
-%Consider the particular experiment data
-\begin{lstlisting}[language=Python]
-data:
-- target: 0
-  ancilla: 1
-  phi: 0.0
-  results_per_circuit:
-  - name: id
-  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
-  mitigation_info:
-	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
-	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
-  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
-\end{lstlisting}
-	The data includes \texttt{target, ancilla, phi},
-	and \texttt{results\_per\_circuit}.   The first three pieces of information have already been described. The last data  \texttt{results\_per\_circuit} gives us
-	the following additional information:
-	\begin{itemize}
-		\item  \texttt{name}:  the information which measurement is used during experiment, either
-		string \texttt{"u"} for $\PP_{U}$ or string \texttt{"id"} for $\PP_{\Id}$. In this example
-		we consider $\PP_{\Id}$.
-		\item \texttt{histogram}: the dictionary with measurements' outcomes. The keys represent
-		possible bitstrings, whereas the values are the number of occurrences.
-		\item \texttt{mitigation\_info}:  for some backends (notably for backends corresponding to
-		IBM Q devices), \texttt{backends.properties().qubits} contains information that might be
-		used for error mitigation using the MThree method \cite{mthree, mthreepublication}. If this
-		info is available, it will be stored in the \texttt{mitigation\_info} field, otherwise this field will be absent.
-		\item \texttt{mitigated\_histogram}: the histogram with measurements' outcomes after the error mitigation.
-	\end{itemize}
-
-\subsubsection{(Optional) Getting status of asynchronous jobs}
- PyQBench provides also a helper command that will fetch the statuses of asynchronous jobs. The command is:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier status async_results.yml
-\end{lstlisting}
-and it will display dictionary with histogram of statuses.
-
-\subsubsection{Resolving asynchronous jobs}
-For asynchronous experiments, the stored intermediate data has to be resolved in actual
-measurements' outcomes. The following command will wait until all jobs are completed and then write
-a result file.
-\begin{lstlisting}[language=Python]
-qbench disc-fourier resolve async-results.yml resolved.yml
-\end{lstlisting}
-The resolved results, stored in \texttt{resolved.yml}, would look just like if the experiment was
-run synchronously. Therefore, the final results will look the same no matter in which mode the
-benchmark was run, and hence in both cases the final output file is suitable for being an input for
-the command computing the discrimination probabilities.
-
-\subsubsection{Computing probabilities}
-As a last step in the processing workflow, the results file has to be passed to \texttt{tabulate}
-command:
-\begin{lstlisting}[language=Python]
-qbench disc-fourier tabulate results.yml results.csv
-\end{lstlisting}
-A sample CSV file is provided below:
-\begin{table}[ht!]
-\begin{center}
-	\begin{tabular}{|c c c c c c|} 
-		\hline
-		target & ancilla & phi & ideal$\_$prob  & disc$\_$prob & mit$\_$disc$\_$prob \\ [0.5ex] 
-		\hline\hline
-		0 & 1 & 0 & 0.5 & 0.46 & 0.45  \\ 
-		\hline
-		0 & 1 & 3.14 & 1 & 0.95 & 0.98  \\
-		\hline
-		0 & 1 & 6.28 & 0.5 & 0.57 & 0.58  \\
-		\hline
-		1 & 2 & 0 & 0.5  & 0.57 & 0.57 \\
-		\hline
-		1 & 2 & 3.14 & 1 & 0.88 & 0.94  \\ 
-		\hline
-		1 & 2 & 6.28 & 0.5 & 0.55 & 0.56  \\ 
-		\hline
-	\end{tabular}
-\caption{The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
-	\texttt{ideal\_prob}, \texttt{disc\_prob} and, optionally, \texttt{mit\_disc\_prob}. Each row in the
-	table describes results for a tuple of \texttt{(target, ancilla, phi)}.  The reference optimal value
-	of discrimination probability is present in \texttt{ideal\_prob} column, whereas the obtained,
-	empirical discrimination probability can be found in the \texttt{disc\_prob} column. The
-	\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
-	\texttt{Mthree} error mitigation \cite{mthree, mthreepublication}, if it was applied.}
-\label{fig:tabulateresults}
-\end{center}
-\end{table}
-
-\section{Impact}
-With the surge of availability of quantum computing architectures in recent
-years it becomes increasingly difficult to keep track of their relative
-performance. To make this case even more difficult, various providers give
-access to different figures of merit for their architectures. Our package allows
-the user to test various architectures, available through \texttt{qiskit} and
-Amazon BraKet using problems with simple operational interpretation. We provide
-one example built-in in the package. Furthermore, we provide a powerful tool for
-the users to extend the range of available problems in a way that suits their
-needs.
-
-Due to this possibility of extension, the users are able to test specific
-aspects of their architecture of interest. For example, if their problem is
-related to the amount of coherence (the sum of absolute value of off-diagonal
-elements) of the states present during computation, they are able to quickly
-prepare a custom experiment, launch it on desired architectures, gather the
-result, based on which they can decide which specific architecture they should
-use.
-
-Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under an open
-source license which will allow users to utilize and extend our package in their
-specific applications.
-
-\section{Conclusions}
-\label{}
-
-In this study, we develop  a Python library PyQBench, an innovative open-source framework for benchmarking
-gate-based quantum computers.
-
-%%%%%%%%%%%%%%
-PyQBench can benchmark NISQ devices by verifying their capability of
-discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
-command line interface (CLI) for running benchmarks using a predefined parameterized Fourier
-family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
-measurements instead of predefined ones.
-\section{Conflict of Interest}
-We wish to confirm that there are no known
-conflicts of interest associated with this publication and there has been no
-significant financial support for this work that could have influenced its out-
-come.
-
-\section*{Acknowledgements}
-
-This work is  supported by
-the project “Near-term quantum computers Challenges, optimal implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the Team-Net programme of the Foundation for Polish Science co-financed by the European Union under the European Regional Development Fund.
-PL is also a holder of European Union scholarship through the European Social Fund,
-grant InterPOWER (POWR.03.05.00-00-Z305).
-
-\begin{thebibliography}{00}
-\bibitem{preskill} Preskill, J. Quantum Computing in the NISQ era and beyond. Quantum 2 (2018): 79.
-\bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
-\bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
-\bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
-\bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
-\bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
-\bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
-\bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
-\bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
-\bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
-\bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
-\bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
-\bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
-\bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
-\bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
-\bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B.
-(2021).
-Benchmarking near-term quantum computers via random circuit sampling.
-arXiv preprint arXiv:2105.05232.
-\bibitem{knill2008randomized}
-Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R.
-B., Jost, J.
-D., Langer, C., Ozeri, R., Seidelin, S.,  Wineland, D.
-J.
-(2008).
-Randomized benchmarking of quantum gates.
-Physical Review A, 77(1), 012307.
-\bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
-\bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
-\bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
-\bibitem{cross2019validating}
-Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
-\bibitem{moll2018quantum}
-Moll, N., Barkoutsos, P., Bishop, L.
-S., Chow, J.
-M., Cross, A., Egger, D.
-J., Filipp, S., Fuhrer, A., Gambetta, J.
-M., Ganzhorn, M., Kandala, A., Mezzacapo, A., M{\"u}ller, P., Riess, W., Salis, G., Smolin, J., Tavernelli, I.,  Temme, K.
-(2018).
-Quantum optimization using variational algorithms on near-term quantum devices.
-Quantum Science and Technology, 3(3), 030503.
-\bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
-	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
-\bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
-	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G.
-S., Smith, K.
-N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F.
-T.
-(2022).
-Supermarq: A scalable quantum benchmark suite.
-In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) 587-603.
-IEEE.
-\bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
-\bibitem{qiskit-randomized} The web resource at
-\url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
-\bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
-\bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
-\bibitem{cross-entropy-bench} The web resource at
-\url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
-\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. Strategies for
-optimal single-shot discrimination of quantum measurements. Physical Review A
-98.4 (2018): 042103.
-\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge university press.
-\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
-\bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
-\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-\bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
-\bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
-\bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
-\bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
-\bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
-\bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
-\bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
-\bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
-\bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
-\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.
-\bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z.
-(2021).
-On the optimal certification of von Neumann measurements.
-Scientific Reports, 11(1), 3623.
-\bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
-\bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
-\bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H.
-(2017).
-Benchmarking gate-based quantum computers.
-Computer Physics Communications, 220, 44-55.
-\bibitem{zhukov2019quantum} Zhukov, A.
-A., Kiktenko, E.
-O., Elistratov, A.
-A., Pogosov, W.
-V.,  Lozovik, Y.
-E.
-(2019).
-Quantum communication protocols as a benchmark for programmable quantum computers.
-Quantum Information Processing, 18(1), 31.
-\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
-and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
-qubits. Physical Review A 99(6), 062323.
-\bibitem{benedetti2018generative} BBenedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y.,  Perdomo-Ortiz, A.
-(2019).
-A generative modeling approach for benchmarking and training shallow quantum circuits.
-Quantum Information, 5(1), 45.
-
-\end{thebibliography}
-
-\appendix
 
@@
 
-	The celebrated Hausdorf-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
+	The celebrated Hausdorff-T{\"o}plitz theorem~\cite{hausdorff, toeplitz} states that
 	$W(A)$ of any matrix $A \in \mathcal{M}_d$ is a convex set, and therefore we have
@@
 \end{lstlisting}
-
 \end{document}
-\endinput
-%%
-%% End of file `SoftwareX_article_template.tex'.

### 2023-07-10 txt/manuscript.tex
Restore pp. as it is required when citing proceedings
Cleanup directory structure

--- 2023-03-23 txt/manuscript.tex
@@
 
-\usepackage{todonotes}
 \usepackage{url}

### 2023-07-10 txt/manuscript_short.tex

@@
 
-\usepackage{amssymb}
-
-\usepackage{amsthm}
-\usepackage{mathtools}
-
+\usepackage{amsmath,amssymb,amsthm}
+\usepackage{caption}
+\usepackage{float}
 \usepackage{lineno}
 \usepackage{listings}
-
-\usepackage{float}
-
+\usepackage{mathtools}
+\usepackage{subcaption}
 \usepackage{todonotes}
 \usepackage{url}
-
 \usepackage{xcolor}
-
-\usepackage{caption}
-\usepackage{subcaption}
 
@@
 
-%
-%\lstdefinestyle{mystyle}{
-%	backgroundcolor=\color{backcolour},
-%	commentstyle=\color{codegreen},
-%	keywordstyle=\color{magenta},
-%	numberstyle=\tiny\color{codegray},
-%	stringstyle=\color{codepurple},
-%	basicstyle=\ttfamily\footnotesize,
-%	breakatwhitespace=false,
-%	breaklines=true,
-%	captionpos=b,
-%	keepspaces=true,
-%	numbers=left,
-%	numbersep=5pt,
-%	showspaces=false,
-%	showstringspaces=false,
-%	showtabs=false,
-%	tabsize=2
-%}
-%
-%\lstset{style=mystyle}
 \lstset{frame=tb,
@@
 	basicstyle={\small\ttfamily},
-%	numberstyle=\color{blue},
-%	keywordstyle=\color{blue},
-%	commentstyle=\color{PineGreen},
-%	stringstyle=\color{ForestGreen},
 	breaklines=true,
@@
 	escapeinside={@}{@},
-%	literate=
-%	{0}{{{\color{red}0}}}1
-%	{1}{{{\color{red}1}}}1
-%	{2}{{{\color{red}2}}}1
-%	{3}{{{\color{red}3}}}1
-%	{4}{{{\color{red}4}}}1
-%	{5}{{{\color{red}5}}}1
-%	{6}{{{\color{red}6}}}1
-%	{7}{{{\color{red}7}}}1
-%	{8}{{{\color{red}8}}}1
-%	{9}{{{\color{red}9}}}1
-%    {v0}{{{\color{black}v0}}}1 %% we can not style only numeric literals
-%    {v1}{{{\color{black}v1}}}1
 }
@@
 
-\usepackage{amsmath}
 \newtheorem{theorem}{Theorem}
@@
 For the synchronous experiment, the part of the output looks similar to the one below. The whole YAML
-file can be seen in Section \ref{app:example.} in the supplemental material.
+file can be seen in Section \ref{app:example} in the supplemental material.
 %Consider the particular experiment data

### 2023-07-10 txt/manuscript_short.tex

--- 2023-04-13 txt/manuscript_short.tex
@@
 single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
-measurement $\PP_U$ performed in the basis $U$. Note, however, that the discrimination scheme
-described below can work regardless of dimensionality of the system, see
-\cite{puchala2018strategies} for details.
-
+measurement $\PP_U$ performed in the basis $U$. 
 The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
@@
 measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
-outcome $i$, we choose another measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
+outcome $i$, we choose another binary measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
 obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
-$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
+$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$.
+
+Note, however, that the discrimination scheme
+described above can work regardless of dimensionality of the unitary $U$ with such a difference that the size of auxiliary system can be larger than the qubit.
+This size depends on the input state which was taken, explicitly on the Schmidt rank of the optimal input state.
+However, for most discrimination schemes, the  Schmidt rank equals at most two, hence the size of auxiliary system remains qubit, see \cite{puchala2018strategies} for details.
+It is also worth mentioning that despite of the size of auxiliary system, the final measurement $\PP_{V_i}$ is always binary.
+
+Naturally, we need to repeat the
 same procedure multiple times for both measurements to obtain a reliable estimate of the underlying

### 2023-07-12 txt/manuscript_short.tex
Sort usepackage statements
Restore formatting from before merge
Improve text
Co-authored-by: <plewandowska777@gmail.com>

--- 2023-07-10 txt/manuscript_short.tex
@@
 measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
-outcome $i$, we choose another measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
+outcome $i$, we choose another binary measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
 obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
-$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
+$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$.
+
+Note, however, that the discrimination scheme described above can work regardless of dimensionality 
+of the unitary $U$. The main difference is the dimension of the auxiliary system, which in general
+can be larger than two. This dimension depends on the Schmidt rank of the optimal input state. However, 
+for most discrimination schemes, the  Schmidt rank equals at most two, and hence the auxiliary system
+is also a qubit, see \cite{puchala2018strategies} for details. Note that the final measurement $\PP_{V_i}$ 
+is always binary, independently of the dimension of auxiliary system.
+
+Naturally, we need to repeat the
 same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
@@
 For the synchronous experiment, the part of the output looks similar to the one below. The whole YAML
-file can be seen in Section \ref{app:example} in the supplemental material.
+file can be seen in Section \ref{app:example.} in the supplemental material.
 %Consider the particular experiment data

### 2023-07-12 reviews/softwarex/reviews_1/response/response.tex
Rename response.txt to response.tex

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}

\newenvironment{response}{\vspace{1em}\noindent\textbf{Response}}{\vspace{1em}}

\begin{document}
We would like to thank the reviewers for their comments. Below we provide
a response to their specific remarks.

\section{Reviewer 1}

\begin{enumerate}

  \item The generalization of the suggested benchmarking technique to multiple qubits should be described in more detail, 
        explicitly mentioning whether the complexity of the derivation and actual benchmarking depends on the number of 
        qubits.

  \begin{response}
  We thank the referee for this suggestion. We extended the manuscript with a paragraph describing differences between
  a single--qubit and higher-dimensional cases.

\end{enumerate}
\section{Reviewer 2}

\end{document}

### 2023-08-18 txt/manuscript_short.tex
cross-netropy

@@
 
+Finally, we should mention cross-entropy
+benchmarking~\cite{boixo2018characterizing}, which was utlilized in validation
+of the Sycamore-53 QPU supremacy experiments~\cite{arute2019quantum}. In this
+approach, the quality of an algorithm implemented on the QPU is measured by
+calculating the cross entropy of bit-strings actually sampled from the QPU,
+compared to ideal bitstrings.
+
 \section{Preliminaries and discrimination scheme approach}
@@
 single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
-measurement $\PP_U$ performed in the basis $U$. 
+measurement $\PP_U$ performed in the basis $U$. Note, however, that the discrimination scheme
+described below can work regardless of dimensionality of the system, see
+\cite{puchala2018strategies} for details.
+
 The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
@@
 measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
-outcome $i$, we choose another binary measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
+outcome $i$, we choose another measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
 obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
-$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$.
-
-Note, however, that the discrimination scheme described above can work regardless of dimensionality 
-of the unitary $U$. The main difference is the dimension of the auxiliary system, which in general
-can be larger than two. This dimension depends on the Schmidt rank of the optimal input state. However, 
-for most discrimination schemes, the  Schmidt rank equals at most two, and hence the auxiliary system
-is also a qubit, see \cite{puchala2018strategies} for details. Note that the final measurement $\PP_{V_i}$ 
-is always binary, independently of the dimension of auxiliary system.
-
-Naturally, we need to repeat the
+$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
 same procedure multiple times for both measurements to obtain a reliable estimate of the underlying

### 2023-08-18 txt/manuscript_short.tex
add more descirption on pros/cons

@@
 
-Finally, we should mention cross-entropy
-benchmarking~\cite{boixo2018characterizing}, which was utlilized in validation
-of the Sycamore-53 QPU supremacy experiments~\cite{arute2019quantum}. In this
-approach, the quality of an algorithm implemented on the QPU is measured by
-calculating the cross entropy of bit-strings actually sampled from the QPU,
-compared to ideal bitstrings.
-
 \section{Preliminaries and discrimination scheme approach}
@@
 \end{scheme}
+
+Compared to these approaches, our approach allows for very simple operational
+interpretation of the scheme and its results. This is especially useful for
+newcomers to the field, who may be put off by more complicated appraoches.
+Another benefit is, epsecailly for advanced users, the ability to control
+resources utilized during the benchmarking. We can consider here resources such
+as entanglement or coherence. Finally, the figure of merit we wish calculate and
+to which we compare are results is fairly simple to obtain. The main downside of
+our approach is the exponential number of circuits we need to consider.
 

### 2023-08-26 txt/manuscript_short.tex

--- 2023-07-12 txt/manuscript_short.tex
@@
 
+Compared to these approaches, our approach allows for very simple operational
+interpretation of the scheme and its results. This is especially useful for
+newcomers to the field, who may be put off by more complicated appraoches.
+Another benefit is, epsecailly for advanced users, the ability to control
+resources utilized during the benchmarking. We can consider here resources such
+as entanglement or coherence. Finally, the figure of merit we wish calculate and
+to which we compare are results is fairly simple to obtain. The main downside of
+our approach is the exponential number of circuits we need to consider.
+
 % \subsubsection{Constructing optimal discrimination scheme}

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex
Generalization for larger U (#3)
Generalization for larger U + CI/CD qol improvements
Add response to reviewer

@@
 \begin{enumerate}
+  \item The cross-entropy benchmarking technique used in the validation of the Sycamore-53 QPU in
+    quantum supremacy experiments (https://www.nature.com/articles/s41586-019-1666-5) should also
+    be mentioned in the Introduction (https://www.nature.com/articles/s41567-018-0124-x).
 
-  \item The generalization of the suggested benchmarking technique to multiple qubits should be described in more detail, 
-        explicitly mentioning whether the complexity of the derivation and actual benchmarking depends on the number of 
-        qubits.
+    \begin{response} We modified manuscript to include mention of cross-entropy benchmarking as
+      suggested by the referee.
+    \end{response}
+  \item The generalization of the suggested benchmarking techniqiue to multiple qubits should be
+    described in more detail, explicitly mentioning whether the complexity of the derivation and
+    actual benchmarking depends on the number of qubits.
 
-  \begin{response}
-  We thank the referee for this suggestion. We extended the manuscript with a paragraph describing differences between
-  a single--qubit and higher-dimensional cases.
+    \begin{response} We thank the referee for this suggestion. We extended the manuscript with a
+      paragraph describing differences between a single--qubit and higher-dimensional cases.
+    \end{response}
 

### 2023-08-26 txt/manuscript_short.tex
Fix typos and grammar issues

--- 2023-08-18 txt/manuscript_short.tex
@@
 
-Compared to these approaches, our approach allows for very simple operational
+Compared to these approaches, our approach allows for a very simple operational
 interpretation of the scheme and its results. This is especially useful for
-newcomers to the field, who may be put off by more complicated appraoches.
-Another benefit is, epsecailly for advanced users, the ability to control
+newcomers to the field, who may be put off by more complicated approaches.
+Another benefit is, especially for advanced users, the ability to control
 resources utilized during the benchmarking. We can consider here resources such
-as entanglement or coherence. Finally, the figure of merit we wish calculate and
-to which we compare are results is fairly simple to obtain. The main downside of
+as entanglement or coherence. Finally, the figure of merit we wish to calculate and
+to which we compare the results is fairly simple to obtain. The main downside of
 our approach is the exponential number of circuits we need to consider.

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex
Include response + response url formatting

@@
 \usepackage{enumitem}
-
+\usepackage[hyphens]{url}
 \newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}
@@
 \begin{enumerate}
+  \item[] In my opinion, the weakest part of the paper is the lack of a more detailed analysis of the pros and cons of the suggested benchmarking scheme and its thorough comparison with other existing NISQ benchmarking schemes.
+Thus, I recommend a minor revision where I would ask the authors to better describe advantages and disadvantages of the suggested NISQ benchmarking scheme with respect to other existing NISQ benchmarking techniques.
+Although the focus of the paper is the PyQBench software, I find it important for the reader to have a clear understanding where and how the underlying NISQ benchmarking technique and corresponding software are superior to other available techniques and software.
+
+  \begin{response}
+    We improved the manuscript, which now includes a short section explaining the pros and cons of our method in the context of other existing benchmarking methods.
+Due to the length limitations in the journal, we do not think this section can become any longer, but we are open to further improvement suggestions if the reviewer finds the current analysis lacking.
+  \end{response}
   \item The cross-entropy benchmarking technique used in the validation of the Sycamore-53 QPU in
-    quantum supremacy experiments (https://www.nature.com/articles/s41586-019-1666-5) should also
-    be mentioned in the Introduction (https://www.nature.com/articles/s41567-018-0124-x).
+    quantum supremacy experiments (\url{https://www.nature.com/articles/s41586-019-1666-5}) should also
+    be mentioned in the Introduction (\url{https://www.nature.com/articles/s41567-018-0124-x}).
 

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex
Use latexindent on response.tex

@@
 \begin{enumerate}
-  \item[] In my opinion, the weakest part of the paper is the lack of a more detailed analysis of the pros and cons of the suggested benchmarking scheme and its thorough comparison with other existing NISQ benchmarking schemes.
-Thus, I recommend a minor revision where I would ask the authors to better describe advantages and disadvantages of the suggested NISQ benchmarking scheme with respect to other existing NISQ benchmarking techniques.
-Although the focus of the paper is the PyQBench software, I find it important for the reader to have a clear understanding where and how the underlying NISQ benchmarking technique and corresponding software are superior to other available techniques and software.
+  \item  In my opinion, the weakest part of the paper is the lack of a more
+    detailed analysis of the pros and cons of the suggested benchmarking scheme
+    and its thorough comparison with other existing NISQ benchmarking schemes.
+    Thus, I recommend a minor revision where I would ask the authors to better
+    describe advantages and disadvantages of the suggested NISQ benchmarking
+    scheme with respect to other existing NISQ benchmarking techniques.
+    Although the focus of the paper is the PyQBench software, I find it
+    important for the reader to have a clear understanding where and how the
+    underlying NISQ benchmarking technique and corresponding software are
+    superior to other available techniques and software.
 
     \begin{response}
-    We improved the manuscript, which now includes a short section explaining the pros and cons of our method in the context of other existing benchmarking methods.
-Due to the length limitations in the journal, we do not think this section can become any longer, but we are open to further improvement suggestions if the reviewer finds the current analysis lacking.
+      We improved the manuscript, which now includes a short section explaining
+      the pros and cons of our method in the context of other existing
+      benchmarking methods. Due to the length limitations in the journal, we do
+      not think this section can become any longer, but we are open to further
+      improvement suggestions if the reviewer finds the current analysis
+      lacking.
     \end{response}
-  \item The cross-entropy benchmarking technique used in the validation of the Sycamore-53 QPU in
-    quantum supremacy experiments (\url{https://www.nature.com/articles/s41586-019-1666-5}) should also
-    be mentioned in the Introduction (\url{https://www.nature.com/articles/s41567-018-0124-x}).
+  \item The cross-entropy benchmarking technique used in the validation of the
+    Sycamore-53 QPU in quantum supremacy experiments
+    (\url{https://www.nature.com/articles/s41586-019-1666-5}) should also be
+    mentioned in the Introduction
+    (\url{https://www.nature.com/articles/s41567-018-0124-x}).
 
-    \begin{response} We modified manuscript to include mention of cross-entropy benchmarking as
-      suggested by the referee.
+    \begin{response} We modified manuscript to include mention of cross-entropy
+                     benchmarking as suggested by the referee.
     \end{response}
-  \item The generalization of the suggested benchmarking techniqiue to multiple qubits should be
-    described in more detail, explicitly mentioning whether the complexity of the derivation and
-    actual benchmarking depends on the number of qubits.
+  \item The generalization of the suggested benchmarking techniqiue to multiple
+    qubits should be described in more detail, explicitly mentioning whether
+    the complexity of the derivation and actual benchmarking depends on the
+    number of qubits.
 
-    \begin{response} We thank the referee for this suggestion. We extended the manuscript with a
-      paragraph describing differences between a single--qubit and higher-dimensional cases.
+    \begin{response} We thank the referee for this suggestion. We extended the
+                     manuscript with a paragraph describing differences between
+                     a single--qubit and higher-dimensional cases.
     \end{response}

### 2023-08-26 txt/manuscript_short.tex
Adds discussion on cross entropy benchmarking (#13)
* cross-netropy

* Add response to reviewer

---------

Co-authored-by: Konrad Jałowiecki <dexter2206@gmail.com>

@@
 
-Compared to these approaches, our approach allows for a very simple operational
-interpretation of the scheme and its results. This is especially useful for
-newcomers to the field, who may be put off by more complicated approaches.
-Another benefit is, especially for advanced users, the ability to control
-resources utilized during the benchmarking. We can consider here resources such
-as entanglement or coherence. Finally, the figure of merit we wish to calculate and
-to which we compare the results is fairly simple to obtain. The main downside of
-our approach is the exponential number of circuits we need to consider.
-
 % \subsubsection{Constructing optimal discrimination scheme}

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex
Add response about XACC and CUDA Quantum to response file

@@
     \end{response}
+  \item When discussing the existing quantum computing frameworks, the
+    Introduction should also mention the XACC framework which is known for its
+    cross-architectural as well as cross-language portability
+    (https://iopscience.iop.org/article/10.1088/2058-9565/ab6bf6).
+    Additionally, the recent CUDA-Quantum framework backed by NVIDIA
+    (https://github.com/NVIDIA/cuda-quantum) is worth mentioning as well.
+    \begin{response}
+      Both XACC and CUDA Quantum have now been mentioned in the manuscript.
+    \end{response}
   \item The cross-entropy benchmarking technique used in the validation of the
@@
 
-    \begin{response} We modified manuscript to include mention of cross-entropy
-                     benchmarking as suggested by the referee.
+    \begin{response}
+      We modified manuscript to include mention of cross-entropy benchmarking
+      as suggested by the referee.
     \end{response}
@@
 
-    \begin{response} We thank the referee for this suggestion. We extended the
-                     manuscript with a paragraph describing differences between
-                     a single--qubit and higher-dimensional cases.
+    \begin{response}
+      We thank the referee for this suggestion. We extended the manuscript with
+      a paragraph describing differences between a single--qubit and
+      higher-dimensional cases.
     \end{response}

### 2023-08-27 txt/manuscript_short.tex
Add references to XACC and CUDA Quantum
Respond to reviewers and improve manuscript (#15)
* Add references to XACC and CUDA Quantum

* Add response about XACC and CUDA Quantum to response file

* Add figure with architecture overview.

--- 2023-08-26 txt/manuscript_short.tex
@@
 API. On top of that, several libraries and frameworks can integrate with multiple hardware vendors.
-Examples of such frameworks include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.
+Examples of such frameworks include IBM Q's Qiskit, Zapata Computing's Orquestra \cite{zapata}, XACC \cite{xacc} and NVIDIA's CUDA Quantum \cite{cudaquantum}.
 
@@
 implemented as a part of \texttt{qbench} Python package. The exposed CLI tool is also named
-\texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead
-refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the
+\texttt{qbench}.
+For brevity, we do not discuss the exact structure of the package here, and instead limit ourselves to summarizing the architecture on the diagram in Fig.
+\ref{fig:architecture}.
+For further details, we refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the
 reference manual \cite{pyqbenchdocs}.
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{pics/architecture.pdf}
+  \caption{Overview of PyQBench's architecture.}
+  \label{fig:architecture}
+\end{figure}
 

### 2023-08-30 txt/manuscript_short.tex
Add original expansion of state-of-the-art section written by P. Lewandowska

@@
 device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
-\cite{forest-benchmarking}.
+\cite{forest-benchmarking}. Another, equally popular benchmarking method is
+quantum tomography. Such
+Python package using this approach for benchmarking NISQ devices can be found in \cite{tomography}. The theory behind the software could be found in \cite{bantysh2021quantum}.
+
+Different authors, Patel et al. \cite{patel2020experimental}  evaluated
+several IBM-Q machines using seven benchmarks regarding the
+error and execution time. Roughly the same time, LaRose \cite{larose2019overview} extended benchmarking methods  comparing up to
+four widely used QC programming environments i.e. PyQuil, Qiskit, Project and QDK/Q$\#$
+in terms of library support, hardware, compiler and simulator performance.
+
+QASMBench \cite{li2023qasmbench} is  one of the first benchmark suite aiming at evaluating NISQ
+devices using quantum applications from a broad range of domains. Their  approach  is mainly based on fidelity estimation. They analyze and compare the fidelity of executions
+among the IBM-Q machines, the IonQ QPU and the Rigetti Aspen M-1 system.
 

### 2023-08-30 txt/manuscript_short.tex
Attempt to improve text.

--- 2023-08-27 txt/manuscript_short.tex
@@
 device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
-\cite{forest-benchmarking}.
+\cite{forest-benchmarking}. Another, equally popular, benchmarking method is
+quantum tomography \cite{bantysh2021quantum}. Implementation of quantum tomography for
+benchmarking NISQ devices can be found in \cite{tomography}.
+
+In \cite{patel2020experimental}, the authors evaluated several IBM-Q machines using seven benchmarks
+taking into account the errors and execution time.
+
+QASMBench \cite{li2023qasmbench} is one of the first benchmark suites aiming at evaluating NISQ
+devices using quantum applications from a broad range of domains, mainly using an approach based on
+fidelity estimation. The benchmark presented in the paper compares the fidelity of execution among
+the IBM-Q machines, the IonQ QPU and the Rigetti Aspen M-1 system.
 
 Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
-characterizes capacity of a device for solving computational problems. It takes into account
-multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library
-allows one to measure quantum volume of a device by using its \texttt{qiskit.ignis.verifica \\
-tion.quantum\_volume}. Other implementations of Quantum Volume can be found as well, see e.g.
+characterizes the capacity of a device for solving computational problems. It takes into account
+multiple factors like the number of qubits, connectivity and measurement errors. The Qiskit library
+allows one to measure the quantum volume of a device by using its \texttt{qiskit.ignis.verification.quantum\_volume}. Other implementations of Quantum Volume can be found as well, see e.g.
 \cite{volume-in-practice}.

### 2023-08-30 reviews/softwarex/reviews_1/response/response.tex
Add paper about standardization

@@
 We would like to thank the reviewers for their comments. Below we provide
-a response to their specific remarks.
+responses to their specific remarks.
 
@@
     \end{response}
-
+  \item The references in Supplementary Materials are unresolved.
+    \begin{response}
+      We apologize for this technical error. The references should now be resolved.
+    \end{response}
 \end{enumerate}
 \section{Reviewer 2}
-
+\item Please extend state-of-the-art: The topic is very hot, including ongoing
+  standardization activities.
+  \begin{response}
+    We extended the state-of-the-art section, which now references several more papers.
+  \end{response}
+  \item Please add more visual material on the SW architecture - UML Diagrams, Component
+  Diagrams --> you can put them in the main part of the paper, such
+  that the presentation is easier to follow.
+  \begin{response}
+    We added a diagram summarizing the software architecture.
+  \end{response}
 \end{document}

### 2023-08-30 reviews/softwarex/reviews_1/response/response.tex
Add missing enumerate env
Improve response formatting

@@
     Introduction should also mention the XACC framework which is known for its
-    cross-architectural as well as cross-language portability
+    cross-architectural as well as cross-language portability \\
     (https://iopscience.iop.org/article/10.1088/2058-9565/ab6bf6).
@@
 \section{Reviewer 2}
+\begin{enumerate}
   \item Please extend state-of-the-art: The topic is very hot, including ongoing
     standardization activities.
+
     \begin{response}
@@
     that the presentation is easier to follow.
+
     \begin{response}
@@
     \end{response}
+\end{enumerate}
 \end{document}

### 2023-08-30 txt/manuscript_short.tex
Expand the state of the art section (#16)
Fixes #9 

The initial version of this PR was created by @plewandowska777.

@@
 
-Finally, we should mention cross-entropy
+We should also mention cross-entropy
 benchmarking~\cite{boixo2018characterizing}, which was utlilized in validation
@@
 compared to ideal bitstrings.
+
+Finally, it is worth pointing out there is an ongoing effort towards standardization
+of benchmarking of quantum computers. In \cite{standardization}, the authors present
+plans for designing a benchmarking suite based on measuring a set of standardized
+key performance indicators (KPIs).
 

### 2023-10-05 txt/manuscript_short.tex
Move section 2 to the appendix + conciseness pass

--- 2023-08-30 txt/manuscript_short.tex
@@
 \cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu
-\cite{xanadu}. Other vendors offer devices operating in different paradigms. Notably, one could
-mention D-Wave \cite{dwave} and their quantum annealers, or QuEra devices \cite{quera} based on
-neural atoms. Most vendors provide their own software stack and application programming interface
-for accessing their devices. To name a few, Rigetti's computers are available through their Forest
+\cite{xanadu}. Other vendors offer devices operating in different paradigms. e.g.  D-Wave \cite{dwave}
+and their quantum annealers, or QuEra devices \cite{quera} based on neural atoms. Most vendors provide their own
+software stack for interacting with their devices. Rigetti's computers are available through Forest
 SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
-through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}. Some cloud
-services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified
-API. On top of that, several libraries and frameworks can integrate with multiple hardware vendors.
-Examples of such frameworks include IBM Q's Qiskit, Zapata Computing's Orquestra \cite{zapata}, XACC \cite{xacc} and NVIDIA's CUDA Quantum \cite{cudaquantum}.
+through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}. Amazon Braket
+\cite{amazon} offers access to several quantum devices under a unified API. There are also several
+libraries able to integrate with multiple hardware vendors. Examples include IBM Q's Qiskit, Zapata Computing's
+Orquestra \cite{zapata}, XACC \cite{xacc} and NVIDIA's CUDA Quantum \cite{cudaquantum}.
 
@@
 cornelissen2021scalable}, benchmarks based on the quantum volume \cite{cross2019validating,
-moll2018quantum, pelofske2022volume}.
+moll2018quantum, pelofske2022volume} or quantum tomography \cite{bantysh2021quantum}.
 
 In this paper, we introduce a different approach to benchmarking gate--based devices with a simple
-operational interpretation. In our method, we test how well the given device is at guessing which of
+operational interpretation. In our method, we test how good the given device is at guessing which of
 the two known von Neumann measurements were performed during the experiment. We implemented our
-approach in an open-source Python library called PyQBench. The library supports any device available
-through the Qiskit library, and thus can be used with providers such as IBM Q or Amazon Braket.
-Along with the library, the PyQBench package contains a command line tool for running most common
+approach in an open-source Python library PyQBench. The library supports any device available
+through the Qiskit library, including all  IBM Q or Amazon Braket.
+Along with the library, the PyQBench package contains a command line tool for running the most common
 benchmarking scenarios.
-
-\section{Existing benchmarking methodologies and software}
-Unsurprisingly, PyQBench is not the only software package for benchmarking gate--based devices.
-While we believe that our approach has significant benefits over other benchmarking techniques, for
-completeness, in this section we discuss some of the currently available similar software.
-
-Probably the simplest benchmarking method one could devise is simply running known algorithms and
-comparing outputs with the expected ones. Analyzing the frequency of the correct outputs, or the
-deviation between actual and expected outputs distribution provides then a metric of the performance
-of a given device. Libraries such as Munich Quantum Toolkit (MQT) \cite{mqt2022, mqt-bench} or
-SupermarQ \cite{supermarq, supermarkq-github} contain benchmarks leveraging multiple algorithms,
-such as Shor's algorithm or Grover's algorithm.
-% or  implementing e.g. GHZ state \cite{ghz}.
-Despite being intuitive and easily interpretable, such benchmarks may have some problems. Most
-importantly, they assess the usefulness of a quantum device only for a very particular algorithm,
-and it might be hard to extrapolate their results to other algorithms and applications. For
-instance, the inability of a device to consistently find factorizations using Shor's algorithms does
-not tell anything about its usefulness in Variational Quantum Algorithm's.
-
-Another possible approach to benchmarking quantum computers is randomized benchmarking. In this
-approach, one samples circuits to be run from some predefined set of gates (e.g. from the Clifford
-group) and tests how much the output distribution obtained from the device running these circuits
-differs from the ideal one. It is also common to concatenate randomly chosen circuits with their
-inverses (which should yield the identity circuit) and run those concatenated circuits on the
-device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
-\cite{forest-benchmarking}. Another, equally popular, benchmarking method is
-quantum tomography \cite{bantysh2021quantum}. Implementation of quantum tomography for
-benchmarking NISQ devices can be found in \cite{tomography}.
-
-In \cite{patel2020experimental}, the authors evaluated several IBM-Q machines using seven benchmarks
-taking into account the errors and execution time.
-
-QASMBench \cite{li2023qasmbench} is one of the first benchmark suites aiming at evaluating NISQ
-devices using quantum applications from a broad range of domains, mainly using an approach based on
-fidelity estimation. The benchmark presented in the paper compares the fidelity of execution among
-the IBM-Q machines, the IonQ QPU and the Rigetti Aspen M-1 system.
-
-Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
-characterizes the capacity of a device for solving computational problems. It takes into account
-multiple factors like the number of qubits, connectivity and measurement errors. The Qiskit library
-allows one to measure the quantum volume of a device by using its \texttt{qiskit.ignis.verification.quantum\_volume}. Other implementations of Quantum Volume can be found as well, see e.g.
-\cite{volume-in-practice}.
-
-Finally, we should mention cross-entropy
-benchmarking~\cite{boixo2018characterizing}, which was utlilized in validation
-of the Sycamore-53 QPU supremacy experiments~\cite{arute2019quantum}. In this
-approach, the quality of an algorithm implemented on the QPU is measured by
-calculating the cross entropy of bit-strings actually sampled from the QPU,
-compared to ideal bitstrings.
 
@@
 discussing necessary mathematical preliminaries. Then, we present the general form of the
-discrimination scheme used in PyQBench and practical considerations on how to implement it taking
-into account the limitations of the current NISQ devices. We encourage the readers interested
-in a more in--depth discussion of the mathematical foundations behind our discrimination scheme to read
-Section \ref{app:preliminaries} in the supplemental materials.
+discrimination scheme used in PyQBench and discuss it in the context of current, limited NISQ devices.
+We refer readers interested in more details concerning the mathematical foundations behind PyQBench to Section
+\ref{app:preliminaries} in the supplementary material.
 
@@
 A von Neumann measurement $\PP$ is a collection of rank--one projectors
-$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to the identity operator, i.e.
+$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$ that sum up to the identity operator, i.e.
 $ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$, one can construct
-a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this case we say that
+a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this case, we say that
 $\PP_{U}$ is described by the matrix $U$.
@@
 \cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between
-single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
+single qubit measurements $\PP_\Id$, performed in the Z-basis, and an alternative
 measurement $\PP_U$ performed in the basis $U$. 
-The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
+The scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
 auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the
@@
 
-Note, however, that the discrimination scheme described above can work regardless of dimensionality 
+Note, however, that the discrimination scheme described above can work regardless of the dimensionality
 of the unitary $U$. The main difference is the dimension of the auxiliary system, which in general
 can be larger than two. This dimension depends on the Schmidt rank of the optimal input state. However, 
-for most discrimination schemes, the  Schmidt rank equals at most two, and hence the auxiliary system
+for most discrimination schemes, the  Schmidt rank equals at most two, and the auxiliary system
 is also a qubit, see \cite{puchala2018strategies} for details. Note that the final measurement $\PP_{V_i}$ 
-is always binary, independently of the dimension of auxiliary system.
+is always binary, independently of the dimension of the auxiliary system.
 
@@
 Current NISQ devices are unable to perform conditional measurements, which is the biggest obstacle
-to implementing our scheme on real hardware. However, we circumvent this problem by slightly
-adjusting our scheme so that it only uses components available on current devices. For this purpose,
-we use two possible options: using a postselection or a direct sum $V_0^\dagger\oplus V_1^\dagger$.
+to implementing our scheme on real hardware. We circumvent this problem by slightly
+adjusting our scheme to only use components available on current devices. There are two possible options: using a postselection or a direct sum $V_0^\dagger\oplus V_1^\dagger$.
 
@@
 	The first idea uses a postselection scheme. In the original scheme, we measure the first qubit
-	and only then determine which measurement should be performed on the second one. Instead of doing
-	this choice, we can run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and measure both
-	qubits. We then discard the results of the circuit for which label $i$ does not match measurement
-	label $k$. Hence, the circuit for postselection looks as depicted in Fig.
+	and only then determine which measurement should be performed on the second one. Instead, we can
+	run two circuits, one with $\PP_{V_0}$ and one with $\PP_{V_1}$ and measure both
+	qubits. We can then discard the results of the circuit for which label $i$ does not match measurement
+	label $k$. The circuit for postselection looks as depicted in Fig.
 	\ref{fig:postselection}.
@@
 	Fig. \ref{fig:directsum}. Now, depending on the outcome $i$, one of the summands in
-	Eq. \eqref{eq:directsum} vanishes, and we end up performing exactly the same operations as in
+	Eq. \eqref{eq:directsum} vanishes, and we end up performing the same operations as in
 	the original scheme.
@@
 
-Compared to these approaches, our approach allows for a very simple operational
+Compared to other approaches, our approach allows for a very simple operational
 interpretation of the scheme and its results. This is especially useful for
@@
 \end{enumerate}
-Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt in
+Note that the execution of circuits by PyQBench is optional. The user might opt-in
 for fine-grained control over the execution of the circuits. For instance, suppose the user wants to
@@
 this particular family of measurements in their benchmarks, then using PyQBench as a command line tool
-might be more straightforward. PyQBench's command line interface allows running the benchmarking process
-without writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the
-benchmark to be performed and the description of the backend on which the benchmark should be run.
+is a more straightforward way. The PyQBench's CLI does not require writing Python code and is driven
+by YAML \cite{yaml} files describing the benchmark to be performed and the description of the backend on which the benchmark should be run.
 The same benchmark can be used with different backends and vice versa.
@@
 \subsubsection{Overview of the software structure}
-As already described, PyQBench can be used both as a library and a CLI. Both functionalities are
+PyQBench can be used both as a library and a CLI. Both functionalities are
 implemented as a part of \texttt{qbench} Python package. The exposed CLI tool is also named
 \texttt{qbench}.
-For brevity, we do not discuss the exact structure of the package here, and instead limit ourselves to summarizing the architecture on the diagram in Fig.
+For brevity, we limit ourselves here to summarizing the architecture on the diagram in Fig.
 \ref{fig:architecture}.
-For further details, we refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the
-reference manual \cite{pyqbenchdocs}.
+For further details, we refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the reference manual \cite{pyqbenchdocs}.
 
@@
 
-PyQBench can be installed from official Python Package Index (PyPI) by running \texttt{pip install
-pyqbench}. In a properly configured Python environment the installation process should also make the
+PyQBench can be installed from the official Python Package Index (PyPI) by running \texttt{pip install
+pyqbench}. In a properly configured Python environment, the installation process should also make the
 \texttt{qbench} command available to the user without a need for further configuration.
@@
 
-When using PyQBench as library, instances of Qiskit backends can be passed to functions that expect
-them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
-backend. An example of such file can be found in Section \ref{sec:examples}, and the detailed
-description of the expected format can be found at PyQBench's documentation.
+When using PyQBench as a library, instances of Qiskit backends can be passed to functions that expect
+them as parameters. In CLI mode, the user has to provide a YAML file describing the
+backend. An example of such a file can be found in Section \ref{sec:examples}, and the detailed
+description of the expected format can be found in  PyQBench's documentation.
 
@@
 
-The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
+The Command Line Interface (CLI) of PyQBench has a nested structure. The general form of the CLI
 invocation is shown in listing \ref{lst:cli}.
@@
 \subsection{Using \texttt{qbench} CLI}
-PyQBench offers a simplified way of conducting benchmarks using a Command Line Interface (CLI).
 The workflow with PyQBench's CLI can be summarized as the following list of steps:
@@
 The configuration of PyQBench CLI is driven by YAML files. The first configuration file describes
-the experiment scenario to be executed. The second file describes the backend. Typically, this
+the experiment scenari. The second file describes the backend. Typically, this
 backend will correspond to the physical device to be benchmarked, but for testing purposes, one
-might as well use any other Qiskit--compatible backend including simulators. Let us first describe
-the experiment configuration file, which might look as follow.
+might as well use any other Qiskit--compatible backend including simulators. The experiment configuration
+file, which might look as follows.
 \begin{lstlisting}[language=Python, caption=Defining the experiment, label=lst:experiment]
@@
 The second configuration file describes the backend. We decided to decouple the experiment and the
-backend files because it facilitates their reuse. For instance, the same experiment file can be used
+backend files because it facilitates their reuse. The same experiment file can be used
 to run benchmarks on multiple backends, and the same backend description file can be used with
@@
 \subsubsection{Running the experiment and collecting measurements data}
-After preparing YAML files defining experiment and backend,
+After preparing YAML files defining an experiment and backend,
 running the benchmark can be launched by using the following command line invocation:
@@
 run synchronously. Therefore, the final results will look the same no matter in which mode the
-benchmark was run, and hence in both cases the final output file is suitable for being an input for
+benchmark was run, and hence in both cases, the final output file is suitable for being an input for
 the command computing the discrimination probabilities.
@@
 With the surge of availability of quantum computing architectures in recent years it becomes
-increasingly difficult to keep track of their relative performance. To make this case even more
-difficult, various providers give access to different figures of merit for their architectures. Our
+increasingly difficult to keep track of their relative performance. Moreover, various providers give access to different figures of merit for their architectures. Our
 package allows the user to test various architectures, available through \texttt{qiskit} and Amazon
@@
 
-Due to this possibility of extension, the users are able to test specific aspects of their
+Due to this possibility of extension, the users can test specific aspects of their
 architecture of interest. For example, if their problem is related to the amount of coherence (the

### 2023-10-05 txt/supplemental.tex
Cleanup manuscript and supplemental file
Temporarily change supplemental to verify CI works
Revert changes in supplemental material
Move section 2 to the appendix + conciseness pass

--- 2023-04-13 software_x_submission/supplemental.tex
@@
 
+\section{Existing benchmarking methodologies and software}
+Unsurprisingly, PyQBench is not the only software package for benchmarking gate--based devices.
+While we believe that our approach has significant benefits over other benchmarking techniques, for
+completeness, in this section we discuss some of the currently available similar software.
+
+Probably the simplest benchmarking method one could devise is simply running known algorithms and
+comparing outputs with the expected ones. Analyzing the frequency of the correct outputs, or the
+deviation between actual and expected outputs distribution provides then a metric of the performance
+of a given device. Libraries such as Munich Quantum Toolkit (MQT) \cite{mqt2022, mqt-bench} or
+SupermarQ \cite{supermarq, supermarkq-github} contain benchmarks leveraging multiple algorithms,
+such as Shor's algorithm or Grover's algorithm.
+% or  implementing e.g. GHZ state \cite{ghz}.
+Despite being intuitive and easily interpretable, such benchmarks may have some problems. Most
+importantly, they assess the usefulness of a quantum device only for a very particular algorithm,
+and it might be hard to extrapolate their results to other algorithms and applications. For
+instance, the inability of a device to consistently find factorizations using Shor's algorithms does
+not tell anything about its usefulness in Variational Quantum Algorithm's.
+
+Another possible approach to benchmarking quantum computers is randomized benchmarking. In this
+approach, one samples circuits to be run from some predefined set of gates (e.g. from the Clifford
+group) and tests how much the output distribution obtained from the device running these circuits
+differs from the ideal one. It is also common to concatenate randomly chosen circuits with their
+inverses (which should yield the identity circuit) and run those concatenated circuits on the
+device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
+\cite{forest-benchmarking}. Another, equally popular, benchmarking method is
+quantum tomography \cite{bantysh2021quantum}. Implementation of quantum tomography for
+benchmarking NISQ devices can be found in \cite{tomography}.
+
+In \cite{patel2020experimental}, the authors evaluated several IBM-Q machines using seven benchmarks
+taking into account the errors and execution time.
+
+QASMBench \cite{li2023qasmbench} is one of the first benchmark suites aiming at evaluating NISQ
+devices using quantum applications from a broad range of domains, mainly using an approach based on
+fidelity estimation. The benchmark presented in the paper compares the fidelity of execution among
+the IBM-Q machines, the IonQ QPU and the Rigetti Aspen M-1 system.
+
+Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
+characterizes the capacity of a device for solving computational problems. It takes into account
+multiple factors like the number of qubits, connectivity and measurement errors. The Qiskit library
+allows one to measure the quantum volume of a device by using its \texttt{qiskit.ignis.verification.quantum\_volume}. Other implementations of Quantum Volume can be found as well, see e.g.
+\cite{volume-in-practice}.
+
+We should also mention cross-entropy
+benchmarking~\cite{boixo2018characterizing}, which was utlilized in validation
+of the Sycamore-53 QPU supremacy experiments~\cite{arute2019quantum}. In this
+approach, the quality of an algorithm implemented on the QPU is measured by
+calculating the cross entropy of bit-strings actually sampled from the QPU,
+compared to ideal bitstrings.
+
+Finally, it is worth pointing out there is an ongoing effort towards standardization
+of benchmarking of quantum computers. In \cite{standardization}, the authors present
+plans for designing a benchmarking suite based on measuring a set of standardized
+key performance indicators (KPIs).
+
 \section{Mathematical preliminaries} \label{app:preliminaries}
-
 Let $\mathcal{M}_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
@@
 \end{lstlisting}
+\bibliographystyle{unsrt}
+\bibliography{references}
 \end{document}

### 2023-10-09 txt/manuscript_short.tex
Explain NISQ devices

--- 2023-08-30 txt/manuscript_short.tex
@@
 
-Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market, with a wide
+Quantum devices are storming the market, with a wide
 selection of devices based on different architectures and accompanying software solutions. Among
@@
 
-It is well known that NISQ devices have their limitations \cite{preskillnew}. The question is to
-what extent those devices can perform meaningful computations? To answer this question, one has to
+All of the currently available quantum computers have to be classified as NISQ, or Noisy Intermediate-Scale
+Quantum devices.
+The term NISQ denotes quantum computers of an intermediate size expected in the next few years, typically comprising 50 to a few hundred qubits.
+The significance of reaching 50 qubits lies in surpassing the simulation capabilities of current digital supercomputers.
+The term 'Noisy' underscores the imperfect control over qubits, with noise imposing substantial limitations on the achievable outcomes of quantum devices in the short term \cite{preskill,preskillnew}.
+The question is to what extent those devices can perform meaningful computations?
+To answer this question, one has to
 devise a methodology for benchmarking them. For gate--based computers, on which this paper focuses,
